### 2022-04-06 ms.tex
init uncmod paper by copying out intro from cogsci2022 and putting in 3 prelim subfigs

% Author: Matthew Turner

% \documentclass[11pt,letterpaper]{article}
\documentclass[letterpaper,11.5pt]{scrartcl}
% \documentclass[11pt]{report}
% \documentclass{report}
% \documentclass{book}
\usepackage[bookmarks, hidelinks]{hyperref}
\usepackage{amssymb,amsmath}
% \usepackage{fullpage}
\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{float}
% \usepackage[margin=1.00in]{geometry}
\usepackage[margin=0.90in]{geometry}

\usepackage{caption}
\usepackage{booktabs}
\usepackage{pslatex}
\usepackage{apacite}
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{wrapfig}
\usepackage[english]{babel}
\usepackage{lmodern}
\usepackage{setspace}
\doublespace
% \usepackage{url}
\usepackage{bigfoot}
\usepackage[export]{adjustbox}
\setlength\intextsep{0pt}

\usepackage{graphicx}

\title{Some forms of uncertainty may suppress the evolution of social learning}

\author{{}}

\begin{document}
\maketitle

\begin{abstract}

Social learning is essential to survival. It is likely to evolve when it is more
efficient than asocial, trial-and-error learning. The consensus in cultural
evolutionary theory holds that some amount of environmental variability and
uncertainty about the best decisions are necessary for social learning to evolve.
However, current models for the evolution of social learning tend to conflate forms
of uncertainty, and rarely consider different ones in tandem. Moreover, many models
are limited by considering only two possible behaviors and environmental states.
Here we use evolutionary agent-based modeling to improve on these shortcomings. We
model a time-varying environment with dozens of possible behaviors performed by
agents engaging in individual and social learning. We show that ambiguous payoffs,
larger possible decision sets, and shorter agent lifespans sometimes increase social
learning prevalence, as expected. However, we also find that, under some conditions,
these forms of uncertainty can select against social learning.
\end{abstract}

\section{Introduction}

Social learning is essential to human and other species' everyday life and survival.
It allows individuals to solve problems when acquiring information from others is more efficient than learning
on one's own~\cite{Laland2004}. Theory predicts that social
learning should be favored in contexts with greater
uncertainty~\cite{BoydRicherson1985,Henrich1998}, and this prediction has received some empirical support~\cite{McElreath2005,Kendal2018}. 
However, the meaning of the term ``uncertainty'' is not always clear, and often conflates environmental variability, spatial heterogeneity, and ambiguity or uncertainty about payoff structure. 
Moreover, most models of the evolution of social learning ``blackbox'' key 
cognitive learning processes that underlie it~\cite{Heyes2016}.

In this paper we use agent-based modeling to compare the effect of
different sources of uncertainty on social learning
by ``unblackboxing'' typically abstracted-out model components 
of environmental variability, payoff structures and
agent life histories, and  learning mechanisms. ``Uncertainty''  
means variability where the probabilistic structure is unknown. %cannot be learned.
Uncertainty increases when payoffs are more similar across behaviors, when
environmental variability increases, when the number of possible behaviors
increases, and when lifespan decreases.  In this paper we show that more ambiguous
payoff structures and shorter lifespans sometimes do lead to greater reliance on
social learning---however, we also identify and explain cases where greater
uncertainty leads to less social learning due to the possibility that social
information is misleading.  We thus conclude that many predictions made by previous
models of the evolution of social learning are likely overgeneralized.
%~\cite{Yarkoni2021}.

\subsection{Social Learning}

Social learning, as we consider it here, occurs whenever an individual acquires a behavior by observing another individual. This need not require explicit instruction, and is, in fact, widespread across a broad range of nonhuman 
taxa~\cite{Kendal2018,Allen2019}. Importantly, social information can be inherited both
from parents --- i.e., via \emph{vertical transmission} like genetic information --- and
from others in the same generation --- i.e., via \emph{horizontal transmission}
\cite{CavalliFeldman1981}. The joint action of vertical and horizontal transmission
gives rise to qualitatively different evolutionary dynamics. For example,
inter-generational environmental change will affect the adaptive value of genetic
information and vertically-transmitted cultural information more than information
that is horizontally transmitted. We include both horizontal and vertical transmission pathways in our
model. For simplicity, we ignore oblique transmission in which non-parental members
of the previous generation are observed.

Environmental variability has been seen as a key selective force in shaping social learning starting with the first formal models of cultural evolution~\cite{CavalliFeldman1981,BoydRicherson1985}.
Totally stable environments will not favor learning mechanisms because information can become genetically hardwired, while  extreme environmental instability will degrade the value
of social learning as information becomes rapidly outdated~\cite{Feldman1996}. This suggests that an intermediate degree of environmental predictability will favor social learning. Strategies can also evolve to mitigate the risks of relying on outdated social information by weighing more heavily information from others who more recently acquired it~\cite{Rendell2010}.

Uncertainty has also been modelled as arising from other aspects of the environment. 
For example, \citeA{Perreault2012} vary the ambiguity of the environmental cue individuals get through individual learning about the state of the world. Perhaps not surprisingly, the more ambiguous the asocial information, the greater the selection for weighing social information heavily. Alternatively, uncertainty about the optimal behavior has been modelled by increasing the number of cultural traits to choose from.

Empirical research supports some of these theoretical predictions. Organisms flexibly use social learning as a function of the ambiguity of the environmental cue and of other environmental features that are often subsumed under the rubric of ``uncertainty.''
While some studies explicitly impose a cost whenever participants use asocial
information \cite{Morgan2012,atkisson_etal2012}, 
others allow the costs of each strategy to emerge as a function of task structure and assess its consequences for learning strategies. 
For example, when participants received equivocal private information about the best investment to make in a lab game,
they were more likely to rely on social information to make their choice~\cite{Toelch2013}. 
\citeA{McElreath2005} developed a similar experiment where participants ``pulled'' virtual slot machine arms (often called ``bandits''), each yielding stochastic payoffs. Participants relied more on social learning when the bandits had higher-variance payoffs, and when the highest-paying bandit changed more frequently. 
The number of options to choose between can also increase uncertainty about the optimal choice, and has been shown to increase participants' reliance on social learning \cite{Muthukrishna2016a}.

Thus existing theoretical work and the empirical evidence seem to support that various forms of uncertainty favor the evolution of social learning. However, uncertain outcomes are operationalized in different ways across models, and any given model tends to focus on only one or two forms of uncertainty at a time. Our agent-based modeling approach enables us to explicitly specify different forms of uncertainty independently in order to understand which of these environmental factors particularly favor the evolution of social learning. Simultaneous modelling also allows us to examine their interaction. We first attempt conceptual replications of previous models' findings, and then examine where they diverge.

\subsection{Research overview}

Computational agents in our model face a problem: every time step they perform
one of several behaviors, with each behavior represented by a ``bandit'' that
pays off 1 or 0 with some probability. One of these behaviors (the optimal
behavior) pays off with a higher probability than all the others.
Agents decide which behavior to 
perform based either on a success-biased observation 
of a peer's behavior (social learning) or based on their own observations (asocial learning).
Agents then update their memory of expected payoffs for each behavior 
when they receive a payoff from their chosen
action. Within this framework we have four mechanisms by which we operationalize 
and vary uncertainty:
(1) the expected payoffs of the optimal behavior and all the rest---when payoffs
are nearly identical, uncertainty in the form of ambiguity increases; (2) the
environmental variability, i.e., the probability that the optimal behavior 
changes between generations; (3) the number of possible behaviors the environment allows---which
behavior is optimal is more uncertain when there are more possibilities; and (4)
 agent lifespan---agents experience fewer learning opportunities and die more uncertain about which behavior
is optimal when their lifespan is shorter.

The primary outcome measure of our
model is the average difference between the frequency of (horizontal) 
social learning and the frequency of asocial
learning across all agents. If social learning is more prevalent than asocial
learning this suggests that the optimal behavior is more likely found
by copying peers than by trial-and-error search.
Conversely, when asocial learning is more prevalent, this suggests social information
is likely to be misleading. 
When social and asocial learning are 
equally prevalent this means there is no discernible advantage to either, i.e.,
the agents have weak priors on which channel provides more reliable information. 
Each agent has its own social learning frequency that it inherits from its
parent (haploid reproduction) with mutation, so evolution selects for,
or computes~\cite{Smaldino2013}, the optimal
social learning frequency.

Using our model we found that increased uncertainty sometimes
led to increased reliance on social learning, as expected from prior literature. However, we also find cases where increased uncertainty decreased agents' reliance on social learning
due to increased uncertainty that made social information less reliable, thereby
increasing reliance on asocial learning.

\section{Model}

\section{Analysis}

\begin{figure}
  \centering
  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{{Figures/SL_over_u_lowpayoff=0.1.pdf}}
  \caption{}
  \label{fig:}
  \end{subfigure}

  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{{Figures/SL_over_u_lowpayoff=0.5.pdf}}
  \caption{}
  \label{fig:}
  \end{subfigure}

  \begin{subfigure}[t]{0.5\textwidth}
    \centering
    \includegraphics[width=\textwidth]{{Figures/SL_over_u_lowpayoff=0.8.pdf}}
  \caption{}
  \label{fig:}
  \end{subfigure}

  \caption{}
  \label{fig:}
\end{figure}

\section{Discussion}

\bibliographystyle{apacite}

\setlength{\bibleftmargin}{.125in}
\setlength{\bibindent}{-\bibleftmargin}

\bibliography{/Users/mt/workspace/Writing/library.bib}

\end{document}

### 2022-04-07 ms.tex
started journal article with updated model

@@
 
+We developed an agent-based model of a society of $N$ individuals who each must decide
+which of $B$ behaviors to perform at each time step. Each behavior is a ``bandit'',
+a common modelling and experimental approach for representing behaviors with
+probabilistic payoffs~\cite{SuttonBartoBook, McElreath2005,Rendell2010,Schulz2019}. %Bandits are like  slot machines in a casino~\ref{fig:behaviorSelection}.
+Each behavior $b$ yields a payoff of 1 with probability $\pi_b$ and a payoff of zero
+otherwise; $\pi_b$ is therefore also the expected payoff of behavior $b$. Agents must
+decide which behavior to perform at each time step. To do this, agents 
+use an explore-exploit strategy to sometimes try the most profitable behavior
+they know about, and other times try alternatives that may pay off more reliably.
+
+We operationalized uncertainty in four different ways: 
+(1) payoff ambiguity, $A_\pi$, which measures the difference
+between the optimal expected payoff behavior $\pi_{high}$ and the expected payoff
+of the other behaviors, $\pi_{low}$; 
+(2) environmental variability, $u$, the probability the optimal behavior changes from one generation to another; 
+(3) the number of possible behaviors, $B$; and 
+(4) the lifespan, or time steps per generation, $M$.
+
+We ran the simulation for $T=1000$ time steps. At
+the end of each generation agents reproduce and then die off. 
+Those selected to reproduce
+pass on their boolean social learning trait, $s$, without mutation,
+which specifes whether agents learn socially. We developed a series of
+computational analyses where we systematically vary the uncertainty
+variables and observe the average prevalence of social learning trait $s$
+across agents and trials, which is our primary outcome measure, 
+denoted $\langle s \rangle$.
+
+\subsection{Agents and learning}
+
+In each time step, $N$ agents---autonomous problem solvers---select 
+which behavior to perform based on their running tally of mean payoffs for 
+each available behavior. %information (Figure~\ref{fig:behaviorSelection}). 
+Agents track the mean payoff of each behavior $b$, denoted $\bar\pi_b$, and a \emph{count} of how many times it has performed each behavior, denoted $c_b$. 
+Agents' beliefs about mean payoffs are updated from $\bar\pi_b$ to $\bar\pi_b'$ using exponential weighted
+averaging, $\bar\pi_b' = \bar\pi_b + \frac{\mathrm{Bandit_b(0, 1)} - \bar\pi_b}{c_b'}$, where
+$\mathrm{Bandit_b(0, 1)}$ is 0 or 1 depending on the result of the bandit draw for behavior $b$. 
+$\bar\pi_b$ is initialized to 0 for all $b$ at model initialization for
+all agents, and after each generation for individual learner agents. Social
+learning agents' $\bar\pi_b$ is initialized as that of its teacher selected
+through performance-biased oblique learning.
+
+Social learning in this model is oblique, which here means
+any agent from the previous generation, including an agent's parent,
+could be an agent's teacher. 
+Agents learn from exactly one teacher, selected as follows:
+First, a learner agent from a new generation selects $N_T$ teachers at random.
+The best-performing of the $N_T$ becomes a new agent's teacher, with ties broken
+randomly. At the end of each generation, all agents die off with some selected
+randomly for reproduction, weighted by accumulated payoffs within the round.
+
+Following Luce's choice axiom \cite{Luce1959}, an agent using asocial information selects a behavior at random, with the probability of selecting any particular behavior weighted by the softmax function applied to that behavior's observed mean payoff relative to all
+mean payoffs: 
+$\Pr(\text{choose behavior }b) = 
+  \frac{\exp(\bar\pi_b / \tau) }{ 
+\sum_{b=1}^B \exp(\bar\pi_b / \tau)}$.
+The softmax method is a biologically plausible model~\cite{Schulz2019} that enables agents to explore alternative behaviors sometimes and exploit the best observed behavior other times.
+The parameter $\tau$ specifies
+how frequently alternative behaviors are explored---higher $\tau$ means more
+frequent exploration. We set $\tau = 0.1$ for all computational analyses 
+presented in the main paper. We (WILL) perform(ED) sensitivity analyses 
+and found a weak dependence on $\tau$ that does not affect our main conclusions.
+
+\subsection{Modeling uncertainty}
+
+In our model uncertainty is a tunable consequence of four environmental features:
+%that structure the behavior of agents.  
+% Many factors contribute to the 
+% uncertainty involved in both social and asocial learning. 
+%We model uncertainty in four distinct ways: 
+\begin{enumerate}
+    \item We vary the frequency at which the optimal behavior changes, which we call \emph{environmental variability}, $u$.
+At the start of each generation, with probability $u$, a new behavior is assigned a payoff of $\pi_{high}$ while all other behaviors are assigned a payoff of $\pi_{low}$.
+Otherwise, the same behavior remains optimal across generations.
+    \item We vary the latent expected payoffs yielded by the bandits. For simplicity,
+      we assume that in any given environmental state, there is one optimal behavior that
+      yields an expected payoff of $\pi_{high}$, while all other behaviors yield a 
+      payoff of $\pi_{low} < \pi_{high}$. 
+      The difference between these quantities is the \emph{payoff ambiguity}, 
+    \begin{equation}
+      A_\pi = 1 - (\pi_{high} - \pi_{low}),
+      \label{eq:payoffAmbiguity}
+    \end{equation}
+    which is maximized when the expected payoffs are close to equal and minimized
+    when they differ greatly. For simplicity we will set $\pi_{high} = 0.9$
+    for all analyses and vary $\pi_{low}$ in order to vary $A_\pi$.
+    \item We vary the total \emph{number of available behaviors}, $B$, which is a
+      source of uncertainty since agents are less likely to know which behavior yields high payoffs.
+%risk, as it becomes increasingly costly to experiment with alternatives.
+\cm{is this risk if it reduces variance of outcomes?
+it sounds like it's just bad for there to be more 0 payoff options}
+    \item Finally, we vary number of behavioral events per generation, $M$.
+This can be viewed as the \emph{effective lifespan} of an agent.
+Decreasing this lifespan effectively increases the importance of each event for acquiring payoffs.
+When lifespans are short ($M$ is small), agents experience greater uncertainty about which behavior is optimal given the fewer learning opportunities.
+\end{enumerate}
+
+\subsection{Dynamics and evolution}
+
+\subsection{Computational analyses}
+
+We manipulated environmental uncertainty parameters described above, $u$,
+$\pi_{low}$, $B$, and $M$, to examine their effects on our
+main outcome measure, the prevalence of social learning $s$. For each parameter setting
+in our analysis we calculated the average value of $s$ at the final time step
+of $T=1000$ across 100 runs for each combination of uncertainty parameter values.
+The model
+
 \section{Analysis}
+
+To analyze the effect of various forms of uncertainty on social learning 
+prevalence, we analyzed the outcomes of several model runs initialized with
+different uncertainty parameters $u$, $A_\pi$ (via $\pi_{low}$), 
+and $M$ (AND SOON $B$???). Specifically, for each parameter setting over
+$\pi_{low} \in \{0.1, 0.5, 0.8\}$ and $M \in \{1, 2, 4\}$, we varied 
+$u \in \{0.0, 0.2, \ldots, 1.0\}$.
+Our analysis confirmed existing theoretical predictions that social learning
+is valuable only when environmental uncertainty is sufficiently small. However
+our analysis also revealed that environmental uncertainty is not the only 
+relevant factor. Payoff ambiguity can alter selection selection pressure for or
+against social learning, depending on the number of time steps per generation.
+We tested three values of $\pi_{low} \in \{0.1, 0.5, 0.8\}$, representing
+low, moderate, and high values of $A_\pi$.
+
+When $\pi_{low} = 0.1$, $M$ had little to no effect (Figure~\ref{fig:results_pilow_0p1}).
+For all three values of $M$, social learning decreases from 1 dramatically over moderate
+values of $u$, going to 0 by $u=0.6$. When $\pi_{low}=0.5$, however, the 
+transition from $\langle s \rangle = 1$ to $\langle s \rangle = 0$ is not as
+sharp, and it is slower for $M=1$ compared to $M=2$ and $M=4$. When $\pi_{low} = 0.8$
+there appears to be a weak dependence of social learning on $u$ across $M$,
+but this trend is mostly dominated by noise.
+(EXPAND THIS---PROBABLY NEED B > 2, WHAT ELSE?)
+
+(EXPLAIN WHY)
 
@@
   \caption{}
-  \label{fig:}
+  \label{fig:results_pilow_0p1}
   \end{subfigure}
@@
 
-  \caption{}
-  \label{fig:}
+  \caption{Dependence of Social Learning ($\langle s \rangle$) on environmental
+  variability $u$ for several values of low payoff $\pi_{low}$ and steps per
+  round, $M$. $\langle s \rangle$ decreases monotonically for $\pi_{low} = 0.1, 0.5$,
+but noise dominates the results for $\pi_{low}=0.8$. When $\pi_{low} = 0.5$, 
+the sigmoid is not as sharp as for $\pi_{low}=0.1$, meaning that social learning
+is reduced for smaller $u$ and increased for larger $u$.}
+  \label{fig:results}
 \end{figure}

### 2022-04-08 ms.tex
added intra-/inter-generational dynamics figure

@@
 
+\begin{figure}
+  \centering
+    \includegraphics[width=0.95\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+  \caption{Model dynamics are composed of two major parts: first, agents perform
+  behaviors for $M$ time steps in a single generation. Then agents reproduce
+  randomly, with more successful agents being more likely to reproduce. Newly
+  ``born'' social learner agents use success bias to select and learn from a chosen
+  teacher. Then, all agents from the previous generation die off, all new agents
+  begin a new generation, and the process continues until 1000 total time steps
+  have elapsed. At model initialization all agents are ``blank slates''.}
+  \label{fig:IntraInterGenerationalDynamics}
+\end{figure}
+
 \subsection{Computational analyses}

### 2022-04-08 ms.tex
Updates from Overleaf

--- 2022-04-07 ms.tex
@@
-% Author: Matthew Turner
-
 % \documentclass[11pt,letterpaper]{article}
@@
 While some studies explicitly impose a cost whenever participants use asocial
-information \cite{Morgan2012,atkisson_etal2012}, 
+information \cite{Morgan2012,Atkisson2012}, 
 others allow the costs of each strategy to emerge as a function of task structure and assess its consequences for learning strategies. 
@@
 
-\bibliography{/Users/mt/workspace/Writing/library.bib}
+% \bibliography{/Users/mt/workspace/Writing/library.bib}
+\bibliography{this.bib}
 

### 2022-04-11 ms.tex
added 3x3 spread of main results plots

--- 2022-04-08 ms.tex
@@
 
-\begin{figure}
-  \centering
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{{Figures/SL_over_u_lowpayoff=0.1.pdf}}
-  \caption{}
-  \label{fig:results_pilow_0p1}
-  \end{subfigure}
-
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{{Figures/SL_over_u_lowpayoff=0.5.pdf}}
-  \caption{}
-  \label{fig:}
-  \end{subfigure}
-
-  \begin{subfigure}[t]{0.5\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{{Figures/SL_over_u_lowpayoff=0.8.pdf}}
-  \caption{}
-  \label{fig:}
-  \end{subfigure}
-
-  \caption{Dependence of Social Learning ($\langle s \rangle$) on environmental
-  variability $u$ for several values of low payoff $\pi_{low}$ and steps per
-  round, $M$. $\langle s \rangle$ decreases monotonically for $\pi_{low} = 0.1, 0.5$,
-but noise dominates the results for $\pi_{low}=0.8$. When $\pi_{low} = 0.5$, 
-the sigmoid is not as sharp as for $\pi_{low}=0.1$, meaning that social learning
-is reduced for smaller $u$ and increased for larger $u$.}
-  \label{fig:results}
-\end{figure}
+\include{mainResultsPlots.tex}
 

### 2022-04-13 ms.tex
outlined analysis section

@@
 \usepackage{float}
-% \usepackage[margin=1.00in]{geometry}
-\usepackage[margin=0.90in]{geometry}
+\usepackage[margin=1.00in]{geometry}
+% \usepackage[margin=0.90in]{geometry}
 
@@
 \maketitle
+
+\newcommand{\pisub}[1]{\pi_{\mathrm{#1}}}
+\newcommand{\pilow}{\pisub{low}}
+
+\newcommand{\meansl}{\langle s \rangle}
 
@@
 (1) payoff ambiguity, $A_\pi$, which measures the difference
-between the optimal expected payoff behavior $\pi_{high}$ and the expected payoff
-of the other behaviors, $\pi_{low}$; 
+between the optimal expected payoff behavior $\pisub{high}$ and the expected payoff
+of the other behaviors, $\pisub{low}$; 
 (2) environmental variability, $u$, the probability the optimal behavior changes from one generation to another; 
@@
 averaging, $\bar\pi_b' = \bar\pi_b + \frac{\mathrm{Bandit_b(0, 1)} - \bar\pi_b}{c_b'}$, where
-$\mathrm{Bandit_b(0, 1)}$ is 0 or 1 depending on the result of the bandit draw for behavior $b$. 
+$\mathrm{Bandit}_b(0, 1)$ is 0 or 1 depending on the result of the bandit draw for behavior $b$. 
 $\bar\pi_b$ is initialized to 0 for all $b$ at model initialization for
@@
     \item We vary the frequency at which the optimal behavior changes, which we call \emph{environmental variability}, $u$.
-At the start of each generation, with probability $u$, a new behavior is assigned a payoff of $\pi_{high}$ while all other behaviors are assigned a payoff of $\pi_{low}$.
+At the start of each generation, with probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all other behaviors are assigned a payoff of $\pisub{low}$.
 Otherwise, the same behavior remains optimal across generations.
@@
       we assume that in any given environmental state, there is one optimal behavior that
-      yields an expected payoff of $\pi_{high}$, while all other behaviors yield a 
-      payoff of $\pi_{low} < \pi_{high}$. 
+      yields an expected payoff of $\pisub{high}$, while all other behaviors yield a 
+      payoff of $\pisub{low} < \pisub{high}$. 
       The difference between these quantities is the \emph{payoff ambiguity}, 
     \begin{equation}
-      A_\pi = 1 - (\pi_{high} - \pi_{low}),
+      A_\pi = 1 - (\pisub{high} - \pisub{low}),
       \label{eq:payoffAmbiguity}
@@
     which is maximized when the expected payoffs are close to equal and minimized
-    when they differ greatly. For simplicity we will set $\pi_{high} = 0.9$
-    for all analyses and vary $\pi_{low}$ in order to vary $A_\pi$.
+    when they differ greatly. For simplicity we will set $\pisub{high} = 0.9$
+    for all analyses and vary $\pisub{low}$ in order to vary $A_\pi$.
     \item We vary the total \emph{number of available behaviors}, $B$, which is a
@@
 \begin{figure}
-  \centering
-    \includegraphics[width=0.95\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
   \caption{Model dynamics are composed of two major parts: first, agents perform
@@
   begin a new generation, and the process continues until 1000 total time steps
-  have elapsed. At model initialization all agents are ``blank slates''.}
+  have elapsed. Agents are initialized as ``blank slates''.}
+  \centering
+    \includegraphics[width=0.9\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
   \label{fig:IntraInterGenerationalDynamics}
@@
 We manipulated environmental uncertainty parameters described above, $u$,
-$\pi_{low}$, $B$, and $M$, to examine their effects on our
+$\pisub{low}$, $B$, and $M$, to examine their effects on our
 main outcome measure, the prevalence of social learning $s$. For each parameter setting
@@
 of $T=1000$ across 100 runs for each combination of uncertainty parameter values.
-The model
+
+To analyze the effect of various forms of uncertainty on social learning 
+prevalence in our Analysis, we initialized several model runs with
+different uncertainty parameters $u$, $\pisub{\mathrm{low}}$, $B$,
+and $M$. We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$ for each combination of
+the following parameters:
+$\pisub{low} \in \{0.1, 0.5, 0.8\}$, $B \in \{2, 4, 10\}$, $M \in \{B/2, B, 2B\}$.
 
@@
 
-To analyze the effect of various forms of uncertainty on social learning 
-prevalence, we analyzed the outcomes of several model runs initialized with
-different uncertainty parameters $u$, $A_\pi$ (via $\pi_{low}$), 
-and $M$ (AND SOON $B$???). Specifically, for each parameter setting over
-$\pi_{low} \in \{0.1, 0.5, 0.8\}$ and $M \in \{1, 2, 4\}$, we varied 
-$u \in \{0.0, 0.2, \ldots, 1.0\}$.
+\begin{itemize}
+  \item 
+    To understand how different forms of uncertainty affect social learning evolution
+    we systematically varied environmental variables in our model and observed
+    corresponding changes in mean social learning prevalence, $\meansl$. We
+    confirmed that, in many cases, increased environmental variability $u$ 
+    suppresses social learning. However\ldots
+
+  \item 
     Our analysis confirmed existing theoretical predictions that social learning
-is valuable only when environmental uncertainty is sufficiently small. However
-our analysis also revealed that environmental uncertainty is not the only 
-relevant factor. Payoff ambiguity can alter selection selection pressure for or
+    is valuable only when environmental variability $u$ is sufficiently small.
+    Because of the central role of $u$, it is set on the x-axis in
+    all plots shown in Figure~\ref{fig:results}. 
+    The threshold at which social learning stops being strongly selected for
+    varies depending on the value of other environmental parameters.
+
+  \item 
+    However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
+    third column respectively in Figure~\ref{fig:results}) can lead
+    social learning to be selected for even for large values of $u$, possibly
+    due to the low risk and potentially high reward of learning an accurate
+    tally of mean payoffs from the previous generation. 
+    Since there are so many behaviors and so
+    few observations, softmax weighting will not significantly 
+    favor a sub-optimal behavior. However, if one does learn an accurate tally
+    then one does have an increased chance of performing the best one.
+    \begin{itemize}
+      \item 
+        (THIS MAKES SENSE, BUT THE EFFECT IS TOO STRONG. WHY SHOULD THERE BE ANY
+        SOCIAL LEARNING WHEN U = 1.0?  I THINK SOMETHING IS SLIGHTLY WRONG WITH THE
+        MODEL---I'M WORKING ON CHECKING WHAT THAT MIGHT BE)
+      \item
+        ONE THING TO CHECK IS THE FRACTION DOING THE OPTIMAL BEHAVIOR WHEN
+        $u=1$. IF MANY START OUT DOING OPTIMAL, THEN SOMETHING MAY BE WRONG.
+    \end{itemize}
+
+  \item 
+    $\pilow$ can alter selection selection pressure for or
     against social learning, depending on the number of time steps per generation.
-We tested three values of $\pi_{low} \in \{0.1, 0.5, 0.8\}$, representing
-low, moderate, and high values of $A_\pi$.
+    For instance, when $B=2$, increasing $\pilow$ (i.e. increased uncertainty
+    about which behavior is optimal) leads at first to less sharp sigmoid curve, 
+    where social learning is less prevalent with increased $\pilow$ when
+    $u < 0.5$ and social learning is more prevalent with increased $\pilow$
+    when $u > 0.5$. When $\pilow = 0.8$ noise and genetic drift dominate across
+    tested values of $B$, with possibly a slight inverse correlation 
+    in social learning as $u$ increases. When $B \in \{4,10\}$, increasing
+    $\pilow \in \{0.1, 0.5\}$ leads uniformly to increased $\meansl$ over 
+    $u$ in those settings.
 
-When $\pi_{low} = 0.1$, $M$ had little to no effect (Figure~\ref{fig:results_pilow_0p1}).
-For all three values of $M$, social learning decreases from 1 dramatically over moderate
-values of $u$, going to 0 by $u=0.6$. When $\pi_{low}=0.5$, however, the 
-transition from $\langle s \rangle = 1$ to $\langle s \rangle = 0$ is not as
-sharp, and it is slower for $M=1$ compared to $M=2$ and $M=4$. When $\pi_{low} = 0.8$
-there appears to be a weak dependence of social learning on $u$ across $M$,
-but this trend is mostly dominated by noise.
-(EXPAND THIS---PROBABLY NEED B > 2, WHAT ELSE?)
+  \item
+    If $M/B$ has an effect it is mostly to 
+    increase reliance on social learning due to social information being of 
+    higher quality since teachers would have had more learning opportunities
+    for larger $M$. (THERE ARE CASES WHERE THIS IS NOT THE CASE BUT THERE IS 
+    STILL TOO MUCH NOISE DUE TO SMALL NTRIALS)
 
-(EXPLAIN WHY)
+  \item
+    Synthesis/analysis conclusion
+
+\end{itemize}
 
@@
 
-% \bibliography{/Users/mt/workspace/Writing/library.bib}
-\bibliography{this.bib}
+\bibliography{/Users/mt/workspace/Writing/library.bib}
+% \bibliography{this.bib}
 

### 2022-04-13 ms.tex
updated model figure, other small changes

@@
 \setlength\intextsep{0pt}
+
+% Colored comments 
+\usepackage{color}
+\definecolor{myorange}{RGB}{240, 96, 0}
+\newcommand{\mt}[1]{{\textcolor{myorange} {({\tiny MT:} #1)}}}
+
+\definecolor{myblue}{RGB}{30,144,255}
+\newcommand{\jhj}[1]{{\textcolor{myblue} {({\tiny JHJ:} #1)}}}
+
+\definecolor{mypurple}{RGB}{148,0,211}
+\newcommand{\cm}[1]{{\textcolor{mypurple} {({\tiny CM:} #1)}}}
+
+\definecolor{mygreen}{RGB}{26, 153, 51}
+\newcommand{\ps}[1]{{\textcolor{mygreen} {({\tiny PS:} #1)}}}
 
@@
 frequent exploration. We set $\tau = 0.1$ for all computational analyses 
-presented in the main paper. We (WILL) perform(ED) sensitivity analyses 
+presented in the main paper. We (WILL HAVE) performed sensitivity analyses 
 and found a weak dependence on $\tau$ that does not affect our main conclusions.
@@
     Our analysis confirmed existing theoretical predictions that social learning
-    is valuable only when environmental variability $u$ is sufficiently small.
+    is valuable only when environments are sufficiently stable, i.e., 
+    environmental variability $u$ is sufficiently small.
     Because of the central role of $u$, it is set on the x-axis in
-    all plots shown in Figure~\ref{fig:results}. 
-    The threshold at which social learning stops being strongly selected for
+    all analysis plots shown in Figure~\ref{fig:results}. 
+    The threshold over $u$ at which social learning begins to decline
     varies depending on the value of other environmental parameters.
@@
       \item 
-        (THIS MAKES SENSE, BUT THE EFFECT IS TOO STRONG. WHY SHOULD THERE BE ANY
-        SOCIAL LEARNING WHEN U = 1.0?  I THINK SOMETHING IS SLIGHTLY WRONG WITH THE
-        MODEL---I'M WORKING ON CHECKING WHAT THAT MIGHT BE)
+        \mt{This makes sense, but the effect is too strong. Why should there be any
+        social learning when u = 1.0?  I think something is slightly wrong with the
+        model---I'm working on checking what that might be}
       \item
-        ONE THING TO CHECK IS THE FRACTION DOING THE OPTIMAL BEHAVIOR WHEN
-        $u=1$. IF MANY START OUT DOING OPTIMAL, THEN SOMETHING MAY BE WRONG.
+        \mt{One thing to check is the fraction doing the optimal behavior when
+        $u=1$. If many start out doing optimal, then something may be wrong.}
     \end{itemize}

### 2022-04-13 ms.tex
Updates from Overleaf

--- 2022-04-13 ms.tex
@@
     tally of mean payoffs from the previous generation. 
-    Since there are so many behaviors and so
+    Since there are many behaviors and
     few observations, softmax weighting will not significantly 
@@
 
-\bibliography{/Users/mt/workspace/Writing/library.bib}
-% \bibliography{this.bib}
+% \bibliography{/Users/mt/workspace/Writing/library.bib}
+\bibliography{this.bib}
 

### 2022-04-19 ms.tex
finished dynamics and evolution subsec first draft

@@
 \newcommand{\pilow}{\pisub{low}}
+\newcommand{\pihigh}{\pisub{high}}
 
@@
 each available behavior. %information (Figure~\ref{fig:behaviorSelection}). 
-Agents track the mean payoff of each behavior $b$, denoted $\bar\pi_b$, and a \emph{count} of how many times it has performed each behavior, denoted $c_b$. 
-Agents' beliefs about mean payoffs are updated from $\bar\pi_b$ to $\bar\pi_b'$ using exponential weighted
-averaging, $\bar\pi_b' = \bar\pi_b + \frac{\mathrm{Bandit_b(0, 1)} - \bar\pi_b}{c_b'}$, where
-$\mathrm{Bandit}_b(0, 1)$ is 0 or 1 depending on the result of the bandit draw for behavior $b$. 
-$\bar\pi_b$ is initialized to 0 for all $b$ at model initialization for
+Agent $i$ tracks the mean payoff of each behavior $b$, denoted $\bar\pi_{ib}$, and
+a \emph{count} of how many times it has performed each behavior, denoted $c_{ib}$.
+$\bar\pi_{ib}$
+is initialized to 0 for all $b$ at model initialization for
 all agents, and after each generation for individual learner agents. Social
-learning agents' $\bar\pi_b$ is initialized as that of its teacher selected
+learning agents' $\bar\pi_{ib}$ is initialized as that of its teacher selected
 through performance-biased oblique learning.
+
+\vspace{2em}
+
+\begin{table}[h]
+    \caption{Dynamic agent-level variables.}
+    \label{tab:modelParameters}
+    \centering \hspace{-3em}
+    \begin{tabular}{cp{4.0in}l} \toprule
+
+        Attribute & Description & Initial value \\
+
+        \midrule
+
+        $s_i$  & Social learner trait: 1 if agent $i$ is social learner; 0 otherwise & 0
+        or 1 w/ equal prob. \\
+
+        $\bar\pi_{ib}$ & ``Ledger'': mean payoffs acquired via behavior $b$ by $i$ 
+                       & $B$-vector of floating-point zeros \\
+
+        $c_{ib}$ & Count of how many times agent $i$ performed $b$ 
+              & $B$-vector of integer zeros \\
+
+        $\pi_i$ & Net payoffs accumulated by $i$ within generation
+                                & 0.0 \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\vspace{2em}
 
@@
 randomly for reproduction, weighted by accumulated payoffs within the round.
-
-Following Luce's choice axiom \cite{Luce1959}, an agent using asocial information selects a behavior at random, with the probability of selecting any particular behavior weighted by the softmax function applied to that behavior's observed mean payoff relative to all
-mean payoffs: 
-$\Pr(\text{choose behavior }b) = 
-  \frac{\exp(\bar\pi_b / \tau) }{ 
-\sum_{b=1}^B \exp(\bar\pi_b / \tau)}$.
-The softmax method is a biologically plausible model~\cite{Schulz2019} that enables agents to explore alternative behaviors sometimes and exploit the best observed behavior other times.
-The parameter $\tau$ specifies
-how frequently alternative behaviors are explored---higher $\tau$ means more
-frequent exploration. We set $\tau = 0.1$ for all computational analyses 
-presented in the main paper. We (WILL HAVE) performed sensitivity analyses 
-and found a weak dependence on $\tau$ that does not affect our main conclusions.
 
@@
       yields an expected payoff of $\pisub{high}$, while all other behaviors yield a 
-      payoff of $\pisub{low} < \pisub{high}$. 
-      The difference between these quantities is the \emph{payoff ambiguity}, 
-    \begin{equation}
-      A_\pi = 1 - (\pisub{high} - \pisub{low}),
-      \label{eq:payoffAmbiguity}
-    \end{equation}
-    which is maximized when the expected payoffs are close to equal and minimized
-    when they differ greatly. For simplicity we will set $\pisub{high} = 0.9$
-    for all analyses and vary $\pisub{low}$ in order to vary $A_\pi$.
+      payoff of $\pisub{low} < \pisub{high}$. As $\pilow$ increases towards 
+      $\pihigh$, uncertainty in the form of \emph{payoff ambiguity} also increases,
+      making it more difficult, and less rewarding, for agents to determine which
+      behavior is the optimal one.
+      % The difference between these quantities is the \emph{payoff ambiguity}, 
+    % \begin{equation}
+    %   A_\pi = 1 - (\pisub{high} - \pisub{low}),
+    %   \label{eq:payoffAmbiguity}
+    % \end{equation}
+    % which is maximized when the expected payoffs are close to equal and minimized
+    % when they differ greatly. For simplicity we will set $\pisub{high} = 0.9$
+    % for all analyses and vary $\pisub{low}$ in order to vary $A_\pi$.
     \item We vary the total \emph{number of available behaviors}, $B$, which is a
       source of uncertainty since agents are less likely to know which behavior yields high payoffs.  
-%risk, as it becomes increasingly costly to experiment with alternatives.
-\cm{is this risk if it reduces variance of outcomes?
-it sounds like it's just bad for there to be more 0 payoff options}
     \item Finally, we vary number of behavioral events per generation, $M$.
@@
 \subsection{Dynamics and evolution}
+
+Model dynamics can be split into three parts: initialization,
+\emph{intra}generational behavior and payoff accumulation, and
+\emph{inter}generational transmission of the social learning trait and oblique
+learning (Figure~\ref{fig:IntraInterGenerationalDynamics}). 
+The model runs that we analyze here were initialized with $N=100$ agents
+to randomly have the social learner trait or not, with no accumulated payoffs, and
+blank ``ledgers''. At each time step, agents select one of $B$ possible behaviors
+to perform, accumulating a payoff of 1 if the bandit pays off, and 0 if it does
+not---a bandit pays off with probability $\pihigh$ if it is the unique optimal
+behavior, or with probability $\pilow$ if it is one of $B-1$ non-optimal
+behaviors. Agents accumulate payoffs in this way for $M$ time steps in each
+generation. At the end of each generation, $N=100$ agents are randomly selected with
+replacement to reproduce (asexual, haploid reproduction), 
+weighted by their net payoffs over the generation,
+i.e., \emph{performance-biased} reproduction. Child agents then learn from 
+one teacher, selected again via a form of performance bias: a child agent chooses
+its teacher by first selecting a fully random subset of agents from the 
+parent generation as potential teachers, then selecting the one with the 
+greatest net payoffs among the subset. This process continues until $T=1000$
+time steps have elapsed \mt{this should probably be changed depending on $M$ so that
+    all analyses use the same number of generations. my informal checks have shown quick
+convergence, but i haven't tested b=4 and b=10 as much.}.
 
@@
 \end{figure}
+
+\subsubsection{Initialization}
+
+Model initialization includes agent and environment initializations. Agents are
+randomly initialized to have the social learning trait or not, with equal 
+probability. Agent ``ledgers'' and behavior counts 
+are uniformly initialized to the no-knowledge,
+blank-slate case where all $\pi_{ib} = 0$ and $c_{ib} = 0$. Both the 
+ledger and behavior count vectors have $B$ entries, one for each
+behavior the environment affords. Net payoffs for
+the generation are also initialized to zero. All agents are initialized with
+the same softmax temperature, $\tau$, that guides their behavior selection 
+to be either more exploratory (greater $\tau$) or more exploitative of
+what agents believe to be the optimal behavior(s) (lesser $\tau$).
+
+The environment is initialized to have $B$ behaviors with one of them selected
+at random to be the optimal behavior, denoted $b^*$. Behavior $b^*$ is 
+initialized to have a probability $\pihigh$ of paying off 1. All other behaviors
+are initialized to have probability $\pilow$ of paying off 1. The modeler must
+specify the environmental variability, $u$, and the number of time steps per 
+generation, $M$.
+
+\vspace{2em}
+\begin{table}[h]
+    \caption{Global environmental and cognitive initialization parameters.}
+    \label{tab:modelParameters}
+    \centering \hspace{-3em}
+    \begin{tabular}{cp{4.0in}l} \toprule
+
+        Symbol & Description & Values tested (bold$=$default) \\
+
+        \midrule
+
+        $B$       & Number of possible behaviors (represented by ``bandits'') 
+                  & 2, 4, 10 \\
+
+        $\pihigh$ & Probability that the unique optimal behavior pays off 1 
+                & \textbf{0.9} \\
+
+        $\pilow$ & Probability one of $B - 1$ non-optimal behaviors pays off 1 
+                 & 0.1, 0.45, 0.8 \\
+
+        $\tau$ & Softmax temp.; $\uparrow=$more exploration, $\downarrow=$more
+                    exploitation 
+               & 0.01, \textbf{0.1}, 1.0 \\
+
+        $u$    & Probability optimal behavior changes between generations 
+               & 0.0, 0.1, \ldots, 1.0 \\
+
+        $M$    & Number of time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
+
+        $N_T$    & Number of teachers to pool, from which best selected 
+                 & \textbf{5} \mt{TODO: Test more for sensitivity analysis?} \\
+
+        \bottomrule
+        \end{tabular} 
+\end{table}
+\vspace{2em}
+
+\subsubsection{Intra-generational behaviors and payoffs}
+
+Each generation begins with agents initialized either by the $t=0$ initialization
+outlined above, or initialized via inter-generational reproduction and learning,
+described in detail below. Within generations, there is no social learning.
+At each time step within a generation, agents select a behavior to perform
+using the softmax algorithm, then update their ledgers $\bar\pi_{ib}$ and behavior
+counts $c_{ib}$. If 
+the chosen bandit pays off for an agent, its net payoff is incremented by one,
+$\pi'_i \leftarrow \pi_i + 1$. This process continues for $M$ time steps, 
+when reproduction, learning, and die-off occur, re-initializing the next 
+generation for performing $M$ behaviors selected via this same process.
+
+At each time step, 
+agent $i$ chooses behavior $b$ at random, with each behavior
+weighted by the softmax function applied to that behavior's observed mean payoff
+relative to all mean payoffs in the ledger,
+\begin{equation}
+  \Pr(i \text{ chooses behavior } b) = \frac{\exp(\bar\pi_{ib}
+  / \tau) }{ \sum_{b=1}^B \exp(\bar\pi_{ib} / \tau)}.
+\end{equation}  
+Softmax behavior selection is a
+biologically plausible model of behavior~\cite{Schulz2019} 
+that enables agents to explore
+alternative behaviors sometimes and exploit the best observed behavior other times,
+in accordance with Luce's choice axiom~\cite{Luce1959},.
+The parameter $\tau$ specifies how frequently alternative behaviors are
+explored versus how frequently the best observed behaviors are 
+exploited. Greater $\tau$ means more frequent exploration, lesser $\tau$ means
+more frequent exploitation. We set $\tau = 0.1$ for
+all computational analyses presented in the main paper. We (WILL HAVE) performed
+sensitivity analyses and found a weak dependence on $\tau$ that does not affect our
+main conclusions.
+
+When agent $i$ performs behavior $b$, $i$'s behavior count 
+is incremented by 1, $c'_{ib} \leftarrow c_{ib} + 1$. Agent $i$'s ledger of mean 
+payoffs are updated % from $\bar\pi_{ib}$ to $\bar\pi_{ib}'$
+using exponential weighted averaging,
+
+\begin{equation}
+  \bar\pi_{ib}' = \bar\pi_{ib} +
+    \frac{\mathrm{Bandit_{b}(0, 1)} - \bar\pi_{ib}}{c_{ib}'},
+\end{equation}
+where 
+$\mathrm{Bandit}_{b}(0, 1)$
+is 0 or 1 depending on the result of the bandit draw for behavior $b$.
+
+\subsubsection{Inter-generational inheritance and social learning}
+
+Every $M$ time steps, agents from the current generation reproduce, teach,
+and die, while the next generation to perform the next $M$ time steps learns
+from one teacher from the previous generation if they inherited the social 
+learner trait. Inter-generational dynamics thus depend on 
+two payoff-biased selection mechanisms: reproducer selection
+and teacher selection.
+
+$N$ reproducers are sampled from the population with
+replacement weighted by net payoffs, i.e., at each of $N$ draws for a parent,
+\begin{equation}
+  \Pr(\text{Agent $i$ chosen for reproduction}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
+\end{equation}
+\noindent
+We sample with replacement to allow for more successful agents to have multiple
+offspring. Child agents inherit their parents' social learning trait, so 
+all social learner parents spawn social learner offspring, and parents lacking
+the trait spawn offspring lacking the trait.
+
+Child agents with the social learning trait then must select and learn from a
+teacher from their parent's generation, including possibly their parent.
+Child agents give no preference to whether potential teachers are social 
+learners. A child selects a teacher by first selecting a pool of $N_T = 5$ potential
+teachers. Among this pool, each child selects the teacher with the greatest
+net payoffs. In case of a tie the teacher is chosen at random from those with
+the shared maximum net payoff.
+
+Social learner child agents each acquire their teacher's ledger, and all social
+learner children behavior counts are reset to 1 to limit ledger values to be between
+0 and 1. Child agents without the social learner trait have all ledger and behavior
+count values re-initialized to 0. At this point the re-initialized child agents
+engage in behavior selection and payoff accumulation described above.
 
@@
 $\pisub{low} \in \{0.1, 0.5, 0.8\}$, $B \in \{2, 4, 10\}$, $M \in \{B/2, B, 2B\}$.
+
+\subsubsection{Outcome variables}
+
+Our primary outcome variable is the mean prevalence of the social learning
+trait over $N=100$ agents in 100 trials at the final time step of each trial,
+denoted $\meansl$.
+Typically at the final time step all agents either have the social learning
+trait or do not (see Supplement for a presentation of time series collections for
+a representative sampling of \mt{TODO}).
+
+\begin{table}[h]
+    \caption{Global environmental and cognitive initialization parameters.}
+    \label{tab:modelParameters}
+    \centering \hspace{-3em}
+    \begin{tabular}{cp{4.0in}l} \toprule
+
+        Symbol & Description & Values \\
+
+        \midrule
+
+        $\meansl$ & Mean social learning prevalence over agents and trials
+                  & $\in [0.0, 1.0]$ \\
+
+        $p_{\text{opt}}$ & Fraction of population performing optimal behavior
+                         & $\in [0.0, 1.0]$ \\
+
+        \texttt{count}$(b_i)$ & Number of agents performing behavior $b$ 
+                              & Behavior-count key-value pairs\\
+        \bottomrule
+    \end{tabular}
+\end{table}
 
@@
     then one does have an increased chance of performing the best one.
-    \begin{itemize}
-      \item 
-        \mt{This makes sense, but the effect is too strong. Why should there be any
-        social learning when u = 1.0?  I think something is slightly wrong with the
-        model---I'm working on checking what that might be}
-      \item
-        \mt{One thing to check is the fraction doing the optimal behavior when
-        $u=1$. If many start out doing optimal, then something may be wrong.}
-    \end{itemize}
 

### 2022-04-20 ms.tex
small edits to new model parts

@@
 
-\subsection{Agents and learning}
+\subsection{Agents and their attributes}
 
@@
 learning agents' $\bar\pi_{ib}$ is initialized as that of its teacher selected
-through performance-biased oblique learning.
+through performance-biased oblique learning. Agent $i$'s accumulated payoffs
+from performing several behaviors over their lifetime of $M$ time steps is
+denoted $\pi_{i}$.
 
@@
 \begin{table}[h]
-    \caption{Dynamic agent-level variables.}
+    \caption{Dynamic agent-level variables. Each has an implicit time dependence.}
     \label{tab:modelParameters}
@@
 \vspace{2em}
-
-Social learning in this model is oblique, which here means
-any agent from the previous generation, including an agent's parent,
-could be an agent's teacher. 
-Agents learn from exactly one teacher, selected as follows:
-First, a learner agent from a new generation selects $N_T$ teachers at random.
-The best-performing of the $N_T$ becomes a new agent's teacher, with ties broken
-randomly. At the end of each generation, all agents die off with some selected
-randomly for reproduction, weighted by accumulated payoffs within the round.
 

### 2022-04-21 ms.tex
updated plots with 100 trials and corrected analysis

@@
 
-\begin{itemize}
-  \item 
-    To understand how different forms of uncertainty affect social learning evolution
-    we systematically varied environmental variables in our model and observed
-    corresponding changes in mean social learning prevalence, $\meansl$. We
-    confirmed that, in many cases, increased environmental variability $u$ 
-    suppresses social learning. However\ldots
+% \begin{itemize}
+%   \item 
+%     To understand how different forms of uncertainty affect social learning evolution
+%     we systematically varied environmental variables in our model and observed
+%     corresponding changes in mean social learning prevalence, $\meansl$. We
+%     confirmed that, in many cases, increased environmental variability $u$ 
+%     suppresses social learning. However\ldots
 
-  \item 
-    Our analysis confirmed existing theoretical predictions that social learning
-    is valuable only when environments are sufficiently stable, i.e., 
-    environmental variability $u$ is sufficiently small.
-    Because of the central role of $u$, it is set on the x-axis in
-    all analysis plots shown in Figure~\ref{fig:results}. 
-    The threshold over $u$ at which social learning begins to decline
-    varies depending on the value of other environmental parameters.
+%   \item 
+%     Our analysis confirmed existing theoretical predictions that social learning
+%     is valuable only when environments are sufficiently stable, i.e., 
+%     environmental variability $u$ is sufficiently small.
+%     Because of the central role of $u$, it is set on the x-axis in
+%     all analysis plots shown in Figure~\ref{fig:results}. 
+%     The threshold over $u$ at which social learning begins to decline
+%     varies depending on the value of other environmental parameters.
 
-  \item 
-    However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
-    third column respectively in Figure~\ref{fig:results}) can lead
-    social learning to be selected for even for large values of $u$, possibly
-    due to the low risk and potentially high reward of learning an accurate
-    tally of mean payoffs from the previous generation. 
-    Since there are many behaviors and
-    few observations, softmax weighting will not significantly 
-    favor a sub-optimal behavior. However, if one does learn an accurate tally
-    then one does have an increased chance of performing the best one.
+%   \item 
+%     However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
+%     third column respectively in Figure~\ref{fig:results}) can lead
+%     social learning to be selected for even for large values of $u$, possibly
+%     due to the low risk and potentially high reward of learning an accurate
+%     tally of mean payoffs from the previous generation. 
+%     Since there are many behaviors and
+%     few observations, softmax weighting will not significantly 
+%     favor a sub-optimal behavior. However, if one does learn an accurate tally
+%     then one does have an increased chance of performing the best one.
 
-  \item 
-    $\pilow$ can alter selection selection pressure for or
-    against social learning, depending on the number of time steps per generation.
-    For instance, when $B=2$, increasing $\pilow$ (i.e. increased uncertainty
-    about which behavior is optimal) leads at first to less sharp sigmoid curve, 
-    where social learning is less prevalent with increased $\pilow$ when
-    $u < 0.5$ and social learning is more prevalent with increased $\pilow$
-    when $u > 0.5$. When $\pilow = 0.8$ noise and genetic drift dominate across
-    tested values of $B$, with possibly a slight inverse correlation 
-    in social learning as $u$ increases. When $B \in \{4,10\}$, increasing
-    $\pilow \in \{0.1, 0.5\}$ leads uniformly to increased $\meansl$ over 
-    $u$ in those settings.
+%   \item 
+%     $\pilow$ can alter selection selection pressure for or
+%     against social learning, depending on the number of time steps per generation.
+%     For instance, when $B=2$, increasing $\pilow$ (i.e. increased uncertainty
+%     about which behavior is optimal) leads at first to less sharp sigmoid curve, 
+%     where social learning is less prevalent with increased $\pilow$ when
+%     $u < 0.5$ and social learning is more prevalent with increased $\pilow$
+%     when $u > 0.5$. When $\pilow = 0.8$ noise and genetic drift dominate across
+%     tested values of $B$, with possibly a slight inverse correlation 
+%     in social learning as $u$ increases. When $B \in \{4,10\}$, increasing
+%     $\pilow \in \{0.1, 0.5\}$ leads uniformly to increased $\meansl$ over 
+%     $u$ in those settings.
 
-  \item
-    If $M/B$ has an effect it is mostly to 
-    increase reliance on social learning due to social information being of 
-    higher quality since teachers would have had more learning opportunities
-    for larger $M$. (THERE ARE CASES WHERE THIS IS NOT THE CASE BUT THERE IS 
-    STILL TOO MUCH NOISE DUE TO SMALL NTRIALS)
+%   \item
+%     If $M/B$ has an effect it is mostly to 
+%     increase reliance on social learning due to social information being of 
+%     higher quality since teachers would have had more learning opportunities
+%     for larger $M$. (THERE ARE CASES WHERE THIS IS NOT THE CASE BUT THERE IS 
+%     STILL TOO MUCH NOISE DUE TO SMALL NTRIALS)
 
-  \item
-    Synthesis/analysis conclusion
+%   \item
+%     Synthesis/analysis conclusion
 
-\end{itemize}
+% \end{itemize}
 

### 2022-04-23 ms.tex
updated figs with 1000 trials

--- 2022-04-19 ms.tex
@@
 Our primary outcome variable is the mean prevalence of the social learning
-trait over $N=100$ agents in 100 trials at the final time step of each trial,
+trait over $N=100$ agents over 1000 trials at the final time step of each trial,
 denoted $\meansl$.
 Typically at the final time step all agents either have the social learning
-trait or do not (see Supplement for a presentation of time series collections for
-a representative sampling of \mt{TODO}).
+trait or do not (see Supplement for a presentation of time series collections
+and histograms of outcomes for
+a representative sampling of variables \mt{TODO}).
 

### 2022-04-28 supplement/meanNetPayoffs.tex
updated appendix figs

\begin{figure}
  \caption{Dependence of average net payoff ($\langle \pi \rangle$) at the
    end of last time step of the simulation on environmental
    variability $u$ for several values of low payoff $\pilow$, number of
    behaviors $B$, and lifespan $L$. Average over 1000 trials.} 
  \vspace{3em}
  % $\langle s \rangle$ decreases monotonically for $\pisub{low} = 0.1, 0.5$,
% but noise dominates the results for $\pisub{low}=0.8$. When $\pisub{low} = 0.5$, 
% the sigmoid is not as sharp as for $\pisub{low}=0.1$, meaning that social learning
% is reduced for smaller $u$ and increased for larger $u$.}
  \label{fig:results}
  \centering
  \begin{subfigure}[t]{0.08\textwidth}
    \vspace{-2em}
    \hspace{-4em}
    % \centering
    \begin{tikzpicture}
      \draw[->,thick] (-.1,0)--(1,0) node[above]
        {$B$};
        % {Number of behaviors $B$};
      \draw[->,thick] (0,.1)--(0,-1) node[below]
        {$\pilow$};
        % {Low payoff frequency $\pilow$};
    \end{tikzpicture}

  \end{subfigure}%
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    {\large $B = 2$} 
    \begin{rotate}{90}
      {\parbox{4cm}{
          \centering
          \vspace{-3.5em}{\large $ \pilow = 0.1$} \\
          {\begin{rotate}{-90}{\large $\langle \pi \rangle$}\end{rotate}}
      }}
    \end{rotate}%
    % \begin{rotate}{90}
    %   Social learning $\langle \pi \rangle$
    % \end{rotate}%
    \includegraphics[width=1.1\textwidth]{
      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
    }
    \centering
    \begin{rotate}{90}
      {\parbox{4cm}{
          \centering
          \vspace{-3.5em} {\large$ \pilow = 0.45$} \\
          {\begin{rotate}{-90}{\large $\langle \pi \rangle$}\hspace{1em}\end{rotate}}
      }}
    \end{rotate}%
    % \hspace{1.5em}%
    % \begin{rotate}{90}
    %   Social learning $\langle \pi \rangle$
    % \end{rotate}%
    \includegraphics[width=1.1\textwidth]{
      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
    }
    \begin{rotate}{90}
      {\parbox{4cm}{
          \centering
          \vspace{-3.5em} {\large $ \pilow = 0.8$} \\
          {\begin{rotate}{-90}{\large $\langle \pi \rangle$}\end{rotate}}
      }}
    \end{rotate}%
    \includegraphics[width=1.1\textwidth]{
      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
    }\\[-.5em]
    {\large $\quad u$}
  \end{subfigure}%
  \begin{subfigure}[t]{0.3\textwidth}
    {\large $B = 4$}
    \includegraphics[width=1.1\textwidth]{
      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
    } \\
    \centering
    \includegraphics[width=1.1\textwidth]{
      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
    } \\
    \includegraphics[width=1.1\textwidth]{
      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
    }\\[-.5em]
    {\large{$\quad u$}}
  \end{subfigure}
  \begin{subfigure}[t]{0.3\textwidth}
    \centering
    {\large $B = 10$}
    \includegraphics[width=1.1\textwidth]{
      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
    } \\
    \centering
    \includegraphics[width=1.1\textwidth]{
      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
    } \\
    \includegraphics[width=1.1\textwidth]{
      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
    } \\[-.5em]
    {\large $\quad u$}
  \end{subfigure}

\end{figure}

### 2022-05-04 ms.tex
updated main results figure with improved design
updated appendix figs
full outline of analysis, now filling it out

@@
 \usepackage[bookmarks, hidelinks]{hyperref}
+\usepackage[chatter]{rotating}
 \usepackage{amssymb,amsmath}
+\usepackage[title]{appendix}
 % \usepackage{fullpage}
@@
 \usepackage{float}
+% \usepackage[margin=0.50in]{geometry}
 \usepackage[margin=1.00in]{geometry}
-% \usepackage[margin=0.90in]{geometry}
 
@@
 
-\title{Some forms of uncertainty may suppress the evolution of social learning}
+\title{Uncertainty in the evolution of social learning}
 
@@
   have elapsed. Agents are initialized as ``blank slates''.}
+  \label{fig:IntraInterGenerationalDynamics}
   \centering
     \includegraphics[width=0.9\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
-  \label{fig:IntraInterGenerationalDynamics}
 \end{figure}
@@
 
-% \begin{itemize}
-%   \item 
-%     To understand how different forms of uncertainty affect social learning evolution
-%     we systematically varied environmental variables in our model and observed
-%     corresponding changes in mean social learning prevalence, $\meansl$. We
-%     confirmed that, in many cases, increased environmental variability $u$ 
-%     suppresses social learning. However\ldots
+We analyzed the outcomes of model runs across systematically varied uncertainty
+parameters over 1000 trials for each parameter setting. 
+We observed complex outcomes where the effects of uncertainty parameters
+were highly dependent on one another as measured by the mean prevalence of
+social learning, $\meansl$, across trials for each parameter setting. 
+The prevalence of social learning
+generally decreased with environmental variability, $u$, as expected from standard
+models of social learning evolution. However, the shape of the decrease was not
+uniform (Figure~\ref{fig:evolutionOfSL}). 
+We observed that social learning did in fact enable populations to 
+do better than individual learners, but only when (multi-dimensional) uncertainty 
+were sufficiently limited (Figure~\ref{fig:meanNetPayoffs}).
 
-%   \item 
-%     Our analysis confirmed existing theoretical predictions that social learning
-%     is valuable only when environments are sufficiently stable, i.e., 
-%     environmental variability $u$ is sufficiently small.
-%     Because of the central role of $u$, it is set on the x-axis in
-%     all analysis plots shown in Figure~\ref{fig:results}. 
-%     The threshold over $u$ at which social learning begins to decline
-%     varies depending on the value of other environmental parameters.
+\subsection{Evolution of social learning under uncertainty}
+The shape of the decrease from all agents
+always becoming social learners ($\meansl = 1.0$) to 
+all agents always becoming individual learners ($\meansl = 0.0$)
+is heterogeneous. We identified patterns in this heterogeneity that inform our
+understanding of when and how social learning is advantageous, and when 
+and why individual learning is advantageous. 
+Changes in the uncertainty parameters ($\pilow$, $B$, $L$) 
+result in the following changes in the shape of the transition from $\meansl = 1.0$ 
+to $\meansl = 0.0$: (1) the transition
+occurs at different critical values of $u$; and (2) the transition occurs
+with greater or lesser rapidity over $u$. 
+For instance, when $B=2$, $\pilow = 0.1$, and $L=8$, $\meansl$ goes from 1 to 
+0 starting at $u=0.1$ and reaches 0 at $u=0.3$ (Figure~\ref{fig:evolutionOfSL},
+top left). When we increased $B=4$ (Figure~\ref{fig:evolutionOfSL}, top center), the
+transition from $\meansl = 1$ to 0 begins at $u=0.3$. When $B=4$, $\pilow=0.1$,
+and $L=1$ the transition from $\meansl=1$ to 0 begins at $u=0.3$ but does not
+reach 0 until $u \approx 0.9$ (again Figure~\ref{fig:evolutionOfSL}, top center).
 
-%   \item 
-%     However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
-%     third column respectively in Figure~\ref{fig:results}) can lead
-%     social learning to be selected for even for large values of $u$, possibly
-%     due to the low risk and potentially high reward of learning an accurate
-%     tally of mean payoffs from the previous generation. 
-%     Since there are many behaviors and
-%     few observations, softmax weighting will not significantly 
-%     favor a sub-optimal behavior. However, if one does learn an accurate tally
-%     then one does have an increased chance of performing the best one.
+We can draw some conclusions about the evolution of social learning by analyzing the
+location and shape of the suppression of social learning as $u$ was increased.
+First, let us observe some general trends. Increased $\pilow$ generally
+flattened the suppression of social learning as $u$ increased.  
+Increased $B$ tended to increase the critical value of $u$ at which the 
+system transitions from favoring social learning to favor individual learning.  
+Increased $L$ generally sharpened the suppression of social learning.
+Within each of these broad trends over the uncertainty parameters are several
+details that depend on context as defined by the values of the other uncertainty
+parameters.
 
-%   \item 
-%     $\pilow$ can alter selection selection pressure for or
-%     against social learning, depending on the number of time steps per generation.
-%     For instance, when $B=2$, increasing $\pilow$ (i.e. increased uncertainty
-%     about which behavior is optimal) leads at first to less sharp sigmoid curve, 
-%     where social learning is less prevalent with increased $\pilow$ when
-%     $u < 0.5$ and social learning is more prevalent with increased $\pilow$
-%     when $u > 0.5$. When $\pilow = 0.8$ noise and genetic drift dominate across
-%     tested values of $B$, with possibly a slight inverse correlation 
-%     in social learning as $u$ increases. When $B \in \{4,10\}$, increasing
-%     $\pilow \in \{0.1, 0.5\}$ leads uniformly to increased $\meansl$ over 
-%     $u$ in those settings.
+When $\pilow$ was increased, the suppression of social learning was, in
+general, less rapid as $u$ increased. This effect is particularly acute when
+$\pilow = 0.8$, which is very nearly equal to the expected value of the optimal
+payoff, $\pihigh = 0.9$. When $\pilow = 0.8$ $\meansl$ never actually reaches 
+1 or 0 for any parameter settings. The suppression of social learning in this
+case is approximately linear, if there is selection at all. When $\pilow = 0.8$
+and $L = 1$ there is little to no selection across $B$, 
+so populations evolve randomly towards $\meansl = 1$ or $\meansl = 0$.
 
-%   \item
-%     If $M/B$ has an effect it is mostly to 
-%     increase reliance on social learning due to social information being of 
-%     higher quality since teachers would have had more learning opportunities
-%     for larger $M$. (THERE ARE CASES WHERE THIS IS NOT THE CASE BUT THERE IS 
-%     STILL TOO MUCH NOISE DUE TO SMALL NTRIALS)
+Increased $B$ generally led to increased critical $u$ at which social learning
+starts to be suppresed. When payoffs are not ambiguous ($\pilow = 0.1$), the the
+suppression of social learning starts at $u \approx 0.1$ for $B=2$; at $u \approx
+0.3$ when $B=4$; and at $u \approx 0.5$ when $B=10$.  When payoffs are more
+ambiguous ($\pilow = 0.45,0.8$), increased $B$ also led to a flattening of the
+suppression of social learning when $L=1$.
 
-%   \item
-%     Synthesis/analysis conclusion
+The general effect of $L$ is to increase the rapidity of the suppression of social
+learning via the strengthening of selection pressure since longer-lived agents
+build up stronger priors over their lifetimes. If it is advantageous to
+learn socially, this will be reliably detected. Inversely, decreased $L$
+can weaken selection pressure since agents cannot amass useful information when
+$L$ is small. This is most extreme when $\pilow = 0.8$ and there is little to
+no selection for or against social learning when $L=1$. However, decreased $L$ can
+also delay the suppression of social learning as $u$ increases, since social
+learning provdes agents with the possibility of learning what the optimal behavior
+might be.  Even when $u$ was large, agents with a lifespan of 1 more often evolved
+to be social learners because social learning was to be preferred over random
+chance.
 
-% \end{itemize}
+\subsection{Social learning capacity increases payoffs}
+
+For social learning to evolve, it must improve upon individual learning. 
+We found that different parameter settings change how advantageous social learning
+is over and above individual learning. To analyze the effect of uncertainty on
+payoffs, it is useful to identify some constant reference values which we will
+use to evaluate the benefit of social learning. First, the optimal expected payoff
+is the optimal behavior payoff times the lifespan, which we can denote
+$\langle \pi^*(L) \rangle = L\cdot\pihigh$. The expected base payoff by chance is 
+$\langle \pi_{\text{base}} \rangle = L \left[ (B - 1) \pilow + \pihigh \right]$, which
+an agent would receive on average from performing purely random behaviors. 
+Agents learn adaptively over their lifespan (via the softmax algorithm in 
+our model), whether or not they are social learners. We calculated this
+value for reference for each triplet of $\pilow$, $B$, and $L$ 
+\mt{calculate this and add to plot as a guide}. 
+Social learning evolves when the expected payoff of
+social learners exceeds the expected payoff of individual learners.
+
+\mt{Use above framework to analyze results after plot guides added as
+promised}
+
+\subsection{Evolutionary outcomes vary in their certainty}
+
+Finally, we found that the \emph{evolutionary uncertainty} of the system increases
+around the values of $u$ where $\meansl$ goes from 1 to 0. 
+In one sense
+To confirm and expand our analysis of this uncertainty, we 
+also measured environmental uncertainty in terms of the
+expected number of time steps to convergence, $\langle T \rangle$. Evolutionary
+uncertainty is an outcome measure---an emergent form of uncertainty due to
+weak selection pressures. When 
+$\meansl \approx 0.5$ this means that approximately equal numbers of trials
+ended with all agents as social learners as they ended with all agents 
+individual learners. We found that increased $\pilow$
+tended to increase the overall uncertainty in terms of $\langle T \rangle$.
+Increasing $B$ also increased the $u$ at which $\langle T \rangle$ peaked.
+This indicates the evolutionary system is significantly less certain of 
+which behavior is optimal around critical uncertainty parameter ensembles.
+
+\mt{interpret this further}
 
 \include{mainResultsPlots.tex}
+
+\include{meanNetPayoffs.tex}
+
+\include{stepResultsPlots.tex}
 
@@
 
+\appendix
+
+\section{Appendix}
+
+\subsection{Convergence information}
+
+\begin{table}[h]
+  \caption{Max. iterations = 5000.}
+  \centering
+  \begin{tabular}{cccc} \toprule
+    $B$ & \# not at fixation & \# total series & Pct. not fixated \\
+    \midrule  
+    2  & 0  & 132000 & 0.0 \% \\
+    4  & 0  & 132000 & 0.0 \% \\
+    10 & 44 & 132000 & 0.00033  \% \\
+    \bottomrule
+  \end{tabular} 
+\end{table}
+
 \end{document}

### 2022-05-05 meanNetPayoffs.tex
full outline of analysis, now filling it out
started explaining net payoffs

--- 2022-04-28 supplement/meanNetPayoffs.tex
@@
     variability $u$ for several values of low payoff $\pilow$, number of
-    behaviors $B$, and lifespan $L$. Average over 1000 trials.} 
+    behaviors $B$, and lifespan $L$. Dashed lines mark expected 
+    payoff from individual learning $\langle \pi_I \rangle$ calculated
+    for each parameter setting (not sensitive to $u$). 
+    Note that when the maximum $L$ is 
+    8, the y-axis runs from 0 to 8, and when the maximum $L$ is 20, the y-axis
+    runs from 0 to 20. Average over 1000 trials.} 
+  \label{fig:meanNetPayoffs}
   \vspace{3em}
@@
 % is reduced for smaller $u$ and increased for larger $u$.}
-  \label{fig:results}
   \centering
+  \addtocounter{figure}{-1}  % Hack to get figure numbering correct with subfigure.
   \begin{subfigure}[t]{0.08\textwidth}

### 2022-05-05 ms.tex
started explaining net payoffs

@@
 \begin{enumerate}
-    \item We vary the frequency at which the optimal behavior changes, which we call \emph{environmental variability}, $u$.
-At the start of each generation, with probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all other behaviors are assigned a payoff of $\pisub{low}$.
-Otherwise, the same behavior remains optimal across generations.
+    \item 
+      We vary the frequency at which the optimal behavior changes, which we call
+      \emph{environmental variability}, $u$. At the start of each generation, with
+      probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all
+      other behaviors are assigned a payoff of $\pisub{low}$. Otherwise, the same
+      behavior remains optimal across generations. 
     \item We vary the latent expected payoffs yielded by the bandits. For simplicity,
@@
 For social learning to evolve, it must improve upon individual learning. 
-We found that different parameter settings change how advantageous social learning
-is over and above individual learning. To analyze the effect of uncertainty on
+We found that different parameter settings indeed change how advantageous social learning
+is compared to individual learning (Figure~\ref{fig:meanNetPayoffs}). 
+To analyze the effect of uncertainty on
 payoffs, it is useful to identify some constant reference values which we will
@@
 an agent would receive on average from performing purely random behaviors. 
-Agents learn adaptively over their lifespan (via the softmax algorithm in 
-our model), whether or not they are social learners. We calculated this
-value for reference for each triplet of $\pilow$, $B$, and $L$ 
-\mt{calculate this and add to plot as a guide}. 
-Social learning evolves when the expected payoff of
-social learners exceeds the expected payoff of individual learners.
+Most importantly for understanding the benefit and evolution of social learning,
+we calculated by simulation the expected payoff to individual learners for
+each triplet ($\pilow$, $B$, $L$), which we denote $\langle \pi_I \rangle$
+and plot for reference in Figure~\ref{fig:meanNetPayoffs}. Note $\langle \pi_I
+\rangle$ is insensitive to $u$, which only affects the benefit of social
+learning.
 
-\mt{Use above framework to analyze results after plot guides added as
-promised}
+We observe across parameter settings that social learning outperforms
+individual learning when $u$ is small. In fact, when $u=0.0$, social learning 
+enables each new generation to know the optimal behavior and achieve the maximum
+expected payoff for their lifespan, $\langle \pi^*(L) \rangle$. 
+However, in some cases, even when $u$ is small, 
+the returns on social learning are truly marginal due to 
+relatively high, uniform expected payoffs whether or not agents identify the optimal
+behavior, especially when $\pilow = 0.8$. In intermediate cases, examining the decay
+of the benefit of social learning informs our understanding of social learning
+evolution analyzed above.  As our analysis of social learning evolution suggested,
+social learning is only beneficial up to a point. When $\pilow=0.1$, increasing $B$
+led both to larger differences between
 

### 2022-05-08 ms.tex
added some additional paragraphs to analysis

@@
 \newcommand{\pihigh}{\pisub{high}}
+\newcommand{\piI}{\langle \pisub{I} \rangle}
+\newcommand{\piS}{\langle \pisub{S} \rangle}
 
@@
 
-We ran the simulation for $T=1000$ time steps. At
+We ran the simulation for a maximum of $T_{max}=20000$ time steps. If after a
+generation all agents are either social or individual learners then the
+simulation is stopped since there is no mutation. At
 the end of each generation agents reproduce and then die off. 
@@
 main outcome measure, the prevalence of social learning $s$. For each parameter setting
-in our analysis we calculated the average value of $s$ at the final time step
-of $T=1000$ across 100 runs for each combination of uncertainty parameter values.
+in our analysis we calculated the average value of $s$ at the final time step,
+either at the maximum $T_{\text{max}}=20000$ across 1000 trials 
+for each combination of uncertainty parameter values.
 
@@
 the following parameters:
-$\pisub{low} \in \{0.1, 0.5, 0.8\}$, $B \in \{2, 4, 10\}$, $M \in \{B/2, B, 2B\}$.
+$\pisub{low} \in \{0.1, 0.45, 0.8\}$, $B \in \{2, 4, 10\}$, $L \in \{1, B/2, B, 2B\}$.
 
@@
 
-For social learning to evolve, it must improve upon individual learning. 
-We found that different parameter settings indeed change how advantageous social learning
+For social learning to reliably evolve, it must be more beneficial
+(in terms of payoffs) than individual learning. Inversely, social learning
+should be suppressed when it misleads agents away from quickly identifying the
+optimal behavior through individual learning.
+We found that different parameter settings indeed change how 
+advantageous social learning
 is compared to individual learning (Figure~\ref{fig:meanNetPayoffs}).
+We find that the transition from $\meansl = 1$ to $\meansl = 0$ occurs when
+the mean net payoff among populations of all social learners is close to 
+that of the expected individual learner payoff, $\piI$.
+
 To analyze the effect of uncertainty on
@@
 we calculated by simulation the expected payoff to individual learners for
-each triplet ($\pilow$, $B$, $L$), which we denote $\langle \pi_I \rangle$
-and plot for reference in Figure~\ref{fig:meanNetPayoffs}. Note $\langle \pi_I
-\rangle$ is insensitive to $u$, which only affects the benefit of social
+each triplet ($\pilow$, $B$, $L$), which we denote $\piI$
+and plot for reference in Figure~\ref{fig:meanNetPayoffs}. Note 
+$\piI$ is insensitive to $u$, which only affects the benefit of social
 learning.
@@
 individual learning when $u$ is small. In fact, when $u=0.0$, social learning
-enables each new generation to know the optimal behavior and achieve the maximum
-expected payoff for their lifespan, $\langle \pi^*(L) \rangle$. 
-However, in some cases, even when $u$ is small, 
-the returns on social learning are truly marginal due to 
-relatively high, uniform expected payoffs whether or not agents identify the optimal
-behavior, especially when $\pilow = 0.8$. In intermediate cases, examining the decay
-of the benefit of social learning informs our understanding of social learning
-evolution analyzed above.  As our analysis of social learning evolution suggested,
-social learning is only beneficial up to a point. When $\pilow=0.1$, increasing $B$
-led both to larger differences between
+enables each new generation to know the optimal behavior and achieve the
+maximum expected payoff for their lifespan, $\langle \pi^*(L) \rangle$.
+However, in some cases, even when $u$ is small, the returns on social learning
+are truly marginal due to relatively high, uniform expected payoffs whether or
+not agents identify the optimal behavior, especially when $\pilow = 0.8$. In
+intermediate cases, examining the decay of the benefit of social learning
+informs our understanding of social learning evolution analyzed above.
 
-\subsection{Evolutionary outcomes vary in their certainty}
+As our analysis of social learning evolution suggested, social learning is only
+beneficial up to a point. When $\pilow=0.1$, increased $B$ led both to larger
+differences between payoffs when social learning was more beneficial, and it
+led to $\piS > \piI$ across more values of $u$. This occurs because when there
+are fewer behaviors it is easier for non-social learners to identify the
+optimal behavior on their own. Even relatively small values of $u$ disrupt
+the fidelity of social learning to the point that it being misled is
+prohibitively costly compared to simply finding the optimal on one's own.
+A relatively short lifespan can also extend the utility of social learning
+across more values of $u$ since there are fewer opportunities for agents to
+independently identify and perform the optimal solution.
 
-Finally, we found that the \emph{evolutionary uncertainty} of the system increases
-around the values of $u$ where $\meansl$ goes from 1 to 0. 
-In one sense
-To confirm and expand our analysis of this uncertainty, we 
-also measured environmental uncertainty in terms of the
-expected number of time steps to convergence, $\langle T \rangle$. Evolutionary
-uncertainty is an outcome measure---an emergent form of uncertainty due to
-weak selection pressures. When 
-$\meansl \approx 0.5$ this means that approximately equal numbers of trials
-ended with all agents as social learners as they ended with all agents 
-individual learners. We found that increased $\pilow$
+\subsection{Evolutionary outcome uncertainty}
+
+Finally, we found that the \emph{evolutionary uncertainty} of the system
+increases around the values of $u$ where $\meansl$ goes from 1 to 0.  We know
+that outcomes are uncertain in this region because we know that $\meansl$
+is equivalent to the fraction of outcomes that ended with all agents being
+social learners. $1 - \meansl$ is the fraction of trials that ended with 
+all agents becoming individual learners. Therefore, when $\meansl \approx 0.5$,
+this means roughly half of the simulated trials fixated at $\meansl = 1.0$
+while the other half fixated at $\meansl = 0.0$.
+Only 44 of nearly 400k trials did not go to fixation ($\meansl = 1$ or $\meansl = 0$) 
+within 20k maximum iterations (Table~\ref{tab:convergence}); all that did not
+reach fixation had $B=10$.
+
+We also measured environmental uncertainty more directly, in terms of the
+expected number of time steps to convergence, $\langle T \rangle$.
+Evolutionary uncertainty is thus an outcome measure---an emergent form of
+uncertainty due to weak selection pressures. We found that increased $\pilow$
 tended to increase the overall uncertainty in terms of $\langle T \rangle$.
@@
   \caption{Max. iterations = 5000.}
+  \label{tab:convergence}
   \centering

### 2022-05-12 meanNetPayoffs.tex
updated figures and analysis text

@@
 \begin{figure}
-  \caption{Dependence of average net payoff ($\langle \pi \rangle$) at the
+  \caption{Dependence of average net payoff normalized by lifespan,
+    $\meanpi/L$, at the
     end of last time step of the simulation on environmental
@@
   \label{fig:meanNetPayoffs}
-  \vspace{3em}
-  % $\langle s \rangle$ decreases monotonically for $\pisub{low} = 0.1, 0.5$,
-% but noise dominates the results for $\pisub{low}=0.8$. When $\pisub{low} = 0.5$, 
-% the sigmoid is not as sharp as for $\pisub{low}=0.1$, meaning that social learning
-% is reduced for smaller $u$ and increased for larger $u$.}
   \centering
-  \addtocounter{figure}{-1}  % Hack to get figure numbering correct with subfigure.
   \begin{subfigure}[t]{0.08\textwidth}
-    \vspace{-2em}
-    \hspace{-4em}
-    % \centering
     \begin{tikzpicture}
@@
         {$B$};
-        % {Number of behaviors $B$};
       \draw[->,thick] (0,.1)--(0,-1) node[below]
         {$\pilow$};
-        % {Low payoff frequency $\pilow$};
     \end{tikzpicture}
@@
           \vspace{-3.5em}{\large $ \pilow = 0.1$} \\
-          {\begin{rotate}{-90}{\large $\langle \pi \rangle$}\end{rotate}}
+          {\begin{rotate}{-90}{\large $\frac{\meanpi}{L}$}\end{rotate}}
       }}
     \end{rotate}%
-    % \begin{rotate}{90}
-    %   Social learning $\langle \pi \rangle$
-    % \end{rotate}%
     \includegraphics[width=1.1\textwidth]{
@@
           \vspace{-3.5em} {\large$ \pilow = 0.45$} \\
-          {\begin{rotate}{-90}{\large $\langle \pi \rangle$}\hspace{1em}\end{rotate}}
+          {\begin{rotate}{-90}{\large $\frac{\meanpi}{L}$}\hspace{1em}\end{rotate}}
       }}
     \end{rotate}%
-    % \hspace{1.5em}%
-    % \begin{rotate}{90}
-    %   Social learning $\langle \pi \rangle$
-    % \end{rotate}%
     \includegraphics[width=1.1\textwidth]{
@@
           \vspace{-3.5em} {\large $ \pilow = 0.8$} \\
-          {\begin{rotate}{-90}{\large $\langle \pi \rangle$}\end{rotate}}
+          {\begin{rotate}{-90}{\large $\frac{\meanpi}{L}$}\end{rotate}}
       }}

### 2022-05-12 ms.tex
updated figures and analysis text

--- 2022-05-04 ms.tex
@@
 
-\newcommand{\meansl}{\langle s \rangle}
+\newcommand{\meanvar}[1]{\langle #1 \rangle}
+\newcommand{\meansl}{\meanvar{s}}
+\newcommand{\meanpi}{\meanvar{\pi}}
+\newcommand{\meansoc}{\meanvar{\pi_\mathrm{S}}}
+\newcommand{\meanasoc}{\meanvar{\pi_\mathrm{A}}}
+\newcommand{\meanT}{\meanvar{T}}
 
@@
 probabilistic payoffs~\cite{SuttonBartoBook, McElreath2005,Rendell2010,Schulz2019}. %Bandits are like  slot machines in a casino~\ref{fig:behaviorSelection}.
-Each behavior $b$ yields a payoff of 1 with probability $\pi_b$ and a payoff of zero
-otherwise; $\pi_b$ is therefore also the expected payoff of behavior $b$. Agents must
+Each behavior $b$ yields Bernoulli payoffs: payoff of 1 with probability $\pi_b$ and zero payoff
+with probability $1 - \pi_b$; 
+$\pi_b$ is therefore also the expected payoff of behavior $b$. Agents must
 decide which behavior to perform at each time step. To do this, agents 
@@
 (3) the number of possible behaviors, $B$; and 
-(4) the lifespan, or time steps per generation, $M$.
+(4) the lifespan, or time steps per generation, $L$.
 
-We ran the simulation for $T=1000$ time steps. At
+We ran the simulation until agents evolved to be all social or all asocial 
+learners, or until 20k time steps was reached. Only 44 out of 396k trials
+did not reach fixation (all social or all asocial). At
 the end of each generation agents reproduce and then die off. 
@@
 across agents and trials, which is our primary outcome measure, 
-denoted $\langle s \rangle$.
+denoted $\meansl$.
 
@@
 through performance-biased oblique learning. Agent $i$'s accumulated payoffs
-from performing several behaviors over their lifetime of $M$ time steps is
+from performing several behaviors over their lifetime of $L$ time steps is
 denoted $\pi_{i}$.
-
-\vspace{2em}
 
@@
     \label{tab:modelParameters}
-    \centering \hspace{-3em}
-    \begin{tabular}{cp{4.0in}l} \toprule
+    \centering %\hspace{-3em}
+    \begin{tabular}{cp{2.5in}p{1.0in}} \toprule
 
@@
 \end{table}
-
-\vspace{2em}
-
 \subsection{Modeling uncertainty}
@@
 In our model uncertainty is a tunable consequence of four environmental features:
-%that structure the behavior of agents.  
-% Many factors contribute to the 
-% uncertainty involved in both social and asocial learning. 
-%We model uncertainty in four distinct ways: 
 \begin{enumerate}
-    \item We vary the frequency at which the optimal behavior changes, which we call \emph{environmental variability}, $u$.
-At the start of each generation, with probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all other behaviors are assigned a payoff of $\pisub{low}$.
-Otherwise, the same behavior remains optimal across generations.
+    \item 
+      We vary the frequency at which the optimal behavior changes, which we call
+      \emph{environmental variability}, $u$. At the start of each generation, with
+      probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all
+      other behaviors are assigned a payoff of $\pisub{low}$. Otherwise, the same
+      behavior remains optimal across generations. 
     \item We vary the latent expected payoffs yielded by the bandits. For simplicity,
@@
       behavior is the optimal one.
-      % The difference between these quantities is the \emph{payoff ambiguity}, 
-    % \begin{equation}
-    %   A_\pi = 1 - (\pisub{high} - \pisub{low}),
-    %   \label{eq:payoffAmbiguity}
-    % \end{equation}
-    % which is maximized when the expected payoffs are close to equal and minimized
-    % when they differ greatly. For simplicity we will set $\pisub{high} = 0.9$
-    % for all analyses and vary $\pisub{low}$ in order to vary $A_\pi$.
     \item We vary the total \emph{number of available behaviors}, $B$, which is a
       source of uncertainty since agents are less likely to know which behavior yields high payoffs.  
-    \item Finally, we vary number of behavioral events per generation, $M$.
+    \item Finally, we vary number of behavioral events per generation, $L$.
 This can be viewed as the \emph{effective lifespan} of an agent.
 Decreasing this lifespan effectively increases the importance of each event for acquiring payoffs.
-When lifespans are short ($M$ is small), agents experience greater uncertainty about which behavior is optimal given the fewer learning opportunities.
+When lifespans are short ($L$ is small), agents experience greater uncertainty about which behavior is optimal given the fewer learning opportunities.
 \end{enumerate}
@@
 behavior, or with probability $\pilow$ if it is one of $B-1$ non-optimal
-behaviors. Agents accumulate payoffs in this way for $M$ time steps in each
+behaviors. Agents accumulate payoffs in this way for $L$ time steps in each
 generation. At the end of each generation, $N=100$ agents are randomly selected with
@@
 parent generation as potential teachers, then selecting the one with the 
-greatest net payoffs among the subset. This process continues until $T=1000$
-time steps have elapsed \mt{this should probably be changed depending on $M$ so that
-    all analyses use the same number of generations. my informal checks have shown quick
-convergence, but i haven't tested b=4 and b=10 as much.}.
+greatest net payoffs among the subset. This process continues until agents
+have become all social or all asocial learners, or when $20k$ time steps have
+elapsed.
 
@@
   \caption{Model dynamics are composed of two major parts: first, agents perform
-  behaviors for $M$ time steps in a single generation. Then agents reproduce
+  behaviors for $L$ time steps in a single generation. Then agents reproduce
   randomly, with more successful agents being more likely to reproduce. Newly
@@
   begin a new generation, and the process continues until 1000 total time steps
-  have elapsed. Agents are initialized as ``blank slates''.}
+  have elapsed. Agents are initialized as ``blank slates''. \mt{Can compress this
+  into triptych. $M \rightarrow L$. Lighten grey background, remove outlines
+around most or all components. Replace text in picture with A, B, C, and 
+explain in caption.}}
   \label{fig:IntraInterGenerationalDynamics}
@@
 specify the environmental variability, $u$, and the number of time steps per 
-generation, $M$.
+generation, $L$.
 
@@
 \begin{table}[h]
-    \caption{Global environmental and cognitive initialization parameters.}
+    \caption{Global environmental and cognitive initialization parameters.
+    \mt{TODO: Test more $N_\text{T}$ for sensitivity analysis}}
     \label{tab:modelParameters}
-    \centering \hspace{-3em}
-    \begin{tabular}{cp{4.0in}l} \toprule
+    \centering %\hspace{-3em}
+    \begin{tabular}{cp{2.5in}p{1in}} \toprule
 
@@
 
-        $M$    & Number of time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
+        $L$    & Number of time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
 
         $N_T$    & Number of teachers to pool, from which best selected 
-                 & \textbf{5} \mt{TODO: Test more for sensitivity analysis?} \\
+                 & \textbf{5}  \\
 
@@
 \end{table}
-\vspace{2em}
 
@@
 the chosen bandit pays off for an agent, its net payoff is incremented by one,
-$\pi'_i \leftarrow \pi_i + 1$. This process continues for $M$ time steps, 
-when reproduction, learning, and die-off occur, re-initializing the next 
-generation for performing $M$ behaviors selected via this same process.
+$\pi'_i \leftarrow \pi_i + 1$. This process continues for $L$ time steps, 
+at which point reproduction, learning, and die-off occur, which re-initializes 
+the next generation for performing $L$ behaviors selected via this same process.
 
@@
 more frequent exploitation. We set $\tau = 0.1$ for
-all computational analyses presented in the main paper. We (WILL HAVE) performed
+all computational analyses presented in the main paper. We 
+ performed
 sensitivity analyses and found a weak dependence on $\tau$ that does not affect our
-main conclusions.
+main conclusions \mt{have run $\tau$ sensitivity checks, need to analyze them}.
 
@@
 
-Every $M$ time steps, agents from the current generation reproduce, teach,
-and die, while the next generation to perform the next $M$ time steps learns
+Every $L$ time steps, agents from the current generation reproduce, teach,
+and die, while the next generation to perform the next $L$ time steps learns
 from one teacher from the previous generation if they inherited the social 
@@
 
-\subsection{Computational analyses}
+\subsection{Computational analyses and outcome measures}
 
 We manipulated environmental uncertainty parameters described above, $u$,
-$\pisub{low}$, $B$, and $M$, to examine their effects on our
-main outcome measure, the prevalence of social learning $s$. For each parameter setting
-in our analysis we calculated the average value of $s$ at the final time step
-of $T=1000$ across 100 runs for each combination of uncertainty parameter values.
-
-To analyze the effect of various forms of uncertainty on social learning 
-prevalence in our Analysis, we initialized several model runs with
-different uncertainty parameters $u$, $\pisub{\mathrm{low}}$, $B$,
-and $M$. We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$ for each combination of
+$\pisub{low}$, $B$, and $L$, to examine their effects on our
+main outcome measure, the mean prevalence of social learning $\meansl$, 
+and supplemental outcome measures $\meanpi / L$ and $\meanT / L$. $\meanpi / L$ is the
+mean net payoffs accumulated by agents at the end of each generation for the
+final generation of agents, normalized by lifespan $L$. $\meanT / L$ is the 
+mean time steps to convergence normalized by the lifespan of agents, i.e., the
+mean number of generations until convergence was reached. Mean values were
+caluculated across 100 model runs for each combination of uncertainty parameter values.
+To test the effect of the uncertainty parameters, 
+we initialized several model runs with
+systematically varied uncertainty parameters, $u$, $\pisub{\mathrm{low}}$, $B$,
+and $L$. We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$ for each combination of
 the following parameters:
-$\pisub{low} \in \{0.1, 0.5, 0.8\}$, $B \in \{2, 4, 10\}$, $M \in \{B/2, B, 2B\}$.
-
-\subsubsection{Outcome variables}
-
-Our primary outcome variable is the mean prevalence of the social learning
-trait over $N=100$ agents over 1000 trials at the final time step of each trial,
-denoted $\meansl$.
-Typically at the final time step all agents either have the social learning
-trait or do not (see Supplement for a presentation of time series collections
-and histograms of outcomes for
-a representative sampling of variables \mt{TODO}).
+$\pisub{low} \in \{0.1, 0.5, 0.8\}$, $B \in \{2, 4, 10\}$, and
+$L \in \{1, B, 2B, 4B\}$ for $B=2$ and $L \in \{1, B/2, B, 2B\}$ for $B=4,10$.
 
 \begin{table}[h]
-    \caption{Global environmental and cognitive initialization parameters.}
-    \label{tab:modelParameters}
-    \centering \hspace{-3em}
-    \begin{tabular}{cp{4.0in}l} \toprule
+    \caption{Outcome variables}
+    \label{tab:outcomeVariables}
+    \centering %\hspace{-3em}
+    \begin{tabular}{cp{2.5in}p{1in}} \toprule
 
@@
 
-        $p_{\text{opt}}$ & Fraction of population performing optimal behavior
-                         & $\in [0.0, 1.0]$ \\
+        $\meanpi / L$ & Mean payoffs accumulated in a generation normalized by
+        lifespan & $\in [0.0, 1.0]$ \\
 
-        \texttt{count}$(b_i)$ & Number of agents performing behavior $b$ 
-                              & Behavior-count key-value pairs\\
+        $\meanT / L$ & Mean number of generations to convergence & Bounded above by 20k / 8\\
         \bottomrule
@@
 
+\subsection{A note on relationship with standard RL formalism and models}
+
+We presented our model as an agent-based model because that is
+how we originally developed it. Howevever, we believe the model could be 
+translated in a straightforward way where each action at time $t$, typically denoted
+$a_t$, is to ``pull'' one of the $B$ bandits, and the policy $\pi$ would 
+involve using the softmax function to weight random behavior
+selection~\cite{SuttonBartoBook}. Because of the complication of two
+relevant time intervals, intervals between actions and generational intervals, and
+space limitations we do not try to put the entire model in standard RL terms.
+\mt{Expand/improve.}
+
 \section{Analysis}
 
-We analyzed the outcomes of model runs across systematically varied uncertainty
-parameters over 1000 trials for each parameter setting. 
-We observed complex outcomes where the effects of uncertainty parameters
-were highly dependent on one another as measured by the mean prevalence of
-social learning, $\meansl$, across trials for each parameter setting. 
-The prevalence of social learning
-generally decreased with environmental variability, $u$, as expected from standard
-models of social learning evolution. However, the shape of the decrease was not
-uniform (Figure~\ref{fig:evolutionOfSL}). 
-We observed that social learning did in fact enable populations to 
-do better than individual learners, but only when (multi-dimensional) uncertainty 
-were sufficiently limited (Figure~\ref{fig:meanNetPayoffs}).
+To understand the effect of uncertainty parameters (1) environmental variability, $u$; (2) payoff
+ambiguity that increases with $\pilow$; (3) number of behavioral options, $B$; and 
+(4) generation length/agent lifespan, $L$, on the evolution of social learning, we analyze the results of
+model runs across systematically varied parameter combinations.  We observed complex
+outcomes where the effects of uncertainty parameters were highly dependent on one
+another as measured by the mean prevalence of social learning, $\meansl$, across
+trials for each parameter setting.  Increased environmental variability, $u$, 
+tended to suppress social learning as expected from standard models of
+social learning evolution. However, the shape of the decrease in $\meansl$ 
+was not uniform (Figure~\ref{fig:evolutionOfSL}). 
+Depending on the parameter settings, the critical value of $u$ at which social 
+learning suppression began varied, as did the steepness of the decrease. 
+We found that the location and width of the decrease in $\meansl$ is correlated
+with the difference between the expected net payoffs of a population of all
+social learners, $\meansoc$, and the expected net payoffs
+of an all-asocial learner population, $\meanasoc$ (Figure~\ref{fig:meanNetPayoffs}). 
+evolution does not always choose the theoretically highest payoff strategy,
+and confirmed that evolution is more uncertain (i.e.\ selection is
+weaker~\cite[p. 103]{BoydRicherson1985}) when $\meansoc - \meanasoc$ is small, 
+where evolutionary uncertainty is measured by the 
+average steps to model convergence, $\meanvar{T}$ (Figure~\ref{fig:steps}).
 
 \subsection{Evolution of social learning under uncertainty}
-The shape of the decrease from all agents
-always becoming social learners ($\meansl = 1.0$) to 
-all agents always becoming individual learners ($\meansl = 0.0$)
-is heterogeneous. We identified patterns in this heterogeneity that inform our
-understanding of when and how social learning is advantageous, and when 
-and why individual learning is advantageous. 
-Changes in the uncertainty parameters ($\pilow$, $B$, $L$) 
-result in the following changes in the shape of the transition from $\meansl = 1.0$ 
-to $\meansl = 0.0$: (1) the transition
-occurs at different critical values of $u$; and (2) the transition occurs
-with greater or lesser rapidity over $u$. 
-For instance, when $B=2$, $\pilow = 0.1$, and $L=8$, $\meansl$ goes from 1 to 
-0 starting at $u=0.1$ and reaches 0 at $u=0.3$ (Figure~\ref{fig:evolutionOfSL},
-top left). When we increased $B=4$ (Figure~\ref{fig:evolutionOfSL}, top center), the
-transition from $\meansl = 1$ to 0 begins at $u=0.3$. When $B=4$, $\pilow=0.1$,
-and $L=1$ the transition from $\meansl=1$ to 0 begins at $u=0.3$ but does not
-reach 0 until $u \approx 0.9$ (again Figure~\ref{fig:evolutionOfSL}, top center).
 
-We can draw some conclusions about the evolution of social learning by analyzing the
-location and shape of the suppression of social learning as $u$ was increased.
-First, let us observe some general trends. Increased $\pilow$ generally
-flattened the suppression of social learning as $u$ increased.  
-Increased $B$ tended to increase the critical value of $u$ at which the 
-system transitions from favoring social learning to favor individual learning.  
-Increased $L$ generally sharpened the suppression of social learning.
-Within each of these broad trends over the uncertainty parameters are several
-details that depend on context as defined by the values of the other uncertainty
-parameters.
+We observed that different uncertainty contexts lead to different patterns in
+the evolution and suppression of social learning. To understand the evolution
+and suppression of social learning we inspected the social learning prevalence,
+$\meansl$, which is the average of the frequency of social learning across
+a model population over all trial model runs for a 4-tuple of uncertainty
+values, $(u, \pilow, B, L)$.  We plot $\meansl$ on the y-axis 
+over $u=0.0,0.1,\ldots,1.0$ on the x-axis in each plot, with nine plots total over
+$\pilow=0.1,0.45,0.8$ and $B=2,4,10$, broken out by $L=1,B/2,B,2B$ within each plot
+(Figure~\ref{fig:evolutionOfSL}). Across uncertainty scenarios, $\meansl$ monotonically
+decreases $u$ increases, in accordance with classic cultural evolutionary
+predictions~\cite{CavalliFeldman1981,BoydRicherson1985,Feldman1996}.  Therefore we compare
+differences between uncertainty contexts in terms of the \emph{suppression of social learning}
+over (increasing) $u$.
 
-When $\pilow$ was increased, the suppression of social learning was, in
-general, less rapid as $u$ increased. This effect is particularly acute when
-$\pilow = 0.8$, which is very nearly equal to the expected value of the optimal
-payoff, $\pihigh = 0.9$. When $\pilow = 0.8$ $\meansl$ never actually reaches 
-1 or 0 for any parameter settings. The suppression of social learning in this
-case is approximately linear, if there is selection at all. When $\pilow = 0.8$
-and $L = 1$ there is little to no selection across $B$, 
-so populations evolve randomly towards $\meansl = 1$ or $\meansl = 0$.
+Differences emerged in the suppression of social learning on two dimensions.
+First there were systematic differences in the value of $u$ when social
+learning first begins to be suppressed, i.e., where $\meansl$ first decreases. We show
+in the following subsection that this occurs when $\meansoc$ approaches $\meanasoc$.
+The second dimension of analysis is the width of the transition from 
+maximal to minimal $\meansl$. In some cases, this width was less than 1, but
+in many other cases the width was equal to 1, meaning that $\meansl$ 
+decreased over all $u$. This indicated weak selection pressure since 
+less than 0.001\% of all trials ended with all agents either social or asocial
+learners. This is confirmed below by examining the average number of time steps
+it took to reach fixation (agents all social or all asocial).
 
-Increased $B$ generally led to increased critical $u$ at which social learning
-starts to be suppresed. When payoffs are not ambiguous ($\pilow = 0.1$), the the
-suppression of social learning starts at $u \approx 0.1$ for $B=2$; at $u \approx
-0.3$ when $B=4$; and at $u \approx 0.5$ when $B=10$.  When payoffs are more
-ambiguous ($\pilow = 0.45,0.8$), increased $B$ also led to a flattening of the
-suppression of social learning when $L=1$.
+For now we will examine differences in the location and width of social 
+learning suppression. \mt{In outline form while I work out each point}
+\begin{itemize}
+  \item 
+    First, note that as $\pilow$ increases towards $\pihigh = 0.9$, social learning
+    suppression widens, becoming linearly decreasing over $u$ with no $\meansl$
+    reaching 1 or 0. This is due to weakened selection as the difference between
+    social and asocial learning payoffs goes to zero.
+  \item
+    Second, as $B$ increases, note that social learning suppression 
+    begins at increasingly high $u$. This is because it is increasingly worth
+    the risk that a socially-learned ledger biases agents towards non-optimal
+    behaviors when the number of choices increases. Furthermore, when $B$ is
+    larger, one large ledger entry is not as misleading as when $B$ is smaller
+    since there is more probability mass in the softmax vector's non-maximal
+    behavior entries when $B$ is larger, and so alternatives to the socially
+    learned ``best'' behavior will be explored more frequently.
+  \item
+    Finally, note that decreased lifespan both increases the location of 
+    social learning suppression and the width of social learning suppression,
+    with the extreme case of $L=1$ becoming linear and eventually flat compared
+    to other values of $L$ as $\pilow$ and $B$ increase.
+\end{itemize}
+To support these explanations we need to analyze the average payoffs 
+obtained by agents in these various uncertainty contexts and compare them
+with the expected payoffs when all agents are individual learners, and with the
+expected payoffs when all agents are social learners.
 
-The general effect of $L$ is to increase the rapidity of the suppression of social
-learning via the strengthening of selection pressure since longer-lived agents
-build up stronger priors over their lifetimes. If it is advantageous to
-learn socially, this will be reliably detected. Inversely, decreased $L$
-can weaken selection pressure since agents cannot amass useful information when
-$L$ is small. This is most extreme when $\pilow = 0.8$ and there is little to
-no selection for or against social learning when $L=1$. However, decreased $L$ can
-also delay the suppression of social learning as $u$ increases, since social
-learning provdes agents with the possibility of learning what the optimal behavior
-might be.  Even when $u$ was large, agents with a lifespan of 1 more often evolved
-to be social learners because social learning was to be preferred over random
-chance.
+\subsection{Relative benefit of social learning}
 
-\subsection{Social learning capacity increases payoffs}
+Social learning begins to be suppressed when the expected payoffs from 
+a population of all social learners, $\meansoc$ (Figure~\ref{fig:meanNetPayoffs};
+small dashed line with diamond markers),
+decreased to the point where they are nearly the same as expected payoffs for
+a population of all individual learners, $\meanasoc$
+(Figure~\ref{fig:meanNetPayoffs}; horizontal long-dash lines). We see that social 
+learning becomes completely suppressed when $\meansoc < \meanasoc$.  Mean 
+payoffs realized by model agents approximately track expected payoffs of
+whichever strategy is optimal, social or asocial learning, but with some important
+variation.
 
-For social learning to evolve, it must improve upon individual learning. 
-We found that different parameter settings change how advantageous social learning
-is over and above individual learning. To analyze the effect of uncertainty on
-payoffs, it is useful to identify some constant reference values which we will
-use to evaluate the benefit of social learning. First, the optimal expected payoff
-is the optimal behavior payoff times the lifespan, which we can denote
-$\langle \pi^*(L) \rangle = L\cdot\pihigh$. The expected base payoff by chance is 
-$\langle \pi_{\text{base}} \rangle = L \left[ (B - 1) \pilow + \pihigh \right]$, which
-an agent would receive on average from performing purely random behaviors. 
-Agents learn adaptively over their lifespan (via the softmax algorithm in 
-our model), whether or not they are social learners. We calculated this
-value for reference for each triplet of $\pilow$, $B$, and $L$ 
-\mt{calculate this and add to plot as a guide}. 
-Social learning evolves when the expected payoff of
-social learners exceeds the expected payoff of individual learners.
+Similarly, sometimes populations that start out mixed outperform all
+social learner populations when $\meansoc > \meanasoc$, indicating that an initial
+diversity of learner types helps with the long-term prosperity of the group, even
+though the asocial learner type tends to die out. \mt{I suspect
+this may be sensitive to $N_T$, so my next analysis will be the effect
+of $N_T$.}
 
-\mt{Use above framework to analyze results after plot guides added as
-promised}
+Second, notice that asocial learning may be the safe fallback option when 
+evolution is unsure which strategy is optimal, 
+but a population of all social learners would do better
+than what evolution tended to select for (Figure~\ref{fig:meanNetPayoffs},
+e.g., when $\pilow=0.45$, $B=2$, and $L=8$ in the middle left plot). \mt{I suspect
+this will also be sensitive to $N_T$.}
 
-\subsection{Evolutionary outcomes vary in their certainty}
+\subsection{Selection strength and evolutionary uncertainty}
 
-Finally, we found that the \emph{evolutionary uncertainty} of the system increases
-around the values of $u$ where $\meansl$ goes from 1 to 0. 
-In one sense
-To confirm and expand our analysis of this uncertainty, we 
-also measured environmental uncertainty in terms of the
-expected number of time steps to convergence, $\langle T \rangle$. Evolutionary
-uncertainty is an outcome measure---an emergent form of uncertainty due to
-weak selection pressures. When 
-$\meansl \approx 0.5$ this means that approximately equal numbers of trials
-ended with all agents as social learners as they ended with all agents 
-individual learners. We found that increased $\pilow$
-tended to increase the overall uncertainty in terms of $\langle T \rangle$.
-Increasing $B$ also increased the $u$ at which $\langle T \rangle$ peaked.
-This indicates the evolutionary system is significantly less certain of 
-which behavior is optimal around critical uncertainty parameter ensembles.
+If selection is truly weaker when $\meansoc \approx \meanasoc$, then we should not
+only see a more perfect bimodality of outcomes, with roughly half of outcomes going
+to both $\meansl = 1$ and $\meansl = 0$, but we should also see the models taking
+longer to converge in this situation.  Indeed, weak selection is also evidenced by
+spiking or elevated average time to convergence, $\meanT$, around when theoretical
+$\meansoc$ and observed $\meanpi$ approach $\meanasoc$. Recall that models are run
+until they reach fixation or until they reach 20k time steps. Only 44 out of 396k
+did not reach fixation, less than 0.001\% of all trials.
 
-\mt{interpret this further}
+\input{mainResultsPlots.tex}
 
-\include{mainResultsPlots.tex}
+\input{meanNetPayoffs.tex}
 
-\include{meanNetPayoffs.tex}
-
-\include{stepResultsPlots.tex}
+\input{stepResultsPlots.tex}
 
 \section{Discussion}
+
+\begin{itemize}
+  \item 
+    Increasingly, engineers are blurring the line between humans and AI agents in designing
+    effective interventions to the wicked problems we face
+    today~\cite{Irrgang2021,Rolnick2022}.
+  \item
+    We have connected such augmented intelligence technologies as MARL to
+    cultural evolution, which is a promising approach to addressing existential
+    threats to life on Earth~\cite{Jones2021}.
+\end{itemize}
+
+% \section{Model}
+
+% We developed an agent-based model of a society of $N$ individuals who each must decide
+% which of $B$ behaviors to perform at each time step. Each behavior is a ``bandit'',
+% a common modelling and experimental approach for representing behaviors with
+% probabilistic payoffs~\cite{SuttonBartoBook, McElreath2005,Rendell2010,Schulz2019}. %Bandits are like  slot machines in a casino~\ref{fig:behaviorSelection}.
+% Each behavior $b$ yields a payoff of 1 with probability $\pi_b$ and a payoff of zero
+% otherwise; $\pi_b$ is therefore also the expected payoff of behavior $b$. Agents must
+% decide which behavior to perform at each time step. To do this, agents 
+% use an explore-exploit strategy to sometimes try the most profitable behavior
+% they know about, and other times try alternatives that may pay off more reliably.
+
+% We operationalized uncertainty in four different ways: 
+% (1) payoff ambiguity, $A_\pi$, which measures the difference
+% between the optimal expected payoff behavior $\pisub{high}$ and the expected payoff
+% of the other behaviors, $\pisub{low}$; 
+% (2) environmental variability, $u$, the probability the optimal behavior changes from one generation to another; 
+% (3) the number of possible behaviors, $B$; and 
+% (4) the lifespan, or time steps per generation, $M$.
+
+% We ran the simulation for $T=1000$ time steps. At
+% the end of each generation agents reproduce and then die off. 
+% Those selected to reproduce
+% pass on their boolean social learning trait, $s$, without mutation,
+% which specifes whether agents learn socially. We developed a series of
+% computational analyses where we systematically vary the uncertainty
+% variables and observe the average prevalence of social learning trait $s$
+% across agents and trials, which is our primary outcome measure, 
+% denoted $\langle s \rangle$.
+
+% \subsection{Agents and their attributes}
+
+% In each time step, $N$ agents---autonomous problem solvers---select 
+% which behavior to perform based on their running tally of mean payoffs for 
+% each available behavior. %information (Figure~\ref{fig:behaviorSelection}). 
+% Agent $i$ tracks the mean payoff of each behavior $b$, denoted $\bar\pi_{ib}$, and
+% a \emph{count} of how many times it has performed each behavior, denoted $c_{ib}$.
+% $\bar\pi_{ib}$
+% is initialized to 0 for all $b$ at model initialization for
+% all agents, and after each generation for individual learner agents. Social
+% learning agents' $\bar\pi_{ib}$ is initialized as that of its teacher selected
+% through performance-biased oblique learning. Agent $i$'s accumulated payoffs
+% from performing several behaviors over their lifetime of $M$ time steps is
+% denoted $\pi_{i}$.
+
+% \vspace{2em}
+
+% \begin{table}[h]
+%     \caption{Dynamic agent-level variables. Each has an implicit time dependence.}
+%     \label{tab:modelParameters}
+%     \centering \hspace{-3em}
+%     \begin{tabular}{cp{4.0in}l} \toprule
+
+%         Attribute & Description & Initial value \\
+
+%         \midrule
+
+%         $s_i$  & Social learner trait: 1 if agent $i$ is social learner; 0 otherwise & 0
+%         or 1 w/ equal prob. \\
+
+%         $\bar\pi_{ib}$ & ``Ledger'': mean payoffs acquired via behavior $b$ by $i$ 
+%                        & $B$-vector of floating-point zeros \\
+
+%         $c_{ib}$ & Count of how many times agent $i$ performed $b$ 
+%               & $B$-vector of integer zeros \\
+
+%         $\pi_i$ & Net payoffs accumulated by $i$ within generation
+%                                 & 0.0 \\
+%         \bottomrule
+%     \end{tabular}
+% \end{table}
+
+% \vspace{2em}
+
+% \subsection{Modeling uncertainty}
+
+% In our model uncertainty is a tunable consequence of four environmental features:
+% \begin{enumerate}
+%     \item 
+%       We vary the frequency at which the optimal behavior changes, which we call
+%       \emph{environmental variability}, $u$. At the start of each generation, with
+%       probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all
+%       other behaviors are assigned a payoff of $\pisub{low}$. Otherwise, the same
+%       behavior remains optimal across generations. 
+%     \item We vary the latent expected payoffs yielded by the bandits. For simplicity,
+%       we assume that in any given environmental state, there is one optimal behavior that
+%       yields an expected payoff of $\pisub{high}$, while all other behaviors yield a 
+%       payoff of $\pisub{low} < \pisub{high}$. As $\pilow$ increases towards 
+%       $\pihigh$, uncertainty in the form of \emph{payoff ambiguity} also increases,
+%       making it more difficult, and less rewarding, for agents to determine which
+%       behavior is the optimal one.
+%     \item We vary the total \emph{number of available behaviors}, $B$, which is a
+%       source of uncertainty since agents are less likely to know which behavior yields high payoffs.  
+%     \item Finally, we vary number of behavioral events per generation, $M$.
+This can be viewed as the \emph{effective lifespan} of an agent.
+Decreasing this lifespan effectively increases the importance of each event for acquiring payoffs.
+When lifespans are short ($M$ is small), agents experience greater uncertainty about which behavior is optimal given the fewer learning opportunities.
+% \end{enumerate}
+
+% \subsection{Dynamics and evolution}
+
+% Model dynamics can be split into three parts: initialization,
+% \emph{intra}generational behavior and payoff accumulation, and
+% \emph{inter}generational transmission of the social learning trait and oblique
+% learning (Figure~\ref{fig:IntraInterGenerationalDynamics}). 
+% The model runs that we analyze here were initialized with $N=100$ agents
+% to randomly have the social learner trait or not, with no accumulated payoffs, and
+% blank ``ledgers''. At each time step, agents select one of $B$ possible behaviors
+% to perform, accumulating a payoff of 1 if the bandit pays off, and 0 if it does
+% not---a bandit pays off with probability $\pihigh$ if it is the unique optimal
+% behavior, or with probability $\pilow$ if it is one of $B-1$ non-optimal
+% behaviors. Agents accumulate payoffs in this way for $M$ time steps in each
+% generation. At the end of each generation, $N=100$ agents are randomly selected with
+% replacement to reproduce (asexual, haploid reproduction), 
+% weighted by their net payoffs over the generation,
+% i.e., \emph{performance-biased} reproduction. Child agents then learn from 
+% one teacher, selected again via a form of performance bias: a child agent chooses
+% its teacher by first selecting a fully random subset of agents from the 
+% parent generation as potential teachers, then selecting the one with the 
+% greatest net payoffs among the subset. This process continues until $T=1000$
+% time steps have elapsed \mt{this should probably be changed depending on $M$ so that
+%     all analyses use the same number of generations. my informal checks have shown quick
+% convergence, but i haven't tested b=4 and b=10 as much.}.
+
+% \begin{figure}
+%   \caption{Model dynamics are composed of two major parts: first, agents perform
+%   behaviors for $M$ time steps in a single generation. Then agents reproduce
+%   randomly, with more successful agents being more likely to reproduce. Newly
+%   ``born'' social learner agents use success bias to select and learn from a chosen
+%   teacher. Then, all agents from the previous generation die off, all new agents
+%   begin a new generation, and the process continues until 1000 total time steps
+%   have elapsed. Agents are initialized as ``blank slates''.}
+%   \label{fig:IntraInterGenerationalDynamics}
+%   \centering
+%     \includegraphics[width=0.9\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+% \end{figure}
+
+% \subsubsection{Initialization}
+
+% Model initialization includes agent and environment initializations. Agents are
+% randomly initialized to have the social learning trait or not, with equal 
+% probability. Agent ``ledgers'' and behavior counts 
+% are uniformly initialized to the no-knowledge,
+% blank-slate case where all $\pi_{ib} = 0$ and $c_{ib} = 0$. Both the 
+% ledger and behavior count vectors have $B$ entries, one for each
+% behavior the environment affords. Net payoffs for
+% the generation are also initialized to zero. All agents are initialized with
+% the same softmax temperature, $\tau$, that guides their behavior selection 
+% to be either more exploratory (greater $\tau$) or more exploitative of
+% what agents believe to be the optimal behavior(s) (lesser $\tau$).
+
+% The environment is initialized to have $B$ behaviors with one of them selected
+% at random to be the optimal behavior, denoted $b^*$. Behavior $b^*$ is 
+% initialized to have a probability $\pihigh$ of paying off 1. All other behaviors
+% are initialized to have probability $\pilow$ of paying off 1. The modeler must
+% specify the environmental variability, $u$, and the number of time steps per 
+% generation, $M$.
+
+% \vspace{2em}
+% \begin{table}[h]
+%     \caption{Global environmental and cognitive initialization parameters.}
+%     \label{tab:modelParameters}
+%     \centering \hspace{-3em}
+%     \begin{tabular}{cp{4.0in}l} \toprule
+
+%         Symbol & Description & Values tested (bold$=$default) \\
+
+%         \midrule
+
+%         $B$       & Number of possible behaviors (represented by ``bandits'') 
+%                   & 2, 4, 10 \\
+
+%         $\pihigh$ & Probability that the unique optimal behavior pays off 1 
+%                 & \textbf{0.9} \\
+
+%         $\pilow$ & Probability one of $B - 1$ non-optimal behaviors pays off 1 
+%                  & 0.1, 0.45, 0.8 \\
+
+%         $\tau$ & Softmax temp.; $\uparrow=$more exploration, $\downarrow=$more
+%                     exploitation 
+%                & 0.01, \textbf{0.1}, 1.0 \\
+
+%         $u$    & Probability optimal behavior changes between generations 
+%                & 0.0, 0.1, \ldots, 1.0 \\
+
+%         $M$    & Number of time steps per generation & 1, $B/2$, $B$, $2B$ \\
+
+%         $N_T$    & Number of teachers to pool, from which best selected 
+%                  & \textbf{5} \mt{TODO: Test more for sensitivity analysis?} \\
+
+%         \bottomrule
+%         \end{tabular} 
+% \end{table}
+% \vspace{2em}
+
+% \subsubsection{Intra-generational behaviors and payoffs}
+
+% Each generation begins with agents initialized either by the $t=0$ initialization
+% outlined above, or initialized via inter-generational reproduction and learning,
+% described in detail below. Within generations, there is no social learning.
+% At each time step within a generation, agents select a behavior to perform
+% using the softmax algorithm, then update their ledgers $\bar\pi_{ib}$ and behavior
+% counts $c_{ib}$. If 
+% the chosen bandit pays off for an agent, its net payoff is incremented by one,
+% $\pi'_i \leftarrow \pi_i + 1$. This process continues for $M$ time steps, 
+% when reproduction, learning, and die-off occur, re-initializing the next 
+% generation for performing $M$ behaviors selected via this same process.
+
+% At each time step, 
+% agent $i$ chooses behavior $b$ at random, with each behavior
+% weighted by the softmax function applied to that behavior's observed mean payoff
+% relative to all mean payoffs in the ledger,
+% \begin{equation}
+%   \Pr(i \text{ chooses behavior } b) = \frac{\exp(\bar\pi_{ib}
+%   / \tau) }{ \sum_{b=1}^B \exp(\bar\pi_{ib} / \tau)}.
+% \end{equation}  
+% Softmax behavior selection is a
+% biologically plausible model of behavior~\cite{Schulz2019} 
+% that enables agents to explore
+% alternative behaviors sometimes and exploit the best observed behavior other times,
+% in accordance with Luce's choice axiom~\cite{Luce1959},.
+% The parameter $\tau$ specifies how frequently alternative behaviors are
+% explored versus how frequently the best observed behaviors are 
+% exploited. Greater $\tau$ means more frequent exploration, lesser $\tau$ means
+% more frequent exploitation. We set $\tau = 0.1$ for
+% all computational analyses presented in the main paper. We (WILL HAVE) performed
+% sensitivity analyses and found a weak dependence on $\tau$ that does not affect our
+% main conclusions.
+
+% When agent $i$ performs behavior $b$, $i$'s behavior count 
+% is incremented by 1, $c'_{ib} \leftarrow c_{ib} + 1$. Agent $i$'s ledger of mean 
+% payoffs are updated % from $\bar\pi_{ib}$ to $\bar\pi_{ib}'$
+% using exponential weighted averaging,
+
+% \begin{equation}
+%   \bar\pi_{ib}' = \bar\pi_{ib} +
+%     \frac{\mathrm{Bandit_{b}(0, 1)} - \bar\pi_{ib}}{c_{ib}'},
+% \end{equation}
+% where 
+% $\mathrm{Bandit}_{b}(0, 1)$
+% is 0 or 1 depending on the result of the bandit draw for behavior $b$.
+
+% \subsubsection{Inter-generational inheritance and social learning}
+
+% Every $M$ time steps, agents from the current generation reproduce, teach,
+% and die, while the next generation to perform the next $M$ time steps learns
+% from one teacher from the previous generation if they inherited the social 
+% learner trait. Inter-generational dynamics thus depend on 
+% two payoff-biased selection mechanisms: reproducer selection
+% and teacher selection.
+
+% $N$ reproducers are sampled from the population with
+% replacement weighted by net payoffs, i.e., at each of $N$ draws for a parent,
+% \begin{equation}
+%   \Pr(\text{Agent $i$ chosen for reproduction}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
+% \end{equation}
+% \noindent
+% We sample with replacement to allow for more successful agents to have multiple
+% offspring. Child agents inherit their parents' social learning trait, so 
+% all social learner parents spawn social learner offspring, and parents lacking
+% the trait spawn offspring lacking the trait.
+
+% Child agents with the social learning trait then must select and learn from a
+% teacher from their parent's generation, including possibly their parent.
+% Child agents give no preference to whether potential teachers are social 
+% learners. A child selects a teacher by first selecting a pool of $N_T = 5$ potential
+% teachers. Among this pool, each child selects the teacher with the greatest
+% net payoffs. In case of a tie the teacher is chosen at random from those with
+% the shared maximum net payoff.
+
+% Social learner child agents each acquire their teacher's ledger, and all social
+% learner children behavior counts are reset to 1 to limit ledger values to be between
+% 0 and 1. Child agents without the social learner trait have all ledger and behavior
+% count values re-initialized to 0. At this point the re-initialized child agents
+% engage in behavior selection and payoff accumulation described above.
+
+% \subsection{Computational analyses}
+
+% We manipulated environmental uncertainty parameters described above, $u$,
+% $\pisub{low}$, $B$, and $M$, to examine their effects on our
+% main outcome measure, the prevalence of social learning $s$. For each parameter setting
+% in our analysis we calculated the average value of $s$ at the final time step
+% of $T=1000$ across 100 runs for each combination of uncertainty parameter values.
+
+% To analyze the effect of various forms of uncertainty on social learning 
+% prevalence in our Analysis, we initialized several model runs with
+% different uncertainty parameters $u$, $\pisub{\mathrm{low}}$, $B$,
+% and $M$. We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$ for each combination of
+% the following parameters:
+% $\pisub{low} \in \{0.1, 0.5, 0.8\}$, $B \in \{2, 4, 10\}$, $M \in \{B/2, B, 2B\}$.
+
+% \subsubsection{Outcome variables}
+
+% Our primary outcome variable is the mean prevalence of the social learning
+% trait over $N=100$ agents over 1000 trials at the final time step of each trial,
+% denoted $\meansl$.
+% Typically at the final time step all agents either have the social learning
+% trait or do not (see Supplement for a presentation of time series collections
+% and histograms of outcomes for
+% a representative sampling of variables \mt{TODO}).
+
+% \begin{table}[h]
+%     \caption{Global environmental and cognitive initialization parameters.}
+%     \label{tab:modelParameters}
+%     \centering \hspace{-3em}
+%     \begin{tabular}{cp{4.0in}l} \toprule
+
+%         Symbol & Description & Values \\
+
+%         \midrule
+
+%         $\meansl$ & Mean social learning prevalence over agents and trials
+%                   & $\in [0.0, 1.0]$ \\
+
+%         $p_{\text{opt}}$ & Fraction of population performing optimal behavior
+%                          & $\in [0.0, 1.0]$ \\
+
+%         \texttt{count}$(b_i)$ & Number of agents performing behavior $b$ 
+%                               & Behavior-count key-value pairs\\
+%         \bottomrule
+%     \end{tabular}
+% \end{table}
+
+% \section{Analysis}
+
+% We analyzed the outcomes of model runs across systematically varied uncertainty
+% parameters over 1000 trials for each parameter setting. 
+% We observed complex outcomes where the effects of uncertainty parameters
+% were highly dependent on one another as measured by the mean prevalence of
+% social learning, $\meansl$, across trials for each parameter setting. 
+% The prevalence of social learning
+% generally decreased with environmental variability, $u$, as expected from standard
+% models of social learning evolution. However, the shape of the decrease was not
+% uniform (Figure~\ref{fig:evolutionOfSL}). 
+% We observed that social learning did in fact enable populations to 
+% do better than individual learners, but only when (multi-dimensional) uncertainty 
+% were sufficiently limited (Figure~\ref{fig:meanNetPayoffs}).
+
+% \subsection{Evolution of social learning under uncertainty}
+% The shape of the decrease from all agents
+% always becoming social learners ($\meansl = 1.0$) to 
+% all agents always becoming individual learners ($\meansl = 0.0$)
+% is heterogeneous. We identified patterns in this heterogeneity that inform our
+% understanding of when and how social learning is advantageous, and when 
+% and why individual learning is advantageous. 
+% Changes in the uncertainty parameters ($\pilow$, $B$, $L$) 
+% result in the following changes in the shape of the transition from $\meansl = 1.0$ 
+% to $\meansl = 0.0$: (1) the transition
+% occurs at different critical values of $u$; and (2) the transition occurs
+% with greater or lesser rapidity over $u$. 
+% For instance, when $B=2$, $\pilow = 0.1$, and $L=8$, $\meansl$ goes from 1 to 
+% 0 starting at $u=0.1$ and reaches 0 at $u=0.3$ (Figure~\ref{fig:evolutionOfSL},
+% top left). When we increased $B=4$ (Figure~\ref{fig:evolutionOfSL}, top center), the
+% transition from $\meansl = 1$ to 0 begins at $u=0.3$. When $B=4$, $\pilow=0.1$,
+% and $L=1$ the transition from $\meansl=1$ to 0 begins at $u=0.3$ but does not
+% reach 0 until $u \approx 0.9$ (again Figure~\ref{fig:evolutionOfSL}, top center).
+
+% We can draw some conclusions about the evolution of social learning by analyzing the
+% location and shape of the suppression of social learning as $u$ was increased.
+% First, let us observe some general trends. Increased $\pilow$ generally
+% flattened the suppression of social learning as $u$ increased.  
+% Increased $B$ tended to increase the critical value of $u$ at which the 
+% system transitions from favoring social learning to favor individual learning.  
+% Increased $L$ generally sharpened the suppression of social learning.
+% Within each of these broad trends over the uncertainty parameters are several
+% details that depend on context as defined by the values of the other uncertainty
+% parameters.
+
+% When $\pilow$ was increased, the suppression of social learning was, in
+% general, less rapid as $u$ increased. This effect is particularly acute when
+% $\pilow = 0.8$, which is very nearly equal to the expected value of the optimal
+% payoff, $\pihigh = 0.9$. When $\pilow = 0.8$ $\meansl$ never actually reaches 
+% 1 or 0 for any parameter settings. The suppression of social learning in this
+% case is approximately linear, if there is selection at all. When $\pilow = 0.8$
+% and $L = 1$ there is little to no selection across $B$, 
+% so populations evolve randomly towards $\meansl = 1$ or $\meansl = 0$.
+
+% Increased $B$ generally led to increased critical $u$ at which social learning
+% starts to be suppresed. When payoffs are not ambiguous ($\pilow = 0.1$), the the
+% suppression of social learning starts at $u \approx 0.1$ for $B=2$; at $u \approx
+% 0.3$ when $B=4$; and at $u \approx 0.5$ when $B=10$.  When payoffs are more
+% ambiguous ($\pilow = 0.45,0.8$), increased $B$ also led to a flattening of the
+% suppression of social learning when $L=1$.
+
+% The general effect of $L$ is to increase the rapidity of the suppression of social
+% learning via the strengthening of selection pressure since longer-lived agents
+% build up stronger priors over their lifetimes. If it is advantageous to
+% learn socially, this will be reliably detected. Inversely, decreased $L$
+% can weaken selection pressure since agents cannot amass useful information when
+% $L$ is small. This is most extreme when $\pilow = 0.8$ and there is little to
+% no selection for or against social learning when $L=1$. However, decreased $L$ can
+% also delay the suppression of social learning as $u$ increases, since social
+% learning provdes agents with the possibility of learning what the optimal behavior
+% might be.  Even when $u$ was large, agents with a lifespan of 1 more often evolved
+% to be social learners because social learning was to be preferred over random
+% chance.
+
+% \subsection{Social learning capacity increases payoffs}
+
+% For social learning to evolve, it must improve upon individual learning. 
+% We found that different parameter settings indeed change how advantageous social learning
+% is compared to individual learning (Figure~\ref{fig:meanNetPayoffs}). 
+% To analyze the effect of uncertainty on
+% payoffs, it is useful to identify some constant reference values which we will
+% use to evaluate the benefit of social learning. First, the optimal expected payoff
+% is the optimal behavior payoff times the lifespan, which we can denote
+% $\langle \pi^*(L) \rangle = L\cdot\pihigh$. The expected base payoff by chance is 
+% $\langle \pi_{\text{base}} \rangle = L \left[ (B - 1) \pilow + \pihigh \right]$, which
+% an agent would receive on average from performing purely random behaviors. 
+% Most importantly for understanding the benefit and evolution of social learning,
+% we calculated by simulation the expected payoff to individual learners for
+% each triplet ($\pilow$, $B$, $L$), which we denote $\langle \pi_I \rangle$
+% and plot for reference in Figure~\ref{fig:meanNetPayoffs}. Note $\langle \pi_I
+% \rangle$ is insensitive to $u$, which only affects the benefit of social
+% learning.
+
+% We observe across parameter settings that social learning outperforms
+% individual learning when $u$ is small. In fact, when $u=0.0$, social learning 
+% enables each new generation to know the optimal behavior and achieve the maximum
+% expected payoff for their lifespan, $\langle \pi^*(L) \rangle$. 
+% However, in some cases, even when $u$ is small, 
+% the returns on social learning are truly marginal due to 
+% relatively high, uniform expected payoffs whether or not agents identify the optimal
+% behavior, especially when $\pilow = 0.8$. In intermediate cases, examining the decay
+% of the benefit of social learning informs our understanding of social learning
+% evolution analyzed above.  As our analysis of social learning evolution suggested,
+% social learning is only beneficial up to a point. When $\pilow=0.1$, increasing $B$
+% led both to larger differences between
+
+% \subsection{Evolutionary outcomes vary in their certainty}
+
+% Finally, we found that the \emph{evolutionary uncertainty} of the system increases
+% around the values of $u$ where $\meansl$ goes from 1 to 0. 
+% In one sense
+% To confirm and expand our analysis of this uncertainty, we 
+% also measured environmental uncertainty in terms of the
+% expected number of time steps to convergence, $\langle T \rangle$. Evolutionary
+% uncertainty is an outcome measure---an emergent form of uncertainty due to
+% weak selection pressures. When 
+% $\meansl \approx 0.5$ this means that approximately equal numbers of trials
+% ended with all agents as social learners as they ended with all agents 
+% individual learners. We found that increased $\pilow$
+% tended to increase the overall uncertainty in terms of $\langle T \rangle$.
+% Increasing $B$ also increased the $u$ at which $\langle T \rangle$ peaked.
+% This indicates the evolutionary system is significantly less certain of 
+% which behavior is optimal around critical uncertainty parameter ensembles.
+
+% \mt{interpret this further}
+
+% \include{mainResultsPlots.tex}
+
+% \include{meanNetPayoffs.tex}
+
+% \include{stepResultsPlots.tex}
+
+% \section{Discussion}
 

### 2022-05-12 ms.tex
Updates from Overleaf

--- 2022-05-05 ms.tex
@@
 \usepackage{float}
-% \usepackage[margin=0.50in]{geometry}
 \usepackage[margin=1.00in]{geometry}
+% \usepackage[margin=0.90in]{geometry}
 
@@
 
-\title{Uncertainty in the evolution of social learning}
+\title{Some forms of uncertainty may suppress the evolution of social learning}
 
@@
 \section{Introduction}
+
+\subsection{The history of "copy when uncertain"}
+It has become a near truism that "theory predicts that it is adaptive to learn when uncertain." This claim has been motivated by empirical work (such as Asch conformism studies) & theoretical models (Boyd Richerson 85, 88) that often do not mention the word uncertainty at all.
+However, they do show related effects of social learning increasing when individual learning is difficult (i.e., ambiguous lines in Asch), and intermediate levels of temporal uncertainty favoring social learning (i.e., too stable and you get genetic canalization of a trait, too much temporal variation and there's selection for individual learning to ensure the most up to date information).
+
+{Galef 2009} https://www.sciencedirect.com/science/article/pii/S006534540939004X#bb0059
+cites {B & R 85/88 & Laland 2004} https://link.springer.com/content/pdf/10.3758/BF03196002.pdf
+Laland 2004 cites {B& R 88} https://books.google.com/books?hl=en&lr=&id=mqFcAgAAQBAJ&oi=fnd&pg=PA29&dq=Boyd+and+Richerson%E2%80%99s+(1988&ots=IfIbB_kx_a&sig=g8CYH5bVfwfXhTRGot0q761f9mw#v=onepage&q&f=false
+
+Other examples of empirical work: https://www.sciencedirect.com/science/article/pii/S0022096516300625
+
+Henrich & Boyd 88 do have something like B that is the difficulty of getting right answer (or rho probability of doing so)
+https://www.sciencedirect.com/science/article/pii/S109051389800018X#FIG5
+
+Lifespan not modelled
+
+\subsection{earlier structure}
 
@@
 \begin{enumerate}
-    \item 
-      We vary the frequency at which the optimal behavior changes, which we call
-      \emph{environmental variability}, $u$. At the start of each generation, with
-      probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all
-      other behaviors are assigned a payoff of $\pisub{low}$. Otherwise, the same
-      behavior remains optimal across generations. 
+    \item We vary the frequency at which the optimal behavior changes, which we call \emph{environmental variability}, $u$.
+At the start of each generation, with probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all other behaviors are assigned a payoff of $\pisub{low}$.
+Otherwise, the same behavior remains optimal across generations.
     \item We vary the latent expected payoffs yielded by the bandits. For simplicity,
@@
   have elapsed. Agents are initialized as ``blank slates''.}
-  \label{fig:IntraInterGenerationalDynamics}
   \centering
     \includegraphics[width=0.9\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+  \label{fig:IntraInterGenerationalDynamics}
 \end{figure}
@@
 
-We analyzed the outcomes of model runs across systematically varied uncertainty
-parameters over 1000 trials for each parameter setting. 
-We observed complex outcomes where the effects of uncertainty parameters
-were highly dependent on one another as measured by the mean prevalence of
-social learning, $\meansl$, across trials for each parameter setting. 
-The prevalence of social learning
-generally decreased with environmental variability, $u$, as expected from standard
-models of social learning evolution. However, the shape of the decrease was not
-uniform (Figure~\ref{fig:evolutionOfSL}). 
-We observed that social learning did in fact enable populations to 
-do better than individual learners, but only when (multi-dimensional) uncertainty 
-were sufficiently limited (Figure~\ref{fig:meanNetPayoffs}).
+% \begin{itemize}
+%   \item 
+%     To understand how different forms of uncertainty affect social learning evolution
+%     we systematically varied environmental variables in our model and observed
+%     corresponding changes in mean social learning prevalence, $\meansl$. We
+%     confirmed that, in many cases, increased environmental variability $u$ 
+%     suppresses social learning. However\ldots
 
-\subsection{Evolution of social learning under uncertainty}
-The shape of the decrease from all agents
-always becoming social learners ($\meansl = 1.0$) to 
-all agents always becoming individual learners ($\meansl = 0.0$)
-is heterogeneous. We identified patterns in this heterogeneity that inform our
-understanding of when and how social learning is advantageous, and when 
-and why individual learning is advantageous. 
-Changes in the uncertainty parameters ($\pilow$, $B$, $L$) 
-result in the following changes in the shape of the transition from $\meansl = 1.0$ 
-to $\meansl = 0.0$: (1) the transition
-occurs at different critical values of $u$; and (2) the transition occurs
-with greater or lesser rapidity over $u$. 
-For instance, when $B=2$, $\pilow = 0.1$, and $L=8$, $\meansl$ goes from 1 to 
-0 starting at $u=0.1$ and reaches 0 at $u=0.3$ (Figure~\ref{fig:evolutionOfSL},
-top left). When we increased $B=4$ (Figure~\ref{fig:evolutionOfSL}, top center), the
-transition from $\meansl = 1$ to 0 begins at $u=0.3$. When $B=4$, $\pilow=0.1$,
-and $L=1$ the transition from $\meansl=1$ to 0 begins at $u=0.3$ but does not
-reach 0 until $u \approx 0.9$ (again Figure~\ref{fig:evolutionOfSL}, top center).
+%   \item 
+%     Our analysis confirmed existing theoretical predictions that social learning
+%     is valuable only when environments are sufficiently stable, i.e., 
+%     environmental variability $u$ is sufficiently small.
+%     Because of the central role of $u$, it is set on the x-axis in
+%     all analysis plots shown in Figure~\ref{fig:results}. 
+%     The threshold over $u$ at which social learning begins to decline
+%     varies depending on the value of other environmental parameters.
 
-We can draw some conclusions about the evolution of social learning by analyzing the
-location and shape of the suppression of social learning as $u$ was increased.
-First, let us observe some general trends. Increased $\pilow$ generally
-flattened the suppression of social learning as $u$ increased.  
-Increased $B$ tended to increase the critical value of $u$ at which the 
-system transitions from favoring social learning to favor individual learning.  
-Increased $L$ generally sharpened the suppression of social learning.
-Within each of these broad trends over the uncertainty parameters are several
-details that depend on context as defined by the values of the other uncertainty
-parameters.
+%   \item 
+%     However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
+%     third column respectively in Figure~\ref{fig:results}) can lead
+%     social learning to be selected for even for large values of $u$, possibly
+%     due to the low risk and potentially high reward of learning an accurate
+%     tally of mean payoffs from the previous generation. 
+%     Since there are many behaviors and
+%     few observations, softmax weighting will not significantly 
+%     favor a sub-optimal behavior. However, if one does learn an accurate tally
+%     then one does have an increased chance of performing the best one.
 
-When $\pilow$ was increased, the suppression of social learning was, in
-general, less rapid as $u$ increased. This effect is particularly acute when
-$\pilow = 0.8$, which is very nearly equal to the expected value of the optimal
-payoff, $\pihigh = 0.9$. When $\pilow = 0.8$ $\meansl$ never actually reaches 
-1 or 0 for any parameter settings. The suppression of social learning in this
-case is approximately linear, if there is selection at all. When $\pilow = 0.8$
-and $L = 1$ there is little to no selection across $B$, 
-so populations evolve randomly towards $\meansl = 1$ or $\meansl = 0$.
+%   \item 
+%     $\pilow$ can alter selection selection pressure for or
+%     against social learning, depending on the number of time steps per generation.
+%     For instance, when $B=2$, increasing $\pilow$ (i.e. increased uncertainty
+%     about which behavior is optimal) leads at first to less sharp sigmoid curve, 
+%     where social learning is less prevalent with increased $\pilow$ when
+%     $u < 0.5$ and social learning is more prevalent with increased $\pilow$
+%     when $u > 0.5$. When $\pilow = 0.8$ noise and genetic drift dominate across
+%     tested values of $B$, with possibly a slight inverse correlation 
+%     in social learning as $u$ increases. When $B \in \{4,10\}$, increasing
+%     $\pilow \in \{0.1, 0.5\}$ leads uniformly to increased $\meansl$ over 
+%     $u$ in those settings.
 
-Increased $B$ generally led to increased critical $u$ at which social learning
-starts to be suppresed. When payoffs are not ambiguous ($\pilow = 0.1$), the the
-suppression of social learning starts at $u \approx 0.1$ for $B=2$; at $u \approx
-0.3$ when $B=4$; and at $u \approx 0.5$ when $B=10$.  When payoffs are more
-ambiguous ($\pilow = 0.45,0.8$), increased $B$ also led to a flattening of the
-suppression of social learning when $L=1$.
+%   \item
+%     If $M/B$ has an effect it is mostly to 
+%     increase reliance on social learning due to social information being of 
+%     higher quality since teachers would have had more learning opportunities
+%     for larger $M$. (THERE ARE CASES WHERE THIS IS NOT THE CASE BUT THERE IS 
+%     STILL TOO MUCH NOISE DUE TO SMALL NTRIALS)
 
-The general effect of $L$ is to increase the rapidity of the suppression of social
-learning via the strengthening of selection pressure since longer-lived agents
-build up stronger priors over their lifetimes. If it is advantageous to
-learn socially, this will be reliably detected. Inversely, decreased $L$
-can weaken selection pressure since agents cannot amass useful information when
-$L$ is small. This is most extreme when $\pilow = 0.8$ and there is little to
-no selection for or against social learning when $L=1$. However, decreased $L$ can
-also delay the suppression of social learning as $u$ increases, since social
-learning provdes agents with the possibility of learning what the optimal behavior
-might be.  Even when $u$ was large, agents with a lifespan of 1 more often evolved
-to be social learners because social learning was to be preferred over random
-chance.
+%   \item
+%     Synthesis/analysis conclusion
 
-\subsection{Social learning capacity increases payoffs}
-
-For social learning to evolve, it must improve upon individual learning. 
-We found that different parameter settings indeed change how advantageous social learning
-is compared to individual learning (Figure~\ref{fig:meanNetPayoffs}). 
-To analyze the effect of uncertainty on
-payoffs, it is useful to identify some constant reference values which we will
-use to evaluate the benefit of social learning. First, the optimal expected payoff
-is the optimal behavior payoff times the lifespan, which we can denote
-$\langle \pi^*(L) \rangle = L\cdot\pihigh$. The expected base payoff by chance is 
-$\langle \pi_{\text{base}} \rangle = L \left[ (B - 1) \pilow + \pihigh \right]$, which
-an agent would receive on average from performing purely random behaviors. 
-Most importantly for understanding the benefit and evolution of social learning,
-we calculated by simulation the expected payoff to individual learners for
-each triplet ($\pilow$, $B$, $L$), which we denote $\langle \pi_I \rangle$
-and plot for reference in Figure~\ref{fig:meanNetPayoffs}. Note $\langle \pi_I
-\rangle$ is insensitive to $u$, which only affects the benefit of social
-learning.
-
-We observe across parameter settings that social learning outperforms
-individual learning when $u$ is small. In fact, when $u=0.0$, social learning 
-enables each new generation to know the optimal behavior and achieve the maximum
-expected payoff for their lifespan, $\langle \pi^*(L) \rangle$. 
-However, in some cases, even when $u$ is small, 
-the returns on social learning are truly marginal due to 
-relatively high, uniform expected payoffs whether or not agents identify the optimal
-behavior, especially when $\pilow = 0.8$. In intermediate cases, examining the decay
-of the benefit of social learning informs our understanding of social learning
-evolution analyzed above.  As our analysis of social learning evolution suggested,
-social learning is only beneficial up to a point. When $\pilow=0.1$, increasing $B$
-led both to larger differences between
-
-\subsection{Evolutionary outcomes vary in their certainty}
-
-Finally, we found that the \emph{evolutionary uncertainty} of the system increases
-around the values of $u$ where $\meansl$ goes from 1 to 0. 
-In one sense
-To confirm and expand our analysis of this uncertainty, we 
-also measured environmental uncertainty in terms of the
-expected number of time steps to convergence, $\langle T \rangle$. Evolutionary
-uncertainty is an outcome measure---an emergent form of uncertainty due to
-weak selection pressures. When 
-$\meansl \approx 0.5$ this means that approximately equal numbers of trials
-ended with all agents as social learners as they ended with all agents 
-individual learners. We found that increased $\pilow$
-tended to increase the overall uncertainty in terms of $\langle T \rangle$.
-Increasing $B$ also increased the $u$ at which $\langle T \rangle$ peaked.
-This indicates the evolutionary system is significantly less certain of 
-which behavior is optimal around critical uncertainty parameter ensembles.
-
-\mt{interpret this further}
+% \end{itemize}
 
 \include{mainResultsPlots.tex}
-
-\include{meanNetPayoffs.tex}
-
-\include{stepResultsPlots.tex}
 
@@
 
+\subsection{Mean payoffs at final time step}
+
+\include{supplement/meanNetPayoffs.tex}
+
 \subsection{Convergence information}
@@
     \midrule  
-    2  & 0  & 132000 & 0.0 \% \\
-    4  & 0  & 132000 & 0.0 \% \\
-    10 & 44 & 132000 & 0.00033  \% \\
+    2  & 21  & 132000 & 0.016 \% \\
+    4  & 30  & 132000 & 0.023 \% \\
+    10 & 971 & 132000 & 0.74  \% \\
     \bottomrule

### 2022-05-12 ms.tex
merged overleaf

--- 2022-05-12 ms.tex
@@
 \section{Introduction}
+
+\subsection{The history of "copy when uncertain"}
+It has become a near truism that "theory predicts that it is adaptive to learn when uncertain."
+This claim has been motivated by empirical work (such as Asch conformism studies) \& theoretical models (Boyd Richerson 85, 88) that often do not mention the word uncertainty at all.
+However, they do show related effects of social learning increasing when individual learning is difficult (i.e., ambiguous lines in Asch), and intermediate levels of temporal uncertainty favoring social learning (i.e., too stable and you get genetic canalization of a trait, too much temporal variation and there's selection for individual learning to ensure the most up to date information).
+
+{Galef 2009} https://www.sciencedirect.com/science/article/pii/S006534540939004X\#bb0059
+cites {B \& R 85/88 \& Laland 2004} https://link.springer.com/content/pdf/10.3758/BF03196002.pdf
+Laland 2004 cites {B\& R 88}
+\url{https://books.google.com/books?hl=en&lr=&id=mqFcAgAAQBAJ&oi=fnd&pg=PA29&dq=Boyd+and+Richerson\%E2\%80\%99s+(1988&ots=IfIbB_kx_a&sig=g8CYH5bVfwfXhTRGot0q761f9mw\#v=onepage&q&f=false}
+
+Other examples of empirical work: https://www.sciencedirect.com/science/article/pii/S0022096516300625
+
+Henrich \& Boyd 88 do have something like B that is the difficulty of getting right answer (or rho probability of doing so)
+https://www.sciencedirect.com/science/article/pii/S109051389800018X\#FIG5
+
+Lifespan not modelled
+
+\subsection{earlier structure}
 

### 2022-05-17 ms.tex
updated model dynamics fig and caption

@@
 
-\title{Uncertainty in the evolution of social learning}
+\title{Uncertainty in social learning evolution}
 
@@
 \begin{figure}
-  \caption{Model dynamics are composed of two major parts: first, agents perform
-  behaviors for $L$ time steps in a single generation. Then agents reproduce
-  randomly, with more successful agents being more likely to reproduce. Newly
-  ``born'' social learner agents use success bias to select and learn from a chosen
-  teacher. Then, all agents from the previous generation die off, all new agents
-  begin a new generation, and the process continues until 1000 total time steps
-  have elapsed. Agents are initialized as ``blank slates''. \mt{Can compress this
-  into triptych. $M \rightarrow L$. Lighten grey background, remove outlines
-around most or all components. Replace text in picture with A, B, C, and 
-explain in caption.}}
+  \caption{\textbf{Model dynamics.} 
+    The first generation of agents are initialized with empty ledgers, 
+    then perform behaviors on each subsequent time step (A). At the end
+    of each generation, after all agents have performed $L$ behaviors
+    chosen using softmax selection, the intergenerational tramsission stage
+    begins (B). During this stage agents reproduce, passing on their social
+    learning trait without mutation (B1). Child agents learn from
+    the previous generation if they are social learners (B2), or are initialized
+    with blank ledgers if they are individual learners. All agents from the previous
+    generation die off, and new child agents begin within-generation dynamics anew.}
   \label{fig:IntraInterGenerationalDynamics}
-  \centering
-    \includegraphics[width=0.9\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+\hspace{-2em}
+  % \centering 
+    \includegraphics[width=1.1\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
 \end{figure}

### 2022-05-18 sci.tex
started modifying figures, reviewing existing model features in table in terms of our model factors

--- 2022-05-12 ms.tex
@@
 \usepackage{float}
+% \usepackage[margin=0.50in]{geometry}
 \usepackage[margin=1.00in]{geometry}
-% \usepackage[margin=0.90in]{geometry}
 
-\usepackage{caption}
 \usepackage{booktabs}
@@
 \usepackage{apacite}
+\usepackage{caption}
 \usepackage{subcaption}
@@
 
-\title{Some forms of uncertainty may suppress the evolution of social learning}
+\title{Uncertainty in social learning evolution}
 
@@
 \newcommand{\pihigh}{\pisub{high}}
+\newcommand{\piI}{\langle \pisub{I} \rangle}
+\newcommand{\piS}{\langle \pisub{S} \rangle}
 
-\newcommand{\meansl}{\langle s \rangle}
+\newcommand{\meanvar}[1]{\langle #1 \rangle}
+\newcommand{\meansl}{\meanvar{s}}
+\newcommand{\meanpi}{\meanvar{\pi}}
+\newcommand{\meansoc}{\meanvar{\pi_\mathrm{S}}}
+\newcommand{\meanasoc}{\meanvar{\pi_\mathrm{A}}}
+\newcommand{\meanT}{\meanvar{T}}
 
@@
 Social learning is essential to survival. It is likely to evolve when it is more
-efficient than asocial, trial-and-error learning. The consensus in cultural
-evolutionary theory holds that some amount of environmental variability and
-uncertainty about the best decisions are necessary for social learning to evolve.
-However, current models for the evolution of social learning tend to conflate forms
-of uncertainty, and rarely consider different ones in tandem. Moreover, many models
-are limited by considering only two possible behaviors and environmental states.
-Here we use evolutionary agent-based modeling to improve on these shortcomings. We
-model a time-varying environment with dozens of possible behaviors performed by
-agents engaging in individual and social learning. We show that ambiguous payoffs,
-larger possible decision sets, and shorter agent lifespans sometimes increase social
-learning prevalence, as expected. However, we also find that, under some conditions,
-these forms of uncertainty can select against social learning.
+efficient than asocial, trial-and-error learning. Theoretically, some uncertainty is
+necessary for social learning to be necessary, however too much uncertainty makes
+social information useless as information becomes outdated. This fact is empirically
+supported across biology and human sciences. However, we lack a theoretical
+framework predict the effects of specific classes and types of uncertainty on social
+learning. Furthermore, existing models and experimental operationalizations of
+uncertainty are ambiguously related, and models of uncertainty and social learning
+tend to only consider a small number of sources of uncertainty and behavioral
+choices.  Here we use evolutionary agent-based modeling to improve on these
+shortcomings. We model a time-varying environment with a varying number
+of possible behaviors agents could perform to acquire payoffs.
+We show that ambiguous payoffs, larger possible decision sets, and shorter agent
+lifespans interact to affect social learning in complex ways that make evolutionary
+selection more or less certain about the optimal strategy. Our work consolidates
+models of uncertainty and social learning and models the evolution of social
+learning that could be used to guide human, non-human, and artificial life
+towards optimal responses to existential threats and new opportunities.
 \end{abstract}
 
-\section{Introduction}
-
-\subsection{The history of "copy when uncertain"}
-It has become a near truism that "theory predicts that it is adaptive to learn when uncertain." This claim has been motivated by empirical work (such as Asch conformism studies) & theoretical models (Boyd Richerson 85, 88) that often do not mention the word uncertainty at all.
-However, they do show related effects of social learning increasing when individual learning is difficult (i.e., ambiguous lines in Asch), and intermediate levels of temporal uncertainty favoring social learning (i.e., too stable and you get genetic canalization of a trait, too much temporal variation and there's selection for individual learning to ensure the most up to date information).
-
-{Galef 2009} https://www.sciencedirect.com/science/article/pii/S006534540939004X#bb0059
-cites {B & R 85/88 & Laland 2004} https://link.springer.com/content/pdf/10.3758/BF03196002.pdf
-Laland 2004 cites {B& R 88} https://books.google.com/books?hl=en&lr=&id=mqFcAgAAQBAJ&oi=fnd&pg=PA29&dq=Boyd+and+Richerson%E2%80%99s+(1988&ots=IfIbB_kx_a&sig=g8CYH5bVfwfXhTRGot0q761f9mw#v=onepage&q&f=false
-
-Other examples of empirical work: https://www.sciencedirect.com/science/article/pii/S0022096516300625
-
-Henrich & Boyd 88 do have something like B that is the difficulty of getting right answer (or rho probability of doing so)
-https://www.sciencedirect.com/science/article/pii/S109051389800018X#FIG5
-
-Lifespan not modelled
-
-\subsection{earlier structure}
-
 Social learning is essential to human and other species' everyday life and survival.
-It allows individuals to solve problems when acquiring information from others is more efficient than learning
-on one's own~\cite{Laland2004}. Theory predicts that social
-learning should be favored in contexts with greater
-uncertainty~\cite{BoydRicherson1985,Henrich1998}, and this prediction has received some empirical support~\cite{McElreath2005,Kendal2018}. 
-However, the meaning of the term ``uncertainty'' is not always clear, and often conflates environmental variability, spatial heterogeneity, and ambiguity or uncertainty about payoff structure. 
-Moreover, most models of the evolution of social learning ``blackbox'' key 
-cognitive learning processes that underlie it~\cite{Heyes2016}.
-
-In this paper we use agent-based modeling to compare the effect of
-different sources of uncertainty on social learning
-by ``unblackboxing'' typically abstracted-out model components 
-of environmental variability, payoff structures and
-agent life histories, and  learning mechanisms. ``Uncertainty''  
-means variability where the probabilistic structure is unknown. %cannot be learned.
-Uncertainty increases when payoffs are more similar across behaviors, when
-environmental variability increases, when the number of possible behaviors
-increases, and when lifespan decreases.  In this paper we show that more ambiguous
-payoff structures and shorter lifespans sometimes do lead to greater reliance on
-social learning---however, we also identify and explain cases where greater
-uncertainty leads to less social learning due to the possibility that social
-information is misleading.  We thus conclude that many predictions made by previous
-models of the evolution of social learning are likely overgeneralized.
-%~\cite{Yarkoni2021}.
-
-\subsection{Social Learning}
-
-Social learning, as we consider it here, occurs whenever an individual acquires a behavior by observing another individual.
-This need not require explicit instruction, and is, in fact, widespread across a broad range of nonhuman
-taxa~\cite{Kendal2018,Allen2019}. Importantly, social information can be inherited both
-from parents --- i.e., via \emph{vertical transmission} like genetic information --- and
-from others in the same generation --- i.e., via \emph{horizontal transmission}
-\cite{CavalliFeldman1981}. The joint action of vertical and horizontal transmission
-gives rise to qualitatively different evolutionary dynamics. For example,
-inter-generational environmental change will affect the adaptive value of genetic
-information and vertically-transmitted cultural information more than information
-that is horizontally transmitted. We include both horizontal and vertical transmission pathways in our
-model. For simplicity, we ignore oblique transmission in which non-parental members
-of the previous generation are observed.
-
-Environmental variability has been seen as a key selective force in shaping social learning starting with the first formal models of cultural evolution~\cite{CavalliFeldman1981,BoydRicherson1985}.
-Totally stable environments will not favor learning mechanisms because information can become genetically hardwired, while  extreme environmental instability will degrade the value
-of social learning as information becomes rapidly outdated~\cite{Feldman1996}.
-This suggests that an intermediate degree of environmental predictability will favor social learning.
-Strategies can also evolve to mitigate the risks of relying on outdated social information by weighing more heavily information from others who more recently acquired it~\cite{Rendell2010}.
-
-Uncertainty has also been modelled as arising from other aspects of the environment. 
-For example, \citeA{Perreault2012} vary the ambiguity of the environmental cue individuals get through individual learning about the state of the world.
-Perhaps not surprisingly, the more ambiguous the asocial information, the greater the selection for weighing social information heavily.
-Alternatively, uncertainty about the optimal behavior has been modelled by increasing the number of cultural traits to choose from.
-
-Empirical research supports some of these theoretical predictions.
-Organisms flexibly use social learning as a function of the ambiguity of the environmental cue and of other environmental features that are often subsumed under the rubric of ``uncertainty.''
-While some studies explicitly impose a cost whenever participants use asocial
-information \cite{Morgan2012,Atkisson2012}, 
-others allow the costs of each strategy to emerge as a function of task structure and assess its consequences for learning strategies. 
-For example, when participants received equivocal private information about the best investment to make in a lab game,
-they were more likely to rely on social information to make their choice~\cite{Toelch2013}. 
-\citeA{McElreath2005} developed a similar experiment where participants ``pulled'' virtual slot machine arms (often called ``bandits''), each yielding stochastic payoffs.
-Participants relied more on social learning when the bandits had higher-variance payoffs, and when the highest-paying bandit changed more frequently.
-The number of options to choose between can also increase uncertainty about the optimal choice, and has been shown to increase participants' reliance on social learning \cite{Muthukrishna2016a}.
-
-Thus existing theoretical work and the empirical evidence seem to support that various forms of uncertainty favor the evolution of social learning.
-However, uncertain outcomes are operationalized in different ways across models, and any given model tends to focus on only one or two forms of uncertainty at a time.
-Our agent-based modeling approach enables us to explicitly specify different forms of uncertainty independently in order to understand which of these environmental factors particularly favor the evolution of social learning.
-Simultaneous modelling also allows us to examine their interaction.
-We first attempt conceptual replications of previous models' findings, and then examine where they diverge.
-
-\subsection{Research overview}
-
-Computational agents in our model face a problem: every time step they perform
-one of several behaviors, with each behavior represented by a ``bandit'' that
-pays off 1 or 0 with some probability. One of these behaviors (the optimal
-behavior) pays off with a higher probability than all the others.
-Agents decide which behavior to 
-perform based either on a success-biased observation 
-of a peer's behavior (social learning) or based on their own observations (asocial learning).
-Agents then update their memory of expected payoffs for each behavior 
-when they receive a payoff from their chosen
-action. Within this framework we have four mechanisms by which we operationalize 
-and vary uncertainty:
-(1) the expected payoffs of the optimal behavior and all the rest---when payoffs
-are nearly identical, uncertainty in the form of ambiguity increases; (2) the
-environmental variability, i.e., the probability that the optimal behavior 
-changes between generations; (3) the number of possible behaviors the environment allows---which
-behavior is optimal is more uncertain when there are more possibilities; and (4)
- agent lifespan---agents experience fewer learning opportunities and die more uncertain about which behavior
-is optimal when their lifespan is shorter.
-
-The primary outcome measure of our
-model is the average difference between the frequency of (horizontal) 
-social learning and the frequency of asocial
-learning across all agents. If social learning is more prevalent than asocial
-learning this suggests that the optimal behavior is more likely found
-by copying peers than by trial-and-error search.
-Conversely, when asocial learning is more prevalent, this suggests social information
-is likely to be misleading. 
-When social and asocial learning are 
-equally prevalent this means there is no discernible advantage to either, i.e.,
-the agents have weak priors on which channel provides more reliable information. 
-Each agent has its own social learning frequency that it inherits from its
-parent (haploid reproduction) with mutation, so evolution selects for,
-or computes~\cite{Smaldino2013}, the optimal
-social learning frequency.
-
-Using our model we found that increased uncertainty sometimes
-led to increased reliance on social learning, as expected from prior literature. However, we also find cases where increased uncertainty decreased agents' reliance on social learning
-due to increased uncertainty that made social information less reliable, thereby
-increasing reliance on asocial learning.
-
-\section{Model}
-
-We developed an agent-based model of a society of $N$ individuals who each must decide
-which of $B$ behaviors to perform at each time step. Each behavior is a ``bandit'',
-a common modelling and experimental approach for representing behaviors with
-probabilistic payoffs~\cite{SuttonBartoBook, McElreath2005,Rendell2010,Schulz2019}. %Bandits are like  slot machines in a casino~\ref{fig:behaviorSelection}.
-Each behavior $b$ yields a payoff of 1 with probability $\pi_b$ and a payoff of zero
-otherwise; $\pi_b$ is therefore also the expected payoff of behavior $b$. Agents must
-decide which behavior to perform at each time step. To do this, agents 
-use an explore-exploit strategy to sometimes try the most profitable behavior
-they know about, and other times try alternatives that may pay off more reliably.
-
-We operationalized uncertainty in four different ways: 
-(1) payoff ambiguity, $A_\pi$, which measures the difference
-between the optimal expected payoff behavior $\pisub{high}$ and the expected payoff
-of the other behaviors, $\pisub{low}$; 
-(2) environmental variability, $u$, the probability the optimal behavior changes from one generation to another; 
-(3) the number of possible behaviors, $B$; and 
-(4) the lifespan, or time steps per generation, $M$.
-
-We ran the simulation for $T=1000$ time steps. At
-the end of each generation agents reproduce and then die off. 
-Those selected to reproduce
-pass on their boolean social learning trait, $s$, without mutation,
-which specifes whether agents learn socially. We developed a series of
-computational analyses where we systematically vary the uncertainty
-variables and observe the average prevalence of social learning trait $s$
-across agents and trials, which is our primary outcome measure, 
-denoted $\langle s \rangle$.
-
-\subsection{Agents and their attributes}
-
-In each time step, $N$ agents---autonomous problem solvers---select 
-which behavior to perform based on their running tally of mean payoffs for 
-each available behavior. %information (Figure~\ref{fig:behaviorSelection}). 
-Agent $i$ tracks the mean payoff of each behavior $b$, denoted $\bar\pi_{ib}$, and
-a \emph{count} of how many times it has performed each behavior, denoted $c_{ib}$.
-$\bar\pi_{ib}$
-is initialized to 0 for all $b$ at model initialization for
-all agents, and after each generation for individual learner agents. Social
-learning agents' $\bar\pi_{ib}$ is initialized as that of its teacher selected
-through performance-biased oblique learning. Agent $i$'s accumulated payoffs
-from performing several behaviors over their lifetime of $M$ time steps is
-denoted $\pi_{i}$.
-
-\vspace{2em}
-
-\begin{table}[h]
-    \caption{Dynamic agent-level variables. Each has an implicit time dependence.}
-    \label{tab:modelParameters}
-    \centering \hspace{-3em}
-    \begin{tabular}{cp{4.0in}l} \toprule
-
-        Attribute & Description & Initial value \\
-
-        \midrule
-
-        $s_i$  & Social learner trait: 1 if agent $i$ is social learner; 0 otherwise & 0
-        or 1 w/ equal prob. \\
-
-        $\bar\pi_{ib}$ & ``Ledger'': mean payoffs acquired via behavior $b$ by $i$ 
-                       & $B$-vector of floating-point zeros \\
-
-        $c_{ib}$ & Count of how many times agent $i$ performed $b$ 
-              & $B$-vector of integer zeros \\
-
-        $\pi_i$ & Net payoffs accumulated by $i$ within generation
-                                & 0.0 \\
-        \bottomrule
-    \end{tabular}
-\end{table}
-
-\vspace{2em}
-
-\subsection{Modeling uncertainty}
-
-In our model uncertainty is a tunable consequence of four environmental features:
-%that structure the behavior of agents.  
-% Many factors contribute to the 
-% uncertainty involved in both social and asocial learning. 
-%We model uncertainty in four distinct ways: 
-\begin{enumerate}
-    \item We vary the frequency at which the optimal behavior changes, which we call \emph{environmental variability}, $u$.
-At the start of each generation, with probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all other behaviors are assigned a payoff of $\pisub{low}$.
-Otherwise, the same behavior remains optimal across generations.
-    \item We vary the latent expected payoffs yielded by the bandits. For simplicity,
-      we assume that in any given environmental state, there is one optimal behavior that
-      yields an expected payoff of $\pisub{high}$, while all other behaviors yield a 
-      payoff of $\pisub{low} < \pisub{high}$. As $\pilow$ increases towards 
-      $\pihigh$, uncertainty in the form of \emph{payoff ambiguity} also increases,
-      making it more difficult, and less rewarding, for agents to determine which
-      behavior is the optimal one.
-      % The difference between these quantities is the \emph{payoff ambiguity}, 
-    % \begin{equation}
-    %   A_\pi = 1 - (\pisub{high} - \pisub{low}),
-    %   \label{eq:payoffAmbiguity}
-    % \end{equation}
-    % which is maximized when the expected payoffs are close to equal and minimized
-    % when they differ greatly. For simplicity we will set $\pisub{high} = 0.9$
-    % for all analyses and vary $\pisub{low}$ in order to vary $A_\pi$.
-    \item We vary the total \emph{number of available behaviors}, $B$, which is a
-      source of uncertainty since agents are less likely to know which behavior yields high payoffs.  
-    \item Finally, we vary number of behavioral events per generation, $M$.
-This can be viewed as the \emph{effective lifespan} of an agent.
-Decreasing this lifespan effectively increases the importance of each event for acquiring payoffs.
-When lifespans are short ($M$ is small), agents experience greater uncertainty about which behavior is optimal given the fewer learning opportunities.
-\end{enumerate}
-
-\subsection{Dynamics and evolution}
-
-Model dynamics can be split into three parts: initialization,
-\emph{intra}generational behavior and payoff accumulation, and
-\emph{inter}generational transmission of the social learning trait and oblique
-learning (Figure~\ref{fig:IntraInterGenerationalDynamics}). 
-The model runs that we analyze here were initialized with $N=100$ agents
-to randomly have the social learner trait or not, with no accumulated payoffs, and
-blank ``ledgers''. At each time step, agents select one of $B$ possible behaviors
-to perform, accumulating a payoff of 1 if the bandit pays off, and 0 if it does
-not---a bandit pays off with probability $\pihigh$ if it is the unique optimal
-behavior, or with probability $\pilow$ if it is one of $B-1$ non-optimal
-behaviors. Agents accumulate payoffs in this way for $M$ time steps in each
-generation. At the end of each generation, $N=100$ agents are randomly selected with
-replacement to reproduce (asexual, haploid reproduction), 
-weighted by their net payoffs over the generation,
-i.e., \emph{performance-biased} reproduction. Child agents then learn from 
-one teacher, selected again via a form of performance bias: a child agent chooses
-its teacher by first selecting a fully random subset of agents from the 
-parent generation as potential teachers, then selecting the one with the 
-greatest net payoffs among the subset. This process continues until $T=1000$
-time steps have elapsed \mt{this should probably be changed depending on $M$ so that
-    all analyses use the same number of generations. my informal checks have shown quick
-convergence, but i haven't tested b=4 and b=10 as much.}.
-
-\begin{figure}
-  \caption{Model dynamics are composed of two major parts: first, agents perform
-  behaviors for $M$ time steps in a single generation. Then agents reproduce
-  randomly, with more successful agents being more likely to reproduce. Newly
-  ``born'' social learner agents use success bias to select and learn from a chosen
-  teacher. Then, all agents from the previous generation die off, all new agents
-  begin a new generation, and the process continues until 1000 total time steps
-  have elapsed. Agents are initialized as ``blank slates''.}
-  \centering
-    \includegraphics[width=0.9\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
-  \label{fig:IntraInterGenerationalDynamics}
-\end{figure}
-
-\subsubsection{Initialization}
-
-Model initialization includes agent and environment initializations. Agents are
-randomly initialized to have the social learning trait or not, with equal 
-probability. Agent ``ledgers'' and behavior counts 
-are uniformly initialized to the no-knowledge,
-blank-slate case where all $\pi_{ib} = 0$ and $c_{ib} = 0$. Both the 
-ledger and behavior count vectors have $B$ entries, one for each
-behavior the environment affords. Net payoffs for
-the generation are also initialized to zero. All agents are initialized with
-the same softmax temperature, $\tau$, that guides their behavior selection 
-to be either more exploratory (greater $\tau$) or more exploitative of
-what agents believe to be the optimal behavior(s) (lesser $\tau$).
-
-The environment is initialized to have $B$ behaviors with one of them selected
-at random to be the optimal behavior, denoted $b^*$. Behavior $b^*$ is 
-initialized to have a probability $\pihigh$ of paying off 1. All other behaviors
-are initialized to have probability $\pilow$ of paying off 1. The modeler must
-specify the environmental variability, $u$, and the number of time steps per 
-generation, $M$.
-
-\vspace{2em}
-\begin{table}[h]
-    \caption{Global environmental and cognitive initialization parameters.}
-    \label{tab:modelParameters}
-    \centering \hspace{-3em}
-    \begin{tabular}{cp{4.0in}l} \toprule
-
-        Symbol & Description & Values tested (bold$=$default) \\
-
-        \midrule
-
-        $B$       & Number of possible behaviors (represented by ``bandits'') 
-                  & 2, 4, 10 \\
-
-        $\pihigh$ & Probability that the unique optimal behavior pays off 1 
-                & \textbf{0.9} \\
-
-        $\pilow$ & Probability one of $B - 1$ non-optimal behaviors pays off 1 
-                 & 0.1, 0.45, 0.8 \\
-
-        $\tau$ & Softmax temp.; $\uparrow=$more exploration, $\downarrow=$more
-                    exploitation 
-               & 0.01, \textbf{0.1}, 1.0 \\
-
-        $u$    & Probability optimal behavior changes between generations 
-               & 0.0, 0.1, \ldots, 1.0 \\
-
-        $M$    & Number of time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
-
-        $N_T$    & Number of teachers to pool, from which best selected 
-                 & \textbf{5} \mt{TODO: Test more for sensitivity analysis?} \\
-
-        \bottomrule
-        \end{tabular} 
-\end{table}
-\vspace{2em}
-
-\subsubsection{Intra-generational behaviors and payoffs}
-
-Each generation begins with agents initialized either by the $t=0$ initialization
-outlined above, or initialized via inter-generational reproduction and learning,
-described in detail below. Within generations, there is no social learning.
-At each time step within a generation, agents select a behavior to perform
-using the softmax algorithm, then update their ledgers $\bar\pi_{ib}$ and behavior
-counts $c_{ib}$. If 
-the chosen bandit pays off for an agent, its net payoff is incremented by one,
-$\pi'_i \leftarrow \pi_i + 1$. This process continues for $M$ time steps, 
-when reproduction, learning, and die-off occur, re-initializing the next 
-generation for performing $M$ behaviors selected via this same process.
-
-At each time step, 
-agent $i$ chooses behavior $b$ at random, with each behavior
-weighted by the softmax function applied to that behavior's observed mean payoff
-relative to all mean payoffs in the ledger,
-\begin{equation}
-  \Pr(i \text{ chooses behavior } b) = \frac{\exp(\bar\pi_{ib}
-  / \tau) }{ \sum_{b=1}^B \exp(\bar\pi_{ib} / \tau)}.
-\end{equation}  
-Softmax behavior selection is a
-biologically plausible model of behavior~\cite{Schulz2019} 
-that enables agents to explore
-alternative behaviors sometimes and exploit the best observed behavior other times,
-in accordance with Luce's choice axiom~\cite{Luce1959},.
-The parameter $\tau$ specifies how frequently alternative behaviors are
-explored versus how frequently the best observed behaviors are 
-exploited. Greater $\tau$ means more frequent exploration, lesser $\tau$ means
-more frequent exploitation. We set $\tau = 0.1$ for
-all computational analyses presented in the main paper. We (WILL HAVE) performed
-sensitivity analyses and found a weak dependence on $\tau$ that does not affect our
-main conclusions.
-
-When agent $i$ performs behavior $b$, $i$'s behavior count 
-is incremented by 1, $c'_{ib} \leftarrow c_{ib} + 1$. Agent $i$'s ledger of mean 
-payoffs are updated % from $\bar\pi_{ib}$ to $\bar\pi_{ib}'$
-using exponential weighted averaging,
-
-\begin{equation}
-  \bar\pi_{ib}' = \bar\pi_{ib} +
-    \frac{\mathrm{Bandit_{b}(0, 1)} - \bar\pi_{ib}}{c_{ib}'},
-\end{equation}
-where 
-$\mathrm{Bandit}_{b}(0, 1)$
-is 0 or 1 depending on the result of the bandit draw for behavior $b$.
-
-\subsubsection{Inter-generational inheritance and social learning}
-
-Every $M$ time steps, agents from the current generation reproduce, teach,
-and die, while the next generation to perform the next $M$ time steps learns
-from one teacher from the previous generation if they inherited the social 
-learner trait. Inter-generational dynamics thus depend on 
-two payoff-biased selection mechanisms: reproducer selection
-and teacher selection.
-
-$N$ reproducers are sampled from the population with
-replacement weighted by net payoffs, i.e., at each of $N$ draws for a parent,
-\begin{equation}
-  \Pr(\text{Agent $i$ chosen for reproduction}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
-\end{equation}
-\noindent
-We sample with replacement to allow for more successful agents to have multiple
-offspring. Child agents inherit their parents' social learning trait, so 
-all social learner parents spawn social learner offspring, and parents lacking
-the trait spawn offspring lacking the trait.
-
-Child agents with the social learning trait then must select and learn from a
-teacher from their parent's generation, including possibly their parent.
-Child agents give no preference to whether potential teachers are social 
-learners. A child selects a teacher by first selecting a pool of $N_T = 5$ potential
-teachers. Among this pool, each child selects the teacher with the greatest
-net payoffs. In case of a tie the teacher is chosen at random from those with
-the shared maximum net payoff.
-
-Social learner child agents each acquire their teacher's ledger, and all social
-learner children behavior counts are reset to 1 to limit ledger values to be between
-0 and 1. Child agents without the social learner trait have all ledger and behavior
-count values re-initialized to 0. At this point the re-initialized child agents
-engage in behavior selection and payoff accumulation described above.
-
-\subsection{Computational analyses}
-
-We manipulated environmental uncertainty parameters described above, $u$,
-$\pisub{low}$, $B$, and $M$, to examine their effects on our
-main outcome measure, the prevalence of social learning $s$. For each parameter setting
-in our analysis we calculated the average value of $s$ at the final time step
-of $T=1000$ across 100 runs for each combination of uncertainty parameter values.
-
-To analyze the effect of various forms of uncertainty on social learning 
-prevalence in our Analysis, we initialized several model runs with
-different uncertainty parameters $u$, $\pisub{\mathrm{low}}$, $B$,
-and $M$. We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$ for each combination of
-the following parameters:
-$\pisub{low} \in \{0.1, 0.5, 0.8\}$, $B \in \{2, 4, 10\}$, $M \in \{B/2, B, 2B\}$.
-
-\subsubsection{Outcome variables}
-
-Our primary outcome variable is the mean prevalence of the social learning
-trait over $N=100$ agents over 1000 trials at the final time step of each trial,
-denoted $\meansl$.
-Typically at the final time step all agents either have the social learning
-trait or do not (see Supplement for a presentation of time series collections
-and histograms of outcomes for
-a representative sampling of variables \mt{TODO}).
-
-\begin{table}[h]
-    \caption{Global environmental and cognitive initialization parameters.}
-    \label{tab:modelParameters}
-    \centering \hspace{-3em}
-    \begin{tabular}{cp{4.0in}l} \toprule
-
-        Symbol & Description & Values \\
-
-        \midrule
-
-        $\meansl$ & Mean social learning prevalence over agents and trials
-                  & $\in [0.0, 1.0]$ \\
-
-        $p_{\text{opt}}$ & Fraction of population performing optimal behavior
-                         & $\in [0.0, 1.0]$ \\
-
-        \texttt{count}$(b_i)$ & Number of agents performing behavior $b$ 
-                              & Behavior-count key-value pairs\\
-        \bottomrule
-    \end{tabular}
-\end{table}
-
-\section{Analysis}
-
-% \begin{itemize}
-%   \item 
-%     To understand how different forms of uncertainty affect social learning evolution
-%     we systematically varied environmental variables in our model and observed
-%     corresponding changes in mean social learning prevalence, $\meansl$. We
-%     confirmed that, in many cases, increased environmental variability $u$ 
-%     suppresses social learning. However\ldots
-
-%   \item 
-%     Our analysis confirmed existing theoretical predictions that social learning
-%     is valuable only when environments are sufficiently stable, i.e., 
-%     environmental variability $u$ is sufficiently small.
-%     Because of the central role of $u$, it is set on the x-axis in
-%     all analysis plots shown in Figure~\ref{fig:results}. 
-%     The threshold over $u$ at which social learning begins to decline
-%     varies depending on the value of other environmental parameters.
-
-%   \item 
-%     However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
-%     third column respectively in Figure~\ref{fig:results}) can lead
-%     social learning to be selected for even for large values of $u$, possibly
-%     due to the low risk and potentially high reward of learning an accurate
-%     tally of mean payoffs from the previous generation. 
-%     Since there are many behaviors and
-%     few observations, softmax weighting will not significantly 
-%     favor a sub-optimal behavior. However, if one does learn an accurate tally
-%     then one does have an increased chance of performing the best one.
-
-%   \item 
-%     $\pilow$ can alter selection selection pressure for or
-%     against social learning, depending on the number of time steps per generation.
-%     For instance, when $B=2$, increasing $\pilow$ (i.e. increased uncertainty
-%     about which behavior is optimal) leads at first to less sharp sigmoid curve, 
-%     where social learning is less prevalent with increased $\pilow$ when
-%     $u < 0.5$ and social learning is more prevalent with increased $\pilow$
-%     when $u > 0.5$. When $\pilow = 0.8$ noise and genetic drift dominate across
-%     tested values of $B$, with possibly a slight inverse correlation 
-%     in social learning as $u$ increases. When $B \in \{4,10\}$, increasing
-%     $\pilow \in \{0.1, 0.5\}$ leads uniformly to increased $\meansl$ over 
-%     $u$ in those settings.
-
-%   \item
-%     If $M/B$ has an effect it is mostly to 
-%     increase reliance on social learning due to social information being of 
-%     higher quality since teachers would have had more learning opportunities
-%     for larger $M$. (THERE ARE CASES WHERE THIS IS NOT THE CASE BUT THERE IS 
-%     STILL TOO MUCH NOISE DUE TO SMALL NTRIALS)
-
-%   \item
-%     Synthesis/analysis conclusion
-
-% \end{itemize}
-
-\include{mainResultsPlots.tex}
-
-\section{Discussion}
-
-\bibliographystyle{apacite}
-
-\setlength{\bibleftmargin}{.125in}
-\setlength{\bibindent}{-\bibleftmargin}
-
-% \bibliography{/Users/mt/workspace/Writing/library.bib}
-\bibliography{this.bib}
-
-\appendix
-
-\section{Appendix}
-
-\subsection{Mean payoffs at final time step}
-
-\include{supplement/meanNetPayoffs.tex}
-
-\subsection{Convergence information}
-
-\begin{table}[h]
-  \caption{Max. iterations = 5000.}
-  \centering
-  \begin{tabular}{cccc} \toprule
-    $B$ & \# not at fixation & \# total series & Pct. not fixated \\
-    \midrule  
-    2  & 21  & 132000 & 0.016 \% \\
-    4  & 30  & 132000 & 0.023 \% \\
-    10 & 971 & 132000 & 0.74  \% \\
-    \bottomrule
-  \end{tabular} 
-\end{table}
+It allows individuals to solve problems when acquiring information from others is
+more efficient than learning on one's own~\cite{Laland2004}. Theory predicts that
+social learning should be favored in contexts with greater
+uncertainty~\cite{BoydRicherson1985,Henrich1998}, and this prediction has received
+some empirical support across species~\cite{McElreath2005,Kendal2018,Allen2019}.
+However, the meaning of the term \emph{uncertainty} is not always clear, and often
+conflates environmental variability, spatial heterogeneity, ambiguity or
+uncertainty about payoff structure, and other possible interpretations of
+\emph{uncertainty}.  Moreover, most models of the do not account for
+individual-level cognition~\cite{Heyes2016}.
 

### 2022-05-18 ms.tex
Updates from Overleaf
started modifying figures, reviewing existing model features in table in terms of our model factors
starting final journal article draft

--- 2022-05-12 ms.tex
@@
-% \documentclass[11pt,letterpaper]{article}
 \documentclass[letterpaper,11.5pt]{scrartcl}
+\usepackage{totcount}
 % \documentclass[11pt]{report}
@@
 
+\newtotcounter{citnum} %From the package documentation
+\def\oldbibitem{} \let\oldbibitem=\bibitem
+\def\bibitem{\stepcounter{citnum}\oldbibitem}
+
 \usepackage{graphicx}
 
-\title{Some forms of uncertainty may suppress the evolution of social learning}
+\title{Uncertainty in social learning evolution}
 
@@
 Social learning is essential to survival. It is likely to evolve when it is more
-efficient than asocial, trial-and-error learning. The consensus in cultural
-evolutionary theory holds that some amount of environmental variability and
-uncertainty about the best decisions are necessary for social learning to evolve.
-However, current models for the evolution of social learning tend to conflate forms
-of uncertainty, and rarely consider different ones in tandem. Moreover, many models
-are limited by considering only two possible behaviors and environmental states.
-Here we use evolutionary agent-based modeling to improve on these shortcomings. We
-model a time-varying environment with dozens of possible behaviors performed by
-agents engaging in individual and social learning. We show that ambiguous payoffs,
-larger possible decision sets, and shorter agent lifespans sometimes increase social
-learning prevalence, as expected. However, we also find that, under some conditions,
-these forms of uncertainty can select against social learning.
+efficient than asocial, trial-and-error learning. Theoretically, some uncertainty is
+necessary for social learning to be necessary, but too much uncertainty makes
+social information useless. This fact is empirically
+supported across biology and human sciences. However, we lack a theoretical
+framework to predict the effects of specific classes and types of uncertainty on social
+learning evolution. Furthermore, existing models and experimental operationalizations of
+uncertainty are ambiguously related, and 
+tend to only consider a small number of sources of uncertainty and behavioral
+choices.  Here we use evolutionary agent-based modeling to consolidate
+models of uncertainty in social learning evolution to improve on these
+shortcomings. We model a time-varying environment with a varying number
+of possible behaviors agents could perform to acquire payoffs.
+We show that environmental variability, ambiguous payoffs, 
+larger decision sets, and shorter agent lifespans interact to 
+affect social learning evolution in complex ways that 
+sometimes confuse evolution about which is the optimal strategy, i.e., 
+emergent evolutionary uncertainty. 
+Our work strengthens social evolution theory that could help 
+guide human, non-human, and artificial life towards optimal responses to existential
+threats and new opportunities.\footnote{This document contains
+\total{citnum} references.}  
 \end{abstract}
@@
 
-\subsection{The history of "copy when uncertain"}
-It has become a near truism that "theory predicts that it is adaptive to learn when uncertain." This claim has been motivated by empirical work (such as Asch conformism studies) & theoretical models (Boyd Richerson 85, 88) that often do not mention the word uncertainty at all.
-However, they do show related effects of social learning increasing when individual learning is difficult (i.e., ambiguous lines in Asch), and intermediate levels of temporal uncertainty favoring social learning (i.e., too stable and you get genetic canalization of a trait, too much temporal variation and there's selection for individual learning to ensure the most up to date information).
+Social learning is essential to human and other species' everyday life and survival.
+It allows individuals to solve problems when acquiring information from others is
+more efficient than learning on one's own~\cite{Laland2004}. Theory predicts that
+social learning should be favored in contexts with greater
+uncertainty~\cite{BoydRicherson1985,Henrich1998}, up to a
+point~\cite{Rogers1988,Feldman1996}; this prediction has received some empirical
+support across species~\cite{McElreath2005,Kendal2018,Allen2019}.  However, the
+meaning of the term \emph{uncertainty} often conflates environmental variability,
+spatial heterogeneity, ambiguity or uncertainty about payoff structure, and other
+variability that could be plausibly interpreted as \emph{uncertainty}.  Many models
+of social learning evolution do not account for 
+individual-level cognition~\cite{Heyes2016}, though humans
+clearly have evolved cognitive mechanisms for dealing with 
+uncertainty generally~\cite{Gershman2019,Schulz2019}.
+Furthermore, social learning evolution theory tends to be organized around an
+increasing number of modeling choices~\cite[Figure 1]{Kendal2018} instead
+of around broader contextual assumptions such as uncertainty conditions. It remains
+an outstanding question, then, to identify how different contexts and forms of
+uncertainty might combine to affect social learning evolution in complex ways.
+Answering this question is critical for understanding human behavior adapting to a
+rapidly changing world, both to mitigate existential
+threats~\cite{Moya2020,Jones2021}, and to captialize on new opportunities such as
+transitioning to clean energy use and
+production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
 
-{Galef 2009} https://www.sciencedirect.com/science/article/pii/S006534540939004X#bb0059
-cites {B & R 85/88 & Laland 2004} https://link.springer.com/content/pdf/10.3758/BF03196002.pdf
-Laland 2004 cites {B& R 88} https://books.google.com/books?hl=en&lr=&id=mqFcAgAAQBAJ&oi=fnd&pg=PA29&dq=Boyd+and+Richerson%E2%80%99s+(1988&ots=IfIbB_kx_a&sig=g8CYH5bVfwfXhTRGot0q761f9mw#v=onepage&q&f=false
+To gain a more systematic understanding of uncertainty and social learning evoluiton,
+we identified a set of common ecological
+uncertainty classes (``eigenvectors'' of uncertainty) used as factors
+in social learning evolution models: (1) environmental variability; (2) payoff
+ambiguity (difference between best behavior choice and others); (3) 
+selection set size (number of ecologically possible behaviors); and 
+(4) the lifespan of agents. These were chosen because modeling and empirical 
+study designs across taxa tend use one or more of these uncertainty dimensions.
+Environmental variability is sometimes modeled as catastrophic and 
+happens only once in an individual's lifetime~\cite{Rogers1988}, or may be
+modeled as occurring with a fixed or variable
+probability~\cite{Feldman1996,McElreath2005}---in all these examples environments
+can only be in one of two states. Payoff ambiguity is sometimes in the form
+of differences in expected payoffs arising from different
+behaviors or strategies~\cite{Enquist2007,Rendell2010}
+or by varying the standard deviation of payoffs~\cite{McElreath2005}. 
+Selection set size is often limited to one size throughout social learning
+evolution studies: empirical studies of \emph{bombus terresteris} (bumble
+bee)~\cite{Baracchi2018} and \emph{parus major} (great tit)~\cite{Aplin2017}
+populations each provided two behaviors for
+the bees and birds to perform, each yielding greater or smaller
+payoffs depending on experimental treatment; studies in humans have used two
+or three possible behaviors~\cite{McElreath2005,Toyokawa2019}; m
+odeling studies have used either two 
+behaviors~\cite{Feldman1996,Rendell2010} or four behaviors~\cite{Enquist2007} 
+in understanding the role of uncertainty. The age or lifespan of individuals was
+found to have an effect on social learning in both \emph{parus
+major}~\cite{Aplin2017} and \emph{poecilia reticulata} 
+(guppies)~\cite{Leris2016} \mt{Need better connection between lifespan and 
+age, or better references to support use of lifespan}.
+Shorter lifespans mean individuals
+die more uncertain of which behaviors are optimal, and pass that uncertainty on
+to their offspring. To answer our research questions about the combined effect
+of various forms of uncertainty on social learning evolution, we developed an
+agent-based model that incorporates all four of
+these uncertainty variables. We systematically vary these parameters
+to understand and predict their effects on social learning evolution.
 
-Other examples of empirical work: https://www.sciencedirect.com/science/article/pii/S0022096516300625
+\paragraph{Social learning evolution} (CRISTINA, PAUL)
+To add to confusion about how to integrate diverse models of social learning
+evolution, different models select different social learning components in
+seemingly \emph{ad hoc} ways 
+\begin{itemize}
+  \item 
+    Vertical, oblique, horizontal transmission
+  \item
+    Conformity, payoff-biased, frequency-dependent, etc. A note about how
+    ``conformity'' is often not distinguished from other forms of social learning
+  \item
+    Review human studies
+  \item
+    Review non-human studies~\cite{Leris2016,Aplin2017,Avargues-Weber2018,Baracchi2018}
+  \item
+    More things from which we selected the operation of our model
+\end{itemize}
 
-Henrich & Boyd 88 do have something like B that is the difficulty of getting right answer (or rho probability of doing so)
-https://www.sciencedirect.com/science/article/pii/S109051389800018X#FIG5
+\paragraph{Meaning of uncertainty in ecology and cognitive and social sciences} (JAMIE, PAUL)
+We need to support our claim that these four classes of uncertainty really 
+count as forms of uncertainty and show how it is consistent across ecology and
+cognitive and social science.
 
-Lifespan not modelled
-
-\subsection{earlier structure}
-
-Social learning is essential to human and other species' everyday life and survival.
-It allows individuals to solve problems when acquiring information from others is more efficient than learning
-on one's own~\cite{Laland2004}. Theory predicts that social
-learning should be favored in contexts with greater
-uncertainty~\cite{BoydRicherson1985,Henrich1998}, and this prediction has received some empirical support~\cite{McElreath2005,Kendal2018}. 
-However, the meaning of the term ``uncertainty'' is not always clear, and often conflates environmental variability, spatial heterogeneity, and ambiguity or uncertainty about payoff structure. 
-Moreover, most models of the evolution of social learning ``blackbox'' key 
-cognitive learning processes that underlie it~\cite{Heyes2016}.
-
-In this paper we use agent-based modeling to compare the effect of
-different sources of uncertainty on social learning
-by ``unblackboxing'' typically abstracted-out model components 
-of environmental variability, payoff structures and
-agent life histories, and  learning mechanisms. ``Uncertainty''  
-means variability where the probabilistic structure is unknown. %cannot be learned.
-Uncertainty increases when payoffs are more similar across behaviors, when
-environmental variability increases, when the number of possible behaviors
-increases, and when lifespan decreases.  In this paper we show that more ambiguous
-payoff structures and shorter lifespans sometimes do lead to greater reliance on
-social learning---however, we also identify and explain cases where greater
-uncertainty leads to less social learning due to the possibility that social
-information is misleading.  We thus conclude that many predictions made by previous
-models of the evolution of social learning are likely overgeneralized.
-%~\cite{Yarkoni2021}.
-
-\subsection{Social Learning}
-
-Social learning, as we consider it here, occurs whenever an individual acquires a behavior by observing another individual.
-This need not require explicit instruction, and is, in fact, widespread across a broad range of nonhuman
-taxa~\cite{Kendal2018,Allen2019}. Importantly, social information can be inherited both
-from parents --- i.e., via \emph{vertical transmission} like genetic information --- and
-from others in the same generation --- i.e., via \emph{horizontal transmission}
-\cite{CavalliFeldman1981}. The joint action of vertical and horizontal transmission
-gives rise to qualitatively different evolutionary dynamics. For example,
-inter-generational environmental change will affect the adaptive value of genetic
-information and vertically-transmitted cultural information more than information
-that is horizontally transmitted. We include both horizontal and vertical transmission pathways in our
-model. For simplicity, we ignore oblique transmission in which non-parental members
-of the previous generation are observed.
-
-Environmental variability has been seen as a key selective force in shaping social learning starting with the first formal models of cultural evolution~\cite{CavalliFeldman1981,BoydRicherson1985}.
-Totally stable environments will not favor learning mechanisms because information can become genetically hardwired, while  extreme environmental instability will degrade the value
-of social learning as information becomes rapidly outdated~\cite{Feldman1996}.
-This suggests that an intermediate degree of environmental predictability will favor social learning.
-Strategies can also evolve to mitigate the risks of relying on outdated social information by weighing more heavily information from others who more recently acquired it~\cite{Rendell2010}.
-
-Uncertainty has also been modelled as arising from other aspects of the environment. 
-For example, \citeA{Perreault2012} vary the ambiguity of the environmental cue individuals get through individual learning about the state of the world.
-Perhaps not surprisingly, the more ambiguous the asocial information, the greater the selection for weighing social information heavily.
-Alternatively, uncertainty about the optimal behavior has been modelled by increasing the number of cultural traits to choose from.
-
-Empirical research supports some of these theoretical predictions.
-Organisms flexibly use social learning as a function of the ambiguity of the environmental cue and of other environmental features that are often subsumed under the rubric of ``uncertainty.''
-While some studies explicitly impose a cost whenever participants use asocial
-information \cite{Morgan2012,Atkisson2012}, 
-others allow the costs of each strategy to emerge as a function of task structure and assess its consequences for learning strategies. 
-For example, when participants received equivocal private information about the best investment to make in a lab game,
-they were more likely to rely on social information to make their choice~\cite{Toelch2013}. 
-\citeA{McElreath2005} developed a similar experiment where participants ``pulled'' virtual slot machine arms (often called ``bandits''), each yielding stochastic payoffs.
-Participants relied more on social learning when the bandits had higher-variance payoffs, and when the highest-paying bandit changed more frequently.
-The number of options to choose between can also increase uncertainty about the optimal choice, and has been shown to increase participants' reliance on social learning \cite{Muthukrishna2016a}.
-
-Thus existing theoretical work and the empirical evidence seem to support that various forms of uncertainty favor the evolution of social learning.
-However, uncertain outcomes are operationalized in different ways across models, and any given model tends to focus on only one or two forms of uncertainty at a time.
-Our agent-based modeling approach enables us to explicitly specify different forms of uncertainty independently in order to understand which of these environmental factors particularly favor the evolution of social learning.
-Simultaneous modelling also allows us to examine their interaction.
-We first attempt conceptual replications of previous models' findings, and then examine where they diverge.
-
-\subsection{Research overview}
-
-Computational agents in our model face a problem: every time step they perform
-one of several behaviors, with each behavior represented by a ``bandit'' that
-pays off 1 or 0 with some probability. One of these behaviors (the optimal
-behavior) pays off with a higher probability than all the others.
-Agents decide which behavior to 
-perform based either on a success-biased observation 
-of a peer's behavior (social learning) or based on their own observations (asocial learning).
-Agents then update their memory of expected payoffs for each behavior 
-when they receive a payoff from their chosen
-action. Within this framework we have four mechanisms by which we operationalize 
-and vary uncertainty:
-(1) the expected payoffs of the optimal behavior and all the rest---when payoffs
-are nearly identical, uncertainty in the form of ambiguity increases; (2) the
-environmental variability, i.e., the probability that the optimal behavior 
-changes between generations; (3) the number of possible behaviors the environment allows---which
-behavior is optimal is more uncertain when there are more possibilities; and (4)
- agent lifespan---agents experience fewer learning opportunities and die more uncertain about which behavior
-is optimal when their lifespan is shorter.
-
-The primary outcome measure of our
-model is the average difference between the frequency of (horizontal) 
-social learning and the frequency of asocial
-learning across all agents. If social learning is more prevalent than asocial
-learning this suggests that the optimal behavior is more likely found
-by copying peers than by trial-and-error search.
-Conversely, when asocial learning is more prevalent, this suggests social information
-is likely to be misleading. 
-When social and asocial learning are 
-equally prevalent this means there is no discernible advantage to either, i.e.,
-the agents have weak priors on which channel provides more reliable information. 
-Each agent has its own social learning frequency that it inherits from its
-parent (haploid reproduction) with mutation, so evolution selects for,
-or computes~\cite{Smaldino2013}, the optimal
-social learning frequency.
-
-Using our model we found that increased uncertainty sometimes
-led to increased reliance on social learning, as expected from prior literature. However, we also find cases where increased uncertainty decreased agents' reliance on social learning
-due to increased uncertainty that made social information less reliable, thereby
-increasing reliance on asocial learning.
+\paragraph{Research overview}
 
 \section{Model}
+
+\paragraph{Model overview (introduce uncertainty variables)}
 
@@
 a common modelling and experimental approach for representing behaviors with
-probabilistic payoffs~\cite{SuttonBartoBook, McElreath2005,Rendell2010,Schulz2019}. %Bandits are like  slot machines in a casino~\ref{fig:behaviorSelection}.
-Each behavior $b$ yields a payoff of 1 with probability $\pi_b$ and a payoff of zero
-otherwise; $\pi_b$ is therefore also the expected payoff of behavior $b$. Agents must
+probabilistic payoffs~\cite{SuttonBartoBook,McElreath2005,Rendell2010,Schulz2019}. 
+Each behavior $b$ yields Bernoulli payoffs: payoff of 1 with probability $\pi_b$ and 
+zero payoff with probability $1 - \pi_b$; 
+$\pi_b$ is therefore also the expected payoff of behavior $b$. Agents must
 decide which behavior to perform at each time step. To do this, agents 
@@
 
-We operationalized uncertainty in four different ways: 
-(1) payoff ambiguity, $A_\pi$, which measures the difference
-between the optimal expected payoff behavior $\pisub{high}$ and the expected payoff
-of the other behaviors, $\pisub{low}$; 
-(2) environmental variability, $u$, the probability the optimal behavior changes from one generation to another; 
-(3) the number of possible behaviors, $B$; and 
-(4) the lifespan, or time steps per generation, $M$.
+\paragraph{Agents}
 
-We ran the simulation for $T=1000$ time steps. At
-the end of each generation agents reproduce and then die off. 
-Those selected to reproduce
-pass on their boolean social learning trait, $s$, without mutation,
-which specifes whether agents learn socially. We developed a series of
-computational analyses where we systematically vary the uncertainty
-variables and observe the average prevalence of social learning trait $s$
-across agents and trials, which is our primary outcome measure, 
-denoted $\langle s \rangle$.
+\paragraph{Dynamics: initialization, behaviors and payoffs, evolution}
 
-\subsection{Agents and their attributes}
+\paragraph{Computational analyses and outcome measures}
 
-In each time step, $N$ agents---autonomous problem solvers---select 
-which behavior to perform based on their running tally of mean payoffs for 
-each available behavior. %information (Figure~\ref{fig:behaviorSelection}). 
-Agent $i$ tracks the mean payoff of each behavior $b$, denoted $\bar\pi_{ib}$, and
-a \emph{count} of how many times it has performed each behavior, denoted $c_{ib}$.
-$\bar\pi_{ib}$
-is initialized to 0 for all $b$ at model initialization for
-all agents, and after each generation for individual learner agents. Social
-learning agents' $\bar\pi_{ib}$ is initialized as that of its teacher selected
-through performance-biased oblique learning. Agent $i$'s accumulated payoffs
-from performing several behaviors over their lifetime of $M$ time steps is
-denoted $\pi_{i}$.
+\paragraph{Analysis 1: patterns in social learning evolution over $u$}
 
-\vspace{2em}
+\paragraph{Analysis 2: evolutionary uncertainty when $\meansoc \approx \meanasoc$}
 
-\begin{table}[h]
-    \caption{Dynamic agent-level variables. Each has an implicit time dependence.}
-    \label{tab:modelParameters}
-    \centering \hspace{-3em}
-    \begin{tabular}{cp{4.0in}l} \toprule
+\paragraph{Disc. 1: Foundation for studying ssortative social learning}~\cite{Katsnelson2014}.
 
-        Attribute & Description & Initial value \\
-
-        \midrule
-
-        $s_i$  & Social learner trait: 1 if agent $i$ is social learner; 0 otherwise & 0
-        or 1 w/ equal prob. \\
-
-        $\bar\pi_{ib}$ & ``Ledger'': mean payoffs acquired via behavior $b$ by $i$ 
-                       & $B$-vector of floating-point zeros \\
-
-        $c_{ib}$ & Count of how many times agent $i$ performed $b$ 
-              & $B$-vector of integer zeros \\
-
-        $\pi_i$ & Net payoffs accumulated by $i$ within generation
-                                & 0.0 \\
-        \bottomrule
-    \end{tabular}
-\end{table}
-
-\vspace{2em}
-
-\subsection{Modeling uncertainty}
-
-In our model uncertainty is a tunable consequence of four environmental features:
-%that structure the behavior of agents.  
-% Many factors contribute to the 
-% uncertainty involved in both social and asocial learning. 
-%We model uncertainty in four distinct ways: 
-\begin{enumerate}
-    \item We vary the frequency at which the optimal behavior changes, which we call \emph{environmental variability}, $u$.
-At the start of each generation, with probability $u$, a new behavior is assigned a payoff of $\pisub{high}$ while all other behaviors are assigned a payoff of $\pisub{low}$.
-Otherwise, the same behavior remains optimal across generations.
-    \item We vary the latent expected payoffs yielded by the bandits. For simplicity,
-      we assume that in any given environmental state, there is one optimal behavior that
-      yields an expected payoff of $\pisub{high}$, while all other behaviors yield a 
-      payoff of $\pisub{low} < \pisub{high}$. As $\pilow$ increases towards 
-      $\pihigh$, uncertainty in the form of \emph{payoff ambiguity} also increases,
-      making it more difficult, and less rewarding, for agents to determine which
-      behavior is the optimal one.
-      % The difference between these quantities is the \emph{payoff ambiguity}, 
-    % \begin{equation}
-    %   A_\pi = 1 - (\pisub{high} - \pisub{low}),
-    %   \label{eq:payoffAmbiguity}
-    % \end{equation}
-    % which is maximized when the expected payoffs are close to equal and minimized
-    % when they differ greatly. For simplicity we will set $\pisub{high} = 0.9$
-    % for all analyses and vary $\pisub{low}$ in order to vary $A_\pi$.
-    \item We vary the total \emph{number of available behaviors}, $B$, which is a
-      source of uncertainty since agents are less likely to know which behavior yields high payoffs.  
-    \item Finally, we vary number of behavioral events per generation, $M$.
-This can be viewed as the \emph{effective lifespan} of an agent.
-Decreasing this lifespan effectively increases the importance of each event for acquiring payoffs.
-When lifespans are short ($M$ is small), agents experience greater uncertainty about which behavior is optimal given the fewer learning opportunities.
-\end{enumerate}
-
-\subsection{Dynamics and evolution}
-
-Model dynamics can be split into three parts: initialization,
-\emph{intra}generational behavior and payoff accumulation, and
-\emph{inter}generational transmission of the social learning trait and oblique
-learning (Figure~\ref{fig:IntraInterGenerationalDynamics}). 
-The model runs that we analyze here were initialized with $N=100$ agents
-to randomly have the social learner trait or not, with no accumulated payoffs, and
-blank ``ledgers''. At each time step, agents select one of $B$ possible behaviors
-to perform, accumulating a payoff of 1 if the bandit pays off, and 0 if it does
-not---a bandit pays off with probability $\pihigh$ if it is the unique optimal
-behavior, or with probability $\pilow$ if it is one of $B-1$ non-optimal
-behaviors. Agents accumulate payoffs in this way for $M$ time steps in each
-generation. At the end of each generation, $N=100$ agents are randomly selected with
-replacement to reproduce (asexual, haploid reproduction), 
-weighted by their net payoffs over the generation,
-i.e., \emph{performance-biased} reproduction. Child agents then learn from 
-one teacher, selected again via a form of performance bias: a child agent chooses
-its teacher by first selecting a fully random subset of agents from the 
-parent generation as potential teachers, then selecting the one with the 
-greatest net payoffs among the subset. This process continues until $T=1000$
-time steps have elapsed \mt{this should probably be changed depending on $M$ so that
-    all analyses use the same number of generations. my informal checks have shown quick
-convergence, but i haven't tested b=4 and b=10 as much.}.
-
-\begin{figure}
-  \caption{Model dynamics are composed of two major parts: first, agents perform
-  behaviors for $M$ time steps in a single generation. Then agents reproduce
-  randomly, with more successful agents being more likely to reproduce. Newly
-  ``born'' social learner agents use success bias to select and learn from a chosen
-  teacher. Then, all agents from the previous generation die off, all new agents
-  begin a new generation, and the process continues until 1000 total time steps
-  have elapsed. Agents are initialized as ``blank slates''.}
-  \centering
-    \includegraphics[width=0.9\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
-  \label{fig:IntraInterGenerationalDynamics}
-\end{figure}
-
-\subsubsection{Initialization}
-
-Model initialization includes agent and environment initializations. Agents are
-randomly initialized to have the social learning trait or not, with equal 
-probability. Agent ``ledgers'' and behavior counts 
-are uniformly initialized to the no-knowledge,
-blank-slate case where all $\pi_{ib} = 0$ and $c_{ib} = 0$. Both the 
-ledger and behavior count vectors have $B$ entries, one for each
-behavior the environment affords. Net payoffs for
-the generation are also initialized to zero. All agents are initialized with
-the same softmax temperature, $\tau$, that guides their behavior selection 
-to be either more exploratory (greater $\tau$) or more exploitative of
-what agents believe to be the optimal behavior(s) (lesser $\tau$).
-
-The environment is initialized to have $B$ behaviors with one of them selected
-at random to be the optimal behavior, denoted $b^*$. Behavior $b^*$ is 
-initialized to have a probability $\pihigh$ of paying off 1. All other behaviors
-are initialized to have probability $\pilow$ of paying off 1. The modeler must
-specify the environmental variability, $u$, and the number of time steps per 
-generation, $M$.
-
-\vspace{2em}
-\begin{table}[h]
-    \caption{Global environmental and cognitive initialization parameters.}
-    \label{tab:modelParameters}
-    \centering \hspace{-3em}
-    \begin{tabular}{cp{4.0in}l} \toprule
-
-        Symbol & Description & Values tested (bold$=$default) \\
-
-        \midrule
-
-        $B$       & Number of possible behaviors (represented by ``bandits'') 
-                  & 2, 4, 10 \\
-
-        $\pihigh$ & Probability that the unique optimal behavior pays off 1 
-                & \textbf{0.9} \\
-
-        $\pilow$ & Probability one of $B - 1$ non-optimal behaviors pays off 1 
-                 & 0.1, 0.45, 0.8 \\
-
-        $\tau$ & Softmax temp.; $\uparrow=$more exploration, $\downarrow=$more
-                    exploitation 
-               & 0.01, \textbf{0.1}, 1.0 \\
-
-        $u$    & Probability optimal behavior changes between generations 
-               & 0.0, 0.1, \ldots, 1.0 \\
-
-        $M$    & Number of time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
-
-        $N_T$    & Number of teachers to pool, from which best selected 
-                 & \textbf{5} \mt{TODO: Test more for sensitivity analysis?} \\
-
-        \bottomrule
-        \end{tabular} 
-\end{table}
-\vspace{2em}
-
-\subsubsection{Intra-generational behaviors and payoffs}
-
-Each generation begins with agents initialized either by the $t=0$ initialization
-outlined above, or initialized via inter-generational reproduction and learning,
-described in detail below. Within generations, there is no social learning.
-At each time step within a generation, agents select a behavior to perform
-using the softmax algorithm, then update their ledgers $\bar\pi_{ib}$ and behavior
-counts $c_{ib}$. If 
-the chosen bandit pays off for an agent, its net payoff is incremented by one,
-$\pi'_i \leftarrow \pi_i + 1$. This process continues for $M$ time steps, 
-when reproduction, learning, and die-off occur, re-initializing the next 
-generation for performing $M$ behaviors selected via this same process.
-
-At each time step, 
-agent $i$ chooses behavior $b$ at random, with each behavior
-weighted by the softmax function applied to that behavior's observed mean payoff
-relative to all mean payoffs in the ledger,
-\begin{equation}
-  \Pr(i \text{ chooses behavior } b) = \frac{\exp(\bar\pi_{ib}
-  / \tau) }{ \sum_{b=1}^B \exp(\bar\pi_{ib} / \tau)}.
-\end{equation}  
-Softmax behavior selection is a
-biologically plausible model of behavior~\cite{Schulz2019} 
-that enables agents to explore
-alternative behaviors sometimes and exploit the best observed behavior other times,
-in accordance with Luce's choice axiom~\cite{Luce1959},.
-The parameter $\tau$ specifies how frequently alternative behaviors are
-explored versus how frequently the best observed behaviors are 
-exploited. Greater $\tau$ means more frequent exploration, lesser $\tau$ means
-more frequent exploitation. We set $\tau = 0.1$ for
-all computational analyses presented in the main paper. We (WILL HAVE) performed
-sensitivity analyses and found a weak dependence on $\tau$ that does not affect our
-main conclusions.
-
-When agent $i$ performs behavior $b$, $i$'s behavior count 
-is incremented by 1, $c'_{ib} \leftarrow c_{ib} + 1$. Agent $i$'s ledger of mean 
-payoffs are updated % from $\bar\pi_{ib}$ to $\bar\pi_{ib}'$
-using exponential weighted averaging,
-
-\begin{equation}
-  \bar\pi_{ib}' = \bar\pi_{ib} +
-    \frac{\mathrm{Bandit_{b}(0, 1)} - \bar\pi_{ib}}{c_{ib}'},
-\end{equation}
-where 
-$\mathrm{Bandit}_{b}(0, 1)$
-is 0 or 1 depending on the result of the bandit draw for behavior $b$.
-
-\subsubsection{Inter-generational inheritance and social learning}
-
-Every $M$ time steps, agents from the current generation reproduce, teach,
-and die, while the next generation to perform the next $M$ time steps learns
-from one teacher from the previous generation if they inherited the social 
-learner trait. Inter-generational dynamics thus depend on 
-two payoff-biased selection mechanisms: reproducer selection
-and teacher selection.
-
-$N$ reproducers are sampled from the population with
-replacement weighted by net payoffs, i.e., at each of $N$ draws for a parent,
-\begin{equation}
-  \Pr(\text{Agent $i$ chosen for reproduction}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
-\end{equation}
-\noindent
-We sample with replacement to allow for more successful agents to have multiple
-offspring. Child agents inherit their parents' social learning trait, so 
-all social learner parents spawn social learner offspring, and parents lacking
-the trait spawn offspring lacking the trait.
-
-Child agents with the social learning trait then must select and learn from a
-teacher from their parent's generation, including possibly their parent.
-Child agents give no preference to whether potential teachers are social 
-learners. A child selects a teacher by first selecting a pool of $N_T = 5$ potential
-teachers. Among this pool, each child selects the teacher with the greatest
-net payoffs. In case of a tie the teacher is chosen at random from those with
-the shared maximum net payoff.
-
-Social learner child agents each acquire their teacher's ledger, and all social
-learner children behavior counts are reset to 1 to limit ledger values to be between
-0 and 1. Child agents without the social learner trait have all ledger and behavior
-count values re-initialized to 0. At this point the re-initialized child agents
-engage in behavior selection and payoff accumulation described above.
-
-\subsection{Computational analyses}
-
-We manipulated environmental uncertainty parameters described above, $u$,
-$\pisub{low}$, $B$, and $M$, to examine their effects on our
-main outcome measure, the prevalence of social learning $s$. For each parameter setting
-in our analysis we calculated the average value of $s$ at the final time step
-of $T=1000$ across 100 runs for each combination of uncertainty parameter values.
-
-To analyze the effect of various forms of uncertainty on social learning 
-prevalence in our Analysis, we initialized several model runs with
-different uncertainty parameters $u$, $\pisub{\mathrm{low}}$, $B$,
-and $M$. We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$ for each combination of
-the following parameters:
-$\pisub{low} \in \{0.1, 0.5, 0.8\}$, $B \in \{2, 4, 10\}$, $M \in \{B/2, B, 2B\}$.
-
-\subsubsection{Outcome variables}
-
-Our primary outcome variable is the mean prevalence of the social learning
-trait over $N=100$ agents over 1000 trials at the final time step of each trial,
-denoted $\meansl$.
-Typically at the final time step all agents either have the social learning
-trait or do not (see Supplement for a presentation of time series collections
-and histograms of outcomes for
-a representative sampling of variables \mt{TODO}).
-
-\begin{table}[h]
-    \caption{Global environmental and cognitive initialization parameters.}
-    \label{tab:modelParameters}
-    \centering \hspace{-3em}
-    \begin{tabular}{cp{4.0in}l} \toprule
-
-        Symbol & Description & Values \\
-
-        \midrule
-
-        $\meansl$ & Mean social learning prevalence over agents and trials
-                  & $\in [0.0, 1.0]$ \\
-
-        $p_{\text{opt}}$ & Fraction of population performing optimal behavior
-                         & $\in [0.0, 1.0]$ \\
-
-        \texttt{count}$(b_i)$ & Number of agents performing behavior $b$ 
-                              & Behavior-count key-value pairs\\
-        \bottomrule
-    \end{tabular}
-\end{table}
-
-\section{Analysis}
-
-% \begin{itemize}
-%   \item 
-%     To understand how different forms of uncertainty affect social learning evolution
-%     we systematically varied environmental variables in our model and observed
-%     corresponding changes in mean social learning prevalence, $\meansl$. We
-%     confirmed that, in many cases, increased environmental variability $u$ 
-%     suppresses social learning. However\ldots
-
-%   \item 
-%     Our analysis confirmed existing theoretical predictions that social learning
-%     is valuable only when environments are sufficiently stable, i.e., 
-%     environmental variability $u$ is sufficiently small.
-%     Because of the central role of $u$, it is set on the x-axis in
-%     all analysis plots shown in Figure~\ref{fig:results}. 
-%     The threshold over $u$ at which social learning begins to decline
-%     varies depending on the value of other environmental parameters.
-
-%   \item 
-%     However, more possible behaviors $B$ ($B=2,4,10$ for the first, second, and
-%     third column respectively in Figure~\ref{fig:results}) can lead
-%     social learning to be selected for even for large values of $u$, possibly
-%     due to the low risk and potentially high reward of learning an accurate
-%     tally of mean payoffs from the previous generation. 
-%     Since there are many behaviors and
-%     few observations, softmax weighting will not significantly 
-%     favor a sub-optimal behavior. However, if one does learn an accurate tally
-%     then one does have an increased chance of performing the best one.
-
-%   \item 
-%     $\pilow$ can alter selection selection pressure for or
-%     against social learning, depending on the number of time steps per generation.
-%     For instance, when $B=2$, increasing $\pilow$ (i.e. increased uncertainty
-%     about which behavior is optimal) leads at first to less sharp sigmoid curve, 
-%     where social learning is less prevalent with increased $\pilow$ when
-%     $u < 0.5$ and social learning is more prevalent with increased $\pilow$
-%     when $u > 0.5$. When $\pilow = 0.8$ noise and genetic drift dominate across
-%     tested values of $B$, with possibly a slight inverse correlation 
-%     in social learning as $u$ increases. When $B \in \{4,10\}$, increasing
-%     $\pilow \in \{0.1, 0.5\}$ leads uniformly to increased $\meansl$ over 
-%     $u$ in those settings.
-
-%   \item
-%     If $M/B$ has an effect it is mostly to 
-%     increase reliance on social learning due to social information being of 
-%     higher quality since teachers would have had more learning opportunities
-%     for larger $M$. (THERE ARE CASES WHERE THIS IS NOT THE CASE BUT THERE IS 
-%     STILL TOO MUCH NOISE DUE TO SMALL NTRIALS)
-
-%   \item
-%     Synthesis/analysis conclusion
-
-% \end{itemize}
-
-\include{mainResultsPlots.tex}
-
-\section{Discussion}
+\paragraph{Disc. 2: Applications to artificial
+intelligence}~\cite{Sandholm1996,Jaques2019,Ndousse2021,Gronauer2022}
 
 \bibliographystyle{apacite}
-
-\setlength{\bibleftmargin}{.125in}
-\setlength{\bibindent}{-\bibleftmargin}
-
-% \bibliography{/Users/mt/workspace/Writing/library.bib}
-\bibliography{this.bib}
-
-\appendix
-
-\section{Appendix}
-
-\subsection{Mean payoffs at final time step}
-
-\include{supplement/meanNetPayoffs.tex}
-
-\subsection{Convergence information}
-
-\begin{table}[h]
-  \caption{Max. iterations = 5000.}
-  \centering
-  \begin{tabular}{cccc} \toprule
-    $B$ & \# not at fixation & \# total series & Pct. not fixated \\
-    \midrule  
-    2  & 21  & 132000 & 0.016 \% \\
-    4  & 30  & 132000 & 0.023 \% \\
-    10 & 971 & 132000 & 0.74  \% \\
-    \bottomrule
-  \end{tabular} 
-\end{table}
+\bibliography{/Users/mt/workspace/Writing/library.bib}
 

### 2022-05-20 ms.tex
first pass method revision

@@
 \newcommand{\piS}{\langle \pisub{S} \rangle}
+\newcommand{\ledger}{\bar\pi_{ib}}
 
@@
 \newcommand{\meanT}{\meanvar{T}}
+
+\newcommand{\bandit}{\text{Bandit}_b(0, 1)}
 
@@
 affect social learning evolution in complex ways that 
-sometimes confuse evolution about which is the optimal strategy, i.e., 
-emergent evolutionary uncertainty. 
+sometimes caused evolution to be highly uncertain about whether social learning was
+the optimal strategy. 
 Our work strengthens social evolution theory that could help 
-guide human, non-human, and artificial life towards optimal responses to existential
-threats and new opportunities.\footnote{This document contains
+guide human, non-human, and artificial intelligence towards optimal responses 
+to existential threats and new opportunities.\footnote{This document contains
 \total{citnum} references.}  
@@
 production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+We will answer this question about how uncertainty drives evolution, including
+identifying regimes where evolution itself is highly uncertain and often 
+leads populations into suboptimal learning strategies~\cite{Rogers1988}.
 
 To gain a more systematic understanding of uncertainty and social learning evoluiton,
-we identified a set of common ecological
-uncertainty classes (``eigenvectors'' of uncertainty) used as factors
+we identified four common classes of ecological
+uncertainty (``principal components'' of uncertainty) used as factors
 in social learning evolution models: (1) environmental variability; (2) payoff
@@
 modeled as occurring with a fixed or variable
-probability~\cite{Feldman1996,McElreath2005}---in all these examples environments
+probability~\cite{Feldman1996,McElreath2005}---in these examples environments
 can only be in one of two states. Payoff ambiguity is sometimes in the form
@@
 in understanding the role of uncertainty. The age or lifespan of individuals was
-found to have an effect on social learning in both \emph{parus
+found to affect on social learning in both \emph{parus
 major}~\cite{Aplin2017} and \emph{poecilia reticulata} 
@@
   \item
+    One sentence on how dual-inheritance theory enables us to gloss over whether
+    social learning is genetically or culturally evolved.
+  \item
     More things from which we selected the operation of our model
@@
 
+\paragraph{Evolutionary ABMs for theory development} (PAUL, MATT)
+
 \paragraph{Research overview}
@@
 
-\paragraph{Model overview (introduce uncertainty variables)}
+To answer our research questions
+we developed an agent-based model of social learning evolution in which a society of
+$N$ individuals each must decide which of $B$ behaviors to perform at each time step
+within a generation of $L$ time steps. After each generation agents are selected
+with replacement from the population to reproduce another $N$ agents. Agents who
+inherit the social learning trait then learn about behavioral payoffs from the
+previous generation, while asocial learners begin life with no \emph{a priori}
+knowledge of the world.  Each behavior is a ``bandit'', a common modelling and
+experimental approach for representing behaviors with probabilistic
+payoffs~\cite{SuttonBartoBook,McElreath2005,Rendell2010,Schulz2019}.  Each behavior
+$b$ yields Bernoulli payoffs: payoff of 1 with probability $\pi_b$ and zero payoff
+with probability $1 - \pi_b$; $\pi_b$ is therefore also the expected payoff of
+behavior $b$. One behavior in each generation is optimal and pays off $\pihigh$,
+while the rest pay off $\pilow < \pihigh$.  Model agents must decide which behavior to
+perform at each time step.  To do this, agents use an explore-exploit strategy to
+sometimes try the most profitable behavior they know about, and other times try
+alternatives that may pay off more reliably.  We developed a series of computational
+analyses by systematically varying uncertainty parameters and observing the
+frequency that model populations evolve to be social learners, the average payoffs
+accrued by agents in each setting, and the time it takes for model populations to
+reach fixation (agents all social or all asocial learners).
 
-We developed an agent-based model of a society of $N$ individuals who each must decide
-which of $B$ behaviors to perform at each time step. Each behavior is a ``bandit'',
-a common modelling and experimental approach for representing behaviors with
-probabilistic payoffs~\cite{SuttonBartoBook,McElreath2005,Rendell2010,Schulz2019}. 
-Each behavior $b$ yields Bernoulli payoffs: payoff of 1 with probability $\pi_b$ and 
-zero payoff with probability $1 - \pi_b$; 
-$\pi_b$ is therefore also the expected payoff of behavior $b$. Agents must
-decide which behavior to perform at each time step. To do this, agents 
-use an explore-exploit strategy to sometimes try the most profitable behavior
-they know about, and other times try alternatives that may pay off more reliably.
+We identified four ``principal components'' of uncertainty that affect the
+ability of agents to find and choose the optimal behavior: 
+\emph{environmental variability}; \emph{payoff ambiguity}; \emph{selection set size}
+(number of behaviors environment affords); and the \emph{effective lifespan}.
+Environmental variability, denoted $u$, is the probability that the behavior
+yielding the optimal payoff, $\pihigh$, changes from one generation to the next.
+We operationalized payoff ambiguity by setting $\pihigh = 0.9$ for all analyses
+and varying $\pilow \in \{0.1, 0.45, 0.8\}$. The selection set size is the
+total number of possible behaviors agents choose from, denoted $B$. The 
+effective life span is the number of time steps agents live for, which is
+also the number of behaviors each agent performs each generation.
 
-\paragraph{Agents}
+To guide behavior selection, agent $i$ counts how many times it
+performed each behavior $b$, denoted $c_{ib}$. Agents use this count to 
+update the mean payoff they have obtained from behavior $b$, denoted $\ledger$.
+$\ledger$ is initialized to 0 for all $b$ at model initialization for
+all agents and after each generation for individual learner agents. Social
+learning agents' $\ledger$ is initialized as that of its teacher selected
+through performance-biased oblique learning. Agent $i$'s accumulated payoffs
+from performing several behaviors over their lifetime of $L$ time steps is
+denoted $\pi_{i}$. If an agent $i$ is a social learner, then we write $s_i = 1$,
+otherwise the agent is an asocial learner and $s_i = 0$.
 
-\paragraph{Dynamics: initialization, behaviors and payoffs, evolution}
+At the beginning of each simulation model dynamics begin with 
+one of the behaviors selected to 
+yield expected payoff $\pihigh$, with the other $B-1$ behavior yielding
+expected payoffs $\pilow$. At each time step, agents perform behavior $b$ 
+with softmax-weighted probability
+\begin{equation}
+  \Pr(\text{Agent $i$ performs behavior $b$}) = 
+    \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}},
+\end{equation}
+\noindent
+where $\beta$ is a parameter that adjusts how frequently agents perform 
+behaviors with high expected payoffs (larger $\beta$) versus how frequently
+agents explore alternative behaviors (smaller $\beta$). 
+Agents probabilistically recieve a payoff of 0 or 1 depending on whether the
+bandit paid off, equivalent to a draw from a Bernoulli distribution with 
+mean $\pi_b$. For concreteness we denote this probabilistic payoff
+$\bandit$. On performing behavior $b$, agent $i$ updates the
+corresponding behavior count by 1, $c_{ib} \leftarrow c_{ib} + 1$, and then
+the expected payoffs calculated for that behavior are updated with
+exponentially-weighted averaging
+\begin{equation}
+  \ledger \leftarrow \ledger + \frac{\bandit - \ledger}{c_{ib}}.
+\end{equation}
+\noindent
+This procedure continues for $L$ time steps within each generation.
 
-\paragraph{Computational analyses and outcome measures}
+In between generations agents first reproduce (asexual haploid reproduction); 
+then new child agents learn from the
+previous generation if they are social learners; and finally all agents from the
+previous generation then die off. $N$ reproducers are selected with replacement, 
+biased by performance:
+\begin{equation}
+  \Pr(\text{Agent $i$ is chosen to reproduce}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
+\end{equation}
+\noindent
+Child agents inherit their parents social learning trait $s_i$ without mutation.
+Child agents with $s_i = 1$ then learn from one teacher from their parent's
+generation, including possibly their parent. Child social learners select
+their teacher first by selecting $N_T$ prospective teachers from the 
+population completely at random, then selecting the one with highest
+net payoffs $\pi_i$ for as their teacher, with ties broken randomly 
+($N_T = 5$ in the main text;
+\mt{Other values will be tested in the supplement}). While it is somewhat
+arbitrary to first subset $N_T$, this is a conservative choice that
+represnts the fact that access to the entire population is not generally
+guaranteed. Social learners adopt their chosen teacher's ledger of 
+expected payoffs $\ledger$, and set
+all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$. 
+Asocial learners ($s_i = 0$) are initialized with all $c_{ib} = 0$ and
+$\ledger = 0$. The newly initialized population then begins behavior selection
+and payoff accumulation for another $L$ time steps and the evolutionary process
+continues until $\sum_i s_i = 1$ or $\sum_i s_i = 0$ \mt{I believe
+all trials will eventually end like this, so in the next set of model runs I will
+not allow early termination before one of these conditions are met}.
+
+To analyze the effect of the four principal uncertainty factors, we systematically
+varied their values and observed three key outcome variables aggregated across 1000
+trial simulations, and across all agents. Specifically we varied $u \in \{0.0,
+0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L
+\in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.  We observed
+three outcome measures: (1) $\meansl$, the average value of $s_i$ over all agents
+and trials; (2) $\meanpi / L$, the average net payoffs within agent lifetimes over
+trials, normalized by their lifespan; and (3) $\meanT / L$, or the mean number
+of time steps to fixation normalized by lifespan\footnote{Equivalent to the mean
+number of generations to fixation} 
+(fixation means $\sum_i s_i = 0 \text{ or } 1$). \mt{Make sure to qualitatively
+introduce these and their evolutionary importance in the intro.}
+We inspect the outcomes through visualization environmental
+variation is on the x-axis since it is the best understood: we expect that as $u$
+increases, social learning prevalence $\meansl \to 0$. We expected and observed
+that the other three uncertainty factors shift at which $u$ $\meansl$ starts to
+decrease, and how rapidly $\meansl$ decreases as $u$ increases. Note the
+hypothesis-testing concept of significance is meaningless here because we could
+make any small outcome difference significant by running more simulation trials.
+The important outcomes for this study are the patterns of our outcome 
+variables over the systematic variation of the uncertainty factors.
+
+\section{Analysis}
 

### 2022-05-21 meanNetPayoffs.tex
updated mean payoffs, step figs to use minipages and standalone

@@
-\begin{figure}
-  \caption{Dependence of average net payoff normalized by lifespan,
-    $\meanpi/L$, at the
-    end of last time step of the simulation on environmental
-    variability $u$ for several values of low payoff $\pilow$, number of
-    behaviors $B$, and lifespan $L$. Dashed lines mark expected 
-    payoff from individual learning $\langle \pi_I \rangle$ calculated
-    for each parameter setting (not sensitive to $u$). 
-    Note that when the maximum $L$ is 
-    8, the y-axis runs from 0 to 8, and when the maximum $L$ is 20, the y-axis
-    runs from 0 to 20. Average over 1000 trials.} 
-  \label{fig:meanNetPayoffs}
+\documentclass[varwidth=true,crop=false]{standalone}
+\usepackage[chatter]{rotating}
+\usepackage{amssymb,amsmath}
+\usepackage{pgfplots}
+
+\usepackage{geometry}
+\geometry{
+paperwidth=8in,
+paperheight=6.25in,
+margin=0.25in
+}
+
+\newcommand{\pisub}[1]{\pi_{\mathrm{#1}}}
+\newcommand{\pilow}{\pisub{low}}
+\newcommand{\pihigh}{\pisub{high}}
+\newcommand{\piI}{\langle \pisub{I} \rangle}
+\newcommand{\piS}{\langle \pisub{S} \rangle}
+\newcommand{\ledger}{\bar\pi_{ib}}
+
+\newcommand{\meanvar}[1]{\langle #1 \rangle}
+\newcommand{\meansl}{\meanvar{s}}
+\newcommand{\meanpi}{\meanvar{\pi}}
+\newcommand{\meansoc}{\meanvar{\pi_\mathrm{S}}}
+\newcommand{\meanasoc}{\meanvar{\pi_\mathrm{A}}}
+\newcommand{\meanT}{\meanvar{T}}
+
+\newcommand{\bandit}{\text{Bandit}_b(0, 1)}
+
+\begin{document}
+
+    \begin{minipage}{3.75in}
       \centering
-  \begin{subfigure}[t]{0.08\textwidth}
-    \begin{tikzpicture}
-      \draw[->,thick] (-.1,0)--(1,0) node[above]
-        {$B$};
-      \draw[->,thick] (0,.1)--(0,-1) node[below]
-        {$\pilow$};
-    \end{tikzpicture}
+      {\hspace{5.25em}\huge $B = 4$}
+    \end{minipage}%
+    \begin{minipage}{3.75in}
+      \centering
+      {\hspace{2.0em}\huge $B = 10$}
+    \end{minipage}~\\
 
-  \end{subfigure}%
-  \begin{subfigure}[t]{0.3\textwidth}
+    \begin{minipage}{3.75in}
+    \begin{rotate}{90}
+      {\parbox{2.5in}{
           \centering
-    {\large $B = 2$} 
-    \begin{rotate}{90}
-      {\parbox{4cm}{
-          \centering
-          \vspace{-3.5em}{\large $ \pilow = 0.1$} \\
-          {\begin{rotate}{-90}{\large $\frac{\meanpi}{L}$}\end{rotate}}
+          \vspace{-2.5em} {\huge$ \pilow = 0.1$} \\
+          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
       }}
     \end{rotate}%
-    \includegraphics[width=1.1\textwidth]{
-      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
-    }
+    \hspace{2em}
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
+    \end{minipage}\noindent\begin{minipage}{3.75in}%
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
+    \end{minipage}~\\[0.5em]
+
+    \begin{minipage}{3.75in}
+    \begin{rotate}{90}
+      {\parbox{2.5in}{
           \centering
-    \begin{rotate}{90}
-      {\parbox{4cm}{
-          \centering
-          \vspace{-3.5em} {\large$ \pilow = 0.45$} \\
-          {\begin{rotate}{-90}{\large $\frac{\meanpi}{L}$}\hspace{1em}\end{rotate}}
+          \vspace{-2.5em} {\huge$ \pilow = 0.45$} \\
+          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
       }}
     \end{rotate}%
-    \includegraphics[width=1.1\textwidth]{
-      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
-    }
-    \begin{rotate}{90}
-      {\parbox{4cm}{
-          \centering
-          \vspace{-3.5em} {\large $ \pilow = 0.8$} \\
-          {\begin{rotate}{-90}{\large $\frac{\meanpi}{L}$}\end{rotate}}
-      }}
-    \end{rotate}%
-    \includegraphics[width=1.1\textwidth]{
-      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
-    }\\[-.5em]
-    {\large $\quad u$}
-  \end{subfigure}%
-  \begin{subfigure}[t]{0.3\textwidth}
-    {\large $B = 4$}
-    \includegraphics[width=1.1\textwidth]{
-      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
-    } \\
-    \centering
-    \includegraphics[width=1.1\textwidth]{
-      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
-    } \\
-    \includegraphics[width=1.1\textwidth]{
-      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
-    }\\[-.5em]
-    {\large{$\quad u$}}
-  \end{subfigure}
-  \begin{subfigure}[t]{0.3\textwidth}
-    \centering
-    {\large $B = 10$}
-    \includegraphics[width=1.1\textwidth]{
-      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
-    } \\
-    \centering
-    \includegraphics[width=1.1\textwidth]{
-      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
-    } \\
-    \includegraphics[width=1.1\textwidth]{
-      {Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
-    } \\[-.5em]
-    {\large $\quad u$}
-  \end{subfigure}
-
-\end{figure}
+    \hspace{2em}
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
+        \\[-2.75em]
+        \begin{center}
+          {\hspace{3.25em} \huge $\quad u$}
+      \end{center}
+        \end{minipage}\noindent\begin{minipage}{3.75in}%
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+      \\[-2.75em]
+      \begin{center}
+        {\huge $\quad u$}
+      \end{center}
+    \end{minipage}
+\end{document}

### 2022-05-21 ms.tex
updated mean payoffs, step figs to use minipages and standalone

@@
 \usepackage[bookmarks, hidelinks]{hyperref}
-\usepackage[chatter]{rotating}
 \usepackage{amssymb,amsmath}
@@
 \usepackage{caption}
-\usepackage{subcaption}
-\usepackage{pgfplots}
+% \usepackage{subcaption}
 \usepackage{wrapfig}
@@
 
-To gain a more systematic understanding of uncertainty and social learning evoluiton,
-we identified four common classes of ecological
+\mt{This paragraph is a first try to introduce the four uncertainty dimensions
+with examples to illustrate the problem we are answering.
+I outlined the next paragraph to get into more details of social learning:
+how cultural evolution works; conformity, success-biased, etc. Cristina, please
+edit this.} 
+To gain a more systematic understanding of uncertainty and social learning
+evoluiton, we identified four common classes of ecological
 uncertainty (``principal components'' of uncertainty) used as factors
@@
 payoffs depending on experimental treatment; studies in humans have used two
-or three possible behaviors~\cite{McElreath2005,Toyokawa2019}; m
-odeling studies have used either two 
-behaviors~\cite{Feldman1996,Rendell2010} or four behaviors~\cite{Enquist2007} 
+or three possible behaviors~\cite{McElreath2005,Toyokawa2019}; 
+modeling studies have used two 
+behaviors~\cite{Feldman1996,Rendell2010} and four behaviors~\cite{Enquist2007} 
 in understanding the role of uncertainty. The age or lifespan of individuals was
@@
 
-\paragraph{Social learning evolution} (CRISTINA, PAUL)
+\paragraph{Social learning evolution} (CRISTINA)
 To add to confusion about how to integrate diverse models of social learning
@@
 
-\paragraph{Meaning of uncertainty in ecology and cognitive and social sciences} (JAMIE, PAUL)
+\paragraph{Meaning of uncertainty in ecology and cognitive and social sciences} (JAMIE)
 We need to support our claim that these four classes of uncertainty really 
@@
 
-\paragraph{Evolutionary ABMs for theory development} (PAUL, MATT)
-
-\paragraph{Research overview}
+\paragraph{ABMs for social learning evolution theory development} (PAUL)
 
@@
 
-In between generations agents first reproduce (asexual haploid reproduction); 
+In between generations agents first reproduce via asexual haploid reproduction; 
 then new child agents learn from the
@@
 varied their values and observed three key outcome variables aggregated across 1000
-trial simulations, and across all agents. Specifically we varied $u \in \{0.0,
+trial simulations, and across all agents. We varied $u \in \{0.0,
 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L
@@
 
-\paragraph{Disc. 1: Foundation for studying ssortative social learning}~\cite{Katsnelson2014}.
+\section{Discussion}
 
-\paragraph{Disc. 2: Applications to artificial
-intelligence}~\cite{Sandholm1996,Jaques2019,Ndousse2021,Gronauer2022}
+By identifying four common uncertainty dimensions we were able to develop a model
+that predicts how they might interact to foster or suppress social learning.
+The model reproduced classic predictions that social learning can yield higher
+payoffs than individual learning, but only up to some upper uncertainty bound.
+By disambiguating and organizing various operationalizations of \emph{uncertainty},
+we were able to add more detail to our theoretical understanding of which forms
+of uncertainty interact in which ways to make social learning more or less
+beneficial compared to asocial learning. When expected social learning payoffs
+approached asocial learning payoffs the system exhibited far stronger drift; when
+social or asocial learning were more obviously better the systems more consistently
+evolved to the more profitable state. Note that in many cases we made modeling choices
+that excluded some important mechanisms of social learning; for example we 
+assumed success-biased learning, although conformity is theoretically important
+as well~\cite{Muthukrishna2016a,Smaldino2018b}. Nonetheless, we believe our model
+advances theoretical parsimony; and the software implementation is designed to
+facilitate testing alternate modeling choices.
+
+\paragraph{Disc. 2: Foundation for studying social learning evolution with group
+structure (PAUL, JAMIE, CRISTINA)}~\cite{Katsnelson2014}.
+
+Our modeling approach may have applications to developing social artificial 
+intelligence. Much effort has gone in to developing the cognitive machinery
+to realize multi-agent reinforcement learning
+systems~\cite{Sandholm1996,Ndousse2021,Gronauer2022}, with some work explicitly
+incorporating cultural evolutionary approaches to social learning~\cite{Jaques2019}.
+However, it seems there are a lack of methods for adapting
+to environmental uncertainty, or determining when social learning is actually
+advantageous under different uncertainty conditions. Our model dynamics could
+be used as an evolutionary algorithm to update AI agents' social learning
+strategy without knowledge of the underlying uncertainty structure.
+Our model could also predict the expected benefit of social learning,
+which may be inherently costly in artificial multi-agent learning systems, 
+and how long the translated evolutionary algorithm may take to converge.
 

### 2022-05-22 ms.tex
updated figures; makefile

@@
 $N$ individuals each must decide which of $B$ behaviors to perform at each time step
-within a generation of $L$ time steps. After each generation agents are selected
+within a generation of $L$ time steps. At the end of each generation, agents are selected
 with replacement from the population to reproduce another $N$ agents. Agents who
@@
 previous generation, while asocial learners begin life with no \emph{a priori}
-knowledge of the world.  Each behavior is a ``bandit'', a common modelling and
+knowledge of the world.  Each behavior is a ``bandit'', a common modeling and
 experimental approach for representing behaviors with probabilistic
@@
 
-\paragraph{Analysis 1: patterns in social learning evolution over $u$}
+\begin{figure}
+  \caption{Social learning prevalence (y-axes) monotonically decreases as 
+  environmental variabilty, $u$, increases (x-axes) in most uncertainty contexts. 
+  Other uncertainty values $\pilow$ (rows), $B$ (columns), and $L$ (keys)
+  shift and flatten the decrease from all-social-learner populations to all-asocial 
+  populations.}
+  \label{fig:mainResults}
+  \centering
+    \includegraphics[width=\textwidth]{Figures/mainResultsPlots.pdf}
+\end{figure}
 
 \paragraph{Analysis 2: evolutionary uncertainty when $\meansoc \approx \meanasoc$}
+
+\begin{figure}
+  \caption{Mean payoff normalized for lifespan (y-axes, solid line with circles)
+    generally track either expected all-social-learners payoff ($\meansoc$, dash-dot
+    line with diamonds) or expected all-asocial payoff ($\meanasoc$, long dash
+    horizontal lines) as $u$ increases (x-axes). When $\meansl$ goes from 1 to
+  0 is when social learning payoffs approach individual learning payoffs due to
+increased environmental variability.} 
+  \label{fig:netPayoffs}
+\centering
+    \includegraphics[width=0.75\textwidth]{Figures/meanNetPayoffs.pdf}
+\end{figure}
+
+\begin{figure}
+  \caption{Average number of generations ($\meanT/L$, y-axes) for populations to fixate
+  where agents either all become social or all become asocial learners. As
+  $u$ increases (x-axes) models take longer to fixate due to drift, up to a point,
+but then fixation accelerates as individual learning becomes more obviously 
+superior. Increased $\pilow$ increases time to fixate; both $\pilow$ and $B$
+shift peak time to fixation over $u$.} 
+  \label{fig:steps}
+\centering
+    \includegraphics[width=0.75\textwidth]{Figures/stepResultsPlots.pdf}
+\end{figure}
 

### 2022-05-22 ms.tex
updated schematic and wrote first analysis paragraph

@@
 production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
-We will answer this question about how uncertainty drives evolution, including
+We will answer this question about how uncertainty drives social learning 
+evolution, including
 identifying regimes where evolution itself is highly uncertain and often 
@@
 
-To answer our research questions
-we developed an agent-based model of social learning evolution in which a society of
-$N$ individuals each must decide which of $B$ behaviors to perform at each time step
-within a generation of $L$ time steps. At the end of each generation, agents are selected
-with replacement from the population to reproduce another $N$ agents. Agents who
-inherit the social learning trait then learn about behavioral payoffs from the
-previous generation, while asocial learners begin life with no \emph{a priori}
-knowledge of the world.  Each behavior is a ``bandit'', a common modeling and
-experimental approach for representing behaviors with probabilistic
+To answer our research questions we developed an agent-based model of social
+learning evolution in which a society of $N$ individuals each must decide which of
+$B$ behaviors to perform at each time step within a generation of $L$ time steps. At
+the end of each generation, agents are selected with replacement from the population
+to reproduce another $N$ agents. Agents who inherit the social learning trait then
+learn about behavioral payoffs from the previous generation, while asocial learners
+begin life with no \emph{a priori} knowledge of the world.  Each behavior is a
+``bandit'', a common modeling and experimental approach for representing behaviors
+with probabilistic
 payoffs~\cite{SuttonBartoBook,McElreath2005,Rendell2010,Schulz2019}.  Each behavior
@@
 behavior $b$. One behavior in each generation is optimal and pays off $\pihigh$,
-while the rest pay off $\pilow < \pihigh$.  Model agents must decide which behavior to
-perform at each time step.  To do this, agents use an explore-exploit strategy to
+while the rest pay off $\pilow < \pihigh$.  Model agents must decide which behavior
+to perform at each time step.  To do this, agents use an explore-exploit strategy to
 sometimes try the most profitable behavior they know about, and other times try
@@
 accrued by agents in each setting, and the time it takes for model populations to
-reach fixation (agents all social or all asocial learners).
+reach fixation (agents all social or all asocial learners). Model dynamics are
+illustrated in Figure~\ref{fig:schematic}.
+
+\begin{figure}
+  \caption{Agents are initialized as randomly social learners or not, with their
+  payoff observations all initialized to zero (A). Then agents begin selecting
+and performing behaviors and accumulating payoffs (1), which goes on for $L$
+timesteps (B). After $L$ time steps (2), agents are selected to reproduce,
+social learner children learn from a member of their parent's generation, and
+the previous generation dies off (C). Stop the simulation if children are all
+social or asocial learners, otherwise repeat another generation and evolution (3).}
+  \label{fig:schematic}
+  \centering
+    \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+\end{figure}
 
@@
 introduce these and their evolutionary importance in the intro.}
-We inspect the outcomes through visualization environmental
-variation is on the x-axis since it is the best understood: we expect that as $u$
-increases, social learning prevalence $\meansl \to 0$. We expected and observed
+We inspect the outcomes through by plotting $\meansl$ on the y-axis and environmental
+variation is on x-axis, since it is the best understood: we expect that as $u$
+increases, $\meansl$ starts at 1 and goes to 0. We expected and observed
 that the other three uncertainty factors shift at which $u$ $\meansl$ starts to
-decrease, and how rapidly $\meansl$ decreases as $u$ increases. Note the
+decrease, and how rapidly $\meansl$ decreases as $u$ increases. Note that the
 hypothesis-testing concept of significance is meaningless here because we could
@@
 variables over the systematic variation of the uncertainty factors. 
+Our model was implemented in the Julia programming language~\cite{Bezanson2017} 
+using the Agents.jl agent-based modeling library~\cite{Datseris2022} and run
+on the Sherlock supercomputing cluster at Stanford University. Model code and
+data are publicly available on GitHub\footnote{\url{https://github.com/mt-digital/UncMod}} 
+and OSF.io\footnote{\mt{TODO}}.
 
 \section{Analysis}
+
+We observed several patterns in the suppression of social learning as environmental
+variability, $u$, increased across different uncertainty contexts defined by the
+payoff ambiguity, selection set size, and effective lifespan
+(Figure~\ref{fig:mainResults}). When payoff ambiguity and selection set size
+were both small ($\pilow = 0.1$ and $B=2$) social learning only evolved when
+$u$ is small since individual learning is relatively efficient in this case
+(Figure~\ref{fig:mainResults} upper left). As $\pilow$ increased the suppression of
+$\meansl$ flattened over $u$, which was more pronounced for smaller $L$ (rows of
+Figure~\ref{fig:mainResults}). 
+When $L$ is smaller, agents have fewer opportunities to learn through trial and
+error, and so it is more difficult for them to discern which strategy, social
+or asocial, is optimal. Increased selection set size led to both a shift in 
+the critical value of $u$ when $\meansl$ begins to decrease, and flattening of
+this social learning suppression. The start of $\meansl$ suppression shifts
+to higher $u$ since misleading social information is less consequential due to
+(1) larger $B$ being a more difficult problem for trial-and-error learning and
+(2) less probability mass of a misidentified optimal behavior relative to
+smaller $B$, meaning agents are more likely to explore behaviors identified
+as non-optimal (columns of Figure~\ref{fig:mainResults}). 
+Increased $B$ led to more pronounced flattening of social learning
+suppression when $L$ was small, apparently again because of the limited data
+available to evolution and more difficult problem caused more drift.
 
@@
 
-\paragraph{Analysis 2: evolutionary uncertainty when $\meansoc \approx \meanasoc$}
+\paragraph{Analysis 2: how payoffs and generations to convergence support our
+explanations}
 
 \begin{figure}
-  \caption{Mean payoff normalized for lifespan (y-axes, solid line with circles)
+  \caption{Mean payoff normalized for lifespan (y-axes, solid lines with circles)
     generally track either expected all-social-learners payoff ($\meansoc$, dash-dot

### 2022-05-22 ms.tex
first full methods, analysis, +, draft

@@
   payoff observations all initialized to zero (A). Then agents begin selecting
-and performing behaviors and accumulating payoffs (1), which goes on for $L$
-timesteps (B). After $L$ time steps (2), agents are selected to reproduce,
+and performing behaviors and accumulating payoffs, which goes on for $L$
+timesteps (B). After $L$ time steps, agents are selected to reproduce,
 social learner children learn from a member of their parent's generation, and
-the previous generation dies off (C). Stop the simulation if children are all
-social or asocial learners, otherwise repeat another generation and evolution (3).}
+the previous generation dies off (C). The simulation stops if children are all
+social or asocial learners (i.e.\ the system reaches fixation), 
+otherwise repeat another generation and evolution (3).}
   \label{fig:schematic}
@@
 \noindent
-Child agents inherit their parents social learning trait $s_i$ without mutation.
+Child agents inherit their parent's social learning trait $s_i$ without mutation.
 Child agents with $s_i = 1$ then learn from one teacher from their parent's
@@
 suppression when $L$ was small, apparently again because of the limited data
-available to evolution and more difficult problem caused more drift.
+available to evolution and more difficult problem caused more drift and individual
+outcomes were more path dependent.
 
@@
 
-\paragraph{Analysis 2: how payoffs and generations to convergence support our
-explanations}
+We observed that the evolution of social learning was correlated with
+population-level payoffs for social versus asocial learning. Furthermore, we
+found that mean payoffs realized by our simulated agents track either the
+expected social learning payoffs, $\meansoc$, or the expected asocial learning
+payoffs, $\meanasoc$. $\meanasoc$ and $\meansoc$ were calculated
+across uncertainty contexts by initializing the model to be all social or all
+individual learners then running the model for 100 generations for social learning
+and across 1000 one-generation trials for individual learning. 
+Observed mean payoffs across agents and trials, $\meanpi$, are initially higher than
+expected asocial learning, $\meanasoc$, and comparable to expected social learning,
+$\meansoc$ (Figure~\ref{fig:payoffs}). But as social learning becomes less
+beneficial due to increased environmental variability, $\meansoc$ and $\meanpi$
+approach $\meanasoc$. It appears agents tend to be conservative as expected
+social and asocial learning payoffs approach each other---the transition to 
+$\meansl = 0$ often completes in cases where social learning is theoretically
+better. When $L=1$, $\meanpi$ can be greater than $\meansoc$
+because asocial learners at the beginning of the simulation help to not pass
+on misleading information, so that the cultural information passed on by 
+eventual all-social learner populations have more noise that will further reduce the
+weighting of the previous generation's observed optimal payoff if it changes
+between generations enabling agents to more efficiently explore alternatives
+before focusing on a misidentified optimal behavior \mt{I think we can do a
+real calculation of this if it would be valuable}.
 
@@
 increased environmental variability.} 
-  \label{fig:netPayoffs}
+  \label{fig:payoffs}
 \centering
@@
 \end{figure}
+
+We also observed that the number of generations it took to reach fixation increased
+when expected social learning payoffs approached expected asocial payoff, which is also
+when $\meansl$ decreased from 1 to 0 (Figure~\ref{fig:steps}). Recall a fixated
+state is when $\sum_i s_i = 0 \text{ or } 0$.  This supports our explanation that
+the supression of social learning begins when individual simulation outcomes are
+more path dependent and susceptible to end in a non-optimal state since simulations
+in these conditions also take longer to reach fixation.  For example, when
+$\pilow=0.1$ and $B=4$, we see a sharp increase in $\meanT$ when social learning
+suppression begins and $L=8$; when $L=1$, social learning suppression is flatter
+than for $L=8$, and  correspondingly its $\meanT$ is not as strongly peaked, but is
+elevated across the $u$ (Figure~\ref{fig:steps} upper left).  In some cases $L=1$
+reaches fixation faster than $L=8$ or $L=20$; larger $L$ had larger peak $\meanT/L$
+than smaller $L$, for example, both for the cases shown in Figure~\ref{fig:steps}
+and across all settings tested but not shown. However, we also see situations where
+$L=1$ and fixation takes longer than $L=8$.  This is especially pronounced for
+$\pilow = 0.45$ where social learning suppression is much flatter for $L=1$
+(Figure~\ref{fig:steps}, bottom row). In general, then, a sharper peak in $\meanT$
+indicates a sharper suppression of social learning over $u$ and a flatter peak
+elevated over more values of $u$ indicates greater path dependence and drift.
 

### 2022-05-23 ms.tex
complete model and analysis; stubbed rest with new figs and old tables

--- 2022-05-22 ms.tex
@@
 Social learning is essential to survival. It is likely to evolve when it is more
-efficient than asocial, trial-and-error learning. Theoretically, some uncertainty is
-necessary for social learning to be necessary, but too much uncertainty makes
-social information useless. This fact is empirically
-supported across biology and human sciences. However, we lack a theoretical
-framework to predict the effects of specific classes and types of uncertainty on social
+efficient than asocial, trial-and-error learning. Theoretically, social learning
+is adaptive for some uncertainty, but too much uncertainty makes
+social information unreliable. This fact is empirically
+supported across biology and human sciences. However, it is unclear how
+specific classes and types of uncertainty affect social
 learning evolution. Furthermore, existing models and experimental operationalizations of
 uncertainty are ambiguously related, and 
-tend to only consider a small number of sources of uncertainty and behavioral
+tend to only consider a small number of behavioral
 choices.  Here we use evolutionary agent-based modeling to consolidate
-models of uncertainty in social learning evolution to improve on these
-shortcomings. We model a time-varying environment with a varying number
-of possible behaviors agents could perform to acquire payoffs.
-We show that environmental variability, ambiguous payoffs, 
-larger decision sets, and shorter agent lifespans interact to 
-affect social learning evolution in complex ways that 
-sometimes caused evolution to be highly uncertain about whether social learning was
-the optimal strategy. 
-Our work strengthens social evolution theory that could help 
+models of uncertainty in social learning evolution to address these issues.
+We model societies of agents who perform one of a number
+of possible behaviors to acquire payoffs in a time-varying environment.
+We identified complex patterns in social learning evolution depending on contextual
+uncertainty variables: environmental variability, ambiguous payoffs, 
+decision sets size, and effective lifespans. 
+Our work advances social learning evolution theory in a way that could help 
 guide human, non-human, and artificial intelligence towards optimal responses 
@@
 Social learning is essential to human and other species' everyday life and survival.
-It allows individuals to solve problems when acquiring information from others is
+Social learning enhances problem solving when acquiring information from others is
 more efficient than learning on one's own~\cite{Laland2004}. Theory predicts that
-social learning should be favored in contexts with greater
-uncertainty~\cite{BoydRicherson1985,Henrich1998}, up to a
+social learning should be favored in uncertain
+environments~\cite{BoydRicherson1985,Henrich1998}, up to a
 point~\cite{Rogers1988,Feldman1996}; this prediction has received some empirical
@@
 meaning of the term \emph{uncertainty} often conflates environmental variability,
-spatial heterogeneity, ambiguity or uncertainty about payoff structure, and other
-variability that could be plausibly interpreted as \emph{uncertainty}.  Many models
-of social learning evolution do not account for 
-individual-level cognition~\cite{Heyes2016}, though humans
-clearly have evolved cognitive mechanisms for dealing with 
-uncertainty generally~\cite{Gershman2019,Schulz2019}.
-Furthermore, social learning evolution theory tends to be organized around an
-increasing number of modeling choices~\cite[Figure 1]{Kendal2018} instead
-of around broader contextual assumptions such as uncertainty conditions. It remains
-an outstanding question, then, to identify how different contexts and forms of
-uncertainty might combine to affect social learning evolution in complex ways.
-Answering this question is critical for understanding human behavior adapting to a
-rapidly changing world, both to mitigate existential
-threats~\cite{Moya2020,Jones2021}, and to captialize on new opportunities such as
-transitioning to clean energy use and
+spatial heterogeneity, ambiguity in behavioral payoff structure, and other
+variability that could plausibly be interpreted as \emph{uncertainty}.  Furthermore,
+many models of social learning evolution do not account for individual-level
+cognition~\cite{Heyes2016}, though humans clearly have evolved cognitive mechanisms
+for dealing with uncertainty generally~\cite{Vul2014,Gershman2019,Schulz2019}.
+Social learning evolution theory tends to be organized around an increasing number
+of modeling choices~\cite[Figure 1]{Kendal2018} instead of around questions of when
+and why social learning is adaptive, in which contexts.  Therefore, we developed
+an evolutionary, empirically-motivated, agent-based model that operationalized
+four principal uncertainty components to generate predictions of when 
+social learning would evolve in which circumstances, and why. Answering this
+question is critical for understanding human behavior adapting to a rapidly changing
+world, both to mitigate existential threats~\cite{Moya2020,Jones2021}, and to
+captialize on new opportunities such as transitioning to clean energy use and
 production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
-We will answer this question about how uncertainty drives evolution, including
-identifying regimes where evolution itself is highly uncertain and often 
-leads populations into suboptimal learning strategies~\cite{Rogers1988}.
 
@@
 probability~\cite{Feldman1996,McElreath2005}---in these examples environments
-can only be in one of two states. Payoff ambiguity is sometimes in the form
+can only be in one of two states. Payoff ambiguity sometimes takes the form
 of differences in expected payoffs arising from different
@@
 or by varying the standard deviation of payoffs~\cite{McElreath2005}. 
-Selection set size is often limited to one size throughout social learning
-evolution studies: empirical studies of \emph{bombus terresteris} (bumble
-bee)~\cite{Baracchi2018} and \emph{parus major} (great tit)~\cite{Aplin2017}
-populations each provided two behaviors for
-the bees and birds to perform, each yielding greater or smaller
-payoffs depending on experimental treatment; studies in humans have used two
-or three possible behaviors~\cite{McElreath2005,Toyokawa2019}; 
-modeling studies have used two 
-behaviors~\cite{Feldman1996,Rendell2010} and four behaviors~\cite{Enquist2007} 
-in understanding the role of uncertainty. The age or lifespan of individuals was
+Selection set size often takes only one value: 
+for example, in empirical studies of \emph{bombus terresteris} (bumble
+bee)~\cite{Baracchi2018} and \emph{parus major} (great tit)~\cite{Aplin2017},
+experimenters provided two behaviors for
+the bees or birds to perform, respectively, each yielding greater or smaller
+payoffs depending on experimental treatment. Human studies have used two
+or three possible behaviors~\cite{McElreath2005,Toyokawa2019}.
+Modeling studies have used two 
+behaviors~\cite{Feldman1996,Rendell2010} and four behaviors~\cite{Enquist2007}. 
+The age or lifespan of individuals was
 found to affect on social learning in both \emph{parus
@@
 
-\paragraph{Meaning of uncertainty in ecology and cognitive and social sciences} (JAMIE)
+\paragraph{Meaning of uncertainty in ecology and cognitive and social sciences } (JAMIE)
 We need to support our claim that these four classes of uncertainty really 
-count as forms of uncertainty and show how it is consistent across ecology and
-cognitive and social science.
+count as forms of uncertainty and show how it is consistent across ecology,
+and maybe connect to uncertainty in cognitive and social sciences more broadly.
 
-\paragraph{ABMs for social learning evolution theory development} (PAUL)
+\paragraph{Evolutionary ABMs for social learning evolution theory development} (PAUL)
 
@@
 
-To answer our research questions
-we developed an agent-based model of social learning evolution in which a society of
-$N$ individuals each must decide which of $B$ behaviors to perform at each time step
-within a generation of $L$ time steps. At the end of each generation, agents are selected
-with replacement from the population to reproduce another $N$ agents. Agents who
-inherit the social learning trait then learn about behavioral payoffs from the
-previous generation, while asocial learners begin life with no \emph{a priori}
-knowledge of the world.  Each behavior is a ``bandit'', a common modeling and
-experimental approach for representing behaviors with probabilistic
+\begin{table}[h]
+    \caption{Dynamic agent-level variables. Each has an implicit time dependence.}
+    \label{tab:modelParameters}
+    \centering %\hspace{-3em}
+    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule
+
+        Attribute & Description & Initial value \\
+
+        \midrule
+
+        $s_i$  & Social learner trait: 1 if agent $i$ is social learner; 0 otherwise & 0
+        or 1 equally likely \\
+
+        $\bar\pi_{ib}$ & ``Ledger'': mean payoffs acquired via behavior $b$ by $i$ 
+                       & $B$-vector of zeros \\
+
+        $c_{ib}$ & Count of how many times agent $i$ performed $b$ 
+              & $B$-vector of zeros \\
+
+        $\pi_i$ & Net payoffs accumulated by $i$ within generation
+                                & 0.0 \\
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+To answer our research questions we developed an agent-based model of social
+learning evolution in which a society of $N$ individuals each must decide which of
+$B$ behaviors to perform at each time step within a generation of $L$ time steps. At
+the end of each generation, agents are selected with replacement from the population
+to reproduce another $N$ agents. Agents who inherit the social learning trait then
+learn about behavioral payoffs from the previous generation, while asocial learners
+begin life with no \emph{a priori} knowledge of the world.  Each behavior is a
+``bandit'', a common modeling and experimental approach for representing behaviors
+with probabilistic
 payoffs~\cite{SuttonBartoBook,McElreath2005,Rendell2010,Schulz2019}.  Each behavior
@@
 accrued by agents in each setting, and the time it takes for model populations to
-reach fixation (agents all social or all asocial learners).
+reach fixation (agents all social or all asocial learners). Model dynamics are
+illustrated in Figure~\ref{fig:schematic}.
+
+\begin{figure}
+  \caption{Agents are initialized as randomly social learners or not, with their
+  payoff observations all initialized to zero (A). Then agents begin selecting
+and performing behaviors and accumulating payoffs, which goes on for $L$
+timesteps (B). After $L$ time steps, agents are selected to reproduce,
+social learner children learn from a member of their parent's generation, and
+the previous generation dies off (C). The simulation stops if children are all
+social or asocial learners (i.e.\ the system reaches fixation), 
+otherwise repeat another generation and evolution (3).}
+  \label{fig:schematic}
+  \centering
+    \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+\end{figure}
 
@@
 
+\vspace{2em}
+\begin{table}[h]
+    \caption{Global environmental and cognitive initialization parameters.
+      Bold indicates \emph{default value tested}.
+    \mt{TODO: Test more $N_\text{T}$ for sensitivity analysis}}
+    \label{tab:modelParameters}
+    \centering %\hspace{-3em}
+    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule
+
+        Symbol & Description & Values tested \\
+
+        \midrule
+
+        $B$       & Number of possible behaviors (represented by ``bandits'') 
+                  & 2, 4, 10 \\
+
+        $\pihigh$ & Probability that the unique optimal behavior pays off 1 
+                & \textbf{0.9} \\
+
+        $\pilow$ & Probability one of $B - 1$ non-optimal behaviors pays off 1 
+                 & 0.1, 0.45, 0.8 \\
+
+        $\tau$ & Softmax temp.; $\uparrow=$more exploration, $\downarrow=$more
+                    exploitation 
+               & 0.01, \textbf{0.1}, 1.0 \\
+
+        $u$    & Probability optimal behavior changes between generations 
+               & 0.0, 0.1, \ldots, 1.0 \\
+
+        $L$    & Number of time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
+
+        $N_T$    & Number of teachers to pool, from which best selected 
+                 & \textbf{5}  \\
+
+        \bottomrule
+        \end{tabular} 
+\end{table}
+
 To guide behavior selection, agent $i$ counts how many times it
@@
 update the mean payoff they have obtained from behavior $b$, denoted $\ledger$.
-$\ledger$ is initialized to 0 for all $b$ at model initialization for
-all agents and after each generation for individual learner agents. Social
-learning agents' $\ledger$ is initialized as that of its teacher selected
-through performance-biased oblique learning. Agent $i$'s accumulated payoffs
-from performing several behaviors over their lifetime of $L$ time steps is
-denoted $\pi_{i}$. If an agent $i$ is a social learner, then we write $s_i = 1$,
-otherwise the agent is an asocial learner and $s_i = 0$.
+$\ledger$ is initialized to 0 for all $b$ at model start for
+all agents (Figure~\ref{fig:schematic}A), and at 
+generation start for asocial learners. Social
+learning agents' $\ledger$ is initialized as that of its teacher, who is selected
+through performance-biased oblique learning; $c_ib$ is set to 1 for all social
+learners $i$ and behaviors $b$ (Figure~\ref{fig:schematic}C). Agent $i$'s
+accumulated payoffs from performing several behaviors over their lifetime of $L$
+time steps is denoted $\pi_{i}$. If an agent $i$ is a social learner, then we write
+$s_i = 1$, otherwise the agent is an asocial learner and $s_i = 0$.
 
-At the beginning of each simulation model dynamics begin with 
-one of the behaviors selected to 
-yield expected payoff $\pihigh$, with the other $B-1$ behavior yielding
+At generation start, one of the behaviors is set to 
+yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
 expected payoffs $\pilow$. At each time step, agents perform behavior $b$ 
@@
 behaviors with high expected payoffs (larger $\beta$) versus how frequently
-agents explore alternative behaviors (smaller $\beta$). 
+agents explore alternative behaviors (smaller $\beta$)~\cite{McElreath2005}. 
 Agents probabilistically recieve a payoff of 0 or 1 depending on whether the
@@
 \noindent
-This procedure continues for $L$ time steps within each generation.
+This procedure continues for $L$ time steps within each generation
+(Figure~\ref{fig:schematic}B).
 
@@
 previous generation if they are social learners; and finally all agents from the
-previous generation then die off. $N$ reproducers are selected with replacement, 
+previous generation then die off (Figure~\ref{fig:schematic}C). 
+$N$ reproducers are selected with replacement over $N$ independent draws, 
 biased by performance:
 \begin{equation}
-  \Pr(\text{Agent $i$ is chosen to reproduce}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
+  \Pr(\text{Agent $i$ is chosen to reproduce in one draw}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
 \end{equation}
 \noindent
-Child agents inherit their parents social learning trait $s_i$ without mutation.
-Child agents with $s_i = 1$ then learn from one teacher from their parent's
-generation, including possibly their parent. Child social learners select
-their teacher first by selecting $N_T$ prospective teachers from the 
-population completely at random, then selecting the one with highest
-net payoffs $\pi_i$ for as their teacher, with ties broken randomly 
-($N_T = 5$ in the main text;
-\mt{Other values will be tested in the supplement}). While it is somewhat
-arbitrary to first subset $N_T$, this is a conservative choice that
-represnts the fact that access to the entire population is not generally
-guaranteed. Social learners adopt their chosen teacher's ledger of 
-expected payoffs $\ledger$, and set
-all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$. 
-Asocial learners ($s_i = 0$) are initialized with all $c_{ib} = 0$ and
-$\ledger = 0$. The newly initialized population then begins behavior selection
-and payoff accumulation for another $L$ time steps and the evolutionary process
-continues until $\sum_i s_i = 1$ or $\sum_i s_i = 0$ \mt{I believe
-all trials will eventually end like this, so in the next set of model runs I will
-not allow early termination before one of these conditions are met}.
+A child inherits its parent's social learning trait $s_i$ without mutation.
+A social learner child with $s_i = 1$ learns from a teacher from its parent's
+generation, including possibly their parent (oblique learning). 
+A child selects its teacher by first selecting $N_T$ prospective
+teachers from the population completely at random, then selecting the one with
+highest net payoffs $\pi_i$ as their teacher, with ties broken randomly ($N_T =
+5$ in the main text; \mt{Other values will be tested in the supplement}). While it
+is somewhat arbitrary to first subset $N_T$, this is a conservative choice that
+represnts the fact that access to the entire population is not generally guaranteed.
+Social learners adopt their chosen teacher's ledger of expected payoffs $\ledger$,
+and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$.  Asocial
+learners ($s_i = 0$) are initialized with all $c_{ib} = 0$ and $\ledger = 0$ 
+(Figure~\ref{fig:schematic}C). The
+newly initialized population then begins behavior selection and payoff accumulation
+for another $L$ time steps. The evolutionary process continues until $\sum_i s_i
+= 1$ or $\sum_i s_i = 0$ \mt{I believe all trials will eventually end like this, so
+in the next set of model runs I will not allow early termination before one of these
+conditions are met}.
+
+\begin{table}[h]
+    \caption{Outcome variables.}
+    \label{tab:outcomeVariables}
+    \centering %\hspace{-3em}
+    \begin{tabular}{cp{4.25in}p{0.85in}} \toprule
+
+        Symbol & Description & Values \\
+
+        \midrule
+
+        $\meansl$ & Mean social learning prevalence over agents and trials
+                  & $\in [0.0, 1.0]$ \\
+
+        $\meanpi / L$ & Mean payoffs accumulated in a generation normalized by
+        lifespan & $\in [0.0, 1.0]$ \\
+
+        $\meanT / L$ & Mean number of generations to convergence & 20k / 8 max. \\
+        \bottomrule
+    \end{tabular}
+\end{table}
 
@@
 varied their values and observed three key outcome variables aggregated across 1000
-trial simulations, and across all agents. We varied $u \in \{0.0,
+trial simulations, and across all agents when appropriate. We varied $u \in \{0.0,
 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L
@@
 three outcome measures: (1) $\meansl$, the average value of $s_i$ over all agents
-and trials; (2) $\meanpi / L$, the average net payoffs within agent lifetimes over
-trials, normalized by their lifespan; and (3) $\meanT / L$, or the mean number
-of time steps to fixation normalized by lifespan\footnote{Equivalent to the mean
-number of generations to fixation} 
+and trials; (2) $\meanpi / L$, the average net payoffs at simulation end across
+agents and trials, normalized by lifespan; and (3) $\meanT / L$, 
+or the mean number of time steps to fixation normalized by
+lifespan\footnote{Equivalent to the mean number of generations to fixation}
 (fixation means $\sum_i s_i = 0 \text{ or } 1$). \mt{Make sure to qualitatively
 introduce these and their evolutionary importance in the intro.}
-We inspect the outcomes through visualization environmental
-variation is on the x-axis since it is the best understood: we expect that as $u$
-increases, social learning prevalence $\meansl \to 0$. We expected and observed
-that the other three uncertainty factors shift at which $u$ $\meansl$ starts to
-decrease, and how rapidly $\meansl$ decreases as $u$ increases. Note the
+We analyze outcomes by plotting $\meansl$ on the y-axis and environmental
+variation is on x-axis since we theoretically expect that $\meansl$ will 
+decrease monotonically from 1 to 0 as $u$ increases. We expected and observed
+that the other three uncertainty factors shift the value of $u$ at which 
+$\meansl$ starts to decrease, and how rapidly $\meansl$ decreases. Note that the
 hypothesis-testing concept of significance is meaningless here because we could
-make any small outcome difference significant by running more simulation trials.
-The important outcomes for this study are the patterns of our outcome 
-variables over the systematic variation of the uncertainty factors.
+make any small outcome difference ``significant'' by running more simulation trials.
+We instead study the patterns of outcome 
+variables over systematically varied uncertainty factor values. 
+Our model was implemented in the Julia programming language~\cite{Bezanson2017} 
+using the Agents.jl agent-based modeling library~\cite{Datseris2022} and run
+on the Sherlock supercomputing cluster at Stanford University. Model code and
+data are publicly available on GitHub\footnote{\url{https://github.com/mt-digital/UncMod}} 
+and OSF.io\footnote{\mt{TODO}}.
 
 \section{Analysis}
+
+Several patterns emerged in changes to the shape of social learning suppression over
+environmental variability, $u$, across different uncertainty contexts defined by the
+payoff ambiguity, selection set size, and effective lifespan
+(Figure~\ref{fig:mainResults}). When payoff ambiguity and selection set size were
+both small ($\pilow = 0.1$ and $B=2$) social learning only evolved when $u$ is small
+since individual learning is relatively efficient in this case
+(Figure~\ref{fig:mainResults}, upper left). As $\pilow$ increased the suppression of
+$\meansl$ flattened over $u$, which was more pronounced for smaller $L$ (rows of
+Figure~\ref{fig:mainResults}).  When $L$ is smaller, agents have fewer opportunities
+to learn through trial and error, and so it is more difficult for them to discern
+which strategy, social or asocial, is optimal. Increased selection set size led to
+both a shift in the critical value of $u$ when $\meansl$ begins to decrease, and
+flattened social learning suppression. This is because possibly misleading 
+social information is less consequential due
+to (1) larger $B$ is a more difficult problem for trial-and-error learning and
+(2) a misidentified optimal behavior is weighted less relative to smaller
+$B$, meaning agents are more likely to explore behaviors identified as non-optimal
+when $B$ is larger (columns of Figure~\ref{fig:mainResults}).  
+Increased $B$ led to more pronounced flattening of social learning suppression when
+$L$ was small, apparently again because of the limited data available to evolution,
+making individual outcomes more path dependent.
 
@@
 
-\paragraph{Analysis 2: evolutionary uncertainty when $\meansoc \approx \meanasoc$}
+Social learning evolution was correlated with differences in population-level
+expected payoffs for social versus asocial learning. Furthermore, we found that mean
+payoffs realized by our simulated agents track either the expected social learning
+payoffs, $\meansoc$, or the expected asocial learning payoffs, $\meanasoc$.
+$\meansoc$ and $\meanasoc$ were calculated across uncertainty contexts by
+initializing the model to be all social or all individual learners then running the
+model for 100 generations for social learning and across 1000 one-generation trials
+for individual learning.  Simulated evolutionary mean payoffs across agents and
+trials, $\meanpi$, are initially higher than expected asocial learning, $\meanasoc$,
+and comparable to expected social learning, $\meansoc$, in most cases 
+(Figure~\ref{fig:payoffs}).  But as social learning becomes less beneficial due to
+increased environmental variability, $\meansoc$ and $\meanpi$ approach $\meanasoc$.
+It appears agents tend
+to be conservative as expected social and asocial learning payoffs approach each
+other---the transition to $\meansl = 0$ often happens although social
+learning is still theoretically optimal. When $L=1$, $\meanpi$ can be greater than
+$\meansoc$ because asocial learners at the beginning of the simulation help to 
+pass on less misleading information on average, so that the cultural information passed on by
+eventual all-social learner populations have more noise. This noise further reduces the
+weighting of the previous generation's observed optimal payoff if it changes between
+generations enabling agents to more efficiently explore alternatives before focusing
+on a misidentified optimal behavior \mt{I think we could calculate this if it were
+valuable}.
 
 \begin{figure}
-  \caption{Mean payoff normalized for lifespan (y-axes, solid line with circles)
+  \caption{Mean payoff normalized for lifespan (y-axes, solid lines with circles)
     generally track either expected all-social-learners payoff ($\meansoc$, dash-dot
@@
 \end{figure}
+
+The number of generations to reach fixation increased
+when expected social learning payoffs approached expected asocial payoffs, i.e.,
+when $\meansl$ becomes suppressed (Figure~\ref{fig:steps}). Recall a fixated
+state is when $\sum_i s_i = 0 \text{ or } 1$.  This supports our explanation that
+the supression of social learning begins when individual simulation outcomes are
+more path dependent and susceptible to end in a non-optimal state since simulations
+in these conditions also take longer to reach fixation.  For example, when
+$\pilow=0.1$, $B=4$, and $L=8$, we see a sharp increase in $\meanT$ when social learning
+suppression begins; but when $L=1$, social learning suppression is flatter
+than for $L=8$, and  correspondingly its $\meanT$ is not as strongly peaked, but is
+elevated across the $u$ (Figure~\ref{fig:steps} upper left).  In some cases $L=1$
+trials reached fixation faster than $L=8$ or $L=20$; larger $L$ had larger peak $\meanT/L$
+than smaller $L$, for example, both for the cases shown in Figure~\ref{fig:steps}
+and across all settings tested \mt{TODO: add full figure to SI}. 
+However, we also see situations where $L=1$ and fixation takes longer than $L=8$.
+This is especially pronounced for
+$\pilow = 0.45$ where social learning suppression is much flatter for $L=1$
+(Figure~\ref{fig:steps}, bottom row). In general, then, a sharper peak in $\meanT$
+indicates a sharper suppression of social learning over $u$ and a flatter peak,
+elevated over more values of $u$, indicates greater path dependence and more 
+drift overall.
 
@@
 
-By identifying four common uncertainty dimensions we were able to develop a model
-that predicts how they might interact to foster or suppress social learning.
-The model reproduced classic predictions that social learning can yield higher
-payoffs than individual learning, but only up to some upper uncertainty bound.
-By disambiguating and organizing various operationalizations of \emph{uncertainty},
-we were able to add more detail to our theoretical understanding of which forms
-of uncertainty interact in which ways to make social learning more or less
-beneficial compared to asocial learning. When expected social learning payoffs
-approached asocial learning payoffs the system exhibited far stronger drift; when
-social or asocial learning were more obviously better the systems more consistently
-evolved to the more profitable state. Note that in many cases we made modeling choices
-that excluded some important mechanisms of social learning; for example we 
-assumed success-biased learning, although conformity is theoretically important
-as well~\cite{Muthukrishna2016a,Smaldino2018b}. Nonetheless, we believe our model
+By identifying four common uncertainty dimensions we developed a model that predicts
+how different forms of uncertainty might interact to foster or suppress social
+learning.  The model reproduced classic predictions that social learning can yield
+higher payoffs than individual learning when uncertainty is sufficiently limited.
+By disambiguating and organizing various operationalizations of uncertainty, 
+we developed a more nuanced theoretical understanding of which forms of
+uncertainty interact in which ways to make social learning more or less beneficial
+compared to asocial learning.  Note that in many cases we made modeling choices that
+excluded some important mechanisms of social learning; for example we assumed
+success-biased learning, although conformity is theoretically important as
+well~\cite{Muthukrishna2016a,Smaldino2018b}. Still, we believe our model
 advances theoretical parsimony; and the software implementation is designed to
@@
 \paragraph{Disc. 2: Foundation for studying social learning evolution with group
-structure (PAUL, JAMIE, CRISTINA)}~\cite{Katsnelson2014}.
+structure or other topics(PAUL, JAMIE, CRISTINA)}~\cite{Katsnelson2014}.
 
 Our modeling approach may have applications to developing social artificial
-intelligence. Much effort has gone in to developing the cognitive machinery
-to realize multi-agent reinforcement learning
+intelligence. Much effort has gone in to developing the cognitive machinery to
+realize multi-agent reinforcement learning
 systems~\cite{Sandholm1996,Ndousse2021,Gronauer2022}, with some work explicitly
 incorporating cultural evolutionary approaches to social learning~\cite{Jaques2019}.
-However, it seems there are a lack of methods for adapting
-to environmental uncertainty, or determining when social learning is actually
-advantageous under different uncertainty conditions. Our model dynamics could
-be used as an evolutionary algorithm to update AI agents' social learning
-strategy without knowledge of the underlying uncertainty structure.
-Our model could also predict the expected benefit of social learning,
-which may be inherently costly in artificial multi-agent learning systems, 
-and how long the translated evolutionary algorithm may take to converge.
+However, it seems there are a lack of methods for adapting to environmental
+uncertainty, or determining when social learning is actually advantageous under
+different uncertainty conditions. Our model dynamics could be used as an
+evolutionary algorithm to update AI agents' social learning strategy without
+explicit knowledge of, or need to approximate, the underlying uncertainty structure.
+Our model could also predict the expected benefit of social learning, which may be
+inherently costly in artificial multi-agent learning systems, and how long the
+translated evolutionary algorithm may take to converge.
 
 \bibliographystyle{apacite}
-\bibliography{/Users/mt/workspace/Writing/library.bib}
+% \bibliography{/Users/mt/workspace/Writing/library.bib}
+\bibliography{this.bib}
+
+\appendix
+
+\section{Appendix}
+
+\subsection{Convergence information}
+
+\begin{table}[h]
+  \caption{Max. iterations = 5000.}
+  \label{tab:convergence}
+  \centering
+  \begin{tabular}{cccc} \toprule
+    $B$ & \# not at fixation & \# total series & Pct. not fixated \\
+    \midrule  
+    2  & 0  & 132000 & 0.0 \% \\
+    4  & 0  & 132000 & 0.0 \% \\
+    10 & 44 & 132000 & 0.00033  \% \\
+    \bottomrule
+  \end{tabular} 
+\end{table}
 

### 2022-06-03 ms.tex
Updates from Overleaf

@@
 
-\title{Uncertainty in social learning evolution}
+\title{The form of uncertainty affects selection for social learning}
 
@@
 
-Social learning is essential to human and other species' everyday life and survival.
-Social learning enhances problem solving when acquiring information from others is
-more efficient than learning on one's own~\cite{Laland2004}. Theory predicts that
-social learning should be favored in uncertain
-environments~\cite{BoydRicherson1985,Henrich1998}, up to a
-point~\cite{Rogers1988,Feldman1996}; this prediction has received some empirical
-support across species~\cite{McElreath2005,Kendal2018,Allen2019}.  However, the
-meaning of the term \emph{uncertainty} often conflates environmental variability,
-spatial heterogeneity, ambiguity in behavioral payoff structure, and other
-variability that could plausibly be interpreted as \emph{uncertainty}.  Furthermore,
-many models of social learning evolution do not account for individual-level
+\cm{Uncertainty -> social learning widespread belief.
+But variously operationalized or not real uncertainty.
+Selling points of this paper 1) real uncertainty, 2) 4 kinds uncertainty, 3) cognition (soft-max temperature varies how much explores).}
+
+Social learning enhances problem solving when acquiring information from others is more efficient than learning on one's own~\cite{Laland2004}.
+However, social learning can also lead individuals astray if, for example, they are copying outdated information.
+Theoretical models have helped clarify the circumstances under which social learning should be evolutionarily favored.
+For example, environments that change across time favor learning from others (as opposed to having a genetically fixed behavior) ~\cite{BoydRicherson1985,Henrich1998}, so long as they are not so variable that the social information reflects outdated and maladaptive behavior
+
+point~\cite{Rogers1988,Feldman1996}.
+\cm{check that the citations still accurate}.
+This theoretical work has motivated much empirical research and helped predict behavior in several species ~\cite{McElreath2005,Kendal2018,Allen2019}.
+
+From this literature, the idea that \emph{uncertainty} supports social learning has proliferated, but the term often conflates several features of the environment, including temporal variability,
+spatial heterogeneity, ambiguity in behavioral payoff structure, and difficulty of the task.
+In translating mathematical models to verbal predictions, the formal meaning of terms like \emph{uncertainty} is often lost, facilitating such conflation.
+Furthermore, as the number of formal models of social learning have expanded, an ever increasing number
+of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of \emph{uncertainty} has made it difficult to compare across models and consolidate our understanding of the contexts in which why social learning is adaptive.
+
+To address these concerns we developed an empirically-motivated, evolutionary agent-based model that operationalizes four principal components of uncertainty.
+We use this integrated model to generate predictions about the kinds of uncertainty that favor social learning and to clarify the logic of why this would be the case.
+Answering this question is critical for understanding human behavior adapting to a rapidly changing world, both to mitigate existential threats~\cite{Moya2020,Jones2021}, and to capitalize on new opportunities such as transitioning to clean energy use and production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+
+ \cm{I moved this for now: \emph{"Furthermore, many models of social learning evolution do not account for individual-level
 cognition~\cite{Heyes2016}, though humans clearly have evolved cognitive mechanisms
-for dealing with uncertainty generally~\cite{Vul2014,Gershman2019,Schulz2019}.
-Social learning evolution theory tends to be organized around an increasing number
-of modeling choices~\cite[Figure 1]{Kendal2018} instead of around questions of when
-and why social learning is adaptive, in which contexts.  Therefore, we developed
-an evolutionary, empirically-motivated, agent-based model that operationalized
-four principal uncertainty components to generate predictions of when 
-social learning would evolve in which circumstances, and why. Answering this
-question is critical for understanding human behavior adapting to a rapidly changing
-world, both to mitigate existential threats~\cite{Moya2020,Jones2021}, and to
-captialize on new opportunities such as transitioning to clean energy use and
-production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+for dealing with uncertainty generally~\cite{Gershman2019,Schulz2019}."} because I think it interrupted the flow and didn't seem directly linked to the goal of understanding aspects of uncertainty.
+However, if this is one of the main features of the model that we want to highlight as an improvement over previous work, then we probably have to say something more about it.
+Perhaps I just wasn't seeing the connection though, and the more accurate cognitive model DOES add to our ability to study the consequences of uncertainty.
+If that's the case, the argument should be sharpened.
+If not, maybe we put this info when the cognitive model is introduced.}\mt{Agreed.
+I put a first draft of a better version of this paragraph closer to/at the end of the Intro.}
 
@@
 edit this.} 
-To gain a more systematic understanding of uncertainty and social learning
-evoluiton, we identified four common classes of ecological
-uncertainty (``principal components'' of uncertainty) used as factors
-in social learning evolution models: (1) environmental variability; (2) payoff
+To systematically study features of uncertainty and its consequences for social learning, we identified four common classes of ecological uncertainty (``principal components'' of uncertainty) used in evolutionary models: (1) temporal environmental variability; (2) payoff
 ambiguity (difference between best behavior choice and others); (3) 
 selection set size (number of ecologically possible behaviors); and 
-(4) the lifespan of agents. These were chosen because modeling and empirical 
-study designs across taxa tend use one or more of these uncertainty dimensions.
-Environmental variability is sometimes modeled as catastrophic and 
-happens only once in an individual's lifetime~\cite{Rogers1988}, or may be
+(4) the lifespan of agents (number of individual learning opportunities).
+These were chosen because modeling and empirical 
+studies across taxa tend use one or more of these uncertainty dimensions [Figure 1].
+
+\cm{Other choices: softmax: existing models underestimate the power of learning from experience can improve both individual and helps social learners recover from outdated / misleading social info , no conformism: but that's ok because we're giving social learning the best chance of success
+no horizontal transmission, no spatial variation}
+
+Temporal environmental variability is usually modeled as an independent probability of the environment changing its state each generation ~\cite{Feldman1996,McElreath2005}.
+The probabilities of environmental change are usually fixed ~\cite{BoydRicherson1985, Kendal2009}, but they have also been modeled as deterministic cycles ~\cite{Feldman1996} or as variable rates \cm{who does this?}.
+Furthermore, the consequences of environmental change can range from mild to  catastrophic.
+In the latter case a change of environment corresponds to no one having the adaptive behavior for the environment ~\cite{Rogers1988}.
+
+or may be
 modeled as occurring with a fixed or variable
-probability~\cite{Feldman1996,McElreath2005}---in these examples environments
+probability---in these examples environments
 can only be in one of two states. Payoff ambiguity sometimes takes the form
@@
 
-\paragraph{Meaning of uncertainty in ecology and cognitive and social sciences } (JAMIE)
+Social learning is the adaptive icing on the cake of intelligent adaptations to ecological uncertainty.
+To deal with uncertainty as individuals, human experiment participants have been observed to update their tendency for exploring alternative behaviors based on how much uncertainty there is globally.
+Furthermore, correlations in uncertainty between potential behaviors, humans tend to adopt directed exploration strategies that favor testing behaviors with greater observed payoff variance \cite{Wilson2014,Gershman2019}.
+Many models of social learning assume little to nothing about the cognitive capabilities of their agents (Cristina unpack this in another paragraph, using the uncertainty studies spreadsheet?).
+We do not do this because \emph{blackboxing}, or ignoring, cognitive mechanisms is “bad” \cite[p.
+658]{Heyes2016, Kendal2018}, but because it is theoretically meaningful.
+In order to understand how social learning evolves as an adaptation to uncertainty, the model is strengthened by assuming a more biologically plausible, and evolutionarily accurate, model of cognition capable of maximizing payoffs under uncertainty for an individual.
+In our model we do not impose any structure in randomness between behaviors, so our cognitive model is only sensitive to total randomness.
+Specifically, we will adopt the softmax distribution for function for selecting a behavior based on its observed payoffs–greater payoff variance means any one behavior is more likely to be selected.
+
+\paragraph{Meaning of uncertainty in ecology (and cognitive and social sciences?) } (JAMIE, PAUL?)
 We need to support our claim that these four classes of uncertainty really 
@@
 \begin{figure}
-  \caption{Agents are initialized as randomly social learners or not, with their
+  \caption{Agents are randomly initialized as social learners or not, with their
   payoff observations all initialized to zero (A). Then agents begin selecting
@@
 social information is less consequential due
-to (1) larger $B$ is a more difficult problem for trial-and-error learning and
+to (1) larger $B$ is a more difficult problem for trial-and-error learning, and
 (2) a misidentified optimal behavior is weighted less relative to smaller
 $B$, meaning agents are more likely to explore behaviors identified as non-optimal
-when $B$ is larger (columns of Figure~\ref{fig:mainResults}).  
+when $B$ is larger (columns of Figure~\ref{fig:mainResults}).  \mt{Support this by calculating the difference between weights when B=2 and B=10 and a social learner learns outdated information}
 Increased $B$ led to more pronounced flattening of social learning suppression when

### 2022-06-03 ms.tex
minor refs update

@@
 with probabilistic
-payoffs~\cite{SuttonBartoBook,McElreath2005,Rendell2010,Schulz2019}.  Each behavior
+payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.  Each behavior
 $b$ yields Bernoulli payoffs: payoff of 1 with probability $\pi_b$ and zero payoff

### 2022-06-21 ms.tex
Updates from Overleaf

@@
 
-Social learning is essential to survival. It is likely to evolve when it is more
+Social learning is essential to human survival. It is likely to evolve when it is more
 efficient than asocial, trial-and-error learning. Theoretically, social learning
@@
 
-\cm{Uncertainty -> social learning widespread belief.
-But variously operationalized or not real uncertainty.
+\cm{Notes on our June 2 discussion (USPs): "Uncertainty favors social learning" is a widespread belief.
+But it is operationalized in different ways, and oftentimes it does not reflect REAL uncertainty.
 Selling points of this paper 1) real uncertainty, 2) 4 kinds uncertainty, 3) cognition (soft-max temperature varies how much explores).}
@@
 Theoretical models have helped clarify the circumstances under which social learning should be evolutionarily favored.
-For example, environments that change across time favor learning from others (as opposed to having a genetically fixed behavior) ~\cite{BoydRicherson1985,Henrich1998}, so long as they are not so variable that the social information reflects outdated and maladaptive behavior
-
-point~\cite{Rogers1988,Feldman1996}.
+For example, environments that change across time favor learning from others (as opposed to having a genetically fixed behavior) ~\cite{BoydRicherson1985,Henrich1998}, so long as they are not so variable that the social information reflects outdated and maladaptive behavior point~\cite{Rogers1988,Feldman1996}.
 \cm{check that the citations still accurate}.
@@
 From this literature, the idea that \emph{uncertainty} supports social learning has proliferated, but the term often conflates several features of the environment, including temporal variability,
-spatial heterogeneity, ambiguity in behavioral payoff structure, and difficulty of the task.
+spatial heterogeneity, ambiguity in behavioral payoff structure, and difficulty of learning the task.
 In translating mathematical models to verbal predictions, the formal meaning of terms like \emph{uncertainty} is often lost, facilitating such conflation.
 Furthermore, as the number of formal models of social learning have expanded, an ever increasing number
-of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of \emph{uncertainty} has made it difficult to compare across models and consolidate our understanding of the contexts in which why social learning is adaptive.
+of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of \emph{uncertainty} has made it difficult to compare across models and consolidate our understanding of the contexts in which social learning is adaptive.
 
@@
 edit this.} 
-To systematically study features of uncertainty and its consequences for social learning, we identified four common classes of ecological uncertainty (``principal components'' of uncertainty) used in evolutionary models: (1) temporal environmental variability; (2) payoff
-ambiguity (difference between best behavior choice and others); (3) 
-selection set size (number of ecologically possible behaviors); and 
-(4) the lifespan of agents (number of individual learning opportunities).
+To systematically study features of uncertainty and its consequences for social learning, we identified four common classes of ecological uncertainty used in evolutionary models: (1) temporal environmental variability; (2) selection set size (number of possible behaviors); (3) payoff
+ambiguity (difference in the reward between adopting the best behavior and alternatives); and (4) the lifespan of agents (number of individual learning opportunities).
 These were chosen because modeling and empirical 
-studies across taxa tend use one or more of these uncertainty dimensions [Figure 1].
+studies across taxa tend use one or more of these uncertainty dimensions (Figure \ref{fig:schematic}).
 
-\cm{Other choices: softmax: existing models underestimate the power of learning from experience can improve both individual and helps social learners recover from outdated / misleading social info , no conformism: but that's ok because we're giving social learning the best chance of success
-no horizontal transmission, no spatial variation}
-
-Temporal environmental variability is usually modeled as an independent probability of the environment changing its state each generation ~\cite{Feldman1996,McElreath2005}.
+Temporal environmental variability is fundamental to most models of social learning, yet even this is implemented in several ways.
+This is usually modeled as an independent probability of the environment changing its state each generation ~\cite{Feldman1996,McElreath2005}.
 The probabilities of environmental change are usually fixed ~\cite{BoydRicherson1985, Kendal2009}, but they have also been modeled as deterministic cycles ~\cite{Feldman1996} or as variable rates \cm{who does this?}.
 Furthermore, the consequences of environmental change can range from mild to  catastrophic.
-In the latter case a change of environment corresponds to no one having the adaptive behavior for the environment ~\cite{Rogers1988}.
+In the latter case a change of environment results in no one having the adaptive behavior for the environment ~\cite{Rogers1988}.
+Such catastrophic environmental changes present a large adaptive challenge as individuals cannot bank on accumulated information from previous generations.
+Other models of environmental change introduce less uncertainty as they fluctuate between two environmental states with corresponding adaptive behaviors.
+This means that all individuals with previously maladaptive behaviors then have adaptive behaviors upon the environment changing ~\cite{Perreault2012}.
 
-or may be
-modeled as occurring with a fixed or variable
-probability---in these examples environments
-can only be in one of two states. Payoff ambiguity sometimes takes the form
-of differences in expected payoffs arising from different
-behaviors or strategies~\cite{Enquist2007,Rendell2010}
-or by varying the standard deviation of payoffs~\cite{McElreath2005}. 
 Selection set size often takes only one value: 
@@
 behaviors~\cite{Feldman1996,Rendell2010} and four behaviors~\cite{Enquist2007}.
+
+Payoff ambiguity differs from selection set size in that it not only affects uncertainty, it also directly influences the strength of selection. This parameter sometimes takes the form
+of differences in expected payoffs arising from different
+behaviors or strategies~\cite{Enquist2007,Rendell2010}
+or by varying the standard deviation of payoffs~\cite{McElreath2005}.
+
 The age or lifespan of individuals was
@@
 \paragraph{Social learning evolution} (CRISTINA) 
+\cm{I think a lot of this may be too much detail.
+I'm still editing and focusing the above on the main forms of uncertainty we are modeling and reviewing the relevant literature as we go.
+Yes we've made choices about things like horizontal vs vertical, but i think we can just justify that when we introduce the model }
 To add to confusion about how to integrate diverse models of social learning
@@
 
+\cm{Other choices we made that might need to be justified: 1) softmax: existing models underestimate the power of learning from experience by not having a rich cognition.
+This rich cognition can improve both individual learning and help social learners recover from outdated / misleading social info.
+2) no conformism: but that's ok because we're giving social learning the best chance of success.
+3) no horizontal transmission, no spatial variation}
+
 \begin{table}[h]
@@
 To answer our research questions we developed an agent-based model of social
-learning evolution in which a society of $N$ individuals each must decide which of
+learning evolution in which a society of $N$ individuals \cm{do we ever define N used?} each must decide which of
 $B$ behaviors to perform at each time step within a generation of $L$ time steps. At

### 2022-07-04 ms.tex
finished tau sensitivity figures

@@
 \usepackage{caption}
-% \usepackage{subcaption}
+\usepackage{subcaption}
 \usepackage{wrapfig}
@@
 
+\newpage
+
+\subsection{Softmax parameter sensitivity analysis}
+\vspace{-3em}
+\begin{figure}
+  \centering
+  \caption{Sensitivity analysis of the main results 
+		   for the softmax parameter $\beta = 100$ and $\beta=1$. Recall the main
+		   results were obtained with $\beta = 10$.}
+  \label{fig:softmaxSensitivity}
+  \vspace{2em}
+  \begin{subfigure}{\textwidth}
+	\caption{$\beta = 100$}
+	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+\newpage
+\begin{figure}
+  \ContinuedFloat
+  \begin{subfigure}{\textwidth}
+	\caption{$\beta = 1$}
+	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+
+\subsection{Number of prospective teachers sensitivty analysis}
+
+\vspace{-3em}
+\begin{figure}
+  \centering
+  \caption{Number of prospective teachers sensitivity analysis for $N_T=2,10,20$. Recall
+  $N_T=5$ was used to generate main text results.}
+  \label{fig:softmaxSensitivity}
+  \vspace{2em}
+  \begin{subfigure}{\textwidth}
+	\caption{$N_T = 2$}
+	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+\newpage
+\begin{figure}
+  \ContinuedFloat
+  \begin{subfigure}{\textwidth}
+	\caption{$N_T = 10$}
+	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+\newpage
+\begin{figure}
+  \ContinuedFloat
+  \begin{subfigure}{\textwidth}
+	\caption{$N_T = 20$}
+	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+
+\subsection{Population size sensitivty analysis}
+
+\begin{figure}
+  \centering
+  \caption{
+	Sensitivity analysis of the main results for different population
+	sizes, $N=50,200,1000$. Recall $N=100$ was used to generate main 
+	text results.
+  }
+  \label{fig:populationSensitivity}
+  \begin{subfigure}{\textwidth}
+	\caption{$N=50$}
+	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_N=50/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+
+\begin{figure}
+  \ContinuedFloat
+	\begin{subfigure}{\textwidth}
+	  \caption{$N=200$}
+	  % \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_N=200/mainResultsPlots.pdf}
+	\end{subfigure}
+\end{figure}
+
+\begin{figure}
+  \ContinuedFloat
+	\begin{subfigure}{\textwidth}
+	  \caption{$N=1000$}
+	  % \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_N=1000/mainResultsPlots.pdf}
+	\end{subfigure}
+\end{figure}
+
 \end{document}

### 2022-07-04 ms.tex
nagents, nteachers sensitivity figures in place

@@
 
-\subsection{Number of prospective teachers sensitivty analysis}
-
-\vspace{-3em}
-\begin{figure}
-  \centering
-  \caption{Number of prospective teachers sensitivity analysis for $N_T=2,10,20$. Recall
-  $N_T=5$ was used to generate main text results.}
-  \label{fig:softmaxSensitivity}
-  \vspace{2em}
-  \begin{subfigure}{\textwidth}
-	\caption{$N_T = 2$}
-	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
-  \end{subfigure}
-\end{figure}
 \newpage
-\begin{figure}
-  \ContinuedFloat
-  \begin{subfigure}{\textwidth}
-	\caption{$N_T = 10$}
-	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
-  \end{subfigure}
-\end{figure}
-\newpage
-\begin{figure}
-  \ContinuedFloat
-  \begin{subfigure}{\textwidth}
-	\caption{$N_T = 20$}
-	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
-  \end{subfigure}
-\end{figure}
-
 \subsection{Population size sensitivty analysis}
@@
 	\caption{$N=50$}
-	% \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_N=50/mainResultsPlots.pdf}
+	\includegraphics[width=\textwidth]{Figures/supplement/nagents=50/mainResultsPlots.pdf}
   \end{subfigure}
@@
 	  \caption{$N=200$}
-	  % \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_N=200/mainResultsPlots.pdf}
+	  \includegraphics[width=\textwidth]{Figures/supplement/nagents=200/mainResultsPlots.pdf}
 	\end{subfigure}
@@
 	  \caption{$N=1000$}
-	  % \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_N=1000/mainResultsPlots.pdf}
+	  \includegraphics[width=\textwidth]{Figures/supplement/nagents=1000/mainResultsPlots.pdf}
+	\end{subfigure}
+\end{figure}
+
+\newpage
+\subsection{Number of prospective teachers sensitivty analysis}
+
+\vspace{-3em}
+\begin{figure}
+  \centering
+  \caption{Number of prospective teachers sensitivity analysis for $N_T=2,10,20$. Recall
+  $N_T=5$ was used to generate main text results.}
+  \label{fig:softmaxSensitivity}
+  \vspace{2em}
+  \begin{subfigure}{\textwidth}
+	\caption{$N_T = 2$}
+	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+\newpage
+\begin{figure}
+  \ContinuedFloat
+  \begin{subfigure}{\textwidth}
+	\caption{$N_T = 10$}
+	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=10/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+\newpage
+\begin{figure}
+  \ContinuedFloat
+  \begin{subfigure}{\textwidth}
+	\caption{$N_T = 20$}
+	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mainResultsPlots.pdf}
   \end{subfigure}

### 2022-07-04 ms.tex
Updates from Overleaf

--- 2022-06-21 ms.tex
@@
 
-\title{The form of uncertainty affects selection for social learning}
+%\title{The form of uncertainty affects selection for social learning}
+\title{Different forms of uncertainty differently affect the evolution of social learning}
 
@@
 \section{Introduction}
-
 \cm{Notes on our June 2 discussion (USPs): "Uncertainty favors social learning" is a widespread belief.
@@
 
-Social learning enhances problem solving when acquiring information from others is more efficient than learning on one's own~\cite{Laland2004}.
+%% for inclusion in the social learning ms
+
+Decision-making under uncertainty is fundamental challenge for any organism.
+Uncertainty weighs particularly heavily on humans adaptation because of our long lifespans, cosmopolitan distribution, and the resulting necessity to adapt to relatively coarse-grain environments \cite{levins1962}.
+
+While the importance of decision-making under uncertainty is generally acknowledged, there is often some confusion about what constitutes uncertainty.
+First, uncertainty needs to be distinguished from risk.
+While the concepts sound similar, uncertainty and risk are quite different.
+Both refer to the existence of non-deterministic outcomes, but with risk, outcomes can be represented probabilistically, whereas uncertainty implies that the probabilities of outcomes remain unknown \cite{knight1921}.
+As it doesn't lend itself to simple mathematical representation, uncertainty presents substantial analytical challenges as first noted by \cite{keynes1921}.
+
+Despite the technical difficulties of dealing with uncertainty, addressing it is an essential task because it potentially changes our understanding of decision-making in a qualitative manner.
+The dominant approach to understanding decisions for choices with variable outcomes is expected utility theory (EUT).
+As the name suggests, EUT requires the ability to calculate expectations, which means that we must know the probability distributions of outcomes.
+The non-probabilistic nature of uncertainty means one cannot calculate expectations.
+Following \cite{savage1954}, various research traditions in decision theory and economics have treated uncertainty as if it were risk, just with subjective probabilities replacing objective ones.
+The fundamental problem with this approach was noted by \cite{geweke2001} and further developed by \cite{weitzman2009}.
+In particular, the probability density function of an outcome that needs to be learned, but for which opportunities for learning are highly constrained, will be heavy-tailed and expected-utility calculations will not work because of the resulting undefined mass-generating function.
+Uncertainty implies heavy-tailed probability distributions and heavy-tailed distributions require different analytical methods \cite{nair_etal2022}.
+
+The heuristic-based adaptive-toolbox approach of \cite{todd_gigerenzer2000} provides an alternative strategy for understanding decision-making under uncertainty.
+There is a strong intuition that uncertainty should activate specific social-learning heuristics.
+Within the cultural-evolution literature, uncertainty is generally thought to lead to a social heuristic known as \emph{conformist-biased learning} \cite{boyd_richerson1985, henrich_boyd1998, muthukrishna_etal2016}.
+
+True uncertainty arises when an organism lacks the capacity to learn about the possible outcomes of a decision task.
+This is very likely for a cosmopolitan species living in a coarse-grain environment.
+Task complexity also.
+Non-stationary environmental change \cite{kay_king2020}.
+These potential sources of uncertainty can also interact.
+
+\cm{CUT in favor of uncertainty intro: Social learning enhances problem solving when acquiring information from others is more efficient than learning on one's own~\cite{Laland2004}.
 However, social learning can also lead individuals astray if, for example, they are copying outdated information.
 Theoretical models have helped clarify the circumstances under which social learning should be evolutionarily favored.
-For example, environments that change across time favor learning from others (as opposed to having a genetically fixed behavior) ~\cite{BoydRicherson1985,Henrich1998}, so long as they are not so variable that the social information reflects outdated and maladaptive behavior point~\cite{Rogers1988,Feldman1996}.
+For example, environments that change across time favor learning from others (as opposed to having a genetically fixed behavior) ~\cite{BoydRicherson1985,Henrich1998}, so long as the environments are not so variable that the social information reflects outdated and maladaptive behavior point~\cite{Rogers1988,Feldman1996, aoki2014evolution}.
 \cm{check that the citations still accurate}.
-This theoretical work has motivated much empirical research and helped predict behavior in several species ~\cite{McElreath2005,Kendal2018,Allen2019}.
+This theoretical work has motivated much empirical research and helped predict social learning behavior in humans and other species ~\cite{McElreath2005,Kendal2018,Allen2019}.
+}
 
-From this literature, the idea that \emph{uncertainty} supports social learning has proliferated, but the term often conflates several features of the environment, including temporal variability,
-spatial heterogeneity, ambiguity in behavioral payoff structure, and difficulty of learning the task.
-In translating mathematical models to verbal predictions, the formal meaning of terms like \emph{uncertainty} is often lost, facilitating such conflation.
-Furthermore, as the number of formal models of social learning have expanded, an ever increasing number
-of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of \emph{uncertainty} has made it difficult to compare across models and consolidate our understanding of the contexts in which social learning is adaptive.
+From this literature, the idea that uncertainty supports social learning has proliferated, but the term ``uncertainty" often conflates several different interpretations of that word.
+For example, different models define uncertainty in terms of the rate of environmental change, the correlation between spatial environments, or the reliability of information acquired from the environment.
+Furthermore, in translating mathematical models to verbal predictions, the formal meaning of terms like uncertainty is often lost \cite{lawson1988probability}, facilitating such conflation. 
+%Furthermore, a
+And as the number of formal models of social learning have expanded, an ever increasing number
+of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of uncertainty have made it difficult to compare across models and consolidate our understanding of the contexts in which social learning is adaptive.
 
-To address these concerns we developed an empirically-motivated, evolutionary agent-based model that operationalizes four principal components of uncertainty.
-We use this integrated model to generate predictions about the kinds of uncertainty that favor social learning and to clarify the logic of why this would be the case.
+To address these concerns we developed an empirically-motivated, evolutionary agent-based model that simultaneously operationalizes four %principal components 
+different forms of uncertainty: (1) temporal environmental variability; (2) selection set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning).
+These were chosen because modeling and empirical
+studies across taxa tend use one or more of these uncertainty dimensions\ps{citation needed}.  
+The model also involves a more cognitively realistic learning mechanism, the softmax algorithm, which allows us to more accurately assess some of the likely tradeoffs between social and individual learning.
+We use this integrated model to ask what kinds of uncertainty are likely to favor social learning, and to clarify the logic of why this would be the case.
 Answering this question is critical for understanding human behavior adapting to a rapidly changing world, both to mitigate existential threats~\cite{Moya2020,Jones2021}, and to capitalize on new opportunities such as transitioning to clean energy use and production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
 
- \cm{I moved this for now: \emph{"Furthermore, many models of social learning evolution do not account for individual-level
-cognition~\cite{Heyes2016}, though humans clearly have evolved cognitive mechanisms
-for dealing with uncertainty generally~\cite{Gershman2019,Schulz2019}."} because I think it interrupted the flow and didn't seem directly linked to the goal of understanding aspects of uncertainty.
+In the remainder of this introduction, we further unpack our motivation for this work justify our approach.
+We then present our model and the results of our analyses.
+We conclude with a discussion of our results and their implications for our understanding of social learning, uncertainty, and cultural evolution.
+
+% \cm{I moved this for now: \emph{"Furthermore, many models of social learning evolution do not account for individual-level cognition~\cite{Heyes2016}, though humans clearly have evolved cognitive mechanisms for dealing with uncertainty generally~\cite{Gershman2019,Schulz2019}."} because I think it interrupted the flow and didn't seem directly linked to the goal of understanding aspects of uncertainty.
 However, if this is one of the main features of the model that we want to highlight as an improvement over previous work, then we probably have to say something more about it.
@@
 
-\mt{This paragraph is a first try to introduce the four uncertainty dimensions
-with examples to illustrate the problem we are answering.
-I outlined the next paragraph to get into more details of social learning:
-how cultural evolution works; conformity, success-biased, etc. Cristina, please
-edit this.} 
-To systematically study features of uncertainty and its consequences for social learning, we identified four common classes of ecological uncertainty used in evolutionary models: (1) temporal environmental variability; (2) selection set size (number of possible behaviors); (3) payoff
-ambiguity (difference in the reward between adopting the best behavior and alternatives); and (4) the lifespan of agents (number of individual learning opportunities).
-These were chosen because modeling and empirical 
-studies across taxa tend use one or more of these uncertainty dimensions (Figure \ref{fig:schematic}).
+%\mt{This paragraph is a first try to introduce the four uncertainty dimensions with examples to illustrate the problem we are answering.
+I outlined the next paragraph to get into more details of social learning: how cultural evolution works; conformity, success-biased, etc.
+Cristina, please edit this.}
 
-Temporal environmental variability is fundamental to most models of social learning, yet even this is implemented in several ways.
-This is usually modeled as an independent probability of the environment changing its state each generation ~\cite{Feldman1996,McElreath2005}.
-The probabilities of environmental change are usually fixed ~\cite{BoydRicherson1985, Kendal2009}, but they have also been modeled as deterministic cycles ~\cite{Feldman1996} or as variable rates \cm{who does this?}.
+\subsection{Varieties of Uncertainty}
+
+Uncertainty involves a reduced ability to predict what will happen in the future or to assess which actions are likely to yield particular outcomes.
+Uncertainty can manifest in many ways.
+We focus on the following four sources of uncertainty for the evolution of social learning: (1) temporal environmental variability, (2) selection set size, (3) payoff ambiguity, and (4) effective lifespan.
+
+\textbf{Temporal environmental variability.}
+When external or internal shocks (e.g., climatic events, migration, technological paradigm shifts) occur, strategies that were previously adaptive may no longer be optimal.
+The difficulty in predicting either when such shocks will occur or what behaviors will adaptive in the resulting environments leads to uncertainty.
+Temporal environmental variability is fundamental to most evolutionary models of social learning, yet even this is implemented in several ways.
+It is usually modeled as an independent probability of the environment changing its state each generation ~\cite{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}.
+The probabilities of environmental change are usually fixed, %~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution},
+but they have also been modeled as deterministic cycles ~\cite{Feldman1996, aoki2014evolution} or as variable rates \cm{who does this?}\ps{Yeah, I'm not even sure what variable rates means in this context}.
 Furthermore, the consequences of environmental change can range from mild to  catastrophic.
-In the latter case a change of environment results in no one having the adaptive behavior for the environment ~\cite{Rogers1988}.
+In the latter case, a change of environment results in the total elimination of any adaptive behavior, which must be learned \emph{de novo} for the new environment ~\cite{Rogers1988}.
 Such catastrophic environmental changes present a large adaptive challenge as individuals cannot bank on accumulated information from previous generations.
 Other models of environmental change introduce less uncertainty as they fluctuate between two environmental states with corresponding adaptive behaviors.
-This means that all individuals with previously maladaptive behaviors then have adaptive behaviors upon the environment changing ~\cite{Perreault2012}.
+This means that all individuals with previously maladaptive behaviors then have adaptive behaviors upon the environment changing ~\cite{perreault2012bayesian}.
 
-Selection set size often takes only one value: 
-for example, in empirical studies of \emph{bombus terresteris} (bumble
+\textbf{Selection set size.}
+When one does not know which option to take, uncertainty increases with the number of options.
+This is a mathematical fact at the core of information theory: the number of bits required to reliably encode the optimal solution increases by one every time the selection set doubles in size  \cite{mackay2003information}.
+This is intuitive; the more options one could potentially investigate, the greater one's uncertainty about which option is the best choice.
+In studies of social learning, the size of the selection set is very often limited to just two options.
+For example, in empirical studies of \emph{bombus terresteris} (bumble
 bee)~\cite{Baracchi2018} and \emph{parus major} (great tit)~\cite{Aplin2017},
 experimenters provided two behaviors for
-the bees or birds to perform, respectively, each yielding greater or smaller
-payoffs depending on experimental treatment. Human studies have used two
+the bees or birds to choose from, where one yielded a higher payoff than the other. %respectively, each yielding greater or smaller payoffs depending on experimental treatment. 
+Many human studies have also used just two
 or three possible behaviors~\cite{McElreath2005,Toyokawa2019}.
-Modeling studies have used two 
-behaviors~\cite{Feldman1996,Rendell2010} and four behaviors~\cite{Enquist2007}.
+Modeling studies have often used just two 
+behaviors~\cite{Rogers1988,Feldman1996,Rendell2010,perreault2012bayesian}, though others have studied systems with larger selection sets where the number of options is usually not explicitly specified~\cite{boyd1995does,Enquist2007}.
+It is very rare, however, to find the size of the selection set manipulated as a measure of changing uncertainty.
 
-Payoff ambiguity differs from selection set size in that it not only affects uncertainty, it also directly influences the strength of selection. This parameter sometimes takes the form
-of differences in expected payoffs arising from different
-behaviors or strategies~\cite{Enquist2007,Rendell2010}
-or by varying the standard deviation of payoffs~\cite{McElreath2005}.
+\textbf{Payoff ambiguity.}
+Many models of social learning differentiate between the payoffs for adopting optimal vs.
+non-optimal behaviors \cite{Rogers1988,Enquist2007,Rendell2010}.
+The size of the difference between these payoffs is usually taken to indicate the strength of selection of learning, which makes sense.
+However, in reality payoffs for particular behaviors are not always consistent.
+A behavior may yield a large payoff sometimes and a small payoff other times \cite{McElreath2005}.
+This means that signals about the relationship between behavior and payoff are often noisy, and differentiating between behavioral options is in part a problem of signal detection.
+When the difference in expected payoffs between optimal and non-optimal behaviors is very large, this noise matters little, as the signal is still very clear.
+However, when the expected payoffs of different behaviors are similar relative to the size of their variances, ambiguity arises about which behaviors really are superior.
+Smaller differences between payoffs corresponds to larger ambiguity.
+Importantly, payoff ambiguity %differs from selection set size in that it not only affects uncertainty, it also directly
+influences both uncertainty \emph{and} the strength of selection.
+%This parameter sometimes takes the form of differences in expected payoffs arising from different behaviors or strategies~\cite{Enquist2007,Rendell2010} or by varying the standard deviation of payoffs~\cite{McElreath2005}.
 
-The age or lifespan of individuals was
-found to affect on social learning in both \emph{parus
-major}~\cite{Aplin2017} and \emph{poecilia reticulata} 
-(guppies)~\cite{Leris2016} \mt{Need better connection between lifespan and 
-age, or better references to support use of lifespan}.
-Shorter lifespans mean individuals
-die more uncertain of which behaviors are optimal, and pass that uncertainty on
-to their offspring. To answer our research questions about the combined effect
-of various forms of uncertainty on social learning evolution, we developed an
-agent-based model that incorporates all four of
-these uncertainty variables. We systematically vary these parameters
-to understand and predict their effects on social learning evolution.
+\textbf{Effective lifespan.}
+Learning can be viewed as a process by which an individual reduces or otherwise manages their uncertainty \cite{jacobs2011bayesian,clark2013whatever}.
+It is an iterative process by which one repeatedly acquires information, forms representations and predictions, and tests and refines those representations and predictions.
+It therefore stands to reason that the more opportunities one has for learning, the more one can in principle reduce one's uncertainty.
+Similarly, a reduction in the number of opportunities to learn will increase the uncertainty about whether one has accurately learned about the available behavioral options and their associated payoffs.
+We refer to the number of learning opportunities as an individual's effective lifespan to imply that it is the number of opportunities to learn throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.
+Empirically, the age of an individual will often correspond with the number of learning opportunities they have had.
+Aplin et al.
+(2017) \nocite{Aplin2017} found that younger great tits more readily used social information compared with older individuals, possibly because they had  accrued less information via individual learning, and also possibly because younger individuals have the most to gain (given their expected remaining lifespan) by switching to superior behavioral options.
+\ps{I got rid of the Leris and Reader reference because it didn't seem relevant to age-based uncertainty.
+They just showed that young guppies exposed to reliable models were more likely to use social information later.
+I also added some human studies, which seems important.} Cross-cultural studies on humans have shown that young children are more likely to acquire their beliefs and simple skills from their parents than are older children or adults, which is also at least partly due to the differential knowledge accrual between young children and the older adults to whom they direct the most trust and attention \cite{kline2013teaching, Reyes2016}.
+\cm{not sure the second phrase is warranted.
+Can't seem to find whether social learning overall is  }
+%The age of individuals was found to have an effect on social learning in both \emph{parus major}~\cite{Aplin2017} and \emph{poecilia reticulata} (guppies)~\cite{Leris2016}.
+\ps{What effect?
+I'm not sure }
+%\mt{Need better connection between lifespan and age, or better references to support use of lifespan}.
+Individuals with shorter effective lifespans will end their lives with more uncertainty about which behaviors are optimal, and thereby transmit some of that uncertainty to anyone who learns from them.
+The effective lifespan for learning varies both across individuals and across species, yet there is little formal theory incorporating this form of uncertainty into our understanding of the evolution of social learning.
 
-\paragraph{Social learning evolution} (CRISTINA) 
+%To answer our research questions about the combined effect of various forms of uncertainty on social learning evolution, we developed an agent-based model that incorporates all four of these uncertainty variables.
+We systematically vary these parameters to understand and predict their effects on social learning evolution.
+
+\subsection{Varieties of learning, social and otherwise} (CRISTINA) 
 \cm{I think a lot of this may be too much detail.
@@
 Yes we've made choices about things like horizontal vs vertical, but i think we can just justify that when we introduce the model }
+\ps{I agree with Cristina here.
+I think we should use this section to justify our way of modeling individual and social learning, which is different from previous models.
+We don't need to provide a detailed review, just why it's worth doing it as we've done it.
+In particular, we should set up (1) social learning as an initial scaffold for future social learning, and (2) softmax individual learning which involves some greediness with occasional trial and error.}
 To add to confusion about how to integrate diverse models of social learning
@@
 
-\paragraph{Meaning of uncertainty in ecology (and cognitive and social sciences?) } (JAMIE, PAUL?)
+\paragraph{Meaning of uncertainty in ecology (and cognitive and social sciences?) } (JAMIE, PAUL?) \ps{I've added a bunch to the section on different types of uncertainty, which could be more fleshed out if we like.
+I don't think an additional section here is needed.}
 We need to support our claim that these four classes of uncertainty really 
@@
 \paragraph{Evolutionary ABMs for social learning evolution theory development} (PAUL)
+\ps{I'm not sure a section is needed on this, but we can add something about how ABMs allow us to capture complexity not possible with purely mathematical approaches.
+I think it probably makes the most sense to address this at the beginning of the model description.}
 

### 2022-07-04 ms.tex

@@
 
+\newpage
+
+\subsection{Softmax parameter sensitivity analysis}
+\vspace{-3em}
+\begin{figure}
+  \centering
+  \caption{Sensitivity analysis of the main results 
+		   for the softmax parameter $\beta = 100$ and $\beta=1$. Recall the main
+		   results were obtained with $\beta = 10$.}
+  \label{fig:softmaxSensitivity}
+  \vspace{2em}
+  \begin{subfigure}{\textwidth}
+	\caption{$\beta = 100$}
+	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+\newpage
+\begin{figure}
+  \ContinuedFloat
+  \begin{subfigure}{\textwidth}
+	\caption{$\beta = 1$}
+	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+
+\newpage
+\subsection{Population size sensitivty analysis}
+
+\begin{figure}
+  \centering
+  \caption{
+	Sensitivity analysis of the main results for different population
+	sizes, $N=50,200,1000$. Recall $N=100$ was used to generate main 
+	text results.
+  }
+  \label{fig:populationSensitivity}
+  \begin{subfigure}{\textwidth}
+	\caption{$N=50$}
+	\includegraphics[width=\textwidth]{Figures/supplement/nagents=50/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+
+\begin{figure}
+  \ContinuedFloat
+	\begin{subfigure}{\textwidth}
+	  \caption{$N=200$}
+	  \includegraphics[width=\textwidth]{Figures/supplement/nagents=200/mainResultsPlots.pdf}
+	\end{subfigure}
+\end{figure}
+
+\begin{figure}
+  \ContinuedFloat
+	\begin{subfigure}{\textwidth}
+	  \caption{$N=1000$}
+	  \includegraphics[width=\textwidth]{Figures/supplement/nagents=1000/mainResultsPlots.pdf}
+	\end{subfigure}
+\end{figure}
+
+\newpage
+\subsection{Number of prospective teachers sensitivty analysis}
+
+\vspace{-3em}
+\begin{figure}
+  \centering
+  \caption{Number of prospective teachers sensitivity analysis for $N_T=2,10,20$. Recall
+  $N_T=5$ was used to generate main text results.}
+  \label{fig:softmaxSensitivity}
+  \vspace{2em}
+  \begin{subfigure}{\textwidth}
+	\caption{$N_T = 2$}
+	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+\newpage
+\begin{figure}
+  \ContinuedFloat
+  \begin{subfigure}{\textwidth}
+	\caption{$N_T = 10$}
+	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=10/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+\newpage
+\begin{figure}
+  \ContinuedFloat
+  \begin{subfigure}{\textwidth}
+	\caption{$N_T = 20$}
+	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+
 \end{document}

### 2022-07-05 ms.tex
updated line numbers, other?

@@
 \usepackage[margin=1.00in]{geometry}
+\usepackage[modulo]{lineno}
+\linenumbers
 
@@
 \begin{abstract}
-
-Social learning is essential to human survival. It is likely to evolve when it is more
-efficient than asocial, trial-and-error learning. Theoretically, social learning
-is adaptive for some uncertainty, but too much uncertainty makes
-social information unreliable. This fact is empirically
-supported across biology and human sciences. However, it is unclear how
-specific classes and types of uncertainty affect social
-learning evolution. Furthermore, existing models and experimental operationalizations of
-uncertainty are ambiguously related, and 
-tend to only consider a small number of behavioral
-choices.  Here we use evolutionary agent-based modeling to consolidate
-models of uncertainty in social learning evolution to address these issues.
-We model societies of agents who perform one of a number
-of possible behaviors to acquire payoffs in a time-varying environment.
-We identified complex patterns in social learning evolution depending on contextual
-uncertainty variables: environmental variability, ambiguous payoffs, 
-decision sets size, and effective lifespans. 
-Our work advances social learning evolution theory in a way that could help 
-guide human, non-human, and artificial intelligence towards optimal responses 
-to existential threats and new opportunities.\footnote{This document contains
+Social learning is essential to human survival---it is a critical adaptation for dealing with uncertainty.
+However, uncertainty takes many forms.
+We identified four theoretically important types of uncertainty: temporal environmental variability, ambiguous payoffs, decision set size, and effective lifespans.
+We used this framework to study conditions for the evolution of social learning in populations with cognitively realistic individual learning capacities.
+We used evolutionary agent-based modeling to track how often social learning evolved.
+Agents performed one of several behaviors to acquire payoffs.
+Individual learning used the softmax algorithm.
+Social learning occurs between generations  through vertical and oblique transmission.
+Different types of uncertainty had different effects.
+Temporal environmental variability suppressed social learning.
+Larger decision set sizes promoted social learning.
+Payoff ambiguity and lifespan had more complex effects on social learning, dependent on other uncertainty parameters.
+This shows the importance of clearly operationalizing uncertainty in theories of social learning evolution.
+% Social learning is essential to human survival. It is likely to evolve when it is more
+% efficient than asocial, trial-and-error learning. Theoretically, social learning
+% is adaptive for some uncertainty, but too much uncertainty makes
+% social information unreliable. This fact is empirically
+% supported across biology and human sciences. However, it is unclear how
+% specific classes and types of uncertainty affect social
+% learning evolution. Furthermore, existing models and experimental operationalizations of
+% uncertainty are ambiguously related, and 
+% tend to only consider a small number of behavioral
+% choices.  Here we use evolutionary agent-based modeling to consolidate
+% models of uncertainty in social learning evolution to address these issues.
+% We model societies of agents who perform one of a number
+% of possible behaviors to acquire payoffs in a time-varying environment.
+% We identified complex patterns in social learning evolution depending on contextual
+% uncertainty variables: environmental variability, ambiguous payoffs, 
+% decision sets size, and effective lifespans. 
+% Our work advances social learning evolution theory in a way that could help 
+% guide human, non-human, and artificial intelligence towards optimal responses 
+% to existential threats and new opportunities.
+\footnote{This document contains
 \total{citnum} references.}  

### 2022-07-15 ms.tex
Updates from Overleaf

@@
 \usepackage{graphicx}
+\usepackage{comment}
 
@@
 \section{Introduction}
-\cm{Notes on our June 2 discussion (USPs): "Uncertainty favors social learning" is a widespread belief.
-But it is operationalized in different ways, and oftentimes it does not reflect REAL uncertainty.
-Selling points of this paper 1) real uncertainty, 2) 4 kinds uncertainty, 3) cognition (soft-max temperature varies how much explores).}
 
-%% for inclusion in the social learning ms
+Social learning enhances problem solving when acquiring information from others is more efficient than learning on one's own~\cite{Laland2004}.
+However, social learning can also lead individuals astray if, for example, they are copying outdated information.
+Theoretical models have helped clarify the circumstances under which social learning should be evolutionarily favored ~\cite{BoydRicherson1985}.
+This theoretical work has motivated much empirical research and helped predict social learning behavior in humans and other species ~\cite{McElreath2005,Kendal2018,Allen2019}.
 
-Decision-making under uncertainty is fundamental challenge for any organism.
-Uncertainty weighs particularly heavily on humans adaptation because of our long lifespans, cosmopolitan distribution, and the resulting necessity to adapt to relatively coarse-grain environments \cite{levins1962}.
+One proposal arising from this literature maintains that social learning is as an adaptation for dealing with uncertainty, and one that humans heavily rely on.
+Uncertainty weighs particularly heavily on human adaptation because of our long lifespans, cosmopolitan distribution, and the resulting necessity to adapt to relatively coarse-grain environments \cite{levins1962}.
+However, the term ``uncertainty" often conflates several different interpretations of that word.
+For example, different models define uncertainty in terms of the rate of environmental change, spatial environmental variation, or the reliability of information acquired from the environment.
+Furthermore, in translating mathematical models to verbal predictions, the formal meaning of terms like uncertainty is often lost \cite{lawson1988probability}, facilitating such conflation.
+As the number of formal models of social learning have expanded, an ever increasing number
+of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of uncertainty have made it difficult to compare across models and consolidate our understanding of the contexts in which social learning is adaptive.
+Finally, while risk and uncertainty are often used interchangeably to refer to non-deterministic outcomes, it can be important to distinguish a narrower definition of uncertainty wherein the probabilities of outcomes remain unknown \cite{knight1921, volz2012}.
 
-While the importance of decision-making under uncertainty is generally acknowledged, there is often some confusion about what constitutes uncertainty.
-First, uncertainty needs to be distinguished from risk.
-While the concepts sound similar, uncertainty and risk are quite different.
-Both refer to the existence of non-deterministic outcomes, but with risk, outcomes can be represented probabilistically, whereas uncertainty implies that the probabilities of outcomes remain unknown \cite{knight1921}.
-As it doesn't lend itself to simple mathematical representation, uncertainty presents substantial analytical challenges as first noted by \cite{keynes1921}.
+Other (asocial) forms of learning may also be adaptations to uncertainty, but are usually under-emphasized in this literature.
+Because cultural evolutionary models are more often used to explain social learning mechanisms, they tend to use a single, and often under-powered individual-learning mechanism for comparison.
+This modelling decision may underestimate the extent to which individual learning can address the adaptive challenges solved by social learning, but also underestimate the quality of information available for social learning.
 
-Despite the technical difficulties of dealing with uncertainty, addressing it is an essential task because it potentially changes our understanding of decision-making in a qualitative manner.
+To address these concerns we developed an evolutionary agent-based model that simultaneously operationalizes several
+different forms of uncertainty and endows agents with a powerful learning mechanism.
+We have chosen to model four kinds of uncertainty that are common in cultural evolution models and the related empirical literature:  (1) temporal environmental variability; (2) selection set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning).\ps{citation needed}.
+The model also involves a more cognitively realistic and empirically-motivated learning mechanism, the softmax algorithm.
+This allows a more accurate assessment of tradeoffs between social and individual learning by fleshing out a learning mechanism that makes full use of the individually and socially learned data.
+We use this integrated model to ask what kinds of uncertainty are likely to favor social learning, and to clarify the logic of why this would be the case.
+
+In the remainder of this introduction we describe previous research on the forms of uncertainty and the learning mechanism we include in our model.
+We then present how our evolutionary agent-based model works.
+Finally, we explain the logic underlying the result that different forms of uncertainty can either suppress or encourage the evolution of social learning.
+
+%% \cm{from Jamie's intro, not sure we should incorporate the rest here since our model doesn't speak much to things like heavy tailed distributions or adaptive toolkit work: Despite the technical difficulties of dealing with uncertainty, addressing it is an essential task because it potentially changes our understanding of decision-making in a qualitative manner.
 The dominant approach to understanding decisions for choices with variable outcomes is expected utility theory (EUT).
@@
 In particular, the probability density function of an outcome that needs to be learned, but for which opportunities for learning are highly constrained, will be heavy-tailed and expected-utility calculations will not work because of the resulting undefined mass-generating function.
-Uncertainty implies heavy-tailed probability distributions and heavy-tailed distributions require different analytical methods \cite{nair_etal2022}.
-
-The heuristic-based adaptive-toolbox approach of \cite{todd_gigerenzer2000} provides an alternative strategy for understanding decision-making under uncertainty.
+Uncertainty implies heavy-tailed probability distributions and heavy-tailed distributions require different analytical methods \cite{nair_etal2022}....para...The heuristic-based adaptive-toolbox approach of \cite{todd_gigerenzer2000} provides an alternative strategy for understanding decision-making under uncertainty.
 There is a strong intuition that uncertainty should activate specific social-learning heuristics.
-Within the cultural-evolution literature, uncertainty is generally thought to lead to a social heuristic known as \emph{conformist-biased learning} \cite{boyd_richerson1985, henrich_boyd1998, muthukrishna_etal2016}.
-
-True uncertainty arises when an organism lacks the capacity to learn about the possible outcomes of a decision task.
+Within the cultural-evolution literature, uncertainty is generally thought to lead to a social heuristic known as \emph{conformist-biased learning} \cite{boyd_richerson1985, henrich_boyd1998, muthukrishna_etal2016}....para...True uncertainty arises when an organism lacks the capacity to learn about the possible outcomes of a decision task.
 This is very likely for a cosmopolitan species living in a coarse-grain environment.
@@
 Non-stationary environmental change \cite{kay_king2020}.
-These potential sources of uncertainty can also interact.
-
-\cm{CUT in favor of uncertainty intro: Social learning enhances problem solving when acquiring information from others is more efficient than learning on one's own~\cite{Laland2004}.
-However, social learning can also lead individuals astray if, for example, they are copying outdated information.
-Theoretical models have helped clarify the circumstances under which social learning should be evolutionarily favored.
-For example, environments that change across time favor learning from others (as opposed to having a genetically fixed behavior) ~\cite{BoydRicherson1985,Henrich1998}, so long as the environments are not so variable that the social information reflects outdated and maladaptive behavior point~\cite{Rogers1988,Feldman1996, aoki2014evolution}.
-\cm{check that the citations still accurate}.
-This theoretical work has motivated much empirical research and helped predict social learning behavior in humans and other species ~\cite{McElreath2005,Kendal2018,Allen2019}.
-}
-
-From this literature, the idea that uncertainty supports social learning has proliferated, but the term ``uncertainty" often conflates several different interpretations of that word.
-For example, different models define uncertainty in terms of the rate of environmental change, the correlation between spatial environments, or the reliability of information acquired from the environment.
-Furthermore, in translating mathematical models to verbal predictions, the formal meaning of terms like uncertainty is often lost \cite{lawson1988probability}, facilitating such conflation. 
-%Furthermore, a
-And as the number of formal models of social learning have expanded, an ever increasing number
-of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of uncertainty have made it difficult to compare across models and consolidate our understanding of the contexts in which social learning is adaptive.
-
-To address these concerns we developed an empirically-motivated, evolutionary agent-based model that simultaneously operationalizes four %principal components 
-different forms of uncertainty: (1) temporal environmental variability; (2) selection set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning).
-These were chosen because modeling and empirical
-studies across taxa tend use one or more of these uncertainty dimensions\ps{citation needed}.  
-The model also involves a more cognitively realistic learning mechanism, the softmax algorithm, which allows us to more accurately assess some of the likely tradeoffs between social and individual learning.
-We use this integrated model to ask what kinds of uncertainty are likely to favor social learning, and to clarify the logic of why this would be the case.
-Answering this question is critical for understanding human behavior adapting to a rapidly changing world, both to mitigate existential threats~\cite{Moya2020,Jones2021}, and to capitalize on new opportunities such as transitioning to clean energy use and production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
-
-In the remainder of this introduction, we further unpack our motivation for this work justify our approach.
-We then present our model and the results of our analyses.
-We conclude with a discussion of our results and their implications for our understanding of social learning, uncertainty, and cultural evolution.
+These potential sources of uncertainty can also interact.}
 
@@
 When external or internal shocks (e.g., climatic events, migration, technological paradigm shifts) occur, strategies that were previously adaptive may no longer be optimal.
-The difficulty in predicting either when such shocks will occur or what behaviors will adaptive in the resulting environments leads to uncertainty.
-Temporal environmental variability is fundamental to most evolutionary models of social learning, yet even this is implemented in several ways.
-It is usually modeled as an independent probability of the environment changing its state each generation ~\cite{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}.
-The probabilities of environmental change are usually fixed, %~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution},
-but they have also been modeled as deterministic cycles ~\cite{Feldman1996, aoki2014evolution} or as variable rates \cm{who does this?}\ps{Yeah, I'm not even sure what variable rates means in this context}.
+The difficulty in predicting either when such shocks will occur or what behaviors will be adaptive in the resulting environments leads to uncertainty.
+
+Temporal environmental variability is fundamental to most evolutionary models of social learning.
+Such fluctuations have been proposed as an important selective pressure for learned as opposed to genetically fixed behaviors ~\cite{Richerson2000}.
+On the other hand, environments that change too quickly will lead the population to have outdated, and therefore maladaptive information, favoring individual updating over social learning point~\cite{Feldman1996, BoydRicherson1985}.
+This suggests that intermediate levels of temporal variation are important for the evolution of social learning mechanisms ~\cite{aoki2005}.
+
+Despite the centrality of temporal fluctuations, even this construct is implemented in several ways \cite{aoki2014evolution}.
+Most commonly, it is modeled as an independent probability of the environment changing its state each generation ~\cite{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}.
+The probabilities of environmental change are usually fixed per generation, %~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution},
+but they have also been modeled as deterministic cycles ~\cite{Feldman1996, aoki2014evolution}.
 Furthermore, the consequences of environmental change can range from mild to  catastrophic.
@@
 This means that all individuals with previously maladaptive behaviors then have adaptive behaviors upon the environment changing ~\cite{perreault2012bayesian}.
+Which strategy one chooses for modelling temporal change can have consequences for at least some of our inferences  ~\cite{aoki2014evolution}.
 
@@
 This is a mathematical fact at the core of information theory: the number of bits required to reliably encode the optimal solution increases by one every time the selection set doubles in size  \cite{mackay2003information}.
-This is intuitive; the more options one could potentially investigate, the greater one's uncertainty about which option is the best choice.
+This is intuitive; the more options to consider, the greater one's uncertainty about which option is the best choice.
+
 In studies of social learning, the size of the selection set is very often limited to just two options. 
-For example, in empirical studies of \emph{bombus terresteris} (bumble
-bee)~\cite{Baracchi2018} and \emph{parus major} (great tit)~\cite{Aplin2017},
-experimenters provided two behaviors for
+For example, in empirical studies of \emph{bombus terresteris} (bumble bee)~\cite{Baracchi2018} and \emph{parus major} (great tit)~\cite{Aplin2017}, experimenters provided two behaviors for
 the bees or birds to choose from, where one yielded a higher payoff than the other. %respectively, each yielding greater or smaller payoffs depending on experimental treatment. 
-Many human studies have also used just two
+Similarly, many human studies have used just two
 or three possible behaviors~\cite{McElreath2005,Toyokawa2019}.
-Modeling studies have often used just two 
-behaviors~\cite{Rogers1988,Feldman1996,Rendell2010,perreault2012bayesian}, though others have studied systems with larger selection sets where the number of options is usually not explicitly specified~\cite{boyd1995does,Enquist2007}.
-It is very rare, however, to find the size of the selection set manipulated as a measure of changing uncertainty.
+The simpler empirical choices are often motivated by modeling studies with similar formulations ~\cite{boyd1995does, Rogers1988,perreault2012bayesian}.\cm{pretty sure boyd1995 uses same trick as rogers 88 so not sure why they were being used as illustrating separate kinds of behavior selection sets.
+correct if wrong} Larger, or more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks ~\cite{derex2013, wasielewski2014}, but these map on imperfectly to the theoretical literature.
+Some models have studied systems with larger, but defined, selection sets ~\cite{Rendell2010}, while in others the number of options is subsumed under probabilities of getting a high payoff ~\cite{Enquist2007}.
+Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviors through time ~\cite{Feldman1996}, but it is very rare to find the size of the selection set manipulated \emph{within} generations as a measure of changing uncertainty in cultural evolutionary models.
 
@@
 Smaller differences between payoffs corresponds to larger ambiguity.
+Payoff ambiguity has been manipulated in both theoretical ~\cite{perreault2012bayesian} and empirical ~\cite{McElreath2005l, Morgan2012} studies, both of which support the claim that payoff ambiguity increases the reliance on social information.
 Importantly, payoff ambiguity %differs from selection set size in that it not only affects uncertainty, it also directly
@@
 It is an iterative process by which one repeatedly acquires information, forms representations and predictions, and tests and refines those representations and predictions.
-It therefore stands to reason that the more opportunities one has for learning, the more one can in principle reduce one's uncertainty.
+It therefore stands to reason that the more opportunities one has for learning, the more one can in principle reduce one's uncertainty, assuming the environment has not changed in the meantime.
 Similarly, a reduction in the number of opportunities to learn will increase the uncertainty about whether one has accurately learned about the available behavioral options and their associated payoffs.
 We refer to the number of learning opportunities as an individual's effective lifespan to imply that it is the number of opportunities to learn throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.
-Empirically, the age of an individual will often correspond with the number of learning opportunities they have had.
-Aplin et al.
+
+Empirically, the number of learning opportunities can be manipulated in the lab, but will also correspond with an individual's age the real world.
+In multi-round studies of information use in novel tasks, US participants' use of social information declined precipitously across rounds ~\cite{McElreath2005}, suggesting they were more likely to use social information when they were most uncertain about the task early on.
+In a more naturalistic context, Aplin et al.
 (2017) \nocite{Aplin2017} found that younger great tits more readily used social information compared with older individuals, possibly because they had accrued less information via individual learning, and also possibly because younger individuals have the most to gain (given their expected remaining lifespan) by switching to superior behavioral options.
@@
 They just showed that young guppies exposed to reliable models were more likely to use social information later.
-I also added some human studies, which seems important.} Cross-cultural studies on humans have shown that young children are more likely to acquire their beliefs and simple skills from their parents than are older children or adults, which is also at least partly due to the differential knowledge accrual between young children and the older adults to whom they direct the most trust and attention \cite{kline2013teaching, Reyes2016}.
-\cm{not sure the second phrase is warranted.
-Can't seem to find whether social learning overall is  }
+I also added some human studies, which seems important.} Cross-cultural studies on humans have shown the importance of childhood as a phase of heavy social learning ~\cite{Reyes2016}.
+Young children are more likely to acquire their beliefs and simple skills from their parents than are older children or adults, which is at least partly due to the differential knowledge accrual between young children and the older adults to whom they direct the most trust and attention \cite{kline2013teaching}.
 %The age of individuals was found to have an effect on social learning in both \emph{parus major}~\cite{Aplin2017} and \emph{poecilia reticulata} (guppies)~\cite{Leris2016}.
@@
 Individuals with shorter effective lifespans will end their lives with more uncertainty about which behaviors are optimal, and thereby transmit some of that uncertainty to anyone who learns from them.
-The effective lifespan for learning varies both across individuals and across species, yet there is little formal theory incorporating this form of uncertainty into our understanding of the evolution of social learning.
+The effective lifespan for learning varies across tasks, individuals, and species, yet most models assume one learning opportunity per generation ~\cite{Feldman1996,Henrich1998, perreault2012bayesian}.
+Some models do allow several cultural generations within 1 genetic generation ~\cite{Enquist2007}, but little formal theory explicitly examines the role of uncertainty based on number of learning opportunities into our understanding of the evolution of social learning.
 
@@
 
-\subsection{Varieties of learning, social and otherwise} (CRISTINA) 
+\subsection{Other adaptations to uncertainty}
+
+\begin{comment}
+
 \cm{I think a lot of this may be too much detail.
@@
 Yes we've made choices about things like horizontal vs vertical, but i think we can just justify that when we introduce the model }
-\ps{I agree with Cristina here.
+ps{I agree with Cristina here.
 I think we should use this section to justify our way of modeling individual and social learning, which is different from previous models.
@@
 In particular, we should set up (1) social learning as an initial scaffold for future social learning, and (2) softmax individual learning which involves some greediness with occasional trial and error.}
+
 To add to confusion about how to integrate diverse models of social learning
@@
 
-Social learning is the adaptive icing on the cake of intelligent adaptations to ecological uncertainty.
-To deal with uncertainty as individuals, human experiment participants have been observed to update their tendency for exploring alternative behaviors based on how much uncertainty there is globally.
-Furthermore, correlations in uncertainty between potential behaviors, humans tend to adopt directed exploration strategies that favor testing behaviors with greater observed payoff variance \cite{Wilson2014,Gershman2019}.
-Many models of social learning assume little to nothing about the cognitive capabilities of their agents (Cristina unpack this in another paragraph, using the uncertainty studies spreadsheet?).
-We do not do this because \emph{blackboxing}, or ignoring, cognitive mechanisms is “bad” \cite[p.
-658]{Heyes2016, Kendal2018}, but because it is theoretically meaningful.
-In order to understand how social learning evolves as an adaptation to uncertainty, the model is strengthened by assuming a more biologically plausible, and evolutionarily accurate, model of cognition capable of maximizing payoffs under uncertainty for an individual.
-In our model we do not impose any structure in randomness between behaviors, so our cognitive model is only sensitive to total randomness.
-Specifically, we will adopt the softmax distribution for function for selecting a behavior based on its observed payoffs–greater payoff variance means any one behavior is more likely to be selected.
+\end{comment}
 
-\paragraph{Meaning of uncertainty in ecology (and cognitive and social sciences?) } (JAMIE, PAUL?) \ps{I've added a bunch to the section on different types of uncertainty, which could be more fleshed out if we like.
+Social learning is the adaptive icing on the cake of other cognitive adaptations to ecological uncertainty. 
+While the literature reviewed above suggests that several forms of uncertainty play a role in favoring the evolution of social learning, several other cognitive mechanisms have also evolved in response to uncertainty ~\cite{volz2012}.
+Many of these are flexible learning mechanisms that do not require assessing others' information.
+For example, people in experimental studies increase their exploratory behavior when total uncertainty in the task increases and are more likely to test %Furthermore, correlations in uncertainty between potential behaviors, humans tend to adopt directed exploration strategies that favor testing
+behaviors with greater observed payoff variance \cite{Wilson2014,Gershman2019}.
+
+Many models of social learning assume little, or nothing, cognitive capabilities of their agents.
+For example, a common modelling strategy compare the payoffs of agents with different pure learning strategies (some will always engage in social learning, and others in individual learning) while revealing nothing about the cognition underlying individuals' decisions  ~\cite{BoydRicherson1985, Rogers1988, aoki2005}.
+Some more complicated learning strategies that make use of both socially and individually learned information have been proposed ~\cite{Enquist2007, perreault2012bayesian}, but these are seldom designed to reflect cognitive mechanisms for integrating information.
+Though such simplifications are often useful, several authors have warned of the risks to \emph{blackboxing}, or ignoring, cognitive mechanisms \cite[p.
+658]{Heyes2016, Kendal2018}, given such details may be theoretically meaningful.
+In order to understand how social learning evolves as an adaptation to uncertainty, we need to endow agents with a  biologically plausible cognition capable of integrating information from various sources in a payoff-maximizing way.
+\cm{I don't understand this next sentence, but think it can be cut with no loss of meaning: In our model we do not impose any structure in randomness between behaviors, so our cognitive model is only sensitive to total randomness.} To do so, we let agents see the payoffs to behaviors and use the softmax function to convert these observations to a probability distribution from which they strategically select their own behavior.
+\cm{does this still make sense?
+and does it need a citation?}
+
+%\paragraph{Meaning of uncertainty in ecology (and cognitive and social sciences?) } (JAMIE, PAUL?) \ps{I've added a bunch to the section on different types of uncertainty, which could be more fleshed out if we like.
 I don't think an additional section here is needed.}
-We need to support our claim that these four classes of uncertainty really 
-count as forms of uncertainty and show how it is consistent across ecology,
-and maybe connect to uncertainty in cognitive and social sciences more broadly.
+%We need to support our claim that these four classes of uncertainty really count as forms of uncertainty and show how it is consistent across ecology, and maybe connect to uncertainty in cognitive and social sciences more broadly.
 
-\paragraph{Evolutionary ABMs for social learning evolution theory development} (PAUL)
-\ps{I'm not sure a section is needed on this, but we can add something about how ABMs allow us to capture complexity not possible with purely mathematical approaches.
+%\paragraph{Evolutionary ABMs for social learning evolution theory development} (PAUL)
+%\ps{I'm not sure a section is needed on this, but we can add something about how ABMs allow us to capture complexity not possible with purely mathematical approaches.
 I think it probably makes the most sense to address this at the beginning of the model description.}
@@
 
-\paragraph{Disc. 2: Foundation for studying social learning evolution with group
-structure or other topics(PAUL, JAMIE, CRISTINA)}~\cite{Katsnelson2014}.
+% \paragraph{Disc. 2: Foundation for studying social learning evolution with group
+% structure or other topics(PAUL, JAMIE, CRISTINA)}~\cite{Katsnelson2014}.
 
@@
 translated evolutionary algorithm may take to converge.
+
+Taking the functional form of uncertainty seriously is critical for understanding how humans adapt to an uncertain and rapidly changing world, both to mitigate existential threats~\cite{Moya2020,Jones2021}, and to capitalize on new opportunities such as transitioning to clean energy use and production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
 

### 2022-07-15 ms.tex
updated nagents sensitivity and started Model revision

--- 2022-07-05 ms.tex
@@
 with probabilistic
-payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.  Each behavior
-$b$ yields Bernoulli payoffs: payoff of 1 with probability $\pi_b$ and zero payoff
-with probability $1 - \pi_b$; $\pi_b$ is therefore also the expected payoff of
-behavior $b$. One behavior in each generation is optimal and pays off $\pihigh$,
-while the rest pay off $\pilow < \pihigh$.  Model agents must decide which behavior
-to perform at each time step.  To do this, agents use an explore-exploit strategy to
-sometimes try the most profitable behavior they know about, and other times try
-alternatives that may pay off more reliably.  We developed a series of computational
-analyses by systematically varying uncertainty parameters and observing the
-frequency that model populations evolve to be social learners, the average payoffs
-accrued by agents in each setting, and the time it takes for model populations to
-reach fixation (agents all social or all asocial learners). Model dynamics are
-illustrated in Figure~\ref{fig:schematic}.
+payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
 
@@
 
-        $\tau$ & Softmax temp.; $\uparrow=$more exploration, $\downarrow=$more
-                    exploitation 
-               & 0.01, \textbf{0.1}, 1.0 \\
+        $\beta$ & Softmax greediness; $\uparrow=$more exploitation, $\downarrow=$more
+                    exploration 
+               & 100, \textbf{10}, 1 \\
 
@@
 \end{table}
+
+\subsection{Agents and learning}
+
+All agents perform individual, trial-and-error learning over their lifespan.
+This learning is guided based on undirected, softmax search which drives
+agents to explore all behavioral options in the selection set when 
+the agent is more uncertain which is optimal, and to exploit the most profitable
+behaviors when the agent is more certain which are most beneficial.
+
+\subsection{Dynamics}
+
+\subsubsection{Initialization}
+
+At generation start, one of the behaviors is set to 
+yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
+expected payoffs $\pilow$. At each time step, agents perform behavior $b$ 
+with softmax-weighted probability
+\begin{equation}
+  \Pr(\text{Agent $i$ performs behavior $b$}) = 
+    \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}},
+\end{equation}
+\noindent
+where $\beta$ is a parameter that adjusts how frequently agents perform 
+behaviors with high expected payoffs (larger $\beta$) versus how frequently
+agents explore alternative behaviors (smaller $\beta$)~\cite{McElreath2005}. 
+Agents probabilistically recieve a payoff of 0 or 1 depending on whether the
+bandit paid off. Behavior payoffs are represented as a draw from a 
+Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from
+behavior $b$.  For concreteness we denote this probabilistic payoff
+$\bandit$. On performing behavior $b$, agent $i$ updates the
+corresponding \emph{behavior count} by 1, $c_{ib} \leftarrow c_{ib} + 1$, and then
+the expected payoffs calculated for that behavior are updated with
+exponentially-weighted averaging
+\begin{equation}
+  \ledger \leftarrow \ledger + \frac{\bandit - \ledger}{c_{ib}}.
+\end{equation}
+\noindent
+This procedure continues for $L$ time steps within each generation
+(Figure~\ref{fig:schematic}B).
+
+\subsubsection{Intragenerational dynamics}
 
@@
 
-At generation start, one of the behaviors is set to 
-yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
-expected payoffs $\pilow$. At each time step, agents perform behavior $b$ 
-with softmax-weighted probability
-\begin{equation}
-  \Pr(\text{Agent $i$ performs behavior $b$}) = 
-    \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}},
-\end{equation}
-\noindent
-where $\beta$ is a parameter that adjusts how frequently agents perform 
-behaviors with high expected payoffs (larger $\beta$) versus how frequently
-agents explore alternative behaviors (smaller $\beta$)~\cite{McElreath2005}. 
-Agents probabilistically recieve a payoff of 0 or 1 depending on whether the
-bandit paid off, equivalent to a draw from a Bernoulli distribution with 
-mean $\pi_b$. For concreteness we denote this probabilistic payoff
-$\bandit$. On performing behavior $b$, agent $i$ updates the
-corresponding behavior count by 1, $c_{ib} \leftarrow c_{ib} + 1$, and then
-the expected payoffs calculated for that behavior are updated with
-exponentially-weighted averaging
-\begin{equation}
-  \ledger \leftarrow \ledger + \frac{\bandit - \ledger}{c_{ib}}.
-\end{equation}
-\noindent
-This procedure continues for $L$ time steps within each generation
-(Figure~\ref{fig:schematic}B).
+\subsubsection{Intergenerational dynamics}
 
@@
 conditions are met}.
+
+\subsection{Computational analyses}
+
+We developed a series of computational
+analyses by systematically varying uncertainty parameters and observing the
+frequency that model populations evolve to be social learners, the average payoffs
+accrued by agents in each setting, and the time it takes for model populations to
+reach fixation (agents all social or all asocial learners). Model dynamics are
+illustrated in Figure~\ref{fig:schematic}.
 
@@
 variables over systematically varied uncertainty factor values.
+
+\subsubsection{Implementation}
 Our model was implemented in the Julia programming language~\cite{Bezanson2017} 
@@
 on the Sherlock supercomputing cluster at Stanford University. Model code and
-data are publicly available on GitHub\footnote{\url{https://github.com/mt-digital/UncMod}} 
-and OSF.io\footnote{\mt{TODO}}.
+data are publicly available on GitHub\footnote{\url{https://github.com/mt-digital/UncMod}}.
 

### 2022-07-16 ms.tex
revised Model section intro paragraphs; next: revise details of each model component

@@
 Furthermore, the consequences of environmental change can range from mild to  catastrophic.
-In the latter case, a change of environment results in the total elimination of any adaptive behavior, which must be learned \emph{de novo} for the new environment ~\cite{Rogers1988}.
+In the latter case, a change of environment results in the total elimination of any adaptive behavior, which must be learned \emph{de novo} for the new environment~\cite{Rogers1988}.
 Such catastrophic environmental changes present a large adaptive challenge as individuals cannot bank on accumulated information from previous generations.
@@
 Smaller differences between payoffs corresponds to larger ambiguity.
-Payoff ambiguity has been manipulated in both theoretical ~\cite{perreault2012bayesian} and empirical ~\cite{McElreath2005l, Morgan2012} studies, both of which support the claim that payoff ambiguity increases the reliance on social information.
+Payoff ambiguity has been manipulated in both theoretical ~\cite{perreault2012bayesian} and empirical ~\cite{McElreath2005, Morgan2012} studies, both of which support the claim that payoff ambiguity increases the reliance on social information.
 Importantly, payoff ambiguity %differs from selection set size in that it not only affects uncertainty, it also directly
@@
 
-\cm{Other choices we made that might need to be justified: 1) softmax: existing models underestimate the power of learning from experience by not having a rich cognition.
+% \cm{Other choices we made that might need to be justified: 1) softmax: existing models underestimate the power of learning from experience by not having a rich cognition.
 This rich cognition can improve both individual learning and help social learners recover from outdated / misleading social info.
@@
 
+To address our research questions we developed an evolutionary agent-based model of
+social learning evolution.  Evolutionary agent-based models simulate changes in
+prevalence of a phenotype over several generations---in this model the phenotype, or
+``trait'', is whether or not an agent engages in social learning.  In the model, a
+population of $N$ individuals each must decide which of $B$ behaviors to perform at
+each time step within a generation consisting of $L$ time steps. At the end of each
+generation, agents are selected with replacement, biased by accumulated payoffs
+within the generation, from the population to reproduce another $N$ agents. Agents
+who inherit the social learning trait then learn about behavioral payoffs from the
+previous generation, while asocial learners begin life with no \emph{a priori}
+knowledge of the world.  Each behavior is a ``bandit'', a common modeling and
+experimental approach for representing behaviors with Bernoulli-distributed
+payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
+All bandits thus yield a payoff of 1 or 0 with a certain probability.  One of the
+bandits/behaviors in the model is more likely to pay off than all the rest.  Agents
+optimize their net payoffs over their lifespan by quickly figuring out which
+behavior is optimal and performing it as often as possible within their lifespan.
+
+We operationalized the four ``principal components'' of uncertainty that affect the
+ability of agents to find and choose the optimal behavior. Recall these varieties of
+uncertainty are \emph{environmental variability}; \emph{payoff ambiguity};
+\emph{selection set size}; and the \emph{effective lifespan}. Environmental
+variability is the probability that the behavior yielding the optimal payoff changes
+from one generation to the next. We do not consider cases where the optimal behavior
+varies within a generation. This is empirically justified since cultural evolution
+occurs when meta-cognitive strategies and information are transferred or not via
+learning and social influence, instead of truly by physical reproduction and death
+as in genetic evolution.  The selection set size is the total number of possible
+behaviors agents choose from, assumed to be constant within a simulation.  We
+operationalized payoff ambiguity by manipulating the payoff difference between optimal
+and non-optimal behaviors. The effective life span is the
+number of time steps in which agents perform behaviors within a generation. 
+Our model is not spatial, so agents have free, instant
+access to all behaviors, and there is no spatial uncertainty, 
+as might be the case for humans in a computer-based lab
+experiment~\cite{McElreath2005,Morgan2012}.  Spatial dimensions could also be
+considered irrelevant if costs associated with accessing a behavior were equal,
+e.g., if it was assumed to be equally easy for bumblebees to fly to alternative
+flower ``species''~\cite{Baracchi2018} or for great tits to fly to different food
+sources~\cite{Aplin2017}.  Each simulated environment provides a distinct challenge
+to the agents, which will lead agents to differently evolve to become social
+learners or not depending on which of those two strategies optimizes net payoffs.
+
+\emph{Agents} here are autonomous, intelligent, simulated problem solvers. Each
+agent evaluates its environment and chooses how to act within that environment based
+on a set of empirically-motivated rules.  Our agents select which behavior to do
+probabilistically, weighted by the softmax function applied to the mean payoff they
+have observed for each behavior. The softmax function is a biologically plausible
+generalization of behavior selection under uncertainty that enables agents to often
+greedily exploit the most lucrative behavior (based on their observations) but also
+to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
+Such individual-level intelligence is a critical adaptation that has apparently
+co-evolved with the capacity for social learning, and has a marked influence on the
+cultural evolution of social learning as we will demonstrate in our Analysis.
+
+In \emph{evolutionary} agent-based models like ours, agent life cycles are
+programmed to cause agents to reproduce and die off, where reproducers pass on
+heritable traits to their offspring. This sets up an inter-generational structure
+that we also use as a scaffold for social learning: we assume social learning occurs
+\emph{obliquely}\mt{is ``oblique learning'' understood to include parents by default
+or do we need to say ``or vertically''?}, meaning learning happens when a new
+generation of agents each select a teacher from the previous generation, possibly
+including their parents.  Natural selection occurs in the model when agents with higher
+payoffs preferentially reproduce. This is a model of cultural evolution, so
+``reproduction'' means teaching the meta-cognitive strategy of whether one should learn
+socially at all; ``death'', in this interpretation, means
+loss of the potential to socially influence others. 
+Evolutionary agent-based models are powerful, but their components need to be
+carefully specified and justified in relation to empirical facts.
+
+Evolution, then, acts as an optimization routine to identify which heritable trait
+values are most rewarded under in different environmental uncertainty contexts,
+defined by different uncertainty parameter settings
+(Table~\ref{tab:uncertaintyParameters}).  The main outcome variable we analyze in
+this model is therefore the value of agents' heritable trait, namely whether or not
+an agent, $i$, learns socially, denoted $s_i$. $s_i$ is a binary variable: it is 1
+if the agent is a social learner, and 0 otherwise. We will aggregate $s_i$ over all
+agents and simulation trials to understand the affects of different uncertainty
+parameter settings. We will support conclusions we make from observing patterns in
+the outcomes with additional measures of the average time it takes for the
+population to either all have $s_i = 1$ or all have $s_i = 0$, and the expected
+payoffs in different contexts among populations that are initialized to all have
+$s_i = 1$ or to all have $s_i = 0$. These outcome measures will be used to predict
+the evolutionarily-favored strategy (to learn socially or not), the number of
+generations it will take for a population to evolve the optimal strategy, and the
+expected payoffs in populations performing the optimal strategy, in several specific
+uncertainty contexts. To understand how different varieties of uncertainty interact
+to affect the evolution of social learning, we systematically created an array of
+simulated environments by systematically varying the uncertainty parameters.
+
+% \begin{itemize}
+%   \item
+%     Softmax-guided behavior selection
+%   \item
+%     Oblique learning, not horizontal; no intragenerational change in optimal
+%     behavior, only intergenerational
+%   \item 
+%     Payoff-biased teacher selection, not aggregation over everyone or large group,
+%     as in conformist transmission
+%   \item
+%     Not spatial in any way. Agents need only to choose among potential behaviors
+%     and the behavior is instantly performed, as a real human can when pointing
+%     and clicking on a computer screen. This approximation could also hold when
+%     all behavioral options require an identical amount of time/money/resources
+%     to enable the agent to actually do the behavior (drive to work, walk to a
+%     watering hole, fly to a flower to gather pollen, etc.). Since teacher and
+%     behavior selection and reproduction are biased by relative payoffs there
+%     is no effect on model dynamics if cost of access is the same for each behavior.
+% \end{itemize}
+
+\clearpage
+
+\begin{figure}
+  \caption{Agents are randomly initialized as social learners or not, with their
+  payoff observations all initialized to zero (A). Then agents begin selecting
+and performing behaviors and accumulating payoffs, which goes on for $L$
+timesteps (B). After $L$ time steps, agents are selected to reproduce,
+social learner children learn from a member of their parent's generation, and
+the previous generation dies off (C). The simulation stops if children are all
+social or asocial learners (i.e.\ the system reaches fixation), 
+otherwise repeat another generation and evolution (3).}
+  \label{fig:schematic}
+  \centering
+    \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+\end{figure}
+
+\subsection{Model environment and uncertainty}
+
+\begin{itemize}
+  \item 
+    A number of parameters specify the structure of the environment in which
+    agents sovle problems and adapt by adjusting their social learning through
+    evolution. \mt{Introduce all parameters; do not give values, but ref
+    (Table~\ref{tab:uncertaintyParameters})}
+  \item
+    \mt{Bandits and payoffs in more detail}
+\end{itemize}
+
+\vspace{2em}
 \begin{table}[h]
-    \caption{Dynamic agent-level variables. Each has an implicit time dependence.}
+\caption{Uncertainty parameters.  Bold indicates default value tested} %\emph{default value tested}.}
+    \label{tab:uncertaintyParameters}
+    \centering %\hspace{-3em}
+    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule
+
+        Symbol & Description & Values tested \\
+
+        \midrule
+
+        $u$    & Probability optimal behavior changes between generations 
+               & 0.0, 0.1, \ldots, 1.0 \\
+
+        $B$       & Number of ``bandits'', i.e., behavior options
+                  & 2, 4, 10 \\
+
+        $\pihigh$ & Probability that the unique optimal behavior pays off 1 
+                & \textbf{0.9} \\
+
+        $\pilow$ & Probability one of $B - 1$ non-optimal behaviors pays off 1 
+                 & 0.1, 0.45, 0.8 \\
+
+        $L$    & Time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
+
+        $N$    & Population size
+                 & 50, 100, 200, \textbf{1000} \\
+
+        \bottomrule
+        \end{tabular} 
+\end{table}
+
+\subsection{Agents and learning}
+
+All agents perform individual, trial-and-error learning over their lifespan.
+This learning is guided based on undirected, softmax search which drives
+agents to explore all behavioral options in the selection set when 
+the agent is more uncertain which is optimal, and to exploit the most profitable
+behaviors when the agent is more certain which are most beneficial. Selection
+for or against social learners occurs when agents are chosen to reproduce 
+with replacement, with probability
+of reproduction biased by net payoffs in each generation.
+
+Several agent-level variables are required to operationalize individual and social
+learning
+
+\begin{table}[h]
+  \caption{Agent-level variables. The first four ($\protect s_i$, $\protect
+    \bar\pi_{ib}$, $\protect c_{ib}$,
+  and $\protect \pi_i$) are dynamic with an implicit time dependence. The softmax
+greediness $\protect \beta$ and number of prospective teachers for social learners,
+$\protect N_T$, are constant throughout each simulation.}
     \label{tab:modelParameters}
@@
 
-        $\pi_i$ & Net payoffs accumulated by $i$ within generation
-                                & 0.0 \\
-        \bottomrule
-    \end{tabular}
-\end{table}
-
-To answer our research questions we developed an agent-based model of social
-learning evolution in which a society of $N$ individuals \cm{do we ever define N used?} each must decide which of
-$B$ behaviors to perform at each time step within a generation of $L$ time steps. At
-the end of each generation, agents are selected with replacement from the population
-to reproduce another $N$ agents. Agents who inherit the social learning trait then
-learn about behavioral payoffs from the previous generation, while asocial learners
-begin life with no \emph{a priori} knowledge of the world.  Each behavior is a
-``bandit'', a common modeling and experimental approach for representing behaviors
-with probabilistic
-payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
-
-\begin{figure}
-  \caption{Agents are randomly initialized as social learners or not, with their
-  payoff observations all initialized to zero (A). Then agents begin selecting
-and performing behaviors and accumulating payoffs, which goes on for $L$
-timesteps (B). After $L$ time steps, agents are selected to reproduce,
-social learner children learn from a member of their parent's generation, and
-the previous generation dies off (C). The simulation stops if children are all
-social or asocial learners (i.e.\ the system reaches fixation), 
-otherwise repeat another generation and evolution (3).}
-  \label{fig:schematic}
-  \centering
-    \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
-\end{figure}
-
-We identified four ``principal components'' of uncertainty that affect the
-ability of agents to find and choose the optimal behavior: 
-\emph{environmental variability}; \emph{payoff ambiguity}; \emph{selection set size}
-(number of behaviors environment affords); and the \emph{effective lifespan}.
-Environmental variability, denoted $u$, is the probability that the behavior
-yielding the optimal payoff, $\pihigh$, changes from one generation to the next.
-We operationalized payoff ambiguity by setting $\pihigh = 0.9$ for all analyses
-and varying $\pilow \in \{0.1, 0.45, 0.8\}$. The selection set size is the
-total number of possible behaviors agents choose from, denoted $B$. The 
-effective life span is the number of time steps agents live for, which is
-also the number of behaviors each agent performs each generation.
-
-\vspace{2em}
-\begin{table}[h]
-    \caption{Global environmental and cognitive initialization parameters.
-      Bold indicates \emph{default value tested}.
-    \mt{TODO: Test more $N_\text{T}$ for sensitivity analysis}}
-    \label{tab:modelParameters}
-    \centering %\hspace{-3em}
-    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule
-
-        Symbol & Description & Values tested \\
-
-        \midrule
-
-        $B$       & Number of possible behaviors (represented by ``bandits'') 
-                  & 2, 4, 10 \\
-
-        $\pihigh$ & Probability that the unique optimal behavior pays off 1 
-                & \textbf{0.9} \\
-
-        $\pilow$ & Probability one of $B - 1$ non-optimal behaviors pays off 1 
-                 & 0.1, 0.45, 0.8 \\
+        $\pi_i$ & Net payoffs accumulated by $i$ within generation & 0.0 \\
 
@@
 
-        $u$    & Probability optimal behavior changes between generations 
-               & 0.0, 0.1, \ldots, 1.0 \\
-
-        $L$    & Number of time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
-
         $N_T$    & Number of teachers to pool, from which best selected 
-                 & \textbf{5}  \\
+                 & 2, \textbf{5}, 10, 20  \\
 
@@
 
-\subsection{Agents and learning}
-
-All agents perform individual, trial-and-error learning over their lifespan.
-This learning is guided based on undirected, softmax search which drives
-agents to explore all behavioral options in the selection set when 
-the agent is more uncertain which is optimal, and to exploit the most profitable
-behaviors when the agent is more certain which are most beneficial.
-
 \subsection{Dynamics}
 
-\subsubsection{Initialization}
+\paragraph{Initialization}
 
@@
 
+\subsubsection{Sensitivity analyses}
+
 \subsubsection{Implementation}
@@
 
-By identifying four common uncertainty dimensions we developed a model that predicts
-how different forms of uncertainty might interact to foster or suppress social
-learning.  The model reproduced classic predictions that social learning can yield
-higher payoffs than individual learning when uncertainty is sufficiently limited.
-By disambiguating and organizing various operationalizations of uncertainty, 
-we developed a more nuanced theoretical understanding of which forms of
-uncertainty interact in which ways to make social learning more or less beneficial
-compared to asocial learning.  Note that in many cases we made modeling choices that
-excluded some important mechanisms of social learning; for example we assumed
+By identifying four common uncertainty dimensions we developed a model that
+predicts how different forms of uncertainty might interact to foster or suppress
+social learning.  The model reproduced classic predictions that social learning can
+yield higher payoffs than individual learning when uncertainty is sufficiently
+limited.  By disambiguating and organizing various operationalizations of
+uncertainty, we developed a more nuanced theoretical understanding of which forms
+of uncertainty interact in which ways to make social learning more or less
+beneficial compared to asocial learning. Taking the functional form of uncertainty
+seriously is critical for understanding how humans adapt to an uncertain and
+rapidly changing world, both to mitigate existential
+threats~\cite{Moya2020,Jones2021}, and to capitalize on new opportunities such as
+transitioning to clean energy use and
+production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+
+Our model necessarily made some simplifying assumptions that may not always hold.
+\mt{Review the ones mentioned in model section: non-spatial, no within-generation
+environmental variability or horizontal learning}.
+Furthermore, we only considered
 success-biased learning, although conformity is theoretically important as
-well~\cite{Muthukrishna2016a,Smaldino2018b}. Still, we believe our model
-advances theoretical parsimony; and the software implementation is designed to
-facilitate testing alternate modeling choices.
+well~\cite{Muthukrishna2016a,Smaldino2018b}. One final implicit assumption
+in our model was that the number of behaviors was constant, as was the relationship
+between their payoffs---one was always optimal, and the rest were equally
+suboptimal. However, this fails to account for evolutionary feedback which creates
+new behavioral affordances as time progresses~\cite{Smaldino2012,Heras-Escribano2020}.
+Our model and its software implementation were designed to be modular and 
+therefore extensible.  Indeed, we plan to extend this model to further develop 
+a more detailed theoretical understanding of the evolution of social learning, 
+and we hope others do, too.
 
-% \paragraph{Disc. 2: Foundation for studying social learning evolution with group
-% structure or other topics(PAUL, JAMIE, CRISTINA)}~\cite{Katsnelson2014}.
-
-Our modeling approach may have applications to developing social artificial
-intelligence. Much effort has gone in to developing the cognitive machinery to
-realize multi-agent reinforcement learning
-systems~\cite{Sandholm1996,Ndousse2021,Gronauer2022}, with some work explicitly
-incorporating cultural evolutionary approaches to social learning~\cite{Jaques2019}.
-However, it seems there are a lack of methods for adapting to environmental
-uncertainty, or determining when social learning is actually advantageous under
-different uncertainty conditions. Our model dynamics could be used as an
+As a final note, we believe 
+our modeling approach may have applications to developing social artificial
+intelligence, sepcifically multi-agent reinforcement learning
+systems~\cite{Sandholm1996,Ndousse2021,Gronauer2022,Jaques2019}.
+It seems to be implicitly assumed by current multi-agent reinforcement learning
+algorithms that social learning
+would always be beneficial. However, we have shown in our work that sometimes 
+it is more efficient for autonomous social agents to solve problems without
+reference to social information across a variety of uncertainty conditions. 
+Our model agents are essentially software
+robots, so our results should predict the benefit to real-world social robots
+to either learn socially or asocially if the assumptions we make here are 
+reasonably met or implemented in the social robot design.
+Our model dynamics could thus be used as an
 evolutionary algorithm to update AI agents' social learning strategy without
 explicit knowledge of, or need to approximate, the underlying uncertainty structure.
+A designer would need only to program the robots to go through evolutionary
+cycles of simulated ``reproduction'' and ``death''.
 Our model could also predict the expected benefit of social learning, which may be
@@
 
-Taking the functional form of uncertainty seriously is critical for understanding how humans adapt to an uncertain and rapidly changing world, both to mitigate existential threats~\cite{Moya2020,Jones2021}, and to capitalize on new opportunities such as transitioning to clean energy use and production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
-
 \bibliographystyle{apacite}
-% \bibliography{/Users/mt/workspace/Writing/library.bib}
-\bibliography{this.bib}
+\bibliography{/Users/mt/workspace/Writing/library.bib}
+% \bibliography{this.bib}
 

### 2022-07-17 ms.tex
further Model sec revisions

@@
 generations it will take for a population to evolve the optimal strategy, and the
-expected payoffs in populations performing the optimal strategy, in several specific
+expected payoffs in populations performing the optimal strategy, across several specific
 uncertainty contexts. To understand how different varieties of uncertainty interact
@@
 All agents perform individual, trial-and-error learning over their lifespan.
-This learning is guided based on undirected, softmax search which drives
+This learning is guided based on the softmax search algorithm which drives
 agents to explore all behavioral options in the selection set when 
 the agent is more uncertain which is optimal, and to exploit the most profitable
-behaviors when the agent is more certain which are most beneficial. Selection
-for or against social learners occurs when agents are chosen to reproduce 
-with replacement, with probability
-of reproduction biased by net payoffs in each generation.
-
-Several agent-level variables are required to operationalize individual and social
-learning
+behaviors more frequently when the agent is more certain which are most beneficial. 
+To do softmax searching, agents track payoffs acquired from each behavior.
+(introduce agent attributes)
+When agents are initialized at the start of the model, all agents are initialized
+with all $\pi_{ib} = 0$. At the start of generations other than the first, 
+$\pi_i$ will be initialized with all $\pi_{ib} = 0$ for asocial learners ($s_i = 0$)
+or with a teacher's $\pi_{ib}$. 
+Agents are thus endowed with dynamic attributes to track payoffs and calculate the
+softmax weights, and with an instruction of whether child agents learn socially
+or not. Details of how these attributes are updated over time is explained below
+with the rest of the model dynamics.
 
@@
 \paragraph{Initialization}
-
 At generation start, one of the behaviors is set to 
@@
 
-\subsubsection{Intragenerational dynamics}
-
+\paragraph{Intragenerational dynamics}
 To guide behavior selection, agent $i$ counts how many times it
@@
 
-\subsubsection{Intergenerational dynamics}
-
+\paragraph{Intergenerational dynamics}
 In between generations agents first reproduce via asexual haploid reproduction; 
@@
 newly initialized population then begins behavior selection and payoff accumulation
-for another $L$ time steps. The evolutionary process continues until $\sum_i s_i
-= 1$ or $\sum_i s_i = 0$ \mt{I believe all trials will eventually end like this, so
+for another $L$ time steps.
+
+\paragraph{Stopping conditions} The evolutionary process continues until $\sum_i s_i
+= 1$ or $\sum_i s_i = 0$.
+
+\mt{I believe all trials will eventually end like this, so
 in the next set of model runs I will not allow early termination before one of these

### 2022-07-18 ms.tex
finished Model restruct
added intro results par

@@
 
+To understand how different forms of uncertainty interact to affect the evolution
+of social learning, we measured simulated social learning prevalence across a 
+suite of simulations over uncertainty parameters. We analyze simulation outcomes
+by plotting the mean observed social learning frequency, $\meansl$ across all agents 
+and 1000 simulation trials for each uncertainty parameter setting. We do not calculate
+significance measures since these can be inflated by simply adding more trials.
+Instead, we visualize and inspect plots with $\meansl$ on the y-axis and
+environmental variability, $u$ on the x-axis. This is convenient because we are
+most certain about how $\meansl$ depends on $u$: we expect $\meansl$ to decrease
+as $u$ increases since environmental variability is well understood to cause
+socially-transmitted information to become outdated. When the other forms of
+uncertainty are varied, this causes changes to when and how quickly social learning
+is suppressed as $u$ increases. To inspect these changes, we show nine plots
+of $\meansl$ over $u$ in a 3x3 plot array (Figure~\ref{fig:mainResults}). 
+Plot array columns correspond to different selection set sizes, $B$; rows
+correspond to different non-optimal payoff values, $\pilow$ (recall optimal
+payoff $\pihigh=0.9$ for all analyses); plot line and marker colors correspond
+to different effective lifespan, $L$, values. 
+We support our conclusions regarding the evolution of
+social learning by analyzing the time to model 
+fixation and by comparing the average net payoffs in our simulations to the
+expected payoffs for individuals in both populations of all social learners
+and in populations of all individual learners. We thus use our analysis 
+to understand changes to how $\meansl$ changes over $u$ for different uncertainty parameter settings.
+
 Several patterns emerged in changes to the shape of social learning suppression over
@@
   \centering
-    \includegraphics[width=\textwidth]{Figures/mainResultsPlots.pdf}
+    \includegraphics[width=\textwidth]{{Figures/supplement/nagents=1000/mainResultsPlots.pdf}}
 \end{figure}
@@
 \bibliographystyle{apacite}
-\bibliography{/Users/mt/workspace/Writing/library.bib}
-% \bibliography{this.bib}
+% \bibliography{/Users/mt/workspace/Writing/library.bib}
+\bibliography{this.bib}
 

### 2022-07-18 ms.tex
nearly done with full revision

@@
 \textbf{Effective lifespan.}
+\mt{Restructure: lead with ``It stands to reason'' sentence or similar that gets
+to the point of this par more quickly, that lifespan affects uncertainty.}
 Learning can be viewed as a process by which an individual reduces or otherwise manages their uncertainty \cite{jacobs2011bayesian,clark2013whatever}.
@@
 (2017) \nocite{Aplin2017} found that younger great tits more readily used social information compared with older individuals, possibly because they had accrued less information via individual learning, and also possibly because younger individuals have the most to gain (given their expected remaining lifespan) by switching to superior behavioral options.
-\ps{I got rid of the Leris and Reader reference because it didn't seem relevant to age-based uncertainty.
+% \ps{I got rid of the Leris and Reader reference because it didn't seem relevant to age-based uncertainty.
 They just showed that young guppies exposed to reliable models were more likely to use social information later.
-I also added some human studies, which seems important.} Cross-cultural studies on humans have shown the importance of childhood as a phase of heavy social learning ~\cite{Reyes2016}.
+I also added some human studies, which seems important.}
+Cross-cultural studies on humans have shown the importance of childhood as a phase of heavy social learning ~\cite{Reyes2016}.
 Young children are more likely to acquire their beliefs and simple skills from their parents than are older children or adults, which is at least partly due to the differential knowledge accrual between young children and the older adults to whom they direct the most trust and attention \cite{kline2013teaching}.
@@
 
-\begin{comment}
-
-\cm{I think a lot of this may be too much detail.
+% \begin{comment}
+
+% \cm{I think a lot of this may be too much detail.
 I'm still editing and focusing the above on the main forms of uncertainty we are modeling and reviewing the relevant literature as we go.
 Yes we've made choices about things like horizontal vs vertical, but i think we can just justify that when we introduce the model }
-ps{I agree with Cristina here.
+% ps{I agree with Cristina here.
 I think we should use this section to justify our way of modeling individual and social learning, which is different from previous models.
@@
 
-To add to confusion about how to integrate diverse models of social learning
-evolution, different models select different social learning components in
-seemingly \emph{ad hoc} ways 
-\begin{itemize}
-  \item 
-    Vertical, oblique, horizontal transmission
-  \item
-    Conformity, payoff-biased, frequency-dependent, etc. A note about how
-    ``conformity'' is often not distinguished from other forms of social learning
-  \item
-    Review human studies
-  \item
-    Review non-human studies~\cite{Leris2016,Aplin2017,Avargues-Weber2018,Baracchi2018}
-  \item
-    One sentence on how dual-inheritance theory enables us to gloss over whether
-    social learning is genetically or culturally evolved.
-  \item
-    More things from which we selected the operation of our model
-\end{itemize}
-
-\end{comment}
+% To add to confusion about how to integrate diverse models of social learning
+% evolution, different models select different social learning components in
+% seemingly \emph{ad hoc} ways 
+% \begin{itemize}
+%   \item 
+%     Vertical, oblique, horizontal transmission
+%   \item
+%     Conformity, payoff-biased, frequency-dependent, etc. A note about how
+%     ``conformity'' is often not distinguished from other forms of social learning
+%   \item
+%     Review human studies
+%   \item
+%     Review non-human studies~\cite{Leris2016,Aplin2017,Avargues-Weber2018,Baracchi2018}
+%   \item
+%     One sentence on how dual-inheritance theory enables us to gloss over whether
+%     social learning is genetically or culturally evolved.
+%   \item
+%     More things from which we selected the operation of our model
+% \end{itemize}
+
+% \end{comment}
 
@@
 programmed to cause agents to reproduce and die off, where reproducers pass on
-heritable traits to their offspring. This sets up an inter-generational structure
-that we also use as a scaffold for social learning: we assume social learning occurs
-\emph{obliquely}\mt{is ``oblique learning'' understood to include parents by default
-or do we need to say ``or vertically''?}, meaning learning happens when a new
-generation of agents each select a teacher from the previous generation, possibly
-including their parents.  Natural selection occurs in the model when agents with higher
+heritable traits to their offspring. 
+Natural selection occurs in the model when agents with higher
 payoffs preferentially reproduce. This is a model of cultural evolution, so
@@
 loss of the potential to socially influence others. 
-Evolutionary agent-based models are powerful, but their components need to be
-carefully specified and justified in relation to empirical facts.
+This sets up an inter-generational structure
+that we also use as a scaffold for social learning: we assume social learning occurs
+\emph{obliquely}, meaning learning happens when a new
+generation of agents each select a teacher from the previous generation, possibly
+including their parents.  
+Evolutionary agent-based models of cultural evolution are powerful, 
+but their components need to be carefully specified and justified in relation to
+empirical facts.
 
@@
 
-% \begin{itemize}
-%   \item
-%     Softmax-guided behavior selection
-%   \item
-%     Oblique learning, not horizontal; no intragenerational change in optimal
-%     behavior, only intergenerational
-%   \item 
-%     Payoff-biased teacher selection, not aggregation over everyone or large group,
-%     as in conformist transmission
-%   \item
-%     Not spatial in any way. Agents need only to choose among potential behaviors
-%     and the behavior is instantly performed, as a real human can when pointing
-%     and clicking on a computer screen. This approximation could also hold when
-%     all behavioral options require an identical amount of time/money/resources
-%     to enable the agent to actually do the behavior (drive to work, walk to a
-%     watering hole, fly to a flower to gather pollen, etc.). Since teacher and
-%     behavior selection and reproduction are biased by relative payoffs there
-%     is no effect on model dynamics if cost of access is the same for each behavior.
-% \end{itemize}
-
-\clearpage
-
-\begin{figure}
-  \caption{Agents are randomly initialized as social learners or not, with their
-  payoff observations all initialized to zero (A). Then agents begin selecting
-and performing behaviors and accumulating payoffs, which goes on for $L$
-timesteps (B). After $L$ time steps, agents are selected to reproduce,
-social learner children learn from a member of their parent's generation, and
-the previous generation dies off (C). The simulation stops if children are all
-social or asocial learners (i.e.\ the system reaches fixation), 
-otherwise repeat another generation and evolution (3).}
-  \label{fig:schematic}
-  \centering
-    \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
-\end{figure}
-
 \subsection{Model environment and uncertainty}
 
-\begin{itemize}
-  \item 
-    A number of parameters specify the structure of the environment in which
-    agents sovle problems and adapt by adjusting their social learning through
-    evolution. \mt{Introduce all parameters; do not give values, but ref
-    (Table~\ref{tab:uncertaintyParameters})}
-  \item
-    \mt{Bandits and payoffs in more detail}
-\end{itemize}
+The model environment provides behaviors for agents to perform. The structure
+of the environment is specified by setting several parameters, including
+three of the uncertainty parameters: environmental variability, selection set size, 
+and payoff ambiguity. 
+Each behavior is indexed by $b$ and modeled as a ``one-armed bandit'', which yields 
+Bernoulli-distributed payoffs of 1 with probability $\pi_b$ and 0 with 
+probability $1 - \pi_b$. $\pi_b$ is equivalently the expected
+payoff of behavior/bandit $b$. The model environment affords $B$ behaviors, where
+$B$ is the \emph{selection set size} uncertainty parameter, which
+is constant throughout the course of a given simulation.
+
+The model environment is dynamic: which behavior is optimal changes between
+generations with probability equal to the \emph{environmental variability}, $u$.
+At the beginning of each generation, one bandit is optimal and yields expected
+payoff $\pihigh$; the other $B-1$ behaviors yield a lower payoff, $\pilow$. 
+The \emph{payoff ambiguity} here between optimal and non-optimal behavior
+payoffs is defined by $\pihigh - \pilow$. We set $\pihigh = 0.9$ to be constant
+across all simulations, so our analysis only varies payoff ambiguity by varying
+$\pilow$. Specifically, payoff ambiguity increases with $\pilow$. 
+By systematically varying these uncertainty parameters we change
+the nature of the challenge faced by the agents. Each parameter individually 
+can increase or decrease ``uncertainty,'' but it is not at all clear \emph{a priori}
+how these uncertainties combine to affect the evolution of social learning.
+These uncertainty parameters and the values we tested in our simulations
+are summarized in Table~\ref{tab:uncertaintyParameters}.
 
@@
 \begin{table}[h]
-\caption{Uncertainty parameters.  Bold indicates default value tested} %\emph{default value tested}.}
+\caption{Model ecological parameters, including uncertainty parameters $u$, $B$,
+$\pilow$, and $L$. Bold indicates default value tested} %\emph{default value tested}.}
     \label{tab:uncertaintyParameters}
@@
 
-All agents perform individual, trial-and-error learning over their lifespan.
-This learning is guided based on the softmax search algorithm which drives
-agents to explore all behavioral options in the selection set when 
-the agent is more uncertain which is optimal, and to exploit the most profitable
-behaviors more frequently when the agent is more certain which are most beneficial. 
-To do softmax searching, agents track payoffs acquired from each behavior.
-(introduce agent attributes)
-When agents are initialized at the start of the model, all agents are initialized
-with all $\pi_{ib} = 0$. At the start of generations other than the first, 
-$\pi_i$ will be initialized with all $\pi_{ib} = 0$ for asocial learners ($s_i = 0$)
-or with a teacher's $\pi_{ib}$. 
-Agents are thus endowed with dynamic attributes to track payoffs and calculate the
-softmax weights, and with an instruction of whether child agents learn socially
-or not. Details of how these attributes are updated over time is explained below
-with the rest of the model dynamics.
-
-\begin{table}[h]
-  \caption{Agent-level variables. The first four ($\protect s_i$, $\protect
-    \bar\pi_{ib}$, $\protect c_{ib}$,
-  and $\protect \pi_i$) are dynamic with an implicit time dependence. The softmax
-greediness $\protect \beta$ and number of prospective teachers for social learners,
-$\protect N_T$, are constant throughout each simulation.}
-    \label{tab:modelParameters}
-    \centering %\hspace{-3em}
-    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule
-
-        Attribute & Description & Initial value \\
-
-        \midrule
-
-        $s_i$  & Social learner trait: 1 if agent $i$ is social learner; 0 otherwise & 0
-        or 1 equally likely \\
-
-        $\bar\pi_{ib}$ & ``Ledger'': mean payoffs acquired via behavior $b$ by $i$ 
-                       & $B$-vector of zeros \\
-
-        $c_{ib}$ & Count of how many times agent $i$ performed $b$ 
-              & $B$-vector of zeros \\
-
-        $\pi_i$ & Net payoffs accumulated by $i$ within generation & 0.0 \\
-
-        $\beta$ & Softmax greediness; $\uparrow=$more exploitation, $\downarrow=$more
-                    exploration 
-               & 100, \textbf{10}, 1 \\
-
-        $N_T$    & Number of teachers to pool, from which best selected 
-                 & 2, \textbf{5}, 10, 20  \\
-
-        \bottomrule
-    \end{tabular}
-\end{table}
-
-\subsection{Dynamics}
-
-\paragraph{Initialization}
-At generation start, one of the behaviors is set to 
-yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
-expected payoffs $\pilow$. At each time step, agents perform behavior $b$ 
+Agents are endowed with dynamic attributes to intelligently select behaviors and
+calculate average payoffs for each behavior, and with a social learning trait value
+that determines whether agents learn socially or not. All agents engage in
+individual learning over their lifespan, whether or not they are social learners.
+The difference between social learners and asocial learners is that social learners
+have initially biased behavioral preferences based on information given to them by a
+teacher of the previous generation. Asocial learners begin life with no behavioral
+preferences. Agents and their learning procedures are specified through several
+parameters introduced below.
+
+\subsubsection{Individual learning}
+
+All agents perform individual, trial-and-error learning at each time step in
+their lifespan.  This learning is guided by softmax search which
+drives agents to more frequently exploit the most profitable behaviors when the
+agent is more certain which are optimal, and to explore more frequently when the
+agent is unsure.  To do softmax searching, agents track average payoffs acquired
+from each behavior, which also requires agents to track the number of times they
+have performed each behavior.  We denote the average payoffs obtained by agent $i$
+for behavior $b$ as $\ledger$. The number of times $i$ performed $b$ is $c_{ib}$
+(``$c$'' stands for count).
+
+At each time step, agents perform behavior $b$ 
 with softmax-weighted probability
@@
 agents explore alternative behaviors (smaller $\beta$)~\cite{McElreath2005}.
+
+\subsubsection{Social learning}
+
+At the beginning of each generation other than the first, social child agents select
+one member of the previous generation to learn from if they are a social learner.
+If agent $i$ is a social learner we write $s_i = 1$, and $s_i = 0$ otherwise.
+A child agent $c$ is a social learner if its parent $p$ was a social learner,
+i.e.\ $s_c \leftarrow s_p$, without mutation. 
+Social learner children select a teacher from 
+the previous generation by first selecting $N_T$ prospective teachers fully
+at random, then by sampling from the $N_T$ with each prospective teacher weighted
+by their net payoffs relative to the other $N_T - 1$.
+
+\begin{table}[h]
+  \vspace{2em}
+  \caption{Agent-level variables. The first four ($\protect s_i$, $\protect
+    \bar\pi_{ib}$, $\protect c_{ib}$,
+  and $\protect \pi_i$) are dynamic with an implicit time dependence. The softmax
+greediness $\protect \beta$ and number of prospective teachers for social learners,
+$\protect N_T$, are constant throughout each simulation.}
+    \label{tab:modelParameters}
+    \centering %\hspace{-3em}
+    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule
+
+        Attribute & Description & Initial value \\
+
+        \midrule
+
+        $s_i$  & Social learner trait: 1 if agent $i$ is social learner; 0 otherwise & 0
+        or 1 equally likely \\
+
+        $\bar\pi_{ib}$ & ``Ledger'': mean payoffs acquired via behavior $b$ by $i$ 
+                       & $B$-vector of zeros \\
+
+        $c_{ib}$ & Count of how many times agent $i$ performed $b$ 
+              & $B$-vector of zeros \\
+
+        $\pi_i$ & Net payoffs accumulated by $i$ within generation & 0.0 \\
+
+        $\beta$ & Softmax greediness; $\uparrow=$more exploitation, $\downarrow=$more
+                    exploration 
+               & 100, \textbf{10}, 1 \\
+
+        $N_T$    & Number of teachers to pool, from which best selected 
+                 & 2, \textbf{5}, 10, 20  \\
+
+        \bottomrule
+    \end{tabular}
+\end{table}
+
+\subsection{Dynamics}
+
+Model dynamics proceed by first initializing the environment and agents according
+to parameter settings for the simulation. Then, within each generation,
+agents select and perform behaviors, updating their observations along the way.
+Between generations, agents reproduce, teach child agents, and die off. 
+Child agents then begin a new round of generational dynamics, followed by
+reproduction. This process continues until the population has fixated as
+all social learners or all asocial learners, or until an upper limit of 
+iterations has been reached. This process is visualized in
+Figure~\ref{fig:schematic}.
+
+\paragraph{Initialization}
+
+The model is initialized with $N$ agents, all with zero observed mean payoffs, 
+$\ledger = 0$, and zero counts of how many times
+they have tried each behavior, $c_{ib} = 0$ (Figure~\ref{fig:schematic}A).
+At generation start, one of the behaviors is set to 
+yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
+expected payoffs $\pilow$. Agents are independently randomly initialized with $s_i
+\in 0,1$.
+
+\paragraph{Intragenerational dynamics}
+% To guide behavior selection, agent $i$ counts how many times it
+% performed each behavior $b$, denoted $c_{ib}$. Agents use this count to 
+% update the mean payoff they have obtained from behavior $b$, denoted $\ledger$.
+% $\ledger$ is initialized to 0 for all $b$ at model start for
+% all agents (Figure~\ref{fig:schematic}A), and at 
+% generation start for asocial learners. Social
+% learning agents' $\ledger$ is initialized as that of its teacher, who is selected
+% through performance-biased oblique learning; $c_ib$ is set to 1 for all social
+% learners $i$ and behaviors $b$ (Figure~\ref{fig:schematic}C). Agent $i$'s
+% accumulated payoffs from performing several behaviors over their lifetime of $L$
+% time steps is denoted $\pi_{i}$. If an agent $i$ is a social learner, then we write
+% $s_i = 1$, otherwise the agent is an asocial learner and $s_i = 0$.
+
+Within each generation, all $N$ agents perform $L$ behaviors sequentially and
+independently (Figure~\ref{fig:schematic}B).
+Agents make one choice for each step in its lifespan using softmax weighting
+described above, updating the mean payoffs it has observed along the way. 
 Agents probabilistically recieve a payoff of 0 or 1 depending on whether the
-bandit paid off. Behavior payoffs are represented as a draw from a 
+bandit paid off. Behavior payoffs are drawn from a 
 Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from
 behavior $b$.  For concreteness we denote this probabilistic payoff
-$\bandit$. On performing behavior $b$, agent $i$ updates the
+$\bandit$. After performing behavior $b$, agent $i$ updates the
 corresponding \emph{behavior count} by 1, $c_{ib} \leftarrow c_{ib} + 1$, and then
@@
 \noindent
-This procedure continues for $L$ time steps within each generation
-(Figure~\ref{fig:schematic}B).
-
-\paragraph{Intragenerational dynamics}
-To guide behavior selection, agent $i$ counts how many times it
-performed each behavior $b$, denoted $c_{ib}$. Agents use this count to 
-update the mean payoff they have obtained from behavior $b$, denoted $\ledger$.
-$\ledger$ is initialized to 0 for all $b$ at model start for
-all agents (Figure~\ref{fig:schematic}A), and at 
-generation start for asocial learners. Social
-learning agents' $\ledger$ is initialized as that of its teacher, who is selected
-through performance-biased oblique learning; $c_ib$ is set to 1 for all social
-learners $i$ and behaviors $b$ (Figure~\ref{fig:schematic}C). Agent $i$'s
-accumulated payoffs from performing several behaviors over their lifetime of $L$
-time steps is denoted $\pi_{i}$. If an agent $i$ is a social learner, then we write
-$s_i = 1$, otherwise the agent is an asocial learner and $s_i = 0$.
 
@@
 teachers from the population completely at random, then selecting the one with
-highest net payoffs $\pi_i$ as their teacher, with ties broken randomly ($N_T =
-5$ in the main text; \mt{Other values will be tested in the supplement}). While it
+highest net payoffs $\pi_i$ as their teacher, with ties broken randomly. While it
 is somewhat arbitrary to first subset $N_T$, this is a conservative choice that
@@
 
-\paragraph{Stopping conditions} The evolutionary process continues until $\sum_i s_i
-= 1$ or $\sum_i s_i = 0$.
-
-\mt{I believe all trials will eventually end like this, so
-in the next set of model runs I will not allow early termination before one of these
-conditions are met}.
+After reproduction and die-off, the optimal behavior changes with probability
+$u$. If a random number draw indicates the behavior should change, the new
+behavior is chosen from all behaviors but the current optimal behavior.
+
+\paragraph{Stopping conditions} The evolutionary process continues until the
+population reaches evolutionary fixation with repsect to social learning, where
+$\sum_i s_i = 1$ or $\sum_i s_i = 0$, or until 20k iterations have run. 
+It is rare for simulations not to reach fixation. We report how frequently
+this happens in Table~\ref{tab:convergence}.
+
+\begin{figure}
+  \caption{Agents are randomly initialized as social learners or not, with their
+  payoff observations all initialized to zero (A). Then agents begin selecting
+and performing behaviors and accumulating payoffs, which goes on for $L$
+timesteps (B). After $L$ time steps, agents are selected to reproduce,
+social learner children learn from a member of their parent's generation, and
+the previous generation dies off (C). The simulation stops if children are all
+social or asocial learners (i.e.\ the system reaches fixation), 
+otherwise repeat another generation and evolution (3).}
+  \label{fig:schematic}
+  \centering
+    \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+\end{figure}
+
+\clearpage
 
 \subsection{Computational analyses}
+\label{ssec:computationalAnalyses}
 
@@
 or the mean number of time steps to fixation normalized by
-lifespan\footnote{Equivalent to the mean number of generations to fixation}
-(fixation means $\sum_i s_i = 0 \text{ or } 1$). \mt{Make sure to qualitatively
-introduce these and their evolutionary importance in the intro.}
-We analyze outcomes by plotting $\meansl$ on the y-axis and environmental
+lifespan. We analyze outcomes by plotting $\meansl$ on the y-axis and environmental
 variation is on x-axis since we theoretically expect that $\meansl$ will 
@@
 
+We performed sensitivity analyses to ensure that our main analysis is reasonably
+robust to a range of auxiliary parameters. Specifically in our sensitivity analyses
+we first varied the population size, $N$, to explore whether smaller $N$ would 
+show more drift due to finite population size effects, but also generally support
+our main conclusions. Next, we varied the
+cognitive model parameter $\beta \in \{1, 100\}$ to supplement the main results
+that used $\beta = 10$. Recall that $\beta$ sets how frequently the softmax algorithm
+exploited the best observed behavior versus explored the rest. We do not
+expect agents with different $\beta$ to perform equally well 
+individually, so certain $\beta$ values may themselves suppress social learning
+since individual learning itself may be unreliable. Nonetheless our results
+should be valid over at least some range of $\beta$. Finally, we varied the
+number of prospective teachers $N_T \in \{2, 10, 20\}$ 
+to supplement the main results that used $N_T = 5$. The number of prospective
+teachers should not change the whether social learning is optimal or not, 
+but it may make model results driftier since the benefit of social learning should
+be more difficult to detect with fewer prosopective teachers.
+
 \subsubsection{Implementation}
@@
 suite of simulations over uncertainty parameters. We analyze simulation outcomes
-by plotting the mean observed social learning frequency, $\meansl$ across all agents 
-and 1000 simulation trials for each uncertainty parameter setting. We do not calculate
-significance measures since these can be inflated by simply adding more trials.
-Instead, we visualize and inspect plots with $\meansl$ on the y-axis and
+by plotting the mean observed social learning frequency, $\meansl$, across all agents 
+and 1000 simulation trials for each uncertainty parameter setting. 
+We visualize and inspect plots with $\meansl$ on the y-axis and
 environmental variability, $u$ on the x-axis. This is convenient because we are
@@
 is suppressed as $u$ increases. To inspect these changes, we show nine plots
-of $\meansl$ over $u$ in a 3x3 plot array (Figure~\ref{fig:mainResults}). 
+of $\meansl$ over $u$ in a $3\times3$ plot array (Figure~\ref{fig:mainResults}). 
 Plot array columns correspond to different selection set sizes, $B$; rows
@@
 We support our conclusions regarding the evolution of
-social learning by analyzing the time to model 
+social learning by analyzing the time to 
 fixation and by comparing the average net payoffs in our simulations to the
@@
 
-Several patterns emerged in changes to the shape of social learning suppression over
-environmental variability, $u$, across different uncertainty contexts defined by the
-payoff ambiguity, selection set size, and effective lifespan
-(Figure~\ref{fig:mainResults}). When payoff ambiguity and selection set size were
+Several patterns emerged in changes to social learning prevalence over
+as the uncertainty parameters were varied (Figure~\ref{fig:mainResults}). 
+First, we indeed observed that increased $u$ uniformly led to decreased
+$\meansl$, across the other uncertainty parameter values. The other uncertainty
+parameters changed at which value of $u$ that $\meansl$ started to decrease,
+and how quickly $\meansl$ decreased. For example, 
+when payoff ambiguity and selection set size were
 both small ($\pilow = 0.1$ and $B=2$) social learning only evolved when $u$ is small
 since individual learning is relatively efficient in this case
-(Figure~\ref{fig:mainResults}, upper left). As $\pilow$ increased the suppression of
-$\meansl$ flattened over $u$, which was more pronounced for smaller $L$ (rows of
-Figure~\ref{fig:mainResults}).  When $L$ is smaller, agents have fewer opportunities
-to learn through trial and error, and so it is more difficult for them to discern
-which strategy, social or asocial, is optimal. Increased selection set size led to
-both a shift in the critical value of $u$ when $\meansl$ begins to decrease, and
-flattened social learning suppression. This is because possibly misleading 
+(Figure~\ref{fig:mainResults}, upper left). As $\pilow$ increased,
+$\meansl$ decreased less rapdily over $u$, which was more pronounced for smaller $L$ (rows of
+Figure~\ref{fig:mainResults}).
+
+Increased selection set size $B$ led nearly uniformly to more prevalent social
+learning with all other uncertainty parameters being equal ($B$ increases along
+columns in Figure~\ref{fig:mainResults}. 
+This is because possibly misleading 
 social information is less consequential due
@@
 
+???$\pilow$ paragraph???
+
+When $L$ is smaller, agents have fewer opportunities
+to learn through trial and error, and so it is more difficult for them to discern
+which strategy, social or asocial, is optimal. We thus saw two distinct 
+trends emerge in the evolution of social learning in response to changes in $L$.
+First, when $\pilow$ was sufficiently small ($\pilow=0.1, 0.45$), we observed that shorter
+lifespan made social learning more beneficial (and increased $\meansl$) 
+across some values of $u$. When $\pilow=0.8$, shorter lifespans decreased 
+$\meansl$ in some cases and increased $\meansl$ in other cases. It seems
+that shorter lifespans in this case led to more evolutionary drift. This can
+be seen in two observations. First,
+$\meansl$ is reduced when $L=1$ compared to other lifespans for small values of
+$u$ when other lifespans lead to $\meansl \approx 1$. At larger $u$, when
+$\meansl \to 0$ for other lifespans, the $L=1$ case has non-zero $\meansl$.
+
 \begin{figure}
@@
 \end{figure}
+
+\subsection{Supplemental measures of social learning}
 
@@
 increased environmental variability, $\meansoc$ and $\meanpi$ approach $\meanasoc$.
-It appears agents tend
-to be conservative as expected social and asocial learning payoffs approach each
-other---the transition to $\meansl = 0$ often happens although social
+
+It appears agents tend to be ``conservative'' with their decision to learn socially
+or not as expected social and asocial learning payoffs approach each
+other---it seems $\meansl \to 0$ while social
 learning is still theoretically optimal. When $L=1$, $\meanpi$ can be greater than
@@
 generations enabling agents to more efficiently explore alternatives before focusing
-on a misidentified optimal behavior \mt{I think we could calculate this if it were
-valuable}.
+on a misidentified optimal behavior.
 
@@
 
-By identifying four common uncertainty dimensions we developed a model that
+By systematizing four common uncertainty dimensions we developed a model of
+the evolution of social learning that
 predicts how different forms of uncertainty might interact to foster or suppress
@@
 of uncertainty interact in which ways to make social learning more or less
-beneficial compared to asocial learning. Taking the functional form of uncertainty
-seriously is critical for understanding how humans adapt to an uncertain and
+beneficial compared to asocial learning.
+Our model did not make any \emph{a priori} assumptions about whether it was
+more costly for agents to be social or asocial learners, as some studies have
+assumed or imposed~\cite{Rogers1988,Feldman1996,Morgan2012}. 
+Instead, the uncertainty structure determined whether
+or not social learning was beneficial or not, and evolution directed successive
+generations towards the optimal strategy.
+Such detailed theoretical models of uncertainty
+are critical for understanding how humans adapt to an uncertain and
 rapidly changing world, both to mitigate existential
@@
 
-Our model necessarily made some simplifying assumptions that may not always hold.
+Our model necessarily made some simplifying assumptions that, while
+empirically justified in many cases, may not always hold.
 \mt{Review the ones mentioned in model section: non-spatial, no within-generation
-environmental variability or horizontal learning}.
+environmental variability; no horizontal learning}.
 Furthermore, we only considered
 success-biased learning, although conformity is theoretically important as
-well~\cite{Muthukrishna2016a,Smaldino2018b}. One final implicit assumption
+well~\cite{Muthukrishna2016a,Smaldino2018b}. Another implicit assumption
 in our model was that the number of behaviors was constant, as was the relationship
@@
 suboptimal. However, this fails to account for evolutionary feedback which creates
-new behavioral affordances as time progresses~\cite{Smaldino2012,Heras-Escribano2020}.
-Our model and its software implementation were designed to be modular and 
-therefore extensible.  Indeed, we plan to extend this model to further develop 
-a more detailed theoretical understanding of the evolution of social learning, 
-and we hope others do, too.
+new behavioral affordances as time progresses, e.g.\ via niche 
+construction~\cite{Smaldino2012,Heras-Escribano2020}.
 
@@
 Our model could also predict the expected benefit of social learning, which may be
-inherently costly in artificial multi-agent learning systems, and how long the
-translated evolutionary algorithm may take to converge.
+inherently costly in artificial multi-agent learning systems due to extra
+energy or time that may be required to transmit information between agents.
+
+\subsection{Conclusion}
+
+Social learning is an immensely complex phenomenon. In just our simple model, we
+found that its evolution is similarly complex, dependent on several interrelated
+factors. By systematically identifying common theoretical assumptions about
+uncertainty in the environments and contexts in which social learning evolves,
+we were able to develop a more systematic understanding of which uncertainty
+factors. This work informs most directly our current understanding of the
+evolution of social learning, but
+has broader importance for the behavioral science of problem solving in uncertain
+conditions, and for the design of artificial social intelligent systems.
+Our model and its software implementation were designed to be modular and 
+therefore extensible.  Indeed, we plan to extend this model to further develop 
+a more detailed theoretical understanding of the evolution of social learning, 
+and we hope others do, too.
 
@@
 \begin{table}[h]
-  \caption{Max. iterations = 5000.}
+  \caption{Max. iterations = 20000.}
   \label{tab:convergence}

### 2022-07-19 ms.tex
added paragraph on soc learn as a scaffold to help explain new par on pilow results

@@
 
+\subsubsection{Social learning as a scaffold for individual learning}
+
+In this model, being a social learner is beneficial when it is more likely
+on average to provide greater net payoffs than being an individual learner,
+since evolution here acts as an optimization routine. 
+Note that, unlike some models in the literature, it is not catastrophic for an 
+individual to receive outdated information\cite[, e.g]{Rogers1988}. Instead,
+agents can explore alternatives and greedily perform the observed optimal behavior
+if they learned outdated information due to environmental variability. We rely
+on this mechanism in the Analysis to explain patterns we observe where
+social learning evolves when $u > 0.5$, meaning that the
+optimal behavior will switch between generations more often than not. If 
+agents could not adjust to changing conditions like this, it seems like 
+social learning would not evolve when $u > 0.5$.
+
 \begin{table}[h]
@@
 
-???$\pilow$ paragraph???
+Payoff ambiguity had a modest effect when $\pilow = 0.1$ increased to $\pilow = 0.45$,
+causing social learning to be favored across more values of $u$, across all
+selection set sizes and lifespans (first two rows of Figure~\ref{fig:mainResults}). 
+This indicates that increased payoff ambiguity significantly increases the 
+difficulty of discerning which behavior is optimal since agents evolve to 
+risk social learning at greater values of $u$.
+When $\pilow = 0.8$ the largest effect is smoothing and flattening of the $\meansl$ curves,
+which indicates more drift (bottom row of Figure~\ref{fig:mainResults}). 
+Initially this results in less frequent evolution
+of social learning for the same values of $u$ and $B$. But after 
+the $u$ value where $\meansl \approx 0.5$, social learning evolves more frequently than
+for the same $u$ and $B$. When $\pilow \to \pihigh$, agents do better and better
+whether they are social learners or not. We see that this leads to less penalty
+for trying social information before possibly having to correct course due to
+outdated social information.
 

### 2022-07-19 ms.tex
content filled in mostly; needs more specificity and more revisions

@@
 \mt{Restructure: lead with ``It stands to reason'' sentence or similar that gets
-to the point of this par more quickly, that lifespan affects uncertainty.}
+to the point of this par more quickly, that lifespan affects uncertainty. Also this Effective
+Lifespan section seems too long.}
 Learning can be viewed as a process by which an individual reduces or otherwise manages their uncertainty \cite{jacobs2011bayesian,clark2013whatever}.
@@
 varies within a generation. This is empirically justified since cultural evolution
-occurs when meta-cognitive strategies and information are transferred or not via
-learning and social influence, instead of truly by physical reproduction and death
+occurs when meta-cognitive strategies and information are transferred via
+learning and social influence, instead of by physical reproduction and death
 as in genetic evolution.  The selection set size is the total number of possible
@@
 to the agents, which will lead agents to differently evolve to become social
-learners or not depending on which of those two strategies optimizes net payoffs.
+learners or not, depending on which strategy optimizes net payoffs.
 
@@
 cultural evolution of social learning as we will demonstrate in our Analysis.
+We will see that individual-level intelligence allows agents to recover from
+the receipt of outdated information due to temporal environmental variability.
 
@@
 $B$ is the \emph{selection set size} uncertainty parameter, which
-is constant throughout the course of a given simulation.
+is constant throughout the course of a given simulation, but varied systematically
+across simulations.
 
@@
 generations with probability equal to the \emph{environmental variability}, $u$.
+The optimal behavior does not change within generations.
 At the beginning of each generation, one bandit is optimal and yields expected
@@
 Note that, unlike some models in the literature, it is not catastrophic for an 
-individual to receive outdated information\cite[, e.g]{Rogers1988}. Instead,
-agents can explore alternatives and greedily perform the observed optimal behavior
-if they learned outdated information due to environmental variability. We rely
-on this mechanism in the Analysis to explain patterns we observe where
+individual to receive outdated information~\cite[e.g.]{Rogers1988}. Instead,
+agents can explore alternatives and greedily perform a different observed optimal behavior
+than an outdated optimal behavior they learned about socially. We rely
+on this mechanism in the Analysis to explain the patterns we observe where
 social learning evolves when $u > 0.5$, meaning that the
@@
 \paragraph{Intergenerational dynamics}
-In between generations agents first reproduce via asexual haploid reproduction; 
+Between generations, agents first reproduce via asexual haploid reproduction; 
 then new child agents learn from the
@@
 After reproduction and die-off, the optimal behavior changes with probability
-$u$. If a random number draw indicates the behavior should change, the new
-behavior is chosen from all behaviors but the current optimal behavior.
+$u$. If a random draw dictates the behavior should change, the new
+behavior is chosen from all other behaviors with the current optimal behavior
+excluded.
 
@@
 the $u$ value where $\meansl \approx 0.5$, social learning evolves more frequently than
-for the same $u$ and $B$. When $\pilow \to \pihigh$, agents do better and better
+for the same $u$, $B$, and $L$. When $\pilow \to \pihigh$, agents do better and better
 whether they are social learners or not. We see that this leads to less penalty
@@
 \subsection{Supplemental measures of social learning}
+
+\mt{This subsec needs revision and associated figures need to be updated with 
+$N=1000$ data}
 
@@
 
+\mt{Need to make this section more specific in reviewing the findings.}
 By systematizing four common uncertainty dimensions we developed a model of
@@
 environmental variability; no horizontal learning}.
-Furthermore, we only considered
-success-biased learning, although conformity is theoretically important as
-well~\cite{Muthukrishna2016a,Smaldino2018b}. Another implicit assumption
+We only considered
+success-biased learning, although conformity is sometimes the dominant mechanism 
+for social influence of behavior well~\cite{Muthukrishna2016a,Smaldino2018b}. 
+Another implicit assumption
 in our model was that the number of behaviors was constant, as was the relationship
@@
 new behavioral affordances as time progresses, e.g.\ via niche 
-construction~\cite{Smaldino2012,Heras-Escribano2020}.
+construction~\cite{Smaldino2012,Heras-Escribano2020}. Adjusting any of these
+assumptions and running new computational analyses could yield further
+understanding of the evolution of social learning across diverse contexts.
 
@@
 
-Social learning is an immensely complex phenomenon. In just our simple model, we
-found that its evolution is similarly complex, dependent on several interrelated
-factors. By systematically identifying common theoretical assumptions about
-uncertainty in the environments and contexts in which social learning evolves,
-we were able to develop a more systematic understanding of which uncertainty
-factors. This work informs most directly our current understanding of the
-evolution of social learning, but
-has broader importance for the behavioral science of problem solving in uncertain
-conditions, and for the design of artificial social intelligent systems.
-Our model and its software implementation were designed to be modular and 
-therefore extensible.  Indeed, we plan to extend this model to further develop 
-a more detailed theoretical understanding of the evolution of social learning, 
-and we hope others do, too.
+We found that the evolution of social learning, under some modest
+assumptions, is a complex phenomenon, dependent on several interrelated factors. By systematically
+identifying common theoretical assumptions about uncertainty in the environments and contexts
+in which social learning evolves, we were able to develop a more systematic understanding of
+which uncertainty factors interact to determine whether social learning evolves. By
+explicitly modeling a key factor of human intelligence, namely the ability to sense and
+adjust to uncertainty and new information, we saw that social learning could be
+valuable even if social learning provides outdated information. This work
+informs most directly our current understanding of the evolution of social learning, but has
+broader significance for the behavioral science of problem solving in uncertain conditions, and
+for the design of artificial social intelligent systems in uncertain environments.  Our model
+and its software implementation were designed to be modular and extensible.  Indeed,
+we plan to extend this model to further develop a more detailed theoretical understanding of
+the evolution of social learning; perhaps others will, too.
 
@@
 
-\begin{table}[h]
-  \caption{Max. iterations = 20000.}
-  \label{tab:convergence}
-  \centering
-  \begin{tabular}{cccc} \toprule
-    $B$ & \# not at fixation & \# total series & Pct. not fixated \\
-    \midrule  
-    2  & 0  & 132000 & 0.0 \% \\
-    4  & 0  & 132000 & 0.0 \% \\
-    10 & 44 & 132000 & 0.00033  \% \\
-    \bottomrule
-  \end{tabular} 
-\end{table}
+\begin{table}[h] \caption{Max. iterations = 20000.} \label{tab:convergence} \centering
+  \begin{tabular}{cccc} \toprule $B$ & \# not at fixation & \# total series & Pct. not fixated
+    \\ \midrule  2  & 0  & 132000 & 0.0 \% \\ 4  & 0  & 132000 & 0.0 \% \\ 10 & 44 & 132000 &
+    0.00033  \% \\ \bottomrule \end{tabular} \end{table}
 
@@
 
-\subsection{Softmax parameter sensitivity analysis}
-\vspace{-3em}
-\begin{figure}
-  \centering
-  \caption{Sensitivity analysis of the main results 
-		   for the softmax parameter $\beta = 100$ and $\beta=1$. Recall the main
-		   results were obtained with $\beta = 10$.}
-  \label{fig:softmaxSensitivity}
-  \vspace{2em}
+\subsection{Softmax parameter sensitivity analysis} \vspace{-3em} \begin{figure} \centering
+  \caption{Sensitivity analysis of the main results for the softmax parameter $\beta = 100$ and
+  $\beta=1$. Recall the main results were obtained with $\beta = 10$.}
+  \label{fig:softmaxSensitivity} \vspace{2em}
   \begin{subfigure}{\textwidth}

### 2022-07-22 ms.tex
few paragraphs in to analysis revision

@@
 
-To address our research questions we developed an evolutionary agent-based model of
+To understand how uncertainty affects social learning, 
+we developed an agent-based model of
 social learning evolution.  Evolutionary agent-based models simulate changes in
-prevalence of a phenotype over several generations---in this model the phenotype, or
-``trait'', is whether or not an agent engages in social learning.  In the model, a
+prevalence of a phenotype over several generations---in this model the phenotype
+is whether or not an agent engages in social learning.  In the model, a
 population of $N$ individuals each must decide which of $B$ behaviors to perform at
 each time step within a generation consisting of $L$ time steps. At the end of each
-generation, agents are selected with replacement, biased by accumulated payoffs
-within the generation, from the population to reproduce another $N$ agents. Agents
-who inherit the social learning trait then learn about behavioral payoffs from the
+generation, agents are selected with replacement to reproduce another $N$ agents, 
+biased by net payoffs. Agents
+who inherit the social learning trait then learn about payoffs from the
 previous generation, while asocial learners begin life with no \emph{a priori}
@@
 
-We operationalized the four ``principal components'' of uncertainty that affect the
-ability of agents to find and choose the optimal behavior. Recall these varieties of
-uncertainty are \emph{environmental variability}; \emph{payoff ambiguity};
+We operationalized four separable varieties of uncertainty that affect the
+ability of agents to find and choose the optimal behavior: 
+\emph{environmental variability}; \emph{payoff ambiguity};
 \emph{selection set size}; and the \emph{effective lifespan}. Environmental
-variability is the probability that the behavior yielding the optimal payoff changes
-from one generation to the next. We do not consider cases where the optimal behavior
-varies within a generation. This is empirically justified since cultural evolution
-occurs when meta-cognitive strategies and information are transferred via
-learning and social influence, instead of by physical reproduction and death
-as in genetic evolution.  The selection set size is the total number of possible
-behaviors agents choose from, assumed to be constant within a simulation.  We
-operationalized payoff ambiguity by manipulating the payoff difference between optimal
+variability is the probability that the optimal behavior changes
+between generations. We do not consider within-generation variability. 
+Furthermore, our model is not spatial, so agents have free, instant
+access to all behaviors, and there is no spatial uncertainty. 
+These conditions reflect humans in a computer-based social learning evolution
+experiment~\cite{McElreath2005,Morgan2012,Derex2016}. Spatial dimensions could also be
+considered irrelevant if costs associated with accessing a behavior were equal,
+e.g., if it was assumed to be equally costly for animals to
+access alternative food sources~\cite{Aplin2017,Baracchi2018}.  
+% This is empirically justified since cultural evolution
+% occurs when meta-cognitive strategies and information are transferred via
+% learning and social influence, instead of by physical reproduction and death
+% as in genetic evolution.  
+The selection set size is the total number of possible
+behaviors agents choose from, assumed to be constant within a simulation.  
+Payoff ambiguity is the payoff difference between optimal
 and non-optimal behaviors. The effective life span is the
 number of time steps in which agents perform behaviors within a generation. 
-Our model is not spatial, so agents have free, instant
-access to all behaviors, and there is no spatial uncertainty, 
-as might be the case for humans in a computer-based lab
-experiment~\cite{McElreath2005,Morgan2012}.  Spatial dimensions could also be
-considered irrelevant if costs associated with accessing a behavior were equal,
-e.g., if it was assumed to be equally easy for bumblebees to fly to alternative
-flower ``species''~\cite{Baracchi2018} or for great tits to fly to different food
-sources~\cite{Aplin2017}.  Each simulated environment provides a distinct challenge
+Each simulated environment provides a distinct challenge
 to the agents, which will lead agents to differently evolve to become social
@@
 including their parents.  
-Evolutionary agent-based models of cultural evolution are powerful, 
-but their components need to be carefully specified and justified in relation to
-empirical facts.
-
 Evolution, then, acts as an optimization routine to identify which heritable trait
@@
 defined by different uncertainty parameter settings
-(Table~\ref{tab:uncertaintyParameters}).  The main outcome variable we analyze in
-this model is therefore the value of agents' heritable trait, namely whether or not
-an agent, $i$, learns socially, denoted $s_i$. $s_i$ is a binary variable: it is 1
-if the agent is a social learner, and 0 otherwise. We will aggregate $s_i$ over all
-agents and simulation trials to understand the affects of different uncertainty
-parameter settings. We will support conclusions we make from observing patterns in
-the outcomes with additional measures of the average time it takes for the
-population to either all have $s_i = 1$ or all have $s_i = 0$, and the expected
-payoffs in different contexts among populations that are initialized to all have
-$s_i = 1$ or to all have $s_i = 0$. These outcome measures will be used to predict
-the evolutionarily-favored strategy (to learn socially or not), the number of
-generations it will take for a population to evolve the optimal strategy, and the
-expected payoffs in populations performing the optimal strategy, across several specific
-uncertainty contexts. To understand how different varieties of uncertainty interact
+(Table~\ref{tab:uncertaintyParameters}).
+
+Agents have one heritable trait in this model, whether or not
+an agent, $i$, learns socially, denoted $s_i$. $s_i$ is binary: it is 1
+if the agent is a social learner, and 0 otherwise. In our analysis, we 
+aggregate $s_i$ over all agents and simulation trials to understand the affects of
+different uncertainty parameter settings. 
+Our computational analysis amounts to observing patterns in
+the aggregated $s_i$, supported by measuring the number of generations 
+to model convergence and expected payoffs. 
+To understand how different varieties of uncertainty interact
 to affect the evolution of social learning, we systematically created an array of
@@
 generations with probability equal to the \emph{environmental variability}, $u$.
-The optimal behavior does not change within generations.
 At the beginning of each generation, one bandit is optimal and yields expected
 payoff $\pihigh$; the other $B-1$ behaviors yield a lower payoff, $\pilow$. 
-The \emph{payoff ambiguity} here between optimal and non-optimal behavior
-payoffs is defined by $\pihigh - \pilow$. We set $\pihigh = 0.9$ to be constant
-across all simulations, so our analysis only varies payoff ambiguity by varying
-$\pilow$. Specifically, payoff ambiguity increases with $\pilow$. 
-By systematically varying these uncertainty parameters we change
-the nature of the challenge faced by the agents. Each parameter individually 
-can increase or decrease ``uncertainty,'' but it is not at all clear \emph{a priori}
-how these uncertainties combine to affect the evolution of social learning.
-These uncertainty parameters and the values we tested in our simulations
-are summarized in Table~\ref{tab:uncertaintyParameters}.
+The \emph{payoff ambiguity} is defined by $\pihigh - \pilow$. 
+We set $\pihigh = 0.9$, constant across all simulations, so we vary
+payoff ambiguity by varying $\pilow$, i.e., payoff ambiguity increases with
+$\pilow$.
 
@@
 Agents are endowed with dynamic attributes to intelligently select behaviors and
-calculate average payoffs for each behavior, and with a social learning trait value
-that determines whether agents learn socially or not. All agents engage in
+calculate average payoffs for each behavior. All agents engage in
 individual learning over their lifespan, whether or not they are social learners.
-The difference between social learners and asocial learners is that social learners
-have initially biased behavioral preferences based on information given to them by a
-teacher of the previous generation. Asocial learners begin life with no behavioral
-preferences. Agents and their learning procedures are specified through several
-parameters introduced below.
+Social learners begin life with
+behavioral preferences based on information from their
+teacher, an agent from the previous generation. 
+Asocial learners begin life with no behavioral
+preferences. 
+% Agents and their learning procedures are specified through several
+% parameters introduced below.
 
@@
 All agents perform individual, trial-and-error learning at each time step in
-their lifespan.  This learning is guided by softmax search which
-drives agents to more frequently exploit the most profitable behaviors when the
-agent is more certain which are optimal, and to explore more frequently when the
+their lifespan.  Learning is guided by softmax search. Softmax search
+guides agents to more frequently exploit the most profitable behaviors when the
+agent is more certain which is optimal, and to explore more frequently when the
 agent is unsure.  To do softmax searching, agents track average payoffs acquired
@@
 have performed each behavior.  We denote the average payoffs obtained by agent $i$
-for behavior $b$ as $\ledger$. The number of times $i$ performed $b$ is $c_{ib}$
-(``$c$'' stands for count).
-
-At each time step, agents perform behavior $b$ 
-with softmax-weighted probability
+for behavior $b$ as $\ledger$. We denote the number of times $i$ performed $b$
+as $c_{ib}$ (``$c$'' stands for count). 
+At each time step, agents perform behavior $b$ with softmax-weighted probability
 \begin{equation}
   \Pr(\text{Agent $i$ performs behavior $b$}) = 
-    \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}},
+    \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}}.
 \end{equation}
 \noindent
-where $\beta$ is a parameter that adjusts how frequently agents perform 
+$\beta$ adjusts how frequently agents perform 
 behaviors with high expected payoffs (larger $\beta$) versus how frequently
@@
 At the beginning of each generation other than the first, social child agents select
-one member of the previous generation to learn from if they are a social learner.
-If agent $i$ is a social learner we write $s_i = 1$, and $s_i = 0$ otherwise.
-A child agent $c$ is a social learner if its parent $p$ was a social learner,
-i.e.\ $s_c \leftarrow s_p$, without mutation. 
-Social learner children select a teacher from 
-the previous generation by first selecting $N_T$ prospective teachers fully
-at random, then by sampling from the $N_T$ with each prospective teacher weighted
-by their net payoffs relative to the other $N_T - 1$.
+one member of the previous generation to learn from, if the child inherited
+$s_i = 1$. A child agent $c$ is a social learner if its parent $p$ was a social
+learner, i.e.\ $s_c \leftarrow s_p$, without mutation.  Social learner children
+select a teacher from the previous generation by first selecting $N_T$ prospective
+teachers fully at random, then by sampling from the $N_T$ with each prospective
+teacher weighted by their net payoffs relative to the other $N_T - 1$.
 
@@
 
-In this model, being a social learner is beneficial when it is more likely
-on average to provide greater net payoffs than being an individual learner,
-since evolution here acts as an optimization routine. 
-Note that, unlike some models in the literature, it is not catastrophic for an 
-individual to receive outdated information~\cite[e.g.]{Rogers1988}. Instead,
-agents can explore alternatives and greedily perform a different observed optimal behavior
-than an outdated optimal behavior they learned about socially. We rely
-on this mechanism in the Analysis to explain the patterns we observe where
-social learning evolves when $u > 0.5$, meaning that the
-optimal behavior will switch between generations more often than not. If 
-agents could not adjust to changing conditions like this, it seems like 
-social learning would not evolve when $u > 0.5$.
+In this model, being a social learner is beneficial when it is more likely on
+average to provide greater net payoffs than being an individual learner.  It is not
+catastrophic for an individual to receive outdated information, as is sometimes
+assumed~\cite[e.g.]{Rogers1988}. Instead, agents explore alternatives and
+greedily perform different behaviors that pay off better. 
+This mechanism is critical for explaining the patterns we observe in the 
+Analysis, where social learning evolves when $u > 0.5$.
+In this case, the optimal behavior will switch between generations more often than
+not. Without individual learning, social learning would not evolve when $u > 0.5$.
 
@@
                     exploration 
-               & 100, \textbf{10}, 1 \\
+               & 1, \textbf{10}, 100 \\
 
@@
 
-\paragraph{Intragenerational dynamics}
+\paragraph{Within-generation dynamics}
 % To guide behavior selection, agent $i$ counts how many times it
@@
 represnts the fact that access to the entire population is not generally guaranteed.
-Social learners adopt their chosen teacher's ledger of expected payoffs $\ledger$,
+Social learners adopt their chosen teacher's expected payoffs observations $\ledger$,
 and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$.  Asocial
-learners ($s_i = 0$) are initialized with all $c_{ib} = 0$ and $\ledger = 0$ 
+learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ 
 (Figure~\ref{fig:schematic}C). The
-newly initialized population then begins behavior selection and payoff accumulation
-for another $L$ time steps.
+newly initialized population then repeats within-generation dynamics.
 
 After reproduction and die-off, the optimal behavior changes with probability
-$u$. If a random draw dictates the behavior should change, the new
-behavior is chosen from all other behaviors with the current optimal behavior
-excluded.
+$u$. The new behavior is chosen from all other behaviors, with the 
+current optimal behavior excluded from selection.
 
@@
 this happens in Table~\ref{tab:convergence}.
+
+\clearpage
 
@@
 
-\clearpage
-
 \subsection{Computational analyses}
@@
 
-We developed a series of computational
-analyses by systematically varying uncertainty parameters and observing the
-frequency that model populations evolve to be social learners, the average payoffs
-accrued by agents in each setting, and the time it takes for model populations to
-reach fixation (agents all social or all asocial learners). Model dynamics are
-illustrated in Figure~\ref{fig:schematic}.
+% We developed a series of computational
+% analyses of the effect of uncertainty on social learning evolution by 
+% systematically varying uncertainty parameters and observing how
+% frequently model populations evolve to be social learners.
+
+To analyze the effect of the four principal uncertainty factors, we systematically
+varied uncertainty values and observed how frequently social learning evolved across
+1000 trial simulations. We varied $u \in
+\{0.0, 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$;
+and $L \in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.  We
+observed three outcome measures, with $\meansl$ as the primary measure: 
+the average value of $s_i$ over all agents and trials. To support our conclusions
+based on $\meansl$, we also measured $\meanpi / L$, the average net 
+payoffs at simulation end across agents and trials, normalized by lifespan; 
+and $\meanT / L$, or the mean
+number of time steps to fixation normalized by lifespan. We analyze outcomes by
+plotting $\meansl$ on the y-axis and environmental variation is on x-axis since we
+theoretically expect that $\meansl$ will decrease monotonically from 1 to 0 as $u$
+increases. Note that the hypothesis-testing concept of significance is meaningless
+here because we could make any small outcome difference ``significant'' by running
+more simulation trials.  We instead study the patterns of outcome variables over
+systematically varied uncertainty factor values.
 
@@
 
-To analyze the effect of the four principal uncertainty factors, we systematically
-varied their values and observed three key outcome variables aggregated across 1000
-trial simulations, and across all agents when appropriate. We varied $u \in \{0.0,
-0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L
-\in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.  We observed
-three outcome measures: (1) $\meansl$, the average value of $s_i$ over all agents
-and trials; (2) $\meanpi / L$, the average net payoffs at simulation end across
-agents and trials, normalized by lifespan; and (3) $\meanT / L$, 
-or the mean number of time steps to fixation normalized by
-lifespan. We analyze outcomes by plotting $\meansl$ on the y-axis and environmental
-variation is on x-axis since we theoretically expect that $\meansl$ will 
-decrease monotonically from 1 to 0 as $u$ increases. We expected and observed
-that the other three uncertainty factors shift the value of $u$ at which 
-$\meansl$ starts to decrease, and how rapidly $\meansl$ decreases. Note that the
-hypothesis-testing concept of significance is meaningless here because we could
-make any small outcome difference ``significant'' by running more simulation trials.
-We instead study the patterns of outcome 
-variables over systematically varied uncertainty factor values.
-
 \subsubsection{Sensitivity analyses}
@@
 We performed sensitivity analyses to ensure that our main analysis is reasonably
-robust to a range of auxiliary parameters. Specifically in our sensitivity analyses
-we first varied the population size, $N$, to explore whether smaller $N$ would 
+robust to a range of auxiliary parameters. Specifically,
+we varied the population size, $N$, to explore whether smaller $N$ would 
 show more drift due to finite population size effects, but also generally support
 our main conclusions. Next, we varied the
-cognitive model parameter $\beta \in \{1, 100\}$ to supplement the main results
-that used $\beta = 10$. Recall that $\beta$ sets how frequently the softmax algorithm
-exploited the best observed behavior versus explored the rest. We do not
+softmax greediness parameter $\beta \in \{1, 100\}$ to supplement the main results
+that used $\beta = 10$. We do not
 expect agents with different $\beta$ to perform equally well 
 individually, so certain $\beta$ values may themselves suppress social learning
-since individual learning itself may be unreliable. Nonetheless our results
-should be valid over at least some range of $\beta$. Finally, we varied the
+by undermining individual learning. Nonetheless, our results
+should be valid over some range of $\beta$. Finally, we varied the
 number of prospective teachers $N_T \in \{2, 10, 20\}$ 
 to supplement the main results that used $N_T = 5$. The number of prospective
-teachers should not change the whether social learning is optimal or not, 
-but it may make model results driftier since the benefit of social learning should
+teachers should not change whether social learning is optimal, 
+but it may induce more drift since the benefit of social learning may
 be more difficult to detect with fewer prosopective teachers.
@@
 
-To understand how different forms of uncertainty interact to affect the evolution
-of social learning, we measured simulated social learning prevalence across a 
-suite of simulations over uncertainty parameters. We analyze simulation outcomes
-by plotting the mean observed social learning frequency, $\meansl$, across all agents 
-and 1000 simulation trials for each uncertainty parameter setting. 
-We visualize and inspect plots with $\meansl$ on the y-axis and
-environmental variability, $u$ on the x-axis. This is convenient because we are
-most certain about how $\meansl$ depends on $u$: we expect $\meansl$ to decrease
-as $u$ increases since environmental variability is well understood to cause
-socially-transmitted information to become outdated. When the other forms of
-uncertainty are varied, this causes changes to when and how quickly social learning
-is suppressed as $u$ increases. To inspect these changes, we show nine plots
-of $\meansl$ over $u$ in a $3\times3$ plot array (Figure~\ref{fig:mainResults}). 
-Plot array columns correspond to different selection set sizes, $B$; rows
-correspond to different non-optimal payoff values, $\pilow$ (recall optimal
-payoff $\pihigh=0.9$ for all analyses); plot line and marker colors correspond
-to different effective lifespan, $L$, values. 
-We support our conclusions regarding the evolution of
-social learning by analyzing the time to 
-fixation and by comparing the average net payoffs in our simulations to the
-expected payoffs for individuals in both populations of all social learners
-and in populations of all individual learners. We thus use our analysis 
-to understand changes to how $\meansl$ changes over $u$ for different uncertainty parameter settings.
+To understand how different forms of uncertainty interact to affect the evolution of
+social learning, we measured how frequently social learning evolved across
+uncertainty parameters. We analyze outcomes by plotting the mean observed social
+learning frequency, $\meansl$, across all agents and 1000 simulation trials for each
+uncertainty parameter setting.  We visualize and inspect plots with $\meansl$ on the
+y-axis and environmental variability, $u$ on the x-axis. 
+% This is convenient because we are most certain about how $\meansl$ depends on $u$:
+% we expect $\meansl$ to decrease as $u$ increases since environmental variability
+% is well understood to cause socially-transmitted information to become outdated. 
+To inspect patterns in $\meansl$ over all uncertainty parameters, we analyze nine
+plots of $\meansl$ over $u$ in a $3\times3$ plot array
+(Figure~\ref{fig:mainResults}).  Plot array columns correspond to different
+selection set sizes, $B$; rows correspond to different ambiguous payoffs via
+non-optimal expected payoffs, $\pilow$ (recall $\pihigh=0.9$ for all analyses);
+finally, plot line and marker colors correspond to different effective lifespans,
+$L$.  
+% We support our conclusions regarding the evolution of social learning by analyzing
+% the time to fixation and by comparing the average net payoffs in our simulations
+% to the expected payoffs for individuals in both populations of all social learners
+% and in populations of all individual learners. We thus use our analysis to
+% understand changes to how $\meansl$ changes over $u$ for different uncertainty
+% parameter settings.
 
 Several patterns emerged in changes to social learning prevalence over
-as the uncertainty parameters were varied (Figure~\ref{fig:mainResults}). 
-First, we indeed observed that increased $u$ uniformly led to decreased
-$\meansl$, across the other uncertainty parameter values. The other uncertainty
-parameters changed at which value of $u$ that $\meansl$ started to decrease,
-and how quickly $\meansl$ decreased. For example, 
+the uncertainty parameters (Figure~\ref{fig:mainResults}). 
+First, we indeed observed that greater $u$ uniformly decreased
+$\meansl$, across all other uncertainty parameter values. The other uncertainty
+parameters changed when $\meansl$ began to decrease in terms of $u$,
+and how quickly $\meansl$ decreased from 1 to 0 over $u$. For example, 
 when payoff ambiguity and selection set size were
-both small ($\pilow = 0.1$ and $B=2$) social learning only evolved when $u$ is small
-since individual learning is relatively efficient in this case
-(Figure~\ref{fig:mainResults}, upper left). As $\pilow$ increased,
-$\meansl$ decreased less rapdily over $u$, which was more pronounced for smaller $L$ (rows of
-Figure~\ref{fig:mainResults}).
+both small ($\pilow = 0.1$ and $B=2$) social learning only evolved when $u$ was
+small.
+This is a relatively easy problem, and individual learning is more
+efficient in this case (Figure~\ref{fig:mainResults}, upper left).
+As $\pilow$ increased, $\meansl$ decreased less rapdily over $u$, 
+which was more pronounced for smaller $L$ (see rows of Figure~\ref{fig:mainResults}).
 
@@
 learning with all other uncertainty parameters being equal ($B$ increases along
-columns in Figure~\ref{fig:mainResults}. 
-This is because possibly misleading 
-social information is less consequential due
-to (1) larger $B$ is a more difficult problem for trial-and-error learning, and
-(2) a misidentified optimal behavior is weighted less relative to smaller
-$B$, meaning agents are more likely to explore behaviors identified as non-optimal
-when $B$ is larger (columns of Figure~\ref{fig:mainResults}).  \mt{Support this by calculating the difference between weights when B=2 and B=10 and a social learner learns outdated information}
-Increased $B$ led to more pronounced flattening of social learning suppression when
-$L$ was small, apparently again because of the limited data available to evolution,
-making individual outcomes more path dependent.
-
-Payoff ambiguity had a modest effect when $\pilow = 0.1$ increased to $\pilow = 0.45$,
-causing social learning to be favored across more values of $u$, across all
-selection set sizes and lifespans (first two rows of Figure~\ref{fig:mainResults}). 
-This indicates that increased payoff ambiguity significantly increases the 
-difficulty of discerning which behavior is optimal since agents evolve to 
-risk social learning at greater values of $u$.
-When $\pilow = 0.8$ the largest effect is smoothing and flattening of the $\meansl$ curves,
-which indicates more drift (bottom row of Figure~\ref{fig:mainResults}). 
-Initially this results in less frequent evolution
-of social learning for the same values of $u$ and $B$. But after 
-the $u$ value where $\meansl \approx 0.5$, social learning evolves more frequently than
-for the same $u$, $B$, and $L$. When $\pilow \to \pihigh$, agents do better and better
-whether they are social learners or not. We see that this leads to less penalty
-for trying social information before possibly having to correct course due to
-outdated social information.
-
-When $L$ is smaller, agents have fewer opportunities
-to learn through trial and error, and so it is more difficult for them to discern
-which strategy, social or asocial, is optimal. We thus saw two distinct 
-trends emerge in the evolution of social learning in response to changes in $L$.
-First, when $\pilow$ was sufficiently small ($\pilow=0.1, 0.45$), we observed that shorter
-lifespan made social learning more beneficial (and increased $\meansl$) 
-across some values of $u$. When $\pilow=0.8$, shorter lifespans decreased 
-$\meansl$ in some cases and increased $\meansl$ in other cases. It seems
-that shorter lifespans in this case led to more evolutionary drift. This can
-be seen in two observations. First,
-$\meansl$ is reduced when $L=1$ compared to other lifespans for small values of
-$u$ when other lifespans lead to $\meansl \approx 1$. At larger $u$, when
-$\meansl \to 0$ for other lifespans, the $L=1$ case has non-zero $\meansl$.
+columns in Figure~\ref{fig:mainResults}).  This is because misleading social
+information is easy to overcome for two reasons: (1) larger $B$ presents a more
+difficult problem for trial-and-error learning; and (2) a misidentified optimal
+behavior is weighted less relative to smaller $B$, meaning agents are more likely to
+explore behaviors identified as non-optimal when $B$ is larger (columns of
+Figure~\ref{fig:mainResults}).  
+To understand point (2), consider the case where a social learner child learns
+that behavior 1 has an expected payoff of 0.8, and the rest have an expected
+payoff of 0, but the optimal behavior changes between generations. Assume
+the child tries behavior 1, but it pays off 0.
+If $B=2$, then at within-generation $t=2$, $\ledger = (0.4, 0.0)$. The probability
+the agent explores behavior 2 is now 0.02. However, if $B=10$ the agent has
+$\ledger = (0.4, 0.0, \ldots, 0.0)$; the probability
+the agent explores one of the nine alternative behaviors increases to 0.14.
+If the agent again tries behavior 1, the probability of exploring alternatives
+with $B=2$ is 0.21, but with $B=10$ the probability of exploring alternatives
+greatly increases to 0.71.
+% Larger $B$ caused more drift when
+% $L$ was small, apparently due to the limited data available to evolution.
+
+Payoff ambiguity had a modest effect when $\pilow = 0.1$ increased to $\pilow =
+0.45$, causing social learning to be favored across more values of $u$, and across
+all selection set sizes and lifespans (first two rows of
+Figure~\ref{fig:mainResults}).  This indicates that increased payoff ambiguity
+increases the difficulty of discerning which behavior is optimal since agents evolve
+to risk social learning at greater values of $u$.  When $\pilow = 0.8$ the largest
+effect is smoothing and flattening of the $\meansl$ curves, which indicates more
+drift (bottom row of Figure~\ref{fig:mainResults}).  Initially this results in less
+frequent evolution of social learning for the same values of $u$ and $B$. But after
+the $u$ value where $\meansl \approx 0.5$, social learning evolves more frequently
+than for the same $u$, $B$, and $L$. When $\pilow \to \pihigh$, agents do better and
+better whether they are social learners or not. We see that this leads to less
+penalty for trying social information before possibly having to correct course due
+to outdated social information.
+
+When $L$ is smaller, agents have fewer opportunities to learn through trial and
+error, and so it is more difficult for them to discern which strategy, social or
+asocial, is optimal. We thus saw two distinct trends emerge in the evolution of
+social learning in response to changes in $L$.  First, when $\pilow$ was
+sufficiently small ($\pilow=0.1, 0.45$), we observed that shorter lifespan made
+social learning more beneficial (and increased $\meansl$) across some values of $u$.
+When $\pilow=0.8$, shorter lifespans decreased $\meansl$ in some cases and increased
+$\meansl$ in other cases. It seems that shorter lifespans in this case led to more
+evolutionary drift. This can be seen in two observations. First, $\meansl$ is
+reduced when $L=1$ compared to other lifespans for small values of $u$ when other
+lifespans lead to $\meansl \approx 1$. At larger $u$, when $\meansl \to 0$ for other
+lifespans, the $L=1$ case has non-zero $\meansl$.
 

### 2022-07-23 ms.tex
nearly done with revision; need N=1000 data changeover

@@
 with $B=2$ is 0.21, but with $B=10$ the probability of exploring alternatives
-greatly increases to 0.71.
-% Larger $B$ caused more drift when
-% $L$ was small, apparently due to the limited data available to evolution.
+greatly increases to 0.71. This explanation does not apply when $L=1$, where
+social learning is increasingly beneficial as $B$ increases because it is more 
+valuable to be possibly misled by outdated information than it is for agents
+to blindly guess which is optimal.
 
@@
 all selection set sizes and lifespans (first two rows of
-Figure~\ref{fig:mainResults}).  This indicates that increased payoff ambiguity
-increases the difficulty of discerning which behavior is optimal since agents evolve
-to risk social learning at greater values of $u$.  When $\pilow = 0.8$ the largest
-effect is smoothing and flattening of the $\meansl$ curves, which indicates more
-drift (bottom row of Figure~\ref{fig:mainResults}).  Initially this results in less
+Figure~\ref{fig:mainResults}).  This is because increased payoff ambiguity increases
+the difficulty, and reduces the overall benefit, of discerning which behavior is
+optimal; it is worth the risk for agents to possibly learn outdated information.
+When $\pilow = 0.8$ the largest effect is the smoothing and flattening of the
+$\meansl$ curves, which indicates more drift (bottom row of
+Figure~\ref{fig:mainResults}).  For smaller values of $u$, this results in less
 frequent evolution of social learning for the same values of $u$ and $B$. But after
-the $u$ value where $\meansl \approx 0.5$, social learning evolves more frequently
-than for the same $u$, $B$, and $L$. When $\pilow \to \pihigh$, agents do better and
-better whether they are social learners or not. We see that this leads to less
-penalty for trying social information before possibly having to correct course due
-to outdated social information.
+the value of $u$ at which $\meansl \approx 0.5$, social learning evolves more
+frequently than for the same $u$, $B$, and $L$. When $\pilow \to \pihigh$, agents 
+accumulate increasingly more payoffs, whether they are social learners or not. 
+Greater payoff ambiguity means lower risk to try possibly outdated social
+information, search for the true optimal if the learned one fails.
 
 When $L$ is smaller, agents have fewer opportunities to learn through trial and
-error, and so it is more difficult for them to discern which strategy, social or
-asocial, is optimal. We thus saw two distinct trends emerge in the evolution of
-social learning in response to changes in $L$.  First, when $\pilow$ was
-sufficiently small ($\pilow=0.1, 0.45$), we observed that shorter lifespan made
-social learning more beneficial (and increased $\meansl$) across some values of $u$.
-When $\pilow=0.8$, shorter lifespans decreased $\meansl$ in some cases and increased
-$\meansl$ in other cases. It seems that shorter lifespans in this case led to more
-evolutionary drift. This can be seen in two observations. First, $\meansl$ is
-reduced when $L=1$ compared to other lifespans for small values of $u$ when other
-lifespans lead to $\meansl \approx 1$. At larger $u$, when $\meansl \to 0$ for other
-lifespans, the $L=1$ case has non-zero $\meansl$.
+error, so it is more difficult for them to discern which strategy is optimal, social
+or asocial. We observed two distinct trends in the evolution of social learning as
+$L$ was varied.  First, when $\pilow$ was sufficiently small ($\pilow=0.1, 0.45$),
+we observed that shorter lifespan selected for social learning for some values of
+$u$.  When $\pilow=0.8$, shorter lifespans decreased $\meansl$ in some cases and
+increased $\meansl$ in other cases due to greater evolutionary drift.  In the first
+case, $\meansl$ was reduced for $L=1$ for small values of $u$, when other $L > 1$
+led to $\meansl \approx 1$. At larger $u$ , the $L=1$ case yields non-zero
+$\meansl$, while for the other $L > 1$, $\meansl \approx 0$.
 
@@
 
-\mt{Need to make this section more specific in reviewing the findings.}
-By systematizing four common uncertainty dimensions we developed a model of
-the evolution of social learning that
-predicts how different forms of uncertainty might interact to foster or suppress
-social learning.  The model reproduced classic predictions that social learning can
-yield higher payoffs than individual learning when uncertainty is sufficiently
-limited.  By disambiguating and organizing various operationalizations of
-uncertainty, we developed a more nuanced theoretical understanding of which forms
-of uncertainty interact in which ways to make social learning more or less
-beneficial compared to asocial learning.
-Our model did not make any \emph{a priori} assumptions about whether it was
-more costly for agents to be social or asocial learners, as some studies have
-assumed or imposed~\cite{Rogers1988,Feldman1996,Morgan2012}. 
-Instead, the uncertainty structure determined whether
-or not social learning was beneficial or not, and evolution directed successive
-generations towards the optimal strategy.
-Such detailed theoretical models of uncertainty
-are critical for understanding how humans adapt to an uncertain and
-rapidly changing world, both to mitigate existential
-threats~\cite{Moya2020,Jones2021}, and to capitalize on new opportunities such as
-transitioning to clean energy use and
+\mt{Need to make this section more specific in reviewing the findings.} By
+systematizing four common uncertainty dimensions we developed a model of the
+evolution of social learning that predicts how different forms of uncertainty might
+interact to foster or suppress social learning.  The model reproduced classic
+predictions that social learning can yield higher payoffs than individual learning
+when uncertainty is sufficiently limited.  
+% By disambiguating and organizing various
+% operationalizations of uncertainty, we developed a more nuanced theoretical
+% understanding of which forms of uncertainty interact in which ways to make social
+% learning more or less beneficial compared to asocial learning. 
+Detailed theoretical
+models and predictions of cultural evolution under uncertainty are critical for
+understanding how humans adapt to an uncertain and rapidly changing world, both to
+mitigate existential threats~\cite{Moya2020,Jones2021}, and to capitalize on new
+opportunities such as transitioning to clean energy use and
 production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+
+% Our model did not make any \emph{a priori} assumptions about whether it was
+% more costly for agents to be social or asocial learners, as some studies have
+% assumed or imposed~\cite{Rogers1988,Feldman1996,Morgan2012}. 
+% Instead, the uncertainty structure determined whether
+% or not social learning was beneficial or not, and evolution directed successive
+% generations towards the optimal strategy.
 
@@
 new behavioral affordances as time progresses, e.g.\ via niche 
-construction~\cite{Smaldino2012,Heras-Escribano2020}. Adjusting any of these
-assumptions and running new computational analyses could yield further
-understanding of the evolution of social learning across diverse contexts.
+construction~\cite{Smaldino2012,Heras-Escribano2020} or cumulative cultural
+evolution and dynamic network structure~\cite{Smolla2019,Derex2020}. 
+Adjusting any of these assumptions and running new computational analyses could
+yield further understanding of the evolution of social learning across diverse
+contexts.
 

### 2022-07-29 ms.tex
edits to analysis and model

@@
 
-\begin{abstract}
-Social learning is essential to human survival---it is a critical adaptation for dealing with uncertainty.
-However, uncertainty takes many forms.
-We identified four theoretically important types of uncertainty: temporal environmental variability, ambiguous payoffs, decision set size, and effective lifespans.
-We used this framework to study conditions for the evolution of social learning in populations with cognitively realistic individual learning capacities.
-We used evolutionary agent-based modeling to track how often social learning evolved.
-Agents performed one of several behaviors to acquire payoffs.
-Individual learning used the softmax algorithm.
-Social learning occurs between generations  through vertical and oblique transmission.
-Different types of uncertainty had different effects.
-Temporal environmental variability suppressed social learning.
-Larger decision set sizes promoted social learning.
-Payoff ambiguity and lifespan had more complex effects on social learning, dependent on other uncertainty parameters.
-This shows the importance of clearly operationalizing uncertainty in theories of social learning evolution.
+\begin{abstract} Social learning is essential to human survival---it is a critical
+  adaptation for dealing with uncertainty. However, uncertainty takes many forms.
+  We identified four theoretically important types of uncertainty: temporal
+  environmental variability, ambiguous payoffs, decision set size, and effective
+  lifespans. We used this framework to study conditions for the evolution of
+  social learning in populations with cognitively realistic individual learning
+  capacities.  We used evolutionary agent-based modeling to track how often social
+  learning evolved. Agents performed one of several behaviors to acquire payoffs.
+  Individual learning used the softmax algorithm. Social learning occurs between
+  generations  through vertical and oblique transmission.  Different types of
+  uncertainty had different effects. Temporal environmental variability suppressed
+  social learning. Larger decision set sizes promoted social learning even
+  when environmental change was more likely than not. Payoff
+  ambiguity and lifespan had more complex effects on social learning, dependent on
+  other uncertainty parameters.  This shows the importance of clearly
+  operationalizing uncertainty in theories of social learning evolution.
 % Social learning is essential to human survival. It is likely to evolve when it is more
@@
 
-\textbf{Temporal environmental variability.}
-When external or internal shocks (e.g., climatic events, migration, technological paradigm shifts) occur, strategies that were previously adaptive may no longer be optimal.
-The difficulty in predicting either when such shocks will occur or what behaviors will be adaptive in the resulting environments leads to uncertainty.
-
-Temporal environmental variability is fundamental to most evolutionary models of social learning.
-Such fluctuations have been proposed as an important selective pressure for learned as opposed to genetically fixed behaviors ~\cite{Richerson2000}.
-On the other hand, environments that change too quickly will lead the population to have outdated, and therefore maladaptive information, favoring individual updating over social learning point~\cite{Feldman1996, BoydRicherson1985}.
-This suggests that intermediate levels of temporal variation are important for the evolution of social learning mechanisms ~\cite{aoki2005}.
-
-Despite the centrality of temporal fluctuations, even this construct is implemented in several ways \cite{aoki2014evolution}.
-Most commonly, it is modeled as an independent probability of the environment changing its state each generation ~\cite{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}.
-The probabilities of environmental change are usually fixed per generation, %~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution},
-but they have also been modeled as deterministic cycles ~\cite{Feldman1996, aoki2014evolution}.
-Furthermore, the consequences of environmental change can range from mild to  catastrophic.
-In the latter case, a change of environment results in the total elimination of any adaptive behavior, which must be learned \emph{de novo} for the new environment~\cite{Rogers1988}.
-Such catastrophic environmental changes present a large adaptive challenge as individuals cannot bank on accumulated information from previous generations.
-Other models of environmental change introduce less uncertainty as they fluctuate between two environmental states with corresponding adaptive behaviors.
-This means that all individuals with previously maladaptive behaviors then have adaptive behaviors upon the environment changing ~\cite{perreault2012bayesian}.
-Which strategy one chooses for modelling temporal change can have consequences for at least some of our inferences  ~\cite{aoki2014evolution}.
+\textbf{Temporal environmental variability.} When external or internal shocks
+(e.g., climatic events, migration, technological paradigm shifts) occur,
+strategies that were previously adaptive may no longer be optimal. The difficulty
+in predicting either when such shocks will occur or what behaviors will be
+adaptive in the resulting environments leads to uncertainty.
+
+Temporal environmental variability is fundamental to most evolutionary models of
+social learning. Such fluctuations have been proposed as an important selective
+pressure for learned as opposed to genetically fixed behaviors
+~\cite{Richerson2000}. On the other hand, environments that change too quickly
+will lead the population to have outdated, and therefore maladaptive information,
+favoring individual updating over social learning point~\cite{Feldman1996,
+BoydRicherson1985}. This suggests that intermediate levels of temporal variation
+are important for the evolution of social learning mechanisms ~\cite{aoki2005}.
+
+Despite the centrality of temporal fluctuations, even this construct is
+implemented in several ways \cite{aoki2014evolution}. Most commonly, it is modeled
+as an independent probability of the environment changing its state each
+generation
+~\cite{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}.
+The probabilities of environmental change are usually fixed per generation,
+%~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution}, but they have also been
+modeled as deterministic cycles ~\cite{Feldman1996, aoki2014evolution}.
+Furthermore, the consequences of environmental change can range from mild to
+catastrophic. In the latter case, a change of environment results in the total
+elimination of any adaptive behavior, which must be learned \emph{de novo} for the
+new environment~\cite{Rogers1988}. Such catastrophic environmental changes present
+a large adaptive challenge as individuals cannot bank on accumulated information
+from previous generations. Other models of environmental change introduce less
+uncertainty as they fluctuate between two environmental states with corresponding
+adaptive behaviors. This means that all individuals with previously maladaptive
+behaviors then have adaptive behaviors upon the environment changing
+~\cite{perreault2012bayesian}. Which strategy one chooses for modelling temporal
+change can have consequences for at least some of our inferences
+~\cite{aoki2014evolution}.
 
@@
 
-In studies of social learning, the size of the selection set is very often limited to just two options. 
-For example, in empirical studies of \emph{bombus terresteris} (bumble bee)~\cite{Baracchi2018} and \emph{parus major} (great tit)~\cite{Aplin2017}, experimenters provided two behaviors for
-the bees or birds to choose from, where one yielded a higher payoff than the other. %respectively, each yielding greater or smaller payoffs depending on experimental treatment. 
-Similarly, many human studies have used just two
-or three possible behaviors~\cite{McElreath2005,Toyokawa2019}.
-The simpler empirical choices are often motivated by modeling studies with similar formulations ~\cite{boyd1995does, Rogers1988,perreault2012bayesian}.\cm{pretty sure boyd1995 uses same trick as rogers 88 so not sure why they were being used as illustrating separate kinds of behavior selection sets.
-correct if wrong} Larger, or more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks ~\cite{derex2013, wasielewski2014}, but these map on imperfectly to the theoretical literature.
-Some models have studied systems with larger, but defined, selection sets ~\cite{Rendell2010}, while in others the number of options is subsumed under probabilities of getting a high payoff ~\cite{Enquist2007}.
-Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviors through time ~\cite{Feldman1996}, but it is very rare to find the size of the selection set manipulated \emph{within} generations as a measure of changing uncertainty in cultural evolutionary models.
-
-\textbf{Payoff ambiguity.}
-Many models of social learning differentiate between the payoffs for adopting optimal vs.
-non-optimal behaviors \cite{Rogers1988,Enquist2007,Rendell2010}.
-The size of the difference between these payoffs is usually taken to indicate the strength of selection of learning, which makes sense.
-However, in reality payoffs for particular behaviors are not always consistent.
-A behavior may yield a large payoff sometimes and a small payoff other times \cite{McElreath2005}.
-This means that signals about the relationship between behavior and payoff are often noisy, and differentiating between behavioral options is in part a problem of signal detection.
-When the difference in expected payoffs between optimal and non-optimal behaviors is very large, this noise matters little, as the signal is still very clear.
-However, when the expected payoffs of different behaviors are similar relative to the size of their variances, ambiguity arises about which behaviors really are superior.
-Smaller differences between payoffs corresponds to larger ambiguity.
-Payoff ambiguity has been manipulated in both theoretical ~\cite{perreault2012bayesian} and empirical ~\cite{McElreath2005, Morgan2012} studies, both of which support the claim that payoff ambiguity increases the reliance on social information.
-Importantly, payoff ambiguity %differs from selection set size in that it not only affects uncertainty, it also directly
-influences both uncertainty \emph{and} the strength of selection.
-%This parameter sometimes takes the form of differences in expected payoffs arising from different behaviors or strategies~\cite{Enquist2007,Rendell2010} or by varying the standard deviation of payoffs~\cite{McElreath2005}.
-
-\textbf{Effective lifespan.}
-\mt{Restructure: lead with ``It stands to reason'' sentence or similar that gets
-to the point of this par more quickly, that lifespan affects uncertainty. Also this Effective
-Lifespan section seems too long.}
-Learning can be viewed as a process by which an individual reduces or otherwise manages their uncertainty \cite{jacobs2011bayesian,clark2013whatever}.
-It is an iterative process by which one repeatedly acquires information, forms representations and predictions, and tests and refines those representations and predictions.
-It therefore stands to reason that the more opportunities one has for learning, the more one can in principle reduce one's uncertainty, assuming the environment has not changed in the meantime.
-Similarly, a reduction in the number of opportunities to learn will increase the uncertainty about whether one has accurately learned about the available behavioral options and their associated payoffs.
-We refer to the number of learning opportunities as an individual's effective lifespan to imply that it is the number of opportunities to learn throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.
-
-Empirically, the number of learning opportunities can be manipulated in the lab, but will also correspond with an individual's age the real world.
-In multi-round studies of information use in novel tasks, US participants' use of social information declined precipitously across rounds ~\cite{McElreath2005}, suggesting they were more likely to use social information when they were most uncertain about the task early on.
-In a more naturalistic context, Aplin et al.
-(2017) \nocite{Aplin2017} found that younger great tits more readily used social information compared with older individuals, possibly because they had accrued less information via individual learning, and also possibly because younger individuals have the most to gain (given their expected remaining lifespan) by switching to superior behavioral options.
-% \ps{I got rid of the Leris and Reader reference because it didn't seem relevant to age-based uncertainty.
-They just showed that young guppies exposed to reliable models were more likely to use social information later.
-I also added some human studies, which seems important.}
-Cross-cultural studies on humans have shown the importance of childhood as a phase of heavy social learning ~\cite{Reyes2016}.
-Young children are more likely to acquire their beliefs and simple skills from their parents than are older children or adults, which is at least partly due to the differential knowledge accrual between young children and the older adults to whom they direct the most trust and attention \cite{kline2013teaching}.
-%The age of individuals was found to have an effect on social learning in both \emph{parus major}~\cite{Aplin2017} and \emph{poecilia reticulata} (guppies)~\cite{Leris2016}.
-\ps{What effect?
-I'm not sure }
-%\mt{Need better connection between lifespan and age, or better references to support use of lifespan}.
-Individuals with shorter effective lifespans will end their lives with more uncertainty about which behaviors are optimal, and thereby transmit some of that uncertainty to anyone who learns from them.
-The effective lifespan for learning varies across tasks, individuals, and species, yet most models assume one learning opportunity per generation ~\cite{Feldman1996,Henrich1998, perreault2012bayesian}.
-Some models do allow several cultural generations within 1 genetic generation ~\cite{Enquist2007}, but little formal theory explicitly examines the role of uncertainty based on number of learning opportunities into our understanding of the evolution of social learning.
+In studies of social learning, the size of the selection set is very often limited
+to just two options.  For example, in empirical studies of \emph{bombus
+terresteris} (bumble bee)~\cite{Baracchi2018} and \emph{parus major} (great
+tit)~\cite{Aplin2017}, experimenters provided two behaviors for the bees or birds
+to choose from, where one yielded a higher payoff than the other. %respectively,
+each yielding greater or smaller payoffs depending on experimental treatment.
+Similarly, many human studies have used just two or three possible
+behaviors~\cite{McElreath2005,Toyokawa2019}. The simpler empirical choices are
+often motivated by modeling studies with similar formulations ~\cite{boyd1995does,
+Rogers1988,perreault2012bayesian}.\cm{pretty sure boyd1995 uses same trick as
+rogers 88 so not sure why they were being used as illustrating separate kinds of
+behavior selection sets. correct if wrong} Larger, or more open sets of behavioral
+choices are not uncommon in experiments trying to capture more complex or
+naturalistic tasks ~\cite{derex2013, wasielewski2014}, but these map on
+imperfectly to the theoretical literature. Some models have studied systems with
+larger, but defined, selection sets ~\cite{Rendell2010}, while in others the
+number of options is subsumed under probabilities of getting a high payoff
+~\cite{Enquist2007}. Researchers have also compared models with a different number
+of environment states, corresponding to a different number of optimal behaviors
+through time ~\cite{Feldman1996}, but it is very rare to find the size of the
+selection set manipulated \emph{within} generations as a measure of changing
+uncertainty in cultural evolutionary models.
+
+\textbf{Payoff ambiguity.} Many models of social learning differentiate between
+the payoffs for adopting optimal vs. non-optimal behaviors
+\cite{Rogers1988,Enquist2007,Rendell2010}. The size of the difference between
+these payoffs is usually taken to indicate the strength of selection of learning,
+which makes sense. However, in reality payoffs for particular behaviors are not
+always consistent. A behavior may yield a large payoff sometimes and a small
+payoff other times \cite{McElreath2005}. This means that signals about the
+relationship between behavior and payoff are often noisy, and differentiating
+between behavioral options is in part a problem of signal detection.  When the
+difference in expected payoffs between optimal and non-optimal behaviors is very
+large, this noise matters little, as the signal is still very clear. However, when
+the expected payoffs of different behaviors are similar relative to the size of
+their variances, ambiguity arises about which behaviors really are superior.
+Smaller differences between payoffs corresponds to larger ambiguity. Payoff
+ambiguity has been manipulated in both theoretical ~\cite{perreault2012bayesian}
+and empirical ~\cite{McElreath2005, Morgan2012} studies, both of which support the
+claim that payoff ambiguity increases the reliance on social information.
+Importantly, payoff ambiguity %differs from selection set size in that it not only
+affects uncertainty, it also directly influences both uncertainty \emph{and} the
+strength of selection. %This parameter sometimes takes the form of differences in
+expected payoffs arising from different behaviors or
+strategies~\cite{Enquist2007,Rendell2010} or by varying the standard deviation of
+payoffs~\cite{McElreath2005}.
+
+\textbf{Effective lifespan.} \mt{Restructure: lead with ``It stands to reason''
+sentence or similar that gets to the point of this par more quickly, that lifespan
+affects uncertainty. Also this Effective Lifespan section seems too long.}
+Learning can be viewed as a process by which an individual reduces or otherwise
+manages their uncertainty \cite{jacobs2011bayesian,clark2013whatever}. It is an
+iterative process by which one repeatedly acquires information, forms
+representations and predictions, and tests and refines those representations and
+predictions. It therefore stands to reason that the more opportunities one has for
+learning, the more one can in principle reduce one's uncertainty, assuming the
+environment has not changed in the meantime. Similarly, a reduction in the number
+of opportunities to learn will increase the uncertainty about whether one has
+accurately learned about the available behavioral options and their associated
+payoffs. We refer to the number of learning opportunities as an individual's
+effective lifespan to imply that it is the number of opportunities to learn
+throughout the individual's lifespan that matters here, not necessarily how long
+they live in the absence of relevant learning opportunities.
+
+Empirically, the number of learning opportunities can be manipulated in the lab,
+but will also correspond with an individual's age the real world. In multi-round
+studies of information use in novel tasks, US participants' use of social
+information declined precipitously across rounds ~\cite{McElreath2005}, suggesting
+they were more likely to use social information when they were most uncertain
+about the task early on. In a more naturalistic context, Aplin et al. (2017)
+\nocite{Aplin2017} found that younger great tits more readily used social
+information compared with older individuals, possibly because they had accrued
+less information via individual learning, and also possibly because younger
+individuals have the most to gain (given their expected remaining lifespan) by
+switching to superior behavioral options. 
+% \ps{I got rid of the Leris and Reader reference because it didn't seem relevant
+% to age-based uncertainty. They just showed that young guppies exposed to
+% reliable models were more likely to use social information later. I also added
+% some human studies, which seems important.} 
+Cross-cultural studies on humans have shown the importance of childhood as a phase
+of heavy social learning ~\cite{Reyes2016}. Young children are more likely to
+acquire their beliefs and simple skills from their parents than are older children
+or adults, which is at least partly due to the differential knowledge accrual
+between young children and the older adults to whom they direct the most trust and
+attention \cite{kline2013teaching}.
+%The age of individuals was found to have an effect on social learning in both
+%\emph{parus major}~\cite{Aplin2017} and \emph{poecilia reticulata}
+%(guppies)~\cite{Leris2016}. \ps{What effect? I'm not sure } \mt{Need better
+%connection between lifespan and age, or better references to support use of
+%lifespan}.
+Individuals with shorter effective lifespans will end their lives with more
+uncertainty about which behaviors are optimal, and thereby transmit some of that
+uncertainty to anyone who learns from them. The effective lifespan for learning
+varies across tasks, individuals, and species, yet most models assume one learning
+opportunity per generation ~\cite{Feldman1996,Henrich1998, perreault2012bayesian}.
+Some models do allow several cultural generations within 1 genetic generation
+~\cite{Enquist2007}, but little formal theory explicitly examines the role of
+uncertainty based on number of learning opportunities into our understanding of
+the evolution of social learning.
 
@@
 
-\subsection{Other adaptations to uncertainty}
+% \subsection{Other adaptations to uncertainty} 
+\subsection{Individual-level adaptations to uncertainty}
 
@@
 
-Social learning is the adaptive icing on the cake of other cognitive adaptations to ecological uncertainty. 
-While the literature reviewed above suggests that several forms of uncertainty play a role in favoring the evolution of social learning, several other cognitive mechanisms have also evolved in response to uncertainty ~\cite{volz2012}.
-Many of these are flexible learning mechanisms that do not require assessing others' information.
-For example, people in experimental studies increase their exploratory behavior when total uncertainty in the task increases and are more likely to test %Furthermore, correlations in uncertainty between potential behaviors, humans tend to adopt directed exploration strategies that favor testing
-behaviors with greater observed payoff variance \cite{Wilson2014,Gershman2019}.
-
-Many models of social learning assume little, or nothing, cognitive capabilities of their agents.
-For example, a common modelling strategy compare the payoffs of agents with different pure learning strategies (some will always engage in social learning, and others in individual learning) while revealing nothing about the cognition underlying individuals' decisions  ~\cite{BoydRicherson1985, Rogers1988, aoki2005}.
-Some more complicated learning strategies that make use of both socially and individually learned information have been proposed ~\cite{Enquist2007, perreault2012bayesian}, but these are seldom designed to reflect cognitive mechanisms for integrating information.
-Though such simplifications are often useful, several authors have warned of the risks to \emph{blackboxing}, or ignoring, cognitive mechanisms \cite[p.
-658]{Heyes2016, Kendal2018}, given such details may be theoretically meaningful.
-In order to understand how social learning evolves as an adaptation to uncertainty, we need to endow agents with a  biologically plausible cognition capable of integrating information from various sources in a payoff-maximizing way.
-\cm{I don't understand this next sentence, but think it can be cut with no loss of meaning: In our model we do not impose any structure in randomness between behaviors, so our cognitive model is only sensitive to total randomness.} To do so, we let agents see the payoffs to behaviors and use the softmax function to convert these observations to a probability distribution from which they strategically select their own behavior.
-\cm{does this still make sense?
-and does it need a citation?}
+Social learning is the adaptive icing on the cake of other cognitive adaptations
+to ecological uncertainty.  While the literature reviewed above suggests that
+several forms of uncertainty play a role in favoring the evolution of social
+learning, several other cognitive mechanisms have also evolved in response to
+uncertainty ~\cite{volz2012}. Many of these are flexible learning mechanisms that
+do not require assessing others' information. For example, people in experimental
+studies increase their exploratory behavior when total uncertainty in the task
+increases and are more likely to test %Furthermore, correlations in uncertainty
+between potential behaviors, humans tend to adopt directed exploration strategies
+that favor testing behaviors with greater observed payoff variance
+\cite{Wilson2014,Gershman2019}.
+
+Many models of social learning assume little, or nothing, cognitive capabilities
+of their agents. For example, a common modelling strategy compare the payoffs of
+agents with different pure learning strategies (some will always engage in social
+learning, and others in individual learning) while revealing nothing about the
+cognition underlying individuals' decisions  ~\cite{BoydRicherson1985, Rogers1988,
+aoki2005}. Some more complicated learning strategies that make use of both
+socially and individually learned information have been proposed
+~\cite{Enquist2007, perreault2012bayesian}, but these are seldom designed to
+reflect cognitive mechanisms for integrating information. Though such
+simplifications are often useful, several authors have warned of the risks to
+\emph{blackboxing}, or ignoring, cognitive mechanisms \cite[p. 658]{Heyes2016,
+Kendal2018}, given such details may be theoretically meaningful. In order to
+understand how social learning evolves as an adaptation to uncertainty, we need to
+endow agents with a  biologically plausible cognition capable of integrating
+information from various sources in a payoff-maximizing way. \cm{I don't
+  understand this next sentence, but think it can be cut with no loss of meaning:
+  In our model we do not impose any structure in randomness between behaviors, so
+our cognitive model is only sensitive to total randomness.} To do so, we let
+agents see the payoffs to behaviors and use the softmax function to convert these
+observations to a probability distribution from which they strategically select
+their own behavior. \cm{does this still make sense? and does it need a citation?}
 
@@
 learning frequency, $\meansl$, across all agents and 1000 simulation trials for each
-uncertainty parameter setting.  We visualize and inspect plots with $\meansl$ on the
-y-axis and environmental variability, $u$ on the x-axis. 
+uncertainty parameter setting.   
 % This is convenient because we are most certain about how $\meansl$ depends on $u$:
@@
 plots of $\meansl$ over $u$ in a $3\times3$ plot array
-(Figure~\ref{fig:mainResults}).  Plot array columns correspond to different
-selection set sizes, $B$; rows correspond to different ambiguous payoffs via
-non-optimal expected payoffs, $\pilow$ (recall $\pihigh=0.9$ for all analyses);
-finally, plot line and marker colors correspond to different effective lifespans,
-$L$.  
+(Figure~\ref{fig:mainResults}). All plots show how $\meansl$ changes (y-axis)
+with environmental variability, $u$ (x-axis). Selection set size, $B$ increases
+from left to right in the plot array (columns). Payoff ambiguity via $\pilow$ 
+increases from top to bottom in the array (recall $\pihigh=0.9$ for all analyses).
+Effective lifespan, $L$, is indicated by plot line and marker colors. 
+Several patterns in social learning prevalence emerged as 
+the uncertainty parameters were varied (Figure~\ref{fig:mainResults}). 
 % We support our conclusions regarding the evolution of social learning by analyzing
@@
 
-Several patterns emerged in changes to social learning prevalence over
-the uncertainty parameters (Figure~\ref{fig:mainResults}). 
-First, we indeed observed that greater $u$ uniformly decreased
-$\meansl$, across all other uncertainty parameter values. The other uncertainty
-parameters changed when $\meansl$ began to decrease in terms of $u$,
-and how quickly $\meansl$ decreased from 1 to 0 over $u$. For example, 
+First, we observed that greater $u$ uniformly decreased
+$\meansl$ across all other uncertainty parameter values. The other uncertainty
+parameters changed at which $u$ $\meansl$ began to decrease,
+and how rapidly $\meansl$ decreased over $u$. For example, 
 when payoff ambiguity and selection set size were
-both small ($\pilow = 0.1$ and $B=2$) social learning only evolved when $u$ was
-small.
-This is a relatively easy problem, and individual learning is more
-efficient in this case (Figure~\ref{fig:mainResults}, upper left).
-As $\pilow$ increased, $\meansl$ decreased less rapdily over $u$, 
-which was more pronounced for smaller $L$ (see rows of Figure~\ref{fig:mainResults}).
+both small ($\pilow = 0.1$ and $B=2$), social learning evolved only when $u$ was
+small. These parameter settings present a relatively easy problem for individuals.
+Furthermore, it is relatively costly for agents to be misled by outdated social 
+information in this case, especially for longer lifespans for finding the 
+optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
+In another example, when $\pilow = 0.8$, $\meansl$ decreased less rapdily over $u$ due to 
+weak selection caused by little advantage for performing the optimal versus
+non-optimal behavior (see rows of Figure~\ref{fig:mainResults}).
 
 Increased selection set size $B$ led nearly uniformly to more prevalent social
-learning with all other uncertainty parameters being equal ($B$ increases along
-columns in Figure~\ref{fig:mainResults}).  This is because misleading social
-information is easy to overcome for two reasons: (1) larger $B$ presents a more
-difficult problem for trial-and-error learning; and (2) a misidentified optimal
-behavior is weighted less relative to smaller $B$, meaning agents are more likely to
-explore behaviors identified as non-optimal when $B$ is larger (columns of
-Figure~\ref{fig:mainResults}).  
-To understand point (2), consider the case where a social learner child learns
+learning, all other uncertainty parameters static. Environments with 
+larger $B$ present a more difficult problem for trial-and-error learning within
+a lifespan. This effect is amplified because a misidentified optimal
+behavior is easier to correct for larger $B$ relative to smaller $B$.  
+To understand this, consider the case where a social learner child learns
 that behavior 1 has an expected payoff of 0.8, and the rest have an expected
@@
 
-As a final note, we believe 
-our modeling approach may have applications to developing social artificial
-intelligence, sepcifically multi-agent reinforcement learning
-systems~\cite{Sandholm1996,Ndousse2021,Gronauer2022,Jaques2019}.
-It seems to be implicitly assumed by current multi-agent reinforcement learning
-algorithms that social learning
-would always be beneficial. However, we have shown in our work that sometimes 
-it is more efficient for autonomous social agents to solve problems without
-reference to social information across a variety of uncertainty conditions. 
-Our model agents are essentially software
-robots, so our results should predict the benefit to real-world social robots
-to either learn socially or asocially if the assumptions we make here are 
-reasonably met or implemented in the social robot design.
-Our model dynamics could thus be used as an
-evolutionary algorithm to update AI agents' social learning strategy without
-explicit knowledge of, or need to approximate, the underlying uncertainty structure.
-A designer would need only to program the robots to go through evolutionary
-cycles of simulated ``reproduction'' and ``death''.
-Our model could also predict the expected benefit of social learning, which may be
-inherently costly in artificial multi-agent learning systems due to extra
-energy or time that may be required to transmit information between agents.
+% As a final note, we believe 
+% our modeling approach may have applications to developing social artificial
+% intelligence, sepcifically multi-agent reinforcement learning
+% systems~\cite{Sandholm1996,Ndousse2021,Gronauer2022,Jaques2019}.
+% It seems to be implicitly assumed by current multi-agent reinforcement learning
+% algorithms that social learning
+% would always be beneficial. However, we have shown in our work that sometimes 
+% it is more efficient for autonomous social agents to solve problems without
+% reference to social information across a variety of uncertainty conditions. 
+% Our model agents are essentially software
+% robots, so our results should predict the benefit to real-world social robots
+% to either learn socially or asocially if the assumptions we make here are 
+% reasonably met or implemented in the social robot design.
+% Our model dynamics could thus be used as an
+% evolutionary algorithm to update AI agents' social learning strategy without
+% explicit knowledge of, or need to approximate, the underlying uncertainty structure.
+% A designer would need only to program the robots to go through evolutionary
+% cycles of simulated ``reproduction'' and ``death''.
+% Our model could also predict the expected benefit of social learning, which may be
+% inherently costly in artificial multi-agent learning systems due to extra
+% energy or time that may be required to transmit information between agents.
 

### 2022-07-30 meanNetPayoffs.tex
updated main analysis figures to all be N=1000

@@
       \centering
-      {\hspace{5.25em}\huge $B = 4$}
+      {\hspace{5.25em}\huge $B = 2$}
     \end{minipage}%
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
     \end{minipage}\noindent\begin{minipage}{3.75in}%
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
         \\[-2.75em]

### 2022-07-30 ms.tex
updated main analysis figures to all be N=1000

@@
 
-\mt{Need to make this section more specific in reviewing the findings.} By
+Structure: 
+\begin{itemize}
+  \item 
+    Review
+  \item
+    Cultural evolutionary considerations/modeling choices reflection/future work
+  \item
+    Improved individual learning/modeling choices/future work
+  \item
+    Keep conclusion subsec
+\end{itemize}
+
+\mt{Need to make this section more specific in reviewing the findings and 
+the key insights and explanations about individual and social payoffs, how
+individual learning supports social learning, etc.} By
 systematizing four common uncertainty dimensions we developed a model of the
@@
 evolution and dynamic network structure~\cite{Smolla2019,Derex2020}. 
-Adjusting any of these assumptions and running new computational analyses could
-yield further understanding of the evolution of social learning across diverse
-contexts.
+Adjusting these or other assumptions and performing new analyses could
+add further nuance to our theoretical understanding of the evolution of social learning.
+
+We hypothesized that individual learning supports social learning. One way to 
+test this would be to improve the individual learning algorithm, say with Q-learning(?).
+If better individual learning really hedges against outdated social information,
+then
 

### 2022-08-01 Figures/supplement/fullMeanPrevNetPayoffs.tex
full revision with N=1000 data

--- 2022-07-30 meanNetPayoffs.tex
@@
 \geometry{
-paperwidth=8in,
-paperheight=6.25in,
+paperwidth=12in,
+paperheight=10in,
 margin=0.25in
@@
 \begin{document}
+\begin{tikzpicture}
+      \draw[->,thick] (-.1,0)--(1.15,0) node[above]
+        {\huge $B$};
+        % {Number of behaviors $B$};
+      \draw[->,thick] (0,.1)--(0,-1.15) node[below]
+        {\huge $\pilow$};
+        % {Low payoff frequency $\pilow$};
+	  \end{tikzpicture}~\\[-2em]
 
@@
       {\hspace{5.25em}\huge $B = 2$}
+    \end{minipage}%
+    \begin{minipage}{3.75in}
+      \centering
+      {\hspace{1.0em}\huge $B = 4$}
     \end{minipage}%
@@
       \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
-    \end{minipage}\noindent\begin{minipage}{3.75in}%
+    \end{minipage}\noindent\hspace{1.25em}
+	\begin{minipage}{3.75in}%
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
+    \end{minipage}\noindent
+	\begin{minipage}{3.75in}%
       \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
@@
       \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
+	\end{minipage}\noindent\hspace{1.25em}
+	\begin{minipage}{3.75in}%
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
+    \end{minipage}\noindent
+	\begin{minipage}{3.75in}%
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+    \end{minipage}~\\[0.5em]
+
+    \begin{minipage}{3.75in}
+    \begin{rotate}{90}
+      {\parbox{2.5in}{
+          \centering
+          \vspace{-2.5em} {\huge$ \pilow = 0.8$} \\
+          {\begin{rotate}{-90}{\huge $\frac{\meanpi}{L}$}\hspace{3em}\end{rotate}}
+      }}
+    \end{rotate}%
+    \hspace{2em}
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
         \\[-2.75em]
@@
       \end{center}
-        \end{minipage}\noindent\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+	  \end{minipage}\noindent\hspace{1.25em}
+		\begin{minipage}{3.75in}%
+		  \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
+		  \\[-2.75em]
+	  \begin{center}
+        {\huge $\quad u$}
+      \end{center}
+    \end{minipage}
+	\begin{minipage}{3.75in}%
+		  \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
 		  \\[-2.75em]

### 2022-08-01 ms.tex
full revision with N=1000 data

--- 2022-07-29 ms.tex
@@
 \newcommand{\meanT}{\meanvar{T}}
+\newcommand{\meanG}{\meanvar{G}}
 
@@
 
-\begin{abstract} Social learning is essential to human survival---it is a critical
+\begin{abstract} 
+  Social learning is essential to human survival---it is a critical
   adaptation for dealing with uncertainty. However, uncertainty takes many forms.
@@
 
-Social learning enhances problem solving when acquiring information from others is more efficient than learning on one's own~\cite{Laland2004}.
-However, social learning can also lead individuals astray if, for example, they are copying outdated information.
-Theoretical models have helped clarify the circumstances under which social learning should be evolutionarily favored ~\cite{BoydRicherson1985}.
-This theoretical work has motivated much empirical research and helped predict social learning behavior in humans and other species ~\cite{McElreath2005,Kendal2018,Allen2019}.
-
-One proposal arising from this literature maintains that social learning is as an adaptation for dealing with uncertainty, and one that humans heavily rely on.
-Uncertainty weighs particularly heavily on human adaptation because of our long lifespans, cosmopolitan distribution, and the resulting necessity to adapt to relatively coarse-grain environments \cite{levins1962}.
-However, the term ``uncertainty" often conflates several different interpretations of that word.
-For example, different models define uncertainty in terms of the rate of environmental change, spatial environmental variation, or the reliability of information acquired from the environment.
-Furthermore, in translating mathematical models to verbal predictions, the formal meaning of terms like uncertainty is often lost \cite{lawson1988probability}, facilitating such conflation.
-As the number of formal models of social learning have expanded, an ever increasing number
-of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of uncertainty have made it difficult to compare across models and consolidate our understanding of the contexts in which social learning is adaptive.
-Finally, while risk and uncertainty are often used interchangeably to refer to non-deterministic outcomes, it can be important to distinguish a narrower definition of uncertainty wherein the probabilities of outcomes remain unknown \cite{knight1921, volz2012}.
-
-Other (asocial) forms of learning may also be adaptations to uncertainty, but are usually under-emphasized in this literature.
-Because cultural evolutionary models are more often used to explain social learning mechanisms, they tend to use a single, and often under-powered individual-learning mechanism for comparison.
-This modelling decision may underestimate the extent to which individual learning can address the adaptive challenges solved by social learning, but also underestimate the quality of information available for social learning.
-
-To address these concerns we developed an evolutionary agent-based model that simultaneously operationalizes several
-different forms of uncertainty and endows agents with a powerful learning mechanism.
-We have chosen to model four kinds of uncertainty that are common in cultural evolution models and the related empirical literature:  (1) temporal environmental variability; (2) selection set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning).\ps{citation needed}.
-The model also involves a more cognitively realistic and empirically-motivated learning mechanism, the softmax algorithm.
-This allows a more accurate assessment of tradeoffs between social and individual learning by fleshing out a learning mechanism that makes full use of the individually and socially learned data.
-We use this integrated model to ask what kinds of uncertainty are likely to favor social learning, and to clarify the logic of why this would be the case.
+Social learning enhances problem solving when acquiring information from others is more
+efficient than learning on one's own~\cite{Laland2004}. However, social learning can also
+lead individuals astray if, for example, they are copying outdated information.
+Theoretical models have helped clarify the circumstances under which social learning
+should be evolutionarily favored ~\cite{BoydRicherson1985}. This theoretical work has
+motivated much empirical research and helped predict social learning behavior in humans
+and other species ~\cite{McElreath2005,Kendal2018,Allen2019}.  This literature
+demonstrates that social learning is a critical adaptation found across taxa for dealing
+with uncertainty.  Uncertainty weighs particularly heavily on human adaptation because of
+our long lifespans, cosmopolitan distribution, and the resulting necessity to adapt to
+relatively coarse-grain environments \cite{levins1962}. However, the term ``uncertainty"
+often conflates several different interpretations of that word. For example, different
+models define uncertainty in terms of the rate of environmental change, spatial
+environmental variation, or the reliability of information acquired from the environment.
+Furthermore, in translating mathematical models to verbal predictions, the formal meaning
+of terms like uncertainty is often lost \cite{lawson1988probability}, facilitating such
+conflation. Furthermore, it can be important to distinguish a narrower definition of
+uncertainty wherein the probabilities of outcomes remain unknown~\cite{knight1921,
+volz2012}. As the number of formal models of social learning have expanded, an ever
+increasing number of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of
+uncertainty have made it difficult to compare across models and consolidate our
+understanding of the contexts in which social learning is adaptive. 
+% Finally, while risk and uncertainty are often used interchangeably to refer to
+% non-deterministic outcomes,
+
+Other (asocial) forms of learning may also be adaptations to uncertainty that could be
+accounted for, but are typically glossed over.  In general, learning is an iterative
+process by which one repeatedly acquires information, forms representations and
+predictions, and tests and refines those representations and predictions to manage
+uncertainty~\cite{jacobs2011bayesian,clark2013whatever}.  Because cultural evolutionary
+models are more often used to explain social learning mechanisms, they tend to use a
+single, weak individual-learning mechanism for comparison. Abstracting away asocial forms
+of learning may lead us to underestimate the extent to which individual learning provides
+quality information for social learning and for the individual to adapt to the challenges
+assumed to be solved by social learning. 
+% underestimate the quality of information
+% available for social learning.
+
+To address these concerns we developed an evolutionary agent-based model that
+simultaneously operationalizes several different forms of uncertainty and endows agents
+with a relatively powerful learning mechanism. We have chosen to model four kinds of
+uncertainty that are common in cultural evolution models and the related empirical
+literature:  (1) temporal environmental variability; (2) selection set size (the number of
+possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for
+different behaviors); and (4) the effective lifespan of agents (the number of
+opportunities for individual learning), explained below. The model also assumes a more
+cognitively realistic and empirically-motivated learning mechanism, the softmax algorithm.
+This allows for a more accurate assessment of tradeoffs between 
+social and asocial learning
+by fleshing out an individual-level learning mechanism that makes full use of 
+the individually and socially learned data. 
+In this work, social learners learn from the previous generation, and 
+asocial learners do not. All agents engage in individual-level learning within
+their lifespans whether they are social learners or not.
+We use this integrated model to ask what kinds of uncertainty are likely to
+favor social learning, and to clarify the logic of why this would be the case.
 
@@
 ~\cite{Richerson2000}. On the other hand, environments that change too quickly
-will lead the population to have outdated, and therefore maladaptive information,
-favoring individual updating over social learning point~\cite{Feldman1996,
+will lead the population away from social learning to avoid outdated, 
+and therefore maladaptive information~\cite{Feldman1996,
 BoydRicherson1985}. This suggests that intermediate levels of temporal variation
-are important for the evolution of social learning mechanisms ~\cite{aoki2005}.
-
-Despite the centrality of temporal fluctuations, even this construct is
-implemented in several ways \cite{aoki2014evolution}. Most commonly, it is modeled
+are important for the evolution of social learning mechanisms~\cite{aoki2005}.
+
+Despite the theoretical centrality of temporal environmental variability, this construct is
+implemented in several ways~\cite{aoki2014evolution}. Most commonly, it is modeled
 as an independent probability of the environment changing its state each
@@
 ~\cite{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}.
-The probabilities of environmental change are usually fixed per generation,
-%~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution}, but they have also been
-modeled as deterministic cycles ~\cite{Feldman1996, aoki2014evolution}.
+% The probabilities of environmental change are usually fixed per generation
+% ~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution}, 
+but has also been modeled as deterministic cycles~\cite{Feldman1996, aoki2014evolution}.
 Furthermore, the consequences of environmental change can range from mild to
@@
 new environment~\cite{Rogers1988}. Such catastrophic environmental changes present
-a large adaptive challenge as individuals cannot bank on accumulated information
+a large adaptive challenge as individuals cannot rely on accumulated information
 from previous generations. Other models of environmental change introduce less
 uncertainty as they fluctuate between two environmental states with corresponding
-adaptive behaviors. This means that all individuals with previously maladaptive
-behaviors then have adaptive behaviors upon the environment changing
-~\cite{perreault2012bayesian}. Which strategy one chooses for modelling temporal
-change can have consequences for at least some of our inferences
-~\cite{aoki2014evolution}.
+adaptive behaviors. This means that previously maladaptive
+behaviors become adaptive when the environment changes
+~\cite{perreault2012bayesian}. The chosen mechanism for modelling temporal
+change has real theoretical consequences~\cite{aoki2014evolution}.
 
 \textbf{Selection set size.}
-When one does not know which option to take, uncertainty increases with the number of options.
-This is a mathematical fact at the core of information theory: the number of bits required to reliably encode the optimal solution increases by one every time the selection set doubles in size  \cite{mackay2003information}.
-This is intuitive; the more options to consider, the greater one's uncertainty about which option is the best choice.
-
-In studies of social learning, the size of the selection set is very often limited
+When one does not know which option to take, uncertainty increases with the number of options, which we call the selection set size.
+% This is a mathematical fact at the
+% core of information theory: the number of bits required to reliably encode the optimal solution increases by one every time the
+% selection set doubles in size~\cite{mackay2003information}. 
+% This is intuitive; the more options to consider, the greater one's uncertainty about which option is the best choice. 
+In studies of social learning, the selection set is often limited
 to just two options.  For example, in empirical studies of \emph{bombus
@@
 Similarly, many human studies have used just two or three possible
-behaviors~\cite{McElreath2005,Toyokawa2019}. The simpler empirical choices are
-often motivated by modeling studies with similar formulations ~\cite{boyd1995does,
-Rogers1988,perreault2012bayesian}.\cm{pretty sure boyd1995 uses same trick as
-rogers 88 so not sure why they were being used as illustrating separate kinds of
-behavior selection sets. correct if wrong} Larger, or more open sets of behavioral
+behaviors~\cite{McElreath2005,Toyokawa2019}. Behavioral study designs are
+often motivated by modeling studies with similar formulations~\cite{Rogers1988,boyd1995does,
+perreault2012bayesian}.
+% \cm{pretty sure boyd1995 uses same trick as
+% rogers 88 so not sure why they were being used as illustrating separate kinds of
+% behavior selection sets. correct if wrong} 
+Larger, more open sets of behavioral
 choices are not uncommon in experiments trying to capture more complex or
-naturalistic tasks ~\cite{derex2013, wasielewski2014}, but these map on
-imperfectly to the theoretical literature. Some models have studied systems with
-larger, but defined, selection sets ~\cite{Rendell2010}, while in others the
-number of options is subsumed under probabilities of getting a high payoff
-~\cite{Enquist2007}. Researchers have also compared models with a different number
+naturalistic tasks~\cite{derex2013, wasielewski2014}, but these map on
+imperfectly to the theoretical literature \mt{How so?}. Some models have studied systems with
+larger, but defined, selection sets~\cite{Rendell2010}, while in others the
+number of options is implicit in the model payoff structure
+~\cite{Enquist2007} \mt{How does this work exactly in Enquist et al 2007?}. 
+Researchers have also compared models with a different number
 of environment states, corresponding to a different number of optimal behaviors
-through time ~\cite{Feldman1996}, but it is very rare to find the size of the
-selection set manipulated \emph{within} generations as a measure of changing
-uncertainty in cultural evolutionary models.
+through time ~\cite{Feldman1996}. These examples share one common feature: 
+the size of the selection set was held static \emph{within} model generations.
+% as a measure of changing uncertainty in cultural evolutionary models.
 
@@
 
-\textbf{Effective lifespan.} \mt{Restructure: lead with ``It stands to reason''
-sentence or similar that gets to the point of this par more quickly, that lifespan
-affects uncertainty. Also this Effective Lifespan section seems too long.}
-Learning can be viewed as a process by which an individual reduces or otherwise
-manages their uncertainty \cite{jacobs2011bayesian,clark2013whatever}. It is an
-iterative process by which one repeatedly acquires information, forms
-representations and predictions, and tests and refines those representations and
-predictions. It therefore stands to reason that the more opportunities one has for
-learning, the more one can in principle reduce one's uncertainty, assuming the
-environment has not changed in the meantime. Similarly, a reduction in the number
+\textbf{Effective lifespan.} 
+The more opportunities one has for
+learning in their lifespan, the more uncertainty can be reduced, assuming a
+static environment. Similarly, a reduction in the number
 of opportunities to learn will increase the uncertainty about whether one has
 accurately learned about the available behavioral options and their associated
-payoffs. We refer to the number of learning opportunities as an individual's
+payoffs. That uncertainty is passed on to future generations.
+% Learning is an iterative process by which one repeatedly acquires information, forms
+% representations and predictions, and tests and refines those representations and
+% predictions to manage uncertainty \cite{jacobs2011bayesian,clark2013whatever}. 
+We refer to the number of learning opportunities as an individual's
 effective lifespan to imply that it is the number of opportunities to learn
@@
 %lifespan}.
-Individuals with shorter effective lifespans will end their lives with more
-uncertainty about which behaviors are optimal, and thereby transmit some of that
-uncertainty to anyone who learns from them. The effective lifespan for learning
+% Individuals with shorter effective lifespans will end their lives with more
+% uncertainty about which behaviors are optimal, and thereby transmit some of that
+% uncertainty to anyone who learns from them. 
+The effective lifespan for learning
 varies across tasks, individuals, and species, yet most models assume one learning
@@
 endow agents with a biologically plausible cognition capable of integrating
-information from various sources in a payoff-maximizing way. \cm{I don't
-  understand this next sentence, but think it can be cut with no loss of meaning:
-  In our model we do not impose any structure in randomness between behaviors, so
-our cognitive model is only sensitive to total randomness.} To do so, we let
+information from various sources in a payoff-maximizing way~\cite{Gershman2019}. 
+% \cm{I don't
+%   understand this next sentence, but think it can be cut with no loss of meaning:
+%   In our model we do not impose any structure in randomness between behaviors, so
+% our cognitive model is only sensitive to total randomness.} 
+To do so, we let
 agents see the payoffs to behaviors and use the softmax function to convert these
 observations to a probability distribution from which they strategically select
-their own behavior. \cm{does this still make sense? and does it need a citation?}
+their own behavior. %\cm{does this still make sense? and does it need a citation?}
 
@@
 ability of agents to find and choose the optimal behavior: 
-\emph{environmental variability}; \emph{payoff ambiguity};
-\emph{selection set size}; and the \emph{effective lifespan}. Environmental
-variability is the probability that the optimal behavior changes
+\emph{environmental variability}; 
+\emph{selection set size}; \emph{payoff ambiguity}; and the \emph{effective lifespan}. 
+Environmental variability is the probability that the optimal behavior changes
 between generations. We do not consider within-generation variability. 
@@
 e.g., if it was assumed to be equally costly for animals to
-access alternative food sources~\cite{Aplin2017,Baracchi2018}.  
+visit alternative food sources~\cite{Aplin2017,Baracchi2018}.  
 % This is empirically justified since cultural evolution
@@
 social learning, we measured how frequently social learning evolved across
-uncertainty parameters. We analyze outcomes by plotting the mean observed social
-learning frequency, $\meansl$, across all agents and 1000 simulation trials for each
+uncertainty parameters. We analyzed outcomes by plotting the mean observed social
+learning frequency, $\meansl$, with mean taken across all agents and 1000 simulation trials for each
 uncertainty parameter setting.   
@@
 % is well understood to cause socially-transmitted information to become outdated. 
-To inspect patterns in $\meansl$ over all uncertainty parameters, we analyze nine
-plots of $\meansl$ over $u$ in a $3\times3$ plot array
-(Figure~\ref{fig:mainResults}). All plots show how $\meansl$ changes (y-axis)
-with environmental variability, $u$ (x-axis). Selection set size, $B$ increases
-from left to right in the plot array (columns). Payoff ambiguity via $\pilow$ 
-increases from top to bottom in the array (recall $\pihigh=0.9$ for all analyses).
-Effective lifespan, $L$, is indicated by plot line and marker colors. 
+% To inspect patterns in $\meansl$ over all uncertainty parameters, 
+We analyze nine plots of how $\meansl$ (y-axis in each plot) changes over $u$ (x-axis) 
+in a $3\times3$ plot array (Figure~\ref{fig:mainResults}). 
+% All plots show how $\meansl$ changes (y-axis)
+% with environmental variability, $u$ (x-axis). 
+Selection set size, $B$ increases from left to right in the plot array (columns). 
+Payoff ambiguity increases as $\pilow$ increases from top to bottom in the array 
+(recall $\pihigh=0.9$ for all analyses).
+Effective lifespan, $L$, is indicated by line and marker colors (inset). 
 Several patterns in social learning prevalence emerged as 
-the uncertainty parameters were varied (Figure~\ref{fig:mainResults}). 
+these uncertainty parameters were varied (Figure~\ref{fig:mainResults}). 
 % We support our conclusions regarding the evolution of social learning by analyzing
@@
 
-First, we observed that greater $u$ uniformly decreased
+First, we confirmed the current theoretical understanding that greater $u$ uniformly decreased
 $\meansl$ across all other uncertainty parameter values. The other uncertainty
-parameters changed at which $u$ $\meansl$ began to decrease,
-and how rapidly $\meansl$ decreased over $u$. For example, 
-when payoff ambiguity and selection set size were
+parameters changed the $u$ value at which $\meansl$ began to decrease,
+and how rapidly $\meansl$ decreased over $u$. 
+For example, when payoff ambiguity and selection set size were
 both small ($\pilow = 0.1$ and $B=2$), social learning evolved only when $u$ was
-small. These parameter settings present a relatively easy problem for individuals.
-Furthermore, it is relatively costly for agents to be misled by outdated social 
-information in this case, especially for longer lifespans for finding the 
-optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
-In another example, when $\pilow = 0.8$, $\meansl$ decreased less rapdily over $u$ due to 
-weak selection caused by little advantage for performing the optimal versus
-non-optimal behavior (see rows of Figure~\ref{fig:mainResults}).
+small. 
+% These parameter settings present a relatively easy problem for individuals.
+% Furthermore, it is relatively costly for agents to be misled by outdated social 
+% information in this case, especially for longer lifespans for finding the 
+% optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
+When $\pilow = 0.8$ and $B=2$, for exapmle, $\meansl$ decreased less rapdily over $u$ due to 
+drift caused by weak selection caused by little advantage for performing the optimal versus
+non-optimal behavior (see rows of Figure~\ref{fig:mainResults}). We analyzed several
+such patterns of social learning evolution and suppression across different uncertainty settings.
 
 Increased selection set size $B$ led nearly uniformly to more prevalent social
-learning, all other uncertainty parameters static. Environments with 
-larger $B$ present a more difficult problem for trial-and-error learning within
-a lifespan. This effect is amplified because a misidentified optimal
-behavior is easier to correct for larger $B$ relative to smaller $B$.  
+learning, with all other uncertainty parameters held constant. This is first 
+because it is more difficuilt to find the optimal behavior with a larger $B$.
+% more options present a more difficult problem for trial-and-error learning within
+% a lifespan. 
+This effect is amplified because agents in a world with larger $B$ are more
+cognitively flexible compared to those in a smaller $B$ world. 
+When $B$ is larger, agents are relatively more likely to choose an alternative to
+their current known optimum. %is easier to correct for larger $B$ relative to smaller $B$.  
 To understand this, consider the case where a social learner child learns
 that behavior 1 has an expected payoff of 0.8, and the rest have an expected
-payoff of 0, but the optimal behavior changes between generations. Assume
+payoff of 0, but the optimal behavior changed between generations. Assume
 the child tries behavior 1, but it pays off 0.
-If $B=2$, then at within-generation $t=2$, $\ledger = (0.4, 0.0)$. The probability
+If $B=2$, then at the next within-generation time step, $\ledger = (0.4, 0.0)$. The probability
 the agent explores behavior 2 is now 0.02. However, if $B=10$ the agent has
@@
 greatly increases to 0.71. This explanation does not apply when $L=1$, where
-social learning is increasingly beneficial as $B$ increases because it is more 
-valuable to be possibly misled by outdated information than it is for agents
-to blindly guess which is optimal.
+individual learning does not occur. %social learning is the only possible form of learning.
 
 Payoff ambiguity had a modest effect when $\pilow = 0.1$ increased to $\pilow =
-0.45$, causing social learning to be favored across more values of $u$, and across
-all selection set sizes and lifespans (first two rows of
+0.45$, causing social learning to be favored across more values of $u$ (first two rows of
 Figure~\ref{fig:mainResults}).  This is because increased payoff ambiguity increases
 the difficulty, and reduces the overall benefit, of discerning which behavior is
-optimal; it is worth the risk for agents to possibly learn outdated information.
-When $\pilow = 0.8$ the largest effect is the smoothing and flattening of the
-$\meansl$ curves, which indicates more drift (bottom row of
+optimal.  When $\pilow = 0.8$ the
+$\meansl$ curves become smoother, indicating more evolutionary drift towards 
+possibly non-optimal fixations (bottom row of
 Figure~\ref{fig:mainResults}). For smaller values of $u$, this results in less
-frequent evolution of social learning for the same values of $u$ and $B$. But after
-the value of $u$ at which $\meansl \approx 0.5$, social learning evolves more
-frequently than for the same $u$, $B$, and $L$. When $\pilow \to \pihigh$, agents 
-accumulate increasingly more payoffs, whether they are social learners or not. 
+frequent evolution of social learning for the same values of $u$ and $B$. But past
+the value of $u$ where $\meansl \approx 0.5$ this switches, and social learning evolves more
+frequently than for smaller $\pilow$. 
+% When $\pilow \to \pihigh$, agents 
+% accumulate increasingly more payoffs, whether they are social learners or not. 
 Greater payoff ambiguity means lower risk to try possibly outdated social
-information, search for the true optimal if the learned one fails.
-
-When $L$ is smaller, agents have fewer opportunities to learn through trial and
-error, so it is more difficult for them to discern which strategy is optimal, social
-or asocial. We observed two distinct trends in the evolution of social learning as
+information by reducing the penalty for performing non-optimal behaviors.
+
+We observed two distinct trends in the evolution of social learning as
 $L$ was varied.  First, when $\pilow$ was sufficiently small ($\pilow=0.1, 0.45$),
-we observed that shorter lifespan selected for social learning for some values of
-$u$.  When $\pilow=0.8$, shorter lifespans decreased $\meansl$ in some cases and
-increased $\meansl$ in other cases due to greater evolutionary drift.  In the first
-case, $\meansl$ was reduced for $L=1$ for small values of $u$, when other $L > 1$
-led to $\meansl \approx 1$. At larger $u$ , the $L=1$ case yields non-zero
-$\meansl$, while for the other $L > 1$, $\meansl \approx 0$.
+we observed that shorter lifespan extended the evolution of social learning over more values of
+$u$, since payoff-biased social learning means teachers are reliable.
+When $\pilow=0.8$, shorter lifespans decreased $\meansl$ in some cases and
+increased $\meansl$ in other cases due to greater evolutionary drift. In
+this setting, many agents will obtain a payoff of 1 at each time step in their 
+lifetime, which, combined with finite population size, will make it more likely for 
+evolution to settle on a non-optimal population fixation.
+% In the first
+% case, $\meansl$ was reduced for $L=1$ for small values of $u$, when other $L > 1$
+% led to $\meansl \approx 1$. At larger $u$ , the $L=1$ case yields non-zero
+% $\meansl$, while for the other $L > 1$, $\meansl \approx 0$. 
+Smaller $L$ means agents end their lives more uncertain about which behavior was
+optimal, but payoff-biased teacher selection and learning can remedy this if
+payoff ambiguity is sufficiently small.
+% When $L$ is smaller, agents have fewer opportunities to learn through trial and
+% error, so it is more difficult for them to discern which strategy is optimal, social
+% or asocial.
 
@@
 
-\subsection{Supplemental measures of social learning}
-
-\mt{This subsec needs revision and associated figures need to be updated with 
-$N=1000$ data}
-
-Social learning evolution was correlated with differences in population-level
-expected payoffs for social versus asocial learning. Furthermore, we found that mean
-payoffs realized by our simulated agents track either the expected social learning
-payoffs, $\meansoc$, or the expected asocial learning payoffs, $\meanasoc$.
-$\meansoc$ and $\meanasoc$ were calculated across uncertainty contexts by
-initializing the model to be all social or all individual learners then running the
-model for 100 generations for social learning and across 1000 one-generation trials
-for individual learning.  Simulated evolutionary mean payoffs across agents and
-trials, $\meanpi$, are initially higher than expected asocial learning, $\meanasoc$,
-and comparable to expected social learning, $\meansoc$, in most cases 
-(Figure~\ref{fig:payoffs}).  But as social learning becomes less beneficial due to
-increased environmental variability, $\meansoc$ and $\meanpi$ approach $\meanasoc$.
-
-It appears agents tend to be ``conservative'' with their decision to learn socially
-or not as expected social and asocial learning payoffs approach each
-other---it seems $\meansl \to 0$ while social
-learning is still theoretically optimal. When $L=1$, $\meanpi$ can be greater than
-$\meansoc$ because asocial learners at the beginning of the simulation help to 
-pass on less misleading information on average, so that the cultural information passed on by
-eventual all-social learner populations have more noise. This noise further reduces the
-weighting of the previous generation's observed optimal payoff if it changes between
-generations enabling agents to more efficiently explore alternatives before focusing
-on a misidentified optimal behavior.
+\subsection{The relative benefit of social learning and the presence of evolutionary drift}
+
+To explain the evolution of social learning we assumed that, first, the relative benefit
+of having the social learning trait is essential to its evolution; and, second,
+we assumed that values of $\meansl \neq 0,1$ indicate evolutionary drift---but does our
+data support these assumptions?  Indeed, social learning evolution and evolutionary
+drift depended on the relative benefit of the social learning trait. We measured
+drift in terms of the average number of generations to fixation, denoted $\langle G
+\rangle$. Indeed, social learning evolution and drift are reflected in the relative
+benefit of social learning to asocial learning.  When social and asocial learning are
+equally beneficial, fixation takes longer to achieve, indicating greater drift.
+
+First, we confirmed that social learning evolves when $\meansoc > \meanasoc$.
+% by first comparing the expected
+% payoff for populations initialized as either all individual learners or all social
+% learners, denoted $\meansoc$ and $\meanasoc$, respectively.  
+In the case of $L=1$ we can calculate $\meanasoc$ directly: it is just the
+expected payoff across all bandits. When $L=8$, and for all uncertainty parameters 
+for $\meansoc$, we calculate expected social and asocial payoffs by respectively setting
+$\sum_i = N$ or $\sum_i = 0$ at model initialization. These stay constant since
+we do not allow for mutation.  We show expected payoffs for these four settings in this main text; we show the same
+plots for $\pilow = 0.8$ in the supplement both for $N=1000$ and $N=100$.
+
+Further inspection of maximal payoff ambiguity ($\pilow = 0.8$) showed strong
+effects of population size under sensitivity analysis\mt{TODO; not currently included in 
+the appendix}. In the default setting
+of $N=1000$, populations of initially all social learners performed much worse
+in many uncertainty contexts than either the actual payoffs accumulated by 
+model agents, and lower than even the expected individual-level payoffs,
+even though social learning evolved in many of the same contexts in our model
+with the default settings (Figure SupplementX1). When the population was
+reduced to $N=100$, there was a tighter evolutionary bottleneck on 
+underperforming agents, and selection more effectively weeded out underperforming agents.
+This demonstrates that larger populations not only can support beneficial
+choices~\cite{Henrich2004}, but also maladaptive information.
 
 \begin{figure}
-  \caption{Mean payoff normalized for lifespan (y-axes, solid lines with circles)
-    generally track either expected all-social-learners payoff ($\meansoc$, dash-dot
-    line with diamonds) or expected all-asocial payoff ($\meanasoc$, long dash
-    horizontal lines) as $u$ increases (x-axes). When $\meansl$ goes from 1 to
-  0 is when social learning payoffs approach individual learning payoffs due to
-increased environmental variability.} 
+  \caption{Comparison of expected payoffs from our computational anaysis (solid
+    lines with circles), expected individual payoffs with no social learning
+    (dashes without markers), and expected payoffs for all-social learner 
+    populations. Only four plots shown to enhance detail; see supplement for
+    five additional plots.
+clarity.} 
   \label{fig:payoffs}
 \centering
-    \includegraphics[width=0.75\textwidth]{Figures/meanNetPayoffs.pdf}
+    \includegraphics[width=0.85\textwidth]{Figures/meanNetPayoffs.pdf}
 \end{figure}
 
-The number of generations to reach fixation increased
-when expected social learning payoffs approached expected asocial payoffs, i.e.,
-when $\meansl$ becomes suppressed (Figure~\ref{fig:steps}). Recall a fixated
-state is when $\sum_i s_i = 0 \text{ or } 1$.  This supports our explanation that
-the supression of social learning begins when individual simulation outcomes are
-more path dependent and susceptible to end in a non-optimal state since simulations
-in these conditions also take longer to reach fixation.  For example, when
-$\pilow=0.1$, $B=4$, and $L=8$, we see a sharp increase in $\meanT$ when social learning
-suppression begins; but when $L=1$, social learning suppression is flatter
-than for $L=8$, and  correspondingly its $\meanT$ is not as strongly peaked, but is
-elevated across the $u$ (Figure~\ref{fig:steps} upper left).  In some cases $L=1$
-trials reached fixation faster than $L=8$ or $L=20$; larger $L$ had larger peak $\meanT/L$
-than smaller $L$, for example, both for the cases shown in Figure~\ref{fig:steps}
-and across all settings tested \mt{TODO: add full figure to SI}. 
-However, we also see situations where $L=1$ and fixation takes longer than $L=8$.
-This is especially pronounced for
-$\pilow = 0.45$ where social learning suppression is much flatter for $L=1$
-(Figure~\ref{fig:steps}, bottom row). In general, then, a sharper peak in $\meanT$
-indicates a sharper suppression of social learning over $u$ and a flatter peak,
-elevated over more values of $u$, indicates greater path dependence and more 
-drift overall.
+We confirmed that drift increased when $\meansl$ transitioned from 1 to 0, 
+and when $\pilow$ was increased. We measured drift by the average number of 
+generations to fixation, $\meanG$. Recall fixation is defined as the population
+becoming homogenous, composed of all social or all asocial learners. 
+$\meanG$ peaks around the values of $u$ 
+when $\meansoc \approx \meanasoc$, which led $\meansl$ to transition from 1 to 0.
+In some cases, especially when $\pilow=0.8$,
+there is no distinct peak in $\meanG$ across $B$ and $L$ settings, 
+indicating little difference in task difficulty across a range of uncertainty parameter settings.
 
 \begin{figure}
-  \caption{Average number of generations ($\meanT/L$, y-axes) for populations to fixate
-  where agents either all become social or all become asocial learners. As
-  $u$ increases (x-axes) models take longer to fixate due to drift, up to a point,
-but then fixation accelerates as individual learning becomes more obviously 
-superior. Increased $\pilow$ increases time to fixate; both $\pilow$ and $B$
-shift peak time to fixation over $u$.} 
+  \caption{Average number of generations ($\meanG$, y-axes) to fixation . 
+    $\meanG$ increases and peaks around values of $u$ (x-axes) where
+  $\meansoc \approx \meanasoc$. Note the y-axis ticks vary between plots,
+indicating different overall time to fixation for different $(\pilow, B)$
+pairs. Only extremal tested values of $L$ shown for clarity.} 
   \label{fig:steps}
 \centering
-    \includegraphics[width=0.75\textwidth]{Figures/stepResultsPlots.pdf}
+    \includegraphics[width=\textwidth]{Figures/stepResultsPlots.pdf}
 \end{figure}
@@
 
-\mt{Need to make this section more specific in reviewing the findings.} By
-systematizing four common uncertainty dimensions we developed a model of the
-evolution of social learning that predicts how different forms of uncertainty might
-interact to foster or suppress social learning.  The model reproduced classic
-predictions that social learning can yield higher payoffs than individual learning
-when uncertainty is sufficiently limited.  
-% By disambiguating and organizing various
-% operationalizations of uncertainty, we developed a more nuanced theoretical
-% understanding of which forms of uncertainty interact in which ways to make social
-% learning more or less beneficial compared to asocial learning. 
-Detailed theoretical
-models and predictions of cultural evolution under uncertainty are critical for
-understanding how humans adapt to an uncertain and rapidly changing world, both to
-mitigate existential threats~\cite{Moya2020,Jones2021}, and to capitalize on new
-opportunities such as transitioning to clean energy use and
+By disambiguating and organizing various operationalizations of
+uncertainty, we developed a more nuanced theoretical understanding of which forms of
+uncertainty interact to affect social learning.  We reviewed and distilled the several empirical and
+theoretical models in the literature along four uncertainty dimensions: temporal
+environmental uncertainty, selection set size, ambiguous payoffs, and effective lifespan.
+The model reproduced classic predictions that social learning can yield higher payoffs
+than individual learning when uncertainty is sufficiently limited. Our model also
+demonstrated a new insight into social learning as a scaffold for individual learning,
+enabled by endowing agents with an evolutionarily- and biologically-plausible individual
+learning mechanism, softmax search. Specifically, we found that agents could recover from
+receiving outdated information, so social learning could evolve even though social
+information was outdated more often than not. We found increased payoff ambiguity and
+lifespan led to greater drift, which is essentially evolutionary uncertainty in a
+finite-size population. Detailed theoretical models and
+predictions of cultural evolution under uncertainty are critical for understanding how
+humans adapt to an uncertain and rapidly changing world, both to mitigate existential
+threats~\cite{Moya2020,Jones2021}, especially in the most vulnerable
+communities~\cite{McNamara2020}, and to capitalize on new behavioral opportunities such as
+transitioning to clean energy use and
 production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
 
-% Our model did not make any \emph{a priori} assumptions about whether it was
-% more costly for agents to be social or asocial learners, as some studies have
-% assumed or imposed~\cite{Rogers1988,Feldman1996,Morgan2012}. 
-% Instead, the uncertainty structure determined whether
-% or not social learning was beneficial or not, and evolution directed successive
-% generations towards the optimal strategy.
-
-Our model necessarily made some simplifying assumptions that, while
-empirically justified in many cases, may not always hold.
-\mt{Review the ones mentioned in model section: non-spatial, no within-generation
-environmental variability; no horizontal learning}.
-We only considered
-success-biased learning, although conformity is sometimes the dominant mechanism 
-for social influence of behavior well~\cite{Muthukrishna2016a,Smaldino2018b}. 
-Another implicit assumption
-in our model was that the number of behaviors was constant, as was the relationship
-between their payoffs---one was always optimal, and the rest were equally
-suboptimal. However, this fails to account for evolutionary feedback which creates
-new behavioral affordances as time progresses, e.g.\ via niche 
-construction~\cite{Smaldino2012,Heras-Escribano2020} or cumulative cultural
-evolution and dynamic network structure~\cite{Smolla2019,Derex2020}. 
-Adjusting any of these assumptions and running new computational analyses could
-yield further understanding of the evolution of social learning across diverse
-contexts.
-
-% As a final note, we believe 
-% our modeling approach may have applications to developing social artificial
-% intelligence, sepcifically multi-agent reinforcement learning
-% systems~\cite{Sandholm1996,Ndousse2021,Gronauer2022,Jaques2019}.
-% It seems to be implicitly assumed by current multi-agent reinforcement learning
-% algorithms that social learning
-% would always be beneficial. However, we have shown in our work that sometimes 
-% it is more efficient for autonomous social agents to solve problems without
-% reference to social information across a variety of uncertainty conditions. 
-% Our model agents are essentially software
-% robots, so our results should predict the benefit to real-world social robots
-% to either learn socially or asocially if the assumptions we make here are 
-% reasonably met or implemented in the social robot design.
-% Our model dynamics could thus be used as an
-% evolutionary algorithm to update AI agents' social learning strategy without
-% explicit knowledge of, or need to approximate, the underlying uncertainty structure.
-% A designer would need only to program the robots to go through evolutionary
-% cycles of simulated ``reproduction'' and ``death''.
-% Our model could also predict the expected benefit of social learning, which may be
-% inherently costly in artificial multi-agent learning systems due to extra
-% energy or time that may be required to transmit information between agents.
+Our modeling choices were judiciously made to address the main question of how
+uncertainty affects the evolution of social learning among populations of intelligent
+autonomous problem solvers.  Our model necessarily made simplifying assumptions that,
+while empirically justified across taxa, may not always hold in more
+specific situations. First, note that we only
+considered success-biased learning, although conformity is sometimes the dominant
+social learning mechanism~\cite{Muthukrishna2016a,Smaldino2018b}.
+Conformity may lead to more drift overall, since success-biased teacher selection, which
+we assumed, maximizes the potential benefit to social learners. We assumed that the
+number of behaviors and their payoffs were constant, but this fails to account for
+evolutionary feedback which creates new behavioral opportunities as time progresses, e.g.\
+via niche construction~\cite{Smaldino2012a,Heras-Escribano2020} or cumulative cultural
+evolution supported by dynamic network structure~\cite{Smolla2019,Derex2020}. 
+Group structure and processes such as homophily
+and outgroup aversion could inhibit the evolution of social learning since 
+successful outgroup teachers
+could be cut off from ingroup learners~\cite{Jackson2012}. Finally, our individual
+learning mechanism, softmax search, is underpowered compared to human individual learning; 
+more powerful individual learning could further support social learning, and
+this might be essential to accurate modeling of human behavior~\cite{Schulz2020a,Wu2022}.
+These considerations reveal new opportunities to further develop a more nuanced 
+theory of social learning by adjusting or extending the present model for other contexts.
 
@@
 
-We found that the evolution of social learning, under some modest
-assumptions, is a complex phenomenon, dependent on several interrelated factors. By systematically
-identifying common theoretical assumptions about uncertainty in the environments and contexts
-in which social learning evolves, we were able to develop a more systematic understanding of
-which uncertainty factors interact to determine whether social learning evolves. By
-explicitly modeling a key factor of human intelligence, namely the ability to sense and
-adjust to uncertainty and new information, we saw that social learning could be
-valuable even if social learning provides outdated information. This work
-informs most directly our current understanding of the evolution of social learning, but has
-broader significance for the behavioral science of problem solving in uncertain conditions, and
-for the design of artificial social intelligent systems in uncertain environments.  Our model
-and its software implementation were designed to be modular and extensible.  Indeed,
-we plan to extend this model to further develop a more detailed theoretical understanding of
-the evolution of social learning; perhaps others will, too.
+We found that the evolution of social learning, under a few modest assumptions, is a
+complex phenomenon, dependent on several interrelated factors. By systematically
+identifying and operationalizing common theoretical assumptions about contextual
+uncertainty in social learning models, we were able to develop a more systematic
+understanding of which uncertainty factors interact to determine whether social learning
+evolves. By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the
+ability to adjust behavior to uncertainty and new information, we saw that social
+learning could evolve even if social learning regularly provides outdated
+information. This work informs most directly our current understanding of the evolution of
+social learning, but has broader significance for understanding problem
+solving under uncertainty. Our model and its software implementation were
+designed to be modular and extensible.  Indeed, we plan to extend this model to further
+develop a more detailed theoretical understanding of the evolution of social learning;
+we hope others will, too.
 
@@
 
+\mt{TODO: Write supporting material explaining supplemental results}
+
 \subsection{Convergence information}
+
+\mt{These here used $N=100$; need to remake with $N=1000$}
 
@@
 
-\subsection{Softmax parameter sensitivity analysis} \vspace{-3em} \begin{figure} \centering
+\subsection{Full net payoff comparison for all nine uncertainty conditions}
+
+\begin{figure}
+  % \addtocounter{figure}{-1}
+  \caption{Comparison of expected payoffs from our computational anaysis (solid
+    lines with circles), expected individual payoffs with no social learning
+    (dashes without markers), and expected payoffs for all-social learner 
+    populations. When $\pilow = 0.8$, all-social learner populations underperform
+    since social learners are not subject to an initial evolutionary bottleneck
+    due to the presence of asocial learners, and behavioral misinformation
+    is allowed to circulate more freely than in the base case tested by 
+    our model with an initially even distribution of social and asocial learners.
+}
+  \label{fig:fullMeanPrevNetPayoffs}
+  \centering
+    \includegraphics[width=\textwidth]{Figures/supplement/fullMeanPrevNetPayoffs.pdf}
+\end{figure}
+
+\subsection{Softmax parameter sensitivity analysis}
+
+\mt{These here used $N=100$; need to remake with $N=1000$}
+
+\vspace{-3em} \begin{figure} %\addtocounter{figure}{-1} 
+  \centering
   \caption{Sensitivity analysis of the main results for the softmax parameter $\beta = 100$ and
@@
 	\begin{subfigure}{\textwidth}
+	  \caption{$N=100$}
+	  \includegraphics[width=\textwidth]{Figures/mainResultsPlots.pdf}
+	\end{subfigure}
+\end{figure}
+
+\begin{figure}
+  \ContinuedFloat
+	\begin{subfigure}{\textwidth}
 	  \caption{$N=200$}
@@
 
-\begin{figure}
-  \ContinuedFloat
-	\begin{subfigure}{\textwidth}
-	  \caption{$N=1000$}
-	  \includegraphics[width=\textwidth]{Figures/supplement/nagents=1000/mainResultsPlots.pdf}
-	\end{subfigure}
-\end{figure}
-
 \newpage
 \subsection{Number of prospective teachers sensitivty analysis}
+
+\mt{These here used $N=100$; need to remake with $N=1000$}
 

### 2022-08-01 ms.tex
Updates from Overleaf

--- 2022-07-29 ms.tex
@@
 %lifespan}.
-Individuals with shorter effective lifespans will end their lives with more
-uncertainty about which behaviors are optimal, and thereby transmit some of that
-uncertainty to anyone who learns from them. The effective lifespan for learning
+%Individuals with shorter effective lifespans will end their lives with more
+%uncertainty about which behaviors are optimal, and thereby transmit some of that
+%uncertainty to anyone who learns from them. 
+The effective lifespan for learning
 varies across tasks, individuals, and species, yet most models assume one learning
@@
 ~\cite{Enquist2007}, but little formal theory explicitly examines the role of
-uncertainty based on number of learning opportunities into our understanding of
-the evolution of social learning.
+learning opportunities in social learning evolution models.
 
@@
 observations to a probability distribution from which they strategically select
-their own behavior. \cm{does this still make sense? and does it need a citation?}
+their own behavior. \cm{does this still make sense? and does it need a citation?} \mt{makes sense, maybe this par could be merged with above into one?}
 

### 2022-08-01 ms.tex

--- 2022-08-01 ms.tex
@@
 %lifespan}.
-% Individuals with shorter effective lifespans will end their lives with more
-% uncertainty about which behaviors are optimal, and thereby transmit some of that
-% uncertainty to anyone who learns from them. 
 The effective lifespan for learning

### 2022-08-01 ms.tex
Updates from Overleaf

@@
 
-Many models of social learning assume little, or nothing, cognitive capabilities
+Many models of social learning assume little to no cognitive capabilities
 of their agents. For example, a common modelling strategy compare the payoffs of
@@
 payoffs at simulation end across agents and trials, normalized by lifespan; 
-and $\meanT / L$, or the mean
-number of time steps to fixation normalized by lifespan. We analyze outcomes by
+and $\meanG$, the mean
+number of generations to fixation. We analyze outcomes by
 plotting $\meansl$ on the y-axis and environmental variation is on x-axis since we
@@
 
-        $\meanT / L$ & Mean number of generations to convergence & 20k / 8 max. \\
+        $\meanG$ & Mean number of generations to convergence & 20k / 8 max. \\
         \bottomrule

### 2022-08-11 ms.tex
Updates from Overleaf

@@
   social learning in populations with cognitively realistic individual learning
-  capacities.  We used evolutionary agent-based modeling to track how often social
+  capacities.  We used evolutionary agent-based modeling to track how often social, rather than individual,
   learning evolved. Agents performed one of several behaviors to acquire payoffs.
@@
   social learning. Larger decision set sizes promoted social learning even
-  when environmental change was more likely than not. Payoff
+  when the environment changed frequently. Payoff
   ambiguity and lifespan had more complex effects on social learning, dependent on
@@
 
-Other (asocial) forms of learning may also be adaptations to uncertainty that could be
-accounted for, but are typically glossed over.  In general, learning is an iterative
+Other (asocial) forms of learning are also likely adaptations to uncertainty that should be
+accounted for, but are typically glossed over in models.  In general, learning is an iterative
 process by which one repeatedly acquires information, forms representations and
@@
 models are more often used to explain social learning mechanisms, they tend to use a
-single, weak individual-learning mechanism for comparison. Abstracting away asocial forms
-of learning may lead us to underestimate the extent to which individual learning provides
-quality information for social learning and for the individual to adapt to the challenges
+single, weak individual-learning mechanism for comparison. Such modelling choices may lead us to underestimate the extent to which individual learning provides
+quality information, both for asocially adapting to uncertainty and for social learners to take advantage of.
+%and for the individual to adapt to the challenges
 assumed to be solved by social learning. 
@@
 To address these concerns we developed an evolutionary agent-based model that
-simultaneously operationalizes several different forms of uncertainty and endows agents
-with a relatively powerful learning mechanism. We have chosen to model four kinds of
+simultaneously operationalizes several forms of uncertainty and endows agents
+with a relatively powerful learning mechanism. We model four kinds of
 uncertainty that are common in cultural evolution models and the related empirical
@@
 their lifespans whether they are social learners or not.
-We use this integrated model to ask what kinds of uncertainty are likely to
-favor social learning, and to clarify the logic of why this would be the case.
+We use this integrated model to ask which kinds of uncertainty are likely to
+favor social learning and to clarify the logic underlying the results.
+%of why this would be the case.
 
@@
 
-\textbf{Temporal environmental variability.} When external or internal shocks
-(e.g., climatic events, migration, technological paradigm shifts) occur,
+\textbf{Temporal environmental variability.} When environments change
+(e.g., climatic events, migration, technological paradigm shifts),
 strategies that were previously adaptive may no longer be optimal. The difficulty
-in predicting either when such shocks will occur or what behaviors will be
+in predicting either when such shocks will occur or which behaviors will be
 adaptive in the resulting environments leads to uncertainty.

### 2022-08-11 ms.tex
minor edits

--- 2022-08-01 ms.tex
@@
 the agent explores one of the nine alternative behaviors increases to 0.14.
-If the agent again tries behavior 1, the probability of exploring alternatives
+If the agent again tries behavior 1 and it pays 0, the probability of exploring alternatives
 with $B=2$ is 0.21, but with $B=10$ the probability of exploring alternatives
-greatly increases to 0.71. This explanation does not apply when $L=1$, where
-individual learning does not occur. %social learning is the only possible form of learning.
+greatly increases to 0.71. \mt{I double checked these calculations, but would appreciate if
+someone triple checked it}. This explanation does not apply when $L=1$, where
+individual learning does not occur.
 
@@
 
-Our modeling choices were judiciously made to address the main question of how
-uncertainty affects the evolution of social learning among populations of intelligent
-autonomous problem solvers.  Our model necessarily made simplifying assumptions that,
-while empirically justified across taxa, may not always hold in more
-specific situations. First, note that we only
-considered success-biased learning, although conformity is sometimes the dominant
-social learning mechanism~\cite{Muthukrishna2016a,Smaldino2018b}.
-Conformity may lead to more drift overall, since success-biased teacher selection, which
-we assumed, maximizes the potential benefit to social learners. We assumed that the
-number of behaviors and their payoffs were constant, but this fails to account for
-evolutionary feedback which creates new behavioral opportunities as time progresses, e.g.\
-via niche construction~\cite{Smaldino2012a,Heras-Escribano2020} or cumulative cultural
-evolution supported by dynamic network structure~\cite{Smolla2019,Derex2020}. 
-Group structure and processes such as homophily
-and outgroup aversion could inhibit the evolution of social learning since 
-successful outgroup teachers
-could be cut off from ingroup learners~\cite{Jackson2012}. Finally, our individual
-learning mechanism, softmax search, is underpowered compared to human individual learning; 
-more powerful individual learning could further support social learning, and
-this might be essential to accurate modeling of human behavior~\cite{Schulz2020a,Wu2022}.
-These considerations reveal new opportunities to further develop a more nuanced 
-theory of social learning by adjusting or extending the present model for other contexts.
+Our modeling choices were judiciously made to address the main question of how uncertainty
+affects the evolution of social learning in general; however there exist alternative
+empirically-valid choices that could help further develop a more nuanced theory of social
+learning.  Our model necessarily made simplifying assumptions that may not always hold in more
+specific situations, though they are empirically justified to be general across taxa. First,
+note that we only considered success-biased learning, although conformity is sometimes the
+dominant social learning mechanism~\cite{Muthukrishna2016a,Smaldino2018b}.  Conformity may lead
+to more drift overall, since success-biased teacher selection, which we assumed, maximizes the
+potential benefit to social learners. We assumed that the number of behaviors and their payoffs
+were constant, but this fails to account for evolutionary feedback which creates new behavioral
+opportunities as time progresses, e.g.\ via niche
+construction~\cite{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
+supported by dynamic network structure~\cite{Smolla2019,Derex2020}.  Group structure and
+processes such as homophily and in-group bias/out-group aversion could inhibit the evolution of
+social learning since successful outgroup teachers could be cut off from in-group
+learners~\cite{Jackson2012}. We assumed agents choose behaviors via softmax search, but this is
+an underpowered algorithm compared to human individual learning~\cite{Schulz2020a,Wu2022}.
+More powerful individual learning could further support social learning.  These considerations
+reveal new opportunities to further by adjusting or extending the present model for other
+contexts.
 

### 2022-08-11 ms.tex
updated all sensitivity analyses with N=1000
Updates from Overleaf

@@
 naturalistic tasks~\cite{derex2013, wasielewski2014}, but these map on
-imperfectly to the theoretical literature \mt{How so?}. Some models have studied systems with
+imperfectly to the theoretical literature that tend to use a limited set of behavioral options.
+%\mt{How so?}. 
+Some models have studied systems with
 larger, but defined, selection sets~\cite{Rendell2010}, while in others the
-number of options is implicit in the model payoff structure
-~\cite{Enquist2007} \mt{How does this work exactly in Enquist et al 2007?}. 
+number of options is implicit in the probability that a learner gets the right answer.
+~\cite{Enquist2007} 
+%\mt{How does this work exactly in Enquist et al 2007?}. 
 Researchers have also compared models with a different number

### 2022-08-13 ms.tex
outlined softmax supplement

--- 2022-08-11 ms.tex
@@
     five additional plots.
-clarity.} 
+} 
   \label{fig:payoffs}
@@
 
-\mt{These here used $N=100$; need to remake with $N=1000$}
+\begin{itemize}
+  \item 
+    We tested two additional settings of the softmax behavior selection
+    greediness parameter, $\beta=0.01,1.0$, which reproduced qualitative patterns in
+    the evolution of social learning. 
+  \item
+    We see that certain details are changed within this broad agreement between
+    results obtained with different $\beta$. 
+    \begin{enumerate}
+      \item 
+        More drift when $\beta=1$, which can be seen in certain $(\pilow, B)$ pairs
+        (entries in plot matrices in Figure~\ref{fig:softmaxSensitivity}b). 
+        For example, when $\pilow = 0.1$ and $B=10$, there are a few more 
+        data points with greater drift, i.e., where $\meansl \approx 0.5$. 
+    \end{enumerate}
+\end{itemize}
 

### 2022-08-13 ms.tex
added stubs for sensitivity and did minor revisions

--- 2022-08-11 ms.tex
@@
 to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
-Such individual-level intelligence is a critical adaptation that has apparently
-co-evolved with the capacity for social learning, and has a marked influence on the
-cultural evolution of social learning as we will demonstrate in our Analysis.
-We will see that individual-level intelligence allows agents to recover from
-the receipt of outdated information due to temporal environmental variability.
+Such individual-level intelligence is a critical adaptation that has 
+co-evolved with the capacity for social learning, and we will show this has a marked influence 
+on the cultural evolution of social learning.
 
@@
 This sets up an inter-generational structure
-that we also use as a scaffold for social learning: we assume social learning occurs
-\emph{obliquely}, meaning learning happens when a new
-generation of agents each select a teacher from the previous generation, possibly
-including their parents.  
-Evolution, then, acts as an optimization routine to identify which heritable trait
-values are most rewarded under in different environmental uncertainty contexts,
-defined by different uncertainty parameter settings
-(Table~\ref{tab:uncertaintyParameters}).
-
-Agents have one heritable trait in this model, whether or not
-an agent, $i$, learns socially, denoted $s_i$. $s_i$ is binary: it is 1
-if the agent is a social learner, and 0 otherwise. In our analysis, we 
-aggregate $s_i$ over all agents and simulation trials to understand the affects of
+that we also use as a scaffold for \emph{oblique} social learning, meaning children
+with the social learning trait learn about payoffs from a member of the
+previous generation. Evolution acts as an optimization routine to identify
+whether individuals with the social learning trait will outperform those without.
+
+Agents inherit one trait in this model, whether or not
+an agent, $i$, learns socially. If $i$ has the trait we write $s_i=1$
+ and 0 otherwise. In our analysis, we 
+average $s_i$ over all agents and simulation trials to understand the affects of
 different uncertainty parameter settings. 
@@
 We performed sensitivity analyses to ensure that our main analysis is reasonably
-robust to a range of auxiliary parameters. Specifically,
+robust to a range of auxiliary parameters. First,
 we varied the population size, $N$, to explore whether smaller $N$ would 
@@
 \subsubsection{Implementation}
+
 Our model was implemented in the Julia programming language~\cite{Bezanson2017} 
@@
 Increased selection set size $B$ led nearly uniformly to more prevalent social
-learning, with all other uncertainty parameters held constant. This is first 
-because it is more difficuilt to find the optimal behavior with a larger $B$.
+learning, with all other uncertainty parameters held constant. This is because,
+first, it is more difficuilt to find the optimal behavior with a larger $B$.
 % more options present a more difficult problem for trial-and-error learning within
 % a lifespan. 
-This effect is amplified because agents in a world with larger $B$ are more
+Second, this effect is amplified because agents in a world with larger $B$ are more
 cognitively flexible compared to those in a smaller $B$ world. 
@@
 
-\mt{These here used $N=100$; need to remake with $N=1000$}
-
 \begin{table}[h] \caption{Max. iterations = 20000.} \label{tab:convergence} \centering
-  \begin{tabular}{cccc} \toprule $B$ & \# not at fixation & \# total series & Pct. not fixated
-    \\ \midrule  2  & 0  & 132000 & 0.0 \% \\ 4  & 0  & 132000 & 0.0 \% \\ 10 & 44 & 132000 &
-    0.00033  \% \\ \bottomrule \end{tabular} \end{table}
+  \begin{tabular}{cccc} 
+    \toprule $B$ & \# not at fixation (out of 132k) & \% not fixated \\ 
+    \midrule  2  & 192  & 0.1 \% \\ 
+              4  & 274  & 0.2 \% \\ 
+              10 & 2935 & 2.0 \% \\ 
+    \bottomrule \end{tabular} 
+\end{table}
 
@@
 \begin{figure}
-  % \addtocounter{figure}{-1}
   \caption{Comparison of expected payoffs from our computational anaysis (solid
@@
 
-\mt{These here used $N=100$; need to remake with $N=1000$}
+We tested two additional settings of the softmax behavior selection greediness parameter,
+$\beta=1,100$, which reproduced qualitative patterns in the evolution of social learning. In
+the main text we used $\beta=10$.  Softmax greediness is achieved formally by increasing the
+probability mass for selecting behaviors that have paid off more frequently over that agent's
+life history. In other words, greater $\beta$ increases the probabilty that the optimal
+observed behavior is chosen over all the rest. If $\beta$ is too small, agents will fail to
+fully exploit their knowledge about which behavior is optimal because they too frequently
+explore less profitable alternatives.  If $\beta$ is too great the agents could more regularly
+settle on a sub-optimal behavior because it paid off first.  In a fuller evolutionary
+exploration of model parameters it would make sense for $\beta$ to co-evolve with the social
+learner trait.  However, our sensitivity analysis demonstrates that our main conclusions of how
+social learning evolves under uncertainty remain unchanged for different $\beta$ over three
+orders of magnitude.
+
+When $\beta=1$, most general trends are preserved, but in many cases the evolution
+of social learning is suppressed or drift dominates due to 
+due to the overall poor quality of information acquired through softmax search-based
+individual learning.
+
+When $\beta=100$, there
+
+Other smaller details can also be observed between tested $\beta$. 
+First, there is generally more drift when $\beta=1$, 
+which can be seen in certain $(\pilow, B)$ pairs
+(entries in plot matrices in Figure~\ref{fig:softmaxSensitivity}a). 
+For example, when $\pilow = 0.1$ and $B=10$, there are a few more 
+data points with greater drift, i.e., where $\meansl \approx 0.5$. 
+The variation in our results when we set $\beta=100$
+(Figure~\ref{fig:softmaxSensitivity}b), changed from the
+main text where $\beta=10$, are more varied and subtle compared
+to setting $\beta=1$. In some cases, such as $(\pilow=0.1, B=10)$ 
+and $(\pilow=0.45, B=2)$,
+there appears to be more drift across all $L$ around the transition
+point when $\meansl = 1$ goes to 0 as $u$ increases. However it appears
+that there is more drift at the transition for $\beta=10$ for
+$(\pilow=0.45, B=10)$.
 
@@
   \begin{subfigure}{\textwidth}
-	\caption{$\beta = 100$}
-	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
+	\caption{$\beta = 1$}
+	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
   \end{subfigure}
@@
   \begin{subfigure}{\textwidth}
-	\caption{$\beta = 1$}
-	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
+	\caption{$\beta = 100$}
+	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
   \end{subfigure}
@@
 \newpage
+
 \subsection{Population size sensitivty analysis}
+
+Drift is greater for smaller populations sizes, especially when
+$\pilow=0.8$, but patterns generally remain.
 
@@
   \centering
+  \addtocounter{figure}{-1}
   \caption{
@@
 
-\mt{These here used $N=100$; need to remake with $N=1000$}
+Slightly more drift when $N_T = 2$, slightly less drift when $N_T = 20$, 
+but mostly just reproduces results for main text setting $N_T = 5$.
 
@@
   \centering
+  \addtocounter{figure}{-1}
   \caption{Number of prospective teachers sensitivity analysis for $N_T=2,10,20$. Recall

### 2022-08-13 ms.tex
minor revision to analysis

--- 2022-08-13 ms.tex
@@
 
-First, we confirmed the current theoretical understanding that greater $u$ uniformly decreased
-$\meansl$ across all other uncertainty parameter values. The other uncertainty
-parameters changed the $u$ value at which $\meansl$ began to decrease,
-and how rapidly $\meansl$ decreased over $u$. 
-For example, when payoff ambiguity and selection set size were
-both small ($\pilow = 0.1$ and $B=2$), social learning evolved only when $u$ was
-small. 
+First, we confirmed existing theoretical predictions that greater $u$
+uniformly decreased $\meansl$ across all other uncertainty parameter values.
+The other uncertainty parameters changed the $u$ value at which $\meansl$
+began to decrease, and how rapidly $\meansl$ decreased over $u$.  For example,
+when payoff ambiguity and selection set size were both small ($\pilow = 0.1$
+and $B=2$), social learning evolved only when $u$ was small. 
 % These parameter settings present a relatively easy problem for individuals.
-% Furthermore, it is relatively costly for agents to be misled by outdated social 
-% information in this case, especially for longer lifespans for finding the 
-% optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
-When $\pilow = 0.8$ and $B=2$, for exapmle, $\meansl$ decreased less rapdily over $u$ due to 
-drift caused by weak selection caused by little advantage for performing the optimal versus
-non-optimal behavior (see rows of Figure~\ref{fig:mainResults}). We analyzed several
-such patterns of social learning evolution and suppression across different uncertainty settings.
+% Furthermore, it is relatively costly for agents to be misled by outdated
+% social information in this case, especially for longer lifespans for finding
+% the optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
+When $\pilow = 0.8$ and $B=2$, for exapmle, $\meansl$ decreased less rapdily
+over $u$ due to drift caused by weak selection caused by little advantage for
+performing the optimal versus non-optimal behavior (see rows of
+Figure~\ref{fig:mainResults}). We analyzed several such patterns of social
+learning evolution and suppression across different uncertainty settings.
 
@@
 
-\begin{itemize}
-  \item 
-    We tested two additional settings of the softmax behavior selection
-    greediness parameter, $\beta=0.01,1.0$, which reproduced qualitative patterns in
-    the evolution of social learning. 
-  \item
-    We see that certain details are changed within this broad agreement between
-    results obtained with different $\beta$. 
-    \begin{enumerate}
-      \item 
-        More drift when $\beta=1$, which can be seen in certain $(\pilow, B)$ pairs
-        (entries in plot matrices in Figure~\ref{fig:softmaxSensitivity}b). 
-        For example, when $\pilow = 0.1$ and $B=10$, there are a few more 
-        data points with greater drift, i.e., where $\meansl \approx 0.5$. 
-    \end{enumerate}
-\end{itemize}
+\mt{These here used $N=100$; need to remake with $N=1000$}
 

### 2022-08-13 ms.tex
revise, extend, restructure supplement

--- 2022-08-13 ms.tex
@@
 
-By disambiguating and organizing various operationalizations of
-uncertainty, we developed a more nuanced theoretical understanding of which forms of
-uncertainty interact to affect social learning.  We reviewed and distilled the several empirical and
-theoretical models in the literature along four uncertainty dimensions: temporal
-environmental uncertainty, selection set size, ambiguous payoffs, and effective lifespan.
-The model reproduced classic predictions that social learning can yield higher payoffs
-than individual learning when uncertainty is sufficiently limited. Our model also
-demonstrated a new insight into social learning as a scaffold for individual learning,
-enabled by endowing agents with an evolutionarily- and biologically-plausible individual
-learning mechanism, softmax search. Specifically, we found that agents could recover from
-receiving outdated information, so social learning could evolve even though social
-information was outdated more often than not. We found increased payoff ambiguity and
-lifespan led to greater drift, which is essentially evolutionary uncertainty in a
-finite-size population. Detailed theoretical models and
-predictions of cultural evolution under uncertainty are critical for understanding how
-humans adapt to an uncertain and rapidly changing world, both to mitigate existential
-threats~\cite{Moya2020,Jones2021}, especially in the most vulnerable
-communities~\cite{McNamara2020}, and to capitalize on new behavioral opportunities such as
-transitioning to clean energy use and
+By disambiguating and organizing various operationalizations of uncertainty
+into a single computational model, we developed a more nuanced theoretical
+understanding of how different forms of uncertainty interact to affect the
+evolution of social learning.  We reviewed and distilled several empirical
+and theoretical models in the literature along four uncertainty dimensions:
+temporal environmental uncertainty, selection set size, ambiguous payoffs, and
+effective lifespan.  The model reproduced classic predictions that social
+learning can yield higher payoffs than individual learning when uncertainty is
+sufficiently limited. Our model also demonstrated a new insight into social
+learning as a scaffold for individual learning, enabled by endowing agents
+with an evolutionarily- and biologically-plausible individual learning
+mechanism, softmax search. Specifically, we found that agents could recover
+from receiving outdated information, so social learning could evolve even
+though social information was outdated more often than not. We found increased
+payoff ambiguity and lifespan led to greater drift, which is essentially
+evolutionary uncertainty in a finite-size population. Detailed theoretical
+models and predictions of cultural evolution under uncertainty are critical
+for understanding how humans adapt to an uncertain and rapidly changing world,
+both to mitigate existential threats~\cite{Moya2020,Jones2021}, especially in
+the most vulnerable communities~\cite{McNamara2020}, and to capitalize on new
+behavioral opportunities such as transitioning to clean energy use and
 production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
@@
 
-\section{Appendix}
-
-\mt{TODO: Write supporting material explaining supplemental results}
-
-\subsection{Convergence information}
-
-\begin{table}[h] \caption{Max. iterations = 20000.} \label{tab:convergence} \centering
-  \begin{tabular}{cccc} 
-    \toprule $B$ & \# not at fixation (out of 132k) & \% not fixated \\ 
-    \midrule  2  & 192  & 0.1 \% \\ 
-              4  & 274  & 0.2 \% \\ 
-              10 & 2935 & 2.0 \% \\ 
-    \bottomrule \end{tabular} 
-\end{table}
-
-\newpage
-
-\subsection{Full net payoff comparison for all nine uncertainty conditions}
+\section{Additional main figure: Full net payoff comparison for all nine uncertainty conditions}
+
+In the main text we showed a $2\times2$ array of plots comparing the observed
+mean net payoffs obtained by agents in our simulations, and in two auxiliary
+sets of simulations that set all agents to either have the social learning
+trait or not, which remained the case for the entire simulation since there
+are no mutations in this model (Figure~\ref{fig:payoffs}). Here we show the full $3\times3$ array of
+all $(\pilow, B)$ combinations shown for the main results. We see that
+populations of all social learners especially underperform initially mixed
+populations that evolve to be social learners 
+(Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row). This highlights the
+importance of diversity for behavioral optimization, even if it is transient.
 
@@
 
-\subsection{Softmax parameter sensitivity analysis}
-
-We tested two additional settings of the softmax behavior selection greediness parameter,
-$\beta=1,100$, which reproduced qualitative patterns in the evolution of social learning. In
-the main text we used $\beta=10$.  Softmax greediness is achieved formally by increasing the
-probability mass for selecting behaviors that have paid off more frequently over that agent's
-life history. In other words, greater $\beta$ increases the probabilty that the optimal
-observed behavior is chosen over all the rest. If $\beta$ is too small, agents will fail to
-fully exploit their knowledge about which behavior is optimal because they too frequently
-explore less profitable alternatives.  If $\beta$ is too great the agents could more regularly
-settle on a sub-optimal behavior because it paid off first.  In a fuller evolutionary
-exploration of model parameters it would make sense for $\beta$ to co-evolve with the social
-learner trait.  However, our sensitivity analysis demonstrates that our main conclusions of how
-social learning evolves under uncertainty remain unchanged for different $\beta$ over three
-orders of magnitude.
-
-When $\beta=1$, most general trends are preserved, but in many cases the evolution
-of social learning is suppressed or drift dominates due to 
-due to the overall poor quality of information acquired through softmax search-based
-individual learning.
-
-When $\beta=100$, there
-
-Other smaller details can also be observed between tested $\beta$. 
-First, there is generally more drift when $\beta=1$, 
-which can be seen in certain $(\pilow, B)$ pairs
-(entries in plot matrices in Figure~\ref{fig:softmaxSensitivity}a). 
-For example, when $\pilow = 0.1$ and $B=10$, there are a few more 
-data points with greater drift, i.e., where $\meansl \approx 0.5$. 
-The variation in our results when we set $\beta=100$
-(Figure~\ref{fig:softmaxSensitivity}b), changed from the
-main text where $\beta=10$, are more varied and subtle compared
-to setting $\beta=1$. In some cases, such as $(\pilow=0.1, B=10)$ 
-and $(\pilow=0.45, B=2)$,
-there appears to be more drift across all $L$ around the transition
-point when $\meansl = 1$ goes to 0 as $u$ increases. However it appears
-that there is more drift at the transition for $\beta=10$ for
-$(\pilow=0.45, B=10)$.
-
-\vspace{-3em} \begin{figure} %\addtocounter{figure}{-1} 
-  \centering
-  \caption{Sensitivity analysis of the main results for the softmax parameter $\beta = 100$ and
-  $\beta=1$. Recall the main results were obtained with $\beta = 10$.}
-  \label{fig:softmaxSensitivity} \vspace{2em}
-  \begin{subfigure}{\textwidth}
-	\caption{$\beta = 1$}
-	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
-  \end{subfigure}
-\end{figure}
 \newpage
-\begin{figure}
-  \ContinuedFloat
-  \begin{subfigure}{\textwidth}
-	\caption{$\beta = 100$}
-	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
-  \end{subfigure}
-\end{figure}
+
+\section{Supplemental supporting information}
+
+In this Supplement we support our model conclusions with auxiliary data
+showing, first, sufficient model convergence and, second, that our model
+outcomes are stable over various settings of the three free auxiliary model
+parameters: the number of agents ($N$), the number of
+prospective teachers pooled by social learner children for social learning
+($N_T$), and the softmax behavior selection greediness parameter ($\beta$).
+The main source of minor deviations from the main results was greater drift
+due to (1) finite population size effects, with greater drift for smaller $N$;
+(2) lower quality of socially-learned information agents can access with fewer
+prospective teachers; and (3) lower quality social information when $\beta$
+was small since teacher agents would have explored non-optimal behaviors more
+frequently, so their observed payoffs would have less probability weight in
+the optimal payoffs on average. We give details below of model convergence, and
+outcomes as we varied the three auxiliary parameters $N$, $N_T$, and $\beta$.
+
+\subsection{Convergence information}
+
+Model populations reached fixation between few to 140 generations on
+average (Figure~\ref{fig:steps}).
+Note 140 generations is equivalent to 2800 time steps. We set the maximum 
+number of iterations globally to $20~000$, which is 1000 generations when
+$L=20$. Although we can be relatively sure that this maximum number of 
+generations is rarely reached based on our main text analysis of $\meanG$,
+we additionally tabulated the number of simulations that did not converge to
+fixation
+within this step limit. We found that 0.1\% of simulations did not converge
+when $B=2$, 0.2\% did not converge when $B=4$, and 2.0\% did not converge
+when $B=10$ (Table~\ref{tab:convergence}). When a trial did not converge we
+still included that trial's $\meansl$ value in the average across trials,
+but for these $0 < \meansl < 1$.
+
+\begin{table}[h] \caption{Maximum number of iterations = 20000.} \label{tab:convergence} \centering
+  \begin{tabular}{cccc} 
+    \toprule $B$ & \# not at fixation (out of 132k) & \% not fixated \\ 
+    \midrule  2  & 192  & 0.1 \% \\ 
+              4  & 274  & 0.2 \% \\ 
+              10 & 2935 & 2.0 \% \\ 
+    \bottomrule \end{tabular} 
+\end{table}
 
@@
 
+\subsection{Softmax parameter sensitivity analysis}
+
+We tested two additional settings of the softmax behavior selection greediness parameter,
+$\beta=1,100$, which reproduced qualitative patterns in the evolution of social learning. In
+the main text we used $\beta=10$.  Softmax greediness is achieved formally by increasing the
+probability mass for selecting behaviors that have paid off more frequently over that agent's
+life history. In other words, greater $\beta$ increases the probabilty that the optimal
+observed behavior is chosen over all the rest. If $\beta$ is too small, agents will fail to
+fully exploit their knowledge about which behavior is optimal because they too frequently
+explore less profitable alternatives.  If $\beta$ is too great the agents could more regularly
+settle on a sub-optimal behavior because it paid off first.  In a fuller evolutionary
+exploration of model parameters it would make sense for $\beta$ to co-evolve with the social
+learner trait.  However, our sensitivity analysis demonstrates that our main conclusions of how
+social learning evolves under uncertainty remain unchanged for different $\beta$ over three
+orders of magnitude.
+
+When $\beta=1$, most general trends are preserved, but in many cases the evolution
+of social learning is suppressed or drift dominates due to 
+due to the overall poor quality of information acquired through softmax search-based
+individual learning.
+
+When $\beta=100$, there
+
+Other smaller details can also be observed between tested $\beta$. 
+First, there is generally more drift when $\beta=1$, 
+which can be seen in certain $(\pilow, B)$ pairs
+(entries in plot matrices in Figure~\ref{fig:softmaxSensitivity}a). 
+For example, when $\pilow = 0.1$ and $B=10$, there are a few more 
+data points with greater drift, i.e., where $\meansl \approx 0.5$. 
+The variation in our results when we set $\beta=100$
+(Figure~\ref{fig:softmaxSensitivity}b), changed from the
+main text where $\beta=10$, are more varied and subtle compared
+to setting $\beta=1$. In some cases, such as $(\pilow=0.1, B=10)$ 
+and $(\pilow=0.45, B=2)$,
+there appears to be more drift across all $L$ around the transition
+point when $\meansl = 1$ goes to 0 as $u$ increases. However it appears
+that there is more drift at the transition for $\beta=10$ for
+$(\pilow=0.45, B=10)$.
+
+\vspace{-3em} \begin{figure} %\addtocounter{figure}{-1} 
+  \centering
+  \caption{Sensitivity analysis of the main results for the softmax parameter $\beta = 100$ and
+  $\beta=1$. Recall the main results were obtained with $\beta = 10$.}
+  \label{fig:softmaxSensitivity} \vspace{2em}
+  \begin{subfigure}{\textwidth}
+	\caption{$\beta = 1$}
+	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+\newpage
+\begin{figure}
+  \ContinuedFloat
+  \begin{subfigure}{\textwidth}
+	\caption{$\beta = 100$}
+	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}
+  \end{subfigure}
+\end{figure}
+
 \end{document}

### 2022-08-13 ms.tex
finished revisions with N=1000 and full supplement

@@
 \usepackage{comment}
+
+\usepackage{xcolor}
+% \renewcommand{\linenumberfont}{\small\color{gray}}
 
@@
 Many models of social learning assume little to no cognitive capabilities
-of their agents. For example, a common modelling strategy compare the payoffs of
+of their agents. For example, a common modelling strategy compares the payoffs of
 agents with different pure learning strategies (some will always engage in social
 learning, and others in individual learning) while revealing nothing about the
-cognition underlying individuals' decisions  ~\cite{BoydRicherson1985, Rogers1988,
+cognition underlying individuals' decisions~\cite{BoydRicherson1985, Rogers1988,
 aoki2005}. Some more complicated learning strategies that make use of both
@@
 Kendal2018}, given such details may be theoretically meaningful. In order to
-understand how social learning evolves as an adaptation to uncertainty, we need to
-endow agents with a biologically plausible cognition capable of integrating
-information from various sources in a payoff-maximizing way~\cite{Gershman2019}. 
+understand how social learning evolves as an adaptation to uncertainty, we 
+endowed agents with a biologically plausible cognition capable of integrating
+information from various sources to maximize payoffs, \emph{softmax
+search}~\cite{Gershman2019}, described in more detail below. 
 % \cm{I don't
@@
 % our cognitive model is only sensitive to total randomness.} 
-To do so, we let
-agents see the payoffs to behaviors and use the softmax function to convert these
-observations to a probability distribution from which they strategically select
-their own behavior. %\cm{does this still make sense? and does it need a citation?}
+% To do so, we let
+% agents see the payoffs to behaviors and use the softmax function to convert these
+% observations to a probability distribution from which they strategically select
+% their own behavior. %\cm{does this still make sense? and does it need a citation?}
 
@@
 social learning evolution.  Evolutionary agent-based models simulate changes in
-prevalence of a phenotype over several generations---in this model the phenotype
-is whether or not an agent engages in social learning.  In the model, a
+the prevalence of a phenotype over several generations---in this model the phenotype
+is whether or not an agent engages in social learning.  In our model, a
 population of $N$ individuals each must decide which of $B$ behaviors to perform at
@@
 knowledge of the world.  Each behavior is a ``bandit'', a common modeling and
-experimental approach for representing behaviors with Bernoulli-distributed
+experimental approach for representing behaviors with random-valued
 payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
-All bandits thus yield a payoff of 1 or 0 with a certain probability.  One of the
+Bandits in our model yield Bernoulli payoffs of 1 or 0 with some probability,
+with that probability defining each behavior's expected payoffs.  One of the
 bandits/behaviors in the model is more likely to pay off than all the rest.  Agents
@@
 behavior is optimal and performing it as often as possible within their lifespan.
+The optimal behavior is static within agent lifespans, but varies in general between
+generations, representing environmental variability.
 
@@
 Environmental variability is the probability that the optimal behavior changes
-between generations. We do not consider within-generation variability. 
-Furthermore, our model is not spatial, so agents have free, instant
-access to all behaviors, and there is no spatial uncertainty. 
-These conditions reflect humans in a computer-based social learning evolution
-experiment~\cite{McElreath2005,Morgan2012,Derex2016}. Spatial dimensions could also be
-considered irrelevant if costs associated with accessing a behavior were equal,
-e.g., if it was assumed to be equally costly for animals to
-visit alternative food sources~\cite{Aplin2017,Baracchi2018}.  
+between generations.   
 % This is empirically justified since cultural evolution
@@
 number of time steps in which agents perform behaviors within a generation. 
+Our model is not spatial, so agents have free, instant
+access to all behaviors, and there is no spatial uncertainty. 
+These conditions reflect humans in a computer-based social learning evolution
+experiment~\cite{McElreath2005,Morgan2012,Derex2016}. Spatial dimensions could also be
+considered irrelevant if costs associated with accessing a behavior were equal,
+e.g., if it was assumed to be equally costly for animals to
+visit alternative food sources~\cite{Aplin2017,Baracchi2018}.
 Each simulated environment provides a distinct challenge
@@
 Such individual-level intelligence is a critical adaptation that has 
-co-evolved with the capacity for social learning, and we will show this has a marked influence 
-on the cultural evolution of social learning.
-
-In \emph{evolutionary} agent-based models like ours, agent life cycles are
+co-evolved with the capacity for social learning. We will show that individual
+learning can support the evolution of social learning.
+
+In our \emph{evolutionary} agent-based model, agent life cycles are
 programmed to cause agents to reproduce and die off, where reproducers pass on
@@
 loss of the potential to socially influence others. 
-This sets up an inter-generational structure
+This sets up an inter-generational cultural structure
 that we also use as a scaffold for \emph{oblique} social learning, meaning children
@@
 different uncertainty parameter settings. 
-Our computational analysis amounts to observing patterns in
-the aggregated $s_i$, supported by measuring the number of generations 
-to model convergence and expected payoffs. 
+Our computational analysis is based on observing and comparing patterns in
+aggregated $s_i$ across different parameter settings, 
+supported by measuring the number of generations 
+to model convergence and expected payoffs in populations across the same contexts. 
 To understand how different varieties of uncertainty interact
 to affect the evolution of social learning, we systematically created an array of
-simulated environments by systematically varying the uncertainty parameters.
+simulated environments by systematically varying the uncertainty parameters, and
+auxiliary model parameters to ensure model validity.
 
@@
 our main conclusions. Next, we varied the
+number of prospective teachers, $N_T \in \{2, 10, 20\}$, 
+to supplement the main results that used $N_T = 5$. The number of prospective
+teachers should not change whether social learning is optimal, 
+but it may induce more drift since the benefit of social learning may
+be more difficult to detect with fewer prosopective teachers. Finally, we varied the
 softmax greediness parameter $\beta \in \{1, 100\}$ to supplement the main results
@@
 by undermining individual learning. Nonetheless, our results
-should be valid over some range of $\beta$. Finally, we varied the
-number of prospective teachers $N_T \in \{2, 10, 20\}$ 
-to supplement the main results that used $N_T = 5$. The number of prospective
-teachers should not change whether social learning is optimal, 
-but it may induce more drift since the benefit of social learning may
-be more difficult to detect with fewer prosopective teachers.
+should be valid over some range of $\beta$.
 
@@
 uncertainty parameters. We analyzed outcomes by plotting the mean observed social
-learning frequency, $\meansl$, with mean taken across all agents and 1000 simulation trials for each
-uncertainty parameter setting.   
+learning frequency, $\meansl$, with mean taken across all 1000 agents and 1000
+simulation trials for each uncertainty parameter setting at model fixation.
 % This is convenient because we are most certain about how $\meansl$ depends on $u$:
@@
 % To inspect patterns in $\meansl$ over all uncertainty parameters, 
-We analyze nine plots of how $\meansl$ (y-axis in each plot) changes over $u$ (x-axis) 
+We analyze nine plots of how $\meansl$ (y-axis in each plot) changes over 
+environmental variability, $u$ (x-axis),
 in a $3\times3$ plot array (Figure~\ref{fig:mainResults}). 
@@
 % with environmental variability, $u$ (x-axis). 
-Selection set size, $B$ increases from left to right in the plot array (columns). 
-Payoff ambiguity increases as $\pilow$ increases from top to bottom in the array 
-(recall $\pihigh=0.9$ for all analyses).
+Selection set size, $B$, increases from left to right in the plot array (columns). 
+Payoff ambiguity increases as the non-optimal payoff, $\pilow$, increases from 
+top to bottom in the array (recall $\pihigh=0.9$ for all analyses).
 Effective lifespan, $L$, is indicated by line and marker colors (inset). 
@@
 these uncertainty parameters were varied (Figure~\ref{fig:mainResults}).
-% We support our conclusions regarding the evolution of social learning by analyzing
-% the time to fixation and by comparing the average net payoffs in our simulations
-% to the expected payoffs for individuals in both populations of all social learners
-% and in populations of all individual learners. We thus use our analysis to
-% understand changes to how $\meansl$ changes over $u$ for different uncertainty
-% parameter settings.
-
-First, we confirmed existing theoretical predictions that greater $u$
-uniformly decreased $\meansl$ across all other uncertainty parameter values.
+
+First, we confirmed existing theoretical predictions that increased $u$
+monotonically decreased $\meansl$ across all other uncertainty parameter values.
 The other uncertainty parameters changed the $u$ value at which $\meansl$
@@
 When $\pilow = 0.8$ and $B=2$, for exapmle, $\meansl$ decreased less rapdily
-over $u$ due to drift caused by weak selection caused by little advantage for
+over $u$ due to drift caused by weak selection due to little advantage for
 performing the optimal versus non-optimal behavior (see rows of
@@
 Increased selection set size $B$ led nearly uniformly to more prevalent social
-learning, with all other uncertainty parameters held constant. This is because,
-first, it is more difficuilt to find the optimal behavior with a larger $B$.
-% more options present a more difficult problem for trial-and-error learning within
-% a lifespan. 
-Second, this effect is amplified because agents in a world with larger $B$ are more
-cognitively flexible compared to those in a smaller $B$ world. 
-When $B$ is larger, agents are relatively more likely to choose an alternative to
-their current known optimum. %is easier to correct for larger $B$ relative to smaller $B$.  
-To understand this, consider the case where a social learner child learns
-that behavior 1 has an expected payoff of 0.8, and the rest have an expected
-payoff of 0, but the optimal behavior changed between generations. Assume
-the child tries behavior 1, but it pays off 0.
-If $B=2$, then at the next within-generation time step, $\ledger = (0.4, 0.0)$. The probability
-the agent explores behavior 2 is now 0.02. However, if $B=10$ the agent has
-$\ledger = (0.4, 0.0, \ldots, 0.0)$; the probability
-the agent explores one of the nine alternative behaviors increases to 0.14.
-If the agent again tries behavior 1 and it pays 0, the probability of exploring alternatives
-with $B=2$ is 0.21, but with $B=10$ the probability of exploring alternatives
-greatly increases to 0.71. \mt{I double checked these calculations, but would appreciate if
-someone triple checked it}. This explanation does not apply when $L=1$, where
-individual learning does not occur.
+learning, with all other uncertainty parameters held constant. This is because, first,
+it is more difficuilt to find the optimal behavior with a larger $B$.  Second, this
+effect is amplified because agents in a world with larger $B$ are more cognitively
+flexible compared to those in a smaller $B$ world.  When $B$ is larger, agents are
+relatively more likely to choose an alternative to their current known optimum.  To
+understand this, consider the case where a social learner child learns that behavior 1
+has an expected payoff of 0.8, and the rest have an expected payoff of 0, but the
+optimal behavior changes between generations. Assume the child tries behavior 1, but
+it pays off 0.  If $B=2$, then at the next time step, $\ledger =
+(0.4, 0.0)$. The probability the agent explores behavior 2 is now 0.02. However, if
+$B=10$ the agent has $\ledger = (0.4, 0.0, \ldots, 0.0)$, and the probability the agent
+explores one of the nine alternative behaviors increases to 0.14.  If the agent again
+tries behavior 1 and it pays 0, the probability of exploring alternatives with $B=2$
+is 0.21, but with $B=10$ the probability of exploring alternatives more greatly increases
+to 0.71. \mt{I double checked these calculations, but would appreciate if someone
+  triple checked it}. 
+This explanation does not apply when $L=1$, where individual learning does not occur.
 
@@
 Greater payoff ambiguity means lower risk to try possibly outdated social
-information by reducing the penalty for performing non-optimal behaviors.
+information by reducing the penalty for performing non-optimal behaviors, leading
+to the observed drift in aggregated results.
 
@@
 lifetime, which, combined with finite population size, will make it more likely for 
-evolution to settle on a non-optimal population fixation.
+evolution to guide the population to non-optimal social/asocial learning stragegy.
 % In the first
@@
 
-To explain the evolution of social learning we assumed that, first, the relative benefit
-of having the social learning trait is essential to its evolution; and, second,
-we assumed that values of $\meansl \neq 0,1$ indicate evolutionary drift---but does our
-data support these assumptions?  Indeed, social learning evolution and evolutionary
-drift depended on the relative benefit of the social learning trait. We measured
-drift in terms of the average number of generations to fixation, denoted $\langle G
-\rangle$. Indeed, social learning evolution and drift are reflected in the relative
-benefit of social learning to asocial learning.  When social and asocial learning are
-equally beneficial, fixation takes longer to achieve, indicating greater drift.
-
-First, we confirmed that social learning evolves when $\meansoc > \meanasoc$.
-% by first comparing the expected
-% payoff for populations initialized as either all individual learners or all social
-% learners, denoted $\meansoc$ and $\meanasoc$, respectively.  
-In the case of $L=1$ we can calculate $\meanasoc$ directly: it is just the
-expected payoff across all bandits. When $L=8$, and for all uncertainty parameters 
-for $\meansoc$, we calculate expected social and asocial payoffs by respectively setting
-$\sum_i = N$ or $\sum_i = 0$ at model initialization. These stay constant since
-we do not allow for mutation.  We show expected payoffs for these four settings in this main text; we show the same
-plots for $\pilow = 0.8$ in the supplement both for $N=1000$ and $N=100$.
-
-Further inspection of maximal payoff ambiguity ($\pilow = 0.8$) showed strong
-effects of population size under sensitivity analysis\mt{TODO; not currently included in 
-the appendix}. In the default setting
-of $N=1000$, populations of initially all social learners performed much worse
+To explain the evolution of social learning we implicitly assumed above that, first,
+the relative benefit of having the social learning trait is essential to its
+evolution; and, second, we assumed that values of $\meansl \neq 0,1$ indicate
+evolutionary drift---but do our data support these assumptions?  Indeed, we found that
+social learning evolution and evolutionary drift depended on the relative benefit of
+the social learning trait. We measured drift in terms of the average number of
+generations to fixation, denoted $\langle G \rangle$. Indeed, social learning
+evolution and drift are reflected in the relative benefit of social learning to
+asocial learning.  When social and asocial learning are equally beneficial, fixation
+takes longer to achieve, indicating greater drift.
+
+First, we confirmed that social learning evolves when the expected payoffs to social
+learners exceed those of asocial learners, which we write $\meansoc > \meanasoc$.
+In the case of $L=1$ we can calculate $\meanasoc$ directly: it is just the expected
+payoff across all bandits. When $L=8$, and for all uncertainty parameters for
+$\meansoc$, we calculate expected social and asocial payoffs by respectively setting
+$\sum_i = N$ or $\sum_i = 0$ at model initialization. These stay constant since we do
+not allow for mutation.  
+In general, we observed that social learning evolved when its expected payoffs
+(Figure~\ref{fig:payoffs}, diamond-dash lines) exceeded expected individual-learner
+payoffs (Figure~\ref{fig:payoffs}, long-dashed lines). 
+However, we also found that populations of initially all social learners performed worse
 in many uncertainty contexts than either the actual payoffs accumulated by 
 model agents, and lower than even the expected individual-level payoffs,
-even though social learning evolved in many of the same contexts in our model
-with the default settings (Figure SupplementX1). When the population was
-reduced to $N=100$, there was a tighter evolutionary bottleneck on 
-underperforming agents, and selection more effectively weeded out underperforming agents.
-This demonstrates that larger populations not only can support beneficial
-choices~\cite{Henrich2004}, but also maladaptive information.
+even though social learning evolved in many of the same contexts in our model,
+especially when $\pilow = 0.8$ 
+(Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row).
 
@@
 We confirmed that drift increased when $\meansl$ transitioned from 1 to 0, 
-and when $\pilow$ was increased. We measured drift by the average number of 
+and when $\pilow$ was increased (Figure~\ref{fig:steps}). 
+We measured drift by the average number of 
 generations to fixation, $\meanG$. Recall fixation is defined as the population
@@
 there is no distinct peak in $\meanG$ across $B$ and $L$ settings, 
-indicating little difference in task difficulty across a range of uncertainty parameter settings.
+indicating little difference in task difficulty across a range of uncertainty
+parameter settings (Figure~\ref{fig:steps}, bottom row).
 
@@
 learning can yield higher payoffs than individual learning when uncertainty is
-sufficiently limited. Our model also demonstrated a new insight into social
-learning as a scaffold for individual learning, enabled by endowing agents
+sufficiently limited. We found increased
+payoff ambiguity and lifespan led to greater drift, which is essentially
+evolutionary uncertainty in a finite-size population. 
+Our model helped us understand that social
+learning acts as a scaffold for individual learning---they are not opposites. 
+We endowed agents
 with an evolutionarily- and biologically-plausible individual learning
-mechanism, softmax search. Specifically, we found that agents could recover
-from receiving outdated information, so social learning could evolve even
-though social information was outdated more often than not. We found increased
-payoff ambiguity and lifespan led to greater drift, which is essentially
-evolutionary uncertainty in a finite-size population. Detailed theoretical
-models and predictions of cultural evolution under uncertainty are critical
-for understanding how humans adapt to an uncertain and rapidly changing world,
-both to mitigate existential threats~\cite{Moya2020,Jones2021}, especially in
+mechanism, softmax search, that provided strong individual
+learning that helped agents recover
+from receiving outdated information. This enabled the evolution of social learning 
+even when social information is likely outdated. 
+Detailed theoretical
+models like this are critical for predicting how humans might adapt to an 
+uncertain and rapidly changing world.
+This knowledge could help suggest plausibly beneficial interventions to mitigate 
+existential threats~\cite{Moya2020,Jones2021}, especially in
 the most vulnerable communities~\cite{McNamara2020}, and to capitalize on new
@@
 
-Our modeling choices were judiciously made to address the main question of how uncertainty
-affects the evolution of social learning in general; however there exist alternative
-empirically-valid choices that could help further develop a more nuanced theory of social
-learning.  Our model necessarily made simplifying assumptions that may not always hold in more
-specific situations, though they are empirically justified to be general across taxa. First,
-note that we only considered success-biased learning, although conformity is sometimes the
-dominant social learning mechanism~\cite{Muthukrishna2016a,Smaldino2018b}.  Conformity may lead
-to more drift overall, since success-biased teacher selection, which we assumed, maximizes the
-potential benefit to social learners. We assumed that the number of behaviors and their payoffs
-were constant, but this fails to account for evolutionary feedback which creates new behavioral
-opportunities as time progresses, e.g.\ via niche
+Our modeling choices were judiciously made to address the main question of how
+uncertainty affects the evolution of social learning in general; however there exist
+alternative empirically-valid choices that could help further develop a more nuanced
+theory of social learning.  Our model necessarily made simplifying assumptions that
+may not always hold in more specific situations, though they are empirically justified
+to be general across taxa. First, note that we only considered success-biased
+learning, although conformity is sometimes the dominant social learning
+mechanism~\cite{Muthukrishna2016a,Smaldino2018b}.  Conformity may lead to more drift
+overall, since success-biased teacher selection, which we assumed, maximizes the
+potential benefit to social learners. We assumed that the number of behaviors and
+their payoffs were constant, but this fails to account for evolutionary feedback which
+creates new behavioral opportunities as time progresses, e.g.\ via niche
 construction~\cite{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
-supported by dynamic network structure~\cite{Smolla2019,Derex2020}.  Group structure and
-processes such as homophily and in-group bias/out-group aversion could inhibit the evolution of
-social learning since successful outgroup teachers could be cut off from in-group
-learners~\cite{Jackson2012}. We assumed agents choose behaviors via softmax search, but this is
-an underpowered algorithm compared to human individual learning~\cite{Schulz2020a,Wu2022}.
-More powerful individual learning could further support social learning.  These considerations
-reveal new opportunities to further by adjusting or extending the present model for other
-contexts.
+supported by dynamic network structure~\cite{Smolla2019,Derex2020}.  Group structure
+and processes such as homophily and in-group bias/out-group aversion could inhibit the
+evolution of social learning since successful outgroup teachers could be cut off from
+in-group learners~\cite{Jackson2012}. We assumed agents choose behaviors via softmax
+search, but this is an underpowered algorithm compared to human individual
+learning~\cite{Schulz2020a,Wu2022}.  More powerful individual learning could further
+support social learning.  These considerations reveal new opportunities to further by
+adjusting or extending the present model for other contexts.
 
@@
 
-We found that the evolution of social learning, under a few modest assumptions, is a
-complex phenomenon, dependent on several interrelated factors. By systematically
+We found that the evolution of social learning, even under only a few modest 
+assumptions, is a complex phenomenon, dependent on several interrelated factors. 
+By systematically
 identifying and operationalizing common theoretical assumptions about contextual
-uncertainty in social learning models, we were able to develop a more systematic
-understanding of which uncertainty factors interact to determine whether social learning
-evolves. By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the
-ability to adjust behavior to uncertainty and new information, we saw that social
-learning could evolve even if social learning regularly provides outdated
-information. This work informs most directly our current understanding of the evolution of
-social learning, but has broader significance for understanding problem
-solving under uncertainty. Our model and its software implementation were
-designed to be modular and extensible.  Indeed, we plan to extend this model to further
-develop a more detailed theoretical understanding of the evolution of social learning;
-we hope others will, too.
+uncertainty in social learning models, we developed a more systematic
+understanding of which uncertainty factors interact to determine whether social
+learning evolves. By explicitly modeling a key individual-level learning mechanism
+shared across taxa, namely the ability to adjust behavior to uncertainty and new
+information, we saw that social learning could evolve even if social learning
+regularly provides outdated information. This work informs most directly our current
+understanding of the evolution of social learning, but has broader significance for
+understanding problem solving under uncertainty. Our model and its software
+implementation were designed to be modular and extensible.  Indeed, we plan to extend
+this model to further develop a more detailed theoretical understanding of the
+evolution of social learning; we hope others will, too.
 
@@
 
-Model populations reached fixation between few to 140 generations on
+Model populations reached fixation within few to 140 generations on
 average (Figure~\ref{fig:steps}).
@@
 
-Drift is greater for smaller populations sizes, especially when
-$\pilow=0.8$, but patterns generally remain.
+Drift was greater for smaller populations sizes, especially when $\pilow=0.8$, but 
+the main patterns generally remain for $N=50$, $N=100$, and $N=200$ (recall
+$N=1000$ tested in main analysis). Drift is also more pronounced for smaller $N$
+for shorter lifespans, especially $L=1$. When $L=1$ and $N=50$ , the S-shaped
+curve of $\meansl$ over $u$ becomes more linear with increasing $B$, 
+with $\meansl$ values pulled towards maximal drift, $\meansl \to 0.5$ (Figure~\ref{fig:populationSensitivity}a,
+purple curves). With
+$N=50$, all $\meansl$ over $u$ curves are flattened with less sharp transitions
+from $\meansl = 1$ for lesser $u$ to $\meansl = 0$ for greater $u$. Despite
+these finite-population effects, we still see the inhibition of social learning
+as $u$ increases, more social learning across $u$ for larger $B$, and the
+same complex drift effects for combinations of $\pilow$ and $L$ that interact
+with $u$ and $B$ settings.
+
+\clearpage
 
@@
 
-\newpage
+\clearpage
+
 \subsection{Number of prospective teachers sensitivty analysis}
 
-Slightly more drift when $N_T = 2$, slightly less drift when $N_T = 20$, 
-but mostly just reproduces results for main text setting $N_T = 5$.
+We found that the number of prospectve teachers had little effect on $\meansl$
+over $u$. There was slightly more drift when $N_T = 2$ compared to our 
+main text analysis, slightly less drift than our main analysis when $N_T = 20$, 
+and no obvious difference between $N_T = 10$ tested here and our main results
+with $N_T = 5$. When $N_T = 2$, increased drift is most notable in the
+$\meansl$ curves when $\pilow=0.8$ (Figure~\ref{fig:nteachersSensitivity}a, 
+bottom row). The transition from $\meansl = 1$ to $\meansl = 0$ is less sharp
+across $L$ values, with social learning evolution being suppressed beginning
+at smaller values of $u$. By contrast, when $N_T = 20$, transitions from 
+$\meansl = 1$ to $\meansl = 0$ are sharper across $L$ when $\pilow = 0.8$
+(Figure~\ref{fig:nteachersSensitivity}c, bottom row). Otherwise, the main 
+results were reproduced across all tested values $N_T=2,5,10,20$.
+
+\clearpage
 
@@
   $N_T=5$ was used to generate main text results.}
-  \label{fig:softmaxSensitivity}
+  \label{fig:nteachersSensitivity}
   \vspace{2em}
@@
 
+\clearpage
+
 \subsection{Softmax parameter sensitivity analysis}
@@
 We tested two additional settings of the softmax behavior selection greediness parameter,
-$\beta=1,100$, which reproduced qualitative patterns in the evolution of social learning. In
-the main text we used $\beta=10$.  Softmax greediness is achieved formally by increasing the
+$\beta=1,100$, which reproduced qualitative patterns in the evolution of social learning
+observed in the main text where we used $\beta=10$.  
+Softmax greediness is achieved formally by increasing the
 probability mass for selecting behaviors that have paid off more frequently over that agent's
@@
 fully exploit their knowledge about which behavior is optimal because they too frequently
-explore less profitable alternatives.  If $\beta$ is too great the agents could more regularly
+explore less profitable alternatives.  If $\beta$ is too great the agents may prematurely
 settle on a sub-optimal behavior because it paid off first.  In a fuller evolutionary
-exploration of model parameters it would make sense for $\beta$ to co-evolve with the social
-learner trait.  However, our sensitivity analysis demonstrates that our main conclusions of how
-social learning evolves under uncertainty remain unchanged for different $\beta$ over three
-orders of magnitude.
-
-When $\beta=1$, most general trends are preserved, but in many cases the evolution
+exploration of model parameters one might allow $\beta$ to co-evolve, through
+mutation and selection, with the social learner trait.  
+However, our sensitivity analysis suggests this would be unnecessary 
+since our main conclusions of how social learning evolves under uncertainty remain unchanged for different
+$\beta$ over three orders of magnitude.
+
+First, when $\beta=1$, most general trends are preserved, but in many cases the evolution
 of social learning is suppressed or drift dominates due to 
 due to the overall poor quality of information acquired through softmax search-based
-individual learning.
-
-When $\beta=100$, there
-
-Other smaller details can also be observed between tested $\beta$. 
-First, there is generally more drift when $\beta=1$, 
-which can be seen in certain $(\pilow, B)$ pairs
-(entries in plot matrices in Figure~\ref{fig:softmaxSensitivity}a). 
-For example, when $\pilow = 0.1$ and $B=10$, there are a few more 
-data points with greater drift, i.e., where $\meansl \approx 0.5$. 
-The variation in our results when we set $\beta=100$
-(Figure~\ref{fig:softmaxSensitivity}b), changed from the
-main text where $\beta=10$, are more varied and subtle compared
-to setting $\beta=1$. In some cases, such as $(\pilow=0.1, B=10)$ 
+individual learning. This increased drift is especially pronounced 
+when $\pilow=0.8$ since sub-optimal behaviors often pay off and $\beta=1$ is
+not aggressive enough to efficiently detect and exploit the optimal 
+behavior (Figure~\ref{fig:softmaxSensitivity}a, bottom row).
+Similarly, when $\beta = 1$, social learning is suppressed at much smaller values
+of $u$ for longer lifespans, $L$, due to maximal excessive exploration of non-optimal
+behaviors under this setting (Figure~\ref{fig:softmaxSensitivity}a, columns 
+for $B$ and inset for $L$).
+
+With $\beta=100$, the changes in outcomes were minimal compared
+to setting $\beta=1$ (Figure~\ref{fig:softmaxSensitivity}b). 
+In some cases, such as $(\pilow=0.1, B=10)$ 
 and $(\pilow=0.45, B=2)$,
@@
   \caption{Sensitivity analysis of the main results for the softmax parameter $\beta = 100$ and
+  \addtocounter{figure}{-1}
   $\beta=1$. Recall the main results were obtained with $\beta = 10$.}

### 2022-08-13 ms.tex
final discussion revision
Updates from Overleaf

@@
 Theoretical models have helped clarify the circumstances under which social learning
-should be evolutionarily favored ~\cite{BoydRicherson1985}. This theoretical work has
+should be evolutionarily favored~\cite{BoydRicherson1985}. This theoretical work has
 motivated much empirical research and helped predict social learning behavior in humans
-and other species ~\cite{McElreath2005,Kendal2018,Allen2019}.  This literature
+and other species~\cite{McElreath2005,Kendal2018,Allen2019}.  This literature
 demonstrates that social learning is a critical adaptation found across taxa for dealing
@@
 volz2012}. As the number of formal models of social learning have expanded, an ever
-increasing number of modeling choices ~\cite[Figure 1]{Kendal2018} and formalizations of
+increasing number of modeling choices~\cite[Figure 1]{Kendal2018} and formalizations of
 uncertainty have made it difficult to compare across models and consolidate our
@@
 % The probabilities of environmental change are usually fixed per generation
-% ~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution}, 
+%~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution}, 
 but has also been modeled as deterministic cycles~\cite{Feldman1996, aoki2014evolution}.
@@
 larger, but defined, selection sets~\cite{Rendell2010}, while in others the
-number of options is implicit in the probability that a learner gets the right answer.
-~\cite{Enquist2007} 
+number of options is implicit in the probability that a learner gets the right answer~\cite{Enquist2007}.
 %\mt{How does this work exactly in Enquist et al 2007?}. 
@@
 of environment states, corresponding to a different number of optimal behaviors
-through time ~\cite{Feldman1996}. These examples share one common feature: 
+through time~\cite{Feldman1996}. These examples share one common feature: 
 the size of the selection set was held static \emph{within} model generations.
@@
 Smaller differences between payoffs corresponds to larger ambiguity. Payoff
-ambiguity has been manipulated in both theoretical ~\cite{perreault2012bayesian}
-and empirical ~\cite{McElreath2005, Morgan2012} studies, both of which support the
+ambiguity has been manipulated in both theoretical~\cite{perreault2012bayesian}
+and empirical~\cite{McElreath2005, Morgan2012} studies, both of which support the
 claim that payoff ambiguity increases the reliance on social information.
@@
 studies of information use in novel tasks, US participants' use of social
-information declined precipitously across rounds ~\cite{McElreath2005}, suggesting
+information declined precipitously across rounds~\cite{McElreath2005}, suggesting
 they were more likely to use social information when they were most uncertain
@@
 Cross-cultural studies on humans have shown the importance of childhood as a phase
-of heavy social learning ~\cite{Reyes2016}. Young children are more likely to
+of heavy social learning~\cite{Reyes2016}. Young children are more likely to
 acquire their beliefs and simple skills from their parents than are older children
@@
 varies across tasks, individuals, and species, yet most models assume one learning
-opportunity per generation ~\cite{Feldman1996,Henrich1998, perreault2012bayesian}.
+opportunity per generation~\cite{Feldman1996,Henrich1998, perreault2012bayesian}.
 Some models do allow several cultural generations within 1 genetic generation
@@
 learning, several other cognitive mechanisms have also evolved in response to
-uncertainty ~\cite{volz2012}. Many of these are flexible learning mechanisms that
+uncertainty~\cite{volz2012}. Many of these are flexible learning mechanisms that
 do not require assessing others' information. For example, people in experimental
@@
 learning~\cite{Schulz2020a,Wu2022}.  More powerful individual learning could further
-support social learning.  These considerations reveal new opportunities to further by
-adjusting or extending the present model for other contexts.
+support social learning.  These considerations reveal new opportunities to enhance
+theoretical nuance by adjusting or extending the present model for other contexts.
 

### 2022-08-19 ms.tex
Updates from Overleaf

@@
 \begin{abstract} 
-  Social learning is essential to human survival---it is a critical
+  Social learning is %essential to human survival---it 
+  is a critical
   adaptation for dealing with uncertainty. However, uncertainty takes many forms.
-  We identified four theoretically important types of uncertainty: temporal
+  We identified four distinct and theoretically important types of uncertainty: temporal
   environmental variability, ambiguous payoffs, decision set size, and effective
-  lifespans. We used this framework to study conditions for the evolution of
-  social learning in populations with cognitively realistic individual learning
-  capacities.  We used evolutionary agent-based modeling to track how often social, rather than individual,
-  learning evolved. Agents performed one of several behaviors to acquire payoffs.
-  Individual learning used the softmax algorithm. Social learning occurs between
-  generations  through vertical and oblique transmission.  Different types of
+  lifespans. We embed this framework in an evolutionary agent-based model to study conditions for the evolution of  social learning in populations with cognitively realistic individual learning
+  capacities. % We used evolutionary agent-based modeling to track the evolution of social learning versus purely individual learning.
+  %how often social, rather than individual,   learning evolved. 
+  Agents could perform one of several behaviors, modeled as multi-armed bandit, to acquire payoffs.
+  Individual learning used the softmax algorithm.
+Social learning involved vertical and oblique transmission between generations, which served as a constraint on subsequent individual learning.
+We found that different types of
   uncertainty had different effects. Temporal environmental variability suppressed
@@
   ambiguity and lifespan had more complex effects on social learning, dependent on
-  other uncertainty parameters.  This shows the importance of clearly
-  operationalizing uncertainty in theories of social learning evolution.
+  other uncertainty parameters.  This study shows the importance of clearly
+  operationalizing uncertainty for understanding its role in social and cultural evolution.
 % Social learning is essential to human survival. It is likely to evolve when it is more
@@
 efficient than learning on one's own~\cite{Laland2004}. However, social learning can also
-lead individuals astray if, for example, they are copying outdated information.
+lead individuals astray if they are copying irrelevant or outdated information.
 Theoretical models have helped clarify the circumstances under which social learning
-should be evolutionarily favored~\cite{BoydRicherson1985}. This theoretical work has
-motivated much empirical research and helped predict social learning behavior in humans
-and other species~\cite{McElreath2005,Kendal2018,Allen2019}.  This literature
-demonstrates that social learning is a critical adaptation found across taxa for dealing
-with uncertainty.  Uncertainty weighs particularly heavily on human adaptation because of
-our long lifespans, cosmopolitan distribution, and the resulting necessity to adapt to
-relatively coarse-grain environments \cite{levins1962}. However, the term ``uncertainty"
+should be evolutionarily favored~\cite{BoydRicherson1985, aoki2014evolution,Kendal2018}, and these models have motivated empirical work that has both validated and refined theoretical predictions concerning social learning behavior in humans
+and other species~\cite{galef2005social,McElreath2005,Kendal2018,Allen2019}.  This literature
+indicates that social learning is a critical adaptation found across taxa for dealing
+with uncertainty. When in doubt, copy others.
+
+Uncertainty weighs particularly heavily on human adaptation because of
+our long lifespans, cosmopolitan societies, and dispersal across a highly variable environments, requiring coarse-grain and plastic behavioral adaptations \cite{levins1962}.
+However, the term ``uncertainty"
 often conflates several different interpretations of that word. For example, different
@@
 Furthermore, in translating mathematical models to verbal predictions, the formal meaning
-of terms like uncertainty is often lost \cite{lawson1988probability}, facilitating such
-conflation. Furthermore, it can be important to distinguish a narrower definition of
-uncertainty wherein the probabilities of outcomes remain unknown~\cite{knight1921,
-volz2012}. As the number of formal models of social learning have expanded, an ever
-increasing number of modeling choices~\cite[Figure 1]{Kendal2018} and formalizations of
-uncertainty have made it difficult to compare across models and consolidate our
-understanding of the contexts in which social learning is adaptive. 
+of terms like uncertainty is often lost \cite{knight1921, lawson1988probability, volz2012}, facilitating such
+conflation. %Furthermore, it can be important to distinguish a narrower definition of uncertainty wherein the probabilities of outcomes remain unknown~\cite{knight1921,volz2012}. 
+As the number of formal models of social learning have expanded, an ever
+increasing number of modeling choices~\cite{Kendal2018} and formalizations of
+uncertainty have made it difficult to compare across models or to consolidate our
+understanding of the contexts in which social learning under uncertainty is adaptive. 
 % Finally, while risk and uncertainty are often used interchangeably to refer to
@@
 
-Other (asocial) forms of learning are also likely adaptations to uncertainty that should be
-accounted for, but are typically glossed over in models.  In general, learning is an iterative
-process by which one repeatedly acquires information, forms representations and
-predictions, and tests and refines those representations and predictions to manage
+%Other (asocial) forms of learning are also likely adaptations to uncertainty that should be accounted for, but are typically glossed over in models.  
+In general, learning is an iterative
+process during which an individual acquires information, forms representations and
+predictions, and then tests and refines those representations and predictions to manage
 uncertainty~\cite{jacobs2011bayesian,clark2013whatever}.  Because cultural evolutionary
-models are more often used to explain social learning mechanisms, they tend to use a
-single, weak individual-learning mechanism for comparison. Such modelling choices may lead us to underestimate the extent to which individual learning provides
-quality information, both for asocially adapting to uncertainty and for social learners to take advantage of.
-%and for the individual to adapt to the challenges
-assumed to be solved by social learning. 
+models are often designed to explain \emph{social} learning mechanisms, they often contrast social learning with an overly simplistic mechanism for individual learning.
+In particular, it is often assumed that individual learners can \emph{always} pay a cost to learn the optimal behavior for a particular environment with certainty.
+This assumption implies that social learning by observing an individual learner is a good bet if the environment has not changed.
+Such modelling choices may lead us to overestimate both the extent to which individual learning provides
+quality information and the value of social learning in a population of individual learners. % , both for asocially adapting to uncertainty and for social learners to take advantage of.
+%and for the individual to adapt to the challenges assumed to be solved by social learning. 
 % underestimate the quality of information
@@
 simultaneously operationalizes several forms of uncertainty and endows agents
-with a relatively powerful learning mechanism. We model four kinds of
+with a relatively powerful mechanism for individul learning. We model four kinds of
 uncertainty that are common in cultural evolution models and the related empirical
@@
 different behaviors); and (4) the effective lifespan of agents (the number of
-opportunities for individual learning), explained below. The model also assumes a more
-cognitively realistic and empirically-motivated learning mechanism, the softmax algorithm.
-This allows for a more accurate assessment of tradeoffs between 
-social and asocial learning
-by fleshing out an individual-level learning mechanism that makes full use of 
-the individually and socially learned data. 
-In this work, social learners learn from the previous generation, and 
-asocial learners do not. All agents engage in individual-level learning within
-their lifespans whether they are social learners or not.
-We use this integrated model to ask which kinds of uncertainty are likely to
-favor social learning and to clarify the logic underlying the results.
+opportunities for individual learning), explained below. In our model, social learners learn from the previous generation and asocial learners do not. All agents engage in individual learning within
+their lifespans. The model also assumes a more
+cognitively realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows  learners to make full use of the available data acquired by both individual and social learning.
+Our model design thereby affords us a richer and possibly more accurate assessment of tradeoffs between 
+social and asocial learning. 
+We use this integrated model to ask which kinds of uncertainty are likely to favor social learning and to clarify the logic underlying the results.
 %of why this would be the case.  
-
-In the remainder of this introduction we describe previous research on the forms of uncertainty and the learning mechanism we include in our model.
-We then present how our evolutionary agent-based model works.
+In the remainder of this introduction we briefly review previous research on both the forms of uncertainty and the learning mechanism used in our model. 
+%We then present how our evolutionary agent-based model works.
 Finally, we explain the logic underlying the result that different forms of uncertainty can either suppress or encourage the evolution of social learning.
@@
 \textbf{Temporal environmental variability.} When environments change
-(e.g., climatic events, migration, technological paradigm shifts),
+(for example, in response to climatic events, migration, or technological paradigm shifts),
 strategies that were previously adaptive may no longer be optimal. The difficulty
@@
 social learning. Such fluctuations have been proposed as an important selective
-pressure for learned as opposed to genetically fixed behaviors
-~\cite{Richerson2000}. On the other hand, environments that change too quickly
-will lead the population away from social learning to avoid outdated, 
-and therefore maladaptive information~\cite{Feldman1996,
+pressure for learned as opposed to genetically fixed behaviors when genetic adaptation cannot keep pace with environmental change 
+~\cite{Richerson2000}. On the other hand, environments that change \emph{too} quickly
+will select against social learning so that individuals avoid learning outdated--- 
+and therefore maladaptive---information~\cite{Feldman1996,
 BoydRicherson1985}. This suggests that intermediate levels of temporal variation
@@
 
-Despite the theoretical centrality of temporal environmental variability, this construct is
-implemented in several ways~\cite{aoki2014evolution}. Most commonly, it is modeled
-as an independent probability of the environment changing its state each
-generation
-~\cite{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}.
+%Despite the theoretical centrality of t
+Temporal environmental variability tends to be modeled in one of 
+several ways~\cite{aoki2014evolution}. Most commonly, it is modeled
+as an independent probability that the environment changes its state (and its corresponding optimal behavior) before each new generation
+~\cite{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}, but
 % The probabilities of environmental change are usually fixed per generation
 %~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution}, 
-but has also been modeled as deterministic cycles~\cite{Feldman1996, aoki2014evolution}.
-Furthermore, the consequences of environmental change can range from mild to
+it has also been modeled using deterministic cycles, so that environments repeat at regular intervals ~\cite{Feldman1996, aoki2014evolution}.
+%Furthermore, t
+The consequences of environmental change can range from mild to
 catastrophic. In the latter case, a change of environment results in the total
@@
 from previous generations. Other models of environmental change introduce less
-uncertainty as they fluctuate between two environmental states with corresponding
+uncertainty as they fluctuate between two or more environmental states with corresponding
 adaptive behaviors. This means that previously maladaptive
@@
 ~\cite{perreault2012bayesian}. The chosen mechanism for modelling temporal
-change has real theoretical consequences~\cite{aoki2014evolution}.
+change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behavior, and instead considers only behaviors that can be learned.
 
@@
 % This is intuitive; the more options to consider, the greater one's uncertainty about which option is the best choice. 
-In studies of social learning, the selection set is often limited
-to just two options.  For example, in empirical studies of \emph{bombus
+In many studies of social learning, the selection set is often limited to just two options.  For example, in empirical studies of \emph{bombus
 terresteris} (bumble bee)~\cite{Baracchi2018} and \emph{parus major} (great
-tit)~\cite{Aplin2017}, experimenters provided two behaviors for the bees or birds
-to choose from, where one yielded a higher payoff than the other. %respectively,
-each yielding greater or smaller payoffs depending on experimental treatment.
+tit)~\cite{Aplin2017}, experimenters provided two behaviors from which the bees or birds
+could choose, with one yielding a higher payoff than the other. %respectively,
+%each yielding greater or smaller payoffs depending on experimental treatment.
 Similarly, many human studies have used just two or three possible
-behaviors~\cite{McElreath2005,Toyokawa2019}. Behavioral study designs are
-often motivated by modeling studies with similar formulations~\cite{Rogers1988,boyd1995does,
+behaviors~\cite{McElreath2005,Morgan2012, Toyokawa2019}. Behavioral study designs are
+often motivated by modeling studies with similar formulations~\cite{Rogers1988,boyd1995does,Feldman1996,
 perreault2012bayesian}.
@@
 Some models have studied systems with
-larger, but defined, selection sets~\cite{Rendell2010}, while in others the
-number of options is implicit in the probability that a learner gets the right answer~\cite{Enquist2007}.
+larger, but defined, selection sets~\cite{Rendell2010, lindstrom2016co}, while in others the
+number of options is subsumed under the probability that a learner gets the right answer~\cite{Feldman1996,Enquist2007}.
 %\mt{How does this work exactly in Enquist et al 2007?}. 
-Researchers have also compared models with a different number
-of environment states, corresponding to a different number of optimal behaviors
-through time~\cite{Feldman1996}. These examples share one common feature: 
-the size of the selection set was held static \emph{within} model generations.
+%Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviors through time~\cite{Feldman1996}. 
+Rarely if ever is the size of the selection set explored explicitly as a source of varying uncertainty, even though the number of options one has is likely to increase with the difficulty of the decision task~\cite{haynes2009testing,white2009testing}.
+%These examples share one common feature: the size of the selection set was held static \emph{within} model generations.
 % as a measure of changing uncertainty in cultural evolutionary models.
 
-\textbf{Payoff ambiguity.} Many models of social learning differentiate between
-the payoffs for adopting optimal vs. non-optimal behaviors
-\cite{Rogers1988,Enquist2007,Rendell2010}. The size of the difference between
-these payoffs is usually taken to indicate the strength of selection of learning,
-which makes sense. However, in reality payoffs for particular behaviors are not
-always consistent. A behavior may yield a large payoff sometimes and a small
+\textbf{Payoff ambiguity.} Most models of social learning necessarily differentiate between the payoffs for adopting optimal vs. non-optimal behaviors
+\cite{BoydRicherson1985,Rogers1988,Enquist2007,Rendell2010,aoki2014evolution}. The size of the difference between
+these payoffs is usually taken to indicate the strength of selection of learning. %, which makes sense. 
+However, the ability to discern payoff differences between behaviors is also a source of uncertainty.
+In reality, payoffs for particular behaviors are not always consistent.
+A behavior may yield a large payoff sometimes and a small
 payoff other times \cite{McElreath2005}. This means that signals about the
@@
 Importantly, payoff ambiguity %differs from selection set size in that it not only 
-affects uncertainty, it also directly influences both uncertainty \emph{and} the
-strength of selection. %This parameter sometimes takes the form of differences in
-expected payoffs arising from different behaviors or
-strategies~\cite{Enquist2007,Rendell2010} or by varying the standard deviation of
-payoffs~\cite{McElreath2005}.
+affects both 
+%affects uncertainty, it also directly influences both 
+uncertainty \emph{and} the
+strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
+%This parameter sometimes takes the form of differences in
+%expected payoffs arising from different behaviors or strategies~\cite{Enquist2007,Rendell2010} or by varying the standard deviation of payoffs~\cite{McElreath2005}.
 
 \textbf{Effective lifespan.} 
-The more opportunities one has for
-learning in their lifespan, the more uncertainty can be reduced, assuming a
-static environment. Similarly, a reduction in the number
-of opportunities to learn will increase the uncertainty about whether one has
-accurately learned about the available behavioral options and their associated
-payoffs. That uncertainty is passed on to future generations.
+The more opportunities one has to learn during one's lifespan, the more uncertainty can be reduced, assuming a
+static environment. Correspondingly, a reduction in the number of opportunities to learn will increase the uncertainty about which behavioral options are available and what their associated
+payoffs are. %Such uncertainty can be passed on to future generations.
 % Learning is an iterative process by which one repeatedly acquires information, forms
@@
 % predictions to manage uncertainty \cite{jacobs2011bayesian,clark2013whatever}. 
-We refer to the number of learning opportunities as an individual's
-effective lifespan to imply that it is the number of opportunities to learn
-throughout the individual's lifespan that matters here, not necessarily how long
-they live in the absence of relevant learning opportunities.
-
-Empirically, the number of learning opportunities can be manipulated in the lab,
-but will also correspond with an individual's age the real world. In multi-round
+We refer to the number of learning opportunities as an individual's effective lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behavior, rather than the number of sunrises one experiences, that determines the level of uncertainty present in one's choices.
+%throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.
+
+Empirically, the number of learning opportunities can be manipulated in the lab, and in the real world will tend to correlate with an individual's relative age. In multi-round
 studies of information use in novel tasks, US participants' use of social
 information declined precipitously across rounds~\cite{McElreath2005}, suggesting
-they were more likely to use social information when they were most uncertain
-about the task early on. In a more naturalistic context, Aplin et al. (2017)
+they were more likely to use social information when they were most uncertain about the task early on. In a more naturalistic context, Aplin et al. (2017)
 \nocite{Aplin2017} found that younger great tits more readily used social
-information compared with older individuals, possibly because they had accrued
-less information via individual learning, and also possibly because younger
-individuals have the most to gain (given their expected remaining lifespan) by
-switching to superior behavioral options. 
+information compared to older individuals, possibly because they had accrued
+less information via individual learning, and possibly because younger
+individuals have the most to gain (given their expected remaining lifespan) by switching to superior behavioral options. 
 % \ps{I got rid of the Leris and Reader reference because it didn't seem relevant
@@
 % some human studies, which seems important.} 
-Cross-cultural studies on humans have shown the importance of childhood as a phase
-of heavy social learning~\cite{Reyes2016}. Young children are more likely to
+Cross-cultural studies have highlighted the importance of childhood as a phase
+of heavy social learning in humans ~\cite{Reyes2016}. Young children are more likely to
 acquire their beliefs and simple skills from their parents than are older children
@@
 The effective lifespan for learning
-varies across tasks, individuals, and species, yet most models assume one learning
-opportunity per generation~\cite{Feldman1996,Henrich1998, perreault2012bayesian}.
-Some models do allow several cultural generations within 1 genetic generation
-~\cite{Enquist2007}, but little formal theory explicitly examines the role of
-learning opportunities in social learning evolution models.
+varies across tasks, individuals, and species, yet most models assume only one learning
+opportunity per generation~\cite{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
+Some models do allow several cultural generations within one genetic generation
+~\cite{Enquist2007,Rendell2010,lindstrom2016co}, but little formal theory explicitly examines the role of
+learning opportunities in the evolution of social learning.
 
@@
 
-Social learning is the adaptive icing on the cake of other cognitive adaptations
-to ecological uncertainty.  While the literature reviewed above suggests that
-several forms of uncertainty play a role in favoring the evolution of social
-learning, several other cognitive mechanisms have also evolved in response to
-uncertainty~\cite{volz2012}. Many of these are flexible learning mechanisms that
-do not require assessing others' information. For example, people in experimental
-studies increase their exploratory behavior when total uncertainty in the task
-increases and are more likely to test %Furthermore, correlations in uncertainty
-between potential behaviors, humans tend to adopt directed exploration strategies
-that favor testing behaviors with greater observed payoff variance
+%Social learning is the adaptive icing on the cake of other cognitive adaptations to ecological uncertainty. 
+While the literature reviewed above suggests that
+several forms of uncertainty have played a role in the evolution of social
+learning, other cognitive mechanisms have likely also evolved in response to
+uncertainty~\cite{volz2012,johnson2013evolution,van2018uncertainty}. Many of these are flexible learning mechanisms that
+do not require imitating the behaviors of others.
+For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviors with greater observed payoff variance
 \cite{Wilson2014,Gershman2019}.
 
-Many models of social learning assume little to no cognitive capabilities
-of their agents. For example, a common modelling strategy compares the payoffs of
-agents with different pure learning strategies (some will always engage in social
-learning, and others in individual learning) while revealing nothing about the
+Many models of social learning simplify by using minimally cognitive %assume little to no cognitive capabilities of their 
+agents. For example, a common modelling strategy compares the payoffs of
+agents with different pure learning strategies (e.g., those who only engage in social
+learning versus those who only engage in individual learning) while revealing nothing about the
 cognition underlying individuals' decisions~\cite{BoydRicherson1985, Rogers1988,
-aoki2005}. Some more complicated learning strategies that make use of both
-socially and individually learned information have been proposed
-~\cite{Enquist2007, perreault2012bayesian}, but these are seldom designed to
-reflect cognitive mechanisms for integrating information. Though such
-simplifications are often useful, several authors have warned of the risks to
-\emph{blackboxing}, or ignoring, cognitive mechanisms \cite[p. 658]{Heyes2016,
-Kendal2018}, given such details may be theoretically meaningful. In order to
-understand how social learning evolves as an adaptation to uncertainty, we 
-endowed agents with a biologically plausible cognition capable of integrating
-information from various sources to maximize payoffs, \emph{softmax
+aoki2005}.
+This sort of behavioral gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to social and cultural evolution \cite{Heyes2016,Kendal2018}.
+Some more complicated learning strategies that make use of both socially and individually learned information have been studied ~\cite{Enquist2007, perreault2012bayesian}, including those that integrate cognitively plausible mechanisms such as reinforcement learning \cite{lindstrom2016co}, though the latter approach remains the exception rather than the norm.
+%but these are seldom designed to reflect cognitive mechanisms for integrating information.
+Though such simplifications are often useful, several authors have warned of the risks to \emph{blackboxing}, or ignoring, cognitive mechanisms \cite[p.
+658]{Heyes2016, Kendal2018}, given such details may be theoretically meaningful.
+In order to understand how social learning evolves as an adaptation to uncertainty, we 
+endowed agents with a biologically plausible cognition capable of integrating information from various sources to maximize payoffs, using \emph{softmax
 search}~\cite{Gershman2019}, described in more detail below. 
@@
 
-To understand how uncertainty affects social learning, 
-we developed an agent-based model of
-social learning evolution.  Evolutionary agent-based models simulate changes in
-the prevalence of a phenotype over several generations---in this model the phenotype
-is whether or not an agent engages in social learning.  In our model, a
-population of $N$ individuals each must decide which of $B$ behaviors to perform at
-each time step within a generation consisting of $L$ time steps. At the end of each
-generation, agents are selected with replacement to reproduce another $N$ agents, 
-biased by net payoffs. Agents
-who inherit the social learning trait then learn about payoffs from the
-previous generation, while asocial learners begin life with no \emph{a priori}
-knowledge of the world.  Each behavior is a ``bandit'', a common modeling and
-experimental approach for representing behaviors with random-valued
-payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
-Bandits in our model yield Bernoulli payoffs of 1 or 0 with some probability,
-with that probability defining each behavior's expected payoffs.  One of the
-bandits/behaviors in the model is more likely to pay off than all the rest.  Agents
+%To understand how uncertainty affects social learning, we developed an agent-based model of social learning evolution.
+Evolutionary agent-based models simulate changes in the prevalence of a phenotype over several generations---in this model the phenotype is whether or not an agent engages in social learning.
+In our model we allow just one trait to evolve; social learning, while all other parameters are exogenous.
+Our primary outcome measure is the overall frequency of the social learning trait at the end of each simulation, and we study how this prevalence responds to the four varieties of uncertainty considered in this paper.
+
+A population of $N$ individuals each must decide which of $B$ behaviors to perform at
+each time step within a generation consisting of $L$ time steps.
+The behavior set is a multi-armed bandit with $B$ arms, that is, agents can pick one of $B$ behaviors with random-valued payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
+\ps{To clarify terminology, the entire set of behaviors is one multi-armed bandit with $B$ arms -- each behavior is not itself a bandit.}
+%Each behavior yields a payoff of either 1 or 0 with some probability that is held fixed within a generation but can change between generations.
+This probability is therefore equal to the behavior's expected payoff within a generation.
+In each generation, exactly one behavior is more likely to pay off than all the rest and is therefore optimal. Agents
 optimize their net payoffs over their lifespan by quickly figuring out which
 behavior is optimal and performing it as often as possible within their lifespan.
-The optimal behavior is static within agent lifespans, but varies in general between
-generations, representing environmental variability.
-
-We operationalized four separable varieties of uncertainty that affect the
-ability of agents to find and choose the optimal behavior: 
-\emph{environmental variability}; 
-\emph{selection set size}; \emph{payoff ambiguity}; and the \emph{effective lifespan}. 
-Environmental variability is the probability that the optimal behavior changes
-between generations.   
-% This is empirically justified since cultural evolution
-% occurs when meta-cognitive strategies and information are transferred via
-% learning and social influence, instead of by physical reproduction and death
-% as in genetic evolution.  
-The selection set size is the total number of possible
-behaviors agents choose from, assumed to be constant within a simulation.  
-Payoff ambiguity is the payoff difference between optimal
-and non-optimal behaviors. The effective life span is the
-number of time steps in which agents perform behaviors within a generation. 
-Our model is not spatial, so agents have free, instant
-access to all behaviors, and there is no spatial uncertainty. 
-These conditions reflect humans in a computer-based social learning evolution
-experiment~\cite{McElreath2005,Morgan2012,Derex2016}. Spatial dimensions could also be
-considered irrelevant if costs associated with accessing a behavior were equal,
-e.g., if it was assumed to be equally costly for animals to
-visit alternative food sources~\cite{Aplin2017,Baracchi2018}.
-Each simulated environment provides a distinct challenge
-to the agents, which will lead agents to differently evolve to become social
-learners or not, depending on which strategy optimizes net payoffs.
-
-\emph{Agents} here are autonomous, intelligent, simulated problem solvers. Each
-agent evaluates its environment and chooses how to act within that environment based
-on a set of empirically-motivated rules.  Our agents select which behavior to do
-probabilistically, weighted by the softmax function applied to the mean payoff they
-have observed for each behavior. The softmax function is a biologically plausible
-generalization of behavior selection under uncertainty that enables agents to often
-greedily exploit the most lucrative behavior (based on their observations) but also
-to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
-Such individual-level intelligence is a critical adaptation that has 
-co-evolved with the capacity for social learning. We will show that individual
-learning can support the evolution of social learning.
-
-In our \emph{evolutionary} agent-based model, agent life cycles are
-programmed to cause agents to reproduce and die off, where reproducers pass on
-heritable traits to their offspring. 
-Natural selection occurs in the model when agents with higher
-payoffs preferentially reproduce. This is a model of cultural evolution, so
-``reproduction'' means teaching the meta-cognitive strategy of whether one should learn
-socially at all; ``death'', in this interpretation, means
-loss of the potential to socially influence others. 
-This sets up an inter-generational cultural structure
-that we also use as a scaffold for \emph{oblique} social learning, meaning children
-with the social learning trait learn about payoffs from a member of the
-previous generation. Evolution acts as an optimization routine to identify
-whether individuals with the social learning trait will outperform those without.
-
-Agents inherit one trait in this model, whether or not
-an agent, $i$, learns socially. If $i$ has the trait we write $s_i=1$
- and 0 otherwise. In our analysis, we 
-average $s_i$ over all agents and simulation trials to understand the affects of
-different uncertainty parameter settings. 
-Our computational analysis is based on observing and comparing patterns in
-aggregated $s_i$ across different parameter settings, 
-supported by measuring the number of generations 
-to model convergence and expected payoffs in populations across the same contexts. 
-To understand how different varieties of uncertainty interact
-to affect the evolution of social learning, we systematically created an array of
-simulated environments by systematically varying the uncertainty parameters, and
-auxiliary model parameters to ensure model validity.
+%The optimal behavior is static within agent lifespans, but varies in general between generations, representing environmental variability.
+At the end of each
+generation, agents are selected with replacement to reproduce a new generation of $N$ agents, with the probability of reproduction biased by net payoffs.
+Agents who inherit the social learning trait learn about payoffs from the previous generation, while asocial learners begin life with no \emph{a priori}
+knowledge of the world. \cm{or would you consider having flat priors over all behaviors knowledge?}  
+%The specifics of the model construction and dynamics are described in detail below.
+\ps{I cut a bunch of stuff that came right here as being redundant or unnecessary.}
+
+% We operationalize four separable varieties of uncertainty that affect the
+% ability of agents to find and choose the optimal behavior: 
+% \emph{environmental variability}; 
+% \emph{selection set size}; \emph{payoff ambiguity}; and the \emph{effective lifespan}. 
+% %Environmental variability is the probability that the optimal behavior changes
+% between generations.   
+% % This is empirically justified since cultural evolution
+% % occurs when meta-cognitive strategies and information are transferred via
+% % learning and social influence, instead of by physical reproduction and death
+% % as in genetic evolution.  
+% The selection set size is the total number of possible
+% behaviors agents choose from, assumed to be constant within a simulation.  
+% Payoff ambiguity is the payoff difference between optimal
+% and non-optimal behaviors. The effective life span is the
+% number of time steps in which agents perform behaviors within a generation. 
+% Our model is not spatial, so agents have free, instant
+% access to all behaviors, and there is no spatial uncertainty. 
+% These conditions reflect humans in a computer-based social learning evolution
+% experiment~\cite{McElreath2005,Morgan2012,Derex2016}. Spatial dimensions could also be
+% considered irrelevant if costs associated with accessing a behavior were equal,
+% e.g., if it was assumed to be equally costly for animals to
+% visit alternative food sources~\cite{Aplin2017,Baracchi2018}.
+% Each simulated environment provides a distinct challenge
+% to the agents, which will lead agents to differently evolve to become social
+% learners or not, depending on which strategy optimizes net payoffs.
+
+% \emph{Agents} here are autonomous, intelligent, simulated problem solvers. Each
+% agent evaluates its environment and chooses how to act within that environment based
+% on a set of empirically-motivated rules.  Our agents select which behavior to do
+% probabilistically, weighted by the softmax function applied to the mean payoff they
+% have observed for each behavior. The softmax function is a biologically plausible
+% generalization of behavior selection under uncertainty that enables agents to often
+% greedily exploit the most lucrative behavior (based on their observations) but also
+% to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
+% Such individual-level intelligence is a critical adaptation that has 
+% co-evolved with the capacity for social learning. We will show that individual
+% learning can support the evolution of social learning.
+
+% In our \emph{evolutionary} agent-based model, agent life cycles are
+% programmed to cause agents to reproduce and die off, where reproducers pass on
+% heritable traits to their offspring. 
+% Natural selection occurs in the model when agents with higher
+% payoffs preferentially reproduce. This is a model of cultural evolution, so
+% ``reproduction'' means teaching the meta-cognitive strategy of whether one should learn
+% socially at all; ``death'', in this interpretation, means
+% loss of the potential to socially influence others. 
+% This sets up an inter-generational cultural structure
+% that we also use as a scaffold for \emph{oblique} social learning, meaning children
+% with the social learning trait learn about payoffs from a member of the
+% previous generation. Evolution acts as an optimization routine to identify
+% whether individuals with the social learning trait will outperform those without.
+
+% Agents inherit one trait in this model, whether or not
+% an agent, $i$, learns socially. If $i$ has the trait we write $s_i=1$
+%  and 0 otherwise. In our analysis, we 
+% average $s_i$ over all agents and simulation trials to understand the affects of
+% different uncertainty parameter settings. 
+% Our computational analysis is based on observing and comparing patterns in
+% aggregated $s_i$ across different parameter settings, 
+% supported by measuring the number of generations 
+% to model convergence and expected payoffs in populations across the same contexts. 
+% To understand how different varieties of uncertainty interact
+% to affect the evolution of social learning, we systematically created an array of
+% simulated environments by systematically varying the uncertainty parameters, and
+% auxiliary model parameters to ensure model validity.
 
@@
 
-The model environment provides behaviors for agents to perform. The structure
-of the environment is specified by setting several parameters, including
-three of the uncertainty parameters: environmental variability, selection set size, 
-and payoff ambiguity. 
-Each behavior is indexed by $b$ and modeled as a ``one-armed bandit'', which yields 
-Bernoulli-distributed payoffs of 1 with probability $\pi_b$ and 0 with 
-probability $1 - \pi_b$. $\pi_b$ is equivalently the expected
-payoff of behavior/bandit $b$. The model environment affords $B$ behaviors, where
-$B$ is the \emph{selection set size} uncertainty parameter, which
-is constant throughout the course of a given simulation, but varied systematically
-across simulations.
-
-The model environment is dynamic: which behavior is optimal changes between
-generations with probability equal to the \emph{environmental variability}, $u$.
-At the beginning of each generation, one bandit is optimal and yields expected
+%The model environment provides behaviors for agents to perform. 
+The structure of the environment is specified by several parameters that remain fixed throughout the course of a given simulation (Table~\ref{tab:uncertaintyParameters}).
+%including three of the uncertainty parameters: environmental variability, selection set size, and payoff ambiguity.
+The environment affords $B$ behaviors, where
+$B$ is the \emph{selection set size}.
+%, but varied systematically across simulations.
+Each behavior is indexed by $b$ and 
+%modeled as a ``one-armed bandit'', which 
+yields a payoff 
+%Bernoulli-distributed payoffs 
+of 1 with probability $\pi_b$ and a payoff of 0 otherwise. % with probability $1 - \pi_b$. 
+$\pi_b$ is equivalently the expected
+payoff of behavior $b$.  
+At the beginning of each generation, one behavior is optimal and yields expected
 payoff $\pihigh$; the other $B-1$ behaviors yield a lower payoff, $\pilow$. 
 The \emph{payoff ambiguity} is defined by $\pihigh - \pilow$. 
-We set $\pihigh = 0.9$, constant across all simulations, so we vary
-payoff ambiguity by varying $\pilow$, i.e., payoff ambiguity increases with
-$\pilow$.
+We fix $\pihigh = 0.9$ to be constant across all simulations, so 
+payoff ambiguity is varied by changing the value of $\pilow$.
+In other words, payoff ambiguity increases with $\pilow$.
+Agents have $L$ timesteps to learn and act per generation (i.e., the \emph{effective lifespan}).
+Uncertainty decreases with $L$.
+At the start of each generation a new optimal behavior is selected at random from the set of all possible behaviors with probability $u$ (the \emph{environmental variability}), otherwise the optimal behavior remains unchanged from the previous generation.
 
@@
 \begin{table}[h]
-\caption{Model ecological parameters, including uncertainty parameters $u$, $B$,
+\caption{Environmental parameters used in our simulations, including uncertainty parameters $u$, $B$,
 $\pilow$, and $L$. Bold indicates default value tested} %\emph{default value tested}.}
@@
 
-        $B$       & Number of ``bandits'', i.e., behavior options
+        $B$       & Number of behavior options
                   & 2, 4, 10 \\
@@
 
-Agents are endowed with dynamic attributes to intelligently select behaviors and
-calculate average payoffs for each behavior. All agents engage in
-individual learning over their lifespan, whether or not they are social learners.
+%Agents are endowed with dynamic attributes to intelligently select behaviors and calculate average payoffs for each behavior. 
+Agents either exclusively rely on asocial learning or additional use social information.
+For simplicity, we refer to the latter as social learners.
+Learning strategies are assumed to be heritable traits.
+Each agent $i$ has a learning trait $s_i$, which is 1 if $i$ is a social learner and zero otherwise.
+Every agent engages in
+individual learning over its lifespan, regardless of learning strategy.
 Social learners begin life with
-behavioral preferences based on information from their
-teacher, an agent from the previous generation. 
+behavioral preferences based on information from an agent chosen  from the previous generation. 
 Asocial learners begin life with no behavioral
-preferences. 
+preferences. Agent-level parameters are described in Table~\ref{tab:modelParameters}. 
 % Agents and their learning procedures are specified through several
@@
 guides agents to more frequently exploit the most profitable behaviors when the
-agent is more certain which is optimal, and to explore more frequently when the
+agent is more certain which is optimal and to explore more frequently when the
 agent is unsure.  To do softmax searching, agents track average payoffs acquired
-from each behavior, which also requires agents to track the number of times they
-have performed each behavior.  We denote the average payoffs obtained by agent $i$
+from each behavior they have performed and the number of times they
+have performed each behavior.
+\cm{is the previous sentence still right?
+I changed it's meaning because it made it sound like tracking average meant keeping track of total number of times it was performed, but that's not inherentely the case.
+Softmax does BOTH right?
+to estimate certainty.}  We denote the average payoffs obtained by agent $i$
 for behavior $b$ as $\ledger$. We denote the number of times $i$ performed $b$
 as $c_{ib}$ (``$c$'' stands for count). 
-At each time step, agents perform behavior $b$ with softmax-weighted probability
+At each time step, agent $i$ performs behavior $b$ with softmax-weighted probability
 \begin{equation}
@@
 behaviors with high expected payoffs (larger $\beta$) versus how frequently
-agents explore alternative behaviors (smaller $\beta$)~\cite{McElreath2005}.
+agents explore alternative behaviors (smaller $\beta$). %~\cite{McElreath2005}. 
+We used a default value of $\beta = 10$, but also varied this value in our sensitivity analyses. 
+The softmax function used here is a biologically plausible
+generalization of behavior selection under uncertainty that enables agents to often
+greedily exploit the most lucrative behavior (based on their observations) but also
+to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
 
@@
 
-At the beginning of each generation other than the first, social child agents select
-one member of the previous generation to learn from, if the child inherited
-$s_i = 1$. A child agent $c$ is a social learner if its parent $p$ was a social
-learner, i.e.\ $s_c \leftarrow s_p$, without mutation.  Social learner children
-select a teacher from the previous generation by first selecting $N_T$ prospective
-teachers fully at random, then by sampling from the $N_T$ with each prospective
-teacher weighted by their net payoffs relative to the other $N_T - 1$.
-
-\subsubsection{Social learning as a scaffold for individual learning}
-
-In this model, being a social learner is beneficial when it is more likely on
-average to provide greater net payoffs than being an individual learner.  It is not
-catastrophic for an individual to receive outdated information, as is sometimes
-assumed~\cite[e.g.]{Rogers1988}. Instead, agents explore alternatives and
-greedily perform different behaviors that pay off better. 
-This mechanism is critical for explaining the patterns we observe in the 
-Analysis, where social learning evolves when $u > 0.5$.
-In this case, the optimal behavior will switch between generations more often than
-not. Without individual learning, social learning would not evolve when $u > 0.5$.
+At the beginning of each generation other than the first, each social learner selects
+one member of the previous generation to learn from in a payoff-biased way. 
+%, if the child inherited $s_i = 1$. A child agent $c$ is a social learner if its parent $p$ was a social learner, i.e.\ $s_c \leftarrow s_p$, without mutation.
+A social learner  
+selects this ``teacher" from the previous generation by first selecting $N_T$ prospective teachers at random, then selects its teacher from this set with a probability weighted by each prospective teacher's net payoff
+relative to the other $N_T - 1$ prospective teachers.
+The social learner then inherits information about the likely payoffs of each behavior from the teacher, whereas asocial learners do not acquire this information.
+\cm{I think this inheritance has to be explained more.
+(I see that you do this later, so maybe it can be cut back here)} In this way, the social learner can potentially reduce the amount of exploration needed to both execute and learn about the optimal behavior.
+
+% \subsubsection{Social learning as a scaffold for individual learning}
+
+% In this model, being a social learner is beneficial when it is more likely on
+% average to provide greater net payoffs than being an individual learner.  It is not
+% catastrophic for an individual to receive outdated information, as is sometimes
+% assumed~\cite[e.g.]{Rogers1988}. Instead, agents explore alternatives and
+% greedily perform different behaviors that pay off better. 
+% This mechanism is critical for explaining the patterns we observe in the 
+% Analysis, where social learning evolves when $u > 0.5$.
+% In this case, the optimal behavior will switch between generations more often than
+% not. Without individual learning, social learning would not evolve when $u > 0.5$.
 
@@
 Model dynamics proceed by first initializing the environment and agents according
-to parameter settings for the simulation. Then, within each generation,
-agents select and perform behaviors, updating their observations along the way.
-Between generations, agents reproduce, teach child agents, and die off. 
-Child agents then begin a new round of generational dynamics, followed by
-reproduction. This process continues until the population has fixated as
-all social learners or all asocial learners, or until an upper limit of 
+to the chosen parameter settings. % for the simulation.
+Then, within each generation, agents select and perform behaviors, updating their estimated payoffs (and their probabilities of choosing each behavior) along the way.
+Between generations, agents reproduce, teach social learners of the next generation, and die off. 
+%Child agents then begin a new round of generational dynamics, followed by reproduction. 
+This process continues until the population has evolved to fixation as either all social learners or all asocial learners, or until an upper limit of 20,000 
 iterations has been reached. This process is visualized in
@@
 they have tried each behavior, $c_{ib} = 0$ (Figure~\ref{fig:schematic}A).
-At generation start, one of the behaviors is set to 
-yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
+One of the behaviors is chosen at random to yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
 expected payoffs $\pilow$. Agents are independently randomly initialized with $s_i
-\in 0,1$.
+\in 0,1$, so that 50\% of the initial population learn socially.
 
@@
 independently (Figure~\ref{fig:schematic}B).
-Agents make one choice for each step in its lifespan using softmax weighting
-described above, updating the mean payoffs it has observed along the way. 
-Agents probabilistically recieve a payoff of 0 or 1 depending on whether the
-bandit paid off. Behavior payoffs are drawn from a 
-Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from
-behavior $b$.  For concreteness we denote this probabilistic payoff
-$\bandit$. After performing behavior $b$, agent $i$ updates the
+Each agent selects one behavior on each step of its lifespan using softmax process
+described above, updating the mean payoffs it has observed after each time step. Agent $i$ using behavior $b$ receives a payoff of 1 with probability $\pi_b$. 
+%Agents probabilistically recieve a payoff of 0 or 1 depending on whether the bandit paid off.
+Behavior payoffs are drawn from a Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from behavior $b$.
+For concreteness we denote this probabilistic payoff $\bandit$.
+After performing behavior $b$, agent $i$ updates the
 corresponding \emph{behavior count} by 1, $c_{ib} \leftarrow c_{ib} + 1$, and then
@@
 \begin{equation}
-  \ledger \leftarrow \ledger + \frac{\bandit - \ledger}{c_{ib}}.
+  \ledger \leftarrow \ledger + \frac{\bandit - \ledger}{c_{ib}},
 \end{equation}
 \noindent
+where $\bandit$ is the actual payoff received by agent $i$ for behavior $b$ on the given time step.
 
 \paragraph{Intergenerational dynamics}
-Between generations, agents first reproduce via asexual haploid reproduction; 
-then new child agents learn from the
-previous generation if they are social learners; and finally all agents from the
-previous generation then die off (Figure~\ref{fig:schematic}C). 
+Between generations, agents first reproduce via asexual haploid reproduction, which determines the transmission of the social learning trait. Social learners then learn from the
+previous generation, after which all agents from the
+previous generation die off (Figure~\ref{fig:schematic}C). More specifically, this all happens as follows. 
 $N$ reproducers are selected with replacement over $N$ independent draws, 
@@
 A social learner child with $s_i = 1$ learns from a teacher from its parent's
-generation, including possibly their parent (oblique learning). 
-A child selects its teacher by first selecting $N_T$ prospective
-teachers from the population completely at random, then selecting the one with
-highest net payoffs $\pi_i$ as their teacher, with ties broken randomly. While it
-is somewhat arbitrary to first subset $N_T$, this is a conservative choice that
-represnts the fact that access to the entire population is not generally guaranteed.
-Social learners adopt their chosen teacher's expected payoffs observations $\ledger$,
-and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$.  Asocial
+generation, including possibly their parent (i.e., both vertical and oblique learning are possible). 
+A child chooses its teacher by first randomly selecting $N_T$ prospective
+teachers from the population, then selecting the one with
+highest net payoffs $\pi_i$ as their teacher, with ties broken randomly \cm{this seems to contradict info under 2.2.2 Social learning section where there seems to be a probabilistic element weighted by relative payoff of teachers.
+I think it doesn't have to be described in both places.}.
+By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \cite{smaldino2019open}.
+Social learners adopt their chosen teacher's expected payoffs observations $\ledger$, \ps{I feel like there should be some indication that the ledger is a vector rather than a scalar.
+Maybe put it in bold or capitalize the $\Pi$?
+Using the overbar makes it look like a single average.}
+and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$.
+Setting $c_{ib}$ to 1 reflects the fact that the social learning is treating the teacher's information as a single observation with the associated uncertainty.
+Asocial
 learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ 
-(Figure~\ref{fig:schematic}C). The
-newly initialized population then repeats within-generation dynamics.
+(Figure~\ref{fig:schematic}C). \ps{How to account for division by zero?} The
+newly initialized population then repeats the within-generation dynamics.
 
@@
 It is rare for simulations not to reach fixation. We report how frequently
-this happens in Table~\ref{tab:convergence}.
+this happens in Table~\ref{tab:convergence}. \ps{Supplementary figures and table should be prefixed with an ``S."}
 
@@
 To analyze the effect of the four principal uncertainty factors, we systematically
-varied uncertainty values and observed how frequently social learning evolved across
-1000 trial simulations. We varied $u \in
-\{0.0, 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$;
-and $L \in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.  We
-observed three outcome measures, with $\meansl$ as the primary measure: 
-the average value of $s_i$ over all agents and trials. To support our conclusions
-based on $\meansl$, we also measured $\meanpi / L$, the average net 
-payoffs at simulation end across agents and trials, normalized by lifespan; 
+varied uncertainty values (Table~\ref{tab:modelParameters}) and observed how frequently social learning evolved across
+1000 trial simulations for each combination of parameters tested.
+%We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L \in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.
+We observed three outcome measures, with $\meansl$ as the primary measure: the average value of $s_i$ over all agents and trials. To support our conclusions
+based on $\meansl$, we also measured $\meanpi / L$, the average net  payoffs at simulation end across agents and trials, normalized by lifespan; 
 and $\meanG$, the mean
-number of generations to fixation. We analyze outcomes by
-plotting $\meansl$ on the y-axis and environmental variation is on x-axis since we
+number of generations to fixation (see Table~\ref{tab:outcomeVariables}). We analyze outcomes by plotting $\meansl$ on the y-axis and environmental variation is on x-axis since we
 theoretically expect that $\meansl$ will decrease monotonically from 1 to 0 as $u$
-increases. Note that the hypothesis-testing concept of significance is meaningless
-here because we could make any small outcome difference ``significant'' by running
-more simulation trials.  We instead study the patterns of outcome variables over
-systematically varied uncertainty factor values.
+increases.
+%Note that the hypothesis-testing concept of significance is meaningless here because we could make any small outcome difference ``significant'' by running more simulation trials.
+We instead study the patterns of outcome variables over systematically varied uncertainty factor values.
 
@@
 We performed sensitivity analyses to ensure that our main analysis is reasonably
-robust to a range of auxiliary parameters. First,
-we varied the population size, $N$, to explore whether smaller $N$ would 
-show more drift due to finite population size effects, but also generally support
-our main conclusions. Next, we varied the
-number of prospective teachers, $N_T \in \{2, 10, 20\}$, 
-to supplement the main results that used $N_T = 5$. The number of prospective
-teachers should not change whether social learning is optimal, 
-but it may induce more drift since the benefit of social learning may
+robust to a range of auxiliary parameters.
+\ps{Say these are presented in the supplementary material?} First, we varied the population size, $N$, to explore whether smaller $N$ would show more drift due to finite population size effects.
+%, but  still generally support our main conclusions.
+Next, we varied the number of prospective teachers, $N_T \in \{2, 10, 20\}$, to supplement the main results that used $N_T = 5$. The number of prospective
+teachers should not change whether social learning is optimal, but it may induce more drift since the benefit of social learning may
 be more difficult to detect with fewer prosopective teachers. Finally, we varied the
@@
 on the Sherlock supercomputing cluster at Stanford University. Model code and
-data are publicly available on GitHub\footnote{\url{https://github.com/mt-digital/UncMod}}.
+data are publicly available on GitHub at \url{https://github.com/mt-digital/UncMod}.
 
@@
 
-To understand how different forms of uncertainty interact to affect the evolution of
-social learning, we measured how frequently social learning evolved across
-uncertainty parameters. We analyzed outcomes by plotting the mean observed social
-learning frequency, $\meansl$, with mean taken across all 1000 agents and 1000
-simulation trials for each uncertainty parameter setting at model fixation.
-% This is convenient because we are most certain about how $\meansl$ depends on $u$:
-% we expect $\meansl$ to decrease as $u$ increases since environmental variability
-% is well understood to cause socially-transmitted information to become outdated. 
-% To inspect patterns in $\meansl$ over all uncertainty parameters, 
-We analyze nine plots of how $\meansl$ (y-axis in each plot) changes over 
-environmental variability, $u$ (x-axis),
-in a $3\times3$ plot array (Figure~\ref{fig:mainResults}). 
-% All plots show how $\meansl$ changes (y-axis)
-% with environmental variability, $u$ (x-axis). 
-Selection set size, $B$, increases from left to right in the plot array (columns). 
-Payoff ambiguity increases as the non-optimal payoff, $\pilow$, increases from 
-top to bottom in the array (recall $\pihigh=0.9$ for all analyses).
-Effective lifespan, $L$, is indicated by line and marker colors (inset). 
-Several patterns in social learning prevalence emerged as 
-these uncertainty parameters were varied (Figure~\ref{fig:mainResults}).
-
-First, we confirmed existing theoretical predictions that increased $u$
-monotonically decreased $\meansl$ across all other uncertainty parameter values.
-The other uncertainty parameters changed the $u$ value at which $\meansl$
-began to decrease, and how rapidly $\meansl$ decreased over $u$.  For example,
-when payoff ambiguity and selection set size were both small ($\pilow = 0.1$
-and $B=2$), social learning evolved only when $u$ was small. 
-% These parameter settings present a relatively easy problem for individuals.
-% Furthermore, it is relatively costly for agents to be misled by outdated
-% social information in this case, especially for longer lifespans for finding
-% the optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
-When $\pilow = 0.8$ and $B=2$, for exapmle, $\meansl$ decreased less rapdily
-over $u$ due to drift caused by weak selection due to little advantage for
-performing the optimal versus non-optimal behavior (see rows of
-Figure~\ref{fig:mainResults}). We analyzed several such patterns of social
-learning evolution and suppression across different uncertainty settings.
-
-Increased selection set size $B$ led nearly uniformly to more prevalent social
-learning, with all other uncertainty parameters held constant. This is because, first,
-it is more difficuilt to find the optimal behavior with a larger $B$.  Second, this
-effect is amplified because agents in a world with larger $B$ are more cognitively
-flexible compared to those in a smaller $B$ world.  When $B$ is larger, agents are
-relatively more likely to choose an alternative to their current known optimum.  To
-understand this, consider the case where a social learner child learns that behavior 1
-has an expected payoff of 0.8, and the rest have an expected payoff of 0, but the
-optimal behavior changes between generations. Assume the child tries behavior 1, but
-it pays off 0.  If $B=2$, then at the next time step, $\ledger =
-(0.4, 0.0)$. The probability the agent explores behavior 2 is now 0.02. However, if
-$B=10$ the agent has $\ledger = (0.4, 0.0, \ldots, 0.0)$, and the probability the agent
-explores one of the nine alternative behaviors increases to 0.14.  If the agent again
-tries behavior 1 and it pays 0, the probability of exploring alternatives with $B=2$
-is 0.21, but with $B=10$ the probability of exploring alternatives more greatly increases
-to 0.71. \mt{I double checked these calculations, but would appreciate if someone
-  triple checked it}. 
-This explanation does not apply when $L=1$, where individual learning does not occur.
-
-Payoff ambiguity had a modest effect when $\pilow = 0.1$ increased to $\pilow =
-0.45$, causing social learning to be favored across more values of $u$ (first two rows of
-Figure~\ref{fig:mainResults}).  This is because increased payoff ambiguity increases
-the difficulty, and reduces the overall benefit, of discerning which behavior is
-optimal.  When $\pilow = 0.8$ the
-$\meansl$ curves become smoother, indicating more evolutionary drift towards 
-possibly non-optimal fixations (bottom row of
-Figure~\ref{fig:mainResults}). For smaller values of $u$, this results in less
-frequent evolution of social learning for the same values of $u$ and $B$. But past
-the value of $u$ where $\meansl \approx 0.5$ this switches, and social learning evolves more
-frequently than for smaller $\pilow$. 
-% When $\pilow \to \pihigh$, agents 
-% accumulate increasingly more payoffs, whether they are social learners or not. 
-Greater payoff ambiguity means lower risk to try possibly outdated social
-information by reducing the penalty for performing non-optimal behaviors, leading
-to the observed drift in aggregated results.
-
-We observed two distinct trends in the evolution of social learning as
-$L$ was varied.  First, when $\pilow$ was sufficiently small ($\pilow=0.1, 0.45$),
-we observed that shorter lifespan extended the evolution of social learning over more values of
-$u$, since payoff-biased social learning means teachers are reliable.
-When $\pilow=0.8$, shorter lifespans decreased $\meansl$ in some cases and
-increased $\meansl$ in other cases due to greater evolutionary drift. In
-this setting, many agents will obtain a payoff of 1 at each time step in their 
-lifetime, which, combined with finite population size, will make it more likely for 
-evolution to guide the population to non-optimal social/asocial learning stragegy.
-% In the first
-% case, $\meansl$ was reduced for $L=1$ for small values of $u$, when other $L > 1$
-% led to $\meansl \approx 1$. At larger $u$ , the $L=1$ case yields non-zero
-% $\meansl$, while for the other $L > 1$, $\meansl \approx 0$. 
-Smaller $L$ means agents end their lives more uncertain about which behavior was
-optimal, but payoff-biased teacher selection and learning can remedy this if
-payoff ambiguity is sufficiently small.
-% When $L$ is smaller, agents have fewer opportunities to learn through trial and
-% error, so it is more difficult for them to discern which strategy is optimal, social
-% or asocial.
+% To understand how different forms of uncertainty interact to affect the evolution of
+% social learning, we measured how frequently social learning evolved across
+% uncertainty parameters. We analyzed outcomes by plotting the mean observed social
+% learning frequency, $\meansl$, with mean taken across all 1000 agents and 1000
+% simulation trials for each uncertainty parameter setting at model fixation.
+% % This is convenient because we are most certain about how $\meansl$ depends on $u$:
+% % we expect $\meansl$ to decrease as $u$ increases since environmental variability
+% % is well understood to cause socially-transmitted information to become outdated. 
+% % To inspect patterns in $\meansl$ over all uncertainty parameters, 
+% We analyze nine plots of how $\meansl$ (y-axis in each plot) changes over 
+% environmental variability, $u$ (x-axis),
+% in a $3\times3$ plot array (Figure~\ref{fig:mainResults}). 
+% % All plots show how $\meansl$ changes (y-axis)
+% % with environmental variability, $u$ (x-axis). 
+% Selection set size, $B$, increases from left to right in the plot array (columns). 
+% Payoff ambiguity increases as the non-optimal payoff, $\pilow$, increases from 
+% top to bottom in the array (recall $\pihigh=0.9$ for all analyses).
+% Effective lifespan, $L$, is indicated by line and marker colors (inset). 
+% Several patterns in social learning prevalence emerged as 
+% these uncertainty parameters were varied (Figure~\ref{fig:mainResults}).
+
+Our main results are illustrated by Figure~\ref{fig:mainResults}, which shows the proportion of simulation runs that fixated to 100\% social learners as a function of each of our four uncertainty measures.
+First, we found that reliance on social learning monotonically decreased as temporal environmental variability, $u$, increased.
+When the environment was more likely to change between generations, information learned from the previous was less likely to be of value, decreasing selection on social learning.
+Past some threshold, social learning was not favored at all.
+However, the exact nature of the relationship between social learning and temporal environmental variability was tempered by our other three uncertainty parameters.
+
+Increasing the selection set size, $B$, favored the evolution of social learning.
+With only two behavioral choices ($B = 2$), a common assumption in many models, social learning is actively detrimental when the environment changes due to social learners being biased against the correct choice.
+When the selection set size increased, social learning was favored for two reasons.
+First, when the environment changed, bias against the new optimal was weaker with more behavioral options.
+Second and more importantly, when the environment remains constant between generations, the value of social learning increases with more behavioral options, because random search is less likely to yield useful information under a large search space.
+When the selection set size is very large, social learning is favored under quite high rates of temporal environmental variability.
+
+A shorter effective lifespan, $L$, also favored the evolution of social learning in most cases.
+When effective lifespans are long and there are many opportunities to gather information via individual learning, the value of social transmission is diminished.
+Given enough opportunities, the agents will all learn the optimal behavior eventually.
+Thus, under most conditions, longer effective lifespans led to a more narrow range of the parameters $u$ and $B$ under which social learning was favored.
+It is noteworthy that in many cases, a large increase in the selection regime for social learning could be observed when $L=1$ and by definition no individual learning occurred.
+
+Of the four types of uncertainty studied in this paper, payoff ambiguity had the most complex effect on the evolution of social learning.
+Recall that we operationalize payoff ambiguity with $\pilow$, the expected payoff for non-optimal behaviors (literally the probability that those behaviors yielded a payoff of 1).
+This was relative to $\pihigh = 0.9$, the expected payoff for the optimal behavior.
+When payoff ambiguity was low, non-optimal behaviors rarely paid off, so that exploration yielded reliable information and selection on learning strategies was  strong.
+When payoff ambiguity was very high ($\pilow = 0.8$), two things happened.
+Not only were agents likely to ascribe high value to non-optimal behaviors, but also selection on strategies that did reliably select the optimal behavior was relatively weak.
+This allowed for the effect of drift to become stronger, weakening selection in favor of social learning under small values of $u$ and weakening selection against social learning under high values of $u$.
+This effect was especially strong under other types of uncertainty: more temporal environmental variability, larger selection set sizes, and especially shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
+
+The effect of drift under short effective lifespans and high payoff ambiguity is powerful and complex.
+We explain how selection on social learning responds to these effects in more detail in the following section.
+
+% First, we confirmed existing theoretical predictions that increased $u$ 
+% monotonically decreased $\meansl$ across all other uncertainty parameter values.
+% The other uncertainty parameters changed the $u$ value at which $\meansl$
+% began to decrease, and how rapidly $\meansl$ decreased over $u$.  For example,
+% when payoff ambiguity and selection set size were both small ($\pilow = 0.1$
+% and $B=2$), social learning evolved only when $u$ was small. 
+% % These parameter settings present a relatively easy problem for individuals.
+% % Furthermore, it is relatively costly for agents to be misled by outdated
+% % social information in this case, especially for longer lifespans for finding
+% % the optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
+% When $\pilow = 0.8$ and $B=2$, for exapmle, $\meansl$ decreased less rapdily
+% over $u$ due to drift caused by weak selection due to little advantage for
+% performing the optimal versus non-optimal behavior (see rows of
+% Figure~\ref{fig:mainResults}). We analyzed several such patterns of social
+% learning evolution and suppression across different uncertainty settings.
+
+% Increased selection set size $B$ led nearly uniformly to more prevalent social
+% learning, with all other uncertainty parameters held constant. This is because, first,
+% it is more difficuilt to find the optimal behavior with a larger $B$.  Second, this
+% effect is amplified because agents in a world with larger $B$ are more cognitively
+% flexible compared to those in a smaller $B$ world.  When $B$ is larger, agents are
+% relatively more likely to choose an alternative to their current known optimum.  To
+% understand this, consider the case where a social learner child learns that behavior 1
+% has an expected payoff of 0.8, and the rest have an expected payoff of 0, but the
+% optimal behavior changes between generations. Assume the child tries behavior 1, but
+% it pays off 0.  If $B=2$, then at the next time step, $\ledger =
+% (0.4, 0.0)$. The probability the agent explores behavior 2 is now 0.02. However, if
+% $B=10$ the agent has $\ledger = (0.4, 0.0, \ldots, 0.0)$, and the probability the agent
+% explores one of the nine alternative behaviors increases to 0.14.  If the agent again
+% tries behavior 1 and it pays 0, the probability of exploring alternatives with $B=2$
+% is 0.21, but with $B=10$ the probability of exploring alternatives more greatly increases
+% to 0.71. \mt{I double checked these calculations, but would appreciate if someone
+%   triple checked it}. 
+% This explanation does not apply when $L=1$, where individual learning does not occur.
+
+% Payoff ambiguity had a modest effect when $\pilow = 0.1$ increased to $\pilow =
+% 0.45$, causing social learning to be favored across more values of $u$ (first two rows of
+% Figure~\ref{fig:mainResults}).  This is because increased payoff ambiguity increases
+% the difficulty, and reduces the overall benefit, of discerning which behavior is
+% optimal.  When $\pilow = 0.8$ the
+% $\meansl$ curves become smoother, indicating more evolutionary drift towards 
+% possibly non-optimal fixations (bottom row of
+% Figure~\ref{fig:mainResults}). For smaller values of $u$, this results in less
+% frequent evolution of social learning for the same values of $u$ and $B$. But past
+% the value of $u$ where $\meansl \approx 0.5$ this switches, and social learning evolves more
+% frequently than for smaller $\pilow$. 
+% % When $\pilow \to \pihigh$, agents 
+% % accumulate increasingly more payoffs, whether they are social learners or not. 
+% Greater payoff ambiguity means lower risk to try possibly outdated social
+% information by reducing the penalty for performing non-optimal behaviors, leading
+% to the observed drift in aggregated results.
+
+% We observed two distinct trends in the evolution of social learning as
+% $L$ was varied.  First, when $\pilow$ was sufficiently small ($\pilow=0.1, 0.45$),
+% we observed that shorter lifespan extended the evolution of social learning over more values of
+% $u$, since payoff-biased social learning means teachers are reliable.
+% When $\pilow=0.8$, shorter lifespans decreased $\meansl$ in some cases and
+% increased $\meansl$ in other cases due to greater evolutionary drift. In
+% this setting, many agents will obtain a payoff of 1 at each time step in their 
+% lifetime, which, combined with finite population size, will make it more likely for 
+% evolution to guide the population to non-optimal social/asocial learning stragegy.
+% % In the first
+% % case, $\meansl$ was reduced for $L=1$ for small values of $u$, when other $L > 1$
+% % led to $\meansl \approx 1$. At larger $u$ , the $L=1$ case yields non-zero
+% % $\meansl$, while for the other $L > 1$, $\meansl \approx 0$. 
+% Smaller $L$ means agents end their lives more uncertain about which behavior was
+% optimal, but payoff-biased teacher selection and learning can remedy this if
+% payoff ambiguity is sufficiently small.
+% % When $L$ is smaller, agents have fewer opportunities to learn through trial and
+% % error, so it is more difficult for them to discern which strategy is optimal, social
+% % or asocial.
 
@@
 
-To explain the evolution of social learning we implicitly assumed above that, first,
-the relative benefit of having the social learning trait is essential to its
-evolution; and, second, we assumed that values of $\meansl \neq 0,1$ indicate
-evolutionary drift---but do our data support these assumptions?  Indeed, we found that
-social learning evolution and evolutionary drift depended on the relative benefit of
-the social learning trait. We measured drift in terms of the average number of
-generations to fixation, denoted $\langle G \rangle$. Indeed, social learning
-evolution and drift are reflected in the relative benefit of social learning to
-asocial learning.  When social and asocial learning are equally beneficial, fixation
-takes longer to achieve, indicating greater drift.
+% To explain the evolution of social learning we implicitly assumed above that, first,
+% the relative benefit of having the social learning trait is essential to its
+% evolution; and, second, we assumed that values of $\meansl \neq 0,1$ indicate
+% evolutionary drift---but do our data support these assumptions?  
+%Indeed, w
+The effect of drift on the evolution of social learning %evolution and evolutionary drift 
+depended on the extent to which the social learning trait provided agents with a consistent benefit.
+Drift infuses randomness into natural selection, which can lead a population under a consistent but weak selection pressure to take longer to reach fixation \cite{plutynski2007drift}.
+Drift is maximal when social and asocial learning are equally beneficial and fixation takes longer to achieve.
+We therefore measured drift by the average number of generations to fixation, denoted $\langle G \rangle$, where fixation means that $\sum_i s_i$ is equal to either zero or $N$.
+%Indeed, social learning evolution and drift are reflected in the relative benefit of social learning to asocial learning.
 
@@
 In the case of $L=1$ we can calculate $\meanasoc$ directly: it is just the expected
-payoff across all bandits. When $L=8$, and for all uncertainty parameters for
-$\meansoc$, we calculate expected social and asocial payoffs by respectively setting
-$\sum_i = N$ or $\sum_i = 0$ at model initialization. These stay constant since we do
-not allow for mutation.  
-In general, we observed that social learning evolved when its expected payoffs
-(Figure~\ref{fig:payoffs}, diamond-dash lines) exceeded expected individual-learner
-payoffs (Figure~\ref{fig:payoffs}, long-dashed lines). 
+payoff across all behaviors. For all other cases, we calculate expected social and asocial payoffs by respectively setting
+$\sum_i s_i = N$ or $\sum_i s_i = 0$ at model initialization.
+These stay constant since we do not allow for mutation.
+These are the payoffs to a homogeneous population of either all social learners or all asocial learners.
+Figure~\ref{fig:payoffs} shows these expected payoffs, normalized by effective lifespan $L$), as well as the observed average payoffs in our simulations.
+\ps{Is this right?
+I'm having trouble understanding what the solid lines in Figs 3 and 5 are.
+I'm also debating the wisdom of separating these figures.
+Maybe we put the 3x3 back in for Fig 3?}
+In general, we observed that social learning evolved in our simulations when the expected payoffs exceeded expected individual-learner
+payoffs (Figure~\ref{fig:payoffs}). 
 However, we also found that populations of initially all social learners performed worse
@@
 especially when $\pilow = 0.8$ 
-(Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row).
+(Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row). \ps{What is the point of this last finding? I'm having trouble figuring out what all this has to do with drift.}
 
 \begin{figure}
-  \caption{Comparison of expected payoffs from our computational anaysis (solid
-    lines with circles), expected individual payoffs with no social learning
-    (dashes without markers), and expected payoffs for all-social learner 
-    populations. Only four plots shown to enhance detail; see supplement for
+  \caption{Expected payoff rates for homogeneous populations of social or asocial learners.
+Dashed lines with no markers are expected payoff rates for a population of individual learners.
+Dashed lines with diamond markers are expected payoff rates to a population of social learners.
+Solid lines with circle markers are the actual average payoff rates for agents in our evolutionary simulations.
+%  Comparison of expected payoffs from our computational anaysis (solid     lines with circles), expected individual payoffs with no social learning     (dashes without markers), and expected payoffs for all-social learner     populations.
+Only four plots are shown to enhance detail; see supplement for
     five additional plots.
@@
 
-We confirmed that drift increased when $\meansl$ transitioned from 1 to 0, 
-and when $\pilow$ was increased (Figure~\ref{fig:steps}). 
-We measured drift by the average number of 
-generations to fixation, $\meanG$. Recall fixation is defined as the population
-becoming homogenous, composed of all social or all asocial learners. 
+Figure~\ref{fig:steps} shows the average time to fixation, $\meanG$, for all our our uncertainty parameters.
+We confirmed that drift increased when $\meansl$ was furthest from either 0 or 1 (that is, when fixation to either extreme was possible),
+and when the payoff ambiguity $\pilow$ was increased (Figure~\ref{fig:steps}). 
+%We measured drift by the average number of generations to fixation, $\meanG$. Recall fixation is defined as the population becoming homogenous, composed of all social or all asocial learners. 
 $\meanG$ peaks around the values of $u$ 
@@
 
-By disambiguating and organizing various operationalizations of uncertainty
-into a single computational model, we developed a more nuanced theoretical
-understanding of how different forms of uncertainty interact to affect the
-evolution of social learning.  We reviewed and distilled several empirical
-and theoretical models in the literature along four uncertainty dimensions:
-temporal environmental uncertainty, selection set size, ambiguous payoffs, and
-effective lifespan.  The model reproduced classic predictions that social
-learning can yield higher payoffs than individual learning when uncertainty is
-sufficiently limited. We found increased
-payoff ambiguity and lifespan led to greater drift, which is essentially
+By disambiguating various formalizations of uncertainty in a single computational model, we have developed a more nuanced theoretical understanding of how uncertainty affects the evolution of social learning.
+%We reviewed and distilled several empirical and theoretical models in the literature along four uncertainty dimensions: temporal environmental uncertainty, selection set size, ambiguous payoffs, and effective lifespan.
+We reproduced the well-known results that the uncertainty derived from a temporally variable environment can favor the evolution of social learning up the point where environmental change is simply too rapid for intergenerational transmission to be of value.
+Importantly, we also showed that this relationship is affected by other sources of uncertainty.
+%Our model reproduced classic predictions that social learning can yield higher payoffs than individual learning when uncertainty is sufficiently limited. 
+We found that larger selection sets, shorter effective lifespans, and increased payoff ambiguity could all favor the evolution of social learning.
+However, these effects were not always straightforward.
+Increased payoff ambiguity and decreased effective lifespan afforded a greater role for drift, which is essentially
 evolutionary uncertainty in a finite-size population.
-Our model helped us understand that social
-learning acts as a scaffold for individual learning---they are not opposites. 
-We endowed agents
-with an evolutionarily- and biologically-plausible individual learning
-mechanism, softmax search, that provided strong individual
-learning that helped agents recover
-from receiving outdated information. This enabled the evolution of social learning 
-even when social information is likely outdated. 
-Detailed theoretical
-models like this are critical for predicting how humans might adapt to an 
-uncertain and rapidly changing world.
-This knowledge could help suggest plausibly beneficial interventions to mitigate 
-existential threats~\cite{Moya2020,Jones2021}, especially in
-the most vulnerable communities~\cite{McNamara2020}, and to capitalize on new
-behavioral opportunities such as transitioning to clean energy use and
+When the ability to learn individually is also fraught with uncertainty, selection either for or against social learning may be substantially weakened.
+
+Our model helps to demonstrate that social learning can act as a scaffold for individual learning---despite the framing of many other papers, they are not opposites. 
+We endowed agents with a biologically-plausible individual learning mechanism, softmax search.
+This allowed for highly successful individual learning that helped agents recover from the potential cost of receiving outdated information.
+This in turn enabled the evolution of social learning
+even when social information was likely to be outdated. 
+Detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly changing world.
+Such understanding could help suggest plausibly beneficial interventions to mitigate existential threats~\cite{Moya2020,Jones2021}, especially in
+the most vulnerable communities~\cite{McNamara2020}, and to capitalize on new behavioral opportunities such as transitioning to clean energy use and
 production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
 
-Our modeling choices were judiciously made to address the main question of how
-uncertainty affects the evolution of social learning in general; however there exist
-alternative empirically-valid choices that could help further develop a more nuanced
-theory of social learning.  Our model necessarily made simplifying assumptions that
-may not always hold in more specific situations, though they are empirically justified
-to be general across taxa. First, note that we only considered success-biased
-learning, although conformity is sometimes the dominant social learning
-mechanism~\cite{Muthukrishna2016a,Smaldino2018b}.  Conformity may lead to more drift
-overall, since success-biased teacher selection, which we assumed, maximizes the
-potential benefit to social learners. We assumed that the number of behaviors and
-their payoffs were constant, but this fails to account for evolutionary feedback which
+Our model necessarily made simplifying assumptions.
+These choices were judiciously made to address the main question of how uncertainty affects the evolution of social learning in general; however there exist alternative empirically-valid choices we could have made, the future exploration of which will be important to the development of a more nuanced theory of social learning.
+% that may not always hold in more specific situations, though they are empirically justified to be general across taxa.
+For example, we considered only success-biased
+learning, although conformity or other context biases may sometimes be the social learning mechanism~\cite{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.  Conformity may lead to more drift
+overall, since success-biased teacher selection, which we assumed, maximizes the potential benefit to social learners. We also assumed that the number of behaviors and
+their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which
 creates new behavioral opportunities as time progresses, e.g.\ via niche
@@
 in-group learners~\cite{Jackson2012}. We assumed agents choose behaviors via softmax
-search, but this is an underpowered algorithm compared to human individual
-learning~\cite{Schulz2020a,Wu2022}.  More powerful individual learning could further
-support social learning.  These considerations reveal new opportunities to enhance
-theoretical nuance by adjusting or extending the present model for other contexts.
-
-\subsection{Conclusion}
-
-We found that the evolution of social learning, even under only a few modest 
-assumptions, is a complex phenomenon, dependent on several interrelated factors. 
-By systematically
-identifying and operationalizing common theoretical assumptions about contextual
-uncertainty in social learning models, we developed a more systematic
+search, but this is an underpowered algorithm compared to the real human individual learning~\cite{Schulz2020a,Wu2022}.  More powerful individual learning could further
+support social learning.  These considerations reveal new opportunities to enhance theoretical nuance by adjusting or extending the present model for other contexts.
+
+%\subsection{Conclusion}
+
+%We found that the 
+The evolution of social learning is a complex phenomenon, dependent on many interrelated factors.
+Although social learning is widely studied, few studies have previously examined how various environmental variables contributing to uncertainty interact.
+By carefully identifying and operationalizing common theoretical assumptions about contextual uncertainty in social learning models, we developed a more systematic
 understanding of which uncertainty factors interact to determine whether social
@@
 information, we saw that social learning could evolve even if social learning
-regularly provides outdated information. This work informs most directly our current
-understanding of the evolution of social learning, but has broader significance for
-understanding problem solving under uncertainty. Our model and its software
-implementation were designed to be modular and extensible.  Indeed, we plan to extend
-this model to further develop a more detailed theoretical understanding of the
-evolution of social learning; we hope others will, too.
+regularly provides outdated information. This work most directly informs our current understanding of the evolution of social learning, but also has broader significance for
+understanding problem solving under uncertainty. \ps{What is this significance? Can't just leave that dangling. I also cut the bit about what comes next. No need for spoilers.} 
+%Our model and its software implementation were designed to be modular and extensible.
+Indeed, we plan to extend this model to further develop a more detailed theoretical understanding of the evolution of social learning; we hope others will, too.
 
@@
 \section{Additional main figure: Full net payoff comparison for all nine uncertainty conditions} 
-
+\ps{This should be part of the supplement. Also, all supplementary figures and tables should be preceded by ``S".}
 In the main text we showed a $2\times2$ array of plots comparing the observed
@@
 \begin{figure}
-  \caption{Comparison of expected payoffs from our computational anaysis (solid
-    lines with circles), expected individual payoffs with no social learning
-    (dashes without markers), and expected payoffs for all-social learner 
-    populations. When $\pilow = 0.8$, all-social learner populations underperform
+  \caption{Expected payoff rates for homogeneous populations of social or asocial learners.
+Dashed lines with no markers are expected payoff rates for a population of individual learners.
+Dashed lines with diamond markers are expected payoff rates to a population of social learners.
+Solid lines with circle markers are the actual average payoff rates for agents in our evolutionary simulations.
+When $\pilow = 0.8$, all-social learner populations underperform
     since social learners are not subject to an initial evolutionary bottleneck

### 2022-08-25 ms.tex
updated convergence in ms, updated expected payoffs component figs
updated figure 5->3 and did supplement S tables and figs

@@
 payoffs (Figure~\ref{fig:payoffs}). 
-However, we also found that populations of initially all social learners performed worse
-in many uncertainty contexts than either the actual payoffs accumulated by 
-model agents, and lower than even the expected individual-level payoffs,
-even though social learning evolved in many of the same contexts in our model,
-especially when $\pilow = 0.8$ 
-(Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row). \ps{What is the point of this last finding? I'm having trouble figuring out what all this has to do with drift.}
+% However, we also found that populations of initially all social learners performed worse
+% in many uncertainty contexts than either the actual payoffs accumulated by 
+% model agents, and lower than even the expected individual-level payoffs,
+% even though social learning evolved in many of the same contexts in our model,
+% especially when $\pilow = 0.8$ 
+% (Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row). \ps{What is the point of this last finding? I'm having trouble figuring out what all this has to do with drift.}
+
+% \begin{figure}
+%   \caption{Expected payoff rates for homogeneous populations of social or asocial learners.
+Dashed lines with no markers are expected payoff rates for a population of individual learners.
+Dashed lines with diamond markers are expected payoff rates to a population of social learners.
+Solid lines with circle markers are the actual average payoff rates for agents in our evolutionary simulations.
+% %  Comparison of expected payoffs from our computational anaysis (solid     lines with circles), expected individual payoffs with no social learning     (dashes without markers), and expected payoffs for all-social learner     populations.
+% Only four plots are shown to enhance detail; see supplement for
+%     five additional plots.
+% } 
+%   \label{fig:payoffs}
+% \centering
+%     \includegraphics[width=0.85\textwidth]{Figures/meanNetPayoffs.pdf}
+% \end{figure}
 
@@
 Solid lines with circle markers are the actual average payoff rates for agents in our evolutionary simulations.
-%  Comparison of expected payoffs from our computational anaysis (solid     lines with circles), expected individual payoffs with no social learning     (dashes without markers), and expected payoffs for all-social learner     populations.
-Only four plots are shown to enhance detail; see supplement for
-    five additional plots.
+When $\pilow = 0.8$, all-social learner populations underperform
+    since social learners are not subject to an initial evolutionary bottleneck
+    due to the presence of asocial learners, and behavioral misinformation
+    is allowed to circulate more freely than in the base case tested by 
+    our model with an initially even distribution of social and asocial learners.
+    \mt{Correct or nah?}
 }
@@
   \centering
-    \includegraphics[width=0.85\textwidth]{Figures/meanNetPayoffs.pdf}
+    \includegraphics[width=\textwidth]{Figures/supplement/fullMeanPrevNetPayoffs.pdf}
 \end{figure}
@@
 evolution of social learning since successful outgroup teachers could be cut off from
-in-group learners~\cite{Jackson2012}. We assumed agents choose behaviors via softmax
+in-group learners~\cite{Golub2012}. We assumed agents choose behaviors via softmax
 search, but this is an underpowered algorithm compared to the real human individual learning~\cite{Schulz2020a,Wu2022}.  More powerful individual learning could further
@@
 
-\appendix
-
-\section{Additional main figure: Full net payoff comparison for all nine uncertainty conditions} 
-\ps{This should be part of the supplement. Also, all supplementary figures and tables should be preceded by ``S".}
-In the main text we showed a $2\times2$ array of plots comparing the observed
-mean net payoffs obtained by agents in our simulations, and in two auxiliary
-sets of simulations that set all agents to either have the social learning
-trait or not, which remained the case for the entire simulation since there
-are no mutations in this model (Figure~\ref{fig:payoffs}). Here we show the full $3\times3$ array of
-all $(\pilow, B)$ combinations shown for the main results. We see that
-populations of all social learners especially underperform initially mixed
-populations that evolve to be social learners 
-(Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row). This highlights the
-importance of diversity for behavioral optimization, even if it is transient.
-
-\begin{figure}
-  \caption{Expected payoff rates for homogeneous populations of social or asocial learners.
-Dashed lines with no markers are expected payoff rates for a population of individual learners.
-Dashed lines with diamond markers are expected payoff rates to a population of social learners.
-Solid lines with circle markers are the actual average payoff rates for agents in our evolutionary simulations.
-When $\pilow = 0.8$, all-social learner populations underperform
-    since social learners are not subject to an initial evolutionary bottleneck
-    due to the presence of asocial learners, and behavioral misinformation
-    is allowed to circulate more freely than in the base case tested by 
-    our model with an initially even distribution of social and asocial learners.
-}
-  \label{fig:fullMeanPrevNetPayoffs}
-  \centering
-    \includegraphics[width=\textwidth]{Figures/supplement/fullMeanPrevNetPayoffs.pdf}
-\end{figure}
-
-\newpage
-
-\section{Supplemental supporting information}
+%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
+\pagebreak
+\begin{center}
+  \textbf{\Large \textsf{Supplement}}
+\end{center}
+%%%%%%%%%% Merge with supplemental materials %%%%%%%%%%
+%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
+\setcounter{equation}{1}
+\setcounter{figure}{0}
+\setcounter{section}{0}
+\setcounter{table}{0}
+\setcounter{page}{1}
+\makeatletter
+\renewcommand{\theequation}{S\arabic{equation}}
+\renewcommand{\thefigure}{S\arabic{figure}}
+\renewcommand{\thetable}{S\arabic{table}}
+\renewcommand{\thesection}{S\arabic{section}}
+\renewcommand{\thepage}{S\arabic{page}}
+% \renewcommand{\bibnumfmt}[1]{[S#1]}
+% \renewcommand{\citenumfont}[1]{S#1}
+%%%%%%%%%% Prefix a "S" to all equations, figures, tables and reset the counter %%%%%%%%%%
+
+% \section{Additional main figure: Full net payoff comparison for all nine uncertainty conditions} 
+% \ps{This should be part of the supplement. Also, all supplementary figures and tables should be preceded by ``S".}
+% In the main text we showed a $2\times2$ array of plots comparing the observed
+% mean net payoffs obtained by agents in our simulations, and in two auxiliary
+% sets of simulations that set all agents to either have the social learning
+% trait or not, which remained the case for the entire simulation since there
+% are no mutations in this model (Figure~\ref{fig:payoffs}). Here we show the full $3\times3$ array of
+% all $(\pilow, B)$ combinations shown for the main results. We see that
+% populations of all social learners especially underperform initially mixed
+% populations that evolve to be social learners 
+% (Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row). This highlights the
+% importance of diversity for behavioral optimization, even if it is transient.
+
+% \newpage
 
@@
 
-\subsection{Convergence information}
+\section{Convergence information}
 
@@
     \toprule $B$ & \# not at fixation (out of 132k) & \% not fixated \\ 
-    \midrule  2  & 192  & 0.1 \% \\ 
-              4  & 274  & 0.2 \% \\ 
-              10 & 2935 & 2.0 \% \\ 
+    \midrule  2  & 0  & 0.0 \% \\ 
+              4  & 0  & 0.0 \% \\ 
+              10 & 20 & 0.02 \% \\ 
     \bottomrule \end{tabular} 
@@
 
-\subsection{Population size sensitivty analysis}
+\section{Population size sensitivty analysis}
 
@@
   \centering
-  \addtocounter{figure}{-1}
+  % \addtocounter{figure}{-1}
   \caption{
@@
 
-\subsection{Number of prospective teachers sensitivty analysis}
+\section{Number of prospective teachers sensitivty analysis}
 
@@
   \centering
-  \addtocounter{figure}{-1}
+  % \addtocounter{figure}{-1}
   \caption{Number of prospective teachers sensitivity analysis for $N_T=2,10,20$. Recall
@@
 
-\subsection{Softmax parameter sensitivity analysis}
+\section{Softmax parameter sensitivity analysis}
 
@@
   \caption{Sensitivity analysis of the main results for the softmax parameter $\beta = 100$ and
-  \addtocounter{figure}{-1}
+  % \addtocounter{figure}{-1}
   $\beta=1$. Recall the main results were obtained with $\beta = 10$.}

### 2022-08-25 ms.tex
addressed some comments in model

@@
 The behavior set is a multi-armed bandit with $B$ arms, that is, agents can pick one of $B$ behaviors with random-valued payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
-\ps{To clarify terminology, the entire set of behaviors is one multi-armed bandit with $B$ arms -- each behavior is not itself a bandit.}
-%Each behavior yields a payoff of either 1 or 0 with some probability that is held fixed within a generation but can change between generations.
-This probability is therefore equal to the behavior's expected payoff within a generation.
 In each generation, exactly one behavior is more likely to pay off than all the rest and is therefore optimal. Agents
@@
 At the end of each
-generation, agents are selected with replacement to reproduce a new generation of $N$ agents, with the probability of reproduction biased by net payoffs.
-Agents who inherit the social learning trait learn about payoffs from the previous generation, while asocial learners begin life with no \emph{a priori}
-knowledge of the world. \cm{or would you consider having flat priors over all behaviors knowledge?}  
+generation, agents are selected with replacement to reproduce a new generation of $N$ agents,
+with the probability of reproduction biased by net payoffs. Agents who inherit the social
+learning trait learn about payoffs from the previous generation, while asocial learners begin
+life only knowing the number of behaviors the environment affords, but no knowledge
+of behavioral payoffs.
+\cm{or would you consider having flat priors over all behaviors knowledge?} 
+\mt{I changed this last sentence to express that they have flat priors, in somewhat different
+terms.}
 %The specifics of the model construction and dynamics are described in detail below.
-\ps{I cut a bunch of stuff that came right here as being redundant or unnecessary.}
+% \ps{I cut a bunch of stuff that came right here as being redundant or unnecessary.}
 
@@
 By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \cite{smaldino2019open}.
-Social learners adopt their chosen teacher's expected payoffs observations $\ledger$, \ps{I feel like there should be some indication that the ledger is a vector rather than a scalar.
-Maybe put it in bold or capitalize the $\Pi$?
-Using the overbar makes it look like a single average.}
+Social learners adopt their chosen teacher's expected payoffs observations $\ledger$, \ps{I feel
+like there should be some indication that the ledger is a vector rather than a scalar. Maybe put
+it in bold or capitalize the $\Pi$? Using the overbar makes it look like a single average.}
+\mt{The subscript $b$ makes it clear it's a vector over behaviors. Maybe we lose the bar,
+or I may change the notation to at least approximately follow Q-learning notation.}
 and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$.
@@
 learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ 
-(Figure~\ref{fig:schematic}C). \ps{How to account for division by zero?} The
+(Figure~\ref{fig:schematic}C). \ps{How to account for division by zero?} \mt{Count increases
+before average are taken, which I think is clear enough in paragraph \textbf{Within-generation
+dynamics}.} The
 newly initialized population then repeats the within-generation dynamics.
@@
 It is rare for simulations not to reach fixation. We report how frequently
-this happens in Table~\ref{tab:convergence}. \ps{Supplementary figures and table should be prefixed with an ``S."}
+this happens in Table~\ref{tab:convergence}.
 

### 2022-08-25 ms.tex

@@
 \begin{abstract} 
-  Social learning is %essential to human survival---it 
+  Social learning %essential to human survival---it 
   is a critical
@@
   environmental variability, ambiguous payoffs, decision set size, and effective
-  lifespans. We embed this framework in an evolutionary agent-based model to study conditions for the evolution of  social learning in populations with cognitively realistic individual learning
+  lifespans. We embed this framework in an evolutionary agent-based model to study conditions for the evolution of social learning in populations with cognitively-realistic individual-learning
   capacities. % We used evolutionary agent-based modeling to track the evolution of social learning versus purely individual learning.
@@
   uncertainty had different effects. Temporal environmental variability suppressed
-  social learning. Larger decision set sizes promoted social learning even
+  social learning, whereas larger decision-set size promoted social learning even
   when the environment changed frequently. Payoff
@@
 efficient than learning on one's own~\cite{Laland2004}. However, social learning can also
-lead individuals astray if they are copying irrelevant or outdated information.
+lead individuals astray if they are copying irrelevant, misleading, or outdated information.
 Theoretical models have helped clarify the circumstances under which social learning
-should be evolutionarily favored~\cite{BoydRicherson1985, aoki2014evolution,Kendal2018}, and these models have motivated empirical work that has both validated and refined theoretical predictions concerning social learning behavior in humans
+should be evolutionarily favored~\cite{BoydRicherson1985, aoki2014evolution,Kendal2018}, and these models have motivated empirical work that has both validated and refined theoretical predictions concerning the use of social learning in humans
 and other species~\cite{galef2005social,McElreath2005,Kendal2018,Allen2019}.  This literature
@@
 our long lifespans, cosmopolitan societies, and dispersal across a highly variable environments, requiring coarse-grain and plastic behavioral adaptations \cite{levins1962}.
-However, the term ``uncertainty"
+However, the term ``uncertainty''
 often conflates several different interpretations of that word. For example, different
@@
 conflation. %Furthermore, it can be important to distinguish a narrower definition of uncertainty wherein the probabilities of outcomes remain unknown~\cite{knight1921,volz2012}. 
-As the number of formal models of social learning have expanded, an ever
-increasing number of modeling choices~\cite{Kendal2018} and formalizations of
+As the number of formal models of social learning have expanded, an increasing number of modeling choices~\cite{Kendal2018} and formalizations of
 uncertainty have made it difficult to compare across models or to consolidate our
@@
 %Other (asocial) forms of learning are also likely adaptations to uncertainty that should be accounted for, but are typically glossed over in models.  
-In general, learning is an iterative
-process during which an individual acquires information, forms representations and
-predictions, and then tests and refines those representations and predictions to manage
-uncertainty~\cite{jacobs2011bayesian,clark2013whatever}.  Because cultural evolutionary
+In general, learning is an iterative process during which an individual acquires information, forms representations and predictions, and then tests and refines those representations and predictions to manage uncertainty~\cite{jacobs2011bayesian,clark2013whatever}.
+Because cultural evolutionary
 models are often designed to explain \emph{social} learning mechanisms, they often contrast social learning with an overly simplistic mechanism for individual learning.
@@
 simultaneously operationalizes several forms of uncertainty and endows agents
-with a relatively powerful mechanism for individul learning. We model four kinds of
+with a relatively powerful mechanism for individual learning. We model four kinds of
 uncertainty that are common in cultural evolution models and the related empirical
@@
 their lifespans. The model also assumes a more
-cognitively realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows  learners to make full use of the available data acquired by both individual and social learning.
-Our model design thereby affords us a richer and possibly more accurate assessment of tradeoffs between 
+cognitively-realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows learners to make full use of the available data acquired by both individual and social learning.
+Our model design thereby affords us a richer and possibly more accurate assessment of trade-offs between 
 social and asocial learning. 
@@
 
-\textbf{Temporal environmental variability.} When environments change
-(for example, in response to climatic events, migration, or technological paradigm shifts),
-strategies that were previously adaptive may no longer be optimal. The difficulty
-in predicting either when such shocks will occur or which behaviors will be
-adaptive in the resulting environments leads to uncertainty.
+\textbf{Temporal environmental variability.} When environmental variability is nonstationary (for example, because of climatic events, migration, or technological paradigm shifts), strategies that were previously adaptive may no longer be optimal.
+The difficulty in predicting either when such shocks will occur or which behaviors will be adaptive in the resulting environments leads to uncertainty.
 
@@
 social learning. Such fluctuations have been proposed as an important selective
-pressure for learned as opposed to genetically fixed behaviors when genetic adaptation cannot keep pace with environmental change 
-~\cite{Richerson2000}. On the other hand, environments that change \emph{too} quickly
-will select against social learning so that individuals avoid learning outdated--- 
-and therefore maladaptive---information~\cite{Feldman1996,
+pressure for learned as opposed to genetically fixed behaviors when genetic adaptation cannot keep pace with environmental change~\cite{Richerson2000}.
+On the other hand, environments that change \emph{too} quickly will select against social learning so that individuals avoid learning outdated---and therefore maladaptive---information~\cite{Feldman1996,
 BoydRicherson1985}. This suggests that intermediate levels of temporal variation
@@
 from previous generations. Other models of environmental change introduce less
-uncertainty as they fluctuate between two or more environmental states with corresponding
-adaptive behaviors. This means that previously maladaptive
-behaviors become adaptive when the environment changes
-~\cite{perreault2012bayesian}. The chosen mechanism for modelling temporal
+uncertainty as they fluctuate between two or more environmental states with corresponding adaptive behaviors. This means that previously maladaptive
+behaviors become adaptive when the environment changes~\cite{perreault2012bayesian}. The chosen mechanism for modelling temporal
 change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behavior, and instead considers only behaviors that can be learned.
@@
 \cm{or would you consider having flat priors over all behaviors knowledge?} 
-\mt{I changed this last sentence to express that they have flat priors, in somewhat different
+\mt{I changed this last sentence to express that they have flat priors, in different
 terms.}
@@
 \begin{table}[h]
-\caption{Environmental parameters used in our simulations, including uncertainty parameters $u$, $B$,
+\caption{Environmental Parameters. These include our four main uncertainty parameters under investigation; $u$, $B$,
 $\pilow$, and $L$. Bold indicates default value tested} %\emph{default value tested}.}
@@
 agent is unsure.  To do softmax searching, agents track average payoffs acquired
-from each behavior they have performed and the number of times they
+from each behavior they have performed, which requires knowing the number of times they
 have performed each behavior.
-\cm{is the previous sentence still right?
-I changed it's meaning because it made it sound like tracking average meant keeping track of total number of times it was performed, but that's not inherentely the case.
-Softmax does BOTH right?
-to estimate certainty.}  We denote the average payoffs obtained by agent $i$
-for behavior $b$ as $\ledger$. We denote the number of times $i$ performed $b$
-as $c_{ib}$ (``$c$'' stands for count). 
-At each time step, agent $i$ performs behavior $b$ with softmax-weighted probability
-\begin{equation}
-  \Pr(\text{Agent $i$ performs behavior $b$}) = 
-    \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}}.
-\end{equation}
-\noindent
-$\beta$ adjusts how frequently agents perform 
-behaviors with high expected payoffs (larger $\beta$) versus how frequently
-agents explore alternative behaviors (smaller $\beta$). %~\cite{McElreath2005}. 
-We used a default value of $\beta = 10$, but also varied this value in our sensitivity analyses. 
-The softmax function used here is a biologically plausible
-generalization of behavior selection under uncertainty that enables agents to often
-greedily exploit the most lucrative behavior (based on their observations) but also
-to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
+The probability that the agent will perform a behavior is a function of the agent's beliefs about a behavior's average payoff in that timestep and a fixed parameter that influences the amount of exploratory behavior (more details below).
+The softmax function used here is a biologically plausible generalization of behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative behavior (based on their observations) but also to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
 
@@
 %, if the child inherited $s_i = 1$. A child agent $c$ is a social learner if its parent $p$ was a social learner, i.e.\ $s_c \leftarrow s_p$, without mutation.
-A social learner  
-selects this ``teacher" from the previous generation by first selecting $N_T$ prospective teachers at random, then selects its teacher from this set with a probability weighted by each prospective teacher's net payoff
-relative to the other $N_T - 1$ prospective teachers.
-The social learner then inherits information about the likely payoffs of each behavior from the teacher, whereas asocial learners do not acquire this information.
-\cm{I think this inheritance has to be explained more.
-(I see that you do this later, so maybe it can be cut back here)} In this way, the social learner can potentially reduce the amount of exploration needed to both execute and learn about the optimal behavior.
+A social learner selects this ``teacher" from the previous generation by first choosing a random subset of the population and choosing among these with a probability weighted by each model's payoff (more details below).
+The social learner then inherits information about the likely payoffs of each behavior from that one teacher, whereas asocial learners do not acquire this information.
+In this way, the social learner can potentially reduce the amount of exploration needed to both execute and learn about the optimal behavior.
 
@@
 independently (Figure~\ref{fig:schematic}B).
-Each agent selects one behavior on each step of its lifespan using softmax process
-described above, updating the mean payoffs it has observed after each time step. Agent $i$ using behavior $b$ receives a payoff of 1 with probability $\pi_b$. 
+Each agent selects one behavior on each step of its lifespan using softmax process that integrates previous knowledge. We denote the average payoffs obtained by agent $i$
+for behavior $b$ as $\ledger$. We denote the number of times $i$ performed $b$
+as $c_{ib}$ (``$c$'' stands for count). 
+At each time step, agent $i$ performs behavior $b$ with softmax-weighted probability
+\begin{equation}
+  \Pr(\text{Agent $i$ performs behavior $b$}) = 
+    \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}}.
+\end{equation}
+\noindent
+$\beta$ adjusts how frequently agents perform 
+behaviors with high expected payoffs (larger $\beta$) versus how frequently
+agents explore alternative behaviors (smaller $\beta$). %~\cite{McElreath2005}. 
+We used a default value of $\beta = 10$, but also varied this value in our sensitivity analyses.
+
+Agent $i$ using behavior $b$ receives a payoff of 1 with probability $\pi_b$. 
 %Agents probabilistically recieve a payoff of 0 or 1 depending on whether the bandit paid off.
@@
 A child chooses its teacher by first randomly selecting $N_T$ prospective
-teachers from the population, then selecting the one with
-highest net payoffs $\pi_i$ as their teacher, with ties broken randomly \cm{this seems to contradict info under 2.2.2 Social learning section where there seems to be a probabilistic element weighted by relative payoff of teachers.
-I think it doesn't have to be described in both places.}.
+teachers from the population, then selecting one from this set with a probability weighted by each prospective teacher's net payoff, $\pi_i$,  
+relative to the other $N_T - 1$ prospective teachers, with ties broken randomly.
 By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \cite{smaldino2019open}.
@@
 social or asocial learners (i.e.\ the system reaches fixation), 
-otherwise repeat another generation and evolution (3).}
+otherwise repeat another generation and evolution (3).} \cm{What does (3) denote at end of Fig 1 caption?
+Does having only green agents in Fig1B give the impression that only social learners are learning within lifetime?
+Could the agent be half green/purple?
+Is it weird that in Fig1C a teacher with relatively low payoffs is being selected?
+Could be fixed by having the dotted line go from rich purple women's head to green baby's.
+}
   \label{fig:schematic}
@@
 We observed three outcome measures, with $\meansl$ as the primary measure: the average value of $s_i$ over all agents and trials. To support our conclusions
-based on $\meansl$, we also measured $\meanpi / L$, the average net  payoffs at simulation end across agents and trials, normalized by lifespan; 
+about $\meansl$, we also measured $\meanpi / L$, the average net  payoffs at the end of the simulation across agents and trials, normalized by lifespan; 
 and $\meanG$, the mean
-number of generations to fixation (see Table~\ref{tab:outcomeVariables}). We analyze outcomes by plotting $\meansl$ on the y-axis and environmental variation is on x-axis since we
+number of generations to fixation (see Table~\ref{tab:outcomeVariables}). We analyze outcomes by plotting $\meansl$ on the y-axis and environmental variability is on x-axis since we
 theoretically expect that $\meansl$ will decrease monotonically from 1 to 0 as $u$
@@
 \begin{table}[h]
-    \caption{Outcome variables.}
+    \caption{Outcome Variables. All averages are computed across trials at the end of the last generation.}
     \label{tab:outcomeVariables}
@@
 
-        $\meansl$ & Mean social learning prevalence over agents and trials
+        $\meansl$ & Mean social learning prevalence over agents
                   & $\in [0.0, 1.0]$ \\
 
-        $\meanpi / L$ & Mean payoffs accumulated in a generation normalized by
+        $\meanpi / L$ & Mean payoffs accumulated across agents, normalized by
         lifespan & $\in [0.0, 1.0]$ \\
 
-        $\meanG$ & Mean number of generations to convergence & 20k / 8 max. \\
+        $\meanG$ & Mean number of generations to convergence & 100k / 8 max. \\
         \bottomrule

### 2022-08-29 meanNetPayoffs.tex
updated legend in payoff fig
major figure updates

@@
 \geometry{
-paperwidth=8in,
-paperheight=6.25in,
+paperwidth=12in,
+paperheight=12in,
 margin=0.25in
@@
       \end{center}
-        \end{minipage}\noindent\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+	  \end{minipage}\noindent\hspace{1.25em}
+		\begin{minipage}{3.75in}%
+		  \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
 		  \\[-2.75em]
@@
     \end{minipage}
+	\begin{minipage}{3.75in}%
+		  \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
+		  \\[-2.75em]
+	  \begin{center}
+        {\huge $\quad u$}
+      \end{center}
+    \end{minipage} \\[2.5em]
+
+    \begin{center}
+      \includegraphics[width=1.25in]{Figures/legendElements/solid.pdf}
+      {\Huge Simulations} \quad \quad 
+      \includegraphics[width=1.25in]{Figures/legendElements/ldash.pdf}
+      {\Huge$\meanasoc$} \quad \quad 
+      \includegraphics[width=1.25in]{Figures/legendElements/dot.pdf}
+      {\Huge$\meansoc$} \quad \quad
+      \includegraphics[width=1.25in]{Figures/legendElements/ldashdot.pdf}
+      {\Huge$\meanasoc = \meansoc$}
+    \end{center}
 \end{document}

### 2022-08-29 ms.tex
major figure updates

--- 2022-08-25 ms.tex
@@
 \begin{abstract} 
-  Social learning is %essential to human survival---it 
-  is a critical
+  Social learning is a critical
   adaptation for dealing with uncertainty. However, uncertainty takes many forms.
@@
   lifespans. We embed this framework in an evolutionary agent-based model to study conditions for the evolution of  social learning in populations with cognitively realistic individual learning
-  capacities. % We used evolutionary agent-based modeling to track the evolution of social learning versus purely individual learning.
-  %how often social, rather than individual,   learning evolved. 
+  capacities.  
   Agents could perform one of several behaviors, modeled as multi-armed bandit, to acquire payoffs.
@@
 % to existential threats and new opportunities.
-\footnote{This document contains
-\total{citnum} references.}  
+% \footnote{This document contains
+% \total{citnum} references.}  
 \end{abstract}
@@
   \centering
-    \includegraphics[width=\textwidth]{{Figures/supplement/nagents=1000/mainResultsPlots.pdf}}
+    \includegraphics[width=\textwidth]{Figures/mainResultsPlots.pdf}
 \end{figure}
@@
 
-\begin{figure}
-  \caption{Expected payoff rates for homogeneous populations of social or asocial learners.
-Dashed lines with no markers are expected payoff rates for a population of individual learners.
-Dashed lines with diamond markers are expected payoff rates to a population of social learners.
-Solid lines with circle markers are the actual average payoff rates for agents in our evolutionary simulations.
-When $\pilow = 0.8$, all-social learner populations underperform
-    since social learners are not subject to an initial evolutionary bottleneck
-    due to the presence of asocial learners, and behavioral misinformation
-    is allowed to circulate more freely than in the base case tested by 
-    our model with an initially even distribution of social and asocial learners.
-    \mt{Correct or nah?}
-}
-  \label{fig:payoffs}
-  \centering
-    \includegraphics[width=\textwidth]{Figures/supplement/fullMeanPrevNetPayoffs.pdf}
-\end{figure}
-
 Figure~\ref{fig:steps} shows the average time to fixation, $\meanG$, for all our our uncertainty parameters.
@@
 parameter settings (Figure~\ref{fig:steps}, bottom row).
-
-\begin{figure}
-  \caption{Average number of generations ($\meanG$, y-axes) to fixation . 
-    $\meanG$ increases and peaks around values of $u$ (x-axes) where
-  $\meansoc \approx \meanasoc$. Note the y-axis ticks vary between plots,
-indicating different overall time to fixation for different $(\pilow, B)$
-pairs. Only extremal tested values of $L$ shown for clarity.} 
-  \label{fig:steps}
-\centering
-    \includegraphics[width=\textwidth]{Figures/stepResultsPlots.pdf}
-\end{figure}
 
@@
 
+\section{Expected payoffs}
+\begin{figure}
+  \caption{Expected payoff rates for homogeneous populations of social or asocial learners.
+Dashed lines with no markers are expected payoff rates for a population of individual learners.
+Dashed lines with diamond markers are expected payoff rates to a population of social learners.
+Solid lines with circle markers are the actual average payoff rates for agents in our evolutionary simulations.
+When $\pilow = 0.8$, all-social learner populations underperform
+    since social learners are not subject to an initial evolutionary bottleneck
+    due to the presence of asocial learners, and behavioral misinformation
+    is allowed to circulate more freely than in the base case tested by 
+    our model with an initially even distribution of social and asocial learners.
+    \mt{Correct or nah?}
+}
+  \label{fig:payoffs}
+  \centering
+    \includegraphics[width=\textwidth]{Figures/meanNetPayoffs.pdf}
+\end{figure}
+
+\clearpage
+
+\section{Drift measured by expected generations to fixation}
+\begin{figure}
+  \caption{Average number of generations ($\meanG$, y-axes) to fixation . 
+    $\meanG$ increases and peaks around values of $u$ (x-axes) where
+  $\meansoc \approx \meanasoc$. Note the y-axis ticks vary between plots,
+indicating different overall time to fixation for different $(\pilow, B)$
+pairs. Only extremal tested values of $L$ shown for clarity.} 
+  \label{fig:steps}
+\centering
+    \includegraphics[width=\textwidth]{Figures/stepResultsPlots.pdf}
+\end{figure}
+
+\clearpage
+
 \section{Convergence information}
@@
 	  \caption{$N=100$}
-	  \includegraphics[width=\textwidth]{Figures/mainResultsPlots.pdf}
+	  \includegraphics[width=\textwidth]{Figures/supplement/nagents=100/mainResultsPlots.pdf}
 	\end{subfigure}

### 2022-08-29 ms.tex

--- 2022-08-25 ms.tex
@@
 \begin{abstract} 
-  Social learning %essential to human survival---it 
-  is a critical
+  Social learning is a critical
   adaptation for dealing with uncertainty. However, uncertainty takes many forms.
@@
   environmental variability, ambiguous payoffs, decision set size, and effective
-  lifespans. We embed this framework in an evolutionary agent-based model to study conditions for the evolution of social learning in populations with cognitively-realistic individual-learning
-  capacities. % We used evolutionary agent-based modeling to track the evolution of social learning versus purely individual learning.
-  %how often social, rather than individual,   learning evolved. 
+  lifespans. We embed this framework in an evolutionary agent-based model to study conditions for the evolution of  social learning in populations with cognitively realistic individual learning
+  capacities.  
   Agents could perform one of several behaviors, modeled as multi-armed bandit, to acquire payoffs.

### 2022-08-29 ms.tex
Updates from Overleaf

--- 2022-08-25 ms.tex
@@
 
-        $\meanG$ & Mean number of generations to convergence & 100k / 8 max. \\
+        $\meanG$ & Mean number of generations to convergence & max 100k / 8 \\
         \bottomrule
@@
 teachers should not change whether social learning is optimal, but it may induce more drift since the benefit of social learning may
-be more difficult to detect with fewer prosopective teachers. Finally, we varied the
+be more difficult to detect with fewer prospective teachers. Finally, we varied the
 softmax greediness parameter $\beta \in \{1, 100\}$ to supplement the main results

### 2022-09-14 ms.tex
Updates from Overleaf

@@
 Our main results are illustrated by Figure~\ref{fig:mainResults}, which shows the proportion of simulation runs that fixated to 100\% social learners as a function of each of our four uncertainty measures.
-First, we found that reliance on social learning monotonically decreased as temporal environmental variability, $u$, increased.
-When the environment was more likely to change between generations, information learned from the previous was less likely to be of value, decreasing selection on social learning.
-Past some threshold, social learning was not favored at all.
-However, the exact nature of the relationship between social learning and temporal environmental variability was tempered by our other three uncertainty parameters.
-
-Increasing the selection set size, $B$, favored the evolution of social learning.
-With only two behavioral choices ($B = 2$), a common assumption in many models, social learning is actively detrimental when the environment changes due to social learners being biased against the correct choice.
-When the selection set size increased, social learning was favored for two reasons.
-First, when the environment changed, bias against the new optimal was weaker with more behavioral options.
-Second and more importantly, when the environment remains constant between generations, the value of social learning increases with more behavioral options, because random search is less likely to yield useful information under a large search space.
-When the selection set size is very large, social learning is favored under quite high rates of temporal environmental variability.
-
-A shorter effective lifespan, $L$, also favored the evolution of social learning in most cases.
-When effective lifespans are long and there are many opportunities to gather information via individual learning, the value of social transmission is diminished.
-Given enough opportunities, the agents will all learn the optimal behavior eventually.
-Thus, under most conditions, longer effective lifespans led to a more narrow range of the parameters $u$ and $B$ under which social learning was favored.
-It is noteworthy that in many cases, a large increase in the selection regime for social learning could be observed when $L=1$ and by definition no individual learning occurred.
-
-Of the four types of uncertainty studied in this paper, payoff ambiguity had the most complex effect on the evolution of social learning.
+First, we find that reliance on social learning monotonically decreases as temporal environmental variability, $u$, increases.
+When the environment is more likely to change between generations, information learned from the previous generation is less likely to be of value, decreasing selection for social learning.
+Past some threshold, social learning is not favored at all.
+However, the exact nature of the relationship between social learning and temporal environmental variability is moderated by our other three uncertainty parameters.
+
+The number of behavioral options, i.e., larger $B$, favors the evolution of social learning.
+Increasing the selection set size expands the range of $u$ over which social learning is favored for two reasons.
+First, when the environment remains constant between generations, the value of social learning increases with more behavioral options, because it effectively increases the number of observations that one can learn from by comparing the payoffs of several models.
+In other words, relying $only$ on one's asocial trial and error learning is less likely to yield useful information when the search space is large.
+Second, when the environment changes, bias against the new optimal is weaker with more behavioral options.
+For example, with only two behavioral choices ($B = 2$), a common assumption in many models, social learning is particularly detrimental when the environment changes since more of the population will have arrived at the optimal behavior in the previous generation and socially learning from them will be biased against the correct choice.
+These two mechanisms make it particularly profitable to engage in social learning when the selection set size is larger -- for large values of $B$ social learning can even be favored when the environment is more likely to change than not (i.e., $u>0.5$).
+
+A shorter effective lifespan, $L$, also favors the evolution of social learning in most cases.
+When effective lifespans are long and there are many opportunities to gather information by learning asocially, the value of social transmission is diminished.
+Given enough opportunities, all agents will learn the optimal behavior eventually.
+Thus, under most conditions, longer effective lifespans lead to a narrower range of the parameters $u$ and $B$ under which social learning was favored.
+It is noteworthy that in many cases, a large increase in the selection regime for social learning could be observed when $L=1$, and by definition no individual learning occurred.
+The exceptions to this general pattern occur for high levels of payoff ambiguity, $\pilow$ combined with low rates of environmental change, $u$ (left parts of plots on bottom row of Figure~\ref{fig:mainResults}).
+This reversal is partially explained by higher levels of drift when there is little difference in the payoffs between behaviors, and by the fact that the quality of social information is poorer when payoffs are ambiguous and lifespans are short (more on these effects of payoff ambiguity below).
+\cm{is this right?
+I thought we should say something about the exceptions in this paragraph though we describe in more detail below, but not sure I have the right explanation}
+
+Of the four types of uncertainty studied in this paper, payoff ambiguity has the most complex effect on the evolution of social learning.
 Recall that we operationalize payoff ambiguity with $\pilow$, the expected payoff for non-optimal behaviors (literally the probability that those behaviors yielded a payoff of 1).
@@
 When payoff ambiguity was low, non-optimal behaviors rarely paid off, so that exploration yielded reliable information and selection on learning strategies was  strong.
-When payoff ambiguity was very high ($\pilow = 0.8$), two things happened.
-Not only were agents likely to ascribe high value to non-optimal behaviors, but also selection on strategies that did reliably select the optimal behavior was relatively weak.
-This allowed for the effect of drift to become stronger, weakening selection in favor of social learning under small values of $u$ and weakening selection against social learning under high values of $u$.
-This effect was especially strong under other types of uncertainty: more temporal environmental variability, larger selection set sizes, and especially shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
-
-The effect of drift under short effective lifespans and high payoff ambiguity is powerful and complex.
-We explain how selection on social learning responds to these effects in more detail in the following section.
+When payoff ambiguity is very high ($\pilow = 0.8$), two things happen.
+First, agents are more likely to err by ascribing high value to non-optimal behaviors, since it is more difficult for them to discern the difference between optimal and sub optimal behaviors.
+Second, and perhaps more importantly, natural selection on strategies that $do$ reliably select the optimal behavior is relatively weak.
+This means that the effect of drift is relatively stronger, weakening selection in favor of social learning under small values of $u$ and weakening selection against social learning under high values of $u$ (Figure~\ref{fig:steps}).
+This effect was especially strong under other types of uncertainty, i.e., larger selection set sizes and especially shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
+
+The effect of drift when effective lifespans are short and payoffs are very ambiguous is powerful and complex.
+We explain how the frequency of social learning evolves in such circumstances in the following section.
+%selection on social learning responds to these effects in more detail in the following section. 
+%\cm{I rephrased as I didn't think selection was RESPONDING to drift. Original framing sounded weird since in essence we have weak selection which is why drift is relatively high. }
 
@@
   environmental variabilty, $u$, increases (x-axes) in most uncertainty contexts. 
-  Other uncertainty values $\pilow$ (rows), $B$ (columns), and $L$ (keys)
-  shift and flatten the decrease from all-social-learner populations to all-asocial 
-  populations.}
+  Other uncertainty values payoff ambiguity, $\pilow$, (rows), number of behavioral options, $B$, (columns), and effective lifespan, $L$, (keys) shift and flatten the slope from all-social-learner populations to all-asocial-learner
+  populations.
+Vertical lines represent when the payoffs of simulated populations of all asocial and social learners experienced equivalent payoffs \cm{is this right?
+I don't understand the arg max u lines} }
   \label{fig:mainResults}
@@
 The effect of drift on the evolution of social learning %evolution and evolutionary drift 
-depended on the extent to which the social learning trait provided agents with a consistent benefit.
-Drift infuses randomness into natural selection, which can lead a population under a consistent but weak selection pressure to take longer to reach fixation \cite{plutynski2007drift}.
-Drift is maximal when social and asocial learning are equally beneficial and fixation takes longer to achieve.
-We therefore measured drift by the average number of generations to fixation, denoted $\langle G \rangle$, where fixation means that $\sum_i s_i$ is equal to either zero or $N$.
+depended on the strength of natural selection, that is, on the extent to which the social learning trait provided agents with a consistent benefit.
+Drift infuses randomness into natural selection.
+In this model, such randomness is introduced at various stages including when agents receive payoffs for a given behavior, when they are reproducing, and when they are being selected as teachers.
+Drift is maximal, and in fact the only evolutionary force in our model, when social and asocial learning are equally beneficial.
+While we do not consider that possibility, even under a consistent but weak selection pressure drift can cause a population to take longer to reach fixation \cite{plutynski2007drift}.
+We therefore measured drift by the average number of generations to fixation, denoted $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
 %Indeed, social learning evolution and drift are reflected in the relative benefit of social learning to asocial learning.
@@
 $\sum_i s_i = N$ or $\sum_i s_i = 0$ at model initialization.
-These stay constant since we do not allow for mutation.
-These are the payoffs to a homogeneous population of either all social learners or all asocial learners.
+These populations remain homogeneous since we do not allow for mutation.
+From these runs we calculate the payoffs to a population of either all social learners or all asocial learners after x generations \cm{you waited for them to stabilize or something right?
+only relevant for social learner population, but needs some more explanation}.
 Figure~\ref{fig:payoffs} shows these expected payoffs, normalized by effective lifespan $L$), as well as the observed average payoffs in our simulations.
@@
 payoffs (Figure~\ref{fig:payoffs}).
+This mapping of expectations to model results is reflected in Figure~\ref{fig:mainResults} given the vertical lines map onto the transitions from social to asocial learning in the curves.
+\cm{wait i wrote this and then noticed that I was looking at the wrong vertical lines (the <G> ones) now I'm confused.
+}
 % However, we also found that populations of initially all social learners performed worse
@@
 Figure~\ref{fig:steps} shows the average time to fixation, $\meanG$, for all our our uncertainty parameters.
-We confirmed that drift increased when $\meansl$ was furthest from either 0 or 1 (that is, when fixation to either extreme was possible),
-and when the payoff ambiguity $\pilow$ was increased (Figure~\ref{fig:steps}). 
+We confirmed that drift is highest, as proxied by high $\meanG$, when runs are similarly likely to fixate at $\meansl$ = 0 or 1,
+and when the payoff ambiguity $\pilow$ was highest (Figure~\ref{fig:steps}). 
 %We measured drift by the average number of generations to fixation, $\meanG$. Recall fixation is defined as the population becoming homogenous, composed of all social or all asocial learners. 
 $\meanG$ peaks around the values of $u$ 
-when $\meansoc \approx \meanasoc$, which led $\meansl$ to transition from 1 to 0.
+when $\meansoc \approx \meanasoc$, \cm{wait does it? Fig S2 doesn't seem to show the vertical lines mapping on well} which led $\meansl$ to transition from 1 to 0.
 In some cases, especially when $\pilow=0.8$,
@@
 
+ Despite the common claim that copying others makes sense when one is uncertain, we find that different forms of uncertainty can either promote, or impede, the evolution of social learning.
 By disambiguating various formalizations of uncertainty in a single computational model, we have developed a more nuanced theoretical understanding of how uncertainty affects the evolution of social learning.
 %We reviewed and distilled several empirical and theoretical models in the literature along four uncertainty dimensions: temporal environmental uncertainty, selection set size, ambiguous payoffs, and effective lifespan.
-We reproduced the well-known results that the uncertainty derived from a temporally variable environment can favor the evolution of social learning up the point where environmental change is simply too rapid for intergenerational transmission to be of value.
+We reproduced the well-known results that the uncertainty derived from a temporally variable environment can limit the evolution of social learning if environmental change is simply too rapid for intergenerational transmission to be of value.
 Importantly, we also showed that this relationship is affected by other sources of uncertainty.
 %Our model reproduced classic predictions that social learning can yield higher payoffs than individual learning when uncertainty is sufficiently limited. 
-We found that larger selection sets, shorter effective lifespans, and increased payoff ambiguity could all favor the evolution of social learning.
+We found that larger sets of behavioral options, shorter effective lifespans, and increased payoff ambiguity could all favor the evolution of social learning.
 However, these effects were not always straightforward.
@@
 evolutionary uncertainty in a finite-size population.
-When the ability to learn individually is also fraught with uncertainty, selection either for or against social learning may be substantially weakened.
-
-Our model helps to demonstrate that social learning can act as a scaffold for individual learning---despite the framing of many other papers, they are not opposites. 
+Not surprisingly, when the consequence of one's choice does not affect payoffs much, selection either for or against social learning is substantially weaker.
+More interestingly, selection is also weaker when the ability to learn asocially is fraught with uncertainty.
+
+Our model helps to demonstrate that social learning can act as a scaffold for asocial learning---despite the framing of many other papers, they are not opposite strategies. 
 We endowed agents with a biologically-plausible individual learning mechanism, softmax search.
-This allowed for highly successful individual learning that helped agents recover from the potential cost of receiving outdated information.
+This allowed for highly successful asocial learning that helped agents recover from the potential cost of receiving outdated information.
 This in turn enabled the evolution of social learning
 even when social information was likely to be outdated.
+\cm{this seems to say the opposite of the topic sentence.
+In topic sentence social learning-> asocial, but the mechanism descibed later is asocial learning -> social.
+Both seem possible, though the latter is easier for me to understand.}
 Detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly changing world.
-Such understanding could help suggest plausibly beneficial interventions to mitigate existential threats~\cite{Moya2020,Jones2021}, especially in
+Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\cite{Moya2020,Jones2021}, especially in
 the most vulnerable communities~\cite{McNamara2020}, and to capitalize on new behavioral opportunities such as transitioning to clean energy use and
 production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+\cm{should we draw out some implications?
+I find this difficult, but e.g.
+stressing environmental change may discourage learning from older gen?
+having more tech options available for dealing with climate change may encourage social learning?
+Frankly so many of these problems seem to come back to encouraging people to socially learn from the RIGHT people, not just socially or asocially learning.}
 
 Our model necessarily made simplifying assumptions.
-These choices were judiciously made to address the main question of how uncertainty affects the evolution of social learning in general; however there exist alternative empirically-valid choices we could have made, the future exploration of which will be important to the development of a more nuanced theory of social learning.
+These were chosen judiciously to address the main question of how uncertainty affects the evolution of social learning.
+Two critical assumptions we made have important consequences for comparing our results with previous findings in the literature.
+First, we assume all agents engage in asocial learning.
+This means that asocial learning is effectively free, though potentially inaccurate.
+Although producing new knowledge may be costly, many other adaptive problems take the form of essentially cost free asocial learning.
+For example, one cannot help but experience, at likely asocially learn about the association between; clouds and rain, drinking water and hunger, or smiling and being avoided.
+This model thus avoids scrounger / producer dynamics common in other models ~\cite{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and asocial learners.
+Second, we only allow for intergenerational social learning and environmental change.
+Within generations agents can only learn asocially, meaning they cannot learn from their peers.
+This assumption allows us to replicate the classic finding that if the environmental change too quickly, socially learned information will be useless.
+Alternative formalizations for the timing of  social learning and environmental change would break this relationship.
+\cm{can cite the Cog Sci version of the paper here to acknowledge the change.}
+
+We could have made alternative, empirically-valid, choices for a range of other structural features, the future exploration of which will be important to the development of a more nuanced theory of social learning.
 % that may not always hold in more specific situations, though they are empirically justified to be general across taxa.
-For example, we considered only success-biased
-learning, although conformity or other context biases may sometimes be the social learning mechanism~\cite{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.  Conformity may lead to more drift
-overall, since success-biased teacher selection, which we assumed, maximizes the potential benefit to social learners. We also assumed that the number of behaviors and
-their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which
-creates new behavioral opportunities as time progresses, e.g.\ via niche
-construction~\cite{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
-supported by dynamic network structure~\cite{Smolla2019,Derex2020}.  Group structure
+For example, we only considered success-biased
+learning, although people may use conformity or other context biases to socially learn ~\cite{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.
+This modelling choice maximizes the potential benefit to social learners suggesting other mechanisms, like conformity, may lead to more drift overall.
+We also assumed that the number of behaviors and
+their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g.\ via niche construction~\cite{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
+%supported by dynamic network structure
+~\cite{Smolla2019,Derex2020}.  Group structure
 and processes such as homophily and in-group bias/out-group aversion could inhibit the
-evolution of social learning since successful outgroup teachers could be cut off from
+evolution of social learning since successful out-group teachers could be cut off from
 in-group learners~\cite{Golub2012}. We assumed agents choose behaviors via softmax
-search, but this is an underpowered algorithm compared to the real human individual learning~\cite{Schulz2020a,Wu2022}.  More powerful individual learning could further
-support social learning.  These considerations reveal new opportunities to enhance theoretical nuance by adjusting or extending the present model for other contexts.
+search, but even though this algorithm is more sophisticated than most used in social learning models, it is algorithm compared to real human learning mechanisms ~\cite{Schulz2020a,Wu2022}.
+Instantiating even more powerful asocial learning could further
+support the evolution of social learning. These considerations reveal new opportunities to enhance theoretical nuance by adjusting or extending the present model for other contexts.
 
@@
 Although social learning is widely studied, few studies have previously examined how various environmental variables contributing to uncertainty interact.
-By carefully identifying and operationalizing common theoretical assumptions about contextual uncertainty in social learning models, we developed a more systematic
+By carefully identifying and operationalizing common forms of  uncertainty in social learning models, we developed a more systematic
 understanding of which uncertainty factors interact to determine whether social
@@
 information, we saw that social learning could evolve even if social learning
-regularly provides outdated information. This work most directly informs our current understanding of the evolution of social learning, but also has broader significance for
+often provides outdated information. This work most directly informs our current understanding of the evolution of social learning, but also has broader significance for
 understanding problem solving under uncertainty. \ps{What is this significance? Can't just leave that dangling. I also cut the bit about what comes next. No need for spoilers.} 
@@
 parameters: the number of agents ($N$), the number of
-prospective teachers pooled by social learner children for social learning
+prospective teachers which social learner children compare
 ($N_T$), and the softmax behavior selection greediness parameter ($\beta$).
@@
 due to (1) finite population size effects, with greater drift for smaller $N$;
-(2) lower quality of socially-learned information agents can access with fewer
+(2) lower quality of socially-learned information when agents can access fewer
 prospective teachers; and (3) lower quality social information when $\beta$
@@
 indicating different overall time to fixation for different $(\pilow, B)$
-pairs. Only extremal tested values of $L$ shown for clarity.} 
+pairs. Only extremal \cm{is this a technical term or you mean extreme? but actually 4 L-values shown} tested values of $L$ shown for clarity.} 
   \label{fig:steps}

### 2022-10-09 ms.tex
Updates from J

@@
 \begin{abstract} 
-  Social learning is a critical
-  adaptation for dealing with uncertainty. However, uncertainty takes many forms.
-  We identified four distinct and theoretically important types of uncertainty: temporal
-  environmental variability, ambiguous payoffs, decision set size, and effective
-  lifespans. We embed this framework in an evolutionary agent-based model to study conditions for the evolution of  social learning in populations with cognitively realistic individual learning
-  capacities.  
-  Agents could perform one of several behaviors, modeled as multi-armed bandit, to acquire payoffs.
+  Social learning is a critical adaptation for dealing with the variable world.
+However, variability takes different forms.
+Uncertainty is a severe form of variability where either probabilities or the outcome space (or both) of decisions are unknown.
+We identified four distinct and theoretically-important types of uncertainty: temporal environmental variability, ambiguous payoffs, decision-set size, and effective lifespan.
+The common thread of these is that they make fully learning variability impossible.
+We embed this framework in an evolutionary agent-based model to study conditions for the evolution of social learning in populations with cognitively-realistic individual learning capacities.
+Agents perform one of several behaviors, modeled as a multi-armed bandit, to acquire payoffs.
 Individual learning used the softmax algorithm.
 Social learning involved vertical and oblique transmission between generations, which served as a constraint on subsequent individual learning.
-We found that different types of
-  uncertainty had different effects. Temporal environmental variability suppressed
-  social learning, whereas larger decision-set size promoted social learning even
-  when the environment changed frequently. Payoff
-  ambiguity and lifespan had more complex effects on social learning, dependent on
-  other uncertainty parameters.  This study shows the importance of clearly
-  operationalizing uncertainty for understanding its role in social and cultural evolution.
+We found that different types of uncertainty had different effects.
+Temporal environmental variability suppressed social learning, whereas larger decision-set size promoted social learning, even when the environment changed frequently.
+Payoff ambiguity and lifespan had more complex effects on social learning, dependent on interactions with other uncertainty parameters.
+This study shows the importance of clearly operationalizing uncertainty for understanding its role in social and cultural evolution.
 % Social learning is essential to human survival. It is likely to evolve when it is more
@@
 
-Social learning enhances problem solving when acquiring information from others is more
-efficient than learning on one's own~\cite{Laland2004}. However, social learning can also
-lead individuals astray if they are copying irrelevant, misleading, or outdated information.
-Theoretical models have helped clarify the circumstances under which social learning
-should be evolutionarily favored~\cite{BoydRicherson1985, aoki2014evolution,Kendal2018}, and these models have motivated empirical work that has both validated and refined theoretical predictions concerning the use of social learning in humans
-and other species~\cite{galef2005social,McElreath2005,Kendal2018,Allen2019}.  This literature
+Social learning enhances problem-solving when acquiring information from others is more efficient than learning on one's own~\cite{Laland2004}.
+However, social learning can also lead individuals astray if they are copying irrelevant, misleading, or outdated information.
+Theoretical models have helped clarify the circumstances under which social learning should be evolutionarily favored~\cite{BoydRicherson1985, aoki2014evolution,Kendal2018}, and these models have motivated empirical work that has both validated and refined theoretical predictions concerning the use of social learning in humans and other species~\cite{galef2005social,McElreath2005,Kendal2018,Allen2019}.
+This literature
 indicates that social learning is a critical adaptation found across taxa for dealing
-with uncertainty. When in doubt, copy others.
+with variable environments. When in doubt, copy others.
 
@@
 our long lifespans, cosmopolitan societies, and dispersal across a highly variable environments, requiring coarse-grain and plastic behavioral adaptations \cite{levins1962}.
-However, the term ``uncertainty''
-often conflates several different interpretations of that word. For example, different
-models define uncertainty in terms of the rate of environmental change, spatial
-environmental variation, or the reliability of information acquired from the environment.
-Furthermore, in translating mathematical models to verbal predictions, the formal meaning
-of terms like uncertainty is often lost \cite{knight1921, lawson1988probability, volz2012}, facilitating such
-conflation. %Furthermore, it can be important to distinguish a narrower definition of uncertainty wherein the probabilities of outcomes remain unknown~\cite{knight1921,volz2012}. 
-As the number of formal models of social learning have expanded, an increasing number of modeling choices~\cite{Kendal2018} and formalizations of
+However, the term ``uncertainty'' is often used loosely in a way that fails to distinguish it from risk.
+\emph{Risk} represents a decision with a variable payoff where the state space and probabilities associated with the different outcomes are both known.
+In contrast, \emph{uncertainty} implies that the outcome probabilities, and possibly the state space, are not known \citep{knight1921, keynes1921}.
+Furthermore, usage of the term uncertainty often conflates several different interpretations of that word.
+For example, different models define uncertainty in terms of the rate of environmental change, spatial environmental variation, or the reliability of information acquired from the environment.
+%Furthermore, in translating mathematical models to verbal predictions, the formal meaning of terms like uncertainty is often lost \cite{knight1921, lawson1988probability, volz2012}, facilitating such conflation.
+%Furthermore, it can be important to distinguish a narrower definition of uncertainty wherein the probabilities of outcomes remain unknown~\cite{knight1921,volz2012}.
+As the number of formal models of social learning has expanded, an increasing number of modeling choices~\cite{Kendal2018} and formalizations of
 uncertainty have made it difficult to compare across models or to consolidate our
@@
 In general, learning is an iterative process during which an individual acquires information, forms representations and predictions, and then tests and refines those representations and predictions to manage uncertainty~\cite{jacobs2011bayesian,clark2013whatever}.
-Because cultural evolutionary
-models are often designed to explain \emph{social} learning mechanisms, they often contrast social learning with an overly simplistic mechanism for individual learning.
+Because cultural evolutionary models are often designed to explain \emph{social} learning mechanisms, they often contrast social learning with an overly-simplistic mechanism for individual learning.
 In particular, it is often assumed that individual learners can \emph{always} pay a cost to learn the optimal behavior for a particular environment with certainty.
 This assumption implies that social learning by observing an individual learner is a good bet if the environment has not changed.
-Such modelling choices may lead us to overestimate both the extent to which individual learning provides
-quality information and the value of social learning in a population of individual learners. % , both for asocially adapting to uncertainty and for social learners to take advantage of.
+Such modelling choices may lead us to overestimate both the extent to which individual learning provides quality information and the value of social learning in a population of individual learners.
+% , both for asocially adapting to uncertainty and for social learners to take advantage of.
 %and for the individual to adapt to the challenges assumed to be solved by social learning. 
@@
 uncertainty that are common in cultural evolution models and the related empirical
-literature:  (1) temporal environmental variability; (2) selection set size (the number of
-possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for
-different behaviors); and (4) the effective lifespan of agents (the number of
-opportunities for individual learning), explained below. In our model, social learners learn from the previous generation and asocial learners do not. All agents engage in individual learning within
-their lifespans. The model also assumes a more
-cognitively-realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows learners to make full use of the available data acquired by both individual and social learning.
-Our model design thereby affords us a richer and possibly more accurate assessment of trade-offs between 
-social and asocial learning. 
+literature:  (1) temporal environmental variability; (2) selection set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning), explained below.
+In our model, social learners learn from the previous generation and asocial learners do not.
+All agents engage in individual learning within their lifespans.
+The model also assumes a more
+cognitively-realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows learners to make full use of the available data acquired by both individual and social learning \cite{SuttonBartoBook}.
+Our model design thereby affords us a richer and possibly more accurate assessment of trade-offs between social and asocial learning.
 We use this integrated model to ask which kinds of uncertainty are likely to favor social learning and to clarify the logic underlying the results.
@@
 
-\textbf{Temporal environmental variability.} When environmental variability is nonstationary (for example, because of climatic events, migration, or technological paradigm shifts), strategies that were previously adaptive may no longer be optimal.
+\paragraph{Temporal environmental variability.} When environmental variability is nonstationary (for example, because of climatic events, migration, or technological paradigm shifts), strategies that were previously adaptive may no longer be optimal.
 The difficulty in predicting either when such shocks will occur or which behaviors will be adaptive in the resulting environments leads to uncertainty.
@@
 %Furthermore, t
-The consequences of environmental change can range from mild to
-catastrophic. In the latter case, a change of environment results in the total
-elimination of any adaptive behavior, which must be learned \emph{de novo} for the
-new environment~\cite{Rogers1988}. Such catastrophic environmental changes present
+The consequences of environmental change can range from mild to catastrophic.
+In the latter case, a change of environment results in the total elimination of any adaptive behavior, which must be learned \emph{de novo} for the new environment~\cite{Rogers1988}.
+Such catastrophic environmental changes present
 a large adaptive challenge as individuals cannot rely on accumulated information
@@
 uncertainty as they fluctuate between two or more environmental states with corresponding adaptive behaviors. This means that previously maladaptive
-behaviors become adaptive when the environment changes~\cite{perreault2012bayesian}. The chosen mechanism for modelling temporal
-change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behavior, and instead considers only behaviors that can be learned.
-
-\textbf{Selection set size.}
+behaviors become adaptive when the environment changes~\cite{perreault2012bayesian}.
+The chosen mechanism for modelling temporal change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behavior, and instead considers only behaviors that can be learned.
+
+\paragraph{Selection set size.}
 When one does not know which option to take, uncertainty increases with the number of options, which we call the selection set size.
@@
 % This is intuitive; the more options to consider, the greater one's uncertainty about which option is the best choice. 
-In many studies of social learning, the selection set is often limited to just two options.  For example, in empirical studies of \emph{bombus
-terresteris} (bumble bee)~\cite{Baracchi2018} and \emph{parus major} (great
-tit)~\cite{Aplin2017}, experimenters provided two behaviors from which the bees or birds
+In many studies of social learning, the selection set is often limited to just two options.  For example, in empirical studies of bumble bees (\emph{Bombus
+terresteris}) \cite{Baracchi2018} and great tits (\emph{Parus major}) \cite{Aplin2017}, experimenters provided two behaviors from which the bees or birds
 could choose, with one yielding a higher payoff than the other. %respectively,
@@
 % behavior selection sets. correct if wrong} 
-Larger, more open sets of behavioral
-choices are not uncommon in experiments trying to capture more complex or
-naturalistic tasks~\cite{derex2013, wasielewski2014}, but these map on
-imperfectly to the theoretical literature that tend to use a limited set of behavioral options.
+Larger, more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\cite{derex2013, wasielewski2014}, but these map imperfectly onto the theoretical literature that tends to use a limited set of behavioral options.
 %\mt{How so?}. 
-Some models have studied systems with
-larger, but defined, selection sets~\cite{Rendell2010, lindstrom2016co}, while in others the
-number of options is subsumed under the probability that a learner gets the right answer~\cite{Feldman1996,Enquist2007}.
+Some models have studied systems with larger, but defined, selection sets~\cite{Rendell2010, lindstrom2016co}, while in others the number of options is subsumed under the probability that a learner gets the right  answer~\cite{Feldman1996,Enquist2007}.
 %\mt{How does this work exactly in Enquist et al 2007?}. 
 %Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviors through time~\cite{Feldman1996}. 
-Rarely if ever is the size of the selection set explored explicitly as a source of varying uncertainty, even though the number of options one has is likely to increase with the difficulty of the decision task~\cite{haynes2009testing,white2009testing}.
+Rarely is the size of the selection set explored explicitly as a source of  uncertainty \citep[though see][]{Muthukrishna2016a}, even though the number of options one has is likely to increase with the difficulty of the decision task~\cite{haynes2009testing,white2009testing}.
 %These examples share one common feature: the size of the selection set was held static \emph{within} model generations.
@@
 
-\textbf{Payoff ambiguity.} Most models of social learning necessarily differentiate between the payoffs for adopting optimal vs. non-optimal behaviors
-\cite{BoydRicherson1985,Rogers1988,Enquist2007,Rendell2010,aoki2014evolution}. The size of the difference between
-these payoffs is usually taken to indicate the strength of selection of learning. %, which makes sense. 
+\paragraph{Payoff ambiguity.} Most models of social learning necessarily differentiate between the payoffs for adopting optimal vs. non-optimal behaviors
+\cite{BoydRicherson1985,Rogers1988,Enquist2007,Rendell2010,aoki2014evolution}.
+The size of the difference between these payoffs is usually taken to indicate the strength of selection of learning.
+%, which makes sense.
 However, the ability to discern payoff differences between behaviors is also a source of uncertainty.
@@
 Importantly, payoff ambiguity %differs from selection set size in that it not only 
-affects both 
-%affects uncertainty, it also directly influences both 
-uncertainty \emph{and} the
-strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
+affects both uncertainty \emph{and} the strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
 %This parameter sometimes takes the form of differences in
@@
 
-\textbf{Effective lifespan.} 
-The more opportunities one has to learn during one's lifespan, the more uncertainty can be reduced, assuming a
-static environment. Correspondingly, a reduction in the number of opportunities to learn will increase the uncertainty about which behavioral options are available and what their associated
+\paragraph{Effective lifespan.} The more opportunities an agent has to learn during its lifespan, the more uncertainty can be reduced, assuming a stationary environment.
+Correspondingly, a reduction in the number of opportunities to learn will increase the uncertainty about which behavioral options are available and what their associated
 payoffs are. %Such uncertainty can be passed on to future generations.
@@
 
-Empirically, the number of learning opportunities can be manipulated in the lab, and in the real world will tend to correlate with an individual's relative age. In multi-round
-studies of information use in novel tasks, US participants' use of social
+Empirically, the number of learning opportunities can be manipulated in the lab, and in the real world will tend to correlate with an individual's relative age.
+In multi-round studies of information use in novel tasks, US participants' use of social
 information declined precipitously across rounds~\cite{McElreath2005}, suggesting
-they were more likely to use social information when they were most uncertain about the task early on. In a more naturalistic context, Aplin et al. (2017)
-\nocite{Aplin2017} found that younger great tits more readily used social
-information compared to older individuals, possibly because they had accrued
-less information via individual learning, and possibly because younger
-individuals have the most to gain (given their expected remaining lifespan) by switching to superior behavioral options. 
-% \ps{I got rid of the Leris and Reader reference because it didn't seem relevant
-% to age-based uncertainty. They just showed that young guppies exposed to
-% reliable models were more likely to use social information later. I also added
-% some human studies, which seems important.} 
-Cross-cultural studies have highlighted the importance of childhood as a phase
-of heavy social learning in humans ~\cite{Reyes2016}. Young children are more likely to
+they were more likely to use social information when they were most uncertain about the task early on.
+In a more naturalistic context, \citet{Aplin2017} found that younger great tits more readily used social information compared to older individuals, possibly because they had accrued less information via individual learning, and possibly because younger individuals have the most to gain (because of higher reproductive value) by switching to superior behavioral options.
+Cross-cultural studies have highlighted the importance of childhood as a phase of heavy social learning in humans \cite{Reyes2016}.
+Young children are more likely to
 acquire their beliefs and simple skills from their parents than are older children
@@
 between young children and the older adults to whom they direct the most trust and
-attention \cite{kline2013teaching}.
-%The age of individuals was found to have an effect on social learning in both
-%\emph{parus major}~\cite{Aplin2017} and \emph{poecilia reticulata}
-%(guppies)~\cite{Leris2016}. \ps{What effect? I'm not sure } \mt{Need better
-%connection between lifespan and age, or better references to support use of
-%lifespan}.
-The effective lifespan for learning
-varies across tasks, individuals, and species, yet most models assume only one learning
-opportunity per generation~\cite{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
-Some models do allow several cultural generations within one genetic generation
-~\cite{Enquist2007,Rendell2010,lindstrom2016co}, but little formal theory explicitly examines the role of
-learning opportunities in the evolution of social learning.
+attention \cite{kline2013teaching}. The effective lifespan for learning
+varies across tasks, individuals, and species, yet most models assume only one learning opportunity per generation \citep{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
+Some models do allow several cultural generations within one genetic generation \citep{Enquist2007,Rendell2010,lindstrom2016co}, but little formal theory explicitly examines the role of learning opportunities in the evolution of social learning.
 
@@
 
-% \subsection{Other adaptations to uncertainty} 
 \subsection{Individual-level adaptations to uncertainty}
 
-% \begin{comment}
-
-% \cm{I think a lot of this may be too much detail.
-I'm still editing and focusing the above on the main forms of uncertainty we are modeling and reviewing the relevant literature as we go.
-Yes we've made choices about things like horizontal vs vertical, but i think we can just justify that when we introduce the model }
-% ps{I agree with Cristina here.
-I think we should use this section to justify our way of modeling individual and social learning, which is different from previous models.
-We don't need to provide a detailed review, just why it's worth doing it as we've done it.
-In particular, we should set up (1) social learning as an initial scaffold for future social learning, and (2) softmax individual learning which involves some greediness with occasional trial and error.}
-
-% To add to confusion about how to integrate diverse models of social learning
-% evolution, different models select different social learning components in
-% seemingly \emph{ad hoc} ways 
-% \begin{itemize}
-%   \item 
-%     Vertical, oblique, horizontal transmission
-%   \item
-%     Conformity, payoff-biased, frequency-dependent, etc. A note about how
-%     ``conformity'' is often not distinguished from other forms of social learning
-%   \item
-%     Review human studies
-%   \item
-%     Review non-human studies~\cite{Leris2016,Aplin2017,Avargues-Weber2018,Baracchi2018}
-%   \item
-%     One sentence on how dual-inheritance theory enables us to gloss over whether
-%     social learning is genetically or culturally evolved.
-%   \item
-%     More things from which we selected the operation of our model
-% \end{itemize}
-
-% \end{comment}
-
-%Social learning is the adaptive icing on the cake of other cognitive adaptations to ecological uncertainty. 
-While the literature reviewed above suggests that
-several forms of uncertainty have played a role in the evolution of social
-learning, other cognitive mechanisms have likely also evolved in response to
-uncertainty~\cite{volz2012,johnson2013evolution,van2018uncertainty}. Many of these are flexible learning mechanisms that
-do not require imitating the behaviors of others.
-For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviors with greater observed payoff variance
-\cite{Wilson2014,Gershman2019}.
-
-Many models of social learning simplify by using minimally cognitive %assume little to no cognitive capabilities of their 
-agents. For example, a common modelling strategy compares the payoffs of
-agents with different pure learning strategies (e.g., those who only engage in social
-learning versus those who only engage in individual learning) while revealing nothing about the
-cognition underlying individuals' decisions~\cite{BoydRicherson1985, Rogers1988,
+While the cultural-evolution literature suggests that several forms of uncertainty have played a role in the evolution of social learning, other cognitive mechanisms have likely also evolved in response to uncertainty \cite{volz2012,johnson2013evolution,van2018uncertainty}.
+Many of these are flexible learning mechanisms that do not require imitating the behaviors of others.
+For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviors with greater observed payoff variance \cite{Wilson2014,Gershman2019}.
+
+Many models of social learning simplify by using minimally-cognitive agents.
+For example, a common modelling strategy compares the payoffs of agents with different pure learning strategies (e.g., those who only engage in social learning versus those who only engage in individual learning) while revealing nothing about the cognition underlying individuals' decisions~\cite{BoydRicherson1985, Rogers1988,
 aoki2005}.
@@
 Some more complicated learning strategies that make use of both socially and individually learned information have been studied ~\cite{Enquist2007, perreault2012bayesian}, including those that integrate cognitively plausible mechanisms such as reinforcement learning \cite{lindstrom2016co}, though the latter approach remains the exception rather than the norm.
-%but these are seldom designed to reflect cognitive mechanisms for integrating information.
-Though such simplifications are often useful, several authors have warned of the risks to \emph{blackboxing}, or ignoring, cognitive mechanisms \cite[p.
-658]{Heyes2016, Kendal2018}, given such details may be theoretically meaningful.
-In order to understand how social learning evolves as an adaptation to uncertainty, we 
-endowed agents with a biologically plausible cognition capable of integrating information from various sources to maximize payoffs, using \emph{softmax
-search}~\cite{Gershman2019}, described in more detail below. 
-% \cm{I don't
-%   understand this next sentence, but think it can be cut with no loss of meaning:
-%   In our model we do not impose any structure in randomness between behaviors, so
-% our cognitive model is only sensitive to total randomness.} 
-% To do so, we let
-% agents see the payoffs to behaviors and use the softmax function to convert these
-% observations to a probability distribution from which they strategically select
-% their own behavior. %\cm{does this still make sense? and does it need a citation?}
-
-%\paragraph{Meaning of uncertainty in ecology (and cognitive and social sciences?) } (JAMIE, PAUL?) \ps{I've added a bunch to the section on different types of uncertainty, which could be more fleshed out if we like.
-I don't think an additional section here is needed.}
-%We need to support our claim that these four classes of uncertainty really count as forms of uncertainty and show how it is consistent across ecology, and maybe connect to uncertainty in cognitive and social sciences more broadly.
-
-%\paragraph{Evolutionary ABMs for social learning evolution theory development} (PAUL)
-%\ps{I'm not sure a section is needed on this, but we can add something about how ABMs allow us to capture complexity not possible with purely mathematical approaches.
-I think it probably makes the most sense to address this at the beginning of the model description.}
+In order to understand how social learning evolves as an adaptation to uncertainty, we endowed agents with a biologically-plausible cognition capable of integrating information from various sources to maximize payoffs, using \emph{softmax search}~\cite{Gershman2019}, described in more detail below.
 
@@
 
-% \cm{Other choices we made that might need to be justified: 1) softmax: existing models underestimate the power of learning from experience by not having a rich cognition.
-This rich cognition can improve both individual learning and help social learners recover from outdated / misleading social info.
-2) no conformism: but that's ok because we're giving social learning the best chance of success.
-3) no horizontal transmission, no spatial variation}
-
-%To understand how uncertainty affects social learning, we developed an agent-based model of social learning evolution.
-Evolutionary agent-based models simulate changes in the prevalence of a phenotype over several generations---in this model the phenotype is whether or not an agent engages in social learning.
 In our model we allow just one trait to evolve; social learning, while all other parameters are exogenous.
@@
 each time step within a generation consisting of $L$ time steps.
-The behavior set is a multi-armed bandit with $B$ arms, that is, agents can pick one of $B$ behaviors with random-valued payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
-In each generation, exactly one behavior is more likely to pay off than all the rest and is therefore optimal. Agents
-optimize their net payoffs over their lifespan by quickly figuring out which
-behavior is optimal and performing it as often as possible within their lifespan.
-%The optimal behavior is static within agent lifespans, but varies in general between generations, representing environmental variability.
-At the end of each
-generation, agents are selected with replacement to reproduce a new generation of $N$ agents,
-with the probability of reproduction biased by net payoffs. Agents who inherit the social
-learning trait learn about payoffs from the previous generation, while asocial learners begin
-life only knowing the number of behaviors the environment affords, but no knowledge
-of behavioral payoffs.
-\cm{or would you consider having flat priors over all behaviors knowledge?} 
-\mt{I changed this last sentence to express that they have flat priors, in different
-terms.}
-%The specifics of the model construction and dynamics are described in detail below.
-% \ps{I cut a bunch of stuff that came right here as being redundant or unnecessary.}
-
-% We operationalize four separable varieties of uncertainty that affect the
-% ability of agents to find and choose the optimal behavior: 
-% \emph{environmental variability}; 
-% \emph{selection set size}; \emph{payoff ambiguity}; and the \emph{effective lifespan}. 
-% %Environmental variability is the probability that the optimal behavior changes
-% between generations.   
-% % This is empirically justified since cultural evolution
-% % occurs when meta-cognitive strategies and information are transferred via
-% % learning and social influence, instead of by physical reproduction and death
-% % as in genetic evolution.  
-% The selection set size is the total number of possible
-% behaviors agents choose from, assumed to be constant within a simulation.  
-% Payoff ambiguity is the payoff difference between optimal
-% and non-optimal behaviors. The effective life span is the
-% number of time steps in which agents perform behaviors within a generation. 
-% Our model is not spatial, so agents have free, instant
-% access to all behaviors, and there is no spatial uncertainty. 
-% These conditions reflect humans in a computer-based social learning evolution
-% experiment~\cite{McElreath2005,Morgan2012,Derex2016}. Spatial dimensions could also be
-% considered irrelevant if costs associated with accessing a behavior were equal,
-% e.g., if it was assumed to be equally costly for animals to
-% visit alternative food sources~\cite{Aplin2017,Baracchi2018}.
-% Each simulated environment provides a distinct challenge
-% to the agents, which will lead agents to differently evolve to become social
-% learners or not, depending on which strategy optimizes net payoffs.
-
-% \emph{Agents} here are autonomous, intelligent, simulated problem solvers. Each
-% agent evaluates its environment and chooses how to act within that environment based
-% on a set of empirically-motivated rules.  Our agents select which behavior to do
-% probabilistically, weighted by the softmax function applied to the mean payoff they
-% have observed for each behavior. The softmax function is a biologically plausible
-% generalization of behavior selection under uncertainty that enables agents to often
-% greedily exploit the most lucrative behavior (based on their observations) but also
-% to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
-% Such individual-level intelligence is a critical adaptation that has 
-% co-evolved with the capacity for social learning. We will show that individual
-% learning can support the evolution of social learning.
-
-% In our \emph{evolutionary} agent-based model, agent life cycles are
-% programmed to cause agents to reproduce and die off, where reproducers pass on
-% heritable traits to their offspring. 
-% Natural selection occurs in the model when agents with higher
-% payoffs preferentially reproduce. This is a model of cultural evolution, so
-% ``reproduction'' means teaching the meta-cognitive strategy of whether one should learn
-% socially at all; ``death'', in this interpretation, means
-% loss of the potential to socially influence others. 
-% This sets up an inter-generational cultural structure
-% that we also use as a scaffold for \emph{oblique} social learning, meaning children
-% with the social learning trait learn about payoffs from a member of the
-% previous generation. Evolution acts as an optimization routine to identify
-% whether individuals with the social learning trait will outperform those without.
-
-% Agents inherit one trait in this model, whether or not
-% an agent, $i$, learns socially. If $i$ has the trait we write $s_i=1$
-%  and 0 otherwise. In our analysis, we 
-% average $s_i$ over all agents and simulation trials to understand the affects of
-% different uncertainty parameter settings. 
-% Our computational analysis is based on observing and comparing patterns in
-% aggregated $s_i$ across different parameter settings, 
-% supported by measuring the number of generations 
-% to model convergence and expected payoffs in populations across the same contexts. 
-% To understand how different varieties of uncertainty interact
-% to affect the evolution of social learning, we systematically created an array of
-% simulated environments by systematically varying the uncertainty parameters, and
-% auxiliary model parameters to ensure model validity.
+The behavior set is a multi-armed bandit with $B$ arms.
+That is, agents can pick one of $B$ behaviors with random-valued payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
+In each generation, exactly one behavior is more likely to pay off than all the rest and is therefore optimal.
+Agents optimize their net payoffs over their lifespan by quickly learning which behavior is optimal and performing it as often as possible within their lifespan.
+At the end of each generation, agents are selected with replacement to reproduce a new generation of $N$ agents, with the probability of reproduction biased by net payoffs.
+Agents who inherit the social-learning trait learn about payoffs from the previous generation, while asocial learners begin life only knowing the number of behaviors the environment affords, but have no knowledge of behavioral payoffs.
 
@@
 
-%The model environment provides behaviors for agents to perform. 
 The structure of the environment is specified by several parameters that remain fixed throughout the course of a given simulation (Table~\ref{tab:uncertaintyParameters}).
-%including three of the uncertainty parameters: environmental variability, selection set size, and payoff ambiguity.
-The environment affords $B$ behaviors, where
-$B$ is the \emph{selection set size}.
-%, but varied systematically across simulations.
-Each behavior is indexed by $b$ and 
-%modeled as a ``one-armed bandit'', which 
-yields a payoff 
-%Bernoulli-distributed payoffs 
-of 1 with probability $\pi_b$ and a payoff of 0 otherwise. % with probability $1 - \pi_b$. 
-$\pi_b$ is equivalently the expected
+The environment affords $B$ behaviors, where $B$ is the \emph{selection set size}.
+Each behavior is indexed by $b$ and yields a payoff of 1 with probability $\pi_b$ and a payoff of 0 otherwise.
+Clearly, $\pi_b$ is equivalently the expected
 payoff of behavior $b$.
-At the beginning of each generation, one behavior is optimal and yields expected
-payoff $\pihigh$; the other $B-1$ behaviors yield a lower payoff, $\pilow$. 
+At the beginning of each generation, one behavior is optimal and yields expected payoff $\pihigh$; the other $B-1$ behaviors yield a lower payoff, $\pilow$.
 The \emph{payoff ambiguity} is defined by $\pihigh - \pilow$.
-We fix $\pihigh = 0.9$ to be constant across all simulations, so 
-payoff ambiguity is varied by changing the value of $\pilow$.
+We fix $\pihigh = 0.9$ to be constant across all simulations, so payoff ambiguity is varied by changing the value of $\pilow$.
 In other words, payoff ambiguity increases with $\pilow$.
-Agents have $L$ timesteps to learn and act per generation (i.e., the \emph{effective lifespan}).
+Agents have $L$ time steps to learn and act per generation (i.e., the \emph{effective lifespan}).
 Uncertainty decreases with $L$.
@@
 %Agents are endowed with dynamic attributes to intelligently select behaviors and calculate average payoffs for each behavior. 
-Agents either exclusively rely on asocial learning or additional use social information.
+Agents are endowed with the capacity to learn asocially, while a subset also adds the capacity to use social information.
 For simplicity, we refer to the latter as social learners.
-Learning strategies are assumed to be heritable traits.
+Learning strategies are assumed to be heritable.
 Each agent $i$ has a learning trait $s_i$, which is 1 if $i$ is a social learner and zero otherwise.
-Every agent engages in
-individual learning over its lifespan, regardless of learning strategy.
-Social learners begin life with
-behavioral preferences based on information from an agent chosen  from the previous generation. 
-Asocial learners begin life with no behavioral
-preferences. Agent-level parameters are described in Table~\ref{tab:modelParameters}. 
-% Agents and their learning procedures are specified through several
-% parameters introduced below.
+Every agent engages in individual learning over its lifespan, regardless of learning strategy.
+Social learners begin life with behavioral preferences based on information from an agent chosen from the previous generation.
+Asocial learners begin life with no behavioral preferences.
+Agent-level parameters are described in Table~\ref{tab:modelParameters}.
 
@@
 their lifespan.  Learning is guided by softmax search. Softmax search
-guides agents to more frequently exploit the most profitable behaviors when the
+guides agents to exploit more frequently the most profitable behaviors when the
 agent is more certain which is optimal and to explore more frequently when the
 agent is unsure. To do softmax searching, agents track average payoffs acquired
-from each behavior they have performed, which requires knowing the number of times they
-have performed each behavior.
-The probability that the agent will perform a behavior is a function of the agent's beliefs about a behavior's average payoff in that timestep and a fixed parameter that influences the amount of exploratory behavior (more details below).
+from each behavior they have performed, which requires knowing the number of times they have performed each behavior.
+The probability that the agent will perform a behavior is a function of the agent's beliefs about a behavior's average payoff in that time step and a fixed parameter that influences the amount of exploratory behavior (more details below).
 The softmax function used here is a biologically plausible generalization of behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative behavior (based on their observations) but also to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
@@
 \begin{figure}
-  \caption{Social learning prevalence (y-axes) monotonically decreases as 
-  environmental variabilty, $u$, increases (x-axes) in most uncertainty contexts. 
+  \caption{Social learning prevalence ($y$-axes) monotonically decreases as 
+  environmental variability, $u$, increases ($x$-axes) in most uncertainty contexts. 
   Other uncertainty values payoff ambiguity, $\pilow$, (rows), number of behavioral options, $B$, (columns), and effective lifespan, $L$, (keys) shift and flatten the slope from all-social-learner populations to all-asocial-learner
@@
 This mapping of expectations to model results is reflected in Figure~\ref{fig:mainResults} given the vertical lines map onto the transitions from social to asocial learning in the curves.
-\cm{wait i wrote this and then noticed that I was looking at the wrong vertical lines (the <G> ones) now I'm confused.
-}
+\cm{wait i wrote this and then noticed that I was looking at the wrong vertical lines (the <G> ones) now I'm confused.}
+
+\begin{enumerate}
+    \item 
+      Note frequency dependence of social learning fixation payoffs due to presence of asocial learners
+      (payoffs plots)
+    \item
+      Explain why social to asocial transition occurs away from where homogenous payoffs are equal
+      (payoffs plots)
+    \item
+      Highlight how observations of increased drift/weaker selection observed in <s> plots is supported by 
+      elevated <G> (generations to fixation plots)
+\end{enumerate}
 % However, we also found that populations of initially all social learners performed worse

### 2022-10-09 meanNetPayoffs.tex
updated figures and converted to natbib

@@
     \begin{center}
-      \includegraphics[width=1.25in]{Figures/legendElements/solid.pdf}
-      {\Huge Simulations} \quad \quad 
-      \includegraphics[width=1.25in]{Figures/legendElements/ldash.pdf}
-      {\Huge$\meanasoc$} \quad \quad 
-      \includegraphics[width=1.25in]{Figures/legendElements/dot.pdf}
-      {\Huge$\meansoc$} \quad \quad
-      \includegraphics[width=1.25in]{Figures/legendElements/ldashdot.pdf}
-      {\Huge$\meanasoc = \meansoc$}
+      {\Huge \textbf{+} \huge Location where homogenous social and asocial payoffs
+      are equal} \quad \quad 
     \end{center}
+
 \end{document}

### 2022-10-09 ms.tex
updated figures and converted to natbib

@@
 \usepackage{pslatex}
-\usepackage{apacite}
+% \usepackage{apacite}
 \usepackage{caption}
+\usepackage{natbib}
 \usepackage{subcaption}
@@
 
-Social learning enhances problem-solving when acquiring information from others is more efficient than learning on one's own~\cite{Laland2004}.
+Social learning enhances problem-solving when acquiring information from others is more efficient than learning on one's own~\citep{Laland2004}.
 However, social learning can also lead individuals astray if they are copying irrelevant, misleading, or outdated information.
-Theoretical models have helped clarify the circumstances under which social learning should be evolutionarily favored~\cite{BoydRicherson1985, aoki2014evolution,Kendal2018}, and these models have motivated empirical work that has both validated and refined theoretical predictions concerning the use of social learning in humans and other species~\cite{galef2005social,McElreath2005,Kendal2018,Allen2019}.
+Theoretical models have helped clarify the circumstances under which social learning should be evolutionarily favored~\citep{BoydRicherson1985, aoki2014evolution,Kendal2018}, and these models have motivated empirical work that has both validated and refined theoretical predictions concerning the use of social learning in humans and other species~\citep{galef2005social,McElreath2005,Kendal2018,Allen2019}.
 This literature
@@
 Uncertainty weighs particularly heavily on human adaptation because of
-our long lifespans, cosmopolitan societies, and dispersal across a highly variable environments, requiring coarse-grain and plastic behavioral adaptations \cite{levins1962}.
+our long lifespans, cosmopolitan societies, and dispersal across a highly variable environments, requiring coarse-grain and plastic behavioral adaptations \citep{levins1962}.
 However, the term ``uncertainty'' is often used loosely in a way that fails to distinguish it from risk.
@@
 For example, different models define uncertainty in terms of the rate of environmental change, spatial environmental variation, or the reliability of information acquired from the environment.
-%Furthermore, in translating mathematical models to verbal predictions, the formal meaning of terms like uncertainty is often lost \cite{knight1921, lawson1988probability, volz2012}, facilitating such conflation.
-%Furthermore, it can be important to distinguish a narrower definition of uncertainty wherein the probabilities of outcomes remain unknown~\cite{knight1921,volz2012}.
-As the number of formal models of social learning has expanded, an increasing number of modeling choices~\cite{Kendal2018} and formalizations of
+%Furthermore, in translating mathematical models to verbal predictions, the formal meaning of terms like uncertainty is often lost \citep{knight1921, lawson1988probability, volz2012}, facilitating such conflation.
+%Furthermore, it can be important to distinguish a narrower definition of uncertainty wherein the probabilities of outcomes remain unknown~\citep{knight1921,volz2012}.
+As the number of formal models of social learning has expanded, an increasing number of modeling choices~\citep{Kendal2018} and formalizations of
 uncertainty have made it difficult to compare across models or to consolidate our
@@
 %Other (asocial) forms of learning are also likely adaptations to uncertainty that should be accounted for, but are typically glossed over in models.  
-In general, learning is an iterative process during which an individual acquires information, forms representations and predictions, and then tests and refines those representations and predictions to manage uncertainty~\cite{jacobs2011bayesian,clark2013whatever}.
+In general, learning is an iterative process during which an individual acquires information, forms representations and predictions, and then tests and refines those representations and predictions to manage uncertainty~\citep{jacobs2011bayesian,clark2013whatever}.
 Because cultural evolutionary models are often designed to explain \emph{social} learning mechanisms, they often contrast social learning with an overly-simplistic mechanism for individual learning.
@@
 The model also assumes a more
-cognitively-realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows learners to make full use of the available data acquired by both individual and social learning \cite{SuttonBartoBook}.
+cognitively-realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
 Our model design thereby affords us a richer and possibly more accurate assessment of trade-offs between social and asocial learning.
@@
 The non-probabilistic nature of uncertainty means one cannot calculate expectations.
-Following \cite{savage1954}, various research traditions in decision theory and economics have treated uncertainty as if it were risk, just with subjective probabilities replacing objective ones.
-The fundamental problem with this approach was noted by \cite{geweke2001} and further developed by \cite{weitzman2009}.
+Following \citep{savage1954}, various research traditions in decision theory and economics have treated uncertainty as if it were risk, just with subjective probabilities replacing objective ones.
+The fundamental problem with this approach was noted by \citep{geweke2001} and further developed by \citep{weitzman2009}.
 In particular, the probability density function of an outcome that needs to be learned, but for which opportunities for learning are highly constrained, will be heavy-tailed and expected-utility calculations will not work because of the resulting undefined mass-generating function.
-Uncertainty implies heavy-tailed probability distributions and heavy-tailed distributions require different analytical methods \cite{nair_etal2022}....para...The heuristic-based adaptive-toolbox approach of \cite{todd_gigerenzer2000} provides an alternative strategy for understanding decision-making under uncertainty.
+Uncertainty implies heavy-tailed probability distributions and heavy-tailed distributions require different analytical methods \citep{nair_etal2022}....para...The heuristic-based adaptive-toolbox approach of \citep{todd_gigerenzer2000} provides an alternative strategy for understanding decision-making under uncertainty.
 There is a strong intuition that uncertainty should activate specific social-learning heuristics.
-Within the cultural-evolution literature, uncertainty is generally thought to lead to a social heuristic known as \emph{conformist-biased learning} \cite{boyd_richerson1985, henrich_boyd1998, muthukrishna_etal2016}....para...True uncertainty arises when an organism lacks the capacity to learn about the possible outcomes of a decision task.
+Within the cultural-evolution literature, uncertainty is generally thought to lead to a social heuristic known as \emph{conformist-biased learning} \citep{boyd_richerson1985, henrich_boyd1998, muthukrishna_etal2016}....para...True uncertainty arises when an organism lacks the capacity to learn about the possible outcomes of a decision task.
 This is very likely for a cosmopolitan species living in a coarse-grain environment.
 Task complexity also.
-Non-stationary environmental change \cite{kay_king2020}.
+Non-stationary environmental change \citep{kay_king2020}.
 These potential sources of uncertainty can also interact.}
 
-% \cm{I moved this for now: \emph{"Furthermore, many models of social learning evolution do not account for individual-level cognition~\cite{Heyes2016}, though humans clearly have evolved cognitive mechanisms for dealing with uncertainty generally~\cite{Gershman2019,Schulz2019}."} because I think it interrupted the flow and didn't seem directly linked to the goal of understanding aspects of uncertainty.
+% \cm{I moved this for now: \emph{"Furthermore, many models of social learning evolution do not account for individual-level cognition~\citep{Heyes2016}, though humans clearly have evolved cognitive mechanisms for dealing with uncertainty generally~\citep{Gershman2019,Schulz2019}."} because I think it interrupted the flow and didn't seem directly linked to the goal of understanding aspects of uncertainty.
 However, if this is one of the main features of the model that we want to highlight as an improvement over previous work, then we probably have to say something more about it.
@@
 social learning. Such fluctuations have been proposed as an important selective
-pressure for learned as opposed to genetically fixed behaviors when genetic adaptation cannot keep pace with environmental change~\cite{Richerson2000}.
-On the other hand, environments that change \emph{too} quickly will select against social learning so that individuals avoid learning outdated---and therefore maladaptive---information~\cite{Feldman1996,
+pressure for learned as opposed to genetically fixed behaviors when genetic adaptation cannot keep pace with environmental change~\citep{Richerson2000}.
+On the other hand, environments that change \emph{too} quickly will select against social learning so that individuals avoid learning outdated---and therefore maladaptive---information~\citep{Feldman1996,
 BoydRicherson1985}. This suggests that intermediate levels of temporal variation
-are important for the evolution of social learning mechanisms~\cite{aoki2005}.
+are important for the evolution of social learning mechanisms~\citep{aoki2005}.
 
@@
 Temporal environmental variability tends to be modeled in one of 
-several ways~\cite{aoki2014evolution}. Most commonly, it is modeled
+several ways~\citep{aoki2014evolution}. Most commonly, it is modeled
 as an independent probability that the environment changes its state (and its corresponding optimal behavior) before each new generation
-~\cite{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}, but
+~\citep{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}, but
 % The probabilities of environmental change are usually fixed per generation
-%~\cite{BoydRicherson1985,Rogers1988,kendal2009evolution}, 
-it has also been modeled using deterministic cycles, so that environments repeat at regular intervals ~\cite{Feldman1996, aoki2014evolution}.
+%~\citep{BoydRicherson1985,Rogers1988,kendal2009evolution}, 
+it has also been modeled using deterministic cycles, so that environments repeat at regular intervals ~\citep{Feldman1996, aoki2014evolution}.
 %Furthermore, t
 The consequences of environmental change can range from mild to catastrophic.
-In the latter case, a change of environment results in the total elimination of any adaptive behavior, which must be learned \emph{de novo} for the new environment~\cite{Rogers1988}.
+In the latter case, a change of environment results in the total elimination of any adaptive behavior, which must be learned \emph{de novo} for the new environment~\citep{Rogers1988}.
 Such catastrophic environmental changes present
@@
 uncertainty as they fluctuate between two or more environmental states with corresponding adaptive behaviors. This means that previously maladaptive
-behaviors become adaptive when the environment changes~\cite{perreault2012bayesian}.
+behaviors become adaptive when the environment changes~\citep{perreault2012bayesian}.
 The chosen mechanism for modelling temporal change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behavior, and instead considers only behaviors that can be learned.
@@
 % core of information theory: the number of bits required to reliably encode the optimal solution increases by one every time the
-% selection set doubles in size~\cite{mackay2003information}. 
+% selection set doubles in size~\citep{mackay2003information}. 
 % This is intuitive; the more options to consider, the greater one's uncertainty about which option is the best choice. 
 In many studies of social learning, the selection set is often limited to just two options.  For example, in empirical studies of bumble bees (\emph{Bombus
-terresteris}) \cite{Baracchi2018} and great tits (\emph{Parus major}) \cite{Aplin2017}, experimenters provided two behaviors from which the bees or birds
+terresteris}) \citep{Baracchi2018} and great tits (\emph{Parus major}) \citep{Aplin2017}, experimenters provided two behaviors from which the bees or birds
 could choose, with one yielding a higher payoff than the other. %respectively,
@@
 Similarly, many human studies have used just two or three possible
-behaviors~\cite{McElreath2005,Morgan2012, Toyokawa2019}. Behavioral study designs are
-often motivated by modeling studies with similar formulations~\cite{Rogers1988,boyd1995does,Feldman1996,
+behaviors~\citep{McElreath2005,Morgan2012, Toyokawa2019}. Behavioral study designs are
+often motivated by modeling studies with similar formulations~\citep{Rogers1988,boyd1995does,Feldman1996,
 perreault2012bayesian}.
@@
 % behavior selection sets. correct if wrong} 
-Larger, more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\cite{derex2013, wasielewski2014}, but these map imperfectly onto the theoretical literature that tends to use a limited set of behavioral options.
+Larger, more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\citep{derex2013, wasielewski2014}, but these map imperfectly onto the theoretical literature that tends to use a limited set of behavioral options.
 %\mt{How so?}. 
-Some models have studied systems with larger, but defined, selection sets~\cite{Rendell2010, lindstrom2016co}, while in others the number of options is subsumed under the probability that a learner gets the right  answer~\cite{Feldman1996,Enquist2007}.
+Some models have studied systems with larger, but defined, selection sets~\citep{Rendell2010, lindstrom2016co}, while in others the number of options is subsumed under the probability that a learner gets the right  answer~\citep{Feldman1996,Enquist2007}.
 %\mt{How does this work exactly in Enquist et al 2007?}. 
-%Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviors through time~\cite{Feldman1996}. 
-Rarely is the size of the selection set explored explicitly as a source of  uncertainty \citep[though see][]{Muthukrishna2016a}, even though the number of options one has is likely to increase with the difficulty of the decision task~\cite{haynes2009testing,white2009testing}.
+%Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviors through time~\citep{Feldman1996}. 
+Rarely is the size of the selection set explored explicitly as a source of  uncertainty \citep[though see][]{Muthukrishna2016a}, even though the number of options one has is likely to increase with the difficulty of the decision task~\citep{haynes2009testing,white2009testing}.
 %These examples share one common feature: the size of the selection set was held static \emph{within} model generations.
@@
 \paragraph{Payoff ambiguity.} Most models of social learning necessarily differentiate between the payoffs for adopting optimal vs. non-optimal behaviors
-\cite{BoydRicherson1985,Rogers1988,Enquist2007,Rendell2010,aoki2014evolution}.
+\citep{BoydRicherson1985,Rogers1988,Enquist2007,Rendell2010,aoki2014evolution}.
 The size of the difference between these payoffs is usually taken to indicate the strength of selection of learning.
@@
 A behavior may yield a large payoff sometimes and a small
-payoff other times \cite{McElreath2005}. This means that signals about the
+payoff other times \citep{McElreath2005}. This means that signals about the
 relationship between behavior and payoff are often noisy, and differentiating
@@
 Smaller differences between payoffs corresponds to larger ambiguity. Payoff
-ambiguity has been manipulated in both theoretical~\cite{perreault2012bayesian}
-and empirical~\cite{McElreath2005, Morgan2012} studies, both of which support the
+ambiguity has been manipulated in both theoretical~\citep{perreault2012bayesian}
+and empirical~\citep{McElreath2005, Morgan2012} studies, both of which support the
 claim that payoff ambiguity increases the reliance on social information.
@@
 %This parameter sometimes takes the form of differences in
-%expected payoffs arising from different behaviors or strategies~\cite{Enquist2007,Rendell2010} or by varying the standard deviation of payoffs~\cite{McElreath2005}.
+%expected payoffs arising from different behaviors or strategies~\citep{Enquist2007,Rendell2010} or by varying the standard deviation of payoffs~\citep{McElreath2005}.
 
@@
 % representations and predictions, and tests and refines those representations and
-% predictions to manage uncertainty \cite{jacobs2011bayesian,clark2013whatever}. 
+% predictions to manage uncertainty \citep{jacobs2011bayesian,clark2013whatever}. 
 We refer to the number of learning opportunities as an individual's effective lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behavior, rather than the number of sunrises one experiences, that determines the level of uncertainty present in one's choices.
@@
 In multi-round studies of information use in novel tasks, US participants' use of social
-information declined precipitously across rounds~\cite{McElreath2005}, suggesting
+information declined precipitously across rounds~\citep{McElreath2005}, suggesting
 they were more likely to use social information when they were most uncertain about the task early on.
 In a more naturalistic context, \citet{Aplin2017} found that younger great tits more readily used social information compared to older individuals, possibly because they had accrued less information via individual learning, and possibly because younger individuals have the most to gain (because of higher reproductive value) by switching to superior behavioral options.
-Cross-cultural studies have highlighted the importance of childhood as a phase of heavy social learning in humans \cite{Reyes2016}.
+Cross-cultural studies have highlighted the importance of childhood as a phase of heavy social learning in humans \citep{Reyes2016}.
 Young children are more likely to
@@
 between young children and the older adults to whom they direct the most trust and
-attention \cite{kline2013teaching}. The effective lifespan for learning
+attention \citep{kline2013teaching}. The effective lifespan for learning
 varies across tasks, individuals, and species, yet most models assume only one learning opportunity per generation \citep{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
@@
 
-While the cultural-evolution literature suggests that several forms of uncertainty have played a role in the evolution of social learning, other cognitive mechanisms have likely also evolved in response to uncertainty \cite{volz2012,johnson2013evolution,van2018uncertainty}.
+While the cultural-evolution literature suggests that several forms of uncertainty have played a role in the evolution of social learning, other cognitive mechanisms have likely also evolved in response to uncertainty \citep{volz2012,johnson2013evolution,van2018uncertainty}.
 Many of these are flexible learning mechanisms that do not require imitating the behaviors of others.
-For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviors with greater observed payoff variance \cite{Wilson2014,Gershman2019}.
+For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviors with greater observed payoff variance \citep{Wilson2014,Gershman2019}.
 
 Many models of social learning simplify by using minimally-cognitive agents.
-For example, a common modelling strategy compares the payoffs of agents with different pure learning strategies (e.g., those who only engage in social learning versus those who only engage in individual learning) while revealing nothing about the cognition underlying individuals' decisions~\cite{BoydRicherson1985, Rogers1988,
+For example, a common modelling strategy compares the payoffs of agents with different pure learning strategies (e.g., those who only engage in social learning versus those who only engage in individual learning) while revealing nothing about the cognition underlying individuals' decisions~\citep{BoydRicherson1985, Rogers1988,
 aoki2005}.
-This sort of behavioral gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to social and cultural evolution \cite{Heyes2016,Kendal2018}.
-Some more complicated learning strategies that make use of both socially and individually learned information have been studied ~\cite{Enquist2007, perreault2012bayesian}, including those that integrate cognitively plausible mechanisms such as reinforcement learning \cite{lindstrom2016co}, though the latter approach remains the exception rather than the norm.
-In order to understand how social learning evolves as an adaptation to uncertainty, we endowed agents with a biologically-plausible cognition capable of integrating information from various sources to maximize payoffs, using \emph{softmax search}~\cite{Gershman2019}, described in more detail below.
+This sort of behavioral gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to social and cultural evolution \citep{Heyes2016,Kendal2018}.
+Some more complicated learning strategies that make use of both socially and individually learned information have been studied ~\citep{Enquist2007, perreault2012bayesian}, including those that integrate cognitively plausible mechanisms such as reinforcement learning \citep{lindstrom2016co}, though the latter approach remains the exception rather than the norm.
+In order to understand how social learning evolves as an adaptation to uncertainty, we endowed agents with a biologically-plausible cognition capable of integrating information from various sources to maximize payoffs, using \emph{softmax search}~\citep{Gershman2019}, described in more detail below.
 
@@
 The behavior set is a multi-armed bandit with $B$ arms.
-That is, agents can pick one of $B$ behaviors with random-valued payoffs~\cite{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
+That is, agents can pick one of $B$ behaviors with random-valued payoffs~\citep{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
 In each generation, exactly one behavior is more likely to pay off than all the rest and is therefore optimal.
@@
 The probability that the agent will perform a behavior is a function of the agent's beliefs about a behavior's average payoff in that time step and a fixed parameter that influences the amount of exploratory behavior (more details below).
-The softmax function used here is a biologically plausible generalization of behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative behavior (based on their observations) but also to sometimes explore alternatives~\cite{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
+The softmax function used here is a biologically plausible generalization of behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative behavior (based on their observations) but also to sometimes explore alternatives~\citep{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
 
@@
 behaviors with high expected payoffs (larger $\beta$) versus how frequently
-agents explore alternative behaviors (smaller $\beta$). %~\cite{McElreath2005}. 
+agents explore alternative behaviors (smaller $\beta$). %~\citep{McElreath2005}. 
 We used a default value of $\beta = 10$, but also varied this value in our sensitivity analyses.
@@
 relative to the other $N_T - 1$ prospective teachers, with ties broken randomly.
-By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \cite{smaldino2019open}.
+By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \citep{smaldino2019open}.
 Social learners adopt their chosen teacher's expected payoffs observations $\ledger$, \ps{I feel
@@
 population reaches evolutionary fixation with repsect to social learning, where
-$\sum_i s_i = 1$ or $\sum_i s_i = 0$, or until 20k iterations have run. 
-It is rare for simulations not to reach fixation. We report how frequently
-this happens in Table~\ref{tab:convergence}.
+$\sum_i s_i = 1$ or $\sum_i s_i = 0$.
 
@@
 
-        $\meanG$ & Mean number of generations to convergence & max 100k / 8 \\
+        $\meanG$ & Mean number of generations to convergence & Unbounded \\
         \bottomrule
@@
 
-Our model was implemented in the Julia programming language~\cite{Bezanson2017} 
-using the Agents.jl agent-based modeling library~\cite{Datseris2022} and run
+Our model was implemented in the Julia programming language~\citep{Bezanson2017} 
+using the Agents.jl agent-based modeling library~\citep{Datseris2022} and run
 on the Sherlock supercomputing cluster at Stanford University. Model code and
@@
 Drift is maximal, and in fact the only evolutionary force in our model, when social and asocial learning are equally beneficial.
-While we do not consider that possibility, even under a consistent but weak selection pressure drift can cause a population to take longer to reach fixation \cite{plutynski2007drift}.
+While we do not consider that possibility, even under a consistent but weak selection pressure drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}.
 We therefore measured drift by the average number of generations to fixation, denoted $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
@@
 Detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly changing world.
-Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\cite{Moya2020,Jones2021}, especially in
-the most vulnerable communities~\cite{McNamara2020}, and to capitalize on new behavioral opportunities such as transitioning to clean energy use and
-production~\cite{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\citep{Moya2020,Jones2021}, especially in
+the most vulnerable communities~\citep{McNamara2020}, and to capitalize on new behavioral opportunities such as transitioning to clean energy use and
+production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
 \cm{should we draw out some implications?
@@
 For example, one cannot help but experience, at likely asocially learn about the association between; clouds and rain, drinking water and hunger, or smiling and being avoided.
-This model thus avoids scrounger / producer dynamics common in other models ~\cite{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and asocial learners.
+This model thus avoids scrounger / producer dynamics common in other models ~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and asocial learners.
 Second, we only allow for intergenerational social learning and environmental change.
@@
 For example, we only considered success-biased
-learning, although people may use conformity or other context biases to socially learn ~\cite{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.
+learning, although people may use conformity or other context biases to socially learn ~\citep{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.
 This modelling choice maximizes the potential benefit to social learners suggesting other mechanisms, like conformity, may lead to more drift overall.
 We also assumed that the number of behaviors and
-their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g.\ via niche construction~\cite{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
+their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g.\ via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
 %supported by dynamic network structure
-~\cite{Smolla2019,Derex2020}.  Group structure
+~\citep{Smolla2019,Derex2020}.  Group structure
 and processes such as homophily and in-group bias/out-group aversion could inhibit the
 evolution of social learning since successful out-group teachers could be cut off from
-in-group learners~\cite{Golub2012}. We assumed agents choose behaviors via softmax
-search, but even though this algorithm is more sophisticated than most used in social learning models, it is algorithm compared to real human learning mechanisms ~\cite{Schulz2020a,Wu2022}.
+in-group learners~\citep{Golub2012}. We assumed agents choose behaviors via softmax
+search, but even though this algorithm is more sophisticated than most used in social learning models, it is algorithm compared to real human learning mechanisms ~\citep{Schulz2020a,Wu2022}.
 Instantiating even more powerful asocial learning could further
@@
 
-\bibliographystyle{apacite}
+\bibliographystyle{apalike} %cite}
 % \bibliography{/Users/mt/workspace/Writing/library.bib}
@@
 \clearpage
-
-\section{Convergence information}
-
-Model populations reached fixation within few to 140 generations on
-average (Figure~\ref{fig:steps}).
-Note 140 generations is equivalent to 2800 time steps. We set the maximum 
-number of iterations globally to $20~000$, which is 1000 generations when
-$L=20$. Although we can be relatively sure that this maximum number of 
-generations is rarely reached based on our main text analysis of $\meanG$,
-we additionally tabulated the number of simulations that did not converge to
-fixation
-within this step limit. We found that 0.1\% of simulations did not converge
-when $B=2$, 0.2\% did not converge when $B=4$, and 2.0\% did not converge
-when $B=10$ (Table~\ref{tab:convergence}). When a trial did not converge we
-still included that trial's $\meansl$ value in the average across trials,
-but for these $0 < \meansl < 1$.
-
-\begin{table}[h] \caption{Maximum number of iterations = 20000.} \label{tab:convergence} \centering
-  \begin{tabular}{cccc} 
-    \toprule $B$ & \# not at fixation (out of 132k) & \% not fixated \\ 
-    \midrule  2  & 0  & 0.0 \% \\ 
-              4  & 0  & 0.0 \% \\ 
-              10 & 20 & 0.02 \% \\ 
-    \bottomrule \end{tabular} 
-\end{table}
 

### 2022-10-10 meanNetPayoffs.tex
edited model and analysis

@@
     \begin{center}
-      {\Huge \textbf{+} \huge Location where homogenous social and asocial payoffs
-      are equal} \quad \quad 
+       \includegraphics[width=1.85in]{Figures/legendElements/dot.pdf}
+       {\huge Average all-social population payoffs}  \\[1.125em]
+       \includegraphics[width=1.85in]{Figures/legendElements/ldash.pdf} 
+       {\huge Average all-asocial population payoffs} \\[1.125em]
+       \includegraphics[width=1.85in]{Figures/legendElements/solid.pdf} 
+       {\huge Simulated average population payoffs} \\[1.125em]
+      {\Huge \textbf{+} \huge $u$ value where homogenous social and asocial payoffs
+      are equal} 
     \end{center}

### 2022-10-10 ms.tex
edited model and analysis

@@
 
-In our model we allow just one trait to evolve; social learning, while all other parameters are exogenous.
-Our primary outcome measure is the overall frequency of the social learning trait at the end of each simulation, and we study how this prevalence responds to the four varieties of uncertainty considered in this paper.
+In our model we allow just one trait to evolve, social learning; 
+all other parameters are exogenous. Our primary outcome measure is the observed
+frequency that the social learning trait fixates in simulated populations. We study
+how the social learning fixation frequency responds to the four varieties of
+uncertainty considered in this paper. \mt{I changed this somewhat, please double
+check it's clear}
 
@@
 At the end of each generation, agents are selected with replacement to reproduce a new generation of $N$ agents, with the probability of reproduction biased by net payoffs.
-Agents who inherit the social-learning trait learn about payoffs from the previous generation, while asocial learners begin life only knowing the number of behaviors the environment affords, but have no knowledge of behavioral payoffs.
+Agents who inherit the social learning trait learn about payoffs from the previous generation, while asocial learners begin life only knowing the number of behaviors the environment affords, but have no knowledge of behavioral payoffs.
 
@@
 \caption{Environmental Parameters. These include our four main uncertainty parameters under investigation; $u$, $B$,
-$\pilow$, and $L$. Bold indicates default value tested} %\emph{default value tested}.}
+$\pilow$, and $L$. Bold indicates default value tested.} %\emph{default value tested}.}
     \label{tab:uncertaintyParameters}
@@
 %Agents are endowed with dynamic attributes to intelligently select behaviors and calculate average payoffs for each behavior. 
-Agents are endowed with the capacity to learn asocially, while a subset also adds the capacity to use social information.
-For simplicity, we refer to the latter as social learners.
-Learning strategies are assumed to be heritable.
-Each agent $i$ has a learning trait $s_i$, which is 1 if $i$ is a social learner and zero otherwise.
-Every agent engages in individual learning over its lifespan, regardless of learning strategy.
-Social learners begin life with behavioral preferences based on information from an agent chosen from the previous generation.
+All agents learn individually over their lifespan, and those with
+the heritable social learner trait use social information to constrain their individual
+learning. For simplicity, we refer to agents with the social learner trait 
+as social learners. 
+% Learning strategies are assumed to be heritable. Each agent $i$ has a learning trait $s_i$, which is 1 if $i$ is a social learner and zero otherwise. 
+% Every agent engages in individual learning over its lifespan, regardless of learning strategy. 
+Social learners begin life with behavioral preferences based on information learned from an agent chosen from the previous generation.
 Asocial learners begin life with no behavioral preferences.
@@
 For concreteness we denote this probabilistic payoff $\bandit$.
-After performing behavior $b$, agent $i$ updates the
-corresponding \emph{behavior count} by 1, $c_{ib} \leftarrow c_{ib} + 1$, and then
-the expected payoffs calculated for that behavior are updated with
+After performing behavior $b$, agent $i$ updates its
+corresponding \emph{behavior count} for $b$ by 1, $c_{ib}' \leftarrow c_{ib} + 1$.
+Then the observed average payoffs known by agent $i$ for behavior $b$ are updated with
 exponentially-weighted averaging
 \begin{equation}
-  \ledger \leftarrow \ledger + \frac{\bandit - \ledger}{c_{ib}},
+  \ledger' \leftarrow \ledger + \frac{\bandit - \ledger}{c_{ib}'},
 \end{equation}
 \noindent
-where $\bandit$ is the actual payoff received by agent $i$ for behavior $b$ on the given time step.
-
-\paragraph{Intergenerational dynamics}
-Between generations, agents first reproduce via asexual haploid reproduction, which determines the transmission of the social learning trait. Social learners then learn from the
-previous generation, after which all agents from the
-previous generation die off (Figure~\ref{fig:schematic}C). More specifically, this all happens as follows. 
-$N$ reproducers are selected with replacement over $N$ independent draws, 
-biased by performance:
-\begin{equation}
-  \Pr(\text{Agent $i$ is chosen to reproduce in one draw}) = \frac{\pi_i}{\sum_{i=1}^N \pi_i}.
-\end{equation}
-\noindent
-A child inherits its parent's social learning trait $s_i$ without mutation.
-A social learner child with $s_i = 1$ learns from a teacher from its parent's
-generation, including possibly their parent (i.e., both vertical and oblique learning are possible). 
-A child chooses its teacher by first randomly selecting $N_T$ prospective
-teachers from the population, then selecting one from this set with a probability weighted by each prospective teacher's net payoff, $\pi_i$,  
-relative to the other $N_T - 1$ prospective teachers, with ties broken randomly.
-By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \citep{smaldino2019open}.
-Social learners adopt their chosen teacher's expected payoffs observations $\ledger$, \ps{I feel
-like there should be some indication that the ledger is a vector rather than a scalar. Maybe put
-it in bold or capitalize the $\Pi$? Using the overbar makes it look like a single average.}
-\mt{The subscript $b$ makes it clear it's a vector over behaviors. Maybe we lose the bar,
-or I may change the notation to at least approximately follow Q-learning notation.}
-and set all $c_{ib} = 1$ so expected payoffs remain within $[0, 1]$.
-Setting $c_{ib}$ to 1 reflects the fact that the social learning is treating the teacher's information as a single observation with the associated uncertainty.
-Asocial
-learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ 
-(Figure~\ref{fig:schematic}C). \ps{How to account for division by zero?} \mt{Count increases
-before average are taken, which I think is clear enough in paragraph \textbf{Within-generation
-dynamics}.} The
-newly initialized population then repeats the within-generation dynamics.
+where $\bandit$ is the actual payoff received by agent $i$ for behavior $b$ on the
+given (implicit) time step.
+
+\paragraph{Intergenerational dynamics} Between generations, agents first reproduce
+via asexual haploid reproduction, which determines the transmission of the social
+learning trait. Social learners then learn from the previous generation, after which
+all agents from the previous generation die off (Figure~\ref{fig:schematic}C). More
+specifically, this all happens as follows.  $N$ reproducers are selected with
+replacement over $N$ independent draws, biased by performance: \begin{equation}
+\Pr(\text{Agent $i$ is chosen to reproduce in one draw}) =
+\frac{\pi_i}{\sum_{i=1}^N \pi_i}.  \end{equation} \noindent A child inherits its
+parent's social learning trait $s_i$ without mutation.  A social learner child with
+$s_i = 1$ learns from a teacher from its parent's generation, including possibly
+their parent (i.e., both vertical and oblique learning are possible).  A child
+chooses its teacher by first randomly selecting $N_T$ prospective teachers from the
+population, then selecting the one in this set with the greatest payoff net, with ties broken randomly. By first subsetting $N_T$
+prospective teachers we represent the fact that access to the entire population is
+not generally guaranteed, though this type of algorithm yields qualitatively
+similar results to ones that do not first produce subsamples
+\citep{smaldino2019open} and we show in the supplement 
+that our results are robust to different $N_T$
+(Figure~\ref{fig:nteachersSensitivity}).  Social learner $i$ adopts their chosen 
+teacher $j$'s observed average payoffs (average indicated by the overbar) 
+for each behavior, $b$, and $c_{ib}$ is set to 1 if teacher $j$ had at least one
+observation of behavior $b$,  
+and $c_{ib}$ is set to 0 otherwise. This way, expected payoffs remain within $[0,
+1]$, but social learners are flexible to adjust to environmental change. 
+Setting $c_{ib}$ to 1 reflects the fact that the social learning is 
+treating the teacher's information as a single observation with the associated
+uncertainty. Asocial learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and
+$\ledger = 0$ for each behavior, $b$.
+(Figure~\ref{fig:schematic}C). The newly initialized population
+then repeats the within-generation dynamics.
 
@@
 social or asocial learners (i.e.\ the system reaches fixation), 
-otherwise repeat another generation and evolution (3).} \cm{What does (3) denote at end of Fig 1 caption?
+otherwise repeat another generation and evolution.} 
+% \cm{What does (3) denote at end of Fig 1 caption?
 Does having only green agents in Fig1B give the impression that only social learners are learning within lifetime?
@@
 We performed sensitivity analyses to ensure that our main analysis is reasonably
-robust to a range of auxiliary parameters.
-\ps{Say these are presented in the supplementary material?} First, we varied the population size, $N$, to explore whether smaller $N$ would show more drift due to finite population size effects.
+robust to a range of auxiliary parameters. These analyses are presented in 
+supplemental material.
+First, we varied the population size, $N$, to explore whether smaller $N$ would show more drift due to finite population size effects.
 %, but  still generally support our main conclusions.
@@
 by undermining individual learning. Nonetheless, our results
-should be valid over some range of $\beta$.
+are valid over a substantial range of $\beta$.
 
@@
 This reversal is partially explained by higher levels of drift when there is little difference in the payoffs between behaviors, and by the fact that the quality of social information is poorer when payoffs are ambiguous and lifespans are short (more on these effects of payoff ambiguity below).
-\cm{is this right?
-I thought we should say something about the exceptions in this paragraph though we describe in more detail below, but not sure I have the right explanation}
-
-Of the four types of uncertainty studied in this paper, payoff ambiguity has the most complex effect on the evolution of social learning.
-Recall that we operationalize payoff ambiguity with $\pilow$, the expected payoff for non-optimal behaviors (literally the probability that those behaviors yielded a payoff of 1).
+% \cm{is this right? I thought we should say something about the exceptions in this paragraph though we describe in more detail below, but not sure I have the right explanation}
+
+Of the four types of uncertainty studied in this paper, payoff ambiguity has the most
+complex effect on the evolution of social learning. Recall that we operationalize
+payoff ambiguity with $\pilow$, the expected payoff for non-optimal behaviors
+(equivalently the probability that those behaviors yielded a payoff of 1).
 This was relative to $\pihigh = 0.9$, the expected payoff for the optimal behavior.
@@
 
-% First, we confirmed existing theoretical predictions that increased $u$ 
-% monotonically decreased $\meansl$ across all other uncertainty parameter values.
-% The other uncertainty parameters changed the $u$ value at which $\meansl$
-% began to decrease, and how rapidly $\meansl$ decreased over $u$.  For example,
-% when payoff ambiguity and selection set size were both small ($\pilow = 0.1$
-% and $B=2$), social learning evolved only when $u$ was small. 
-% % These parameter settings present a relatively easy problem for individuals.
-% % Furthermore, it is relatively costly for agents to be misled by outdated
-% % social information in this case, especially for longer lifespans for finding
-% % the optimal behavior (Figure~\ref{fig:mainResults}, upper left). 
-% When $\pilow = 0.8$ and $B=2$, for exapmle, $\meansl$ decreased less rapdily
-% over $u$ due to drift caused by weak selection due to little advantage for
-% performing the optimal versus non-optimal behavior (see rows of
-% Figure~\ref{fig:mainResults}). We analyzed several such patterns of social
-% learning evolution and suppression across different uncertainty settings.
-
-% Increased selection set size $B$ led nearly uniformly to more prevalent social
-% learning, with all other uncertainty parameters held constant. This is because, first,
-% it is more difficuilt to find the optimal behavior with a larger $B$.  Second, this
-% effect is amplified because agents in a world with larger $B$ are more cognitively
-% flexible compared to those in a smaller $B$ world.  When $B$ is larger, agents are
-% relatively more likely to choose an alternative to their current known optimum.  To
-% understand this, consider the case where a social learner child learns that behavior 1
-% has an expected payoff of 0.8, and the rest have an expected payoff of 0, but the
-% optimal behavior changes between generations. Assume the child tries behavior 1, but
-% it pays off 0.  If $B=2$, then at the next time step, $\ledger =
-% (0.4, 0.0)$. The probability the agent explores behavior 2 is now 0.02. However, if
-% $B=10$ the agent has $\ledger = (0.4, 0.0, \ldots, 0.0)$, and the probability the agent
-% explores one of the nine alternative behaviors increases to 0.14.  If the agent again
-% tries behavior 1 and it pays 0, the probability of exploring alternatives with $B=2$
-% is 0.21, but with $B=10$ the probability of exploring alternatives more greatly increases
-% to 0.71. \mt{I double checked these calculations, but would appreciate if someone
-%   triple checked it}. 
-% This explanation does not apply when $L=1$, where individual learning does not occur.
-
-% Payoff ambiguity had a modest effect when $\pilow = 0.1$ increased to $\pilow =
-% 0.45$, causing social learning to be favored across more values of $u$ (first two rows of
-% Figure~\ref{fig:mainResults}).  This is because increased payoff ambiguity increases
-% the difficulty, and reduces the overall benefit, of discerning which behavior is
-% optimal.  When $\pilow = 0.8$ the
-% $\meansl$ curves become smoother, indicating more evolutionary drift towards 
-% possibly non-optimal fixations (bottom row of
-% Figure~\ref{fig:mainResults}). For smaller values of $u$, this results in less
-% frequent evolution of social learning for the same values of $u$ and $B$. But past
-% the value of $u$ where $\meansl \approx 0.5$ this switches, and social learning evolves more
-% frequently than for smaller $\pilow$. 
-% % When $\pilow \to \pihigh$, agents 
-% % accumulate increasingly more payoffs, whether they are social learners or not. 
-% Greater payoff ambiguity means lower risk to try possibly outdated social
-% information by reducing the penalty for performing non-optimal behaviors, leading
-% to the observed drift in aggregated results.
-
-% We observed two distinct trends in the evolution of social learning as
-% $L$ was varied.  First, when $\pilow$ was sufficiently small ($\pilow=0.1, 0.45$),
-% we observed that shorter lifespan extended the evolution of social learning over more values of
-% $u$, since payoff-biased social learning means teachers are reliable.
-% When $\pilow=0.8$, shorter lifespans decreased $\meansl$ in some cases and
-% increased $\meansl$ in other cases due to greater evolutionary drift. In
-% this setting, many agents will obtain a payoff of 1 at each time step in their 
-% lifetime, which, combined with finite population size, will make it more likely for 
-% evolution to guide the population to non-optimal social/asocial learning stragegy.
-% % In the first
-% % case, $\meansl$ was reduced for $L=1$ for small values of $u$, when other $L > 1$
-% % led to $\meansl \approx 1$. At larger $u$ , the $L=1$ case yields non-zero
-% % $\meansl$, while for the other $L > 1$, $\meansl \approx 0$. 
-% Smaller $L$ means agents end their lives more uncertain about which behavior was
-% optimal, but payoff-biased teacher selection and learning can remedy this if
-% payoff ambiguity is sufficiently small.
-% % When $L$ is smaller, agents have fewer opportunities to learn through trial and
-% % error, so it is more difficult for them to discern which strategy is optimal, social
-% % or asocial.
-
 \begin{figure}
@@
   Other uncertainty values payoff ambiguity, $\pilow$, (rows), number of behavioral options, $B$, (columns), and effective lifespan, $L$, (keys) shift and flatten the slope from all-social-learner populations to all-asocial-learner
-  populations.
-Vertical lines represent when the payoffs of simulated populations of all asocial and social learners experienced equivalent payoffs \cm{is this right?
-I don't understand the arg max u lines} }
+  populations.}
   \label{fig:mainResults}
@@
 
-\subsection{The relative benefit of social learning and the presence of evolutionary drift}
-
-% To explain the evolution of social learning we implicitly assumed above that, first,
-% the relative benefit of having the social learning trait is essential to its
-% evolution; and, second, we assumed that values of $\meansl \neq 0,1$ indicate
-% evolutionary drift---but do our data support these assumptions?  
-%Indeed, w
+\subsection{Evolutionary drift and the relative benefit of social learning}
+
 The effect of drift on the evolution of social learning %evolution and evolutionary drift 
-depended on the strength of natural selection, that is, on the extent to which the social learning trait provided agents with a consistent benefit.
-Drift infuses randomness into natural selection.
-In this model, such randomness is introduced at various stages including when agents receive payoffs for a given behavior, when they are reproducing, and when they are being selected as teachers.
-Drift is maximal, and in fact the only evolutionary force in our model, when social and asocial learning are equally beneficial.
-While we do not consider that possibility, even under a consistent but weak selection pressure drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}.
+depended on the strength of natural selection, that is, on the extent to which the
+social learning trait provided agents with a consistent benefit. Drift infuses
+randomness into natural selection. In this model, such randomness is introduced at
+various stages including when agents receive payoffs for a given behavior, when they
+are reproducing, and when they are being selected as teachers. Drift is maximal, and
+in fact the only evolutionary force in our model, when social and asocial learning
+are equally beneficial.
+Even under consistent but weak selection pressure, drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}.
 We therefore measured drift by the average number of generations to fixation, denoted $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
@@
 
-First, we confirmed that social learning evolves when the expected payoffs to social
-learners exceed those of asocial learners, which we write $\meansoc > \meanasoc$.
-In the case of $L=1$ we can calculate $\meanasoc$ directly: it is just the expected
-payoff across all behaviors. For all other cases, we calculate expected social and asocial payoffs by respectively setting
-$\sum_i s_i = N$ or $\sum_i s_i = 0$ at model initialization.
+Figure~\ref{fig:steps} shows drift in terms of the average number of generations to fixation, 
+$\meanG$, across all uncertainty
+parameters. Drift was greatest overall when payoff ambiguity was greatest, i.e., when $\pilow = 0.8$.
+When payoffs are highly ambiguous there is relatively little advantage to the
+optimal learning strategy, and therefore relatively weak selective pressure.
+
+$\meanG$ peaks at the values of $u$ where social learning becomes suppressed. $B$, and $\pilow$ have the
+clearest effects on the location of greatest drift over $u$. $L$ has some effect on the location of peak
+drift over $u$, but $L$ also has a large effect on the overall amount of drift: $L=1$ tends to have the most
+drift with sufficiently low payoff ambiguity ($\pilow < 0.8$). The effect of lifespan on drift is
+non-monotonic, since we observe that long lifespans can also result in relatively greater drift
+compared to lifespans other than $L=1$ (e.g., in Figure~\ref{fig:steps}, top left and right).
+When $L=1$ selection pressure may be relatively weak since agents have no opportunity
+for individual learning, and social learning is the only learning channel. 
+When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning has many 
+opportunities for finding the optimal behavior, which means social learning
+provides a relatively weaker constraint on net payoffs over agent lifespans.
+This also results in weaker selection pressure since there is relatively little
+difference between social and asocial constraints when $L$ is large.
+
+We also tracked and analyzed average net payoffs of agent populations across
+all uncertainty parameters, and compared the simulated payoffs to 
+all-social learner or all-asocial learner populations. 
+Figure~\ref{fig:payoffs} shows the average net payoffs normalzied by lifespan
+for our simulations and two reference conditions where agents are initialized
+as homogenous populations fixated either as all social or all asocial learners.
+Often the simulated payoffs follow the payoffs from the better-performing
+homogenous group, but there are several important deviations to understand.
+First, we observed frequency dependence of social learning, where 
+agents from our main simulations who evolved to be social learners 
+outperform agents in the homogenous social learner populations. This is most
+pronounced when $L=1$, across all other uncertainty parameters, and even more
+pronounced when $\pilow=0.45$ and $B=10$ (Figure~\ref{fig:payoffs}, middle right).
+In these cases, the presence of individual learners before social learning fixation
+enabled social learners in our simulations to outperform all-social learner populations.
+Next, we observed cases where long-lived populations ($L=8$) in simple environments
+($B=2$) evolved to be individual learners, even though all-social learner populations
+outperformed all-individual learner populations (Figure~\ref{fig:payoffs}, upper left).
+By inspecting time series of individual model runs, we observe that
+asocial learning fixates in response to a period of protracted environmental
+instability, which causes social learning to more frequently provide
+outdated information (Figure~\ref{fig:timeseries}a).
+Conversely, sometimes when lifespan was short ($L=1$) and environmental variability
+was moderately high ($u\approx0.5$), a period of environmental
+stability led populations to fixate to social learning, despite individual learning
+being the superior long-term strategy (Figure~\ref{fig:payoffs}, center top and middle). 
+This behavior was again confirmed by examining time series of simultations
+initialized with the commensurate uncertainty parameters, which show that
+social learning fixates during periods of protratcted environmental stability
+(Figure~\ref{fig:timeseries}b).
+
+%We measured drift by the average number of generations to fixation, $\meanG$. Recall fixation is defined as the population becoming homogenous, composed of all social or all asocial learners. 
+% $\meanG$ peaks around the values of $u$ 
+% when $\meansoc \approx \meanasoc$, \cm{wait does it? Fig S2 doesn't seem to show the vertical lines mapping on well} which led $\meansl$ to transition from 1 to 0.
+% In some cases, especially when $\pilow=0.8$,
+% there is no distinct peak in $\meanG$ across $B$ and $L$ settings, 
+% indicating little difference in task difficulty across a range of uncertainty
+% parameter settings (Figure~\ref{fig:steps}, bottom row).
+
+% First, we confirmed that social learning evolves when the expected payoffs to social
+% learners exceed those of asocial learners, which we write $\meansoc > \meanasoc$.
+% In the case of $L=1$ we can calculate $\meanasoc$ directly: it is just the expected
+% payoff across all behaviors. For all other cases, we calculate expected social and asocial payoffs by respectively setting
+% $\sum_i s_i = N$ or $\sum_i s_i = 0$ at model initialization.
 These populations remain homogeneous since we do not allow for mutation.
@@
 Maybe we put the 3x3 back in for Fig 3?}
-In general, we observed that social learning evolved in our simulations when the expected payoffs exceeded expected individual-learner
-payoffs (Figure~\ref{fig:payoffs}).
+% In general, we observed that social learning evolved in our simulations when the expected payoffs exceeded expected individual-learner
+% payoffs (Figure~\ref{fig:payoffs}).
 This mapping of expectations to model results is reflected in Figure~\ref{fig:mainResults} given the vertical lines map onto the transitions from social to asocial learning in the curves.
@@
 
-\begin{enumerate}
-    \item 
-      Note frequency dependence of social learning fixation payoffs due to presence of asocial learners
-      (payoffs plots)
-    \item
-      Explain why social to asocial transition occurs away from where homogenous payoffs are equal
-      (payoffs plots)
-    \item
-      Highlight how observations of increased drift/weaker selection observed in <s> plots is supported by 
-      elevated <G> (generations to fixation plots)
-\end{enumerate}
-% However, we also found that populations of initially all social learners performed worse
-% in many uncertainty contexts than either the actual payoffs accumulated by 
-% model agents, and lower than even the expected individual-level payoffs,
-% even though social learning evolved in many of the same contexts in our model,
-% especially when $\pilow = 0.8$ 
-% (Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row). \ps{What is the point of this last finding? I'm having trouble figuring out what all this has to do with drift.}
-
-% \begin{figure}
-%   \caption{Expected payoff rates for homogeneous populations of social or asocial learners.
-Dashed lines with no markers are expected payoff rates for a population of individual learners.
-Dashed lines with diamond markers are expected payoff rates to a population of social learners.
-Solid lines with circle markers are the actual average payoff rates for agents in our evolutionary simulations.
-% %  Comparison of expected payoffs from our computational anaysis (solid     lines with circles), expected individual payoffs with no social learning     (dashes without markers), and expected payoffs for all-social learner     populations.
-% Only four plots are shown to enhance detail; see supplement for
-%     five additional plots.
-% } 
-%   \label{fig:payoffs}
-% \centering
-%     \includegraphics[width=0.85\textwidth]{Figures/meanNetPayoffs.pdf}
-% \end{figure}
-
-Figure~\ref{fig:steps} shows the average time to fixation, $\meanG$, for all our our uncertainty parameters.
-We confirmed that drift is highest, as proxied by high $\meanG$, when runs are similarly likely to fixate at $\meansl$ = 0 or 1,
-and when the payoff ambiguity $\pilow$ was highest (Figure~\ref{fig:steps}). 
-%We measured drift by the average number of generations to fixation, $\meanG$. Recall fixation is defined as the population becoming homogenous, composed of all social or all asocial learners. 
-$\meanG$ peaks around the values of $u$ 
-when $\meansoc \approx \meanasoc$, \cm{wait does it? Fig S2 doesn't seem to show the vertical lines mapping on well} which led $\meansl$ to transition from 1 to 0.
-In some cases, especially when $\pilow=0.8$,
-there is no distinct peak in $\meanG$ across $B$ and $L$ settings, 
-indicating little difference in task difficulty across a range of uncertainty
-parameter settings (Figure~\ref{fig:steps}, bottom row).
+\begin{figure}
+  \caption{Average number of generations ($\meanG$, y-axes) to fixation. 
+    Note the y-axis ticks vary between plots, indicating different overall 
+    time to fixation for different $(\pilow, B)$ pairs.} 
+  \label{fig:steps}
+\centering
+    \includegraphics[width=\textwidth]{Figures/stepResultsPlots.pdf}
+\end{figure}
+
+\clearpage
+\begin{figure}
+  \caption{Comparison of observed average payoffs in simulations with average payoffs
+    obtained by populations homogenously initialized to be all social or all asocial learners.
+    Often the simulated payoffs follow the payoffs from the better-performing
+    homogenous group, with some exceptions discussed in the main text.
+}
+  \label{fig:payoffs}
+  \centering
+    \includegraphics[width=\textwidth]{Figures/meanNetPayoffs.pdf}
+\end{figure}
 
@@
 
-Our model necessarily made simplifying assumptions.
-These were chosen judiciously to address the main question of how uncertainty affects the evolution of social learning.
-Two critical assumptions we made have important consequences for comparing our results with previous findings in the literature.
-First, we assume all agents engage in asocial learning.
-This means that asocial learning is effectively free, though potentially inaccurate.
-Although producing new knowledge may be costly, many other adaptive problems take the form of essentially cost free asocial learning.
-For example, one cannot help but experience, at likely asocially learn about the association between; clouds and rain, drinking water and hunger, or smiling and being avoided.
-This model thus avoids scrounger / producer dynamics common in other models ~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and asocial learners.
-Second, we only allow for intergenerational social learning and environmental change.
-Within generations agents can only learn asocially, meaning they cannot learn from their peers.
-This assumption allows us to replicate the classic finding that if the environmental change too quickly, socially learned information will be useless.
-Alternative formalizations for the timing of  social learning and environmental change would break this relationship.
-\cm{can cite the Cog Sci version of the paper here to acknowledge the change.}
+Our model necessarily made simplifying assumptions. These were chosen judiciously to address the main
+question of how uncertainty affects the evolution of social learning. Two critical assumptions we made have
+important consequences for comparing our results with previous findings in the literature. First, we assume
+all agents engage in asocial learning. This means that asocial learning is effectively free, though
+potentially inaccurate. Although producing new knowledge may be costly, many other adaptive problems take
+the form of essentially cost free asocial learning. For example, one cannot help but experience, at likely
+asocially learn about the association between; clouds and rain, drinking water and hunger, or smiling and
+being avoided. This model thus avoids scrounger / producer dynamics common in other models
+~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and
+asocial learners.  Second, we only allow for intergenerational social learning and environmental change.
+Within generations agents can only learn asocially, meaning they cannot learn from their peers. This
+assumption allows us to replicate the classic finding that if the environmental change too quickly, socially
+learned information will be useless. Alternative formalizations for the timing of social learning and
+environmental change would break this relationship~\citep{Turner2022}.
 
@@
 
-In this Supplement we support our model conclusions with auxiliary data
-showing, first, sufficient model convergence and, second, that our model
+In this Supplement we support our model conclusions by showing that our model
 outcomes are stable over various settings of the three free auxiliary model
@@
 
-\section{Expected payoffs}
-\begin{figure}
-  \caption{Expected payoff rates for homogeneous populations of social or asocial learners.
-Dashed lines with no markers are expected payoff rates for a population of individual learners.
-Dashed lines with diamond markers are expected payoff rates to a population of social learners.
-Solid lines with circle markers are the actual average payoff rates for agents in our evolutionary simulations.
-When $\pilow = 0.8$, all-social learner populations underperform
-    since social learners are not subject to an initial evolutionary bottleneck
-    due to the presence of asocial learners, and behavioral misinformation
-    is allowed to circulate more freely than in the base case tested by 
-    our model with an initially even distribution of social and asocial learners.
-    \mt{Correct or nah?}
-}
-  \label{fig:payoffs}
-  \centering
-    \includegraphics[width=\textwidth]{Figures/meanNetPayoffs.pdf}
-\end{figure}
-
-\clearpage
-
-\section{Drift measured by expected generations to fixation}
-\begin{figure}
-  \caption{Average number of generations ($\meanG$, y-axes) to fixation . 
-    $\meanG$ increases and peaks around values of $u$ (x-axes) where
-  $\meansoc \approx \meanasoc$. Note the y-axis ticks vary between plots,
-indicating different overall time to fixation for different $(\pilow, B)$
-pairs. Only extremal \cm{is this a technical term or you mean extreme? but actually 4 L-values shown} tested values of $L$ shown for clarity.} 
-  \label{fig:steps}
-\centering
-    \includegraphics[width=\textwidth]{Figures/stepResultsPlots.pdf}
-\end{figure}
+% \section{Expected payoffs}
 

### 2022-10-11 ms.tex
added timeseries figure

@@
 
+\begin{figure}
+    \caption{Example time series of geometric moving average (GMA) with window of 3
+      of payoffs from three select simulations (see main text), broken out by 
+    social learners, asocial learners, and whole population, compared with the
+    expected homogenous social and asocial population payoffs. 
+    Social learner prevalence is also plotted. Vertical lines indicate
+  environmental change.}
+    \label{fig:payoffTimeseries}
+  \centering
+
+\vspace{1em}
+\hspace{-2em}
+  \begin{subfigure}[]{0.75\textwidth}
+      \centering
+      \caption{$\pilow=0.1$, $B=2$, $L=4$, $u=0.2$}
+      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=4.pdf}
+    \end{subfigure} \\
+
+\hspace{-2em}
+    \begin{subfigure}[]{0.75\textwidth}
+      \centering
+      \caption{$\pilow=0.1$, $B=2$, $L=8$, $u=0.2$}
+      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=8.pdf}
+    \end{subfigure} \\
+
+\hspace{-2em}
+    \begin{subfigure}[]{0.75\textwidth}
+      \centering
+    \caption{$\pilow=0.1$, $B=4$, $L=1$, $u=0.5$}
+      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=4-L=1.pdf}
+    \end{subfigure}
+    % \\
+    % \begin{subfigure}[]{0.6\textwidth}
+    %   \centering
+    %   \caption{$\pilow=0.1$, $B=10$, $L=20$, $u=0.5$}
+    %   \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=10-L=20.pdf}
+    % \end{subfigure}
+
+\end{figure}
+
 \section{Discussion}

### 2022-10-11 ms.tex
Updates from Overleaf

--- 2022-10-10 ms.tex
@@
 all uncertainty parameters, and compared the simulated payoffs to 
-all-social learner or all-asocial learner populations. 
-Figure~\ref{fig:payoffs} shows the average net payoffs normalzied by lifespan
+homogenous all-social learner or all-asocial learner populations. Homogenous payoffs
+were calculated by initializing simulation populations to be all social or all asocial learners,
+then running the model for 100 generations so payoffs could stabilize; we then averaged 
+the net payoffs from the final generation across 1000 trials to calculate the average
+homogenous payoffs.
+
+Figure~\ref{fig:payoffs} shows the average net payoffs normalized by lifespan
 for our simulations and two reference conditions where agents are initialized
@@
 
-Our model helps to demonstrate that social learning can act as a scaffold for asocial learning---despite the framing of many other papers, they are not opposite strategies. 
+Our model helps to demonstrate that social learning can act as a scaffold for individual learning---they are not opposite strategies. 
 We endowed agents with a biologically-plausible individual learning mechanism, softmax search.
-This allowed for highly successful asocial learning that helped agents recover from the potential cost of receiving outdated information.
+This enabled agents to recover from the potential cost of receiving outdated information.
 This in turn enabled the evolution of social learning
 even when social information was likely to be outdated. 
-\cm{this seems to say the opposite of the topic sentence.
+% \cm{this seems to say the opposite of the topic sentence.
 In topic sentence social learning-> asocial, but the mechanism descibed later is asocial learning -> social.

### 2022-10-11 ms.tex
Full draft in overleaf; finalizing sensitivity analyses locally

@@
 pronounced when $\pilow=0.45$ and $B=10$ (Figure~\ref{fig:payoffs}, middle right).
-In these cases, the presence of individual learners before social learning fixation
+In these cases, the presence of asocial learners before social learning fixates
 enabled social learners in our simulations to outperform all-social learner populations.
-Next, we observed cases where long-lived populations ($L=8$) in simple environments
+Frequency dependence of social learning payoffs even pushed social learning to evolve even
+when the expected homogenous social learning payoff was less than the expected homogenous
+asocial learning payoff (Figure~\ref{fig:payoffs}, middle center $L=1$).
+We also observed cases where long-lived populations ($L=4$ and $L=8$) in simple environments
 ($B=2$) evolved to be individual learners, even though all-social learner populations
 outperformed all-individual learner populations (Figure~\ref{fig:payoffs}, upper left).
-By inspecting time series of individual model runs, we observe that
-asocial learning fixates in response to a period of protracted environmental
-instability, which causes social learning to more frequently provide
-outdated information (Figure~\ref{fig:timeseries}a).
-Conversely, sometimes when lifespan was short ($L=1$) and environmental variability
-was moderately high ($u\approx0.5$), a period of environmental
+
+We explain these deviations from expected homogenous payoffs 
+by inspecting time series of individual model runs where we plot the geometric moving averages (with time window 3) of the payoffs for the whole population, and for the series of payoffs broken out by asocial/social learner sub-populations, and compare these series to the expected homogenous social and asocial payoffs, the time series of social learner prevalence, and to the timing of environmental changes within the simulation (Figure~\ref{fig:payoffTimeseries}).
+When lifespan was minimal ($L=1$) and environmental variability
+was moderately high ($u\approx0.5$), inspection of payoffs a period of environmental
 stability led populations to fixate to social learning, despite individual learning
 being the superior long-term strategy (Figure~\ref{fig:payoffs}, center top and middle).
-This behavior was again confirmed by examining time series of simultations
+This behavior was again confirmed by examining time series of simulations
 initialized with the commensurate uncertainty parameters, which show that
-social learning fixates during periods of protratcted environmental stability
-(Figure~\ref{fig:timeseries}b).
+social learning fixates during periods of protracted environmental stability
+(Figure~\ref{fig:payoffTimeseries}a).
+When payoff ambiguity was large, decision set size was small $B=2$, and lifespan was long ($L=4$ and $L=8$),
+asocial learning fixates as a hedge against periods of protracted environmental
+instability, which causes social learning to frequently provide
+outdated information, even though expected homogenous social payoffs are greater than
+homogenous asocial payoffs (Figure~\ref{fig:payoffTimeseries}b,c).
 
@@
     \caption{Example time series of geometric moving average (GMA) with window of 3
-      of payoffs from three select simulations (see main text), broken out by 
+      of payoffs from three select uncertainty settings (see main text), broken out by 
     social learners, asocial learners, and whole population, compared with the
@@
       \centering
+    \caption{$\pilow=0.1$, $B=4$, $L=1$, $u=0.5$}
+      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=4-L=1.pdf}
+    \end{subfigure} \\
+
+\hspace{-2em}
+  \begin{subfigure}[]{0.75\textwidth}
+      \centering
       \caption{$\pilow=0.1$, $B=2$, $L=4$, $u=0.2$}
@@
       \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=8.pdf}
-    \end{subfigure} \\
-
-\hspace{-2em}
-    \begin{subfigure}[]{0.75\textwidth}
-      \centering
-    \caption{$\pilow=0.1$, $B=4$, $L=1$, $u=0.5$}
-      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=4-L=1.pdf}
     \end{subfigure}
+
     % \\
@@
     % \end{subfigure}
-
 \end{figure}
@@
 More interestingly, selection is also weaker when the ability to learn asocially is fraught with uncertainty.
-
-Our model helps to demonstrate that social learning can act as a scaffold for individual learning---they are not opposite strategies. 
+Our model demonstrated that social learning can act as a scaffold for individual learning---they are not opposite strategies.
 We endowed agents with a biologically-plausible individual learning mechanism, softmax search.
 This enabled agents to recover from the potential cost of receiving outdated information.
-This in turn enabled the evolution of social learning
-even when social information was likely to be outdated. 
+This in turn enabled the evolution of social learning even when social information was likely to be outdated.
+
 % \cm{this seems to say the opposite of the topic sentence.
@@
 Both seem possible, though the latter is easier for me to understand.}
-Detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly changing world.
+
+Our modeling results suggest, on the one hand, that society might be better to ignore social information from previous generations since our natural world is rapidly changing~\citep{IPCC2022}; on the other hand, however, humans have increasingly more behavioral options (decision set size) with high levels of uncertainty about which behaviors are most beneficial (payoff ambiguity), and in this case our model predicts a greater prevalence of social learning.
+In general, detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly changing world.
 Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\citep{Moya2020,Jones2021}, especially in
@@
 production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+However, to better identify potential pathways to effective adaptation it may be necessary to adjust some of our modeling assumptions to include both the cumulative nature of cultural evolution and group structure of interpersonal exchange, both of which have serious consequences for understanding the sustainability of novel adaptations~\citep{Derex2020,Centola2018,Smaldino2021a}.
 \cm{should we draw out some implications?
@@
 having more tech options available for dealing with climate change may encourage social learning?
-Frankly so many of these problems seem to come back to encouraging people to socially learn from the RIGHT people, not just socially or asocially learning.}
+Frankly so many of these problems seem to come back to encouraging people to socially learn from the RIGHT people, not just socially or asocially learning.} \mt{I gave this a try, with some restructuring to put the note about social learning as a scaffold for individual learning in the above paragraph.}
 
@@
 important consequences for comparing our results with previous findings in the literature. First, we assume
-all agents engage in asocial learning. This means that asocial learning is effectively free, though
+all agents engage in individual learning. This means that individual learning is effectively free, though
 potentially inaccurate. Although producing new knowledge may be costly, many other adaptive problems take
-the form of essentially cost free asocial learning. For example, one cannot help but experience, at likely
-asocially learn about the association between; clouds and rain, drinking water and hunger, or smiling and
-being avoided. This model thus avoids scrounger / producer dynamics common in other models
+the form of essentially cost free individual learning. For example, one cannot help but experience the association between; clouds and rain, thirst and drinking water, or smiling and
+being avoided. This model thus avoids scrounger/producer dynamics common in other models
 ~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and
@@
 information, we saw that social learning could evolve even if social learning
-often provides outdated information. This work most directly informs our current understanding of the evolution of social learning, but also has broader significance for
-understanding problem solving under uncertainty. \ps{What is this significance? Can't just leave that dangling. I also cut the bit about what comes next. No need for spoilers.} 
+often provides outdated information.
+
+Social learning is a critical component of problem solving among social creatures. Our work identified and clarified some important forms of uncertainty and catalogued their effects on 
+model populations' collective decisions to learn socially or not when collectively problem solving.
+Our work, then, advances both the theory of social learning and the theory of collective problem solving more generally, and could eventually be of practical use in designing sustainable adaptations to the immense threats and uncertainties faced by humans today.
+% This work most directly informs our current understanding of the evolution of social learning, but also has broader significance for understanding problem solving under uncertainty. 
+\ps{What is this significance? Can't just leave that dangling. I also cut the bit about what comes next. No need for spoilers.} \mt{Gave this a try, but I think Jamie should have a crack at this.}
 %Our model and its software implementation were designed to be modular and extensible.

### 2022-10-12 ms.tex
updated supplement, finished one revision

@@
 %, if the child inherited $s_i = 1$. A child agent $c$ is a social learner if its parent $p$ was a social learner, i.e.\ $s_c \leftarrow s_p$, without mutation.
-A social learner selects this ``teacher" from the previous generation by first choosing a random subset of the population and choosing among these with a probability weighted by each model's payoff (more details below).
+A social learner selects this ``teacher" from the previous generation by first
+choosing the payoff maximizer among these (more details below).
 The social learner then inherits information about the likely payoffs of each behavior from that one teacher, whereas asocial learners do not acquire this information.
@@
 
-        $\bar\pi_{ib}$ & ``Ledger'': mean payoffs acquired via behavior $b$ by $i$ 
+        $\bar\pi_{ib}$ & Mean payoffs acquired by agent $i$ from behavior $b$
                        & $B$-vector of zeros \\
@@
 %Child agents then begin a new round of generational dynamics, followed by reproduction. 
-This process continues until the population has evolved to fixation as either all social learners or all asocial learners, or until an upper limit of 20,000 
-iterations has been reached. This process is visualized in
+This process continues until the population has evolved to fixation as either all social learners or all asocial learners. This process is visualized in
 Figure~\ref{fig:schematic}.
@@
 
-The model is initialized with $N$ agents, all with zero observed mean payoffs, 
-$\ledger = 0$, and zero counts of how many times
-they have tried each behavior, $c_{ib} = 0$ (Figure~\ref{fig:schematic}A).
+The model is initialized with $N$ agents. Each agent $i$ tracks 
+observed mean payoffs for each behavior, $b$, which is denoted $\ledger$. Each
+agent $i$ also counts how many times they have tried each behavior $b$, 
+denoted $c_{ib}$. At model initialization, $\ledger = 0.0$ and $c_{ib} = 0$ for
+all $i$ and $b$ (Figure~\ref{fig:schematic}A).
 One of the behaviors is chosen at random to yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
 expected payoffs $\pilow$. Agents are independently randomly initialized with $s_i
-\in 0,1$, so that 50\% of the initial population learn socially.
+\in 0,1$, so that $\sim$50\% of the initial population learn socially.
 
@@
 independently (Figure~\ref{fig:schematic}B).
-Each agent selects one behavior on each step of its lifespan using softmax process that integrates previous knowledge. We denote the average payoffs obtained by agent $i$
-for behavior $b$ as $\ledger$. We denote the number of times $i$ performed $b$
-as $c_{ib}$ (``$c$'' stands for count). 
+% Each agent $i$ selects one behavior on each step of its lifespan using softmax applied
+% to the vector of mean payoffs the agent has observed for each behavior
+% ($\ledger$), integrating previous knowledge. 
+% We denote the average payoffs obtained by agent $i$
+% for behavior $b$ as $\ledger$. We denote the number of times $i$ performed $b$
+% as $c_{ib}$ (``$c$'' stands for count). 
 At each time step, agent $i$ performs behavior $b$ with softmax-weighted probability
@@
 agents explore alternative behaviors (smaller $\beta$). %~\citep{McElreath2005}. 
-We used a default value of $\beta = 10$, but also varied this value in our sensitivity analyses.
-
-Agent $i$ using behavior $b$ receives a payoff of 1 with probability $\pi_b$. 
+We used a default value of $\beta = 10$, but also varied this value in our
+sensitivity analyses~(Figure~\ref{fig:softmaxSensitivity}).
+
+Agent $i$ using behavior $b$ receives a payoff of 1 with probability $\pihigh$
+if $b$ is the optimal behavior, or with probability $\pilow$ otherwise. 
 %Agents probabilistically recieve a payoff of 0 or 1 depending on whether the bandit paid off.
@@
 specifically, this all happens as follows.  $N$ reproducers are selected with
-replacement over $N$ independent draws, biased by performance: \begin{equation}
+replacement over $N$ independent draws, biased by performance: 
+\begin{equation}
   \Pr(\text{Agent $i$ is chosen to reproduce in one draw}) =
-\frac{\pi_i}{\sum_{i=1}^N \pi_i}.  \end{equation} \noindent A child inherits its
+\frac{\pi_i}{\sum_{i=1}^N \pi_i}.  
+\end{equation} 
+\noindent 
+A child inherits its
 parent's social learning trait $s_i$ without mutation.  A social learner child with
@@
 (Figure~\ref{fig:nteachersSensitivity}).  Social learner $i$ adopts their chosen 
-teacher $j$'s observed average payoffs (average indicated by the overbar) 
-for each behavior, $b$, and $c_{ib}$ is set to 1 if teacher $j$ had at least one
-observation of behavior $b$,  
+teacher $j$'s observed average payoffs for each behavior, $b$, i.e. 
+$\ledger \leftarrow \bar\pi_{jb}$; 
+and agent $i$'s count of behavioral observations, $c_{ib}$, is set to 1 if teacher $j$ had at least one observation of behavior $b$,  
 and $c_{ib}$ is set to 0 otherwise. This way, expected payoffs remain within $[0,
@@
 and $\meanG$, the mean
-number of generations to fixation (see Table~\ref{tab:outcomeVariables}). We analyze outcomes by plotting $\meansl$ on the y-axis and environmental variability is on x-axis since we
-theoretically expect that $\meansl$ will decrease monotonically from 1 to 0 as $u$
+number of generations to fixation (see Table~\ref{tab:outcomeVariables}). We analyze
+outcomes by plotting $\meansl$ on the y-axis and environmental variability on
+x-axis, since we
+theoretically expect that $\meansl$ will always decrease monotonically from 1 to 0 as $u$
 increases.
@@
 robust to a range of auxiliary parameters. These analyses are presented in 
-supplemental material.
-First, we varied the population size, $N$, to explore whether smaller $N$ would show more drift due to finite population size effects.
-%, but  still generally support our main conclusions.
-Next, we varied the number of prospective teachers, $N_T \in \{2, 10, 20\}$, to supplement the main results that used $N_T = 5$. The number of prospective
+supplemental material. First, we varied the population size, $N$, to confirm that
+smaller $N$ would make similar predictions, but with more drift due to finite population size effects. %, but  still generally support our main conclusions. 
+Next, we tested model robustness to the number of prospective teachers, $N_T \in \{2, 10, 20\}$, to supplement the main results that used $N_T = 5$. The number of prospective
 teachers should not change whether social learning is optimal, but it may induce more drift since the benefit of social learning may
-be more difficult to detect with fewer prospective teachers. Finally, we varied the
-softmax greediness parameter $\beta \in \{1, 100\}$ to supplement the main results
+be more difficult to detect with fewer prospective teachers. Finally, we tested
+model robustness to varying the
+softmax greediness parameter $\beta \in \{1, 100\}$, to supplement the main results
 that used $\beta = 10$. We do not
@@
 individually, so certain $\beta$ values may themselves suppress social learning
-by undermining individual learning. Nonetheless, our results
-are valid over a substantial range of $\beta$.
+by improving or undermining individual learning.
 
@@
 using the Agents.jl agent-based modeling library~\citep{Datseris2022} and run
-on the Sherlock supercomputing cluster at Stanford University. Model code and
-data are publicly available on GitHub at \url{https://github.com/mt-digital/UncMod}.
+on the Sherlock supercomputing cluster at Stanford University. Model code is
+publicly available on GitHub at \url{https://github.com/mt-digital/UncMod},
+and output data used to generate the figures presented here are available on OSF.io
+\mt{TODO: \url{https://make.OSF.repo}}.
 
@@
 
-Our main results are illustrated by Figure~\ref{fig:mainResults}, which shows the proportion of simulation runs that fixated to 100\% social learners as a function of each of our four uncertainty measures.
-First, we find that reliance on social learning monotonically decreases as temporal environmental variability, $u$, increases.
-When the environment is more likely to change between generations, information learned from the previous generation is less likely to be of value, decreasing selection for social learning.
-Past some threshold, social learning is not favored at all.
-However, the exact nature of the relationship between social learning and temporal environmental variability is moderated by our other three uncertainty parameters.
+Our main results are illustrated by Figure~\ref{fig:mainResults}, which shows the
+proportion of simulation runs that fixated to 100\% social learners as a function of
+each of our four uncertainty measures.  First, we found that reliance on social
+learning monotonically decreases as temporal environmental variability, $u$,
+increases. When the environment is more likely to change between generations,
+information learned from the previous generation is less likely to be of value,
+decreasing selection for social learning. Past some threshold, social learning is
+not favored at all. However, the exact nature of the relationship between social
+learning and temporal environmental variability was moderated by the other three uncertainty parameters.
 
@@
 
-Of the four types of uncertainty studied in this paper, payoff ambiguity has the most
-complex effect on the evolution of social learning. Recall that we operationalize
+Of the four types of uncertainty studied in this paper, payoff ambiguity had the most
+complex effect on the evolution of social learning. Recall that we operationalized
 payoff ambiguity with $\pilow$, the expected payoff for non-optimal behaviors
-(equivalently the probability that those behaviors yielded a payoff of 1).
-This was relative to $\pihigh = 0.9$, the expected payoff for the optimal behavior.
-When payoff ambiguity was low, non-optimal behaviors rarely paid off, so that exploration yielded reliable information and selection on learning strategies was  strong.
-When payoff ambiguity is very high ($\pilow = 0.8$), two things happen.
-First, agents are more likely to err by ascribing high value to non-optimal behaviors, since it is more difficult for them to discern the difference between optimal and sub optimal behaviors.
-Second, and perhaps more importantly, natural selection on strategies that $do$ reliably select the optimal behavior is relatively weak.
-This means that the effect of drift is relatively stronger, weakening selection in favor of social learning under small values of $u$ and weakening selection against social learning under high values of $u$ (Figure~\ref{fig:steps}).
+(equivalently the probability that those behaviors yielded a payoff of 1). This was
+relative to $\pihigh = 0.9$, the expected payoff for the optimal behavior. When
+payoff ambiguity was low, non-optimal behaviors rarely paid off, so that exploration
+yielded reliable information and selection on learning strategies was  strong. When
+payoff ambiguity is very high ($\pilow = 0.8$), two things happen. First, agents are
+more likely to err by ascribing high value to non-optimal behaviors, since it is
+more difficult for them to discern the difference between optimal and sub optimal
+behaviors. Second, and perhaps more importantly, natural selection on strategies
+that $do$ reliably select the optimal behavior is relatively weak. This means that
+the effect of drift is relatively stronger, weakening selection in favor of social
+learning under small values of $u$ and weakening selection against social learning
+under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row). 
 This effect was especially strong under other types of uncertainty, i.e., larger selection set sizes and especially shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
 
-The effect of drift when effective lifespans are short and payoffs are very ambiguous is powerful and complex.
-We explain how the frequency of social learning evolves in such circumstances in the following section.
+The effect of drift when the benefit of social learning is ambiguous is powerful and complex. We explain how the frequency of social learning evolves in such circumstances in the following section.
 %selection on social learning responds to these effects in more detail in the following section. 
@@
 
-$\meanG$ peaks at the values of $u$ where social learning becomes suppressed. $B$, and $\pilow$ have the
+$\meanG$ peaks at the values of $u$ where social learning becomes suppressed. 
+$B$ and $\pilow$ have the
 clearest effects on the location of greatest drift over $u$. $L$ has some effect on the location of peak
@@
 This also results in weaker selection pressure since there is relatively little
-difference between social and asocial constraints when $L$ is large.
+difference between social and asocial constraints when $L$ is large
+(Figure~\ref{fig:steps}, top two rows).
 
@@
 Figure~\ref{fig:payoffs} shows the average net payoffs normalized by lifespan
-for our simulations and two reference conditions where agents are initialized
-as homogenous populations fixated either as all social or all asocial learners.
+for our simulations compared with the two reference homogenous populations
+initialized either as all social or all asocial learners.
 Often the simulated payoffs follow the payoffs from the better-performing
@@
 pronounced when $\pilow=0.45$ and $B=10$ (Figure~\ref{fig:payoffs}, middle right).
-In these cases, the presence of asocial learners before social learning fixates
+In these cases, the presence of asocial learners before social learning fixated
 enabled social learners in our simulations to outperform all-social learner populations.
@@
 We explain these deviations from expected homogenous payoffs 
-by inspecting time series of individual model runs where we plot the geometric moving averages (with time window 3) of the payoffs for the whole population, and for the series of payoffs broken out by asocial/social learner sub-populations, and compare these series to the expected homogenous social and asocial payoffs, the time series of social learner prevalence, and to the timing of environmental changes within the simulation (Figure~\ref{fig:payoffTimeseries}).
+by inspecting time series of individual model runs where we plot the geometric
+moving averages (with time window 3) of the payoffs for the whole population, and
+for the series of payoffs broken out by asocial/social learner sub-populations; we
+compare these mean payoff series to the expected homogenous social and asocial payoffs, the time series of social learner prevalence, and to the timing of environmental changes within the simulation (Figure~\ref{fig:payoffTimeseries}).
 When lifespan was minimal ($L=1$) and environmental variability
-was moderately high ($u\approx0.5$), inspection of payoffs a period of environmental
+was moderate ($u\approx0.5$), the payoff time series show a period of environmental
 stability led populations to fixate to social learning, despite individual learning
-being the superior long-term strategy (Figure~\ref{fig:payoffs}, center top and middle).
-This behavior was again confirmed by examining time series of simulations
-initialized with the commensurate uncertainty parameters, which show that
-social learning fixates during periods of protracted environmental stability
-(Figure~\ref{fig:payoffTimeseries}a).
-When payoff ambiguity was large, decision set size was small $B=2$, and lifespan was long ($L=4$ and $L=8$),
-asocial learning fixates as a hedge against periods of protracted environmental
-instability, which causes social learning to frequently provide
+being the superior long-term strategy (Figure~\ref{fig:payoffTimeseries}a).
+When payoff ambiguity and decision set size was small ($\pilow=0.1$ and $B=2$), 
+and lifespan was long ($L=4$ and $L=8$),
+asocial learning fixated as a hedge against periods of protracted environmental
+instability, which caused social learning to frequently provide
 outdated information, even though expected homogenous social payoffs are greater than
@@
 
-Our modeling results suggest, on the one hand, that society might be better to ignore social information from previous generations since our natural world is rapidly changing~\citep{IPCC2022}; on the other hand, however, humans have increasingly more behavioral options (decision set size) with high levels of uncertainty about which behaviors are most beneficial (payoff ambiguity), and in this case our model predicts a greater prevalence of social learning.
+Our modeling results suggest, on the one hand, that society might be better to
+ignore social information from previous generations since our natural world is
+rapidly changing~\citep{IPCC2022}; on the other hand, humans have increasingly more
+behavioral options (selection set size) with high levels of uncertainty about which behaviors are most beneficial (payoff ambiguity), and in this case our model predicts a greater prevalence of social learning.
 In general, detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly changing world.
@@
 the most vulnerable communities~\citep{McNamara2020}, and to capitalize on new behavioral opportunities such as transitioning to clean energy use and
-production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
-However, to better identify potential pathways to effective adaptation it may be necessary to adjust some of our modeling assumptions to include both the cumulative nature of cultural evolution and group structure of interpersonal exchange, both of which have serious consequences for understanding the sustainability of novel adaptations~\citep{Derex2020,Centola2018,Smaldino2021a}.
+production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}. However, to better identify
+potential pathways to effective adaptation it may be necessary to adjust some of our modeling assumptions to
+include both the cumulative nature of cultural evolution and group structure of interpersonal exchange, both
+of which have been shown to affect the sustainability of novel adaptations~\citep{Derex2020,Centola2018,Smaldino2021a}.
 \cm{should we draw out some implications?
@@
 For example, we only considered success-biased
-learning, although people may use conformity or other context biases to socially learn ~\citep{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.
-This modelling choice maximizes the potential benefit to social learners suggesting other mechanisms, like conformity, may lead to more drift overall.
-We also assumed that the number of behaviors and
+learning, although people may use conformity or other context biases to socially
+learn~\citep{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.  This modelling
+choice maximizes the potential benefit to social learners, which suggests that
+other mechanisms, like conformity, may lead to more drift overall. We also assumed that the number of behaviors and
 their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g.\ via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
@@
 ~\citep{Smolla2019,Derex2020}.  Group structure
-and processes such as homophily and in-group bias/out-group aversion could inhibit the
+and processes such as homophily and other group-level biases could inhibit the
 evolution of social learning since successful out-group teachers could be cut off from
@@
 
-Social learning is a critical component of problem solving among social creatures. Our work identified and clarified some important forms of uncertainty and catalogued their effects on 
-model populations' collective decisions to learn socially or not when collectively problem solving.
-Our work, then, advances both the theory of social learning and the theory of collective problem solving more generally, and could eventually be of practical use in designing sustainable adaptations to the immense threats and uncertainties faced by humans today.
+Social learning is a critical component of problem solving among social creatures.
+Our work identified and systematized some important forms of uncertainty and catalogued their effects on 
+the evolution of social learning. Our work, then, both advances the theory of social
+learning and could eventually be of practical use in designing sustainable
+adaptations to an uncertain future.
 % This work most directly informs our current understanding of the evolution of social learning, but also has broader significance for understanding problem solving under uncertainty. 
@@
 Drift was greater for smaller populations sizes, especially when $\pilow=0.8$, but 
-the main patterns generally remain for $N=50$, $N=100$, and $N=200$ (recall
-$N=1000$ tested in main analysis). Drift is also more pronounced for smaller $N$
+the main patterns are robust with greater finite population size effects, specifically
+with $N=50$ and $N=200$ (recall $N=1000$ tested in main analysis). 
+Drift is also more pronounced for smaller $N$
 for shorter lifespans, especially $L=1$. When $L=1$ and $N=50$ , the S-shaped
@@
   \caption{
-	Sensitivity analysis of the main results for different population
-	sizes, $N=50,200,1000$. Recall $N=100$ was used to generate main 
+	Sensitivity analysis of the main results for two population
+	sizes, $N=50,200$. Recall $N=1000$ was used to generate main 
 	text results.
@@
 	\caption{$N=50$}
-	\includegraphics[width=\textwidth]{Figures/supplement/nagents=50/mainResultsPlots.pdf}
-  \end{subfigure}
-\end{figure}
-
-\begin{figure}
-  \ContinuedFloat
-	\begin{subfigure}{\textwidth}
-	  \caption{$N=100$}
-	  \includegraphics[width=\textwidth]{Figures/supplement/nagents=100/mainResultsPlots.pdf}
+	\includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mainResultsPlots.pdf}
   \end{subfigure}
@@
 	  \caption{$N=200$}
-	  \includegraphics[width=\textwidth]{Figures/supplement/nagents=200/mainResultsPlots.pdf}
+	  \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mainResultsPlots.pdf}
 	\end{subfigure}
@@
 over $u$. There was slightly more drift when $N_T = 2$ compared to our 
-main text analysis, slightly less drift than our main analysis when $N_T = 20$, 
-and no obvious difference between $N_T = 10$ tested here and our main results
-with $N_T = 5$. When $N_T = 2$, increased drift is most notable in the
+main text analysis, slightly less drift than our main analysis when $N_T = 20$; 
+we also tested $N_T=10$, which showed no obvious difference from our main results
+with $N_T = 5$. When $N_T = 2$, increased drift is most pronounced in the
 $\meansl$ curves when $\pilow=0.8$ (Figure~\ref{fig:nteachersSensitivity}a, 
@@
   % \addtocounter{figure}{-1}
-  \caption{Number of prospective teachers sensitivity analysis for $N_T=2,10,20$. Recall
+  \caption{Number of prospective teachers sensitivity analysis for $N_T=2,20$. Recall
   $N_T=5$ was used to generate main text results.}
@@
 \end{figure}
-\newpage
-\begin{figure}
-  \ContinuedFloat
-  \begin{subfigure}{\textwidth}
-	\caption{$N_T = 10$}
-	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=10/mainResultsPlots.pdf}
-  \end{subfigure}
-\end{figure}
+% \newpage
+% \begin{figure}
+%   \ContinuedFloat
+%   \begin{subfigure}{\textwidth}
+% 	\caption{$N_T = 10$}
+% 	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=10/mainResultsPlots.pdf}
+%   \end{subfigure}
+% \end{figure}
 \newpage
@@
 
-With $\beta=100$, the changes in outcomes were minimal compared
-to setting $\beta=1$ (Figure~\ref{fig:softmaxSensitivity}b). 
-In some cases, such as $(\pilow=0.1, B=10)$ 
-and $(\pilow=0.45, B=2)$,
-there appears to be more drift across all $L$ around the transition
-point when $\meansl = 1$ goes to 0 as $u$ increases. However it appears
-that there is more drift at the transition for $\beta=10$ for
-$(\pilow=0.45, B=10)$.
+The main results were again qualitatively obtained again with $\beta=100$
+(Figure~\ref{fig:softmaxSensitivity}b). 
+In some cases, especially when $\pilow=0.1$, individual learning may be performing
+better with $\beta=100$ compared to results in the main text ($\beta=10$), 
+evidenced by a quicker decline of social learning prevalence over $u$ when
+$L > 1$ (Figure~\ref{fig:softmaxSensitivity}b,
+top row).
 

### 2022-10-12 ms.tex
fixed error in fixation equation

@@
 \paragraph{Stopping conditions} The evolutionary process continues until the
-population reaches evolutionary fixation with repsect to social learning, where
-$\sum_i s_i = 1$ or $\sum_i s_i = 0$.
+population reaches evolutionary fixation with respect to social learning, where
+$\sum_i s_i = N$ or $\sum_i s_i = 0$.
 

### 2022-10-18 ms.tex
updated figures and added affiliations

@@
 
+\usepackage{authblk}
+\renewcommand\Affilfont{\small}
+
+\author[1,*]{Matthew A. Turner}
+\author[2,3]{Cristina Moya}
+\author[4,5,6]{Paul E. Smaldino}
+\author[1,6]{James Holland Jones}
+
+\affil[1]{Department of Earth System Science, Stanford University, Stanford, CA 94305 USA}
+\affil[2]{Department of Anthropology, University of California at Davis, Davis, CA 95616 USA}
+\affil[3]{Centre for Culture and Evolution, Brunel University London, Uxbridge, UB8 3PH UK}
+\affil[4]{Cognitive and Information Sciences, University of California at Merced, Merced, CA 95340 USA}
+\affil[5]{Santa Fe Institute, Santa Fe, NM 87501 USA}
+\affil[6]{Center for Advanced Study in the Behavioral Sciences, Stanford University, Stanford, CA 94305 USA}
+\affil[*]{Corresponding author; email: \href{mailto:maturner@stanford.edu}{maturner@stanford.edu}}
 \usepackage{xcolor}
@@
 
-\author{{}}
-
 \begin{document}
 \maketitle
+\clearpage
 

### 2022-10-18 ms.tex
Updates from Overleaf

--- 2022-10-12 ms.tex
@@
 
-In our model we allow just one trait to evolve, social learning; 
-all other parameters are exogenous. Our primary outcome measure is the observed
-frequency that the social learning trait fixates in simulated populations. We study
-how the social learning fixation frequency responds to the four varieties of
+In our model we allow just one trait to evolve: social learning. All other parameters are exogenous. Our primary outcome measure is the observed
+frequency at which the social learning trait fixates in simulated populations. We study
+how the social learning fixation frequency responds to each of the four varieties of
 uncertainty considered in this paper. \mt{I changed this somewhat, please double
-check it's clear}
+check it's clear} \ps{I edited a couple of words but looks good.}
 
@@
 \paragraph{Stopping conditions} The evolutionary process continues until the
-population reaches evolutionary fixation with respect to social learning, where
+population reaches evolutionary fixation with respect to social learning, that is, when
 $\sum_i s_i = N$ or $\sum_i s_i = 0$.
@@
 Thus, under most conditions, longer effective lifespans lead to a narrower range of the parameters $u$ and $B$ under which social learning was favored.
-It is noteworthy that in many cases, a large increase in the selection regime for social learning could be observed when $L=1$, and by definition no individual learning occurred.
+It is noteworthy that in many cases, a large increase in the selection regime for social learning is observed when $L=1$, and by definition no individual learning can occur.
 The exceptions to this general pattern occur for high levels of payoff ambiguity, $\pilow$ combined with low rates of environmental change, $u$ (left parts of plots on bottom row of Figure~\ref{fig:mainResults}).
@@
 the effect of drift is relatively stronger, weakening selection in favor of social
-learning under small values of $u$ and weakening selection against social learning
+learning under low values of $u$ and weakening selection against social learning
 under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row). 
@@
 
- Despite the common claim that copying others makes sense when one is uncertain, we find that different forms of uncertainty can either promote, or impede, the evolution of social learning.
+ Despite the common claim that copying others makes sense when one is uncertain, we find that different forms of uncertainty can either promote or impede the evolution of social learning.
 By disambiguating various formalizations of uncertainty in a single computational model, we have developed a more nuanced theoretical understanding of how uncertainty affects the evolution of social learning.
@@
 
-Our modeling results suggest, on the one hand, that society might be better to
+Our modeling results suggest, on the one hand, that it might sometimes be better to
 ignore social information from previous generations since our natural world is
@@
 
-\section{Number of prospective teachers sensitivty analysis}
-
-We found that the number of prospectve teachers had little effect on $\meansl$
+\section{Number of prospective teachers sensitivtiy analysis}
+
+We found that the number of prospective teachers had little effect on $\meansl$
 over $u$. There was slightly more drift when $N_T = 2$ compared to our 
@@
 
-\section{Softmax parameter sensitivity analysis}
+\section{Robust patterns, interesting variation, with different agent greediness}
 
@@
 probability mass for selecting behaviors that have paid off more frequently over that agent's
-life history. In other words, greater $\beta$ increases the probabilty that the optimal
+life history. In other words, greater $\beta$ increases the probability that the optimal
 observed behavior is chosen over all the rest. If $\beta$ is too small, agents will fail to
@@
 
-The main results were again qualitatively obtained again with $\beta=100$
+\mt{This is the greedier sensitivity analysis---need to frame it that way, note that excessive greediness suppresses the usefulness of social learning.} The main results were obtained with $\beta=100$
 (Figure~\ref{fig:softmaxSensitivity}b). 
@@
 \end{figure}
+
 \newpage
+
 \begin{figure}

### 2022-10-20 ms.tex
Updates from Overleaf

@@
 However, variability takes different forms.
-Uncertainty is a severe form of variability where either probabilities or the outcome space (or both) of decisions are unknown.
-We identified four distinct and theoretically-important types of uncertainty: temporal environmental variability, ambiguous payoffs, decision-set size, and effective lifespan.
-The common thread of these is that they make fully learning variability impossible.
-We embed this framework in an evolutionary agent-based model to study conditions for the evolution of social learning in populations with cognitively-realistic individual learning capacities.
+Uncertainty is a severe form of variability where the space of possible decisions or probabilities of associated outcomes are unknown.
+  %"probabilities of decisions" didn't make sense to me so I rephrased, but hopefully still accurate.
+  We identified four distinct and theoretically-important sources of uncertainty: temporal environmental variability, payoff ambiguity, decision-set size, and effective lifespan.
+All these kinds of uncertainty make it near impossible to fully learn about variability.
+We develop an evolutionary agent-based model to test how each form of uncertainty affects the evolution of social learning.
 Agents perform one of several behaviors, modeled as a multi-armed bandit, to acquire payoffs.
-Individual learning used the softmax algorithm.
-Social learning involved vertical and oblique transmission between generations, which served as a constraint on subsequent individual learning.
+All agents learn asocially using the cognitively-realistic softmax algorithm.
+Additional use of vertical and oblique social learning was allowed to evolve and served as a constraint on intra-generational asocial learning.
 We found that different types of uncertainty had different effects.
@@
 Payoff ambiguity and lifespan had more complex effects on social learning, dependent on interactions with other uncertainty parameters.
-This study shows the importance of clearly operationalizing uncertainty for understanding its role in social and cultural evolution.
+This study shows the importance of clearly operationalizing uncertainty for understanding its role in cultural evolution.
 % Social learning is essential to human survival. It is likely to evolve when it is more
@@
 indicates that social learning is a critical adaptation found across taxa for dealing
-with variable environments. When in doubt, copy others.
+with variable environments. %When in doubt, copy others.
 
@@
 %Other (asocial) forms of learning are also likely adaptations to uncertainty that should be accounted for, but are typically glossed over in models.  
-In general, learning is an iterative process during which an individual acquires information, forms representations and predictions, and then tests and refines those representations and predictions to manage uncertainty~\citep{jacobs2011bayesian,clark2013whatever}.
+Learning, be it social or not, is an iterative process during which an individual acquires information, forms representations and predictions, and then tests and refines those representations and predictions to manage uncertainty~\citep{jacobs2011bayesian,clark2013whatever}.
 Because cultural evolutionary models are often designed to explain \emph{social} learning mechanisms, they often contrast social learning with an overly-simplistic mechanism for individual learning.
-In particular, it is often assumed that individual learners can \emph{always} pay a cost to learn the optimal behavior for a particular environment with certainty.
+In particular, it is often assumed that individual learners can pay a cost to definitively learn the optimal behavior for a particular environment with certainty.
 This assumption implies that social learning by observing an individual learner is a good bet if the environment has not changed.
@@
 uncertainty that are common in cultural evolution models and the related empirical
-literature:  (1) temporal environmental variability; (2) selection set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning), explained below.
+literature:  (1) temporal environmental variability; (2) selection set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning), see next section for more details.
 In our model, social learners learn from the previous generation and asocial learners do not.
@@
 
-\paragraph{Temporal environmental variability.} When environmental variability is nonstationary (for example, because of climatic events, migration, or technological paradigm shifts), strategies that were previously adaptive may no longer be optimal.
+\paragraph{Temporal environmental variability.} When environmental variability is nonstationary (for example, because of climatic events %, migration,
+or technological paradigm shifts), strategies that were previously adaptive may no longer be optimal.
 The difficulty in predicting either when such shocks will occur or which behaviors will be adaptive in the resulting environments leads to uncertainty.
@@
 several ways~\citep{aoki2014evolution}. Most commonly, it is modeled
-as an independent probability that the environment changes its state (and its corresponding optimal behavior) before each new generation
-~\citep{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}, but
+as an independent probability that the environment changes its state (and its corresponding optimal behavior) before each new generation~\citep{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}, but
 % The probabilities of environmental change are usually fixed per generation
@@
 \citep{BoydRicherson1985,Rogers1988,Enquist2007,Rendell2010,aoki2014evolution}.
-The size of the difference between these payoffs is usually taken to indicate the strength of selection of learning.
+The size of the difference between these payoffs is usually taken to influence the strength of selection on learning strategies.
 %, which makes sense.
@@
 % predictions to manage uncertainty \citep{jacobs2011bayesian,clark2013whatever}. 
-We refer to the number of learning opportunities as an individual's effective lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behavior, rather than the number of sunrises one experiences, that determines the level of uncertainty present in one's choices.
+We refer to the number of individual learning opportunities within a generation as an individual's effective lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behavior, rather than the number of sunrises one experiences, that determines one's uncertainty about the behavioral options.
 %throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.
@@
 between young children and the older adults to whom they direct the most trust and
-attention \citep{kline2013teaching}. The effective lifespan for learning
-varies across tasks, individuals, and species, yet most models assume only one learning opportunity per generation \citep{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
+attention \citep{kline2013teaching}.
+While these phenomena map on imperfectly to effective lifespan in our model given social learning is only allowed intergenerationally, effective lifespans for learning do vary across tasks, individuals, and species, yet most models assume only one learning opportunity per generation \citep{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
 Some models do allow several cultural generations within one genetic generation \citep{Enquist2007,Rendell2010,lindstrom2016co}, but little formal theory explicitly examines the role of learning opportunities in the evolution of social learning.
@@
 aoki2005}.
-This sort of behavioral gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to social and cultural evolution \citep{Heyes2016,Kendal2018}.
+This sort of behavioral gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to cultural evolution \citep{Heyes2016,Kendal2018}.
 Some more complicated learning strategies that make use of both socially and individually learned information have been studied ~\citep{Enquist2007, perreault2012bayesian}, including those that integrate cognitively plausible mechanisms such as reinforcement learning \citep{lindstrom2016co}, though the latter approach remains the exception rather than the norm.
@@
 how the social learning fixation frequency responds to each of the four varieties of
-uncertainty considered in this paper. \mt{I changed this somewhat, please double
-check it's clear} \ps{I edited a couple of words but looks good.}
-
-A population of $N$ individuals each must decide which of $B$ behaviors to perform at
+uncertainty considered in this paper. 
+% \mt{I changed this somewhat, please double
+% check it's clear} \ps{I edited a couple of words but looks good.}
+
+A population consists of $N$ individuals, each of whom must decide which of $B$ behaviors to perform at
 each time step within a generation consisting of $L$ time steps.
@@
 The environment affords $B$ behaviors, where $B$ is the \emph{selection set size}.
+Uncertainty increases with $B$.
 Each behavior is indexed by $b$ and yields a payoff of 1 with probability $\pi_b$ and a payoff of 0 otherwise.
-Clearly, $\pi_b$ is equivalently the expected
+As such, $\pi_b$ is equivalently the expected
 payoff of behavior $b$.
@@
 We fix $\pihigh = 0.9$ to be constant across all simulations, so payoff ambiguity is varied by changing the value of $\pilow$.
-In other words, payoff ambiguity increases with $\pilow$.
+In other words, payoff ambiguity, and therefore uncertainty, increases with $\pilow$.
 Agents have $L$ time steps to learn and act per generation (i.e., the \emph{effective lifespan}).
@@
 At the start of each generation a new optimal behavior is selected at random from the set of all possible behaviors with probability $u$ (the \emph{environmental variability}), otherwise the optimal behavior remains unchanged from the previous generation.
+Uncertainty increases with $u$.
 
@@
 \begin{table}[h]
-\caption{Environmental Parameters. These include our four main uncertainty parameters under investigation; $u$, $B$,
-$\pilow$, and $L$. Bold indicates default value tested.} %\emph{default value tested}.}
+\caption{Environmental Parameters. These include our four main uncertainty parameters under investigation; 
+$\pilow$, $B$, $L$, and $u$. Bold indicates default value tested.} %\emph{default value tested}.}
     \label{tab:uncertaintyParameters}
@@
         \midrule  
-
-        $u$    & Probability optimal behavior changes between generations 
-               & 0.0, 0.1, \ldots, 1.0 \\
-
-        $B$       & Number of behavior options
-                  & 2, 4, 10 \\
+        $N$    & Population size
+                 & 50, 100, 200, \textbf{1000} \\
 
@@
 
-        $\pilow$ & Probability one of $B - 1$ non-optimal behaviors pays off 1 
+        $\pilow$ & Payoff ambiguity: probability one of $B - 1$ non-optimal behaviors pays off 1
                  & 0.1, 0.45, 0.8 \\
 
-        $L$    & Time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
-
-        $N$    & Population size
-                 & 50, 100, 200, \textbf{1000} \\
+        $B$       & Selection set size: number of behavior options
+                  & 2, 4, 10 \\
+
+        $L$    & Effective lifespan: time steps per generation & 1, $B/2$, $B$, $2B$, $4B$ \\
+
+        $u$    & Environmental variability: Probability optimal behavior changes between generations
+               & 0.0, 0.1, \ldots, 1.0 \\
 
@@
 All agents learn individually over their lifespan, and those with
-the heritable social learner trait use social information to constrain their individual
+the heritable social learner trait additionally use social information to constrain their individual
 learning. For simplicity, we refer to agents with the social learner trait 
@@
 guides agents to exploit more frequently the most profitable behaviors when the
-agent is more certain which is optimal and to explore more frequently when the
+agent is more certain it is the optimal one and to explore more frequently when the
 agent is unsure. To do softmax searching, agents track average payoffs acquired
@@
 The probability that the agent will perform a behavior is a function of the agent's beliefs about a behavior's average payoff in that time step and a fixed parameter that influences the amount of exploratory behavior (more details below).
-The softmax function used here is a biologically plausible generalization of behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative behavior (based on their observations) but also to sometimes explore alternatives~\citep{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
+The softmax function used here is a biologically plausible generalization of behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative behavior they have observed, but also to sometimes explore alternatives~\citep{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
 
@@
     \label{tab:modelParameters}
-    \centering %\hspace{-3em}
-    \begin{tabular}{cp{4.0in}p{1.25in}} \toprule
+    \centering \hspace{-1em}
+    \begin{tabular}{cp{4.5in}p{1.25in}} \toprule
 
@@
 
-        $c_{ib}$ & Count of how many times agent $i$ performed $b$ 
+        $c_{ib}$ & Count of how many times agent $i$ performed behavior $b$ 
               & $B$-vector of zeros \\
@@
 
-        $\beta$ & Softmax greediness; $\uparrow=$more exploitation, $\downarrow=$more
+        $\beta$ & Softmax greediness: $\uparrow=$more exploitation, $\downarrow=$more
                     exploration 
@@
 to the chosen parameter settings. % for the simulation.
-Then, within each generation, agents select and perform behaviors, updating their estimated payoffs (and their probabilities of choosing each behavior) along the way.
+Then, within each generation, agents select and perform behaviors, updating their estimated payoffs, and thus their probabilities of choosing each behavior, along the way.
 Between generations, agents reproduce, teach social learners of the next generation, and die off. 
 %Child agents then begin a new round of generational dynamics, followed by reproduction. 
-This process continues until the population has evolved to fixation as either all social learners or all asocial learners. This process is visualized in
+This process continues until the population has evolved to fixation as either all social learners or all asocial learners. This process is represented in
 Figure~\ref{fig:schematic}.
@@
 \noindent
-where $\bandit$ is the actual payoff received by agent $i$ for behavior $b$ on the
-given (implicit) time step.
+where $\bandit$ is the actual payoff received by agent $i$ for behavior $b$ on a
+given %(implicit) 
+time step.
 
@@
 1]$, but social learners are flexible to adjust to environmental change. 
-Setting $c_{ib}$ to 1 reflects the fact that the social learning is 
-treating the teacher's information as a single observation with the associated
+Setting $c_{ib}$ to 1 reflects the fact that the social learner
+treats the teacher's information as a single observation with the associated
 uncertainty. Asocial learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and
@@
 the previous generation dies off (C). The simulation stops if children are all
-social or asocial learners (i.e.\ the system reaches fixation), 
-otherwise repeat another generation and evolution.} 
+social or asocial learners (i.e.\ the system reaches fixation).
+Otherwise it repeats another generation and evolution continues.} 
 % \cm{What does (3) denote at end of Fig 1 caption?
@@
 We observed three outcome measures, with $\meansl$ as the primary measure: the average value of $s_i$ over all agents and trials. To support our conclusions
-about $\meansl$, we also measured $\meanpi / L$, the average net  payoffs at the end of the simulation across agents and trials, normalized by lifespan; 
-and $\meanG$, the mean
-number of generations to fixation (see Table~\ref{tab:outcomeVariables}). We analyze
+about $\meansl$, we also measured $\meanG$, the mean
+number of generations to fixation, and $\meanpi / L$, the average net  payoffs at the end of the simulation across agents and trials, normalized by lifespan (see Table~\ref{tab:outcomeVariables}). 
+We analyze
 outcomes by plotting $\meansl$ on the y-axis and environmental variability on
@@
         $\meansl$ & Mean social learning prevalence over agents
-                  & $\in [0.0, 1.0]$ \\
+                  & $ [0.0, 1.0]$ \\
 
         $\meanpi / L$ & Mean payoffs accumulated across agents, normalized by
-        lifespan & $\in [0.0, 1.0]$ \\
-
-        $\meanG$ & Mean number of generations to convergence & Unbounded \\
+        lifespan & $ [0.0, 1.0]$ \\
+
+        $\meanG$ & Mean number of generations to convergence & \{1,2,\ldots\} \\
         \bottomrule
@@
 
-\subsubsection{Sensitivity analyses}
-
-We performed sensitivity analyses to ensure that our main analysis is reasonably
-robust to a range of auxiliary parameters. These analyses are presented in 
-supplemental material. First, we varied the population size, $N$, to confirm that
-smaller $N$ would make similar predictions, but with more drift due to finite population size effects. %, but  still generally support our main conclusions. 
-Next, we tested model robustness to the number of prospective teachers, $N_T \in \{2, 10, 20\}$, to supplement the main results that used $N_T = 5$. The number of prospective
-teachers should not change whether social learning is optimal, but it may induce more drift since the benefit of social learning may
-be more difficult to detect with fewer prospective teachers. Finally, we tested
-model robustness to varying the
-softmax greediness parameter $\beta \in \{1, 100\}$, to supplement the main results
-that used $\beta = 10$. We do not
-expect agents with different $\beta$ to perform equally well 
-individually, so certain $\beta$ values may themselves suppress social learning
-by improving or undermining individual learning.
-
 \subsubsection{Implementation}
@@
 using the Agents.jl agent-based modeling library~\citep{Datseris2022} and run
-on the Sherlock supercomputing cluster at Stanford University. Model code is
-publicly available on GitHub at \url{https://github.com/mt-digital/UncMod},
-and output data used to generate the figures presented here are available on OSF.io
-\mt{TODO: \url{https://make.OSF.repo}}.
+on the Sherlock supercomputing cluster at Stanford University. Model and analysis code is
+publicly available on GitHub at \url{https://github.com/mt-digital/UncMod}.
 
@@
 
-% To understand how different forms of uncertainty interact to affect the evolution of
-% social learning, we measured how frequently social learning evolved across
-% uncertainty parameters. We analyzed outcomes by plotting the mean observed social
-% learning frequency, $\meansl$, with mean taken across all 1000 agents and 1000
-% simulation trials for each uncertainty parameter setting at model fixation.
-% % This is convenient because we are most certain about how $\meansl$ depends on $u$:
-% % we expect $\meansl$ to decrease as $u$ increases since environmental variability
-% % is well understood to cause socially-transmitted information to become outdated. 
-% % To inspect patterns in $\meansl$ over all uncertainty parameters, 
-% We analyze nine plots of how $\meansl$ (y-axis in each plot) changes over 
-% environmental variability, $u$ (x-axis),
-% in a $3\times3$ plot array (Figure~\ref{fig:mainResults}). 
-% % All plots show how $\meansl$ changes (y-axis)
-% % with environmental variability, $u$ (x-axis). 
-% Selection set size, $B$, increases from left to right in the plot array (columns). 
-% Payoff ambiguity increases as the non-optimal payoff, $\pilow$, increases from 
-% top to bottom in the array (recall $\pihigh=0.9$ for all analyses).
-% Effective lifespan, $L$, is indicated by line and marker colors (inset). 
-% Several patterns in social learning prevalence emerged as 
-% these uncertainty parameters were varied (Figure~\ref{fig:mainResults}).
-
 Our main results are illustrated by Figure~\ref{fig:mainResults}, which shows the
-proportion of simulation runs that fixated to 100\% social learners as a function of
+proportion of simulation runs that fixated at 100\% social learners as a function of
 each of our four uncertainty measures.  First, we found that reliance on social
@@
 A shorter effective lifespan, $L$, also favors the evolution of social learning in most cases.
-When effective lifespans are long and there are many opportunities to gather information by learning asocially, the value of social transmission is diminished.
+When effective lifespans are long and there are many opportunities to gather information by individual learning, the value of social transmission is diminished.
 Given enough opportunities, all agents will learn the optimal behavior eventually.
@@
 
+\subsection{Sensitivity analyses}
+
+We performed sensitivity analyses to ensure that our main analysis is reasonably
+robust to a range of auxiliary parameters. These sensitivity analyses are presented in full in the
+supplemental material.
+First, we confirmed that our results were robust to various population sizes $N$, though smaller $N$ simulations had more drift as expected due to stronger finite population size effects (Figure~\ref{fig:populationSensitivity}).
+%, but  still generally support our main conclusions.
+Next, we verified model robustness to the number of prospective teachers, $N_T \in \{2, 20\}$, to supplement the main results that used $N_T = 5$. The number of prospective
+teachers did not change the results (Figure~\ref{fig:nteachersSensitivity}), except to increase drift when $N_T = 2$, since the benefit of social learning may
+be more difficult to detect with fewer prospective teachers (Figure~\ref{fig:nteachersSensitivity}a). Finally, we confirmed our results were reasonably 
+robust to a wide range of
+softmax greediness parameters, $\beta \in \{1, 100\}$, to supplement the main results
+that used $\beta = 10$.
+However, when $\beta = 1$, a lack of greed caused agents to often ignore helpful social information  (Figure~\ref{fig:softmaxSensitivity}a).
+Too much greed ($\beta=100$) made social learners inflexible so they could not recover as well when when they learned outdated social information, which was most pronounced for longer-lived agents who may spend several time steps performing a sub-optimal behavior (Figure~\ref{fig:softmaxSensitivity}b).
+
 \section{Discussion}
@@
 include both the cumulative nature of cultural evolution and group structure of interpersonal exchange, both
-of which have been shown to affect the sustainability of novel adaptations~\citep{Derex2020,Centola2018,Smaldino2021a}.
+of which affect the sustainability of novel adaptations~\citep{Derex2020,Centola2018,Smaldino2021a}.
 \cm{should we draw out some implications?
@@
 in-group learners~\citep{Golub2012}. We assumed agents choose behaviors via softmax
-search, but even though this algorithm is more sophisticated than most used in social learning models, it is algorithm compared to real human learning mechanisms ~\citep{Schulz2020a,Wu2022}.
-Instantiating even more powerful asocial learning could further
+search, which is more cognitively sophisticated than most social learning models, but real human learning mechanisms are more powerful~\citep{Schulz2020a,Wu2022}.
+More powerful individual learning could further
 support the evolution of social learning. These considerations reveal new opportunities to enhance theoretical nuance by adjusting or extending the present model for other contexts.
@@
 Indeed, we plan to extend this model to further develop a more detailed theoretical understanding of the evolution of social learning; we hope others will, too.
+
+\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \mt{OSF link to PDF when final and separated)}.
+Model and analysis code is publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF (\url{https://osf.io/t8exa/}).
+
+\paragraph{Acknowledgements.} \mt{Do we write any at this point? Please fill in as you see fit.}
+
+\paragraph{Author contributions.} MAT led model development and analysis, with contributions from CM, PES, and JHJ.
+MAT wrote and edited the initial manuscript draft, which was extensively expanded and edited by CM, PES, and JHJ.
+
+\paragraph{Financial support.} \mt{Please fill in, thanks!}
+
+\paragraph{Conflict of interest.} No conflict declared.
 
@@
 
-\section{Population size sensitivty analysis}
+\section{Population size sensitivity analysis}
 
@@
 
-\section{Number of prospective teachers sensitivtiy analysis}
+\section{Number of prospective teachers sensitivity analysis}
 
@@
   \centering
-  % \addtocounter{figure}{-1}
+   \addtocounter{figure}{-1}
   \caption{Number of prospective teachers sensitivity analysis for $N_T=2,20$. Recall
@@
 
-\section{Robust patterns, interesting variation, with different agent greediness}
+\section{Agent greediness sensitivity analysis}
 
@@
 observed in the main text where we used $\beta=10$.  
-Softmax greediness is achieved formally by increasing the
-probability mass for selecting behaviors that have paid off more frequently over that agent's
-life history. In other words, greater $\beta$ increases the probability that the optimal
-observed behavior is chosen over all the rest. If $\beta$ is too small, agents will fail to
+Formally, softmax greediness changes the 
+probability mass allocated to selecting behaviors according to observed payoffs within that agent's
+life history or learned from a teacher of the previous generation. 
+Greater $\beta$ increases the probability that the optimal
+observed behavior is chosen over all the rest, while smaller $\beta$ leads agents to explore alternative behaviors more frequently. If $\beta$ is too small, agents will fail to
 fully exploit their knowledge about which behavior is optimal because they too frequently
 explore less profitable alternatives.  If $\beta$ is too great the agents may prematurely
-settle on a sub-optimal behavior because it paid off first.  In a fuller evolutionary
+settle on a sub-optimal behavior because that is what they learned from a teacher, 
+or because that behavior happened to pay off first. In a fuller evolutionary
 exploration of model parameters one might allow $\beta$ to co-evolve, through
 mutation and selection, with the social learner trait.  
-However, our sensitivity analysis suggests this would be unnecessary 
-since our main conclusions of how social learning evolves under uncertainty remain unchanged for different
-$\beta$ over three orders of magnitude.
+Regardless, our sensitivity analysis shows our main conclusions of how social learning evolves under uncertainty remain unchanged for different $\beta$ over three orders of magnitude.
 
@@
 of social learning is suppressed or drift dominates due to 
-due to the overall poor quality of information acquired through softmax search-based
-individual learning. This increased drift is especially pronounced 
+the overall poor quality of information acquired through softmax search-based
+individual learning with this setting. This increased drift is especially pronounced 
 when $\pilow=0.8$ since sub-optimal behaviors often pay off and $\beta=1$ is
-not aggressive enough to efficiently detect and exploit the optimal 
+not greedy enough to efficiently detect and exploit the optimal 
 behavior (Figure~\ref{fig:softmaxSensitivity}a, bottom row).
 Similarly, when $\beta = 1$, social learning is suppressed at much smaller values
-of $u$ for longer lifespans, $L$, due to maximal excessive exploration of non-optimal
+of $u$ for longer lifespans, $L$, due to extended exploration of non-optimal
 behaviors under this setting (Figure~\ref{fig:softmaxSensitivity}a, columns 
@@
 
-\mt{This is the greedier sensitivity analysis---need to frame it that way, note that excessive greediness suppresses the usefulness of social learning.} The main results were obtained with $\beta=100$
-(Figure~\ref{fig:softmaxSensitivity}b). 
-In some cases, especially when $\pilow=0.1$, individual learning may be performing
-better with $\beta=100$ compared to results in the main text ($\beta=10$), 
-evidenced by a quicker decline of social learning prevalence over $u$ when
-$L > 1$ (Figure~\ref{fig:softmaxSensitivity}b,
-top row).
+When $\beta=100$, our analysis again recovered general trends observed in the main analysis with
+$\beta=10$ (Figure~\ref{fig:softmaxSensitivity}b). However, 
+in some cases, especially when $\pilow=0.1$, social learning is suppressed compared to the main text results ($\beta=10$), because social learners may often greedily perform an outdated socially-learned optimal behavior over several time steps before possibly identifying the true optimal behavior (Figure~\ref{fig:softmaxSensitivity}b, top row).
 
@@
   \centering
+  \addtocounter{figure}{-1}
   \caption{Sensitivity analysis of the main results for the softmax parameter $\beta = 100$ and
-  % \addtocounter{figure}{-1}
   $\beta=1$. Recall the main results were obtained with $\beta = 10$.}

### 2022-10-20 meanNetPayoffs.tex
updated figures final for submission

--- 2022-10-09 meanNetPayoffs.tex
@@
     \begin{center}
-      {\Huge \textbf{+} \huge Location where homogenous social and asocial payoffs
-      are equal} \quad \quad 
+       \includegraphics[width=1.15in]{Figures/legendElements/dot.pdf}
+       {\huge Average all-social population payoffs}  \\[1.125em]
+       \includegraphics[width=1.15in]{Figures/legendElements/ldash.pdf} 
+       {\huge Average all-asocial population payoffs} \\[1.125em]
+       \includegraphics[width=1.15in]{Figures/legendElements/solid.pdf} 
+       {\huge Simulated average population payoffs} \\[1.125em]
+       {\Large $\pmb{|}$ \huge \quad $u$ value where homogenous social and asocial payoffs
+      are equal} 
     \end{center}

### 2022-10-23 ms.tex
final update of time series figures
final updates from Jamie

@@
 \author[2,3]{Cristina Moya}
-\author[4,5,6]{Paul E. Smaldino}
-\author[1,6]{James Holland Jones}
+\author[4,5,7]{Paul E. Smaldino}
+\author[1,6,7]{James~Holland~Jones}
 
@@
 \affil[5]{Santa Fe Institute, Santa Fe, NM 87501 USA}
-\affil[6]{Center for Advanced Study in the Behavioral Sciences, Stanford University, Stanford, CA 94305 USA}
+\affil[6]{Division of Social Sciences, Stanford Doerr School of Sustainability, Stanford University, Stanford, CA 94305 USA}
+\affil[7]{Center for Advanced Study in the Behavioral Sciences, Stanford University, Stanford, CA 94305 USA}
 \affil[*]{Corresponding author; email: \href{mailto:maturner@stanford.edu}{maturner@stanford.edu}}
@@
 
-%\title{The form of uncertainty affects selection for social learning}
-\title{Different forms of uncertainty differently affect the evolution of social learning}
+\title{The Form of Uncertainty Affects Selection for Social Learning}
+%\title{Different forms of uncertainty differently affect the evolution of social learning}
+%\title{The Many Faces of Uncertainty: ... }
 
@@
   We identified four distinct and theoretically-important sources of uncertainty: temporal environmental variability, payoff ambiguity, decision-set size, and effective lifespan.
-All these kinds of uncertainty make it near impossible to fully learn about variability.
+All these kinds of uncertainty make it nearly impossible to fully learn about variability.
 We develop an evolutionary agent-based model to test how each form of uncertainty affects the evolution of social learning.
@@
 Additional use of vertical and oblique social learning was allowed to evolve and served as a constraint on intra-generational asocial learning.
-We found that different types of uncertainty had different effects.
+We found that different types of uncertainty had varying effects.
 Temporal environmental variability suppressed social learning, whereas larger decision-set size promoted social learning, even when the environment changed frequently.
@@
 Uncertainty weighs particularly heavily on human adaptation because of
-our long lifespans, cosmopolitan societies, and dispersal across a highly variable environments, requiring coarse-grain and plastic behavioral adaptations \citep{levins1962}.
+our long lifespans, cosmopolitan societies, and dispersal across highly variable environments, requiring coarse-grained and plastic behavioral adaptations \citep{levins1962}.
 However, the term ``uncertainty'' is often used loosely in a way that fails to distinguish it from risk.
@@
 Learning, be it social or not, is an iterative process during which an individual acquires information, forms representations and predictions, and then tests and refines those representations and predictions to manage uncertainty~\citep{jacobs2011bayesian,clark2013whatever}.
-Because cultural evolutionary models are often designed to explain \emph{social} learning mechanisms, they often contrast social learning with an overly-simplistic mechanism for individual learning.
-In particular, it is often assumed that individual learners can pay a cost to definitively learn the optimal behavior for a particular environment with certainty.
-This assumption implies that social learning by observing an individual learner is a good bet if the environment has not changed.
-Such modelling choices may lead us to overestimate both the extent to which individual learning provides quality information and the value of social learning in a population of individual learners.
+Because cultural evolutionary models are frequently designed to explain \emph{social} learning mechanisms, they often contrast social learning with a simplistic mechanism for individual learning.
+In particular, a common assumption is that individual learners can pay a cost to definitively learn the optimal behavior for a particular environment with certainty.
+This assumption implies that social learning, by observing an individual learner, is a good bet if the environment has not changed.
+Such modeling choices may lead us to overestimate both the extent to which individual learning provides quality information and the value of social learning in a population of individual learners.
 % , both for asocially adapting to uncertainty and for social learners to take advantage of.
@@
 uncertainty that are common in cultural evolution models and the related empirical
-literature:  (1) temporal environmental variability; (2) selection set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning), see next section for more details.
+literature:  (1) temporal environmental variability; (2) selection-set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning), see next section for more details.
 In our model, social learners learn from the previous generation and asocial learners do not.
@@
 Uncertainty can manifest in many ways.
-We focus on the following four sources of uncertainty for the evolution of social learning: (1) temporal environmental variability, (2) selection set size, (3) payoff ambiguity, and (4) effective lifespan.
+We focus on the following four sources of uncertainty for the evolution of social learning: (1) temporal environmental variability, (2) selection-set size, (3) payoff ambiguity, and (4) effective lifespan.
 
@@
 
-\paragraph{Selection set size.}
-When one does not know which option to take, uncertainty increases with the number of options, which we call the selection set size.
+\paragraph{Selection-set size.}
+When one does not know which option to take, uncertainty increases with the number of options, which we call the selection-set size.
 % This is a mathematical fact at the
 % core of information theory: the number of bits required to reliably encode the optimal solution increases by one every time the
-% selection set doubles in size~\citep{mackay2003information}. 
+% selection-set doubles in size~\citep{mackay2003information}. 
 % This is intuitive; the more options to consider, the greater one's uncertainty about which option is the best choice. 
@@
 claim that payoff ambiguity increases the reliance on social information.
-Importantly, payoff ambiguity %differs from selection set size in that it not only 
+Importantly, payoff ambiguity %differs from selection-set size in that it not only 
 affects both uncertainty \emph{and} the strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
@@
 
-In our model we allow just one trait to evolve: social learning. All other parameters are exogenous. Our primary outcome measure is the observed
-frequency at which the social learning trait fixates in simulated populations. We study
-how the social learning fixation frequency responds to each of the four varieties of
-uncertainty considered in this paper. 
+In our model we allow just one trait to evolve: social learning.
+All other parameters are exogenous.
+Our primary outcome measure is the observed frequency at which the social learning trait fixates in simulated populations.
+We study how the social learning fixation frequency responds to each of the four varieties of uncertainty considered in this paper.
 % \mt{I changed this somewhat, please double
@@
 The structure of the environment is specified by several parameters that remain fixed throughout the course of a given simulation (Table~\ref{tab:uncertaintyParameters}).
-The environment affords $B$ behaviors, where $B$ is the \emph{selection set size}.
+The environment affords $B$ behaviors, where $B$ is the \emph{selection-set size}.
 Uncertainty increases with $B$.
 Each behavior is indexed by $b$ and yields a payoff of 1 with probability $\pi_b$ and a payoff of 0 otherwise.
-As such, $\pi_b$ is equivalently the expected
-payoff of behavior $b$.
+As such, $\pi_b$ is equivalently the expected payoff of behavior $b$.
 At the beginning of each generation, one behavior is optimal and yields expected payoff $\pihigh$; the other $B-1$ behaviors yield a lower payoff, $\pilow$.
@@
 
-        $B$       & Selection set size: number of behavior options
+        $B$       & selection-set size: number of behavior options
                   & 2, 4, 10 \\
@@
 \noindent 
-A child inherits its
-parent's social learning trait $s_i$ without mutation.  A social learner child with
-$s_i = 1$ learns from a teacher from its parent's generation, including possibly
-their parent (i.e., both vertical and oblique learning are possible).  A child
-chooses its teacher by first randomly selecting $N_T$ prospective teachers from the
-population, then selecting the one in this set with the greatest payoff net, with ties broken randomly. By first subsetting $N_T$
-prospective teachers we represent the fact that access to the entire population is
-not generally guaranteed, though this type of algorithm yields qualitatively
-similar results to ones that do not first produce subsamples
-\citep{smaldino2019open} and we show in the supplement 
-that our results are robust to different $N_T$
+A child inherits its parent's social learning trait $s_i$ without mutation.
+A social learner child with $s_i = 1$ learns from a teacher from its parent's generation, including possibly their parent (i.e., both vertical and oblique learning are possible).
+A child chooses its teacher by first randomly selecting $N_T$ prospective teachers from the population, then selecting the one in this set with the greatest payoff net, with ties broken randomly.
+By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \citep{smaldino2019open} and we show in the supplement that our results are robust to different $N_T$
 (Figure~\ref{fig:nteachersSensitivity}). Social learner $i$ adopts their chosen 
-teacher $j$'s observed average payoffs for each behavior, $b$, i.e. 
+teacher $j$'s observed average payoffs for each behavior, $b$, i.e., 
 $\ledger \leftarrow \bar\pi_{jb}$; 
-and agent $i$'s count of behavioral observations, $c_{ib}$, is set to 1 if teacher $j$ had at least one observation of behavior $b$,  
-and $c_{ib}$ is set to 0 otherwise. This way, expected payoffs remain within $[0,
-1]$, but social learners are flexible to adjust to environmental change. 
-Setting $c_{ib}$ to 1 reflects the fact that the social learner
-treats the teacher's information as a single observation with the associated
-uncertainty. Asocial learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and
-$\ledger = 0$ for each behavior, $b$.
-(Figure~\ref{fig:schematic}C). The newly initialized population
-then repeats the within-generation dynamics.
+and agent $i$'s count of behavioral observations, $c_{ib}$, is set to 1 if teacher $j$ had at least one observation of behavior $b$, and $c_{ib}$ is set to 0 otherwise.
+This way, expected payoffs remain within $[0, 1]$, but social learners are flexible to adjust to environmental change.
+Setting $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single observation with the associated uncertainty.
+Asocial learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ for each behavior, $b$.
+(Figure~\ref{fig:schematic}C).
+The newly initialized population then repeats the within-generation dynamics.
 
@@
 To analyze the effect of the four principal uncertainty factors, we systematically
-varied uncertainty values (Table~\ref{tab:modelParameters}) and observed how frequently social learning evolved across
-1000 trial simulations for each combination of parameters tested.
+varied uncertainty values (Table~\ref{tab:modelParameters}) and observed how frequently social learning evolved across 1000 trial simulations for each combination of parameters tested.
 %We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L \in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.
-We observed three outcome measures, with $\meansl$ as the primary measure: the average value of $s_i$ over all agents and trials. To support our conclusions
-about $\meansl$, we also measured $\meanG$, the mean
-number of generations to fixation, and $\meanpi / L$, the average net  payoffs at the end of the simulation across agents and trials, normalized by lifespan (see Table~\ref{tab:outcomeVariables}). 
+We observed three outcome measures, with $\meansl$ as the primary measure: the average value of $s_i$ over all agents and trials.
+To support our conclusions about $\meansl$, we also measured $\meanG$, the mean number of generations to fixation, and $\meanpi / L$, the average net  payoffs at the end of the simulation across agents and trials, normalized by lifespan (see Table~\ref{tab:outcomeVariables}).
 We analyze
 outcomes by plotting $\meansl$ on the y-axis and environmental variability on
-x-axis, since we
-theoretically expect that $\meansl$ will always decrease monotonically from 1 to 0 as $u$
-increases.
+x-axis, since we theoretically expect that $\meansl$ will always decrease monotonically from 1 to 0 as $u$ increases.
 %Note that the hypothesis-testing concept of significance is meaningless here because we could make any small outcome difference ``significant'' by running more simulation trials.
@@
 using the Agents.jl agent-based modeling library~\citep{Datseris2022} and run
-on the Sherlock supercomputing cluster at Stanford University. Model and analysis code is
-publicly available on GitHub at \url{https://github.com/mt-digital/UncMod}.
+on the Sherlock supercomputing cluster at Stanford University. Model and analysis code is publicly available on GitHub at \url{https://github.com/mt-digital/UncMod}.
 
@@
 The number of behavioral options, i.e., larger $B$, favors the evolution of social learning.
-Increasing the selection set size expands the range of $u$ over which social learning is favored for two reasons.
+Increasing the selection-set size expands the range of $u$ over which social learning is favored for two reasons.
 First, when the environment remains constant between generations, the value of social learning increases with more behavioral options, because it effectively increases the number of observations that one can learn from by comparing the payoffs of several models.
-In other words, relying $only$ on one's asocial trial and error learning is less likely to yield useful information when the search space is large.
+In other words, relying \emph{only} on one's asocial trial-and-error learning is less likely to yield useful information when the search space is large.
 Second, when the environment changes, bias against the new optimal is weaker with more behavioral options.
 For example, with only two behavioral choices ($B = 2$), a common assumption in many models, social learning is particularly detrimental when the environment changes since more of the population will have arrived at the optimal behavior in the previous generation and socially learning from them will be biased against the correct choice.
-These two mechanisms make it particularly profitable to engage in social learning when the selection set size is larger -- for large values of $B$ social learning can even be favored when the environment is more likely to change than not (i.e., $u>0.5$).
+These two mechanisms make it particularly profitable to engage in social learning when the selection-set size is larger---for large values of $B$ social learning can even be favored when the environment is more likely to change than not (i.e., $u>0.5$).
 
@@
 behaviors. Second, and perhaps more importantly, natural selection on strategies
-that $do$ reliably select the optimal behavior is relatively weak. This means that
-the effect of drift is relatively stronger, weakening selection in favor of social
-learning under low values of $u$ and weakening selection against social learning
-under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row). 
-This effect was especially strong under other types of uncertainty, i.e., larger selection set sizes and especially shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
+that \emph{do} reliably select the optimal behavior is relatively weak.
+This means that the effect of drift is relatively stronger, weakening selection in favor of social learning under low values of $u$ and weakening selection against social learning under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row).
+This effect was especially strong under other types of uncertainty, i.e., larger selection-set sizes and especially shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
 
@@
 
-\subsection{Evolutionary drift and the relative benefit of social learning}
+\subsection{Evolutionary drift}
 
@@
 
-Figure~\ref{fig:steps} shows drift in terms of the average number of generations to fixation, 
-$\meanG$, across all uncertainty
-parameters. Drift was greatest overall when payoff ambiguity was greatest, i.e., when $\pilow = 0.8$.
-When payoffs are highly ambiguous there is relatively little advantage to the
-optimal learning strategy, and therefore relatively weak selective pressure.
-
-$\meanG$ peaks at the values of $u$ where social learning becomes suppressed. 
-$B$ and $\pilow$ have the
-clearest effects on the location of greatest drift over $u$. $L$ has some effect on the location of peak
-drift over $u$, but $L$ also has a large effect on the overall amount of drift: $L=1$ tends to have the most
-drift with sufficiently low payoff ambiguity ($\pilow < 0.8$). The effect of lifespan on drift is
-non-monotonic, since we observe that long lifespans can also result in relatively greater drift
-compared to lifespans other than $L=1$ (e.g., in Figure~\ref{fig:steps}, top left and right).
-When $L=1$ selection pressure may be relatively weak since agents have no opportunity
-for individual learning, and social learning is the only learning channel. 
-When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning has many 
-opportunities for finding the optimal behavior, which means social learning
-provides a relatively weaker constraint on net payoffs over agent lifespans.
-This also results in weaker selection pressure since there is relatively little
-difference between social and asocial constraints when $L$ is large
+Figure~\ref{fig:steps} shows drift in terms of the average number of generations to fixation, $\meanG$, across all uncertainty parameters.
+Drift was greatest overall when payoff ambiguity was greatest, i.e., when $\pilow = 0.8$.
+When payoffs are highly ambiguous there is relatively little advantage to the optimal learning strategy, and therefore relatively weak selective pressure.
+
+$\meanG$ peaks at the values of $u$ where social learning goes from being favored to suppressed.
+Uncertainty due to selection-set size, $B$, and payoff ambiguity, $\pilow$, has the clearest effects on the values of $u$ for which we see greatest drift.
+As uncertainty due to $B$ and $\pilow$ increase, social learning is generally favored for a greater range of $u$.
+This pushes up the values of $u$ with greatest drift.
+Effective lifespan, $L$, has some effect on the location of peak
+drift over $u$, but $L$ has a more consistent effect on the overall amount of drift: $L=1$ tends to have the most drift, especially when payoff ambiguity is low ($\pilow < 0.8$).
+However, the effect of lifespan on drift is non-monotonic---longer lifespans can also result in greater drift compared to intermediate lifespans (e.g., in Figure~\ref{fig:steps}, top left and top right).
+When $L=1$, selection pressure may be relatively weak since agents have no opportunity for individual learning, and social learning is the only learning channel.
+When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning allows agents many opportunities to find the optimal behavior, which means social learning provides a relatively weaker constraint on net payoffs over agent lifespans.
+This also results in weaker selection pressure since there is relatively little difference between social and asocial constraints when $L$ is large
 (Figure~\ref{fig:steps}, top two rows).
 
-We also tracked and analyzed average net payoffs of agent populations across
-all uncertainty parameters, and compared the simulated payoffs to 
-homogenous all-social learner or all-asocial learner populations. Homogenous payoffs
-were calculated by initializing simulation populations to be all social or all asocial learners,
-then running the model for 100 generations so payoffs could stabilize; we then averaged 
-the net payoffs from the final generation across 1000 trials to calculate the average
-homogenous payoffs.
+\subsection{Relative benefits of social learning in context}
+
+To check that populations evolved towards the learning strategy with higher expected payoffs, we also tracked the average net payoffs of agent populations across
+all uncertainty parameters and compared these to the payoffs of homogeneous populations of all-social learners or all-asocial learners.
+Average payoffs for the homogeneous populations were calculated by initializing simulation populations to be all-social or all-asocial learners, running the model for 100 generations so payoffs could stabilize, and finally averaging the net payoffs from the last generation across 1000 trials.
+Because simulations had no mutation, these homogeneous populations persisted as all social or asocial learners.
 
 Figure~\ref{fig:payoffs} shows the average net payoffs normalized by lifespan
-for our simulations compared with the two reference homogenous populations
+for our main simulation compared with the two reference homogeneous populations
 initialized either as all social or all asocial learners.
-Often the simulated payoffs follow the payoffs from the better-performing
-homogenous group, but there are several important deviations to understand.
-First, we observed frequency dependence of social learning, where 
-agents from our main simulations who evolved to be social learners 
-outperform agents in the homogenous social learner populations. This is most
-pronounced when $L=1$, across all other uncertainty parameters, and even more
-pronounced when $\pilow=0.45$ and $B=10$ (Figure~\ref{fig:payoffs}, middle right).
-In these cases, the presence of asocial learners before social learning fixated
-enabled social learners in our simulations to outperform all-social learner populations.
-Frequency dependence of social learning payoffs even pushed social learning to evolve even
-when the expected homogenous social learning payoff was less than the expected homogenous
-asocial learning payoff (Figure~\ref{fig:payoffs}, middle center $L=1$).
-We also observed cases where long-lived populations ($L=4$ and $L=8$) in simple environments
-($B=2$) evolved to be individual learners, even though all-social learner populations
-outperformed all-individual learner populations (Figure~\ref{fig:payoffs}, upper left).
-
-We explain these deviations from expected homogenous payoffs 
-by inspecting time series of individual model runs where we plot the geometric
-moving averages (with time window 3) of the payoffs for the whole population, and
-for the series of payoffs broken out by asocial/social learner sub-populations; we
-compare these mean payoff series to the expected homogenous social and asocial payoffs, the time series of social learner prevalence, and to the timing of environmental changes within the simulation (Figure~\ref{fig:payoffTimeseries}).
-When lifespan was minimal ($L=1$) and environmental variability
-was moderate ($u\approx0.5$), the payoff time series show a period of environmental
-stability led populations to fixate to social learning, despite individual learning
-being the superior long-term strategy (Figure~\ref{fig:payoffTimeseries}a).
-When payoff ambiguity and decision set size was small ($\pilow=0.1$ and $B=2$), 
-and lifespan was long ($L=4$ and $L=8$),
-asocial learning fixated as a hedge against periods of protracted environmental
-instability, which caused social learning to frequently provide
-outdated information, even though expected homogenous social payoffs are greater than
-homogenous asocial payoffs (Figure~\ref{fig:payoffTimeseries}b,c).
-
-%We measured drift by the average number of generations to fixation, $\meanG$. Recall fixation is defined as the population becoming homogenous, composed of all social or all asocial learners. 
+Often the simulated payoffs follow the payoffs of the better-performing homogeneous group.
+However, there are several important deviations worth explaining.
+First, agents from our main simulations who evolved to be social learners sometimes outperformed agents in the homogeneous social learner populations.
+This is most pronounced when $L=1$, and even more
+so when $\pilow=0.45$ and $B=10$ (Figure~\ref{fig:payoffs}, middle right).
+In fact, social learning evolved even in parts of the parameter space where the expected homogeneous social learning payoff was lower than the expected homogeneous
+asocial learning payoff (Figure~\ref{fig:payoffs}, e.g., middle center $L=1$).
+Second, we also observed the opposite dynamic: populations sometimes evolved to be asocial learners, even though all-social learner populations outperformed all-individual-learner populations when agents were long-lived ($L=4$ and $L=8$) and in simple environments ($B=2$; Figure~\ref{fig:payoffs}, e.g., upper left).
+
+Our simulations' deviations from expected homogeneous payoffs reflect the effects of frequency-dependent payoffs and of stochastic environmental changes that affect geometric mean fitness.
+Frequency dependence is implicated in cases where our simulated agents that ended up as social learners outperformed homogeneous all-social-learner populations.
+In such cases, the earlier presence of asocial learners before social learning fixated enabled social learners in our simulations to outperform all-social learner populations.
+To illustrate the effects of stochastic runs of stable and unstable environments we inspected time series of individual model runs (Figure~\ref{fig:payoffTimeseries}).
+We plotted the geometric moving averages (time window = 3) of the payoffs for the whole simulated population, and for the simulated sub-populations of asocial and social learners.
+We compared these mean payoff series to the expected homogeneous social and asocial payoffs, the time series of social-learner prevalence, and to the timing of environmental changes within the simulation (Figure~\ref{fig:payoffTimeseries}).
+
+When lifespan was minimal ($L=1$) and environmental variability was moderate ($u\approx0.5$), the payoff time series showed a period of environmental stability could lead the population to fixate to social learning, despite individual learning being the superior long-term strategy (Figure~\ref{fig:payoffTimeseries}a).
+On the other hand, when payoff ambiguity and decision-set size was small ($\pilow=0.1$ and $B=2$), and lifespan was long ($L=4$ and $L=8$), asocial learning fixated as a hedge against periods of protracted environmental instability, even though expected homogeneous social payoffs were greater than homogeneous asocial payoffs (Figure~\ref{fig:payoffTimeseries}b,c).
+Runs of environmental change strongly affected the geometric mean fitness of social learners who were weighing
+outdated information too heavily. %\cm{is there something worth pointing out as different between b and c? If not maybe just choose one? I'd choose b}
+
+%We measured drift by the average number of generations to fixation, $\meanG$. Recall fixation is defined as the population becoming homogeneous, composed of all social or all asocial learners. 
 % $\meanG$ peaks around the values of $u$ 
@@
   \caption{Average number of generations ($\meanG$, y-axes) to fixation. 
-    Note the y-axis ticks vary between plots, indicating different overall 
-    time to fixation for different $(\pilow, B)$ pairs.} 
+    Note the y-axis scale varies between plots, indicating different overall 
+    time to fixation for different $(\pilow, B)$ combinations.} 
   \label{fig:steps}
@@
   \caption{Comparison of observed average payoffs in simulations with average payoffs
-    obtained by populations homogenously initialized to be all social or all asocial learners.
-    Often the simulated payoffs follow the payoffs from the better-performing
-    homogenous group, with some exceptions discussed in the main text.
-}
+    obtained by populations homogeneously initialized to be all social or all asocial learners.
+Often the simulated payoffs follow the payoffs from the better-performing homogeneous group, with some exceptions discussed in the main text.}
   \label{fig:payoffs}
@@
     social learners, asocial learners, and whole population, compared with the
-    expected homogenous social and asocial population payoffs. 
-    Social learner prevalence is also plotted. Vertical lines indicate
-  environmental change.}
+    expected homogeneous social and asocial population payoffs. Social-learner prevalence is also plotted. Vertical lines indicate environmental change.}
     \label{fig:payoffTimeseries}
@@
       \centering
-    \caption{$\pilow=0.1$, $B=4$, $L=1$, $u=0.5$}
+    \caption{$u=0.5$, $\pilow=0.1$, $B=4$, $L=1$}
       \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=4-L=1.pdf}
@@
       \centering
-      \caption{$\pilow=0.1$, $B=2$, $L=4$, $u=0.2$}
+      \caption{$u=0.2$, $\pilow=0.1$, $B=2$, $L=4$}
       \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=4.pdf}
@@
       \centering
-      \caption{$\pilow=0.1$, $B=2$, $L=8$, $u=0.2$}
+      \caption{$u=0.2$, $\pilow=0.1$, $B=2$, $L=8$}
       \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=8.pdf}
@@
 
-We performed sensitivity analyses to ensure that our main analysis is reasonably
-robust to a range of auxiliary parameters. These sensitivity analyses are presented in full in the
-supplemental material.
-First, we confirmed that our results were robust to various population sizes $N$, though smaller $N$ simulations had more drift as expected due to stronger finite population size effects (Figure~\ref{fig:populationSensitivity}).
+We performed sensitivity analyses to ensure that our main analysis was reasonably
+robust to a range of auxiliary parameters.
+These sensitivity analyses are presented in full in the supplemental material.
+First, we confirmed that our results were robust to various population sizes $N$, though smaller-$N$ simulations had more drift, as expected, due to stronger effects of finite population size (Figure~\ref{fig:populationSensitivity}).
 %, but  still generally support our main conclusions.
-Next, we verified model robustness to the number of prospective teachers, $N_T \in \{2, 20\}$, to supplement the main results that used $N_T = 5$. The number of prospective
-teachers did not change the results (Figure~\ref{fig:nteachersSensitivity}), except to increase drift when $N_T = 2$, since the benefit of social learning may
-be more difficult to detect with fewer prospective teachers (Figure~\ref{fig:nteachersSensitivity}a). Finally, we confirmed our results were reasonably 
-robust to a wide range of
-softmax greediness parameters, $\beta \in \{1, 100\}$, to supplement the main results
-that used $\beta = 10$.
-However, when $\beta = 1$, a lack of greed caused agents to often ignore helpful social information  (Figure~\ref{fig:softmaxSensitivity}a).
-Too much greed ($\beta=100$) made social learners inflexible so they could not recover as well when when they learned outdated social information, which was most pronounced for longer-lived agents who may spend several time steps performing a sub-optimal behavior (Figure~\ref{fig:softmaxSensitivity}b).
+Next, we verified model robustness to the number of prospective teachers, $N_T \in \{2, 20\}$, to supplement the main results that used $N_T = 5$.
+The number of prospective teachers did not change the results (Figure~\ref{fig:nteachersSensitivity}), except to increase drift when $N_T = 2$, since the benefit of social learning may be more difficult to detect with fewer prospective teachers (Figure~\ref{fig:nteachersSensitivity}a).
+Finally, we confirmed our results were reasonably robust to a wide range of softmax greediness parameters, $\beta \in \{1, 100\}$, to supplement the main results that used $\beta = 10$.
+However, when $\beta = 1$, an insufficient reliance on the best-paying behavior (i.e., low greed) caused agents to often ignore helpful social information  (Figure~\ref{fig:softmaxSensitivity}a).
+On the other hand, too much greed ($\beta=100$) made social learners inflexible so they could not recover as well when when they learned outdated social information.
+This cost to greediness was most pronounced for longer-lived agents who may spend several time steps performing a sub-optimal behavior (Figure~\ref{fig:softmaxSensitivity}b).
 
@@
 By disambiguating various formalizations of uncertainty in a single computational model, we have developed a more nuanced theoretical understanding of how uncertainty affects the evolution of social learning.
-%We reviewed and distilled several empirical and theoretical models in the literature along four uncertainty dimensions: temporal environmental uncertainty, selection set size, ambiguous payoffs, and effective lifespan.
-We reproduced the well-known results that the uncertainty derived from a temporally variable environment can limit the evolution of social learning if environmental change is simply too rapid for intergenerational transmission to be of value.
+%(but see \citet{healy2017}).
+%We reviewed and distilled several empirical and theoretical models in the literature along four uncertainty dimensions: temporal environmental uncertainty, selection-set size, ambiguous payoffs, and effective lifespan.
+We reproduced the well-known results that the uncertainty derived from a temporally-variable environment can limit the evolution of social learning if environmental change is simply too frequent for intergenerational transmission to be of value.
 Importantly, we also showed that this relationship is affected by other sources of uncertainty.
@@
 However, these effects were not always straightforward.
-Increased payoff ambiguity and decreased effective lifespan afforded a greater role for drift, which is essentially
-evolutionary uncertainty in a finite-size population.
+Increased payoff ambiguity and decreased effective lifespan afforded a greater role for drift (i.e., evolutionary uncertainty in a finite-size population).
 Not surprisingly, when the consequence of one's choice does not affect payoffs much, selection either for or against social learning is substantially weaker.
@@
 This enabled agents to recover from the potential cost of receiving outdated information.
-This in turn enabled the evolution of social learning even when social information was likely to be outdated.
+This, in turn, enabled the evolution of social learning even when social information was likely to be outdated.
 
@@
 ignore social information from previous generations since our natural world is
-rapidly changing~\citep{IPCC2022}; on the other hand, humans have increasingly more
-behavioral options (selection set size) with high levels of uncertainty about which behaviors are most beneficial (payoff ambiguity), and in this case our model predicts a greater prevalence of social learning.
-In general, detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly changing world.
-Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\citep{Moya2020,Jones2021}, especially in
-the most vulnerable communities~\citep{McNamara2020}, and to capitalize on new behavioral opportunities such as transitioning to clean energy use and
-production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}. However, to better identify
-potential pathways to effective adaptation it may be necessary to adjust some of our modeling assumptions to
-include both the cumulative nature of cultural evolution and group structure of interpersonal exchange, both
-of which affect the sustainability of novel adaptations~\citep{Derex2020,Centola2018,Smaldino2021a}.
-\cm{should we draw out some implications?
-I find this difficult, but e.g.
-stressing environmental change may discourage learning from older gen?
-having more tech options available for dealing with climate change may encourage social learning?
-Frankly so many of these problems seem to come back to encouraging people to socially learn from the RIGHT people, not just socially or asocially learning.} \mt{I gave this a try, with some restructuring to put the note about social learning as a scaffold for individual learning in the above paragraph.}
-
-Our model necessarily made simplifying assumptions. These were chosen judiciously to address the main
-question of how uncertainty affects the evolution of social learning. Two critical assumptions we made have
-important consequences for comparing our results with previous findings in the literature. First, we assume
-all agents engage in individual learning. This means that individual learning is effectively free, though
-potentially inaccurate. Although producing new knowledge may be costly, many other adaptive problems take
-the form of essentially cost free individual learning. For example, one cannot help but experience the association between; clouds and rain, thirst and drinking water, or smiling and
-being avoided. This model thus avoids scrounger/producer dynamics common in other models
-~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and
-asocial learners.  Second, we only allow for intergenerational social learning and environmental change.
-Within generations agents can only learn asocially, meaning they cannot learn from their peers. This
-assumption allows us to replicate the classic finding that if the environmental change too quickly, socially
-learned information will be useless. Alternative formalizations for the timing of social learning and
-environmental change would break this relationship~\citep{Turner2022}.
+rapidly changing~\citep[e.g.,][]{IPCC2022}.
+On the other hand, humans have increasingly more behavioral options (selection-set size) with high levels of uncertainty about which behaviors are most beneficial (payoff ambiguity), and in this case our model mostly predicts a greater prevalence of social learning.
+In general, detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly-changing world.
+%Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\citep{Moya2020,Jones2021}, especially in the most vulnerable communities~\citep{McNamara2020}, and to capitalize on new behavioral opportunities such as transitioning to clean energy use and production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+However, to better identify potential pathways to effective adaptation it may be necessary to adjust some of our modeling assumptions to the cumulative nature of cultural evolution and group structure of interpersonal exchange, both of which affect the sustainability of novel adaptations~\citep{Derex2020,Centola2018,Smaldino2021a}.
+%\cm{I guess I'd delete everything from "Such understandinc could suggest ....
+" It seems like such an implausible connectin and cheap talk, but others may disagree.} \mt{I gave this a try, with some restructuring to put the note about social learning as a scaffold for individual learning in the above paragraph.}
+
+Our model necessarily made simplifying assumptions.
+These were chosen judiciously to address the main question of how uncertainty affects the evolution of social learning.
+Two critical assumptions we made have important consequences for comparing our results with previous findings in the literature.
+First, we assume all agents engage in individual learning.
+This means that individual learning is effectively free, though
+potentially inaccurate.
+Although producing new knowledge may be costly, many other adaptive problems take the form of essentially cost-free individual learning.
+For example, it is hard not to encode association between clouds and rain, between thirst and drinking water, or between friendship and warm laughter.
+This model thus avoids producer/scrounger dynamics common in other models ~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and asocial learners.
+Second, we only allow for intergenerational social learning and environmental change.
+Within generations, agents can only learn asocially, meaning they cannot learn from their peers.
+This
+assumption allows us to replicate the classic finding that if the environment changes too quickly, socially-learned information will be useless.
+Alternative formalizations for the timing of social learning and environmental change would break this relationship~\citep{Turner2022}.
 
@@
 % that may not always hold in more specific situations, though they are empirically justified to be general across taxa.
-For example, we only considered success-biased
-learning, although people may use conformity or other context biases to socially
-learn~\citep{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.  This modelling
+For example, we only considered success-biased learning, although people may use conformity or other context biases to socially learn~\citep{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.
+This modeling
 choice maximizes the potential benefit to social learners, which suggests that
-other mechanisms, like conformity, may lead to more drift overall. We also assumed that the number of behaviors and
-their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g.\ via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
+other mechanisms, like conformity, may lead to more drift overall.
+We also assumed that the number of behaviors and their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g., via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
 %supported by dynamic network structure
-~\citep{Smolla2019,Derex2020}.  Group structure
-and processes such as homophily and other group-level biases could inhibit the
-evolution of social learning since successful out-group teachers could be cut off from
-in-group learners~\citep{Golub2012}. We assumed agents choose behaviors via softmax
-search, which is more cognitively sophisticated than most social learning models, but real human learning mechanisms are more powerful~\citep{Schulz2020a,Wu2022}.
-More powerful individual learning could further
-support the evolution of social learning. These considerations reveal new opportunities to enhance theoretical nuance by adjusting or extending the present model for other contexts.
+~\citep{Smolla2019,Derex2020}.
+Group structure and processes such as homophily and other group-level biases could inhibit the evolution of social learning since successful out-group teachers could be cut off from in-group learners~\citep{Golub2012}.
+We assumed agents choose behaviors via softmax
+search, which is more cognitively sophisticated than most social-learning models, but in line with real human learning mechanisms ~\citep{Schulz2020a,Wu2022}.
+Even more realistic and powerful individual learning could further support the evolution of social learning.
+These considerations provide novel opportunities to expand the evolutionary theory of social learning by adding novel learning mechanisms to our model.
+%% Too much nuance!! This is the third time. Always remember Healy (2017).
 
@@
 %We found that the 
-The evolution of social learning is a complex phenomenon, dependent on many interrelated factors.
-Although social learning is widely studied, few studies have previously examined how various environmental variables contributing to uncertainty interact.
-By carefully identifying and operationalizing common forms of  uncertainty in social learning models, we developed a more systematic
-understanding of which uncertainty factors interact to determine whether social
-learning evolves. By explicitly modeling a key individual-level learning mechanism
-shared across taxa, namely the ability to adjust behavior to uncertainty and new
-information, we saw that social learning could evolve even if social learning
-often provides outdated information.
-
-Social learning is a critical component of problem solving among social creatures.
-Our work identified and systematized some important forms of uncertainty and catalogued their effects on 
-the evolution of social learning. Our work, then, both advances the theory of social
-learning and could eventually be of practical use in designing sustainable
-adaptations to an uncertain future.
+The evolution of social learning is a complex phenomenon, dependent on many interrelated factors, yet it is widespread across a range of taxa.
+Although social learning is broadly studied, few studies have taken a systematic approach to understanding the role of uncertainty in the evolution social learning.
+Understanding the role of uncertainty in social evolution is particularly important for understanding human evolution as evidence increasingly suggests that the genus \emph{Homo} emerged in the context of substantial (nonstationary) environmental variability \citep{anton_etal2014, levin2015} and our global dispersal suggests that human groups regularly face novel environments.
+By carefully identifying and operationalizing different forms of  uncertainty common in social learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution.
+By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the ability to adjust behavior to uncertainty and new information, we found that social learning could evolve even if it provides outdated information.
+%Social learning is a critical component of problem solving among social creatures.
+Our work identified and systematized some important forms of uncertainty and catalogued their effects on the evolution of social learning.
+Our work, then, both advances the theory of social learning and could eventually be of practical use in identifying specific mechanisms underlying adaptations to an uncertain environments.
 % This work most directly informs our current understanding of the evolution of social learning, but also has broader significance for understanding problem solving under uncertainty. 
-\ps{What is this significance? Can't just leave that dangling. I also cut the bit about what comes next. No need for spoilers.} \mt{Gave this a try, but I think Jamie should have a crack at this.}
+%\ps{What is this significance? Can't just leave that dangling. I also cut the bit about what comes next. No need for spoilers.} \mt{Gave this a try, but I think Jamie should have a crack at this.}
 %Our model and its software implementation were designed to be modular and extensible.
@@
 
-\paragraph{Acknowledgements.} \mt{Do we write any at this point? Please fill in as you see fit.}
-
-\paragraph{Author contributions.} MAT led model development and analysis, with contributions from CM, PES, and JHJ.
+\paragraph{Acknowledgements.} %\mt{Do we write any at this point? Please fill in as you see fit.} \cm{can do later since should be blinded anyway}
+%
+
+\paragraph{Author contributions.} JHJ, CM, and PES conceived of the project.
+MAT led model development and analysis, with contributions from CM, PES, and JHJ.
 MAT wrote and edited the initial manuscript draft, which was extensively expanded and edited by CM, PES, and JHJ.
 
-\paragraph{Financial support.} \mt{Please fill in, thanks!}
+\paragraph{Financial support.} This work was supported by NSF grants BCS-2028160 and BCS-2118926 (JHJ PI) and  awards from the Center for Innovation in Global Health and the Center for Existential Risk, Stanford University to JHJ.
 
@@
 
-In this Supplement we support our model conclusions by showing that our model
+In this supplement we support our model conclusions by showing that our model
 outcomes are stable over various settings of the three free auxiliary model
@@
 ($N_T$), and the softmax behavior selection greediness parameter ($\beta$).
-The main source of minor deviations from the main results was greater drift
-due to (1) finite population size effects, with greater drift for smaller $N$;
+The results deviate only in minor ways from the main results primarily because of greater drift
+due to (1) finite population size effects (smaller $N$);
 (2) lower quality of socially-learned information when agents can access fewer
-prospective teachers; and (3) lower quality social information when $\beta$
-was small since teacher agents would have explored non-optimal behaviors more
+prospective teachers (lower $N_T$); and (3) lower quality social information when $\beta$
+was small (teacher agents would have explored non-optimal behaviors more
 frequently, so their observed payoffs would have less probability weight in
-the optimal payoffs on average. We give details below of model convergence, and
+the optimal payoffs on average). We give details below of model convergence, and
 outcomes as we varied the three auxiliary parameters $N$, $N_T$, and $\beta$.

### 2022-10-23 ms.tex
final for submission

@@
 
-\author[1,*]{Matthew A. Turner}
-\author[2,3]{Cristina Moya}
-\author[4,5,7]{Paul E. Smaldino}
-\author[1,6,7]{James~Holland~Jones}
+\author[1,2,*]{Matthew A. Turner}
+\author[3,4]{Cristina Moya}
+\author[5,6,7]{Paul E. Smaldino}
+\author[1,2,7]{James~Holland~Jones}
 
 \affil[1]{Department of Earth System Science, Stanford University, Stanford, CA 94305 USA}
-\affil[2]{Department of Anthropology, University of California at Davis, Davis, CA 95616 USA}
-\affil[3]{Centre for Culture and Evolution, Brunel University London, Uxbridge, UB8 3PH UK}
-\affil[4]{Cognitive and Information Sciences, University of California at Merced, Merced, CA 95340 USA}
-\affil[5]{Santa Fe Institute, Santa Fe, NM 87501 USA}
-\affil[6]{Division of Social Sciences, Stanford Doerr School of Sustainability, Stanford University, Stanford, CA 94305 USA}
+\affil[2]{Division of Social Sciences, Stanford Doerr School of Sustainability, Stanford University, Stanford, CA 94305 USA}
+\affil[3]{Department of Anthropology, University of California at Davis, Davis, CA 95616 USA}
+\affil[4]{Centre for Culture and Evolution, Brunel University London, Uxbridge, UB8 3PH UK}
+\affil[5]{Cognitive and Information Sciences, University of California at Merced, Merced, CA 95340 USA}
+\affil[6]{Santa Fe Institute, Santa Fe, NM 87501 USA}
 \affil[7]{Center for Advanced Study in the Behavioral Sciences, Stanford University, Stanford, CA 94305 USA}
@@
 \usepackage{xcolor}
-% \renewcommand{\linenumberfont}{\small\color{gray}}
 
@@
   %"probabilities of decisions" didn't make sense to me so I rephrased, but hopefully still accurate.
-  We identified four distinct and theoretically-important sources of uncertainty: temporal environmental variability, payoff ambiguity, decision-set size, and effective lifespan.
-All these kinds of uncertainty make it nearly impossible to fully learn about variability.
-We develop an evolutionary agent-based model to test how each form of uncertainty affects the evolution of social learning.
-Agents perform one of several behaviors, modeled as a multi-armed bandit, to acquire payoffs.
-All agents learn asocially using the cognitively-realistic softmax algorithm.
-Additional use of vertical and oblique social learning was allowed to evolve and served as a constraint on intra-generational asocial learning.
-We found that different types of uncertainty had varying effects.
-Temporal environmental variability suppressed social learning, whereas larger decision-set size promoted social learning, even when the environment changed frequently.
+  We identified four distinct and theoretically-important sources of uncertainty: temporal environmental variability, payoff ambiguity, selection-set size, and
+  effective lifespan. All these kinds of uncertainty make it nearly impossible to fully learn about variability. We develop an evolutionary agent-based model to
+  test how each form of uncertainty affects the evolution of social learning. Agents perform one of several behaviors, modeled as a multi-armed bandit, to
+  acquire payoffs. All agents learn individually using the cognitively-realistic softmax algorithm. Additional use of vertical and oblique social learning was
+  allowed to evolve and served as a constraint on intra-generational individual learning. We found that different types of uncertainty had varying effects. Temporal
+  environmental variability suppressed social learning, whereas larger selection-set size promoted social learning, even when the environment changed frequently.
 Payoff ambiguity and lifespan had more complex effects on social learning, dependent on interactions with other uncertainty parameters.
@@
 
-Social learning enhances problem-solving when acquiring information from others is more efficient than learning on one's own~\citep{Laland2004}.
+Social learning enhances problem solving when acquiring information from others is more efficient than learning on one's own~\citep{Laland2004}.
 However, social learning can also lead individuals astray if they are copying irrelevant, misleading, or outdated information.
@@
 uncertainty that are common in cultural evolution models and the related empirical
-literature:  (1) temporal environmental variability; (2) selection-set size (the number of possible behaviors); (3) payoff ambiguity (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of opportunities for individual learning), see next section for more details.
-In our model, social learners learn from the previous generation and asocial learners do not.
-All agents engage in individual learning within their lifespans.
-The model also assumes a more
+literature:  (1) temporal environmental variability; (2) selection-set size (the number of possible behaviors); (3) payoff ambiguity
+(the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of
+opportunities for individual learning), see next section for more details. In our model, social learners learn from the previous
+generation and asocial learners do not. All agents engage in individual learning within their lifespans. The model also assumes a
 cognitively-realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
@@
 We use this integrated model to ask which kinds of uncertainty are likely to favor social learning and to clarify the logic underlying the results.
-%of why this would be the case.  
 In the remainder of this introduction we briefly review previous research on both the forms of uncertainty and the learning mechanism used in our model.
-%We then present how our evolutionary agent-based model works.
-Finally, we explain the logic underlying the result that different forms of uncertainty can either suppress or encourage the evolution of social learning.
-
-%% \cm{from Jamie's intro, not sure we should incorporate the rest here since our model doesn't speak much to things like heavy tailed distributions or adaptive toolkit work: Despite the technical difficulties of dealing with uncertainty, addressing it is an essential task because it potentially changes our understanding of decision-making in a qualitative manner.
-The dominant approach to understanding decisions for choices with variable outcomes is expected utility theory (EUT).
-As the name suggests, EUT requires the ability to calculate expectations, which means that we must know the probability distributions of outcomes.
-The non-probabilistic nature of uncertainty means one cannot calculate expectations.
-Following \citep{savage1954}, various research traditions in decision theory and economics have treated uncertainty as if it were risk, just with subjective probabilities replacing objective ones.
-The fundamental problem with this approach was noted by \citep{geweke2001} and further developed by \citep{weitzman2009}.
-In particular, the probability density function of an outcome that needs to be learned, but for which opportunities for learning are highly constrained, will be heavy-tailed and expected-utility calculations will not work because of the resulting undefined mass-generating function.
-Uncertainty implies heavy-tailed probability distributions and heavy-tailed distributions require different analytical methods \citep{nair_etal2022}....para...The heuristic-based adaptive-toolbox approach of \citep{todd_gigerenzer2000} provides an alternative strategy for understanding decision-making under uncertainty.
-There is a strong intuition that uncertainty should activate specific social-learning heuristics.
-Within the cultural-evolution literature, uncertainty is generally thought to lead to a social heuristic known as \emph{conformist-biased learning} \citep{boyd_richerson1985, henrich_boyd1998, muthukrishna_etal2016}....para...True uncertainty arises when an organism lacks the capacity to learn about the possible outcomes of a decision task.
-This is very likely for a cosmopolitan species living in a coarse-grain environment.
-Task complexity also.
-Non-stationary environmental change \citep{kay_king2020}.
-These potential sources of uncertainty can also interact.}
-
-% \cm{I moved this for now: \emph{"Furthermore, many models of social learning evolution do not account for individual-level cognition~\citep{Heyes2016}, though humans clearly have evolved cognitive mechanisms for dealing with uncertainty generally~\citep{Gershman2019,Schulz2019}."} because I think it interrupted the flow and didn't seem directly linked to the goal of understanding aspects of uncertainty.
-However, if this is one of the main features of the model that we want to highlight as an improvement over previous work, then we probably have to say something more about it.
-Perhaps I just wasn't seeing the connection though, and the more accurate cognitive model DOES add to our ability to study the consequences of uncertainty.
-If that's the case, the argument should be sharpened.
-If not, maybe we put this info when the cognitive model is introduced.}\mt{Agreed.
-I put a first draft of a better version of this paragraph closer to/at the end of the Intro.}
-
-%\mt{This paragraph is a first try to introduce the four uncertainty dimensions with examples to illustrate the problem we are answering.
-I outlined the next paragraph to get into more details of social learning: how cultural evolution works; conformity, success-biased, etc.
-Cristina, please edit this.}
 
@@
 %~\citep{BoydRicherson1985,Rogers1988,kendal2009evolution}, 
-it has also been modeled using deterministic cycles, so that environments repeat at regular intervals ~\citep{Feldman1996, aoki2014evolution}.
+it has also been modeled using deterministic cycles, so that environments repeat at regular intervals~\citep{Feldman1996, aoki2014evolution}.
 %Furthermore, t
@@
 perreault2012bayesian}.
-% \cm{pretty sure boyd1995 uses same trick as
-% rogers 88 so not sure why they were being used as illustrating separate kinds of
-% behavior selection sets. correct if wrong} 
 Larger, more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\citep{derex2013, wasielewski2014}, but these map imperfectly onto the theoretical literature that tends to use a limited set of behavioral options.
-%\mt{How so?}. 
 Some models have studied systems with larger, but defined, selection sets~\citep{Rendell2010, lindstrom2016co}, while in others the number of options is subsumed under the probability that a learner gets the right  answer~\citep{Feldman1996,Enquist2007}.
@@
 All other parameters are exogenous.
-Our primary outcome measure is the observed frequency at which the social learning trait fixates in simulated populations.
+Our primary outcome measure is the observed frequency at which the social-learning trait fixates in simulated populations.
 We study how the social learning fixation frequency responds to each of the four varieties of uncertainty considered in this paper.
-% \mt{I changed this somewhat, please double
-% check it's clear} \ps{I edited a couple of words but looks good.}
 
@@
 each time step within a generation consisting of $L$ time steps.
-The behavior set is a multi-armed bandit with $B$ arms.
+The behavioral selection set is a multi-armed bandit with $B$ arms.
 That is, agents can pick one of $B$ behaviors with random-valued payoffs~\citep{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
@@
 At the end of each generation, agents are selected with replacement to reproduce a new generation of $N$ agents, with the probability of reproduction biased by net payoffs.
-Agents who inherit the social learning trait learn about payoffs from the previous generation, while asocial learners begin life only knowing the number of behaviors the environment affords, but have no knowledge of behavioral payoffs.
+Agents who inherit the social-learning trait learn about payoffs from the previous generation, while asocial learners begin life only knowing the number of behaviors the environment affords, but have no knowledge of behavioral payoffs.
 
@@
 
-        $B$       & selection-set size: number of behavior options
+        $B$       & Selection-set size: number of behavior options
                   & 2, 4, 10 \\
@@
 
-        $s_i$  & Social learner trait: 1 if agent $i$ is social learner; 0 otherwise & 0
+        $s_i$  & Social-learner trait: 1 if agent $i$ is social learner; 0 otherwise & 0
         or 1 equally likely \\
@@
 Within each generation, all $N$ agents perform $L$ behaviors sequentially and
-independently (Figure~\ref{fig:schematic}B).
+independently (Figure~\ref{fig:softmaxSensitivity}b).
 % Each agent $i$ selects one behavior on each step of its lifespan using softmax applied
@@
 \noindent 
-A child inherits its parent's social learning trait $s_i$ without mutation.
+A child inherits its parent's social-learning trait $s_i$ without mutation.
 A social learner child with $s_i = 1$ learns from a teacher from its parent's generation, including possibly their parent (i.e., both vertical and oblique learning are possible).
@@
 
-        $\meansl$ & Mean social learning prevalence over agents
+        $\meansl$ & Mean social-learning prevalence over agents
                   & $ [0.0, 1.0]$ \\
@@
 
-The number of behavioral options, i.e., larger $B$, favors the evolution of social learning.
-Increasing the selection-set size expands the range of $u$ over which social learning is favored for two reasons.
-First, when the environment remains constant between generations, the value of social learning increases with more behavioral options, because it effectively increases the number of observations that one can learn from by comparing the payoffs of several models.
-In other words, relying \emph{only} on one's asocial trial-and-error learning is less likely to yield useful information when the search space is large.
+The number of behavioral options, i.e., larger $B$, favors the evolution of social learning. Increasing the selection-set size
+expands the range of $u$ over which social learning is favored for two reasons. First, when the environment remains constant between
+generations, the value of social learning increases with more behavioral options, because it effectively increases the number of
+observations that one can learn from by comparing the payoffs of several models. In other words, relying \emph{only} on one's
+individual trial-and-error learning is less likely to yield useful information when the search space is large.
 Second, when the environment changes, bias against the new optimal is weaker with more behavioral options.
@@
 This means that the effect of drift is relatively stronger, weakening selection in favor of social learning under low values of $u$ and weakening selection against social learning under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row).
-This effect was especially strong under other types of uncertainty, i.e., larger selection-set sizes and especially shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
+This effect was especially strong under other types of uncertainty, i.e., larger selection-set sizes and shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
 
@@
 depended on the strength of natural selection, that is, on the extent to which the
-social learning trait provided agents with a consistent benefit. Drift infuses
+social-learning trait provided agents with a consistent benefit. Drift infuses
 randomness into natural selection. In this model, such randomness is introduced at
@@
 To check that populations evolved towards the learning strategy with higher expected payoffs, we also tracked the average net payoffs of agent populations across
-all uncertainty parameters and compared these to the payoffs of homogeneous populations of all-social learners or all-asocial learners.
-Average payoffs for the homogeneous populations were calculated by initializing simulation populations to be all-social or all-asocial learners, running the model for 100 generations so payoffs could stabilize, and finally averaging the net payoffs from the last generation across 1000 trials.
-Because simulations had no mutation, these homogeneous populations persisted as all social or asocial learners.
+all uncertainty parameters and compared these to the payoffs of homogeneous populations of all-social learners or all-asocial
+learners. Average payoffs for the homogeneous populations were calculated by initializing simulation populations to be all-social or
+all-asocial learners, running the model for 100 generations so payoffs could stabilize, and finally averaging the net payoffs from
+the last generation across 1000 trials. Because simulations had no mutation, these homogeneous populations persisted as all-social
+or all-asocial learners.
 
@@
 for our main simulation compared with the two reference homogeneous populations
-initialized either as all social or all asocial learners.
+initialized either as all-social or all-asocial learners.
 Often the simulated payoffs follow the payoffs of the better-performing homogeneous group.
@@
 so when $\pilow=0.45$ and $B=10$ (Figure~\ref{fig:payoffs}, middle right).
-In fact, social learning evolved even in parts of the parameter space where the expected homogeneous social learning payoff was lower than the expected homogeneous
-asocial learning payoff (Figure~\ref{fig:payoffs}, e.g., middle center $L=1$).
+In fact, social learning evolved even in parts of the parameter space where the expected homogeneous social-learning payoff was lower than the expected homogeneous
+asocial-learning payoff (Figure~\ref{fig:payoffs}, e.g., middle center $L=1$).
 Second, we also observed the opposite dynamic: populations sometimes evolved to be asocial learners, even though all-social learner populations outperformed all-individual-learner populations when agents were long-lived ($L=4$ and $L=8$) and in simple environments ($B=2$; Figure~\ref{fig:payoffs}, e.g., upper left).
@@
 We plotted the geometric moving averages (time window = 3) of the payoffs for the whole simulated population, and for the simulated sub-populations of asocial and social learners.
-We compared these mean payoff series to the expected homogeneous social and asocial payoffs, the time series of social-learner prevalence, and to the timing of environmental changes within the simulation (Figure~\ref{fig:payoffTimeseries}).
-
-When lifespan was minimal ($L=1$) and environmental variability was moderate ($u\approx0.5$), the payoff time series showed a period of environmental stability could lead the population to fixate to social learning, despite individual learning being the superior long-term strategy (Figure~\ref{fig:payoffTimeseries}a).
-On the other hand, when payoff ambiguity and decision-set size was small ($\pilow=0.1$ and $B=2$), and lifespan was long ($L=4$ and $L=8$), asocial learning fixated as a hedge against periods of protracted environmental instability, even though expected homogeneous social payoffs were greater than homogeneous asocial payoffs (Figure~\ref{fig:payoffTimeseries}b,c).
+We compared these mean-payoff series to the expected homogeneous social and asocial payoffs, the time series of social-learner prevalence, and to the timing of environmental changes within the simulation (Figure~\ref{fig:payoffTimeseries}).
+
+When lifespan was minimal ($L=1$) and environmental variability was moderate ($u\approx0.5$), the payoff time series showed a period
+of environmental stability that
+could lead the population to fixate to social learning, despite individual learning being the superior long-term strategy (Figure~\ref{fig:payoffTimeseries}a).
+On the other hand, when payoff ambiguity and selection-set size was small ($\pilow=0.1$ and $B=2$), and lifespan was long ($L \geq 4$), asocial learning fixated as a hedge against periods of protracted environmental instability, even though expected
+homogeneous social payoffs were greater than homogeneous asocial payoffs (Figure~\ref{fig:payoffTimeseries}b).
 Runs of environmental change strongly affected the geometric mean fitness of social learners who were weighing
 outdated information too heavily. %\cm{is there something worth pointing out as different between b and c? If not maybe just choose one? I'd choose b}
-
-%We measured drift by the average number of generations to fixation, $\meanG$. Recall fixation is defined as the population becoming homogeneous, composed of all social or all asocial learners. 
-% $\meanG$ peaks around the values of $u$ 
-% when $\meansoc \approx \meanasoc$, \cm{wait does it? Fig S2 doesn't seem to show the vertical lines mapping on well} which led $\meansl$ to transition from 1 to 0.
-% In some cases, especially when $\pilow=0.8$,
-% there is no distinct peak in $\meanG$ across $B$ and $L$ settings, 
-% indicating little difference in task difficulty across a range of uncertainty
-% parameter settings (Figure~\ref{fig:steps}, bottom row).
-
-% First, we confirmed that social learning evolves when the expected payoffs to social
-% learners exceed those of asocial learners, which we write $\meansoc > \meanasoc$.
-% In the case of $L=1$ we can calculate $\meanasoc$ directly: it is just the expected
-% payoff across all behaviors. For all other cases, we calculate expected social and asocial payoffs by respectively setting
-% $\sum_i s_i = N$ or $\sum_i s_i = 0$ at model initialization.
-These populations remain homogeneous since we do not allow for mutation.
-From these runs we calculate the payoffs to a population of either all social learners or all asocial learners after x generations \cm{you waited for them to stabilize or something right?
-only relevant for social learner population, but needs some more explanation}.
-Figure~\ref{fig:payoffs} shows these expected payoffs, normalized by effective lifespan $L$), as well as the observed average payoffs in our simulations.
-\ps{Is this right?
-I'm having trouble understanding what the solid lines in Figs 3 and 5 are.
-I'm also debating the wisdom of separating these figures.
-Maybe we put the 3x3 back in for Fig 3?}
-% In general, we observed that social learning evolved in our simulations when the expected payoffs exceeded expected individual-learner
-% payoffs (Figure~\ref{fig:payoffs}).
-This mapping of expectations to model results is reflected in Figure~\ref{fig:mainResults} given the vertical lines map onto the transitions from social to asocial learning in the curves.
-\cm{wait i wrote this and then noticed that I was looking at the wrong vertical lines (the <G> ones) now I'm confused.}
 
@@
     \caption{Example time series of geometric moving average (GMA) with window of 3
-      of payoffs from three select uncertainty settings (see main text), broken out by
+      of payoffs from two select uncertainty settings (see main text), broken out by
     social learners, asocial learners, and whole population, compared with the
@@
       \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=4.pdf}
-    \end{subfigure} \\
-
-\hspace{-2em}
-    \begin{subfigure}[]{0.75\textwidth}
-      \centering
-      \caption{$u=0.2$, $\pilow=0.1$, $B=2$, $L=8$}
-      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=8.pdf}
-    \end{subfigure}
-
-    % \\
-    % \begin{subfigure}[]{0.6\textwidth}
+    \end{subfigure} %\\
+
+% \hspace{-2em}
+%     \begin{subfigure}[]{0.75\textwidth}
 %       \centering
-    %   \caption{$\pilow=0.1$, $B=10$, $L=20$, $u=0.5$}
-    %   \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=10-L=20.pdf}
+%       \caption{$u=0.2$, $\pilow=0.1$, $B=2$, $L=8$}
+%       \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=8.pdf}
 %     \end{subfigure}
+
 \end{figure}
@@
 
- Despite the common claim that copying others makes sense when one is uncertain, we find that different forms of uncertainty can either promote or impede the evolution of social learning.
-By disambiguating various formalizations of uncertainty in a single computational model, we have developed a more nuanced theoretical understanding of how uncertainty affects the evolution of social learning.
-%(but see \citet{healy2017}).
+ Despite the common claim that copying others makes sense when one is uncertain, we find that different forms of uncertainty can
+ either promote or impede the evolution of social learning. By disambiguating various formalizations of uncertainty in a single
+ computational model, we have developed a more nuanced theoretical understanding of how uncertainty affects the evolution of social learning. %(but see \citet{healy2017}).
 %We reviewed and distilled several empirical and theoretical models in the literature along four uncertainty dimensions: temporal environmental uncertainty, selection-set size, ambiguous payoffs, and effective lifespan.
@@
 %Our model reproduced classic predictions that social learning can yield higher payoffs than individual learning when uncertainty is sufficiently limited. 
-We found that larger sets of behavioral options, shorter effective lifespans, and increased payoff ambiguity could all favor the evolution of social learning.
-However, these effects were not always straightforward.
-Increased payoff ambiguity and decreased effective lifespan afforded a greater role for drift (i.e., evolutionary uncertainty in a finite-size population).
-Not surprisingly, when the consequence of one's choice does not affect payoffs much, selection either for or against social learning is substantially weaker.
-More interestingly, selection is also weaker when the ability to learn asocially is fraught with uncertainty.
+We found that larger sets of behavioral options, shorter effective lifespans, and increased payoff ambiguity could all favor the
+evolution of social learning. However, these effects were not always straightforward. Increased payoff ambiguity and decreased
+effective lifespan afforded a greater role for drift (i.e., evolutionary uncertainty in a finite-size population). Not surprisingly,
+when the consequence of one's choice does not affect payoffs much, selection either for or against social learning is substantially
+weaker.
+More interestingly, selection is also weaker when the ability to learn individually is fraught with uncertainty.
 Our model demonstrated that social learning can act as a scaffold for individual learning---they are not opposite strategies.
@@
 
-Our model necessarily made simplifying assumptions.
-These were chosen judiciously to address the main question of how uncertainty affects the evolution of social learning.
-Two critical assumptions we made have important consequences for comparing our results with previous findings in the literature.
-First, we assume all agents engage in individual learning.
-This means that individual learning is effectively free, though
-potentially inaccurate.
-Although producing new knowledge may be costly, many other adaptive problems take the form of essentially cost-free individual learning.
-For example, it is hard not to encode association between clouds and rain, between thirst and drinking water, or between friendship and warm laughter.
-This model thus avoids producer/scrounger dynamics common in other models ~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and asocial learners.
-Second, we only allow for intergenerational social learning and environmental change.
-Within generations, agents can only learn asocially, meaning they cannot learn from their peers.
-This
+Our model necessarily made simplifying assumptions. These were chosen judiciously to address the main question of how uncertainty
+affects the evolution of social learning. Two critical assumptions we made have important consequences for comparing our results
+with previous findings in the literature. First, we assumed all agents engage in individual learning. This means that individual learning is effectively free, though
+potentially inaccurate. Although producing new knowledge may be costly, many other adaptive problems take the form of essentially
+cost-free individual learning. For example, it is hard not to encode association between clouds and rain, between thirst and
+drinking water, or between friendship and warm laughter. This model thus avoids producer/scrounger dynamics common in other
+models~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and asocial learners.
+Second, we only allow for intergenerational social learning and environmental change. Within generations, agents can only learn
+individually, meaning they cannot learn from their peers. This
 assumption allows us to replicate the classic finding that if the environment changes too quickly, socially-learned information will be useless.
@@
 
-We could have made alternative, empirically-valid, choices for a range of other structural features, the future exploration of which will be important to the development of a more nuanced theory of social learning.
+We could have made alternative, empirically-valid, choices for a range of other structural features, the future exploration of which
+will be important to the development of more parsimonious theories of social learning.
 % that may not always hold in more specific situations, though they are empirically justified to be general across taxa.
@@
 other mechanisms, like conformity, may lead to more drift overall.
-We also assumed that the number of behaviors and their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g., via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution
-%supported by dynamic network structure
-~\citep{Smolla2019,Derex2020}.
+We also assumed that the number of behaviors and their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g., via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution~\citep{Smolla2019,Derex2020}.
 Group structure and processes such as homophily and other group-level biases could inhibit the evolution of social learning since successful out-group teachers could be cut off from in-group learners~\citep{Golub2012}.
 We assumed agents choose behaviors via softmax
-search, which is more cognitively sophisticated than most social-learning models, but in line with real human learning mechanisms ~\citep{Schulz2020a,Wu2022}.
-Even more realistic and powerful individual learning could further support the evolution of social learning.
-These considerations provide novel opportunities to expand the evolutionary theory of social learning by adding novel learning mechanisms to our model.
-%% Too much nuance!! This is the third time. Always remember Healy (2017).
+search, which is more cognitively sophisticated than most social-learning models, but in line with real human learning
+mechanisms~\citep{Schulz2020a,Wu2022}. Even more realistic and powerful individual learning could further support the evolution of
+social learning. These considerations provide novel opportunities to expand the evolutionary theory of social learning by adding
+such learning mechanisms to our model.
 
@@
 %We found that the 
-The evolution of social learning is a complex phenomenon, dependent on many interrelated factors, yet it is widespread across a range of taxa.
-Although social learning is broadly studied, few studies have taken a systematic approach to understanding the role of uncertainty in the evolution social learning.
-Understanding the role of uncertainty in social evolution is particularly important for understanding human evolution as evidence increasingly suggests that the genus \emph{Homo} emerged in the context of substantial (nonstationary) environmental variability \citep{anton_etal2014, levin2015} and our global dispersal suggests that human groups regularly face novel environments.
-By carefully identifying and operationalizing different forms of  uncertainty common in social learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution.
+The evolution of social learning is a complex phenomenon, dependent on many interrelated factors, yet it is widespread across a
+range of taxa. Although social learning is broadly studied, few studies have taken a systematic approach to understanding the role
+of uncertainty in the evolution social learning. Understanding the role of uncertainty in social evolution is particularly important
+for understanding human evolution as evidence increasingly suggests that the genus \emph{Homo} emerged in the context of substantial
+(nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal suggests that human groups regularly face novel environments.
+By carefully identifying and operationalizing different forms of uncertainty common in social-learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution.
 By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the ability to adjust behavior to uncertainty and new information, we found that social learning could evolve even if it provides outdated information.
@@
 Our work, then, both advances the theory of social learning and could eventually be of practical use in identifying specific mechanisms underlying adaptations to an uncertain environments.
-% This work most directly informs our current understanding of the evolution of social learning, but also has broader significance for understanding problem solving under uncertainty. 
-%\ps{What is this significance? Can't just leave that dangling. I also cut the bit about what comes next. No need for spoilers.} \mt{Gave this a try, but I think Jamie should have a crack at this.}
-%Our model and its software implementation were designed to be modular and extensible.
-Indeed, we plan to extend this model to further develop a more detailed theoretical understanding of the evolution of social learning; we hope others will, too.
 
@@
 \bibliographystyle{apalike} %cite}
-% \bibliography{/Users/mt/workspace/Writing/library.bib}
 \bibliography{this.bib}
@@
 bottom row). The transition from $\meansl = 1$ to $\meansl = 0$ is less sharp
-across $L$ values, with social learning evolution being suppressed beginning
+across $L$ values, with social-learning evolution being suppressed beginning
 at smaller values of $u$. By contrast, when $N_T = 20$, transitions from 
@@
   \centering
-   \addtocounter{figure}{-1}
+   % \addtocounter{figure}{-1}
   \caption{Number of prospective teachers sensitivity analysis for $N_T=2,20$. Recall
@@
   \centering
-  \addtocounter{figure}{-1}
+  % \addtocounter{figure}{-1}
   \caption{Sensitivity analysis of the main results for the softmax parameter $\beta = 100$ and

### 2022-10-23 ms.tex
final submitted version

@@
 Uncertainty is a severe form of variability where the space of possible decisions or probabilities of associated outcomes are unknown.
-  %"probabilities of decisions" didn't make sense to me so I rephrased, but hopefully still accurate.
-  We identified four distinct and theoretically-important sources of uncertainty: temporal environmental variability, payoff ambiguity, selection-set size, and
-  effective lifespan. All these kinds of uncertainty make it nearly impossible to fully learn about variability. We develop an evolutionary agent-based model to
-  test how each form of uncertainty affects the evolution of social learning. Agents perform one of several behaviors, modeled as a multi-armed bandit, to
-  acquire payoffs. All agents learn individually using the cognitively-realistic softmax algorithm. Additional use of vertical and oblique social learning was
-  allowed to evolve and served as a constraint on intra-generational individual learning. We found that different types of uncertainty had varying effects. Temporal
-  environmental variability suppressed social learning, whereas larger selection-set size promoted social learning, even when the environment changed frequently.
+We identified four distinct and theoretically-important sources of uncertainty: temporal environmental variability, payoff ambiguity, selection-set size, and effective lifespan.
+All these kinds of uncertainty make it nearly impossible to fully learn about variability.
+We develop an evolutionary agent-based model to test how each form of uncertainty affects the evolution of social learning.
+Agents perform one of several behaviors, modeled as a multi-armed bandit, to acquire payoffs.
+All agents learn individually using the cognitively-realistic softmax algorithm.
+Additional use of vertical and oblique social learning was allowed to evolve and served as a constraint on intra-generational individual learning.
+We found that different types of uncertainty had varying effects.
+Temporal environmental variability suppressed social learning, whereas larger selection-set size promoted social learning, even when the environment changed frequently.
 Payoff ambiguity and lifespan had more complex effects on social learning, dependent on interactions with other uncertainty parameters.
 This study shows the importance of clearly operationalizing uncertainty for understanding its role in cultural evolution.
-% Social learning is essential to human survival. It is likely to evolve when it is more
+% Social learning is essential to human survival.
+It is likely to evolve when it is more
 % efficient than asocial, trial-and-error learning. Theoretically, social learning
@@
 
-\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \mt{OSF link to PDF when final and separated)}.
-Model and analysis code is publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF (\url{https://osf.io/t8exa/}).
+\paragraph{Supplementary material.} Model and analysis code is publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}).
+Supplemental analyses confirming model robustness to free parameters and the data used to make the figures presented here is available via OSF (\url{https://osf.io/t8exa/}).
 
@@
 \begin{center}
-  \textbf{\Large \textsf{Supplement}}
+  \textbf{\Large \textsf{The Form of Uncertainty Affects Selection for Social Learning (Supplementary Material)}}
 \end{center}
@@
 $\meansl = 1$ to $\meansl = 0$ are sharper across $L$ when $\pilow = 0.8$
-(Figure~\ref{fig:nteachersSensitivity}c, bottom row). Otherwise, the main 
+(Figure~\ref{fig:nteachersSensitivity}b, bottom row). Otherwise, the main 
 results were reproduced across all tested values $N_T=2,5,10,20$.
@@
   \centering
-   % \addtocounter{figure}{-1}
+   \addtocounter{figure}{-1}
   \caption{Number of prospective teachers sensitivity analysis for $N_T=2,20$. Recall
@@
   \centering
-  % \addtocounter{figure}{-1}
+  \addtocounter{figure}{-1}
   \caption{Sensitivity analysis of the main results for the softmax parameter $\beta = 100$ and

### 2023-02-15 ms.tex
started edits

--- 2022-10-23 ms.tex
@@
 
+\newcommand{\edit}[1]{{\textcolor{blue} {#1}}}
+
 \newtotcounter{citnum} %From the package documentation
@@
   effective lifespan. All these kinds of uncertainty make it nearly impossible to fully learn about variability. We develop an evolutionary agent-based model to
-  test how each form of uncertainty affects the evolution of social learning. Agents perform one of several behaviors, modeled as a multi-armed bandit, to
-  acquire payoffs. All agents learn individually using the cognitively-realistic softmax algorithm. Additional use of vertical and oblique social learning was
-  allowed to evolve and served as a constraint on intra-generational individual learning. We found that different types of uncertainty had varying effects. Temporal
-  environmental variability suppressed social learning, whereas larger selection-set size promoted social learning, even when the environment changed frequently.
-Payoff ambiguity and lifespan had more complex effects on social learning, dependent on interactions with other uncertainty parameters.
-This study shows the importance of clearly operationalizing uncertainty for understanding its role in cultural evolution.
+  test how each form of uncertainty affects the evolution of social learning. Agents perform one of several behaviours, modeled as a multi-armed bandit, to
+  acquire payoffs. \edit{Agents explore and learn about behavioural payoffs individually through an adaptive cognitive model that uses a softmax decision rule and
+  Rescorla-Wagner-style behavioural valuation rule}. Use of vertical and oblique social learning 
+  \edit{evolved} to serve as a scaffold \edit{for adaptive individual learning, meaning social
+  and individual learning complemented one another---they are not opposites.} 
+  We found that different types of uncertainty had varying effects. Temporal
+  environmental variability suppressed social learning, whereas larger selection-set size promoted social learning,
+  even when the environment changed frequently. Payoff ambiguity and lifespan had more complex effects on social
+  learning, dependent on interactions with other uncertainty parameters. \edit{By assuming adaptive individual-level
+  cognition, this study begins to explain how social learning can predominate despite high levels of various forms of 
+  uncertainty in the real-world.}
+
+  % the importance of clearly operationalizing uncertainty for understanding its role in cultural evolution.
 % Social learning is essential to human survival. It is likely to evolve when it is more
@@
 % uncertainty are ambiguously related, and 
-% tend to only consider a small number of behavioral
+% tend to only consider a small number of behavioural
 % choices.  Here we use evolutionary agent-based modeling to consolidate
@@
 % We model societies of agents who perform one of a number
-% of possible behaviors to acquire payoffs in a time-varying environment.
+% of possible behaviours to acquire payoffs in a time-varying environment.
 % We identified complex patterns in social learning evolution depending on contextual
@@
 Uncertainty weighs particularly heavily on human adaptation because of
-our long lifespans, cosmopolitan societies, and dispersal across highly variable environments, requiring coarse-grained and plastic behavioral adaptations \citep{levins1962}.
+our long lifespans, cosmopolitan societies, and dispersal across highly variable environments, requiring coarse-grained and plastic behavioural adaptations \citep{levins1962}.
 However, the term ``uncertainty'' is often used loosely in a way that fails to distinguish it from risk.
@@
 Because cultural evolutionary models are frequently designed to explain \emph{social} learning mechanisms, they often contrast social learning with a simplistic mechanism for individual learning.
-In particular, a common assumption is that individual learners can pay a cost to definitively learn the optimal behavior for a particular environment with certainty.
+In particular, a common assumption is that individual learners can pay a cost to definitively learn the optimal behaviour for a particular environment with certainty.
 This assumption implies that social learning, by observing an individual learner, is a good bet if the environment has not changed.
@@
 uncertainty that are common in cultural evolution models and the related empirical
-literature:  (1) temporal environmental variability; (2) selection-set size (the number of possible behaviors); (3) payoff ambiguity
-(the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of
+literature:  (1) temporal environmental variability; (2) selection-set size (the number of possible behaviours); (3) payoff ambiguity
+(the difference in the expected rewards for different behaviours); and (4) the effective lifespan of agents (the number of
 opportunities for individual learning), see next section for more details. In our model, social learners learn from the previous
@@
 or technological paradigm shifts), strategies that were previously adaptive may no longer be optimal.
-The difficulty in predicting either when such shocks will occur or which behaviors will be adaptive in the resulting environments leads to uncertainty.
+The difficulty in predicting either when such shocks will occur or which behaviours will be adaptive in the resulting environments leads to uncertainty.
 
@@
 social learning. Such fluctuations have been proposed as an important selective
-pressure for learned as opposed to genetically fixed behaviors when genetic adaptation cannot keep pace with environmental change~\citep{Richerson2000}.
+pressure for learned as opposed to genetically fixed behaviours when genetic adaptation cannot keep pace with environmental change~\citep{Richerson2000}.
 On the other hand, environments that change \emph{too} quickly will select against social learning so that individuals avoid learning outdated---and therefore maladaptive---information~\citep{Feldman1996,
@@
 several ways~\citep{aoki2014evolution}. Most commonly, it is modeled
-as an independent probability that the environment changes its state (and its corresponding optimal behavior) before each new generation~\citep{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}, but
+as an independent probability that the environment changes its state (and its corresponding optimal behaviour) before each new generation~\citep{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}, but
 % The probabilities of environmental change are usually fixed per generation
@@
 The consequences of environmental change can range from mild to catastrophic.
-In the latter case, a change of environment results in the total elimination of any adaptive behavior, which must be learned \emph{de novo} for the new environment~\citep{Rogers1988}.
+In the latter case, a change of environment results in the total elimination of any adaptive behaviour, which must be learned \emph{de novo} for the new environment~\citep{Rogers1988}.
 Such catastrophic environmental changes present
@@
 from previous generations. Other models of environmental change introduce less
-uncertainty as they fluctuate between two or more environmental states with corresponding adaptive behaviors. This means that previously maladaptive
-behaviors become adaptive when the environment changes~\citep{perreault2012bayesian}.
-The chosen mechanism for modelling temporal change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behavior, and instead considers only behaviors that can be learned.
+uncertainty as they fluctuate between two or more environmental states with corresponding adaptive behaviours. This means that previously maladaptive
+behaviours become adaptive when the environment changes~\citep{perreault2012bayesian}.
+The chosen mechanism for modelling temporal change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behaviour, and instead considers only behaviours that can be learned.
 
@@
 In many studies of social learning, the selection set is often limited to just two options.  For example, in empirical studies of bumble bees (\emph{Bombus
-terresteris}) \citep{Baracchi2018} and great tits (\emph{Parus major}) \citep{Aplin2017}, experimenters provided two behaviors from which the bees or birds
+terresteris}) \citep{Baracchi2018} and great tits (\emph{Parus major}) \citep{Aplin2017}, experimenters provided two behaviours from which the bees or birds
 could choose, with one yielding a higher payoff than the other. %respectively,
@@
 Similarly, many human studies have used just two or three possible
-behaviors~\citep{McElreath2005,Morgan2012, Toyokawa2019}. Behavioral study designs are
+behaviours~\citep{McElreath2005,Morgan2012, Toyokawa2019}. Behavioral study designs are
 often motivated by modeling studies with similar formulations~\citep{Rogers1988,boyd1995does,Feldman1996,
 perreault2012bayesian}.
-Larger, more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\citep{derex2013, wasielewski2014}, but these map imperfectly onto the theoretical literature that tends to use a limited set of behavioral options.
+Larger, more open sets of behavioural choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\citep{derex2013, wasielewski2014}, but these map imperfectly onto the theoretical literature that tends to use a limited set of behavioural options.
 Some models have studied systems with larger, but defined, selection sets~\citep{Rendell2010, lindstrom2016co}, while in others the number of options is subsumed under the probability that a learner gets the right  answer~\citep{Feldman1996,Enquist2007}.
 %\mt{How does this work exactly in Enquist et al 2007?}. 
-%Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviors through time~\citep{Feldman1996}. 
+%Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviours through time~\citep{Feldman1996}. 
 Rarely is the size of the selection set explored explicitly as a source of  uncertainty \citep[though see][]{Muthukrishna2016a}, even though the number of options one has is likely to increase with the difficulty of the decision task~\citep{haynes2009testing,white2009testing}.
@@
 
-\paragraph{Payoff ambiguity.} Most models of social learning necessarily differentiate between the payoffs for adopting optimal vs. non-optimal behaviors
+\paragraph{Payoff ambiguity.} Most models of social learning necessarily differentiate between the payoffs for adopting optimal vs. non-optimal behaviours
 \citep{BoydRicherson1985,Rogers1988,Enquist2007,Rendell2010,aoki2014evolution}.
 The size of the difference between these payoffs is usually taken to influence the strength of selection on learning strategies.
-%, which makes sense.
-However, the ability to discern payoff differences between behaviors is also a source of uncertainty.
-In reality, payoffs for particular behaviors are not always consistent.
-A behavior may yield a large payoff sometimes and a small
+However, the ability to discern payoff differences between behaviours is also a source of uncertainty.
+In reality, payoffs for particular behaviours are not always consistent.
+A behaviour may yield a large payoff sometimes and a small
 payoff other times \citep{McElreath2005}. This means that signals about the
-relationship between behavior and payoff are often noisy, and differentiating
-between behavioral options is in part a problem of signal detection. When the
-difference in expected payoffs between optimal and non-optimal behaviors is very
+relationship between behaviour and payoff are often noisy, and differentiating
+between behavioural options is in part a problem of signal detection. When the
+difference in expected payoffs between optimal and non-optimal behaviours is very
 large, this noise matters little, as the signal is still very clear. However, when
-the expected payoffs of different behaviors are similar relative to the size of
-their variances, ambiguity arises about which behaviors really are superior.
+the expected payoffs of different behaviours are similar relative to the size of
+their variances, ambiguity arises about which behaviours really are superior.
 Smaller differences between payoffs corresponds to larger ambiguity. Payoff
 ambiguity has been manipulated in both theoretical~\citep{perreault2012bayesian}
-and empirical~\citep{McElreath2005, Morgan2012} studies, both of which support the
+and empirical~\citep{McElreath2005,Toyokawa2019} studies, both of which support the
 claim that payoff ambiguity increases the reliance on social information.
@@
 affects both uncertainty \emph{and} the strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
+\edit{It is a major problem to understand how payoff variance and payoff distributions
+generally affect evolved behavioural strategies~\citep{Haaland2019}. For the sake
+of theoretical clarity considering the \emph{interaction} of various sources of uncertainty
+we only operationalize payoff ambiguity as the difference between expected 
+payoffs, even though empirical studies often include both forms of payoff
+uncertainty~\citep{McElreath2005,Toyokawa2019}, and a more complete
+model would include differences in mean and variance of payoffs.}
+
 %This parameter sometimes takes the form of differences in
-%expected payoffs arising from different behaviors or strategies~\citep{Enquist2007,Rendell2010} or by varying the standard deviation of payoffs~\citep{McElreath2005}.
+%expected payoffs arising from different behaviours or strategies~\citep{Enquist2007,Rendell2010} or by varying the standard deviation of payoffs~\citep{McElreath2005}.
 
 \paragraph{Effective lifespan.} The more opportunities an agent has to learn during its lifespan, the more uncertainty can be reduced, assuming a stationary environment.
-Correspondingly, a reduction in the number of opportunities to learn will increase the uncertainty about which behavioral options are available and what their associated
+Correspondingly, a reduction in the number of opportunities to learn will increase the uncertainty about which behavioural options are available and what their associated
 payoffs are. %Such uncertainty can be passed on to future generations.
@@
 % predictions to manage uncertainty \citep{jacobs2011bayesian,clark2013whatever}. 
-We refer to the number of individual learning opportunities within a generation as an individual's effective lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behavior, rather than the number of sunrises one experiences, that determines one's uncertainty about the behavioral options.
+We refer to the number of individual learning opportunities within a generation as an individual's effective lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behaviour, rather than the number of sunrises one experiences, that determines one's uncertainty about the behavioural options.
 %throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.
@@
 they were more likely to use social information when they were most uncertain about the task early on.
-In a more naturalistic context, \citet{Aplin2017} found that younger great tits more readily used social information compared to older individuals, possibly because they had accrued less information via individual learning, and possibly because younger individuals have the most to gain (because of higher reproductive value) by switching to superior behavioral options.
+In a more naturalistic context, \citet{Aplin2017} found that younger great tits more readily used social information compared to older individuals, possibly because they had accrued less information via individual learning, and possibly because younger individuals have the most to gain (because of higher reproductive value) by switching to superior behavioural options.
 Cross-cultural studies have highlighted the importance of childhood as a phase of heavy social learning in humans \citep{Reyes2016}.
@@
 While the cultural-evolution literature suggests that several forms of uncertainty have played a role in the evolution of social learning, other cognitive mechanisms have likely also evolved in response to uncertainty \citep{volz2012,johnson2013evolution,van2018uncertainty}.
-Many of these are flexible learning mechanisms that do not require imitating the behaviors of others.
-For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviors with greater observed payoff variance \citep{Wilson2014,Gershman2019}.
+Many of these are flexible learning mechanisms that do not require imitating the behaviours of others.
+For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviours with greater observed payoff variance \citep{Wilson2014,Gershman2019}.
 
@@
 aoki2005}.
-This sort of behavioral gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to cultural evolution \citep{Heyes2016,Kendal2018}.
+This sort of behavioural gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to cultural evolution \citep{Heyes2016,Kendal2018}.
 Some more complicated learning strategies that make use of both socially and individually learned information have been studied ~\citep{Enquist2007, perreault2012bayesian}, including those that integrate cognitively plausible mechanisms such as reinforcement learning \citep{lindstrom2016co}, though the latter approach remains the exception rather than the norm.
@@
 
-A population consists of $N$ individuals, each of whom must decide which of $B$ behaviors to perform at
+A population consists of $N$ individuals, each of whom must decide which of $B$ behaviours to perform at
 each time step within a generation consisting of $L$ time steps.
-The behavioral selection set is a multi-armed bandit with $B$ arms.
-That is, agents can pick one of $B$ behaviors with random-valued payoffs~\citep{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
-In each generation, exactly one behavior is more likely to pay off than all the rest and is therefore optimal.
-Agents optimize their net payoffs over their lifespan by quickly learning which behavior is optimal and performing it as often as possible within their lifespan.
+The behavioural selection set is a multi-armed bandit with $B$ arms.
+That is, agents can pick one of $B$ behaviours with random-valued payoffs~\citep{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
+In each generation, exactly one behaviour is more likely to pay off than all the rest and is therefore optimal.
+Agents optimize their net payoffs over their lifespan by quickly learning which behaviour is optimal and performing it as often as possible within their lifespan.
 At the end of each generation, agents are selected with replacement to reproduce a new generation of $N$ agents, with the probability of reproduction biased by net payoffs.
-Agents who inherit the social-learning trait learn about payoffs from the previous generation, while asocial learners begin life only knowing the number of behaviors the environment affords, but have no knowledge of behavioral payoffs.
+Agents who inherit the social-learning trait learn about payoffs from the previous generation, while asocial learners begin life only knowing the number of behaviours the environment affords, but have no knowledge of behavioural payoffs.
 
@@
 The structure of the environment is specified by several parameters that remain fixed throughout the course of a given simulation (Table~\ref{tab:uncertaintyParameters}).
-The environment affords $B$ behaviors, where $B$ is the \emph{selection-set size}.
+The environment affords $B$ behaviours, where $B$ is the \emph{selection-set size}.
 Uncertainty increases with $B$.
-Each behavior is indexed by $b$ and yields a payoff of 1 with probability $\pi_b$ and a payoff of 0 otherwise.
-As such, $\pi_b$ is equivalently the expected payoff of behavior $b$.
-At the beginning of each generation, one behavior is optimal and yields expected payoff $\pihigh$; the other $B-1$ behaviors yield a lower payoff, $\pilow$.
+Each behaviour is indexed by $b$ and yields a payoff of 1 with probability $\pi_b$ and a payoff of 0 otherwise.
+As such, $\pi_b$ is equivalently the expected payoff of behaviour $b$.
+At the beginning of each generation, one behaviour is optimal and yields expected payoff $\pihigh$; the other $B-1$ behaviours yield a lower payoff, $\pilow$.
 The \emph{payoff ambiguity} is defined by $\pihigh - \pilow$.
@@
 Uncertainty decreases with $L$.
-At the start of each generation a new optimal behavior is selected at random from the set of all possible behaviors with probability $u$ (the \emph{environmental variability}), otherwise the optimal behavior remains unchanged from the previous generation.
+At the start of each generation a new optimal behaviour is selected at random from the set of all possible behaviours with probability $u$ (the \emph{environmental variability}), otherwise the optimal behaviour remains unchanged from the previous generation.
 Uncertainty increases with $u$.
@@
 
-        $\pihigh$ & Probability that the unique optimal behavior pays off 1 
+        $\pihigh$ & Probability that the unique optimal behaviour pays off 1 
                 & \textbf{0.9} \\
 
-        $\pilow$ & Payoff ambiguity: probability one of $B - 1$ non-optimal behaviors pays off 1
+        $\pilow$ & Payoff ambiguity: probability one of $B - 1$ non-optimal behaviours pays off 1
                  & 0.1, 0.45, 0.8 \\
 
-        $B$       & Selection-set size: number of behavior options
+        $B$       & Selection-set size: number of behaviour options
                   & 2, 4, 10 \\
@@
 
-        $u$    & Environmental variability: Probability optimal behavior changes between generations
+        $u$    & Environmental variability: Probability optimal behaviour changes between generations
                & 0.0, 0.1, \ldots, 1.0 \\
@@
 
-%Agents are endowed with dynamic attributes to intelligently select behaviors and calculate average payoffs for each behavior. 
+%Agents are endowed with dynamic attributes to intelligently select behaviours and calculate average payoffs for each behaviour. 
 All agents learn individually over their lifespan, and those with
@@
 % Every agent engages in individual learning over its lifespan, regardless of learning strategy. 
-Social learners begin life with behavioral preferences based on information learned from an agent chosen from the previous generation.
-Asocial learners begin life with no behavioral preferences.
+Social learners begin life with behavioural preferences based on information learned from an agent chosen from the previous generation.
+Asocial learners begin life with no behavioural preferences.
 Agent-level parameters are described in Table~\ref{tab:modelParameters}.
@@
 their lifespan.  Learning is guided by softmax search. Softmax search
-guides agents to exploit more frequently the most profitable behaviors when the
+guides agents to exploit more frequently the most profitable behaviours when the
 agent is more certain it is the optimal one and to explore more frequently when the
 agent is unsure. To do softmax searching, agents track average payoffs acquired
-from each behavior they have performed, which requires knowing the number of times they have performed each behavior.
-The probability that the agent will perform a behavior is a function of the agent's beliefs about a behavior's average payoff in that time step and a fixed parameter that influences the amount of exploratory behavior (more details below).
-The softmax function used here is a biologically plausible generalization of behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative behavior they have observed, but also to sometimes explore alternatives~\citep{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
+from each behaviour they have performed, which requires knowing the number of times they have performed each behaviour.
+The probability that the agent will perform a behaviour is a function of the agent's beliefs about a behaviour's average payoff in that time step and a fixed parameter that influences the amount of exploratory behaviour (more details below).
+The softmax function used here is a biologically plausible generalization of behaviour selection under uncertainty that enables agents to often greedily exploit the most lucrative behaviour they have observed, but also to sometimes explore alternatives~\citep{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
 
@@
 choosing the payoff maximizer among these (more details below).
-The social learner then inherits information about the likely payoffs of each behavior from that one teacher, whereas asocial learners do not acquire this information.
-In this way, the social learner can potentially reduce the amount of exploration needed to both execute and learn about the optimal behavior.
+The social learner then inherits information about the likely payoffs of each behaviour from that one teacher, whereas asocial learners do not acquire this information.
+In this way, the social learner can potentially reduce the amount of exploration needed to both execute and learn about the optimal behaviour.
 
@@
 % assumed~\cite[e.g.]{Rogers1988}. Instead, agents explore alternatives and
-% greedily perform different behaviors that pay off better. 
+% greedily perform different behaviours that pay off better. 
 % This mechanism is critical for explaining the patterns we observe in the 
 % Analysis, where social learning evolves when $u > 0.5$.
-% In this case, the optimal behavior will switch between generations more often than
+% In this case, the optimal behaviour will switch between generations more often than
 % not. Without individual learning, social learning would not evolve when $u > 0.5$.
@@
 
-        $\bar\pi_{ib}$ & Mean payoffs acquired by agent $i$ from behavior $b$
+        $\bar\pi_{ib}$ & Mean payoffs acquired by agent $i$ from behaviour $b$
                        & $B$-vector of zeros \\
 
-        $c_{ib}$ & Count of how many times agent $i$ performed behavior $b$ 
+        $c_{ib}$ & Count of how many times agent $i$ performed behaviour $b$ 
               & $B$-vector of zeros \\
@@
 to the chosen parameter settings. % for the simulation.
-Then, within each generation, agents select and perform behaviors, updating their estimated payoffs, and thus their probabilities of choosing each behavior, along the way.
+Then, within each generation, agents select and perform behaviours, updating their estimated payoffs, and thus their probabilities of choosing each behaviour, along the way.
 Between generations, agents reproduce, teach social learners of the next generation, and die off. 
@@
 The model is initialized with $N$ agents. Each agent $i$ tracks 
-observed mean payoffs for each behavior, $b$, which is denoted $\ledger$. Each
-agent $i$ also counts how many times they have tried each behavior $b$, 
+observed mean payoffs for each behaviour, $b$, which is denoted $\ledger$. Each
+agent $i$ also counts how many times they have tried each behaviour $b$, 
 denoted $c_{ib}$. At model initialization, $\ledger = 0.0$ and $c_{ib} = 0$ for
 all $i$ and $b$ (Figure~\ref{fig:schematic}A).
-One of the behaviors is chosen at random to yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
+One of the behaviours is chosen at random to yield expected payoff $\pihigh$, with the other $B-1$ behaviours yielding
 expected payoffs $\pilow$. Agents are independently randomly initialized with $s_i
@@
 \paragraph{Within-generation dynamics}
-% To guide behavior selection, agent $i$ counts how many times it
-% performed each behavior $b$, denoted $c_{ib}$. Agents use this count to 
-% update the mean payoff they have obtained from behavior $b$, denoted $\ledger$.
+% To guide behaviour selection, agent $i$ counts how many times it
+% performed each behaviour $b$, denoted $c_{ib}$. Agents use this count to 
+% update the mean payoff they have obtained from behaviour $b$, denoted $\ledger$.
 % $\ledger$ is initialized to 0 for all $b$ at model start for
@@
 % through performance-biased oblique learning; $c_ib$ is set to 1 for all social
-% learners $i$ and behaviors $b$ (Figure~\ref{fig:schematic}C). Agent $i$'s
-% accumulated payoffs from performing several behaviors over their lifetime of $L$
+% learners $i$ and behaviours $b$ (Figure~\ref{fig:schematic}C). Agent $i$'s
+% accumulated payoffs from performing several behaviours over their lifetime of $L$
 % time steps is denoted $\pi_{i}$. If an agent $i$ is a social learner, then we write
@@
 
-Within each generation, all $N$ agents perform $L$ behaviors sequentially and
+Within each generation, all $N$ agents perform $L$ behaviours sequentially and
 independently (Figure~\ref{fig:softmaxSensitivity}b).
-% Each agent $i$ selects one behavior on each step of its lifespan using softmax applied
-% to the vector of mean payoffs the agent has observed for each behavior
+% Each agent $i$ selects one behaviour on each step of its lifespan using softmax applied
+% to the vector of mean payoffs the agent has observed for each behaviour
 % ($\ledger$), integrating previous knowledge. 
 % We denote the average payoffs obtained by agent $i$
-% for behavior $b$ as $\ledger$. We denote the number of times $i$ performed $b$
+% for behaviour $b$ as $\ledger$. We denote the number of times $i$ performed $b$
 % as $c_{ib}$ (``$c$'' stands for count). 
-At each time step, agent $i$ performs behavior $b$ with softmax-weighted probability
+At each time step, agent $i$ performs behaviour $b$ with softmax-weighted probability
 \begin{equation}
-  \Pr(\text{Agent $i$ performs behavior $b$}) = 
+  \Pr(\text{Agent $i$ performs behaviour $b$}) = 
     \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}}.
@@
 $\beta$ adjusts how frequently agents perform 
-behaviors with high expected payoffs (larger $\beta$) versus how frequently
-agents explore alternative behaviors (smaller $\beta$). %~\citep{McElreath2005}. 
+behaviours with high expected payoffs (larger $\beta$) versus how frequently
+agents explore alternative behaviours (smaller $\beta$). %~\citep{McElreath2005}. 
 We used a default value of $\beta = 10$, but also varied this value in our
@@
 
-Agent $i$ using behavior $b$ receives a payoff of 1 with probability $\pihigh$
-if $b$ is the optimal behavior, or with probability $\pilow$ otherwise. 
+Agent $i$ using behaviour $b$ receives a payoff of 1 with probability $\pihigh$
+if $b$ is the optimal behaviour, or with probability $\pilow$ otherwise. 
 %Agents probabilistically recieve a payoff of 0 or 1 depending on whether the bandit paid off.
-Behavior payoffs are drawn from a Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from behavior $b$.
+Behavior payoffs are drawn from a Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from behaviour $b$.
 For concreteness we denote this probabilistic payoff $\bandit$.
-After performing behavior $b$, agent $i$ updates its
-corresponding \emph{behavior count} for $b$ by 1, $c_{ib}' \leftarrow c_{ib} + 1$.
-Then the observed average payoffs known by agent $i$ for behavior $b$ are updated with
+After performing behaviour $b$, agent $i$ updates its
+corresponding \emph{behaviour count} for $b$ by 1, $c_{ib}' \leftarrow c_{ib} + 1$.
+Then the observed average payoffs known by agent $i$ for behaviour $b$ are updated with
 exponentially-weighted averaging
@@
 \noindent
-where $\bandit$ is the actual payoff received by agent $i$ for behavior $b$ on a
+where $\bandit$ is the actual payoff received by agent $i$ for behaviour $b$ on a
 given %(implicit) 
@@
 (Figure~\ref{fig:nteachersSensitivity}). Social learner $i$ adopts their chosen 
-teacher $j$'s observed average payoffs for each behavior, $b$, i.e., 
+teacher $j$'s observed average payoffs for each behaviour, $b$, i.e., 
 $\ledger \leftarrow \bar\pi_{jb}$; 
-and agent $i$'s count of behavioral observations, $c_{ib}$, is set to 1 if teacher $j$ had at least one observation of behavior $b$, and $c_{ib}$ is set to 0 otherwise.
+and agent $i$'s count of behavioural observations, $c_{ib}$, is set to 1 if teacher $j$ had at least one observation of behaviour $b$, and $c_{ib}$ is set to 0 otherwise.
 This way, expected payoffs remain within $[0, 1]$, but social learners are flexible to adjust to environmental change.
 Setting $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single observation with the associated uncertainty.
-Asocial learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ for each behavior, $b$.
+Asocial learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ for each behaviour, $b$.
 (Figure~\ref{fig:schematic}C).
@@
 
-After reproduction and die-off, the optimal behavior changes with probability
-$u$. The new behavior is chosen from all other behaviors, with the 
-current optimal behavior excluded from selection.
+After reproduction and die-off, the optimal behaviour changes with probability
+$u$. The new behaviour is chosen from all other behaviours, with the 
+current optimal behaviour excluded from selection.
 
@@
   payoff observations all initialized to zero (A). Then agents begin selecting
-and performing behaviors and accumulating payoffs, which goes on for $L$
+and performing behaviours and accumulating payoffs, which goes on for $L$
 timesteps (B). After $L$ time steps, agents are selected to reproduce,
@@
 
-The number of behavioral options, i.e., larger $B$, favors the evolution of social learning. Increasing the selection-set size
+The number of behavioural options, i.e., larger $B$, favors the evolution of social learning. Increasing the selection-set size
 expands the range of $u$ over which social learning is favored for two reasons. First, when the environment remains constant between
-generations, the value of social learning increases with more behavioral options, because it effectively increases the number of
+generations, the value of social learning increases with more behavioural options, because it effectively increases the number of
 observations that one can learn from by comparing the payoffs of several models. In other words, relying \emph{only} on one's
 individual trial-and-error learning is less likely to yield useful information when the search space is large.
-Second, when the environment changes, bias against the new optimal is weaker with more behavioral options.
-For example, with only two behavioral choices ($B = 2$), a common assumption in many models, social learning is particularly detrimental when the environment changes since more of the population will have arrived at the optimal behavior in the previous generation and socially learning from them will be biased against the correct choice.
+Second, when the environment changes, bias against the new optimal is weaker with more behavioural options.
+For example, with only two behavioural choices ($B = 2$), a common assumption in many models, social learning is particularly detrimental when the environment changes since more of the population will have arrived at the optimal behaviour in the previous generation and socially learning from them will be biased against the correct choice.
 These two mechanisms make it particularly profitable to engage in social learning when the selection-set size is larger---for large values of $B$ social learning can even be favored when the environment is more likely to change than not (i.e., $u>0.5$).
@@
 When effective lifespans are long and there are many opportunities to gather information by individual learning, the value of social transmission is diminished.
-Given enough opportunities, all agents will learn the optimal behavior eventually.
+Given enough opportunities, all agents will learn the optimal behaviour eventually.
 Thus, under most conditions, longer effective lifespans lead to a narrower range of the parameters $u$ and $B$ under which social learning was favored.
@@
 The exceptions to this general pattern occur for high levels of payoff ambiguity, $\pilow$ combined with low rates of environmental change, $u$ (left parts of plots on bottom row of Figure~\ref{fig:mainResults}).
-This reversal is partially explained by higher levels of drift when there is little difference in the payoffs between behaviors, and by the fact that the quality of social information is poorer when payoffs are ambiguous and lifespans are short (more on these effects of payoff ambiguity below).
+This reversal is partially explained by higher levels of drift when there is little difference in the payoffs between behaviours, and by the fact that the quality of social information is poorer when payoffs are ambiguous and lifespans are short (more on these effects of payoff ambiguity below).
 % \cm{is this right? I thought we should say something about the exceptions in this paragraph though we describe in more detail below, but not sure I have the right explanation}
@@
 complex effect on the evolution of social learning. Recall that we operationalized
-payoff ambiguity with $\pilow$, the expected payoff for non-optimal behaviors
-(equivalently the probability that those behaviors yielded a payoff of 1). This was
-relative to $\pihigh = 0.9$, the expected payoff for the optimal behavior. When
-payoff ambiguity was low, non-optimal behaviors rarely paid off, so that exploration
+payoff ambiguity with $\pilow$, the expected payoff for non-optimal behaviours
+(equivalently the probability that those behaviours yielded a payoff of 1). This was
+relative to $\pihigh = 0.9$, the expected payoff for the optimal behaviour. When
+payoff ambiguity was low, non-optimal behaviours rarely paid off, so that exploration
 yielded reliable information and selection on learning strategies was strong. When
 payoff ambiguity is very high ($\pilow = 0.8$), two things happen. First, agents are
-more likely to err by ascribing high value to non-optimal behaviors, since it is
+more likely to err by ascribing high value to non-optimal behaviours, since it is
 more difficult for them to discern the difference between optimal and sub optimal
-behaviors. Second, and perhaps more importantly, natural selection on strategies
-that \emph{do} reliably select the optimal behavior is relatively weak.
+behaviours. Second, and perhaps more importantly, natural selection on strategies
+that \emph{do} reliably select the optimal behaviour is relatively weak.
 This means that the effect of drift is relatively stronger, weakening selection in favor of social learning under low values of $u$ and weakening selection against social learning under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row).
@@
   environmental variability, $u$, increases ($x$-axes) in most uncertainty contexts. 
-  Other uncertainty values payoff ambiguity, $\pilow$, (rows), number of behavioral options, $B$, (columns), and effective lifespan, $L$, (keys) shift and flatten the slope from all-social-learner populations to all-asocial-learner
+  Other uncertainty values payoff ambiguity, $\pilow$, (rows), number of behavioural options, $B$, (columns), and effective lifespan, $L$, (keys) shift and flatten the slope from all-social-learner populations to all-asocial-learner
   populations.}
@@
 randomness into natural selection. In this model, such randomness is introduced at
-various stages including when agents receive payoffs for a given behavior, when they
+various stages including when agents receive payoffs for a given behaviour, when they
 are reproducing, and when they are being selected as teachers. Drift is maximal, and
@@
 When $L=1$, selection pressure may be relatively weak since agents have no opportunity for individual learning, and social learning is the only learning channel.
-When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning allows agents many opportunities to find the optimal behavior, which means social learning provides a relatively weaker constraint on net payoffs over agent lifespans.
+When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning allows agents many opportunities to find the optimal behaviour, which means social learning provides a relatively weaker constraint on net payoffs over agent lifespans.
 This also results in weaker selection pressure since there is relatively little difference between social and asocial constraints when $L$ is large
@@
 Finally, we confirmed our results were reasonably robust to a wide range of softmax greediness parameters, $\beta \in \{1, 100\}$, to supplement the main results that used $\beta = 10$.
-However, when $\beta = 1$, an insufficient reliance on the best-paying behavior (i.e., low greed) caused agents to often ignore helpful social information  (Figure~\ref{fig:softmaxSensitivity}a).
+However, when $\beta = 1$, an insufficient reliance on the best-paying behaviour (i.e., low greed) caused agents to often ignore helpful social information  (Figure~\ref{fig:softmaxSensitivity}a).
 On the other hand, too much greed ($\beta=100$) made social learners inflexible so they could not recover as well when when they learned outdated social information.
-This cost to greediness was most pronounced for longer-lived agents who may spend several time steps performing a sub-optimal behavior (Figure~\ref{fig:softmaxSensitivity}b).
+This cost to greediness was most pronounced for longer-lived agents who may spend several time steps performing a sub-optimal behaviour (Figure~\ref{fig:softmaxSensitivity}b).
 
@@
 %Our model reproduced classic predictions that social learning can yield higher payoffs than individual learning when uncertainty is sufficiently limited. 
-We found that larger sets of behavioral options, shorter effective lifespans, and increased payoff ambiguity could all favor the
+We found that larger sets of behavioural options, shorter effective lifespans, and increased payoff ambiguity could all favor the
 evolution of social learning. However, these effects were not always straightforward. Increased payoff ambiguity and decreased
@@
 rapidly changing~\citep[e.g.,][]{IPCC2022}.
-On the other hand, humans have increasingly more behavioral options (selection-set size) with high levels of uncertainty about which behaviors are most beneficial (payoff ambiguity), and in this case our model mostly predicts a greater prevalence of social learning.
+On the other hand, humans have increasingly more behavioural options (selection-set size) with high levels of uncertainty about which behaviours are most beneficial (payoff ambiguity), and in this case our model mostly predicts a greater prevalence of social learning.
 In general, detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly-changing world.
-%Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\citep{Moya2020,Jones2021}, especially in the most vulnerable communities~\citep{McNamara2020}, and to capitalize on new behavioral opportunities such as transitioning to clean energy use and production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+%Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\citep{Moya2020,Jones2021}, especially in the most vulnerable communities~\citep{McNamara2020}, and to capitalize on new behavioural opportunities such as transitioning to clean energy use and production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
 However, to better identify potential pathways to effective adaptation it may be necessary to adjust some of our modeling assumptions to the cumulative nature of cultural evolution and group structure of interpersonal exchange, both of which affect the sustainability of novel adaptations~\citep{Derex2020,Centola2018,Smaldino2021a}.
@@
 other mechanisms, like conformity, may lead to more drift overall.
-We also assumed that the number of behaviors and their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g., via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution~\citep{Smolla2019,Derex2020}.
+We also assumed that the number of behaviours and their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioural opportunities as time progresses, e.g., via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution~\citep{Smolla2019,Derex2020}.
 Group structure and processes such as homophily and other group-level biases could inhibit the evolution of social learning since successful out-group teachers could be cut off from in-group learners~\citep{Golub2012}.
-We assumed agents choose behaviors via softmax
+We assumed agents choose behaviours via softmax
 search, which is more cognitively sophisticated than most social-learning models, but in line with real human learning
@@
 By carefully identifying and operationalizing different forms of uncertainty common in social-learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution.
-By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the ability to adjust behavior to uncertainty and new information, we found that social learning could evolve even if it provides outdated information.
+By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the ability to adjust behaviour to uncertainty and new information, we found that social learning could evolve even if it provides outdated information.
 %Social learning is a critical component of problem solving among social creatures.
@@
 % (Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row). This highlights the
-% importance of diversity for behavioral optimization, even if it is transient.
+% importance of diversity for behavioural optimization, even if it is transient.
 
@@
 prospective teachers which social learner children compare
-($N_T$), and the softmax behavior selection greediness parameter ($\beta$).
+($N_T$), and the softmax behaviour selection greediness parameter ($\beta$).
 The results deviate only in minor ways from the main results primarily because of greater drift
@@
 prospective teachers (lower $N_T$); and (3) lower quality social information when $\beta$
-was small (teacher agents would have explored non-optimal behaviors more
+was small (teacher agents would have explored non-optimal behaviours more
 frequently, so their observed payoffs would have less probability weight in
@@
 
-We tested two additional settings of the softmax behavior selection greediness parameter,
+We tested two additional settings of the softmax behaviour selection greediness parameter,
 $\beta=1,100$, which reproduced qualitative patterns in the evolution of social learning
@@
 Formally, softmax greediness changes the 
-probability mass allocated to selecting behaviors according to observed payoffs within that agent's
+probability mass allocated to selecting behaviours according to observed payoffs within that agent's
 life history or learned from a teacher of the previous generation. 
 Greater $\beta$ increases the probability that the optimal
-observed behavior is chosen over all the rest, while smaller $\beta$ leads agents to explore alternative behaviors more frequently. If $\beta$ is too small, agents will fail to
-fully exploit their knowledge about which behavior is optimal because they too frequently
+observed behaviour is chosen over all the rest, while smaller $\beta$ leads agents to explore alternative behaviours more frequently. If $\beta$ is too small, agents will fail to
+fully exploit their knowledge about which behaviour is optimal because they too frequently
 explore less profitable alternatives.  If $\beta$ is too great the agents may prematurely
-settle on a sub-optimal behavior because that is what they learned from a teacher, 
-or because that behavior happened to pay off first. In a fuller evolutionary
+settle on a sub-optimal behaviour because that is what they learned from a teacher, 
+or because that behaviour happened to pay off first. In a fuller evolutionary
 exploration of model parameters one might allow $\beta$ to co-evolve, through
@@
 individual learning with this setting. This increased drift is especially pronounced 
-when $\pilow=0.8$ since sub-optimal behaviors often pay off and $\beta=1$ is
+when $\pilow=0.8$ since sub-optimal behaviours often pay off and $\beta=1$ is
 not greedy enough to efficiently detect and exploit the optimal 
-behavior (Figure~\ref{fig:softmaxSensitivity}a, bottom row).
+behaviour (Figure~\ref{fig:softmaxSensitivity}a, bottom row).
 Similarly, when $\beta = 1$, social learning is suppressed at much smaller values
 of $u$ for longer lifespans, $L$, due to extended exploration of non-optimal
-behaviors under this setting (Figure~\ref{fig:softmaxSensitivity}a, columns 
+behaviours under this setting (Figure~\ref{fig:softmaxSensitivity}a, columns 
 for $B$ and inset for $L$).
@@
 $\beta=10$ (Figure~\ref{fig:softmaxSensitivity}b). However, 
-in some cases, especially when $\pilow=0.1$, social learning is suppressed compared to the main text results ($\beta=10$), because social learners may often greedily perform an outdated socially-learned optimal behavior over several time steps before possibly identifying the true optimal behavior (Figure~\ref{fig:softmaxSensitivity}b, top row).
+in some cases, especially when $\pilow=0.1$, social learning is suppressed compared to the main text results ($\beta=10$), because social learners may often greedily perform an outdated socially-learned optimal behaviour over several time steps before possibly identifying the true optimal behaviour (Figure~\ref{fig:softmaxSensitivity}b, top row).
 

### 2023-02-18 ms.tex
many revisions/updates according to reviewer comments

@@
 \usepackage[margin=1.00in]{geometry}
-\usepackage[modulo]{lineno}
+% \usepackage[modulo]{lineno}
+\usepackage{lineno}
 \linenumbers
@@
 \begin{abstract} 
-  Social learning is a critical adaptation for dealing with the variable world.
-However, variability takes different forms.
-Uncertainty is a severe form of variability where the space of possible decisions or probabilities of associated outcomes are unknown.
+Social learning is a critical adaptation for dealing with the variable world. However, variability
+takes different forms. Uncertainty is a severe form of variability where the space of possible
+decisions or probabilities of associated outcomes are unknown.
 %"probabilities of decisions" didn't make sense to me so I rephrased, but hopefully still accurate.
-  We identified four distinct and theoretically-important sources of uncertainty: temporal environmental variability, payoff ambiguity, selection-set size, and
-  effective lifespan. All these kinds of uncertainty make it nearly impossible to fully learn about variability. We develop an evolutionary agent-based model to
-  test how each form of uncertainty affects the evolution of social learning. Agents perform one of several behaviours, modeled as a multi-armed bandit, to
-  acquire payoffs. \edit{Agents explore and learn about behavioural payoffs individually through an adaptive cognitive model that uses a softmax decision rule and
-  Rescorla-Wagner-style behavioural valuation rule}. Use of vertical and oblique social learning 
-  \edit{evolved} to serve as a scaffold \edit{for adaptive individual learning, meaning social
-  and individual learning complemented one another---they are not opposites.} 
-  We found that different types of uncertainty had varying effects. Temporal
-  environmental variability suppressed social learning, whereas larger selection-set size promoted social learning,
-  even when the environment changed frequently. Payoff ambiguity and lifespan had more complex effects on social
-  learning, dependent on interactions with other uncertainty parameters. \edit{By assuming adaptive individual-level
-  cognition, this study begins to explain how social learning can predominate despite high levels of various forms of 
-  uncertainty in the real-world.}
+We identified four distinct and theoretically-important sources of uncertainty: temporal
+environmental variability, payoff ambiguity, selection-set size, and effective lifespan. All these
+kinds of uncertainty make it nearly impossible to fully learn about variability. We develop an
+evolutionary agent-based model to test how each form of uncertainty affects the evolution of social
+learning. Agents perform one of several behaviours, modeled as a multi-armed bandit, to acquire
+payoffs. \edit{Agents explore and learn about behavioural payoffs individually through an adaptive
+cognitive model that uses a softmax decision rule for behavior choice.} Use of vertical and oblique social learning \edit{evolved} to serve as a scaffold \edit{for
+adaptive individual learning, meaning social and individual learning complement one
+another---they are not opposite strategies.} We found that different types of uncertainty had varying effects.
+Temporal environmental variability suppressed social learning, whereas larger selection-set size
+promoted social learning, even when the environment changed frequently. Payoff ambiguity and lifespan
+had more complex effects on social learning, dependent on interactions with other uncertainty
+parameters. \edit{By assuming adaptive individual-level cognition, this study begins to explain how
+social learning can predominate despite high levels of various forms of uncertainty in the
+real-world.}
 
@@
 %Child agents then begin a new round of generational dynamics, followed by reproduction. 
-This process continues until the population has evolved to fixation as either all social learners or all asocial learners. This process is represented in
-Figure~\ref{fig:schematic}.
+This process continues until the population has evolved to fixation as either all social learners or
+all asocial learners. %This process is represented in Figure~\ref{fig:schematic}.
 
@@
 denoted $c_{ib}$. At model initialization, $\ledger = 0.0$ and $c_{ib} = 0$ for
-all $i$ and $b$ (Figure~\ref{fig:schematic}A).
+all $i$ and $b$.% (Figure~\ref{fig:schematic}A).
 One of the behaviours is chosen at random to yield expected payoff $\pihigh$, with the other $B-1$ behaviours yielding
@@
 learning trait. Social learners then learn from the previous generation, after which
-all agents from the previous generation die off (Figure~\ref{fig:schematic}C). More
+all agents from the previous generation die off. % (Figure~\ref{fig:schematic}C). 
+More
 specifically, this all happens as follows.  $N$ reproducers are selected with
@@
 $\ledger \leftarrow \bar\pi_{jb}$; 
-and agent $i$'s count of behavioural observations, $c_{ib}$, is set to 1 if teacher $j$ had at least one observation of behaviour $b$, and $c_{ib}$ is set to 0 otherwise.
-This way, expected payoffs remain within $[0, 1]$, but social learners are flexible to adjust to environmental change.
-Setting $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single observation with the associated uncertainty.
-Asocial learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ for each behaviour, $b$.
-(Figure~\ref{fig:schematic}C).
+and agent $i$'s count of behavioural observations, $c_{ib}$, is set to 1 if teacher $j$ had at least
+one observation of behaviour $b$, and $c_{ib}$ is set to 0 otherwise. This way, expected payoffs
+remain within $[0, 1]$, but social learners are flexible to adjust to environmental change. Setting
+$c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single
+observation with the associated uncertainty. Asocial learners ($s_i = 0$) are initialized with
+$c_{ib} = 0$ and $\ledger = 0$ for each behaviour, $b$. % (Figure~\ref{fig:schematic}C). 
 The newly initialized population then repeats the within-generation dynamics.
@@
 
-\begin{figure}
-  \caption{Agents are randomly initialized as social learners or not, with their
-  payoff observations all initialized to zero (A). Then agents begin selecting
-and performing behaviours and accumulating payoffs, which goes on for $L$
-timesteps (B). After $L$ time steps, agents are selected to reproduce,
-social learner children learn from a member of their parent's generation, and
-the previous generation dies off (C). The simulation stops if children are all
-social or asocial learners (i.e.\ the system reaches fixation).
-Otherwise it repeats another generation and evolution continues.} 
-% \cm{What does (3) denote at end of Fig 1 caption?
+% \begin{figure}
+%   \caption{Agents are randomly initialized as social learners or not, with their
+%   payoff observations all initialized to zero (A). Then agents begin selecting
+% and performing behaviours and accumulating payoffs, which goes on for $L$
+% timesteps (B). After $L$ time steps, agents are selected to reproduce,
+% social learner children learn from a member of their parent's generation, and
+% the previous generation dies off (C). The simulation stops if children are all
+% social or asocial learners (i.e.\ the system reaches fixation).
+% Otherwise it repeats another generation and evolution continues.} 
+% % \cm{What does (3) denote at end of Fig 1 caption?
 Does having only green agents in Fig1B give the impression that only social learners are learning within lifetime?
@@
 }
-  \label{fig:schematic}
-  \centering
-    \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
-\end{figure}
+%   \label{fig:schematic}
+%   \centering
+%     \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+% \end{figure}
 
@@
 
-\subsection{Evolutionary drift}
-
-The effect of drift on the evolution of social learning %evolution and evolutionary drift 
-depended on the strength of natural selection, that is, on the extent to which the
-social-learning trait provided agents with a consistent benefit. Drift infuses
-randomness into natural selection. In this model, such randomness is introduced at
-various stages including when agents receive payoffs for a given behaviour, when they
-are reproducing, and when they are being selected as teachers. Drift is maximal, and
-in fact the only evolutionary force in our model, when social and asocial learning
-are equally beneficial.
-Even under consistent but weak selection pressure, drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}.
+\subsection{Strength of selection}
+
+\edit{To begin to confirm our interpretation of , we measured strength of selection via the number of
+time steps to fixation. More steps to fixation here indicates weaker selection.} Strength of selection is the extent to which the
+social-learning trait provided agents with a consistent benefit. \edit{Selection
+  strength is minimal when social and asocial learning
+are equally beneficial.} Even under consistent but weak selection pressure, drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}.
 We therefore measured drift by the average number of generations to fixation, denoted $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
@@
 
-Figure~\ref{fig:steps} shows drift in terms of the average number of generations to fixation, $\meanG$, across all uncertainty parameters.
+Figure~\ref{fig:steps} shows the average number of generations to fixation across all uncertainty parameters.
 Drift was greatest overall when payoff ambiguity was greatest, i.e., when $\pilow = 0.8$.
@@
 
-$\meanG$ peaks at the values of $u$ where social learning goes from being favored to suppressed.
-Uncertainty due to selection-set size, $B$, and payoff ambiguity, $\pilow$, has the clearest effects on the values of $u$ for which we see greatest drift.
-As uncertainty due to $B$ and $\pilow$ increase, social learning is generally favored for a greater range of $u$.
-This pushes up the values of $u$ with greatest drift.
-Effective lifespan, $L$, has some effect on the location of peak
-drift over $u$, but $L$ has a more consistent effect on the overall amount of drift: $L=1$ tends to have the most drift, especially when payoff ambiguity is low ($\pilow < 0.8$).
-However, the effect of lifespan on drift is non-monotonic---longer lifespans can also result in greater drift compared to intermediate lifespans (e.g., in Figure~\ref{fig:steps}, top left and top right).
-When $L=1$, selection pressure may be relatively weak since agents have no opportunity for individual learning, and social learning is the only learning channel.
-When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning allows agents many opportunities to find the optimal behaviour, which means social learning provides a relatively weaker constraint on net payoffs over agent lifespans.
-This also results in weaker selection pressure since there is relatively little difference between social and asocial constraints when $L$ is large
+The average number of steps to fixation peaks at environmental variabilities 
+where social learning goes from being favored to suppressed. 
+Selection-set size, $B$, 
+and payoff ambiguity, $\pilow$, 
+had the clearest effects on which values of environmental variability maximized
+the number of steps to fixation. As selection-set size and uncertainty were increased, 
+social learning was favored for a greater range of environmental variability. 
+% This pushes up the values of $u$ with greatest drift. 
+Effective lifespan, $L$, 
+had some effect on the location of peak
+drift over environmental variability, but effective lifespan, $L$, had a more consistent effect on the
+overall selection strength: $L=1$ trials took longer to reach fixation on average, 
+especially when payoff ambiguity 
+was low ($\pilow < 0.8$). However, the effect of lifespan on time to fixation was non-monotonic---longer
+lifespans also resulted in longer times to fixation compared to intermediate lifespans (e.g., in
+Figure~\ref{fig:steps}, top left and top right). When $L=1$, selection pressure may be relatively
+weak since agents have no opportunity for individual learning, and social learning is the only
+learning channel. When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning allows agents
+many opportunities to find the optimal behaviour, which means social learning provides a relatively
+weaker constraint on net payoffs over agent lifespans.
+This would also results in weaker selection pressure since there is relatively little difference between social and asocial constraints when $L$ is large
 (Figure~\ref{fig:steps}, top two rows).
@@
   \label{fig:payoffs}
-  \centering
-    \includegraphics[width=\textwidth]{Figures/meanNetPayoffs.pdf}
+  \vspace{1em}
+  \centering 
+    {\textsf A, Low payoff $=$ 0.1, selection-set size $=$ 2} \\
+    \begin{subfigure}[]{0.4\textwidth}
+      \centering
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
+    \end{subfigure} \\
+    \centering
+    {\textsf B, Low payoff $=$ 0.45, selection-set size $=$ 4} \\
+    \begin{subfigure}[]{0.4\textwidth}
+      % {\large \textsf B}
+      \centering
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
+    \end{subfigure} \\
+    {\textsf C, Low payoff $=$ 0.45, selection-set size $=$ 10} \\
+    \begin{subfigure}[]{0.4\textwidth}
+      \centering
+      % {\large \textsf C}
+      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+    \end{subfigure}
+
+    \begin{center}
+       \includegraphics[width=.75in]{Figures/legendElements/dot.pdf}
+       { Average all-social population payoffs}  \\[.725em]
+       \includegraphics[width=.75in]{Figures/legendElements/ldash.pdf} 
+       { Average all-asocial population payoffs} \\[.725em]
+       \includegraphics[width=.75in]{Figures/legendElements/solid.pdf} 
+       { Simulated average population payoffs} \\[.725em]
+       { $\pmb{|}$  \quad $u$ value where homogenous social and asocial payoffs
+      are equal} 
+    \end{center}
 \end{figure}
@@
 %Our model reproduced classic predictions that social learning can yield higher payoffs than individual learning when uncertainty is sufficiently limited. 
-We found that larger sets of behavioural options, shorter effective lifespans, and increased payoff ambiguity could all favor the
-evolution of social learning. However, these effects were not always straightforward. Increased payoff ambiguity and decreased
-effective lifespan afforded a greater role for drift (i.e., evolutionary uncertainty in a finite-size population). Not surprisingly,
-when the consequence of one's choice does not affect payoffs much, selection either for or against social learning is substantially
-weaker.
-More interestingly, selection is also weaker when the ability to learn individually is fraught with uncertainty.
-Our model demonstrated that social learning can act as a scaffold for individual learning---they are not opposite strategies.
-We endowed agents with a biologically-plausible individual learning mechanism, softmax search.
-This enabled agents to recover from the potential cost of receiving outdated information.
-This, in turn, enabled the evolution of social learning even when social information was likely to be outdated.
+We found that larger sets of behavioural options, shorter effective lifespans,
+and increased payoff ambiguity could all favor the evolution of social learning.
+However, these effects were not always straightforward. Increased payoff
+ambiguity and decreased effective lifespan afforded a greater role for drift
+(i.e., evolutionary uncertainty in a finite-size population). Not surprisingly,
+when the consequence of one's choice does not affect payoffs much, selection
+either for or against social learning is substantially weaker. More
+interestingly, selection is also weaker when the ability to learn individually
+is fraught with uncertainty. Our model demonstrated that social learning can act
+as a scaffold for \edit{adaptive} individual learning. We endowed agents with a
+biologically-plausible individual learning mechanism, softmax search. This
+enabled agents to recover from the potential cost of receiving outdated
+information. This, in turn, enabled the evolution of social learning even when
+social information was likely to be outdated.
 
@@
 with previous findings in the literature. First, we assumed all agents engage in individual learning. This means that individual learning is effectively free, though
-potentially inaccurate. Although producing new knowledge may be costly, many other adaptive problems take the form of essentially
-cost-free individual learning. For example, it is hard not to encode association between clouds and rain, between thirst and
-drinking water, or between friendship and warm laughter. This model thus avoids producer/scrounger dynamics common in other
-models~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and asocial learners.
-Second, we only allow for intergenerational social learning and environmental change. Within generations, agents can only learn
-individually, meaning they cannot learn from their peers. This
-assumption allows us to replicate the classic finding that if the environment changes too quickly, socially-learned information will be useless.
-Alternative formalizations for the timing of social learning and environmental change would break this relationship~\citep{Turner2022}.
-
-We could have made alternative, empirically-valid, choices for a range of other structural features, the future exploration of which
+potentially inaccurate. Although producing new knowledge may be costly, many other adaptive problems take the form
+of essentially cost-free individual learning. For example, it is hard not to encode association between clouds and
+rain, between thirst and drinking water, or between friendship and warm laughter. This model thus avoids
+producer/scrounger dynamics common in other models~\citep{BoydRicherson1985,Rogers1988} and therefore does not
+produce any mixed equilibria of social and asocial learners.  Second, we only allow for intergenerational social
+learning and environmental change. Within generations, agents can only learn individually. This assumption allows us
+to replicate the classic finding that if the environment changes too quickly, socially-learned information may
+become \edit{outdated. Adding horizontal social learning between vertical/oblique learning in this model would 
+likely expand the range of environmental variability over which social learning would evolve~\citep{Turner2022},
+i.e., horizontal learning would increase what we have called the social learning extinction variability.}
+
+We could have made alternative choices for a range of other structural features, the future exploration of which
 will be important to the development of more parsimonious theories of social learning.  
-% that may not always hold in more specific situations, though they are empirically justified to be general across taxa.
 For example, we only considered success-biased learning, although people may use conformity or other context biases to socially learn~\citep{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.
@@
 range of taxa. Although social learning is broadly studied, few studies have taken a systematic approach to understanding the role
-of uncertainty in the evolution social learning. Understanding the role of uncertainty in social evolution is particularly important
+of uncertainty in the evolution \edit{of} social learning. Understanding the role of uncertainty in social evolution is particularly important
 for understanding human evolution as evidence increasingly suggests that the genus \emph{Homo} emerged in the context of substantial

### 2023-02-18 ms.tex
updates for revisions from local desktop

--- 2023-02-15 ms.tex
@@
 \usepackage{pslatex}
-% \usepackage{apacite}
 \usepackage{caption}
@@
 affects both uncertainty \emph{and} the strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
-\edit{It is a major problem to understand how payoff variance and payoff distributions
+\edit{It is an outstanding problem to understand how payoff variance and payoff distributions
 generally affect evolved behavioural strategies~\citep{Haaland2019}. For the sake
-of theoretical clarity considering the \emph{interaction} of various sources of uncertainty
+of theoretical clarity for our goal of understanding the \emph{interaction} of various sources of uncertainty
 we only operationalize payoff ambiguity as the difference between expected 

### 2023-02-20 ms.tex
updates for revision

@@
 %Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviours through time~\citep{Feldman1996}. 
-Rarely is the size of the selection set explored explicitly as a source of  uncertainty \citep[though see][]{Muthukrishna2016a}, even though the number of options one has is likely to increase with the difficulty of the decision task~\citep{haynes2009testing,white2009testing}.
+Rarely is the size of the selection set explored explicitly as a source of  uncertainty \citep[though see][]{Muthukrishna2016a}, even though the number of options one has is likely to increase the difficulty of the decision task~\citep{haynes2009testing,white2009testing}.
 %These examples share one common feature: the size of the selection set was held static \emph{within} model generations.

### 2023-02-20 ms.tex
updates

@@
 Our work identified and systematized some important forms of uncertainty and catalogued their effects on the evolution of social learning.
-Our work, then, both advances the theory of social learning and could eventually be of practical use in identifying specific mechanisms underlying adaptations to an uncertain environments.
+Our work, then, both advances the theory of social learning and could eventually be of practical use in identifying specific mechanisms underlying adaptations to uncertain environments.
 

### 2023-02-21 ms.tex
through addressing Reviewer 1

@@
 
+\usepackage{xcolor}
+
 % Colored comments 
@@
 
-\newcommand{\edit}[1]{{\textcolor{blue} {#1}}}
+\definecolor{editblue}{HTML}{1055CB}
+
+% \newcommand{\edit}[1]{{\bfseries \textcolor{editblue} {#1}}}
+\newcommand{\edit}[1]{{\bfseries \textcolor{blue} {#1}}}
 
@@
 \affil[*]{Corresponding author; email: \href{mailto:maturner@stanford.edu}{maturner@stanford.edu}}
-\usepackage{xcolor}
 
@@
 evolutionary agent-based model to test how each form of uncertainty affects the evolution of social
-learning. Agents perform one of several behaviours, modeled as a multi-armed bandit, to acquire
-payoffs. \edit{Agents explore and learn about behavioural payoffs individually through an adaptive
-cognitive model that uses a softmax decision rule for behavior choice.} Use of vertical and oblique social learning \edit{evolved} to serve as a scaffold \edit{for
+learning. Agents perform one of several behaviors, modeled as a multi-armed bandit, to acquire
+payoffs. \edit{Agents explore and learn about behavioral payoffs individually through an adaptive
+cognitive model that uses a softmax decision rule for behavior choice.} Use of
+vertical and oblique \edit{payoff-biased} social learning \edit{evolved} to serve as a scaffold \edit{for
 adaptive individual learning, meaning social and individual learning complement one
@@
 % uncertainty are ambiguously related, and 
-% tend to only consider a small number of behavioural
+% tend to only consider a small number of behavioral
 % choices.  Here we use evolutionary agent-based modeling to consolidate
@@
 % We model societies of agents who perform one of a number
-% of possible behaviours to acquire payoffs in a time-varying environment.
+% of possible behaviors to acquire payoffs in a time-varying environment.
 % We identified complex patterns in social learning evolution depending on contextual
@@
 Uncertainty weighs particularly heavily on human adaptation because of
-our long lifespans, cosmopolitan societies, and dispersal across highly variable environments, requiring coarse-grained and plastic behavioural adaptations \citep{levins1962}.
+our long lifespans, cosmopolitan societies, and dispersal across highly variable environments, requiring coarse-grained and plastic behavioral adaptations \citep{levins1962}.
 However, the term ``uncertainty'' is often used loosely in a way that fails to distinguish it from risk.
@@
 Because cultural evolutionary models are frequently designed to explain \emph{social} learning mechanisms, they often contrast social learning with a simplistic mechanism for individual learning.
-In particular, a common assumption is that individual learners can pay a cost to definitively learn the optimal behaviour for a particular environment with certainty.
+In particular, a common assumption is that individual learners can pay a cost to definitively learn the optimal behavior for a particular environment with certainty.
 This assumption implies that social learning, by observing an individual learner, is a good bet if the environment has not changed.
@@
 uncertainty that are common in cultural evolution models and the related empirical
-literature:  (1) temporal environmental variability; (2) selection-set size (the number of possible behaviours); (3) payoff ambiguity
-(the difference in the expected rewards for different behaviours); and (4) the effective lifespan of agents (the number of
+literature:  (1) temporal environmental variability; (2) selection-set size (the number of possible behaviors); (3) payoff ambiguity
+(the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of
 opportunities for individual learning), see next section for more details. In our model, social learners learn from the previous
-generation and asocial learners do not. All agents engage in individual learning within their lifespans. The model also assumes a
-cognitively-realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
+generation and asocial learners do not. All agents engage in individual learning
+within their lifespans. The model also assumes \edit{an adaptive},
+empirically-motivated learning mechanism, the softmax decision rule, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
 Our model design thereby affords us a richer and possibly more accurate assessment of trade-offs between social and asocial learning.
@@
 or technological paradigm shifts), strategies that were previously adaptive may no longer be optimal.
-The difficulty in predicting either when such shocks will occur or which behaviours will be adaptive in the resulting environments leads to uncertainty.
+The difficulty in predicting either when such shocks will occur or which behaviors will be adaptive in the resulting environments leads to uncertainty.
 
@@
 social learning. Such fluctuations have been proposed as an important selective
-pressure for learned as opposed to genetically fixed behaviours when genetic adaptation cannot keep pace with environmental change~\citep{Richerson2000}.
+pressure for learned as opposed to genetically fixed behaviors when genetic adaptation cannot keep pace with environmental change~\citep{Richerson2000}.
 On the other hand, environments that change \emph{too} quickly will select against social learning so that individuals avoid learning outdated---and therefore maladaptive---information~\citep{Feldman1996,
@@
 several ways~\citep{aoki2014evolution}. Most commonly, it is modeled
-as an independent probability that the environment changes its state (and its corresponding optimal behaviour) before each new generation~\citep{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}, but
+as an independent probability that the environment changes its state (and its corresponding optimal behavior) before each new generation~\citep{BoydRicherson1985,Rogers1988,Feldman1996,McElreath2005,Enquist2007,perreault2012bayesian,aoki2014evolution}, but
 % The probabilities of environmental change are usually fixed per generation
@@
 The consequences of environmental change can range from mild to catastrophic.
-In the latter case, a change of environment results in the total elimination of any adaptive behaviour, which must be learned \emph{de novo} for the new environment~\citep{Rogers1988}.
+In the latter case, a change of environment results in the total elimination of any adaptive behavior, which must be learned \emph{de novo} for the new environment~\citep{Rogers1988}.
 Such catastrophic environmental changes present
@@
 from previous generations. Other models of environmental change introduce less
-uncertainty as they fluctuate between two or more environmental states with corresponding adaptive behaviours. This means that previously maladaptive
-behaviours become adaptive when the environment changes~\citep{perreault2012bayesian}.
-The chosen mechanism for modelling temporal change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behaviour, and instead considers only behaviours that can be learned.
+uncertainty as they fluctuate between two or more environmental states with corresponding adaptive behaviors. This means that previously maladaptive
+behaviors become adaptive when the environment changes~\citep{perreault2012bayesian}.
+The chosen mechanism for modeling temporal change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behavior, and instead considers only behaviors that can be learned.
 
@@
 In many studies of social learning, the selection set is often limited to just two options.  For example, in empirical studies of bumble bees (\emph{Bombus
-terresteris}) \citep{Baracchi2018} and great tits (\emph{Parus major}) \citep{Aplin2017}, experimenters provided two behaviours from which the bees or birds
+terresteris}) \citep{Baracchi2018} and great tits (\emph{Parus major}) \citep{Aplin2017}, experimenters provided two behaviors from which the bees or birds
 could choose, with one yielding a higher payoff than the other. %respectively,
@@
 Similarly, many human studies have used just two or three possible
-behaviours~\citep{McElreath2005,Morgan2012, Toyokawa2019}. Behavioral study designs are
+behaviors~\citep{McElreath2005,Morgan2012, Toyokawa2019}. Behavioral study designs are
 often motivated by modeling studies with similar formulations~\citep{Rogers1988,boyd1995does,Feldman1996,
 perreault2012bayesian}.
-Larger, more open sets of behavioural choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\citep{derex2013, wasielewski2014}, but these map imperfectly onto the theoretical literature that tends to use a limited set of behavioural options.
+Larger, more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\citep{derex2013, wasielewski2014}, but these map imperfectly onto the theoretical literature that tends to use a limited set of behavioral options.
 Some models have studied systems with larger, but defined, selection sets~\citep{Rendell2010, lindstrom2016co}, while in others the number of options is subsumed under the probability that a learner gets the right  answer~\citep{Feldman1996,Enquist2007}.
 %\mt{How does this work exactly in Enquist et al 2007?}. 
-%Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviours through time~\citep{Feldman1996}. 
+%Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviors through time~\citep{Feldman1996}. 
 Rarely is the size of the selection set explored explicitly as a source of  uncertainty \citep[though see][]{Muthukrishna2016a}, even though the number of options one has is likely to increase the difficulty of the decision task~\citep{haynes2009testing,white2009testing}.
@@
 
-\paragraph{Payoff ambiguity.} Most models of social learning necessarily differentiate between the payoffs for adopting optimal vs. non-optimal behaviours
+\paragraph{Payoff ambiguity.} Most models of social learning necessarily differentiate between the payoffs for adopting optimal vs. non-optimal behaviors
 \citep{BoydRicherson1985,Rogers1988,Enquist2007,Rendell2010,aoki2014evolution}.
 The size of the difference between these payoffs is usually taken to influence the strength of selection on learning strategies.
-However, the ability to discern payoff differences between behaviours is also a source of uncertainty.
-In reality, payoffs for particular behaviours are not always consistent.
-A behaviour may yield a large payoff sometimes and a small
+However, the ability to discern payoff differences between behaviors is also a source of uncertainty.
+In reality, payoffs for particular behaviors are not always consistent.
+A behavior may yield a large payoff sometimes and a small
 payoff other times \citep{McElreath2005}. This means that signals about the
-relationship between behaviour and payoff are often noisy, and differentiating
-between behavioural options is in part a problem of signal detection. When the
-difference in expected payoffs between optimal and non-optimal behaviours is very
+relationship between behavior and payoff are often noisy, and differentiating
+between behavioral options is in part a problem of signal detection. When the
+difference in expected payoffs between optimal and non-optimal behaviors is very
 large, this noise matters little, as the signal is still very clear. However, when
-the expected payoffs of different behaviours are similar relative to the size of
-their variances, ambiguity arises about which behaviours really are superior.
+the expected payoffs of different behaviors are similar relative to the size of
+their variances, ambiguity arises about which behaviors really are superior.
 Smaller differences between payoffs corresponds to larger ambiguity. Payoff
@@
 affects both uncertainty \emph{and} the strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
-\edit{It is an outstanding problem to understand how payoff variance and payoff distributions
-generally affect evolved behavioural strategies~\citep{Haaland2019}. For the sake
-of theoretical clarity for our goal of understanding the \emph{interaction} of various sources of uncertainty
-we only operationalize payoff ambiguity as the difference between expected 
-payoffs, even though empirical studies often include both forms of payoff
-uncertainty~\citep{McElreath2005,Toyokawa2019}, and a more complete
-model would include differences in mean and variance of payoffs.}
+\edit{It is an outstanding problem to understand how payoff variance and payoff distributions generally affect evolved behavioral strategies~\citep{Haaland2019}.
+For the sake of theoretical clarity for our goal of understanding the \emph{interaction} of various sources of uncertainty we only operationalize payoff ambiguity as the difference between expected payoffs, even though empirical studies often include both forms of payoff uncertainty~\citep{McElreath2005,Toyokawa2019}, and a more complete model would include differences in mean and variance of payoffs.}
 
 %This parameter sometimes takes the form of differences in
-%expected payoffs arising from different behaviours or strategies~\citep{Enquist2007,Rendell2010} or by varying the standard deviation of payoffs~\citep{McElreath2005}.
+%expected payoffs arising from different behaviors or strategies~\citep{Enquist2007,Rendell2010} or by varying the standard deviation of payoffs~\citep{McElreath2005}.
 
 \paragraph{Effective lifespan.} The more opportunities an agent has to learn during its lifespan, the more uncertainty can be reduced, assuming a stationary environment.
-Correspondingly, a reduction in the number of opportunities to learn will increase the uncertainty about which behavioural options are available and what their associated
+Correspondingly, a reduction in the number of opportunities to learn will increase the uncertainty about which behavioral options are available and what their associated
 payoffs are. %Such uncertainty can be passed on to future generations.
@@
 % predictions to manage uncertainty \citep{jacobs2011bayesian,clark2013whatever}. 
-We refer to the number of individual learning opportunities within a generation as an individual's effective lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behaviour, rather than the number of sunrises one experiences, that determines one's uncertainty about the behavioural options.
+We refer to the number of individual learning opportunities within a generation as an individual's effective lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behavior, rather than the number of sunrises one experiences, that determines one's uncertainty about the behavioral options.
 %throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.
@@
 they were more likely to use social information when they were most uncertain about the task early on.
-In a more naturalistic context, \citet{Aplin2017} found that younger great tits more readily used social information compared to older individuals, possibly because they had accrued less information via individual learning, and possibly because younger individuals have the most to gain (because of higher reproductive value) by switching to superior behavioural options.
+In a more naturalistic context, \citet{Aplin2017} found that younger great tits more readily used social information compared to older individuals, possibly because they had accrued less information via individual learning, and possibly because younger individuals have the most to gain (because of higher reproductive value) by switching to superior behavioral options.
 Cross-cultural studies have highlighted the importance of childhood as a phase of heavy social learning in humans \citep{Reyes2016}.
@@
 While the cultural-evolution literature suggests that several forms of uncertainty have played a role in the evolution of social learning, other cognitive mechanisms have likely also evolved in response to uncertainty \citep{volz2012,johnson2013evolution,van2018uncertainty}.
-Many of these are flexible learning mechanisms that do not require imitating the behaviours of others.
-For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviours with greater observed payoff variance \citep{Wilson2014,Gershman2019}.
+Many of these are flexible learning mechanisms that do not require imitating the behaviors of others.
+For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviors with greater observed payoff variance \citep{Wilson2014,Gershman2019}.
 
 Many models of social learning simplify by using minimally-cognitive agents.
-For example, a common modelling strategy compares the payoffs of agents with different pure learning strategies (e.g., those who only engage in social learning versus those who only engage in individual learning) while revealing nothing about the cognition underlying individuals' decisions~\citep{BoydRicherson1985, Rogers1988,
+For example, a common modeling strategy compares the payoffs of agents with different pure learning strategies (e.g., those who only engage in social learning versus those who only engage in individual learning) while revealing nothing about the cognition underlying individuals' decisions~\citep{BoydRicherson1985, Rogers1988,
 aoki2005}.
-This sort of behavioural gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to cultural evolution \citep{Heyes2016,Kendal2018}.
-Some more complicated learning strategies that make use of both socially and individually learned information have been studied ~\citep{Enquist2007, perreault2012bayesian}, including those that integrate cognitively plausible mechanisms such as reinforcement learning \citep{lindstrom2016co}, though the latter approach remains the exception rather than the norm.
-In order to understand how social learning evolves as an adaptation to uncertainty, we endowed agents with a biologically-plausible cognition capable of integrating information from various sources to maximize payoffs, using \emph{softmax search}~\citep{Gershman2019}, described in more detail below.
+This sort of behavioral gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to cultural evolution \citep{Heyes2016,Kendal2018}.
+Some more complicated learning strategies that make use of both socially and
+individually learned information have been studied ~\citep{Enquist2007,
+perreault2012bayesian}, including those that integrate cognitively plausible
+mechanisms such as reinforcement learning \citep{lindstrom2016co}, though the latter
+approach remains the exception rather than the norm. In order to understand how
+social learning evolves as an adaptation to uncertainty, we endowed agents with an
+\edit{adaptive} cognition based on a softmax decision rule capable of integrating information from various sources to maximize payoffs~\citep{Gershman2019}, described in more detail below.
 
@@
 
-A population consists of $N$ individuals, each of whom must decide which of $B$ behaviours to perform at
+A population consists of $N$ individuals, each of whom must decide which of $B$ behaviors to perform at
 each time step within a generation consisting of $L$ time steps.
-The behavioural selection set is a multi-armed bandit with $B$ arms.
-That is, agents can pick one of $B$ behaviours with random-valued payoffs~\citep{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
-In each generation, exactly one behaviour is more likely to pay off than all the rest and is therefore optimal.
-Agents optimize their net payoffs over their lifespan by quickly learning which behaviour is optimal and performing it as often as possible within their lifespan.
+The behavioral selection set is a multi-armed bandit with $B$ arms.
+That is, agents can pick one of $B$ behaviors with random-valued payoffs~\citep{SuttonBartoBook,McElreath2005,Steyvers2009,Rendell2010,Schulz2019}.
+In each generation, exactly one behavior is more likely to pay off than all the rest and is therefore optimal.
+Agents optimize their net payoffs over their lifespan by quickly learning which behavior is optimal and performing it as often as possible within their lifespan.
 At the end of each generation, agents are selected with replacement to reproduce a new generation of $N$ agents, with the probability of reproduction biased by net payoffs.
-Agents who inherit the social-learning trait learn about payoffs from the previous generation, while asocial learners begin life only knowing the number of behaviours the environment affords, but have no knowledge of behavioural payoffs.
+Agents who inherit the social-learning trait learn about payoffs from the previous generation, while asocial learners begin life only knowing the number of behaviors the environment affords, but have no knowledge of behavioral payoffs.
 
@@
 The structure of the environment is specified by several parameters that remain fixed throughout the course of a given simulation (Table~\ref{tab:uncertaintyParameters}).
-The environment affords $B$ behaviours, where $B$ is the \emph{selection-set size}.
+The environment affords $B$ behaviors, where $B$ is the \emph{selection-set size}.
 Uncertainty increases with $B$.
-Each behaviour is indexed by $b$ and yields a payoff of 1 with probability $\pi_b$ and a payoff of 0 otherwise.
-As such, $\pi_b$ is equivalently the expected payoff of behaviour $b$.
-At the beginning of each generation, one behaviour is optimal and yields expected payoff $\pihigh$; the other $B-1$ behaviours yield a lower payoff, $\pilow$.
+Each behavior is indexed by $b$ and yields a payoff of 1 with probability $\pi_b$ and a payoff of 0 otherwise.
+As such, $\pi_b$ is equivalently the expected payoff of behavior $b$.
+At the beginning of each generation, one behavior is optimal and yields expected payoff $\pihigh$; the other $B-1$ behaviors yield a lower payoff, $\pilow$.
 The \emph{payoff ambiguity} is defined by $\pihigh - \pilow$.
@@
 Uncertainty decreases with $L$.
-At the start of each generation a new optimal behaviour is selected at random from the set of all possible behaviours with probability $u$ (the \emph{environmental variability}), otherwise the optimal behaviour remains unchanged from the previous generation.
+At the start of each generation a new optimal behavior is selected at random from the set of all possible behaviors with probability $u$ (the \emph{environmental variability}), otherwise the optimal behavior remains unchanged from the previous generation.
 Uncertainty increases with $u$.
@@
 
-        $\pihigh$ & Probability that the unique optimal behaviour pays off 1 
+        $\pihigh$ & Probability that the unique optimal behavior pays off 1 
                 & \textbf{0.9} \\
 
-        $\pilow$ & Payoff ambiguity: probability one of $B - 1$ non-optimal behaviours pays off 1
+        $\pilow$ & Payoff ambiguity: probability one of $B - 1$ non-optimal behaviors pays off 1
                  & 0.1, 0.45, 0.8 \\
 
-        $B$       & Selection-set size: number of behaviour options
+        $B$       & Selection-set size: number of behavior options
                   & 2, 4, 10 \\
@@
 
-        $u$    & Environmental variability: Probability optimal behaviour changes between generations
+        $u$    & Environmental variability: Probability optimal behavior changes between generations
                & 0.0, 0.1, \ldots, 1.0 \\
@@
 
-%Agents are endowed with dynamic attributes to intelligently select behaviours and calculate average payoffs for each behaviour. 
+%Agents are endowed with dynamic attributes to intelligently select behaviors and calculate average payoffs for each behavior. 
 All agents learn individually over their lifespan, and those with
@@
 % Every agent engages in individual learning over its lifespan, regardless of learning strategy. 
-Social learners begin life with behavioural preferences based on information learned from an agent chosen from the previous generation.
-Asocial learners begin life with no behavioural preferences.
+Social learners begin life with behavioral preferences based on information learned from an agent chosen from the previous generation.
+Asocial learners begin life with no behavioral preferences.
 Agent-level parameters are described in Table~\ref{tab:modelParameters}.
@@
 their lifespan.  Learning is guided by softmax search. Softmax search
-guides agents to exploit more frequently the most profitable behaviours when the
+guides agents to exploit more frequently the most profitable behaviors when the
 agent is more certain it is the optimal one and to explore more frequently when the
 agent is unsure. To do softmax searching, agents track average payoffs acquired
-from each behaviour they have performed, which requires knowing the number of times they have performed each behaviour.
-The probability that the agent will perform a behaviour is a function of the agent's beliefs about a behaviour's average payoff in that time step and a fixed parameter that influences the amount of exploratory behaviour (more details below).
-The softmax function used here is a biologically plausible generalization of behaviour selection under uncertainty that enables agents to often greedily exploit the most lucrative behaviour they have observed, but also to sometimes explore alternatives~\citep{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
+from each behavior they have performed, which requires knowing the number of times they have performed each behavior.
+The probability that the agent will perform a behavior is a function of the agent's beliefs about a behavior's average payoff in that time step and a fixed parameter that influences the amount of exploratory behavior (more details below).
+The softmax function used here is a biologically plausible generalization of behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative behavior they have observed, but also to sometimes explore alternatives~\citep{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
 
@@
 choosing the payoff maximizer among these (more details below).
-The social learner then inherits information about the likely payoffs of each behaviour from that one teacher, whereas asocial learners do not acquire this information.
-In this way, the social learner can potentially reduce the amount of exploration needed to both execute and learn about the optimal behaviour.
+The social learner then inherits information about the likely payoffs of each behavior from that one teacher, whereas asocial learners do not acquire this information.
+In this way, the social learner can potentially reduce the amount of exploration needed to both execute and learn about the optimal behavior.
 
@@
 % assumed~\cite[e.g.]{Rogers1988}. Instead, agents explore alternatives and
-% greedily perform different behaviours that pay off better. 
+% greedily perform different behaviors that pay off better. 
 % This mechanism is critical for explaining the patterns we observe in the 
 % Analysis, where social learning evolves when $u > 0.5$.
-% In this case, the optimal behaviour will switch between generations more often than
+% In this case, the optimal behavior will switch between generations more often than
 % not. Without individual learning, social learning would not evolve when $u > 0.5$.
@@
 
-        $\bar\pi_{ib}$ & Mean payoffs acquired by agent $i$ from behaviour $b$
+        $\bar\pi_{ib}$ & Mean payoffs acquired by agent $i$ from behavior $b$
                        & $B$-vector of zeros \\
 
-        $c_{ib}$ & Count of how many times agent $i$ performed behaviour $b$ 
+        $c_{ib}$ & Count of how many times agent $i$ performed behavior $b$ 
               & $B$-vector of zeros \\
@@
 to the chosen parameter settings. % for the simulation.
-Then, within each generation, agents select and perform behaviours, updating their estimated payoffs, and thus their probabilities of choosing each behaviour, along the way.
+Then, within each generation, agents select and perform behaviors, updating their estimated payoffs, and thus their probabilities of choosing each behavior, along the way.
 Between generations, agents reproduce, teach social learners of the next generation, and die off. 
@@
 The model is initialized with $N$ agents. Each agent $i$ tracks 
-observed mean payoffs for each behaviour, $b$, which is denoted $\ledger$. Each
-agent $i$ also counts how many times they have tried each behaviour $b$, 
+observed mean payoffs for each behavior, $b$, which is denoted $\ledger$. Each
+agent $i$ also counts how many times they have tried each behavior $b$, 
 denoted $c_{ib}$. At model initialization, $\ledger = 0.0$ and $c_{ib} = 0$ for
 all $i$ and $b$.% (Figure~\ref{fig:schematic}A).
-One of the behaviours is chosen at random to yield expected payoff $\pihigh$, with the other $B-1$ behaviours yielding
+One of the behaviors is chosen at random to yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
 expected payoffs $\pilow$. Agents are independently randomly initialized with $s_i
@@
 \paragraph{Within-generation dynamics}
-% To guide behaviour selection, agent $i$ counts how many times it
-% performed each behaviour $b$, denoted $c_{ib}$. Agents use this count to 
-% update the mean payoff they have obtained from behaviour $b$, denoted $\ledger$.
+% To guide behavior selection, agent $i$ counts how many times it
+% performed each behavior $b$, denoted $c_{ib}$. Agents use this count to 
+% update the mean payoff they have obtained from behavior $b$, denoted $\ledger$.
 % $\ledger$ is initialized to 0 for all $b$ at model start for
@@
 % through performance-biased oblique learning; $c_ib$ is set to 1 for all social
-% learners $i$ and behaviours $b$ (Figure~\ref{fig:schematic}C). Agent $i$'s
-% accumulated payoffs from performing several behaviours over their lifetime of $L$
+% learners $i$ and behaviors $b$ (Figure~\ref{fig:schematic}C). Agent $i$'s
+% accumulated payoffs from performing several behaviors over their lifetime of $L$
 % time steps is denoted $\pi_{i}$. If an agent $i$ is a social learner, then we write
@@
 
-Within each generation, all $N$ agents perform $L$ behaviours sequentially and
+Within each generation, all $N$ agents perform $L$ behaviors sequentially and
 independently (Figure~\ref{fig:softmaxSensitivity}b).
-% Each agent $i$ selects one behaviour on each step of its lifespan using softmax applied
-% to the vector of mean payoffs the agent has observed for each behaviour
+% Each agent $i$ selects one behavior on each step of its lifespan using softmax applied
+% to the vector of mean payoffs the agent has observed for each behavior
 % ($\ledger$), integrating previous knowledge. 
 % We denote the average payoffs obtained by agent $i$
-% for behaviour $b$ as $\ledger$. We denote the number of times $i$ performed $b$
+% for behavior $b$ as $\ledger$. We denote the number of times $i$ performed $b$
 % as $c_{ib}$ (``$c$'' stands for count). 
-At each time step, agent $i$ performs behaviour $b$ with softmax-weighted probability
+At each time step, agent $i$ performs behavior $b$ with softmax-weighted probability
 \begin{equation}
-  \Pr(\text{Agent $i$ performs behaviour $b$}) = 
+  \Pr(\text{Agent $i$ performs behavior $b$}) = 
     \frac{e^{\beta \ledger}}{\sum_{b=1}^B e^{\beta \ledger}}.
@@
 $\beta$ adjusts how frequently agents perform 
-behaviours with high expected payoffs (larger $\beta$) versus how frequently
-agents explore alternative behaviours (smaller $\beta$). %~\citep{McElreath2005}. 
+behaviors with high expected payoffs (larger $\beta$) versus how frequently
+agents explore alternative behaviors (smaller $\beta$). %~\citep{McElreath2005}. 
 We used a default value of $\beta = 10$, but also varied this value in our
@@
 
-Agent $i$ using behaviour $b$ receives a payoff of 1 with probability $\pihigh$
-if $b$ is the optimal behaviour, or with probability $\pilow$ otherwise. 
+Agent $i$ using behavior $b$ receives a payoff of 1 with probability $\pihigh$
+if $b$ is the optimal behavior, or with probability $\pilow$ otherwise. 
 %Agents probabilistically recieve a payoff of 0 or 1 depending on whether the bandit paid off.
-Behavior payoffs are drawn from a Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from behaviour $b$.
+Behavior payoffs are drawn from a Bernoulli distribution with mean $\pi_b$, so $\pi_b$ is also the mean payoff from behavior $b$.
 For concreteness we denote this probabilistic payoff $\bandit$.
-After performing behaviour $b$, agent $i$ updates its
-corresponding \emph{behaviour count} for $b$ by 1, $c_{ib}' \leftarrow c_{ib} + 1$.
-Then the observed average payoffs known by agent $i$ for behaviour $b$ are updated with
-exponentially-weighted averaging
+After performing behavior $b$, agent $i$ updates its
+corresponding \emph{behavior count} for $b$ by 1, $c_{ib}' \leftarrow c_{ib} + 1$.
+Then the observed average payoffs known by agent $i$ for behavior $b$ are updated
+via \edit{moving arithmetic averaging},
 \begin{equation}
@@
 \noindent
-where $\bandit$ is the actual payoff received by agent $i$ for behaviour $b$ on a
+where $\bandit$ is the actual payoff received by agent $i$ for behavior $b$ on a
 given %(implicit) 
-time step.
+time step. \edit{This form allows the running mean payoffs to be calculated for each
+behavior, weighting each observation equally, without knowing in advance how many
+times a behavior will be performed. While more or less sophisticated averaging may
+better represent specific species' abilities in different contexts, this form
+provides a basic observational learning mechanism that may be further specified as
+appropriate for different cases.}
 
@@
 (Figure~\ref{fig:nteachersSensitivity}). Social learner $i$ adopts their chosen 
-teacher $j$'s observed average payoffs for each behaviour, $b$, i.e., 
+teacher $j$'s observed average payoffs for each behavior, $b$, i.e., 
 $\ledger \leftarrow \bar\pi_{jb}$; 
-and agent $i$'s count of behavioural observations, $c_{ib}$, is set to 1 if teacher $j$ had at least
-one observation of behaviour $b$, and $c_{ib}$ is set to 0 otherwise. This way, expected payoffs
+and agent $i$'s count of behavioral observations, $c_{ib}$, is set to 1 if teacher $j$ had at least
+one observation of behavior $b$, and $c_{ib}$ is set to 0 otherwise. This way, expected payoffs
 remain within $[0, 1]$, but social learners are flexible to adjust to environmental change. Setting
 $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single
-observation with the associated uncertainty. Asocial learners ($s_i = 0$) are initialized with
-$c_{ib} = 0$ and $\ledger = 0$ for each behaviour, $b$. % (Figure~\ref{fig:schematic}C). 
+observation with the associated uncertainty. \edit{If students have more confidence
+in the teacher's information, or there are biological or cultural factors that more
+strongly weight teacher information, it may be more justifiable to set the learner's $c_{ib}$ to its teacher's $c_{jb}$}. Asocial learners ($s_i = 0$) are initialized with
+$c_{ib} = 0$ and $\ledger = 0$ for each behavior, $b$. % (Figure~\ref{fig:schematic}C). 
 The newly initialized population then repeats the within-generation dynamics.
 
-After reproduction and die-off, the optimal behaviour changes with probability
-$u$. The new behaviour is chosen from all other behaviours, with the 
-current optimal behaviour excluded from selection.
+After reproduction and die-off, the optimal behavior changes with probability
+$u$. The new behavior is chosen from all other behaviors, with the 
+current optimal behavior excluded from selection.
 
@@
 %   payoff observations all initialized to zero (A). Then agents begin selecting
-% and performing behaviours and accumulating payoffs, which goes on for $L$
+% and performing behaviors and accumulating payoffs, which goes on for $L$
 % timesteps (B). After $L$ time steps, agents are selected to reproduce,
@@
 
-The number of behavioural options, i.e., larger $B$, favors the evolution of social learning. Increasing the selection-set size
+The number of behavioral options, i.e., larger $B$, favors the evolution of social learning. Increasing the selection-set size
 expands the range of $u$ over which social learning is favored for two reasons. First, when the environment remains constant between
-generations, the value of social learning increases with more behavioural options, because it effectively increases the number of
+generations, the value of social learning increases with more behavioral options, because it effectively increases the number of
 observations that one can learn from by comparing the payoffs of several models. In other words, relying \emph{only} on one's
 individual trial-and-error learning is less likely to yield useful information when the search space is large.
-Second, when the environment changes, bias against the new optimal is weaker with more behavioural options.
-For example, with only two behavioural choices ($B = 2$), a common assumption in many models, social learning is particularly detrimental when the environment changes since more of the population will have arrived at the optimal behaviour in the previous generation and socially learning from them will be biased against the correct choice.
+Second, when the environment changes, bias against the new optimal is weaker with more behavioral options.
+For example, with only two behavioral choices ($B = 2$), a common assumption in many models, social learning is particularly detrimental when the environment changes since more of the population will have arrived at the optimal behavior in the previous generation and socially learning from them will be biased against the correct choice.
 These two mechanisms make it particularly profitable to engage in social learning when the selection-set size is larger---for large values of $B$ social learning can even be favored when the environment is more likely to change than not (i.e., $u>0.5$).
 
-A shorter effective lifespan, $L$, also favors the evolution of social learning in most cases.
-When effective lifespans are long and there are many opportunities to gather information by individual learning, the value of social transmission is diminished.
-Given enough opportunities, all agents will learn the optimal behaviour eventually.
-Thus, under most conditions, longer effective lifespans lead to a narrower range of the parameters $u$ and $B$ under which social learning was favored.
-It is noteworthy that in many cases, a large increase in the selection regime for social learning is observed when $L=1$, and by definition no individual learning can occur.
-The exceptions to this general pattern occur for high levels of payoff ambiguity, $\pilow$ combined with low rates of environmental change, $u$ (left parts of plots on bottom row of Figure~\ref{fig:mainResults}).
-This reversal is partially explained by higher levels of drift when there is little difference in the payoffs between behaviours, and by the fact that the quality of social information is poorer when payoffs are ambiguous and lifespans are short (more on these effects of payoff ambiguity below).
+A shorter effective lifespan, $L$, also favors the evolution of social learning in
+most cases. When effective lifespans are long and there are many opportunities to
+gather information by individual learning, the value of social transmission is
+diminished. Given enough opportunities, all agents will learn the optimal behavior
+eventually. Thus, under most conditions, longer effective lifespans lead to a
+narrower range of the parameters $u$ and $B$ under which social learning was
+favored. It is noteworthy that in many cases, a large increase in the selection
+regime for social learning is observed when $L=1$, and by definition no individual
+learning can occur. The exceptions to this general pattern occur for high levels of
+payoff ambiguity, $\pilow$ combined with low rates of environmental change, $u$
+(left parts of plots on bottom row of Figure~\ref{fig:mainResults}). This reversal
+is partially explained by \edit{weaker selection} when there is little difference in the payoffs between behaviors, and by the fact that the quality of social information is poorer when payoffs are ambiguous and lifespans are short (more on these effects of payoff ambiguity below).
 % \cm{is this right? I thought we should say something about the exceptions in this paragraph though we describe in more detail below, but not sure I have the right explanation}
@@
 complex effect on the evolution of social learning. Recall that we operationalized
-payoff ambiguity with $\pilow$, the expected payoff for non-optimal behaviours
-(equivalently the probability that those behaviours yielded a payoff of 1). This was
-relative to $\pihigh = 0.9$, the expected payoff for the optimal behaviour. When
-payoff ambiguity was low, non-optimal behaviours rarely paid off, so that exploration
+payoff ambiguity with $\pilow$, the expected payoff for non-optimal behaviors
+(equivalently the probability that those behaviors yielded a payoff of 1). This was
+relative to $\pihigh = 0.9$, the expected payoff for the optimal behavior. When
+payoff ambiguity was low, non-optimal behaviors rarely paid off, so that exploration
 yielded reliable information and selection on learning strategies was strong. When
 payoff ambiguity is very high ($\pilow = 0.8$), two things happen. First, agents are
-more likely to err by ascribing high value to non-optimal behaviours, since it is
+more likely to err by ascribing high value to non-optimal behaviors, since it is
 more difficult for them to discern the difference between optimal and sub optimal
-behaviours. Second, and perhaps more importantly, natural selection on strategies
-that \emph{do} reliably select the optimal behaviour is relatively weak.
-This means that the effect of drift is relatively stronger, weakening selection in favor of social learning under low values of $u$ and weakening selection against social learning under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row).
-This effect was especially strong under other types of uncertainty, i.e., larger selection-set sizes and shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
-
-The effect of drift when the benefit of social learning is ambiguous is powerful and complex. We explain how the frequency of social learning evolves in such circumstances in the following section.
+behaviors. Second, and perhaps more importantly, natural selection on strategies
+that \emph{do} reliably select the optimal behavior is relatively weak. This means
+\edit{selection} is weaker \emph{in favor} of social learning under low values of $u$ and
+\edit{weaker} \emph{against} social learning under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row). 
+This effect was especially \edit{pronounced} under other types of uncertainty, i.e., larger selection-set sizes and shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
+
+The effect of \edit{selection strength} when the benefit of social learning is ambiguous is powerful and complex.
+We explain how the frequency of social learning evolves in such circumstances in the following section.
 %selection on social learning responds to these effects in more detail in the following section. 
@@
   environmental variability, $u$, increases ($x$-axes) in most uncertainty contexts. 
-  Other uncertainty values payoff ambiguity, $\pilow$, (rows), number of behavioural options, $B$, (columns), and effective lifespan, $L$, (keys) shift and flatten the slope from all-social-learner populations to all-asocial-learner
+  Other uncertainty values payoff ambiguity, $\pilow$, (rows), number of behavioral options, $B$, (columns), and effective lifespan, $L$, (keys) shift and flatten the slope from all-social-learner populations to all-asocial-learner
   populations.}
@@
 
-\edit{To begin to confirm our interpretation of , we measured strength of selection via the number of
-time steps to fixation. More steps to fixation here indicates weaker selection.} Strength of selection is the extent to which the
+\edit{To begin to confirm our interpretation of our analysis above, we measured
+  strength of selection via the ensemble average of the number of
+time steps to fixation over all simulation trials for a given parameter setting. More steps to fixation here indicates weaker selection.} Strength of selection is the extent to which the
 social-learning trait provided agents with a consistent benefit. \edit{Selection
   strength is minimal when social and asocial learning
-are equally beneficial.} Even under consistent but weak selection pressure, drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}.
-We therefore measured drift by the average number of generations to fixation, denoted $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
+are equally beneficial.} 
+% Even under consistent but weak selection pressure, drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}. 
+We denote the ensemble average over simultaion trials of the number of generations to fixation, denoted $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
 %Indeed, social learning evolution and drift are reflected in the relative benefit of social learning to asocial learning.
@@
 Effective lifespan, $L$, 
-had some effect on the location of peak
-drift over environmental variability, but effective lifespan, $L$, had a more consistent effect on the
+had some effect on the location of peak time to fixation over environmental variability, 
+but effective lifespan, $L$, had a more consistent effect on the
 overall selection strength: $L=1$ trials took longer to reach fixation on average, 
@@
 learning channel. When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning allows agents
-many opportunities to find the optimal behaviour, which means social learning provides a relatively
+many opportunities to find the optimal behavior, which means social learning provides a relatively
 weaker constraint on net payoffs over agent lifespans.
@@
 We performed sensitivity analyses to ensure that our main analysis was reasonably
-robust to a range of auxiliary parameters.
-These sensitivity analyses are presented in full in the supplemental material.
-First, we confirmed that our results were robust to various population sizes $N$, though smaller-$N$ simulations had more drift, as expected, due to stronger effects of finite population size (Figure~\ref{fig:populationSensitivity}).
-%, but  still generally support our main conclusions.
-Next, we verified model robustness to the number of prospective teachers, $N_T \in \{2, 20\}$, to supplement the main results that used $N_T = 5$.
-The number of prospective teachers did not change the results (Figure~\ref{fig:nteachersSensitivity}), except to increase drift when $N_T = 2$, since the benefit of social learning may be more difficult to detect with fewer prospective teachers (Figure~\ref{fig:nteachersSensitivity}a).
+robust to a range of auxiliary parameters. These sensitivity analyses are presented
+in full in the supplemental material. First, we confirmed that our results were
+robust to various population sizes $N$, though smaller-$N$ simulations demonstrated
+weaker selection strength, as expected, due to stronger effects of finite population size (Figure~\ref{fig:populationSensitivity}). %, but  still generally support our main conclusions. 
+Next, we verified model robustness to the number of prospective teachers, $N_T \in
+\{2, 20\}$, to supplement the main results that used $N_T = 5$. The number of
+prospective teachers did not change the results
+(Figure~\ref{fig:nteachersSensitivity}), except to increase time to fixation when $N_T = 2$, since the benefit of social learning may be more difficult to detect with fewer prospective teachers (Figure~\ref{fig:nteachersSensitivity}a).
 Finally, we confirmed our results were reasonably robust to a wide range of softmax greediness parameters, $\beta \in \{1, 100\}$, to supplement the main results that used $\beta = 10$.
-However, when $\beta = 1$, an insufficient reliance on the best-paying behaviour (i.e., low greed) caused agents to often ignore helpful social information  (Figure~\ref{fig:softmaxSensitivity}a).
+However, when $\beta = 1$, an insufficient reliance on the best-paying behavior (i.e., low greed) caused agents to often ignore helpful social information  (Figure~\ref{fig:softmaxSensitivity}a).
 On the other hand, too much greed ($\beta=100$) made social learners inflexible so they could not recover as well when when they learned outdated social information.
-This cost to greediness was most pronounced for longer-lived agents who may spend several time steps performing a sub-optimal behaviour (Figure~\ref{fig:softmaxSensitivity}b).
+This cost to greediness was most pronounced for longer-lived agents who may spend several time steps performing a sub-optimal behavior (Figure~\ref{fig:softmaxSensitivity}b).
 
@@
 %Our model reproduced classic predictions that social learning can yield higher payoffs than individual learning when uncertainty is sufficiently limited. 
-We found that larger sets of behavioural options, shorter effective lifespans,
+We found that larger sets of behavioral options, shorter effective lifespans,
 and increased payoff ambiguity could all favor the evolution of social learning.
 However, these effects were not always straightforward. Increased payoff
-ambiguity and decreased effective lifespan afforded a greater role for drift
+ambiguity and decreased effective lifespan weakened selection strength
 (i.e., evolutionary uncertainty in a finite-size population). Not surprisingly,
@@
 rapidly changing~\citep[e.g.,][]{IPCC2022}.
-On the other hand, humans have increasingly more behavioural options (selection-set size) with high levels of uncertainty about which behaviours are most beneficial (payoff ambiguity), and in this case our model mostly predicts a greater prevalence of social learning.
+On the other hand, humans have increasingly more behavioral options (selection-set size) with high levels of uncertainty about which behaviors are most beneficial (payoff ambiguity), and in this case our model mostly predicts a greater prevalence of social learning.
 In general, detailed theoretical models like this are likely to be critical for understanding how humans might adapt to an uncertain and rapidly-changing world.
-%Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\citep{Moya2020,Jones2021}, especially in the most vulnerable communities~\citep{McNamara2020}, and to capitalize on new behavioural opportunities such as transitioning to clean energy use and production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
+%Such understanding could suggest plausibly beneficial interventions to mitigate existential threats~\citep{Moya2020,Jones2021}, especially in the most vulnerable communities~\citep{McNamara2020}, and to capitalize on new behavioral opportunities such as transitioning to clean energy use and production~\citep{NatureEnergyEditorialPromisesPremises2018,Brisbois2022}.
 However, to better identify potential pathways to effective adaptation it may be necessary to adjust some of our modeling assumptions to the cumulative nature of cultural evolution and group structure of interpersonal exchange, both of which affect the sustainability of novel adaptations~\citep{Derex2020,Centola2018,Smaldino2021a}.
@@
 
-Our model necessarily made simplifying assumptions. These were chosen judiciously to address the main question of how uncertainty
-affects the evolution of social learning. Two critical assumptions we made have important consequences for comparing our results
-with previous findings in the literature. First, we assumed all agents engage in individual learning. This means that individual learning is effectively free, though
-potentially inaccurate. Although producing new knowledge may be costly, many other adaptive problems take the form
-of essentially cost-free individual learning. For example, it is hard not to encode association between clouds and
-rain, between thirst and drinking water, or between friendship and warm laughter. This model thus avoids
-producer/scrounger dynamics common in other models~\citep{BoydRicherson1985,Rogers1988} and therefore does not
-produce any mixed equilibria of social and asocial learners.  Second, we only allow for intergenerational social
-learning and environmental change. Within generations, agents can only learn individually. This assumption allows us
-to replicate the classic finding that if the environment changes too quickly, socially-learned information may
-become \edit{outdated. Adding horizontal social learning between vertical/oblique learning in this model would 
-likely expand the range of environmental variability over which social learning would evolve~\citep{Turner2022},
-i.e., horizontal learning would increase what we have called the social learning extinction variability.}
+Our model necessarily made simplifying assumptions. These were chosen judiciously to
+address the main question of how uncertainty affects the evolution of social
+learning. Two critical assumptions we made have important consequences for comparing
+our results with previous findings in the literature. First, we assumed all agents
+engage in individual learning. This means that individual learning is effectively
+free, though potentially inaccurate. Although producing new knowledge may be costly,
+many other adaptive problems take the form of essentially cost-free individual
+learning. For example, it is hard not to encode association between clouds and rain,
+between thirst and drinking water, or between friendship and warm laughter.
+\edit{Our model operationalizes environmental variability as fully stochastic,
+which forces evolution towards either a population of social or asocial learners
+since environmental change is unpredictable, unlike precursor
+models that allowed for persistent frequency
+dependence~\citep{BoydRicherson1985,Rogers1988,Feldman1996}.} Second, we only allow for
+intergenerational social learning and environmental change. Within generations,
+agents can only learn individually. This assumption allows us to replicate the
+classic finding that if the environment changes too quickly, socially-learned
+information may become \edit{outdated. Adding horizontal social learning between
+vertical/oblique learning in this model would likely expand the range of
+environmental variability over which social learning would
+evolve~\citep{Turner2022}, i.e., horizontal learning would increase what we have
+called the social learning extinction variability. However, depending on the
+setting, there may be little difference between horizontal and oblique learning, for
+example if the generations are purely cultural ‘generations’ where parents, and
+others of the parent's generation, may also be peers.}
 
@@
 choice maximizes the potential benefit to social learners, which suggests that
-other mechanisms, like conformity, may lead to more drift overall.
-We also assumed that the number of behaviours and their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioural opportunities as time progresses, e.g., via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution~\citep{Smolla2019,Derex2020}.
-Group structure and processes such as homophily and other group-level biases could inhibit the evolution of social learning since successful out-group teachers could be cut off from in-group learners~\citep{Golub2012}.
-We assumed agents choose behaviours via softmax
-search, which is more cognitively sophisticated than most social-learning models, but in line with real human learning
-mechanisms~\citep{Schulz2020a,Wu2022}. Even more realistic and powerful individual learning could further support the evolution of
+other mechanisms, like conformity, may lead to \edit{weaker selection} overall. 
+\edit{Furthermore, our learning procedure could be interpreted as direct copying of
+latent psychological variables (expected payoffs for each behavior); if children
+learned instead from observations of the parent's behaviors without knowing rewards,
+which in some cases would be a more realistic assumption~\citep{Wu2022b}, this may weaken the strength of selection for social learning.} We
+also assumed that the number of behaviors and their payoffs were constant within a
+given simulation, but this fails to account for evolutionary feedback which creates
+new behavioral opportunities as time progresses\edit{~\citep{Chimento2022}}, e.g., via niche
+construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural
+evolution~\citep{Smolla2019,Derex2020}.  Group structure and processes such as
+homophily and other group-level biases could inhibit the evolution of social
+learning since successful out-group teachers could be cut off from in-group
+learners~\citep{Golub2012}.
+We assumed agents choose behaviors via a softmax \edit{decision rule, which is more cognitively sophisticated than most social-learning models and captures the adaptiveness of real human learning mechanisms, which was essential for developing our understanding of how social and individual learning can combine to multiply problem solving capacity of our agents---however true human learning is significantly more sophisticated~\citep{Schulz2020a,Wu2022}}.
+More realistic and powerful individual learning could further support the evolution of
 social learning. These considerations provide novel opportunities to expand the evolutionary theory of social learning by adding
@@
 By carefully identifying and operationalizing different forms of uncertainty common in social-learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution.
-By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the ability to adjust behaviour to uncertainty and new information, we found that social learning could evolve even if it provides outdated information.
+By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the ability to adjust behavior to uncertainty and new information, we found that social learning could evolve even if it provides outdated information.
 %Social learning is a critical component of problem solving among social creatures.
@@
 % (Figure~\ref{fig:fullMeanPrevNetPayoffs}, bottom row). This highlights the
-% importance of diversity for behavioural optimization, even if it is transient.
+% importance of diversity for behavioral optimization, even if it is transient.
 
@@
 prospective teachers which social learner children compare
-($N_T$), and the softmax behaviour selection greediness parameter ($\beta$).
-The results deviate only in minor ways from the main results primarily because of greater drift
+($N_T$), and the softmax behavior selection greediness parameter ($\beta$).
+The results deviate only in minor ways from the main results primarily because of
+\edit{weaker selection}
 due to (1) finite population size effects (smaller $N$);
@@
 prospective teachers (lower $N_T$); and (3) lower quality social information when $\beta$
-was small (teacher agents would have explored non-optimal behaviours more
+was small (teacher agents would have explored non-optimal behaviors more
 frequently, so their observed payoffs would have less probability weight in
@@
 curve of $\meansl$ over $u$ becomes more linear with increasing $B$, 
-with $\meansl$ values pulled towards maximal drift, $\meansl \to 0.5$ (Figure~\ref{fig:populationSensitivity}a,
+with $\meansl$ values pulled towards \edit{neutral selection}, $\meansl \to 0.5$ (Figure~\ref{fig:populationSensitivity}a,
 purple curves). With
@@
 as $u$ increases, more social learning across $u$ for larger $B$, and the
-same complex drift effects for combinations of $\pilow$ and $L$ that interact
+same complex \edit{selection-strength} effects for combinations of $\pilow$ and $L$ that interact
 with $u$ and $B$ settings.
@@
 We found that the number of prospective teachers had little effect on $\meansl$
-over $u$. There was slightly more drift when $N_T = 2$ compared to our 
-main text analysis, slightly less drift than our main analysis when $N_T = 20$; 
+over $u$. There was slightly \edit{weaker selection} when $N_T = 2$ compared to our 
+main text analysis, slightly \edit{stronger selection} than our main analysis when $N_T = 20$; 
 we also tested $N_T=10$, which showed no obvious difference from our main results
-with $N_T = 5$. When $N_T = 2$, increased drift is most pronounced in the
+with $N_T = 5$. When $N_T = 2$, \edit{weakened selection} is most pronounced in the
 $\meansl$ curves when $\pilow=0.8$ (Figure~\ref{fig:nteachersSensitivity}a, 
@@
 
-We tested two additional settings of the softmax behaviour selection greediness parameter,
+We tested two additional settings of the softmax behavior selection greediness parameter,
 $\beta=1,100$, which reproduced qualitative patterns in the evolution of social learning
@@
 Formally, softmax greediness changes the 
-probability mass allocated to selecting behaviours according to observed payoffs within that agent's
+probability mass allocated to selecting behaviors according to observed payoffs within that agent's
 life history or learned from a teacher of the previous generation. 
 Greater $\beta$ increases the probability that the optimal
-observed behaviour is chosen over all the rest, while smaller $\beta$ leads agents to explore alternative behaviours more frequently. If $\beta$ is too small, agents will fail to
-fully exploit their knowledge about which behaviour is optimal because they too frequently
+observed behavior is chosen over all the rest, while smaller $\beta$ leads agents to explore alternative behaviors more frequently. If $\beta$ is too small, agents will fail to
+fully exploit their knowledge about which behavior is optimal because they too frequently
 explore less profitable alternatives.  If $\beta$ is too great the agents may prematurely
-settle on a sub-optimal behaviour because that is what they learned from a teacher, 
-or because that behaviour happened to pay off first. In a fuller evolutionary
+settle on a sub-optimal behavior because that is what they learned from a teacher, 
+or because that behavior happened to pay off first. In a fuller evolutionary
 exploration of model parameters one might allow $\beta$ to co-evolve, through
@@
 First, when $\beta=1$, most general trends are preserved, but in many cases the evolution
-of social learning is suppressed or drift dominates due to 
+of social learning is suppressed, \edit{or selection strength weakens}, due to 
 the overall poor quality of information acquired through softmax search-based
-individual learning with this setting. This increased drift is especially pronounced 
-when $\pilow=0.8$ since sub-optimal behaviours often pay off and $\beta=1$ is
+individual learning with this setting. \edit{Weakened selection} is especially pronounced 
+when $\pilow=0.8$ since sub-optimal behaviors often pay off and $\beta=1$ is
 not greedy enough to efficiently detect and exploit the optimal 
-behaviour (Figure~\ref{fig:softmaxSensitivity}a, bottom row).
+behavior (Figure~\ref{fig:softmaxSensitivity}a, bottom row).
 Similarly, when $\beta = 1$, social learning is suppressed at much smaller values
 of $u$ for longer lifespans, $L$, due to extended exploration of non-optimal
-behaviours under this setting (Figure~\ref{fig:softmaxSensitivity}a, columns 
+behaviors under this setting (Figure~\ref{fig:softmaxSensitivity}a, columns 
 for $B$ and inset for $L$).
@@
 $\beta=10$ (Figure~\ref{fig:softmaxSensitivity}b). However, 
-in some cases, especially when $\pilow=0.1$, social learning is suppressed compared to the main text results ($\beta=10$), because social learners may often greedily perform an outdated socially-learned optimal behaviour over several time steps before possibly identifying the true optimal behaviour (Figure~\ref{fig:softmaxSensitivity}b, top row).
+in some cases, especially when $\pilow=0.1$, social learning is suppressed compared to the main text results ($\beta=10$), because social learners may often greedily perform an outdated socially-learned optimal behavior over several time steps before possibly identifying the true optimal behavior (Figure~\ref{fig:softmaxSensitivity}b, top row).
 

### 2023-02-21 ms.tex
reversed order in Figure 5
revisions nearly done

@@
 within their lifespans. The model also assumes \edit{an adaptive},
-empirically-motivated learning mechanism, the softmax decision rule, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
+empirically-motivated learning mechanism, the softmax \edit{decision rule}, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
 Our model design thereby affords us a richer and possibly more accurate assessment of trade-offs between social and asocial learning.
@@
 To analyze the effect of the four principal uncertainty factors, we systematically
-varied uncertainty values (Table~\ref{tab:modelParameters}) and observed how frequently social learning evolved across 1000 trial simulations for each combination of parameters tested.
+varied uncertainty values %(Table~\ref{tab:modelParameters}) 
+and observed how frequently social learning evolved across 1000 trial simulations for each combination of parameters tested.
 %We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L \in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.
-We observed three outcome measures, with $\meansl$ as the primary measure: the average value of $s_i$ over all agents and trials.
-To support our conclusions about $\meansl$, we also measured $\meanG$, the mean number of generations to fixation, and $\meanpi / L$, the average net  payoffs at the end of the simulation across agents and trials, normalized by lifespan (see Table~\ref{tab:outcomeVariables}).
-We analyze
+\edit{We observed three outcome measures: first, the social learning (SL) fixation ferquency, denoted
+$\meansl$, is how frequently
+social learning evolved to fixation across all trials for a given parameter setting. To support our
+analysis about why we observe the patterns in social learning fixation frequency that we did, we also
+measured the mean number of generations to fixation, which measures the strength of selection.} Finally we
+measured the average net payoffs at the end of the simulation across agents and trials, normalized by lifespan. We analyze
 outcomes by plotting $\meansl$ on the y-axis and environmental variability on
@@
 
-\begin{table}[h]
-    \caption{Outcome Variables. All averages are computed across trials at the end of the last generation.}
-    \label{tab:outcomeVariables}
-    \centering %\hspace{-3em}
-    \begin{tabular}{cp{4.25in}p{0.85in}} \toprule
-
-        Symbol & Description & Values \\
-
-        \midrule
-
-        $\meansl$ & Mean social-learning prevalence over agents
-                  & $ [0.0, 1.0]$ \\
-
-        $\meanpi / L$ & Mean payoffs accumulated across agents, normalized by
-        lifespan & $ [0.0, 1.0]$ \\
-
-        $\meanG$ & Mean number of generations to convergence & \{1,2,\ldots\} \\
-        \bottomrule
-    \end{tabular}
-\end{table}
+% \begin{table}[h]
+%     \caption{Outcome Variables. All averages are computed across trials at the end of the last generation.}
+%     \label{tab:outcomeVariables}
+%     \centering %\hspace{-3em}
+%     \begin{tabular}{cp{4.25in}p{0.85in}} \toprule
+
+%         Symbol & Description & Values \\
+
+%         \midrule
+
+%         $\meansl$ & Mean social-learning prevalence over agents
+%                   & $ [0.0, 1.0]$ \\
+
+%         $\meanpi / L$ & Mean payoffs accumulated across agents, normalized by
+%         lifespan & $ [0.0, 1.0]$ \\
+
+%         $\meanG$ & Mean number of generations to convergence & \{1,2,\ldots\} \\
+%         \bottomrule
+%     \end{tabular}
+% \end{table}
 
@@
 information learned from the previous generation is less likely to be of value,
-decreasing selection for social learning. Past some threshold, social learning is
-not favored at all. However, the exact nature of the relationship between social
+decreasing selection for social learning.
+\edit{Past some threshold, social learning never evolves.
+We define this threshold environmental variability as the \emph{social learning extinction variability} (Figure~\ref{fig:extinctionVariability}).}
+However, the exact nature of the relationship between social
 learning and temporal environmental variability was moderated by the other three uncertainty parameters.
@@
 observations that one can learn from by comparing the payoffs of several models. In other words, relying \emph{only} on one's
-individual trial-and-error learning is less likely to yield useful information when the search space is large.
-Second, when the environment changes, bias against the new optimal is weaker with more behavioral options.
-For example, with only two behavioral choices ($B = 2$), a common assumption in many models, social learning is particularly detrimental when the environment changes since more of the population will have arrived at the optimal behavior in the previous generation and socially learning from them will be biased against the correct choice.
-These two mechanisms make it particularly profitable to engage in social learning when the selection-set size is larger---for large values of $B$ social learning can even be favored when the environment is more likely to change than not (i.e., $u>0.5$).
+individual trial-and-error learning is less likely to yield useful information when the search space is
+large. Second, when the environment changes, bias against the new optimal is weaker with more behavioral
+options. For example, with only two behavioral choices ($B = 2$), a common assumption in many models, social
+learning is particularly detrimental when the environment changes since more of the population will have
+arrived at the optimal behavior in the previous generation and socially learning from them will be biased
+against the correct choice. These two mechanisms make it particularly profitable to engage in social
+learning when the selection-set size is larger---for large values of $B$ social learning can even be favored
+when the environment is more likely to change than not (i.e.,
+$u>0.5$\edit{---see Figure~\ref{fig:extinctionVariability}}).
 
@@
 (left parts of plots on bottom row of Figure~\ref{fig:mainResults}). This reversal
-is partially explained by \edit{weaker selection} when there is little difference in the payoffs between behaviors, and by the fact that the quality of social information is poorer when payoffs are ambiguous and lifespans are short (more on these effects of payoff ambiguity below).
+is partially explained by \edit{weaker selection} when there is little difference in the payoffs between
+behaviors, and by the fact that the quality of social information is poorer when payoffs are ambiguous and
+lifespans are short (more on these effects of payoff ambiguity below).  
+\edit{When $L$ becomes roughly equal to or greater than $B$ there is little marginal effect of increasing $L$, indicating that more individual learning experiences are unlikely to significantly affect an agent's ability to identify the optimal behavior in their lifetime.}
 % \cm{is this right? I thought we should say something about the exceptions in this paragraph though we describe in more detail below, but not sure I have the right explanation}
@@
 \begin{figure}
-  \caption{Social learning prevalence ($y$-axes) monotonically decreases as 
-  environmental variability, $u$, increases ($x$-axes) in most uncertainty contexts. 
+  \caption{Social learning fixation frequency across trials (y-axes) monotonically decreases as 
+  environmental variability, $u$, increases (x-axes) in most uncertainty contexts. 
   Other uncertainty values payoff ambiguity, $\pilow$, (rows), number of behavioral options, $B$, (columns), and effective lifespan, $L$, (keys) shift and flatten the slope from all-social-learner populations to all-asocial-learner
@@
     \includegraphics[width=\textwidth]{Figures/mainResultsPlots.pdf}
+\end{figure}
+
+\begin{figure}
+  \caption{Social learning goes extinct for larger values of environmental variability (SL extinction
+    varibility, y-axis) as the number of
+  behaviors afforded by the environment increases (x-axis).}
+  \label{fig:extinctionVariability}
+  \centering
+    \includegraphics[width=0.8\textwidth]{Figures/SL_Extinction_Variability.pdf}
 \end{figure}
@@
 However, there are several important deviations worth explaining.
-First, agents from our main simulations who evolved to be social learners sometimes outperformed agents in the homogeneous social learner populations.
+First, populations sometimes evolved to be asocial learners, even
+though all-social learner populations outperformed all-individual-learner populations when agents were
+long-lived ($L=4$ and $L=8$) and in simple environments ($B=2$; e.g., Figure~\ref{fig:payoffs}A).
+Second, we also observed the opposite dynamic: agents from our main simulations who evolved to be social learners sometimes outperformed agents in the homogeneous social learner populations.
 This is most pronounced when $L=1$, and even more
-so when $\pilow=0.45$ and $B=10$ (Figure~\ref{fig:payoffs}, middle right).
+so when $\pilow=0.45$ and $B=10$ (Figure~\ref{fig:payoffs}C).
 In fact, social learning evolved even in parts of the parameter space where the expected homogeneous social-learning payoff was lower than the expected homogeneous
-asocial-learning payoff (Figure~\ref{fig:payoffs}, e.g., middle center $L=1$).
-Second, we also observed the opposite dynamic: populations sometimes evolved to be asocial learners, even though all-social learner populations outperformed all-individual-learner populations when agents were long-lived ($L=4$ and $L=8$) and in simple environments ($B=2$; Figure~\ref{fig:payoffs}, e.g., upper left).
+asocial-learning payoff (Figure~\ref{fig:payoffs}B, e.g., $L=1$).
 
@@
 
-When lifespan was minimal ($L=1$) and environmental variability was moderate ($u\approx0.5$), the payoff time series showed a period
-of environmental stability that
-could lead the population to fixate to social learning, despite individual learning being the superior long-term strategy (Figure~\ref{fig:payoffTimeseries}a).
-On the other hand, when payoff ambiguity and selection-set size was small ($\pilow=0.1$ and $B=2$), and lifespan was long ($L \geq 4$), asocial learning fixated as a hedge against periods of protracted environmental instability, even though expected
-homogeneous social payoffs were greater than homogeneous asocial payoffs (Figure~\ref{fig:payoffTimeseries}b).
+When payoff ambiguity and selection-set size was small ($\pilow=0.1$ and $B=2$), and lifespan was long ($L \geq 4$), asocial learning fixated as a hedge against periods of protracted environmental instability, even though expected
+homogeneous social payoffs were greater than homogeneous asocial payoffs (Figure~\ref{fig:payoffTimeseries}A).
 Runs of environmental change strongly affected the geometric mean fitness of social learners who were weighing
-outdated information too heavily. %\cm{is there something worth pointing out as different between b and c? If not maybe just choose one? I'd choose b}
+outdated information too heavily.
+\edit{In other words, environmental change lowers social learners' mean payoffs, but social learner payoffs build back up when (blue dots, Figure~\ref{fig:payoffTimeseries}A).
+Even though an homogenous population of social learners would outperform individual learners in this case, unpredictable environmental stochasticity undermines the reliability of social learning.
+When lifespan was minimal ($L=1$) and environmental variability was moderate ($u\approx0.5$), the opposite, unexpected outcome could occur where social learning fixates despite the fact that an homogenous population of asocial learners would outperform an homogenous population of social learners (Figure~\ref{fig:payoffTimeseries}B).
+In this case, it takes relatively few consecutive generations with environmental stability to attract the population to all become social learners.}
 
 \begin{figure}
-  \caption{Average number of generations ($\meanG$, y-axes) to fixation. 
+  \caption{Average number of generations (y-axes) to fixation. 
     Note the y-axis scale varies between plots, indicating different overall 
@@
 \begin{figure}
+  \addtocounter{figure}{-1}
     \caption{Example time series of geometric moving average (GMA) with window of 3
@@
 \hspace{-2em}
-    \begin{subfigure}[]{0.75\textwidth}
+
       \centering
-    \caption{$u=0.5$, $\pilow=0.1$, $B=4$, $L=1$}
-      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=4-L=1.pdf}
-    \end{subfigure} \\
+      % \caption{$u=0.2$, $\pilow=0.1$, $B=2$, $L=4$}
+      {\textsf A, Environmental variability $=$ 0.2, Low payoff $=$ 0.1, selection-set size $=$ 2, effective lifespan $=$ 4} \\
+      \includegraphics[width=0.85\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=4.pdf} \\
+
+    % \caption{$u=0.5$, $\pilow=0.1$, $B=4$, $L=1$}
+      {\textsf B, Environmental variability $=$ 0.5, Low payoff $=$ 0.1, selection-set size $=$ 4, effective lifespan $=$ 1} \\
+      \includegraphics[width=0.85\textwidth]{Figures/geopayoff_series/geopayseries_u=0.5-lowpayoff=0.1-nbehaviors=4-L=1.pdf}
 
 \hspace{-2em}
-  \begin{subfigure}[]{0.75\textwidth}
-      \centering
-      \caption{$u=0.2$, $\pilow=0.1$, $B=2$, $L=4$}
-      \includegraphics[width=0.95\textwidth]{Figures/geopayoff_series/geopayseries_u=0.2-lowpayoff=0.1-nbehaviors=2-L=4.pdf}
-    \end{subfigure} %\\
 
@@
 as a scaffold for \edit{adaptive} individual learning. We endowed agents with a
-biologically-plausible individual learning mechanism, softmax search. This
+biologically-plausible individual learning mechanism \edit{based on a softmax decision rule}. This
 enabled agents to recover from the potential cost of receiving outdated
@@
 between thirst and drinking water, or between friendship and warm laughter.
-\edit{Our model operationalizes environmental variability as fully stochastic,
+\edit{If there were an exogenous cost of individual learning, this would likely increase the social learning extinction variability across uncertainty parameter settings.
+Our model operationalizes environmental variability as fully stochastic,
 which forces evolution towards either a population of social or asocial learners
@@
 for understanding human evolution as evidence increasingly suggests that the genus \emph{Homo} emerged in the context of substantial
-(nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal suggests that human groups regularly face novel environments.
+(nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal
+suggests that human groups regularly face novel environments. \edit{In our model, more numerous behavioral
+options led agents to be more cognitively flexible via the softmax decision rule, and thus better able to
+adjust their behavior if social learning provided outdated information. While Rogers'-style models of social
+learning evolution may also predict greater social learning reliance in more challenging contexts (larger
+selection-set sizes), they cannot predict that social learning should be favored for such high values of
+environmental variability as we observed here.} 
 By carefully identifying and operationalizing different forms of uncertainty common in social-learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution.
@@
 
-\paragraph{Author contributions.} JHJ, CM, and PES conceived of the project.
-MAT led model development and analysis, with contributions from CM, PES, and JHJ.
+\paragraph{Author contributions.} JHJ, CM, PES, and MAT conceived of the project. MAT developed the model
+and analyses, with contributions from CM, PES, and JHJ.
+MAT implemented and analyzed the model.
 MAT wrote and edited the initial manuscript draft, which was extensively expanded and edited by CM, PES, and JHJ.

### 2023-02-21 ms.tex

@@
 \begin{figure}
-  \caption{Social learning goes extinct for larger values of environmental variability (SL extinction
-    varibility, y-axis) as the number of
-  behaviors afforded by the environment increases (x-axis).}
+  \caption{As the number of
+  behaviors afforded by the environment increases (x-axis), 
+  social learning is supported up to increasingly large values of environmental variability (SL extinction
+    varibility, y-axis).}
   \label{fig:extinctionVariability}
@@
 (nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal
-suggests that human groups regularly face novel environments. \edit{In our model, more numerous behavioral
-options led agents to be more cognitively flexible via the softmax decision rule, and thus better able to
-adjust their behavior if social learning provided outdated information. While Rogers'-style models of social
-learning evolution may also predict greater social learning reliance in more challenging contexts (larger
-selection-set sizes), they cannot predict that social learning should be favored for such high values of
+suggests that human groups regularly face novel environments.
+\edit{In our model, more numerous behavioral options led agents to be more cognitively flexible via the softmax decision rule, and thus better able to adjust their behavior if social learning provided outdated information.
+While Rogers'-style models of social learning evolution may also predict greater social learning reliance in more challenging contexts (larger selection-set sizes), they cannot predict that social learning should be favored for such high values of
 environmental variability as we observed here.} 

### 2023-02-21 ms.tex
Updates from Overleaf

--- 2023-02-21 ms.tex
@@
 \usepackage[margin=1.00in]{geometry}
-% \usepackage[modulo]{lineno}
-\usepackage{lineno}
+\usepackage[modulo]{lineno}
 \linenumbers
@@
 \usepackage{pslatex}
+% \usepackage{apacite}
 \usepackage{caption}
@@
 
-\usepackage{xcolor}
-
 % Colored comments 
@@
 \newcommand{\ps}[1]{{\textcolor{mygreen} {({\tiny PS:} #1)}}}
-
-\definecolor{editblue}{HTML}{1055CB}
-
-% \newcommand{\edit}[1]{{\bfseries \textcolor{editblue} {#1}}}
-\newcommand{\edit}[1]{{\bfseries \textcolor{blue} {#1}}}
 
@@
 \affil[*]{Corresponding author; email: \href{mailto:maturner@stanford.edu}{maturner@stanford.edu}}
+\usepackage{xcolor}
 
@@
 \begin{abstract} 
-Social learning is a critical adaptation for dealing with the variable world. However, variability
-takes different forms. Uncertainty is a severe form of variability where the space of possible
-decisions or probabilities of associated outcomes are unknown.
+  Social learning is a critical adaptation for dealing with the variable world.
+However, variability takes different forms.
+Uncertainty is a severe form of variability where the space of possible decisions or probabilities of associated outcomes are unknown.
   %"probabilities of decisions" didn't make sense to me so I rephrased, but hopefully still accurate.
-We identified four distinct and theoretically-important sources of uncertainty: temporal
-environmental variability, payoff ambiguity, selection-set size, and effective lifespan. All these
-kinds of uncertainty make it nearly impossible to fully learn about variability. We develop an
-evolutionary agent-based model to test how each form of uncertainty affects the evolution of social
-learning. Agents perform one of several behaviors, modeled as a multi-armed bandit, to acquire
-payoffs. \edit{Agents explore and learn about behavioral payoffs individually through an adaptive
-cognitive model that uses a softmax decision rule for behavior choice.} Use of
-vertical and oblique \edit{payoff-biased} social learning \edit{evolved} to serve as a scaffold \edit{for
-adaptive individual learning, meaning social and individual learning complement one
-another---they are not opposite strategies.} We found that different types of uncertainty had varying effects.
-Temporal environmental variability suppressed social learning, whereas larger selection-set size
-promoted social learning, even when the environment changed frequently. Payoff ambiguity and lifespan
-had more complex effects on social learning, dependent on interactions with other uncertainty
-parameters. \edit{By assuming adaptive individual-level cognition, this study begins to explain how
-social learning can predominate despite high levels of various forms of uncertainty in the
-real-world.}
-
-  % the importance of clearly operationalizing uncertainty for understanding its role in cultural evolution.
+  We identified four distinct and theoretically-important sources of uncertainty: temporal environmental variability, payoff ambiguity, selection-set size, and
+  effective lifespan. All these kinds of uncertainty make it nearly impossible to fully learn about variability. We develop an evolutionary agent-based model to
+  test how each form of uncertainty affects the evolution of social learning. Agents perform one of several behaviors, modeled as a multi-armed bandit, to
+  acquire payoffs. All agents learn individually using the cognitively-realistic softmax algorithm. Additional use of vertical and oblique social learning was
+  allowed to evolve and served as a constraint on intra-generational individual learning. We found that different types of uncertainty had varying effects. Temporal
+  environmental variability suppressed social learning, whereas larger selection-set size promoted social learning, even when the environment changed frequently.
+Payoff ambiguity and lifespan had more complex effects on social learning, dependent on interactions with other uncertainty parameters.
+This study shows the importance of clearly operationalizing uncertainty for understanding its role in cultural evolution.
 % Social learning is essential to human survival. It is likely to evolve when it is more
@@
 opportunities for individual learning), see next section for more details. In our model, social learners learn from the previous
-generation and asocial learners do not. All agents engage in individual learning
-within their lifespans. The model also assumes \edit{an adaptive},
-empirically-motivated learning mechanism, the softmax decision rule, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
+generation and asocial learners do not. All agents engage in individual learning within their lifespans. The model also assumes a
+cognitively-realistic and empirically-motivated learning mechanism, the softmax algorithm, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
 Our model design thereby affords us a richer and possibly more accurate assessment of trade-offs between social and asocial learning.
@@
 behaviors become adaptive when the environment changes~\citep{perreault2012bayesian}.
-The chosen mechanism for modeling temporal change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behavior, and instead considers only behaviors that can be learned.
+The chosen mechanism for modelling temporal change has important theoretical consequences, reviewed in Aoki \& Feldman (2014).~\nocite{aoki2014evolution} Our study design ignores cases where temporal variation is low enough that genetic selection can canalize a behavior, and instead considers only behaviors that can be learned.
 
@@
 %Researchers have also compared models with a different number of environment states, corresponding to a different number of optimal behaviors through time~\citep{Feldman1996}. 
-Rarely is the size of the selection set explored explicitly as a source of  uncertainty \citep[though see][]{Muthukrishna2016a}, even though the number of options one has is likely to increase the difficulty of the decision task~\citep{haynes2009testing,white2009testing}.
+Rarely is the size of the selection set explored explicitly as a source of  uncertainty \citep[though see][]{Muthukrishna2016a}, even though the number of options one has is likely to increase with the difficulty of the decision task~\citep{haynes2009testing,white2009testing}.
 %These examples share one common feature: the size of the selection set was held static \emph{within} model generations.
@@
 The size of the difference between these payoffs is usually taken to influence the strength of selection on learning strategies.
+%, which makes sense.
 However, the ability to discern payoff differences between behaviors is also a source of uncertainty.
@@
 ambiguity has been manipulated in both theoretical~\citep{perreault2012bayesian}
-and empirical~\citep{McElreath2005,Toyokawa2019} studies, both of which support the
+and empirical~\citep{McElreath2005, Morgan2012} studies, both of which support the
 claim that payoff ambiguity increases the reliance on social information.
@@
 affects both uncertainty \emph{and} the strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
-\edit{It is an outstanding problem to understand how payoff variance and payoff distributions generally affect evolved behavioral strategies~\citep{Haaland2019}.
-For the sake of theoretical clarity for our goal of understanding the \emph{interaction} of various sources of uncertainty we only operationalize payoff ambiguity as the difference between expected payoffs, even though empirical studies often include both forms of payoff uncertainty~\citep{McElreath2005,Toyokawa2019}, and a more complete model would include differences in mean and variance of payoffs.}
-
 %This parameter sometimes takes the form of differences in
@@
 Many models of social learning simplify by using minimally-cognitive agents.
-For example, a common modeling strategy compares the payoffs of agents with different pure learning strategies (e.g., those who only engage in social learning versus those who only engage in individual learning) while revealing nothing about the cognition underlying individuals' decisions~\citep{BoydRicherson1985, Rogers1988,
+For example, a common modelling strategy compares the payoffs of agents with different pure learning strategies (e.g., those who only engage in social learning versus those who only engage in individual learning) while revealing nothing about the cognition underlying individuals' decisions~\citep{BoydRicherson1985, Rogers1988,
 aoki2005}.
 This sort of behavioral gambit is common in evolutionary modeling, but has also been criticized as `blackboxing' key cognitive processes that are important to cultural evolution \citep{Heyes2016,Kendal2018}.
-Some more complicated learning strategies that make use of both socially and
-individually learned information have been studied ~\citep{Enquist2007,
-perreault2012bayesian}, including those that integrate cognitively plausible
-mechanisms such as reinforcement learning \citep{lindstrom2016co}, though the latter
-approach remains the exception rather than the norm. In order to understand how
-social learning evolves as an adaptation to uncertainty, we endowed agents with an
-\edit{adaptive} cognition based on a softmax decision rule capable of integrating information from various sources to maximize payoffs~\citep{Gershman2019}, described in more detail below.
+Some more complicated learning strategies that make use of both socially and individually learned information have been studied ~\citep{Enquist2007, perreault2012bayesian}, including those that integrate cognitively plausible mechanisms such as reinforcement learning \citep{lindstrom2016co}, though the latter approach remains the exception rather than the norm.
+In order to understand how social learning evolves as an adaptation to uncertainty, we endowed agents with a biologically-plausible cognition capable of integrating information from various sources to maximize payoffs, using \emph{softmax search}~\citep{Gershman2019}, described in more detail below.
 
@@
 %Child agents then begin a new round of generational dynamics, followed by reproduction. 
-This process continues until the population has evolved to fixation as either all social learners or
-all asocial learners. %This process is represented in Figure~\ref{fig:schematic}.
+This process continues until the population has evolved to fixation as either all social learners or all asocial learners. This process is represented in
+Figure~\ref{fig:schematic}.
 
@@
 denoted $c_{ib}$. At model initialization, $\ledger = 0.0$ and $c_{ib} = 0$ for
-all $i$ and $b$.% (Figure~\ref{fig:schematic}A).
+all $i$ and $b$ (Figure~\ref{fig:schematic}A).
 One of the behaviors is chosen at random to yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
@@
 corresponding \emph{behavior count} for $b$ by 1, $c_{ib}' \leftarrow c_{ib} + 1$.
-Then the observed average payoffs known by agent $i$ for behavior $b$ are updated
-via \edit{moving arithmetic averaging},
+Then the observed average payoffs known by agent $i$ for behavior $b$ are updated with
+exponentially-weighted averaging
 \begin{equation}
@@
 given %(implicit) 
-time step. \edit{This form allows the running mean payoffs to be calculated for each
-behavior, weighting each observation equally, without knowing in advance how many
-times a behavior will be performed. While more or less sophisticated averaging may
-better represent specific species' abilities in different contexts, this form
-provides a basic observational learning mechanism that may be further specified as
-appropriate for different cases.}
+time step.
 
@@
 learning trait. Social learners then learn from the previous generation, after which
-all agents from the previous generation die off. % (Figure~\ref{fig:schematic}C). 
-More
+all agents from the previous generation die off (Figure~\ref{fig:schematic}C). More
 specifically, this all happens as follows.  $N$ reproducers are selected with
@@
 $\ledger \leftarrow \bar\pi_{jb}$; 
-and agent $i$'s count of behavioral observations, $c_{ib}$, is set to 1 if teacher $j$ had at least
-one observation of behavior $b$, and $c_{ib}$ is set to 0 otherwise. This way, expected payoffs
-remain within $[0, 1]$, but social learners are flexible to adjust to environmental change. Setting
-$c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single
-observation with the associated uncertainty. \edit{If students have more confidence
-in the teacher's information, or there are biological or cultural factors that more
-strongly weight teacher information, it may be more justifiable to set the learner's $c_{ib}$ to its teacher's $c_{jb}$}. Asocial learners ($s_i = 0$) are initialized with
-$c_{ib} = 0$ and $\ledger = 0$ for each behavior, $b$. % (Figure~\ref{fig:schematic}C). 
+and agent $i$'s count of behavioral observations, $c_{ib}$, is set to 1 if teacher $j$ had at least one observation of behavior $b$, and $c_{ib}$ is set to 0 otherwise.
+This way, expected payoffs remain within $[0, 1]$, but social learners are flexible to adjust to environmental change.
+Setting $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single observation with the associated uncertainty.
+Asocial learners ($s_i = 0$) are initialized with $c_{ib} = 0$ and $\ledger = 0$ for each behavior, $b$.
+(Figure~\ref{fig:schematic}C).
 The newly initialized population then repeats the within-generation dynamics.
@@
 
-% \begin{figure}
-%   \caption{Agents are randomly initialized as social learners or not, with their
-%   payoff observations all initialized to zero (A). Then agents begin selecting
-% and performing behaviors and accumulating payoffs, which goes on for $L$
-% timesteps (B). After $L$ time steps, agents are selected to reproduce,
-% social learner children learn from a member of their parent's generation, and
-% the previous generation dies off (C). The simulation stops if children are all
-% social or asocial learners (i.e.\ the system reaches fixation).
-% Otherwise it repeats another generation and evolution continues.} 
-% % \cm{What does (3) denote at end of Fig 1 caption?
+\begin{figure}
+  \caption{Agents are randomly initialized as social learners or not, with their
+  payoff observations all initialized to zero (A). Then agents begin selecting
+and performing behaviors and accumulating payoffs, which goes on for $L$
+timesteps (B). After $L$ time steps, agents are selected to reproduce,
+social learner children learn from a member of their parent's generation, and
+the previous generation dies off (C). The simulation stops if children are all
+social or asocial learners (i.e.\ the system reaches fixation).
+Otherwise it repeats another generation and evolution continues.} 
+% \cm{What does (3) denote at end of Fig 1 caption?
 Does having only green agents in Fig1B give the impression that only social learners are learning within lifetime?
@@
 }
-%   \label{fig:schematic}
-%   \centering
-%     \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
-% \end{figure}
+  \label{fig:schematic}
+  \centering
+    \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+\end{figure}
 
@@
 
-A shorter effective lifespan, $L$, also favors the evolution of social learning in
-most cases. When effective lifespans are long and there are many opportunities to
-gather information by individual learning, the value of social transmission is
-diminished. Given enough opportunities, all agents will learn the optimal behavior
-eventually. Thus, under most conditions, longer effective lifespans lead to a
-narrower range of the parameters $u$ and $B$ under which social learning was
-favored. It is noteworthy that in many cases, a large increase in the selection
-regime for social learning is observed when $L=1$, and by definition no individual
-learning can occur. The exceptions to this general pattern occur for high levels of
-payoff ambiguity, $\pilow$ combined with low rates of environmental change, $u$
-(left parts of plots on bottom row of Figure~\ref{fig:mainResults}). This reversal
-is partially explained by \edit{weaker selection} when there is little difference in the payoffs between behaviors, and by the fact that the quality of social information is poorer when payoffs are ambiguous and lifespans are short (more on these effects of payoff ambiguity below).
+A shorter effective lifespan, $L$, also favors the evolution of social learning in most cases.
+When effective lifespans are long and there are many opportunities to gather information by individual learning, the value of social transmission is diminished.
+Given enough opportunities, all agents will learn the optimal behavior eventually.
+Thus, under most conditions, longer effective lifespans lead to a narrower range of the parameters $u$ and $B$ under which social learning was favored.
+It is noteworthy that in many cases, a large increase in the selection regime for social learning is observed when $L=1$, and by definition no individual learning can occur.
+The exceptions to this general pattern occur for high levels of payoff ambiguity, $\pilow$ combined with low rates of environmental change, $u$ (left parts of plots on bottom row of Figure~\ref{fig:mainResults}).
+This reversal is partially explained by higher levels of drift when there is little difference in the payoffs between behaviors, and by the fact that the quality of social information is poorer when payoffs are ambiguous and lifespans are short (more on these effects of payoff ambiguity below).
 % \cm{is this right? I thought we should say something about the exceptions in this paragraph though we describe in more detail below, but not sure I have the right explanation}
@@
 behaviors. Second, and perhaps more importantly, natural selection on strategies
-that \emph{do} reliably select the optimal behavior is relatively weak. This means
-\edit{selection} is weaker \emph{in favor} of social learning under low values of $u$ and
-\edit{weaker} \emph{against} social learning under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row). 
-This effect was especially \edit{pronounced} under other types of uncertainty, i.e., larger selection-set sizes and shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
-
-The effect of \edit{selection strength} when the benefit of social learning is ambiguous is powerful and complex.
-We explain how the frequency of social learning evolves in such circumstances in the following section.
+that \emph{do} reliably select the optimal behavior is relatively weak.
+This means that the effect of drift is relatively stronger, weakening selection in favor of social learning under low values of $u$ and weakening selection against social learning under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row).
+This effect was especially strong under other types of uncertainty, i.e., larger selection-set sizes and shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
+
+The effect of drift when the benefit of social learning is ambiguous is powerful and complex. We explain how the frequency of social learning evolves in such circumstances in the following section.
 %selection on social learning responds to these effects in more detail in the following section. 
@@
 
-\subsection{Strength of selection}
-
-\edit{To begin to confirm our interpretation of our analysis above, we measured
-  strength of selection via the ensemble average of the number of
-time steps to fixation over all simulation trials for a given parameter setting. More steps to fixation here indicates weaker selection.} Strength of selection is the extent to which the
-social-learning trait provided agents with a consistent benefit. \edit{Selection
-  strength is minimal when social and asocial learning
-are equally beneficial.} 
-% Even under consistent but weak selection pressure, drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}. 
-We denote the ensemble average over simultaion trials of the number of generations to fixation, denoted $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
+\subsection{Evolutionary drift}
+
+The effect of drift on the evolution of social learning %evolution and evolutionary drift 
+depended on the strength of natural selection, that is, on the extent to which the
+social-learning trait provided agents with a consistent benefit. Drift infuses
+randomness into natural selection. In this model, such randomness is introduced at
+various stages including when agents receive payoffs for a given behavior, when they
+are reproducing, and when they are being selected as teachers. Drift is maximal, and
+in fact the only evolutionary force in our model, when social and asocial learning
+are equally beneficial.
+Even under consistent but weak selection pressure, drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}.
+We therefore measured drift by the average number of generations to fixation, denoted $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
 %Indeed, social learning evolution and drift are reflected in the relative benefit of social learning to asocial learning.
 
-Figure~\ref{fig:steps} shows the average number of generations to fixation across all uncertainty parameters.
+Figure~\ref{fig:steps} shows drift in terms of the average number of generations to fixation, $\meanG$, across all uncertainty parameters.
 Drift was greatest overall when payoff ambiguity was greatest, i.e., when $\pilow = 0.8$.
@@
 
-The average number of steps to fixation peaks at environmental variabilities 
-where social learning goes from being favored to suppressed. 
-Selection-set size, $B$, 
-and payoff ambiguity, $\pilow$, 
-had the clearest effects on which values of environmental variability maximized
-the number of steps to fixation. As selection-set size and uncertainty were increased, 
-social learning was favored for a greater range of environmental variability. 
-% This pushes up the values of $u$ with greatest drift. 
-Effective lifespan, $L$, 
-had some effect on the location of peak time to fixation over environmental variability, 
-but effective lifespan, $L$, had a more consistent effect on the
-overall selection strength: $L=1$ trials took longer to reach fixation on average, 
-especially when payoff ambiguity 
-was low ($\pilow < 0.8$). However, the effect of lifespan on time to fixation was non-monotonic---longer
-lifespans also resulted in longer times to fixation compared to intermediate lifespans (e.g., in
-Figure~\ref{fig:steps}, top left and top right). When $L=1$, selection pressure may be relatively
-weak since agents have no opportunity for individual learning, and social learning is the only
-learning channel. When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning allows agents
-many opportunities to find the optimal behavior, which means social learning provides a relatively
-weaker constraint on net payoffs over agent lifespans.
-This would also results in weaker selection pressure since there is relatively little difference between social and asocial constraints when $L$ is large
+$\meanG$ peaks at the values of $u$ where social learning goes from being favored to suppressed.
+Uncertainty due to selection-set size, $B$, and payoff ambiguity, $\pilow$, has the clearest effects on the values of $u$ for which we see greatest drift.
+As uncertainty due to $B$ and $\pilow$ increase, social learning is generally favored for a greater range of $u$.
+This pushes up the values of $u$ with greatest drift.
+Effective lifespan, $L$, has some effect on the location of peak
+drift over $u$, but $L$ has a more consistent effect on the overall amount of drift: $L=1$ tends to have the most drift, especially when payoff ambiguity is low ($\pilow < 0.8$).
+However, the effect of lifespan on drift is non-monotonic---longer lifespans can also result in greater drift compared to intermediate lifespans (e.g., in Figure~\ref{fig:steps}, top left and top right).
+When $L=1$, selection pressure may be relatively weak since agents have no opportunity for individual learning, and social learning is the only learning channel.
+When $L=8$ ($B=2,4$) or when $L=20$ ($B=10$), individual learning allows agents many opportunities to find the optimal behavior, which means social learning provides a relatively weaker constraint on net payoffs over agent lifespans.
+This also results in weaker selection pressure since there is relatively little difference between social and asocial constraints when $L$ is large
 (Figure~\ref{fig:steps}, top two rows).
@@
   \label{fig:payoffs}
-  \vspace{1em}
   \centering
-    {\textsf A, Low payoff $=$ 0.1, selection-set size $=$ 2} \\
-    \begin{subfigure}[]{0.4\textwidth}
-      \centering
-      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
-    \end{subfigure} \\
-    \centering
-    {\textsf B, Low payoff $=$ 0.45, selection-set size $=$ 4} \\
-    \begin{subfigure}[]{0.4\textwidth}
-      % {\large \textsf B}
-      \centering
-      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
-    \end{subfigure} \\
-    {\textsf C, Low payoff $=$ 0.45, selection-set size $=$ 10} \\
-    \begin{subfigure}[]{0.4\textwidth}
-      \centering
-      % {\large \textsf C}
-      \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
-    \end{subfigure}
-
-    \begin{center}
-       \includegraphics[width=.75in]{Figures/legendElements/dot.pdf}
-       { Average all-social population payoffs}  \\[.725em]
-       \includegraphics[width=.75in]{Figures/legendElements/ldash.pdf} 
-       { Average all-asocial population payoffs} \\[.725em]
-       \includegraphics[width=.75in]{Figures/legendElements/solid.pdf} 
-       { Simulated average population payoffs} \\[.725em]
-       { $\pmb{|}$  \quad $u$ value where homogenous social and asocial payoffs
-      are equal} 
-    \end{center}
+    \includegraphics[width=\textwidth]{Figures/meanNetPayoffs.pdf}
 \end{figure}
@@
 We performed sensitivity analyses to ensure that our main analysis was reasonably
-robust to a range of auxiliary parameters. These sensitivity analyses are presented
-in full in the supplemental material. First, we confirmed that our results were
-robust to various population sizes $N$, though smaller-$N$ simulations demonstrated
-weaker selection strength, as expected, due to stronger effects of finite population size (Figure~\ref{fig:populationSensitivity}). %, but  still generally support our main conclusions. 
-Next, we verified model robustness to the number of prospective teachers, $N_T \in
-\{2, 20\}$, to supplement the main results that used $N_T = 5$. The number of
-prospective teachers did not change the results
-(Figure~\ref{fig:nteachersSensitivity}), except to increase time to fixation when $N_T = 2$, since the benefit of social learning may be more difficult to detect with fewer prospective teachers (Figure~\ref{fig:nteachersSensitivity}a).
+robust to a range of auxiliary parameters.
+These sensitivity analyses are presented in full in the supplemental material.
+First, we confirmed that our results were robust to various population sizes $N$, though smaller-$N$ simulations had more drift, as expected, due to stronger effects of finite population size (Figure~\ref{fig:populationSensitivity}).
+%, but  still generally support our main conclusions.
+Next, we verified model robustness to the number of prospective teachers, $N_T \in \{2, 20\}$, to supplement the main results that used $N_T = 5$.
+The number of prospective teachers did not change the results (Figure~\ref{fig:nteachersSensitivity}), except to increase drift when $N_T = 2$, since the benefit of social learning may be more difficult to detect with fewer prospective teachers (Figure~\ref{fig:nteachersSensitivity}a).
 Finally, we confirmed our results were reasonably robust to a wide range of softmax greediness parameters, $\beta \in \{1, 100\}$, to supplement the main results that used $\beta = 10$.
@@
 %Our model reproduced classic predictions that social learning can yield higher payoffs than individual learning when uncertainty is sufficiently limited. 
-We found that larger sets of behavioral options, shorter effective lifespans,
-and increased payoff ambiguity could all favor the evolution of social learning.
-However, these effects were not always straightforward. Increased payoff
-ambiguity and decreased effective lifespan weakened selection strength
-(i.e., evolutionary uncertainty in a finite-size population). Not surprisingly,
-when the consequence of one's choice does not affect payoffs much, selection
-either for or against social learning is substantially weaker. More
-interestingly, selection is also weaker when the ability to learn individually
-is fraught with uncertainty. Our model demonstrated that social learning can act
-as a scaffold for \edit{adaptive} individual learning. We endowed agents with a
-biologically-plausible individual learning mechanism, softmax search. This
-enabled agents to recover from the potential cost of receiving outdated
-information. This, in turn, enabled the evolution of social learning even when
-social information was likely to be outdated.
+We found that larger sets of behavioral options, shorter effective lifespans, and increased payoff ambiguity could all favor the
+evolution of social learning. However, these effects were not always straightforward. Increased payoff ambiguity and decreased
+effective lifespan afforded a greater role for drift (i.e., evolutionary uncertainty in a finite-size population). Not surprisingly,
+when the consequence of one's choice does not affect payoffs much, selection either for or against social learning is substantially
+weaker.
+More interestingly, selection is also weaker when the ability to learn individually is fraught with uncertainty.
+Our model demonstrated that social learning can act as a scaffold for individual learning---they are not opposite strategies.
+We endowed agents with a biologically-plausible individual learning mechanism, softmax search.
+This enabled agents to recover from the potential cost of receiving outdated information.
+This, in turn, enabled the evolution of social learning even when social information was likely to be outdated.
 
@@
 
-Our model necessarily made simplifying assumptions. These were chosen judiciously to
-address the main question of how uncertainty affects the evolution of social
-learning. Two critical assumptions we made have important consequences for comparing
-our results with previous findings in the literature. First, we assumed all agents
-engage in individual learning. This means that individual learning is effectively
-free, though potentially inaccurate. Although producing new knowledge may be costly,
-many other adaptive problems take the form of essentially cost-free individual
-learning. For example, it is hard not to encode association between clouds and rain,
-between thirst and drinking water, or between friendship and warm laughter.
-\edit{Our model operationalizes environmental variability as fully stochastic,
-which forces evolution towards either a population of social or asocial learners
-since environmental change is unpredictable, unlike precursor
-models that allowed for persistent frequency
-dependence~\citep{BoydRicherson1985,Rogers1988,Feldman1996}.} Second, we only allow for
-intergenerational social learning and environmental change. Within generations,
-agents can only learn individually. This assumption allows us to replicate the
-classic finding that if the environment changes too quickly, socially-learned
-information may become \edit{outdated. Adding horizontal social learning between
-vertical/oblique learning in this model would likely expand the range of
-environmental variability over which social learning would
-evolve~\citep{Turner2022}, i.e., horizontal learning would increase what we have
-called the social learning extinction variability. However, depending on the
-setting, there may be little difference between horizontal and oblique learning, for
-example if the generations are purely cultural ‘generations’ where parents, and
-others of the parent's generation, may also be peers.}
-
-We could have made alternative choices for a range of other structural features, the future exploration of which
+Our model necessarily made simplifying assumptions. These were chosen judiciously to address the main question of how uncertainty
+affects the evolution of social learning. Two critical assumptions we made have important consequences for comparing our results
+with previous findings in the literature. First, we assumed all agents engage in individual learning. This means that individual learning is effectively free, though
+potentially inaccurate. Although producing new knowledge may be costly, many other adaptive problems take the form of essentially
+cost-free individual learning. For example, it is hard not to encode association between clouds and rain, between thirst and
+drinking water, or between friendship and warm laughter. This model thus avoids producer/scrounger dynamics common in other
+models~\citep{BoydRicherson1985,Rogers1988} and therefore does not produce any mixed equilibria of social and asocial learners.
+Second, we only allow for intergenerational social learning and environmental change. Within generations, agents can only learn
+individually, meaning they cannot learn from their peers. This
+assumption allows us to replicate the classic finding that if the environment changes too quickly, socially-learned information will be useless.
+Alternative formalizations for the timing of social learning and environmental change would break this relationship~\citep{Turner2022}.
+
+We could have made alternative, empirically-valid, choices for a range of other structural features, the future exploration of which
 will be important to the development of more parsimonious theories of social learning.
+% that may not always hold in more specific situations, though they are empirically justified to be general across taxa.
 For example, we only considered success-biased learning, although people may use conformity or other context biases to socially learn~\citep{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.
@@
 choice maximizes the potential benefit to social learners, which suggests that
-other mechanisms, like conformity, may lead to \edit{weaker selection} overall. 
-\edit{Furthermore, our learning procedure could be interpreted as direct copying of
-latent psychological variables (expected payoffs for each behavior); if children
-learned instead from observations of the parent's behaviors without knowing rewards,
-which in some cases would be a more realistic assumption~\citep{Wu2022b}, this may weaken the strength of selection for social learning.} We
-also assumed that the number of behaviors and their payoffs were constant within a
-given simulation, but this fails to account for evolutionary feedback which creates
-new behavioral opportunities as time progresses\edit{~\citep{Chimento2022}}, e.g., via niche
-construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural
-evolution~\citep{Smolla2019,Derex2020}.  Group structure and processes such as
-homophily and other group-level biases could inhibit the evolution of social
-learning since successful out-group teachers could be cut off from in-group
-learners~\citep{Golub2012}.
-We assumed agents choose behaviors via a softmax \edit{decision rule, which is more cognitively sophisticated than most social-learning models and captures the adaptiveness of real human learning mechanisms, which was essential for developing our understanding of how social and individual learning can combine to multiply problem solving capacity of our agents---however true human learning is significantly more sophisticated~\citep{Schulz2020a,Wu2022}}.
-More realistic and powerful individual learning could further support the evolution of
+other mechanisms, like conformity, may lead to more drift overall.
+We also assumed that the number of behaviors and their payoffs were constant within a given simulation, but this fails to account for evolutionary feedback which creates new behavioral opportunities as time progresses, e.g., via niche construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural evolution~\citep{Smolla2019,Derex2020}.
+Group structure and processes such as homophily and other group-level biases could inhibit the evolution of social learning since successful out-group teachers could be cut off from in-group learners~\citep{Golub2012}.
+We assumed agents choose behaviors via softmax
+search, which is more cognitively sophisticated than most social-learning models, but in line with real human learning
+mechanisms~\citep{Schulz2020a,Wu2022}. Even more realistic and powerful individual learning could further support the evolution of
 social learning. These considerations provide novel opportunities to expand the evolutionary theory of social learning by adding
@@
 range of taxa. Although social learning is broadly studied, few studies have taken a systematic approach to understanding the role
-of uncertainty in the evolution \edit{of} social learning. Understanding the role of uncertainty in social evolution is particularly important
+of uncertainty in the evolution social learning. Understanding the role of uncertainty in social evolution is particularly important
 for understanding human evolution as evidence increasingly suggests that the genus \emph{Homo} emerged in the context of substantial
@@
 Our work identified and systematized some important forms of uncertainty and catalogued their effects on the evolution of social learning.
-Our work, then, both advances the theory of social learning and could eventually be of practical use in identifying specific mechanisms underlying adaptations to uncertain environments.
+Our work, then, both advances the theory of social learning and could eventually be of practical use in identifying specific mechanisms underlying adaptations to an uncertain environments.
 
@@
 ($N_T$), and the softmax behavior selection greediness parameter ($\beta$).
-The results deviate only in minor ways from the main results primarily because of
-\edit{weaker selection}
+The results deviate only in minor ways from the main results primarily because of greater drift
 due to (1) finite population size effects (smaller $N$);
@@
 curve of $\meansl$ over $u$ becomes more linear with increasing $B$, 
-with $\meansl$ values pulled towards \edit{neutral selection}, $\meansl \to 0.5$ (Figure~\ref{fig:populationSensitivity}a,
+with $\meansl$ values pulled towards maximal drift, $\meansl \to 0.5$ (Figure~\ref{fig:populationSensitivity}a,
 purple curves). With
@@
 as $u$ increases, more social learning across $u$ for larger $B$, and the
-same complex \edit{selection-strength} effects for combinations of $\pilow$ and $L$ that interact
+same complex drift effects for combinations of $\pilow$ and $L$ that interact
 with $u$ and $B$ settings.
@@
 We found that the number of prospective teachers had little effect on $\meansl$
-over $u$. There was slightly \edit{weaker selection} when $N_T = 2$ compared to our 
-main text analysis, slightly \edit{stronger selection} than our main analysis when $N_T = 20$; 
+over $u$. There was slightly more drift when $N_T = 2$ compared to our 
+main text analysis, slightly less drift than our main analysis when $N_T = 20$; 
 we also tested $N_T=10$, which showed no obvious difference from our main results
-with $N_T = 5$. When $N_T = 2$, \edit{weakened selection} is most pronounced in the
+with $N_T = 5$. When $N_T = 2$, increased drift is most pronounced in the
 $\meansl$ curves when $\pilow=0.8$ (Figure~\ref{fig:nteachersSensitivity}a, 
@@
 First, when $\beta=1$, most general trends are preserved, but in many cases the evolution
-of social learning is suppressed, \edit{or selection strength weakens}, due to 
+of social learning is suppressed or drift dominates due to 
 the overall poor quality of information acquired through softmax search-based
-individual learning with this setting. \edit{Weakened selection} is especially pronounced 
+individual learning with this setting. This increased drift is especially pronounced 
 when $\pilow=0.8$ since sub-optimal behaviors often pay off and $\beta=1$ is

### 2023-02-22 ms.tex
more revisions

--- 2023-02-21 ms.tex
@@
 affects both uncertainty \emph{and} the strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
-\edit{It is an outstanding problem to understand how payoff variance and payoff distributions generally affect evolved behavioral strategies~\citep{Haaland2019}.
-For the sake of theoretical clarity for our goal of understanding the \emph{interaction} of various sources of uncertainty we only operationalize payoff ambiguity as the difference between expected payoffs, even though empirical studies often include both forms of payoff uncertainty~\citep{McElreath2005,Toyokawa2019}, and a more complete model would include differences in mean and variance of payoffs.}
+\edit{It is an outstanding problem to understand how payoff variance and payoff
+distributions generally affect evolved behavioral strategies~\citep{Haaland2019}.
+For the sake of theoretical clarity for our goal of understanding the
+\emph{interaction} of various sources of uncertainty we only operationalize payoff
+ambiguity as the difference between expected payoffs, even though empirical studies
+have sometimes included both forms of payoff uncertainty~\citep{McElreath2005,Toyokawa2019}, and a more complete model would include differences in mean and variance of payoffs.}
 
@@
 
-% \begin{table}[h]
-%     \caption{Outcome Variables. All averages are computed across trials at the end of the last generation.}
-%     \label{tab:outcomeVariables}
-%     \centering %\hspace{-3em}
-%     \begin{tabular}{cp{4.25in}p{0.85in}} \toprule
-
-%         Symbol & Description & Values \\
-
-%         \midrule
-
-%         $\meansl$ & Mean social-learning prevalence over agents
-%                   & $ [0.0, 1.0]$ \\
-
-%         $\meanpi / L$ & Mean payoffs accumulated across agents, normalized by
-%         lifespan & $ [0.0, 1.0]$ \\
-
-%         $\meanG$ & Mean number of generations to convergence & \{1,2,\ldots\} \\
-%         \bottomrule
-%     \end{tabular}
-% \end{table}
+\begin{table}[h]
+    \caption{Outcome Variables. All averages are computed across trials at the end of the last generation.}
+    \label{tab:outcomeVariables}
+    \centering %\hspace{-3em}
+    \begin{tabular}{clp{0.85in}} \toprule
+
+        Symbol & Description & Values \\
+
+        \midrule
+
+        $\meansl$ & Mean social-learning prevalence over agents (Fig.~\ref{fig:mainResults})
+                  & $ [0.0, 1.0]$ \\
+
+        $\meanG$ & Mean number of generations to convergence (Fig.~\ref{fig:steps}) & \{1,2,\ldots\} \\
+
+        $\meanpi / L$ & Mean payoffs accumulated across agents, normalized by
+        lifespan (Fig.~\ref{fig:payoffs}) & $ [0.0, 1.0]$ \\
+
+        \bottomrule
+    \end{tabular}
+\end{table}
 
@@
   \centering 
-    {\textsf A, Low payoff $=$ 0.1, selection-set size $=$ 2} \\
+    {\textsf A \quad Low payoff, $\pilow = 0.1$; selection-set size, $B = 2$} \\
     \begin{subfigure}[]{0.4\textwidth}
@@
       \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
-    \end{subfigure} \\
-    \centering
-    {\textsf B, Low payoff $=$ 0.45, selection-set size $=$ 4} \\
+      \\[-0.8em]
+      {\centering \quad Environmental variability, $u$}
+    \end{subfigure} \\[1.5em]
+    \centering
+    {\textsf B \quad Low payoff, $\pilow = 0.45$; selection-set size, $B = 4$} \\
     \begin{subfigure}[]{0.4\textwidth}
@@
       \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
-    \end{subfigure} \\
-    {\textsf C, Low payoff $=$ 0.45, selection-set size $=$ 10} \\
+      \\[-0.8em]
+      {\centering \quad Environmental variability, $u$}
+    \end{subfigure} \\[1.5em]
+    {\textsf C \quad Low payoff, $\pilow = 0.45$; selection-set size, $B = 10$} \\
     \begin{subfigure}[]{0.4\textwidth}
@@
       \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+      \\[-0.8em]
+      {\centering \quad Environmental variability, $u$}
+
     \end{subfigure}
@@
 learning since successful out-group teachers could be cut off from in-group
-learners~\citep{Golub2012}.
-We assumed agents choose behaviors via a softmax \edit{decision rule, which is more cognitively sophisticated than most social-learning models and captures the adaptiveness of real human learning mechanisms, which was essential for developing our understanding of how social and individual learning can combine to multiply problem solving capacity of our agents---however true human learning is significantly more sophisticated~\citep{Schulz2020a,Wu2022}}.
-More realistic and powerful individual learning could further support the evolution of
+learners~\citep{Golub2012}. We assumed agents choose behaviors via a softmax
+\edit{decision rule, which is more cognitively sophisticated than most
+social-learning models and captures the adaptiveness of real human learning
+mechanisms. This modeling decision was essential for developing our understanding of
+how social and individual learning can combine to multiply problem solving capacity
+of our agents, though it is still a pale shadow of the true sophistication of human
+learning capabilities~\citep{Schulz2020a,Wu2022}}. More realistic and powerful individual learning could further support the evolution of
 social learning. These considerations provide novel opportunities to expand the evolutionary theory of social learning by adding
@@
 suggests that human groups regularly face novel environments.
-\edit{In our model, more numerous behavioral options led agents to be more cognitively flexible via the softmax decision rule, and thus better able to adjust their behavior if social learning provided outdated information.
+\edit{In our model, more numerous behavioral options meant agents more flexibly adjusted their behavior if social learning provided outdated information since in the softmax decision rule, more options means relatively less weight is assigned to the most profitable behavior known to agents, and greater weight is put on unexplored behaviors or those behaviors perceived to be less optimal.
 While Rogers'-style models of social learning evolution may also predict greater social learning reliance in more challenging contexts (larger selection-set sizes), they cannot predict that social learning should be favored for such high values of

### 2023-02-23 ms.tex
revisions nearly if not totally done

@@
 \begin{abstract} 
-Social learning is a critical adaptation for dealing with the variable world. However, variability
-takes different forms. Uncertainty is a severe form of variability where the space of possible
+Social learning is a critical adaptation for dealing with different forms of variability. 
+Uncertainty is a severe form of variability where the space of possible
 decisions or probabilities of associated outcomes are unknown.
-%"probabilities of decisions" didn't make sense to me so I rephrased, but hopefully still accurate.
-We identified four distinct and theoretically-important sources of uncertainty: temporal
-environmental variability, payoff ambiguity, selection-set size, and effective lifespan. All these
-kinds of uncertainty make it nearly impossible to fully learn about variability. We develop an
+We identified four theoretically-important sources of uncertainty: temporal
+environmental variability, payoff ambiguity, selection-set size, and effective lifespan. When these combine,
+it is nearly impossible to fully learn about the environment. We develop an
 evolutionary agent-based model to test how each form of uncertainty affects the evolution of social
 learning. Agents perform one of several behaviors, modeled as a multi-armed bandit, to acquire
-payoffs. \edit{Agents explore and learn about behavioral payoffs individually through an adaptive
-cognitive model that uses a softmax decision rule for behavior choice.} Use of
+payoffs. \edit{All agents learn about behavioral payoffs individually through an adaptive
+behavior-choice model that uses a softmax decision rule.} Use of
 vertical and oblique \edit{payoff-biased} social learning \edit{evolved} to serve as a scaffold \edit{for
-adaptive individual learning, meaning social and individual learning complement one
-another---they are not opposite strategies.} We found that different types of uncertainty had varying effects.
+adaptive individual learning---they are not opposite strategies}. Different types of uncertainty had varying effects.
 Temporal environmental variability suppressed social learning, whereas larger selection-set size
 promoted social learning, even when the environment changed frequently. Payoff ambiguity and lifespan
-had more complex effects on social learning, dependent on interactions with other uncertainty
-parameters. \edit{By assuming adaptive individual-level cognition, this study begins to explain how
-social learning can predominate despite high levels of various forms of uncertainty in the
-real-world.}
-
+interacted with other uncertainty parameters. \edit{This study begins to explain how
+social learning can predominate despite highly variable real-world environments when effective individual learning helps individuals recover from learning outdated social information.}
+%, meaning social and individual learning complement one another
   % the importance of clearly operationalizing uncertainty for understanding its role in cultural evolution.
@@
   \centering
-    \includegraphics[width=\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
+    \includegraphics[width=1.05\textwidth]{Figures/IntraInterGenerationalDynamics.pdf}
 \end{figure}
@@
 
-        $\meansl$ & Mean social-learning prevalence over agents (Fig.~\ref{fig:mainResults})
-                  & $ [0.0, 1.0]$ \\
-
-        $\meanG$ & Mean number of generations to convergence (Fig.~\ref{fig:steps}) & \{1,2,\ldots\} \\
+        $\meansl$ & Social learning fixation frequency (Fig.~\ref{fig:mainResults})
+                  &  $[0.0, 1.0]$ \\
+
+        $\meanG$ & Mean time to convergence in units of generations (Fig.~\ref{fig:steps}) & \{1,2,\ldots\} \\
 
@@
 learning monotonically decreases as temporal environmental variability, $u$,
-increases. When the environment is more likely to change between generations,
+increases \edit{(Figure~\ref{fig:mainResults})}. 
+When the environment is more likely to change between generations,
 information learned from the previous generation is less likely to be of value,
 decreasing selection for social learning.  
-\edit{Past some threshold, social learning never evolves.
-We define this threshold environmental variability as the \emph{social learning extinction variability} (Figure~\ref{fig:extinctionVariability}).}
 However, the exact nature of the relationship between social
 learning and temporal environmental variability was moderated by the other three uncertainty parameters.
+
+\edit{Across all parameter settings, we observed that there exists some threshold value of environmental
+  variability beyond which the evolution of social learning is exceedingly rare.  We call this the
+  \emph{social learning extinction variability}, denoted $u_\text{e}$ (Figure~\ref{fig:extinctionVariability}), which is expressed formally as 
+\begin{equation}
+  u_\text{e} = \min~\{ u~|~\meansl < 0.01 \}.
+  \label{eq:extinctionVariability}
+\end{equation}
+\noindent
+In other words, $u_\text{e}$ is the smallest value of $u$ for which the social learning fixated
+less than one in one hundred times. We will use this auxiliary measure to analyze the effect of
+the other uncertainty parameters and to highlight that social learning frequently 
+evolves despite high levels of environmental variability.}
 
@@
 \begin{figure}
-  \caption{As the number of
-  behaviors afforded by the environment increases (x-axis), 
-  social learning is supported up to increasingly large values of environmental variability (SL extinction
-    varibility, y-axis).}
+  \caption{As the selection-set size, $B$, and effective lifespan, $L$, increase (set equal along x-axis), 
+  social learning frequently evolves across an increasingly large range of
+  environmental variability values, i.e., up to
+  increasingly large values of social learning extinction variability
+(y-axis; defined in Equation~\ref{eq:extinctionVariability}).}
   \label{fig:extinctionVariability}

### 2023-02-23 ms.tex
updates

@@
 
-\paragraph{Initialization}
+\paragraph{Initialization.}
 
@@
 
-\paragraph{Within-generation dynamics}
+\paragraph{Within-generation dynamics.}
 % To guide behavior selection, agent $i$ counts how many times it
@@
 
-\paragraph{Intergenerational dynamics} Between generations, agents first reproduce
+\paragraph{Intergenerational dynamics.} Between generations, agents first reproduce
 via asexual haploid reproduction, which determines the transmission of the social
@@
 
-\paragraph{Stopping conditions} The evolutionary process continues until the
+\paragraph{Stopping condition.} The evolutionary process continues until the
 population reaches evolutionary fixation with respect to social learning, that is, when
@@
 
-        $\meansl$ & Social learning fixation frequency (Fig.~\ref{fig:mainResults})
+        $\meansl$ & Social learning fixation frequency (Figure~\ref{fig:mainResults})
                   &  $[0.0, 1.0]$ \\
 
-        $\meanG$ & Mean time to convergence in units of generations (Fig.~\ref{fig:steps}) & \{1,2,\ldots\} \\
+        $\meanG$ & Mean time to fixation in units of generations (Figure~\ref{fig:steps}) & \{1,2,\ldots\} \\
 
         $\meanpi / L$ & Mean payoffs accumulated across agents, normalized by
-        lifespan (Fig.~\ref{fig:payoffs}) & $ [0.0, 1.0]$ \\
+        lifespan (Figure~\ref{fig:payoffs}) & $ [0.0, 1.0]$ \\
 
@@
 using the Agents.jl agent-based modeling library~\citep{Datseris2022} and run
-on the Sherlock supercomputing cluster at Stanford University. Model and analysis code is publicly available on GitHub at \url{https://github.com/mt-digital/UncMod}.
+on the Sherlock supercomputing cluster at Stanford University. All Analysis figures
+except Figure~\ref{fig:extinctionVariability} were made using the Julia plotting
+library Gadfly~\citep{Jones2021b}. Figure~\ref{fig:extinctionVariability} was made in R~\citep{R}
+using the ggplot2 package~\citep{ggplot2}. 
+Model and analysis code is publicly available on GitHub at \url{https://github.com/mt-digital/UncMod}.
 

### 2023-02-24 ms.tex
updated SL ceiling

@@
 on the Sherlock supercomputing cluster at Stanford University. All Analysis figures
-except Figure~\ref{fig:extinctionVariability} were made using the Julia plotting
-library Gadfly~\citep{Jones2021b}. Figure~\ref{fig:extinctionVariability} was made in R~\citep{R}
+except Figure~\ref{fig:slCeiling} were made using the Julia plotting
+library Gadfly~\citep{Jones2021b}. Figure~\ref{fig:slCeiling} was made in R~\citep{R}
 using the ggplot2 package~\citep{ggplot2}. 
@@
   variability beyond which the evolution of social learning is exceedingly rare.  We call this the
-  \emph{social learning extinction variability}, denoted $u_\text{e}$ (Figure~\ref{fig:extinctionVariability}), which is expressed formally as 
+  \emph{social learning ceiling}, denoted $u_\text{c}$ (Figure~\ref{fig:slCeiling}), which is expressed formally as 
 \begin{equation}
-  u_\text{e} = \min~\{ u~|~\meansl < 0.01 \}.
-  \label{eq:extinctionVariability}
+  u_\text{c} = \min~\{ u~|~\meansl < 0.01 \}.
+  \label{eq:slCeiling}
 \end{equation}
 \noindent
-In other words, $u_\text{e}$ is the smallest value of $u$ for which the social learning fixated
+In other words, $u_\text{c}$ is the smallest value of $u$ for which social learning fixated
 less than one in one hundred times. We will use this auxiliary measure to analyze the effect of
@@
 when the environment is more likely to change than not (i.e.,
-$u>0.5$\edit{---see Figure~\ref{fig:extinctionVariability}}).
+$u>0.5$\edit{---see Figure~\ref{fig:slCeiling}}).
 
@@
   environmental variability values, i.e., up to
-  increasingly large values of social learning extinction variability
-(y-axis; defined in Equation~\ref{eq:extinctionVariability}).}
-  \label{fig:extinctionVariability}
+  increasingly large values of the social learning ceiling
+(y-axis; defined in Equation~\ref{eq:slCeiling}).}
+  \label{fig:slCeiling}
   \centering
@@
 between thirst and drinking water, or between friendship and warm laughter.
-\edit{If there were an exogenous cost of individual learning, this would likely increase the social learning extinction variability across uncertainty parameter settings.
+\edit{If there were an exogenous cost of individual learning, this would likely
+  increase the social learning ceiling across uncertainty parameter settings.
 Our model operationalizes environmental variability as fully stochastic,
@@
 evolve~\citep{Turner2022}, i.e., horizontal learning would increase what we have
-called the social learning extinction variability. However, depending on the
+called the social learning ceiling. However, depending on the
 setting, there may be little difference between horizontal and oblique learning, for

### 2023-02-24 Figures/supplement/nteachers=2/mainResultsPlots.tex
updated supplement figures labels to match new main text figure labels

\documentclass[varwidth=true,crop=false]{standalone}
\usepackage[chatter]{rotating}
\usepackage{amssymb,amsmath}
\usepackage{pgfplots}

\usepackage{geometry}
\geometry{
paperwidth=12in,
paperheight=12in,
margin=0.25in
}

\newcommand{\pisub}[1]{\pi_{\mathrm{#1}}}
\newcommand{\pilow}{\pisub{low}}
\newcommand{\pihigh}{\pisub{high}}
\newcommand{\piI}{\langle \pisub{I} \rangle}
\newcommand{\piS}{\langle \pisub{S} \rangle}
\newcommand{\ledger}{\bar\pi_{ib}}

\newcommand{\meanvar}[1]{\langle #1 \rangle}
\newcommand{\meansl}{\meanvar{s}}
\newcommand{\meanpi}{\meanvar{\pi}}
\newcommand{\meansoc}{\meanvar{\pi_\mathrm{S}}}
\newcommand{\meanasoc}{\meanvar{\pi_\mathrm{A}}}
\newcommand{\meanT}{\meanvar{T}}

\newcommand{\bandit}{\text{Bandit}_b(0, 1)}

\begin{document}
% \begin{tikzpicture}
      % \draw[->,thick] (-.1,0)--(1.15,0) node[above]
      %   {\huge Selection-set size};
      %   % {Number of behaviors $B$};
      % \draw[->,thick] (0,.1)--(0,-1.15) node[below]
      %   {\huge Low payoff\\(payoff ambiguity proxy)};
      %   % {Low payoff frequency $\pilow$};
	  % \end{tikzpicture}~\\[2em]

    \begin{minipage}{3.75in}
      \centering
      {\hspace{5.25em}\huge Selection-set size, $B = 2$}
    \end{minipage}%
    \begin{minipage}{3.75in}
      \centering
      {\hspace{3.0em}\huge Selection-set size, $B = 4$}
    \end{minipage}%
    \begin{minipage}{3.75in}
      \centering
      {\hspace{3.0em}\huge Selection-set size, $B = 10$}
    \end{minipage}~\\

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{3.0in}{
          \centering
          \vspace{-1.0em}\hspace{-1.5em} {\huge Low payoff, $\pilow = 0.1$} \\[1em]
          {\huge SL fixation frequency, $\meansl$}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
    \end{minipage}\noindent\hspace{1.25em}
	\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
    \end{minipage}\noindent
	\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
    \end{minipage}~\\[4.0em]

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{3.0in}{
          \centering
          \vspace{-1.0em}\hspace{-1.5em} {\huge Low payoff, $\pilow = 0.45$} \\[1em]
          {\huge SL fixation frequency, $\meansl$}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
	\end{minipage}\noindent\hspace{1.25em}
	\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
    \end{minipage}\noindent
	\begin{minipage}{3.75in}%
      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
    \end{minipage}~\\[4.0em]

    \begin{minipage}{3.75in}
    \begin{rotate}{90}
      {\parbox{3.0in}{
          \centering
          \vspace{-1.0em}\hspace{-1.5em}{\huge Low payoff, $\pilow = 0.8$} \\[1em]
          {\huge SL fixation frequency, $\meansl$}
          % {\begin{rotate}{-90}{\huge $\meansl$}\hspace{3em}\end{rotate}}
      }}
    \end{rotate}%
    \hspace{2em}
      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
        \\[-2.75em]
        \begin{center}
          {\hspace{3.25em} \huge Environmental variability, $u$}
      \end{center}
	  \end{minipage}\noindent\hspace{1.25em}
		\begin{minipage}{3.75in}%
		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
		  \\[-2.75em]
	  \begin{center}
        {\hspace{3.25em} \huge Environmental variability, $u$}
      \end{center}
    \end{minipage}
	\begin{minipage}{3.75in}%
		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
		  \\[-2.75em]
	  \begin{center}
        {\hspace{3.25em} \huge Environmental variability, $u$}
      \end{center}
    \end{minipage} 
    % \\[2.5em]
    % \begin{center}
    %   \includegraphics[width=1.85in]{Figures/legendElements/ldashdot.pdf}
    %   {\Huge$\meanasoc = \meansoc$} \quad \quad
    %   \includegraphics[width=1.85in]{Figures/legendElements/dot.pdf}
    %   {\Huge$\underset{u}{\arg\max}~\langle G(u) \rangle$}
    % \end{center}
\end{document}

### 2023-02-24 Figures/supplement/nteachers=20/mainResultsPlots.tex
updated supplement figures labels to match new main text figure labels

--- 2023-02-24 Figures/supplement/nteachers=2/mainResultsPlots.tex
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
     \end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
 	\end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
         \\[-2.75em]
@@
 		\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
 		  \\[-2.75em]
@@
 	\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
 		  \\[-2.75em]

### 2023-02-24 Figures/supplement/numagents=200/mainResultsPlots.tex
updated supplement figures labels to match new main text figure labels

--- 2023-02-24 Figures/supplement/nteachers=2/mainResultsPlots.tex
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
     \end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
 	\end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
         \\[-2.75em]
@@
 		\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
 		  \\[-2.75em]
@@
 	\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
 		  \\[-2.75em]

### 2023-02-24 Figures/supplement/numagents=50/mainResultsPlots.tex
updated supplement figures labels to match new main text figure labels

--- 2023-02-24 Figures/supplement/nteachers=2/mainResultsPlots.tex
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
     \end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
 	\end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
         \\[-2.75em]
@@
 		\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
 		  \\[-2.75em]
@@
 	\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
 		  \\[-2.75em]

### 2023-02-24 Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.tex
updated supplement figures labels to match new main text figure labels

--- 2023-02-24 Figures/supplement/numagents=50/mainResultsPlots.tex
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
     \end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
 	\end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
         \\[-2.75em]
@@
 		\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
 		  \\[-2.75em]
@@
 	\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
 		  \\[-2.75em]

### 2023-02-24 Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.tex
updated supplement figures labels to match new main text figure labels

--- 2023-02-24 Figures/supplement/numagents=50/mainResultsPlots.tex
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
     \end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mean_social_learner_over_u_lowpayoff=0.1_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=2.pdf}
 	\end{minipage}\noindent\hspace{1.25em}
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
     \end{minipage}\noindent
 	\begin{minipage}{3.75in}%
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mean_social_learner_over_u_lowpayoff=0.45_nbehaviors=10.pdf}
     \end{minipage}~\\[4.0em]
@@
     \hspace{2em}
-      \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
+      \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=2.pdf}
         \\[-2.75em]
@@
 		\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=4.pdf}
 		  \\[-2.75em]
@@
 	\begin{minipage}{3.75in}%
-		  \includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
+		  \includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mean_social_learner_over_u_lowpayoff=0.8_nbehaviors=10.pdf}
 		  \\[-2.75em]

### 2023-02-25 ms.tex
updated supplement figures labels to match new main text figure labels

@@
 \author[1,2,*]{Matthew A. Turner}
-\author[3,4]{Cristina Moya}
-\author[5,6,7]{Paul E. Smaldino}
-\author[1,2,7]{James~Holland~Jones}
+\author[3]{Cristina Moya}
+\author[4,5,6]{Paul E. Smaldino}
+\author[1,2,6]{James~Holland~Jones}
 
@@
 \affil[3]{Department of Anthropology, University of California at Davis, Davis, CA 95616 USA}
-\affil[4]{Centre for Culture and Evolution, Brunel University London, Uxbridge, UB8 3PH UK}
-\affil[5]{Cognitive and Information Sciences, University of California at Merced, Merced, CA 95340 USA}
-\affil[6]{Santa Fe Institute, Santa Fe, NM 87501 USA}
-\affil[7]{Center for Advanced Study in the Behavioral Sciences, Stanford University, Stanford, CA 94305 USA}
+\affil[4]{Cognitive and Information Sciences, University of California at Merced, Merced, CA 95340 USA}
+\affil[5]{Santa Fe Institute, Santa Fe, NM 87501 USA}
+\affil[6]{Center for Advanced Study in the Behavioral Sciences, Stanford University, Stanford, CA 94305 USA}
 \affil[*]{Corresponding author; email: \href{mailto:maturner@stanford.edu}{maturner@stanford.edu}}
@@
 payoffs. \edit{All agents learn about behavioral payoffs individually through an adaptive
-behavior-choice model that uses a softmax decision rule.} Use of
-vertical and oblique \edit{payoff-biased} social learning \edit{evolved} to serve as a scaffold \edit{for
-adaptive individual learning---they are not opposite strategies}. Different types of uncertainty had varying effects.
+behavior-choice model that uses a softmax decision rule.} Use of vertical and oblique \edit{payoff-biased} social learning \edit{evolved} to serve as a scaffold \edit{for adaptive individual learning---they are not opposite strategies}.
+Different types of uncertainty had varying effects.
 Temporal environmental variability suppressed social learning, whereas larger selection-set size
 promoted social learning, even when the environment changed frequently. Payoff ambiguity and lifespan
-interacted with other uncertainty parameters. \edit{This study begins to explain how
-social learning can predominate despite highly variable real-world environments when effective individual learning helps individuals recover from learning outdated social information.}
+interacted with other uncertainty parameters.
+\edit{This study begins to explain how social learning can predominate despite highly variable real-world environments when effective individual learning helps individuals recover from learning outdated social information.}
 %, meaning social and individual learning complement one another
@@
   \centering
-    \includegraphics[width=0.8\textwidth]{Figures/SL_Extinction_Variability.pdf}
+    \includegraphics[width=0.8\textwidth]{Figures/SL_ceiling.pdf}
 \end{figure}
@@
 outdated information too heavily.
-\edit{In other words, environmental change lowers social learners' mean payoffs, but social learner payoffs build back up when (blue dots, Figure~\ref{fig:payoffTimeseries}A).
+\edit{In other words, environmental change lowers social learners' mean payoffs, but social learner payoffs build back up as the information quality in the population improves (blue dots, Figure~\ref{fig:payoffTimeseries}A).
 Even though an homogenous population of social learners would outperform individual learners in this case, unpredictable environmental stochasticity undermines the reliability of social learning.
@@
 intergenerational social learning and environmental change. Within generations,
-agents can only learn individually. This assumption allows us to replicate the
+agents can only learn individually. This assumption \edit{is consistent with previous modeling work starting at least from \cite{Rogers1988}, and therefore} allows us to replicate the
 classic finding that if the environment changes too quickly, socially-learned
@@
 other mechanisms, like conformity, may lead to \edit{weaker selection} overall. 
-\edit{Furthermore, our learning procedure could be interpreted as direct copying of
-latent psychological variables (expected payoffs for each behavior); if children
-learned instead from observations of the parent's behaviors without knowing rewards,
-which in some cases would be a more realistic assumption~\citep{Wu2022b}, this may weaken the strength of selection for social learning.} We
-also assumed that the number of behaviors and their payoffs were constant within a
+\edit{Furthermore, our learning procedure could be interpreted as direct copying of latent psychological variables (expected payoffs for each behavior).
+Such detailed information is most likely transmitted through teaching wherein the model explicitly informs the learner of their experiences.
+If children learned instead from observations of the parent's behaviors without knowing rewards, which in some cases would be a more realistic assumption~\citep{Wu2022b}, this may weaken the strength of selection for social learning.} We also assumed that the number of behaviors and their payoffs were constant within a
 given simulation, but this fails to account for evolutionary feedback which creates
@@
 suggests that human groups regularly face novel environments.
-\edit{In our model, more numerous behavioral options meant agents more flexibly adjusted their behavior if social learning provided outdated information since in the softmax decision rule, more options means relatively less weight is assigned to the most profitable behavior known to agents, and greater weight is put on unexplored behaviors or those behaviors perceived to be less optimal.
-While Rogers'-style models of social learning evolution may also predict greater social learning reliance in more challenging contexts (larger selection-set sizes), they cannot predict that social learning should be favored for such high values of
+\edit{In our model, more behavioral options meant agents more flexibly adjusted their behavior if social learning provided outdated information since in the softmax decision rule, more options means relatively less weight is assigned to the most profitable behavior known to agents, and greater weight is put on unexplored behaviors or those behaviors perceived to be less optimal.
+While Rogers'-style models of social learning evolution may also predict greater social learning reliance in more challenging contexts (larger selection-set sizes), they would not predict that social learning should be favored for such high values of
 environmental variability as we observed here.} 
@@
   \begin{subfigure}{\textwidth}
-	\caption{$N=50$}
+	\caption{Population size, $N=50$}
 	\includegraphics[width=\textwidth]{Figures/supplement/numagents=50/mainResultsPlots.pdf}
@@
 	\begin{subfigure}{\textwidth}
-	  \caption{$N=200$}
+	  \caption{Population size, $N=200$}
 	  \includegraphics[width=\textwidth]{Figures/supplement/numagents=200/mainResultsPlots.pdf}
@@
   \begin{subfigure}{\textwidth}
-	\caption{$N_T = 2$}
+	\caption{Number of prospective teachers, $N_T = 2$}
 	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=2/mainResultsPlots.pdf}
@@
   \begin{subfigure}{\textwidth}
-	\caption{$N_T = 20$}
+	\caption{Number of prospective teachers, $N_T = 20$}
 	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=20/mainResultsPlots.pdf}
@@
   \begin{subfigure}{\textwidth}
-	\caption{$\beta = 1$}
+	\caption{Softmax greediness, $\beta = 1$}
 	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=1.0/mainResultsPlots.pdf}
@@
   \begin{subfigure}{\textwidth}
-	\caption{$\beta = 100$}
+	\caption{Softmax greediness, $\beta = 100$}
 	\includegraphics[width=\textwidth]{Figures/supplement/sensitivity_tau=0.01/mainResultsPlots.pdf}

### 2023-02-26 ms.tex
Updates from Overleaf

@@
 Uncertainty weighs particularly heavily on human adaptation because of
-our long lifespans, cosmopolitan societies, and dispersal across highly variable environments, requiring coarse-grained and plastic behavioral adaptations \citep{levins1962}.
+our long lifespans, cosmopolitan distribution, and dispersal across highly variable environments, requiring coarse-grained and plastic behavioral adaptations \citep{levins1962}.
 However, the term ``uncertainty'' is often used loosely in a way that fails to distinguish it from risk.
@@
 %Other (asocial) forms of learning are also likely adaptations to uncertainty that should be accounted for, but are typically glossed over in models.  
-Learning, be it social or not, is an iterative process during which an individual acquires information, forms representations and predictions, and then tests and refines those representations and predictions to manage uncertainty~\citep{jacobs2011bayesian,clark2013whatever}.
+Learning, social or otherwise, is an iterative process during which an individual acquires information, forms representations and predictions, and then tests and refines those representations and predictions to manage uncertainty~\citep{jacobs2011bayesian,clark2013whatever}.
 Because cultural evolutionary models are frequently designed to explain \emph{social} learning mechanisms, they often contrast social learning with a simplistic mechanism for individual learning.
@@
 Similarly, many human studies have used just two or three possible
-behaviors~\citep{McElreath2005,Morgan2012, Toyokawa2019}. Behavioral study designs are
+behaviors~\citep{McElreath2005,Morgan2012, Toyokawa2019}. The designs of behavioral experiments are 
 often motivated by modeling studies with similar formulations~\citep{Rogers1988,boyd1995does,Feldman1996,
@@
 For the sake of theoretical clarity for our goal of understanding the
-\emph{interaction} of various sources of uncertainty we only operationalize payoff
+\emph{interaction} of various sources of uncertainty, we only operationalize payoff
 ambiguity as the difference between expected payoffs, even though empirical studies
@@
 % predictions to manage uncertainty \citep{jacobs2011bayesian,clark2013whatever}. 
-We refer to the number of individual learning opportunities within a generation as an individual's effective lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behavior, rather than the number of sunrises one experiences, that determines one's uncertainty about the behavioral options.
+We refer to the number of individual learning opportunities within a generation as an individual's \emph{effective} lifespan to highlight that it is the number of opportunities to learn about the payoffs associated with a behavior, rather than the number of sunrises one experiences, that determines one's uncertainty about the behavioral options.
 %throughout the individual's lifespan that matters here, not necessarily how long they live in the absence of relevant learning opportunities.
 
-Empirically, the number of learning opportunities can be manipulated in the lab, and in the real world will tend to correlate with an individual's relative age.
+Empirically, the number of learning opportunities can be manipulated in the lab and in the real world will tend to correlate with an individual's relative age.
 In multi-round studies of information use in novel tasks, US participants' use of social
@@
 attention \citep{kline2013teaching}.
-While these phenomena map on imperfectly to effective lifespan in our model given social learning is only allowed intergenerationally, effective lifespans for learning do vary across tasks, individuals, and species, yet most models assume only one learning opportunity per generation \citep{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
+While these phenomena map imperfectly onto effective lifespan in our model, given social learning is only allowed intergenerationally, \edit{the relative number of individual to social learning opportunities, i.e., this model's version of }effective lifespan, do vary across tasks, individuals, and species, yet most models assume only one learning opportunity per generation \citep{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
 Some models do allow several cultural generations within one genetic generation \citep{Enquist2007,Rendell2010,lindstrom2016co}, but little formal theory explicitly examines the role of learning opportunities in the evolution of social learning.
@@
 Many of these are flexible learning mechanisms that do not require imitating the behaviors of others.
-For example, when faced with greater uncertainty individuals may adopt more exploratory learning strategies and may even preferentially test behaviors with greater observed payoff variance \citep{Wilson2014,Gershman2019}.
+For example, when faced with greater uncertainty, individuals may adopt more exploratory learning strategies and may even preferentially test behaviors with greater observed payoff variance \citep{Wilson2014,Gershman2019}.
 
@@
 In other words, payoff ambiguity, and therefore uncertainty, increases with $\pilow$.
-Agents have $L$ time steps to learn and act per generation (i.e., the \emph{effective lifespan}).
+Agents have $L$ time steps to \edit{act and learn asocially} per generation (i.e., the \emph{effective lifespan}).
 Uncertainty decreases with $L$.
@@
 \begin{table}[h]
-\caption{Environmental Parameters. These include our four main uncertainty parameters under investigation; 
+\caption{Environmental parameters. These include our four main uncertainty parameters under investigation; 
 $\pilow$, $B$, $L$, and $u$. Bold indicates default value tested.} %\emph{default value tested}.}
@@
 \begin{figure}
-  \caption{Agents are randomly initialized as social learners or not, with their
+  \caption{\edit{Model summary}. Agents are randomly initialized as social learners or not, with their
   payoff observations all initialized to zero (A). Then agents begin selecting
@@
 %We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L \in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.
-\edit{We observed three outcome measures: first, the social learning (SL) fixation ferquency, denoted
+\edit{We observed three outcome measures: first, the social learning (SL) fixation frequency, denoted
 $\meansl$, is how frequently
@@
 \begin{table}[h]
-    \caption{Outcome Variables. All averages are computed across trials at the end of the last generation.}
+    \caption{Outcome variables. All averages are computed across trials at the end of the last generation.}
     \label{tab:outcomeVariables}
@@
 options. For example, with only two behavioral choices ($B = 2$), a common assumption in many models, social
-learning is particularly detrimental when the environment changes since more of the population will have
+learning is particularly detrimental when the environment changes, since more of the population will have
 arrived at the optimal behavior in the previous generation and socially learning from them will be biased
@@
 \begin{figure}
-  \caption{Social learning fixation frequency across trials (y-axes) monotonically decreases as 
+  \caption{\edit{Effect of four forms of uncertainty on evolution of social learning}. Social learning fixation frequency across trials (y-axes) monotonically decreases as 
   environmental variability, $u$, increases (x-axes) in most uncertainty contexts. 
@@
 \begin{figure}
-  \caption{As the selection-set size, $B$, and effective lifespan, $L$, increase (set equal along x-axis), 
+  \caption{\edit{Effect of uncertainty on social learning ceiling.} As the selection-set size, $B$, and effective lifespan, $L$, increase (set equal along x-axis), 
   social learning frequently evolves across an increasingly large range of
@@
 
-When payoff ambiguity and selection-set size was small ($\pilow=0.1$ and $B=2$), and lifespan was long ($L \geq 4$), asocial learning fixated as a hedge against periods of protracted environmental instability, even though expected
+When payoff ambiguity and selection-set size were small ($\pilow=0.1$ and $B=2$), and lifespan was long ($L \geq 4$), asocial learning fixated as a hedge against periods of protracted environmental instability, even though expected
 homogeneous social payoffs were greater than homogeneous asocial payoffs (Figure~\ref{fig:payoffTimeseries}A).
@@
 outdated information too heavily.
-\edit{In other words, environmental change lowers social learners' mean payoffs, but social learner payoffs build back up as the information quality in the population improves (blue dots, Figure~\ref{fig:payoffTimeseries}A).
-Even though an homogenous population of social learners would outperform individual learners in this case, unpredictable environmental stochasticity undermines the reliability of social learning.
-When lifespan was minimal ($L=1$) and environmental variability was moderate ($u\approx0.5$), the opposite, unexpected outcome could occur where social learning fixates despite the fact that an homogenous population of asocial learners would outperform an homogenous population of social learners (Figure~\ref{fig:payoffTimeseries}B).
+\edit{In other words, environmental change lowers social learners' mean payoffs, but social-learner payoffs build back up as the information quality in the population improves (blue dots, Figure~\ref{fig:payoffTimeseries}A).
+Even though a homogenous population of social learners would outperform individual learners in this case, unpredictable environmental stochasticity undermines the reliability of social learning.
+When lifespan was minimal ($L=1$) and environmental variability was moderate ($u\approx0.5$), the opposite, unexpected outcome could occur where social learning fixates despite the fact that a homogenous population of asocial learners would outperform a homogenous population of social learners (Figure~\ref{fig:payoffTimeseries}B).
 In this case, it takes relatively few consecutive generations with environmental stability to attract the population to all become social learners.}
@@
   increase the social learning ceiling across uncertainty parameter settings.
-Our model operationalizes environmental variability as fully stochastic,
-which forces evolution towards either a population of social or asocial learners
-since environmental change is unpredictable, unlike precursor
+This means that our model does not capture the information-scrounging rewards to individual learning that produce mixed equilibria in precursor models \cite{Rogers1988}.
+Furthermore, our model operationalizes environmental variability as fully stochastic in a finite population.
+This makes it exceedingly unlikely for a heterogeneous population to persist since chance runs of very stable environments will lead to the extinction of asocial learners, while runs of very unstable environments will lead to the extinction of social learners.
+This further differentiates our results from precursor
 models that allowed for persistent frequency
@@
 other mechanisms, like conformity, may lead to \edit{weaker selection} overall. 
-\edit{Furthermore, our learning procedure could be interpreted as direct copying of latent psychological variables (expected payoffs for each behavior).
+\edit{Furthermore, our social learning procedure could be interpreted as direct copying of latent psychological variables (expected payoffs for each behavior).
 Such detailed information is most likely transmitted through teaching wherein the model explicitly informs the learner of their experiences.
@@
 mechanisms. This modeling decision was essential for developing our understanding of
-how social and individual learning can combine to multiply problem solving capacity
+how social and individual learning can combine to multiply the problem solving capacity
 of our agents, though it is still a pale shadow of the true sophistication of human
@@
 (nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal
-suggests that human groups regularly face novel environments.
-\edit{In our model, more behavioral options meant agents more flexibly adjusted their behavior if social learning provided outdated information since in the softmax decision rule, more options means relatively less weight is assigned to the most profitable behavior known to agents, and greater weight is put on unexplored behaviors or those behaviors perceived to be less optimal.
-While Rogers'-style models of social learning evolution may also predict greater social learning reliance in more challenging contexts (larger selection-set sizes), they would not predict that social learning should be favored for such high values of
-environmental variability as we observed here.} 
+\edit{meant} that human groups regularly face novel environments.
+\edit{These conditions, combined with long lifespan, obviated the possibility of genetic adaptation to specific ecological circumstances, requiring instead the evolution of learning mechanisms for dealing with uncertainty.
+In our model, numerous behavioral options led agents to be more cognitively flexible via the softmax decision rule, and thus better able to adjust their behavior if social learning provided outdated information.
+While Rogers-style models of social learning evolution may also predict greater social learning reliance in more challenging contexts (larger selection-set sizes), these models rely on limited individual learning mechanisms that are furthermore mutually exclusive with social learning.
+This may prevent social learning from evolving under such high values of environmental variability as we observed here, even if these models included more adaptive individual learning mechanisms.}
 By carefully identifying and operationalizing different forms of uncertainty common in social-learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution.

### 2023-02-26 ms.tex
final

@@
 \usepackage{totcount}
+\usepackage[chatter]{rotating}
 % \documentclass[11pt]{report}
@@
 %We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L \in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.
-\edit{We observed three outcome measures: first, the social learning (SL) fixation frequency, denoted
-$\meansl$, is how frequently
-social learning evolved to fixation across all trials for a given parameter setting. To support our
-analysis about why we observe the patterns in social learning fixation frequency that we did, we also
-measured the mean number of generations to fixation, which measures the strength of selection.} Finally we
-measured the average net payoffs at the end of the simulation across agents and trials, normalized by lifespan. We analyze
+\edit{We observed three outcome measures: first, the social learning (SL) fixation frequency, denoted $\meansl$, is how frequently social learning evolved to fixation across all trials for a given parameter setting.
+To support our analysis about why we observed the patterns in social learning fixation frequency that we did, we also measured the mean number of generations to fixation, which measures the strength of selection.} Finally we measured the average net payoffs at the end of the simulation across agents and trials, normalized by lifespan.
+We analyze
 outcomes by plotting $\meansl$ on the y-axis and environmental variability on
@@
     {\textsf A \quad Low payoff, $\pilow = 0.1$; selection-set size, $B = 2$} \\
-    \begin{subfigure}[]{0.4\textwidth}
-      \centering
+    % \begin{subfigure}[]{0.4\textwidth}
+    \begin{minipage}[]{0.4\textwidth}
+      \centering
+      \begin{rotate}{90}
+        {\parbox{3.0in}{
+            \centering
+            % \vspace{-1.0em}\hspace{-1.5em} {\huge Low payoff, $\pilow = 0.1$} \\[1em]
+            {\hspace{-7em} Mean payoffs, $\meanpi / L$}
+        }}
+      \end{rotate}%
       \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.1_nbehaviors=2.pdf}
@@
       {\centering \quad Environmental variability, $u$}
-    \end{subfigure} \\[1.5em]
+    \end{minipage} \\[1.5em]
+    % \end{subfigure} \\[1.5em]
     \centering
     {\textsf B \quad Low payoff, $\pilow = 0.45$; selection-set size, $B = 4$} \\
-    \begin{subfigure}[]{0.4\textwidth}
+    % \begin{subfigure}[]{0.4\textwidth}
+    \begin{minipage}[]{0.4\textwidth}
       % {\large \textsf B}
       \centering
+      \begin{rotate}{90}
+        {\parbox{3.0in}{
+            \centering
+            % \vspace{-1.0em}\hspace{-1.5em} {\huge Low payoff, $\pilow = 0.1$} \\[1em]
+            {\hspace{-7em} Mean payoffs, $\meanpi / L$}
+        }}
+      \end{rotate}%
       \includegraphics[width=\textwidth]{Figures/mean_prev_net_payoff_over_u_lowpayoff=0.45_nbehaviors=4.pdf}
@@
       {\centering \quad Environmental variability, $u$}
-    \end{subfigure} \\[1.5em]
+    \end{minipage} \\[1.5em]
+    % \end{subfigure} \\[1.5em]
     {\textsf C \quad Low payoff, $\pilow = 0.45$; selection-set size, $B = 10$} \\
-    \begin{subfigure}[]{0.4\textwidth}
-      \centering
+    % \begin{subfigure}[]{0.4\textwidth}
+    \begin{minipage}[]{0.4\textwidth}
+      \centering
+      \begin{rotate}{90}
+        {\parbox{3.0in}{
+            \centering
+            % \vspace{-1.0em}\hspace{-1.5em} {\huge Low payoff, $\pilow = 0.1$} \\[1em]
+            {\hspace{-7em} Mean payoffs, $\meanpi / L$}
+        }}
+      \end{rotate}%
       % {\large \textsf C}
@@
 
-    \end{subfigure}
+    \end{minipage}
+    % \end{subfigure}
 
@@
 (nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal
-\edit{meant} that human groups regularly face novel environments.
+\edit{meant} that human groups regularly faced novel environments.
 \edit{These conditions, combined with long lifespan, obviated the possibility of genetic adaptation to specific ecological circumstances, requiring instead the evolution of learning mechanisms for dealing with uncertainty.
@@
 
-\paragraph{Acknowledgements.} %\mt{Do we write any at this point? Please fill in as you see fit.} \cm{can do later since should be blinded anyway}
+\paragraph{Acknowledgements.} We thank colleagues at the Cultural Evolution
+Society and Cognitive Science Society annual meetings in 2022 who provided helpful feedback
+to presentations of this work. We also thank the editor and two anonymous reviewers
+for helping to improve to the original manuscript.%\mt{Do we write any at this point? Please fill in as you see fit.} \cm{can do later since should be blinded anyway}
 %
@@
 
-\paragraph{Conflict of interest.} No conflict declared.
+\paragraph{Conflict of interest.} No conflict declared. \\[1em]
 

### 2023-02-26 ms.tex
final updates

@@
 $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single
-observation with the associated uncertainty. \edit{If students have more confidence
+observation with the associated uncertainty. \edit{If learners have more confidence
 in the teacher's information, or there are biological or cultural factors that more
@@
 models that allowed for persistent frequency
-dependence~\citep{BoydRicherson1985,Rogers1988,Feldman1996}.} Second, we only allow for
+dependence of social learning benefit~\citep{BoydRicherson1985,Rogers1988,Feldman1996}.} Second, we only allow for
 intergenerational social learning and environmental change. Within generations,
-agents can only learn individually. This assumption \edit{is consistent with previous modeling work starting at least from \cite{Rogers1988}, and therefore} allows us to replicate the
-classic finding that if the environment changes too quickly, socially-learned
-information may become \edit{outdated. Adding horizontal social learning between
-vertical/oblique learning in this model would likely expand the range of
-environmental variability over which social learning would
-evolve~\citep{Turner2022}, i.e., horizontal learning would increase what we have
-called the social learning ceiling. However, depending on the
+agents can only learn individually.
+This assumption \edit{is consistent with previous modeling work starting at least from \cite{Rogers1988}, and therefore} allows us to replicate the classic finding that if the environment changes too quickly, socially-learned information may become \edit{outdated.
+Adding horizontal social learning between vertical/oblique learning in this model would likely expand the range of environmental variability over which social learning would evolve~\citep{Turner2022}, i.e., horizontal learning would increase what we have called the social learning ceiling.
+However, depending on the
 setting, there may be little difference between horizontal and oblique learning, for
@@
 learning since successful out-group teachers could be cut off from in-group
-learners~\citep{Golub2012}. We assumed agents choose behaviors via a softmax
-\edit{decision rule, which is more cognitively sophisticated than most
-social-learning models and captures the adaptiveness of real human learning
-mechanisms. This modeling decision was essential for developing our understanding of
-how social and individual learning can combine to multiply the problem solving capacity
-of our agents, though it is still a pale shadow of the true sophistication of human
-learning capabilities~\citep{Schulz2020a,Wu2022}}. More realistic and powerful individual learning could further support the evolution of
+learners~\citep{Golub2012}.
+We assumed agents choose behaviors via a softmax \edit{decision rule, which is more cognitively sophisticated than most social-learning models and captures the adaptiveness of real human learning mechanisms.
+This modeling decision was essential for developing our understanding of how social and individual learning can combine to multiply the problem solving capacity of our agents, though it is still a pale shadow of the true sophistication of human learning capabilities~\citep{Schulz2020a,Wu2022}}.
+More realistic and powerful individual learning could further support the evolution of
 social learning. These considerations provide novel opportunities to expand the evolutionary theory of social learning by adding
@@
 (nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal
-\edit{meant} that human groups regularly faced novel environments.
-\edit{These conditions, combined with long lifespan, obviated the possibility of genetic adaptation to specific ecological circumstances, requiring instead the evolution of learning mechanisms for dealing with uncertainty.
-In our model, numerous behavioral options led agents to be more cognitively flexible via the softmax decision rule, and thus better able to adjust their behavior if social learning provided outdated information.
-While Rogers-style models of social learning evolution may also predict greater social learning reliance in more challenging contexts (larger selection-set sizes), these models rely on limited individual learning mechanisms that are furthermore mutually exclusive with social learning.
+\edit{meant} that human groups regularly faced novel environments. \edit{These
+conditions and our longevity obviated the possibility of genetic
+adaptation to specific ecological circumstances, requiring instead the evolution of
+learning mechanisms for dealing with uncertainty. In our model, numerous behavioral
+options led agents to be more cognitively flexible via the softmax decision rule, and
+thus better able to adjust their behavior if social learning provided outdated
+information.
+While Rogers'-style models of social learning evolution may also predict greater social learning reliance in more challenging contexts (larger selection-set sizes), these models rely on limited individual learning mechanisms that are furthermore mutually exclusive with social learning.
 This may prevent social learning from evolving under such high values of environmental variability as we observed here, even if these models included more adaptive individual learning mechanisms.}

### 2023-02-26 ms.tex
updated ms

@@
 
-\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \mt{OSF link to PDF when final and separated)}.
-Model and analysis code is publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF (\url{https://osf.io/t8exa/}).
+\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \url{https://osf.io/tpsy9}. Model and analysis code is
+publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF
+(\url{https://osf.io/t8exa/}). A guide to running the analyses is available on the GitHub repository.
 
@@
 Society and Cognitive Science Society annual meetings in 2022 who provided helpful feedback
-to presentations of this work. We also thank the editor and two anonymous reviewers
+on presentations of this work. We also thank the editor and two anonymous reviewers
 for helping to improve to the original manuscript.%\mt{Do we write any at this point? Please fill in as you see fit.} \cm{can do later since should be blinded anyway}

### 2023-02-26 ms.tex
Updates from Overleaf

--- 2023-02-26 ms.tex
@@
 
-\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \mt{OSF link to PDF when final and separated)}.
+\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \url{https://osf.io/tpsy9}.
 Model and analysis code is publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF (\url{https://osf.io/t8exa/}).

### 2023-04-04 ms.tex
fixed two Figure 5's issue
revision #2 updates

--- 2023-02-26 ms.tex
@@
 learning. Agents perform one of several behaviors, modeled as a multi-armed bandit, to acquire
-payoffs. \edit{All agents learn about behavioral payoffs individually through an adaptive
-behavior-choice model that uses a softmax decision rule.} Use of vertical and oblique \edit{payoff-biased} social learning \edit{evolved} to serve as a scaffold \edit{for adaptive individual learning---they are not opposite strategies}.
+payoffs. All agents learn about behavioral payoffs individually through an adaptive
+behavior-choice model that uses a softmax decision rule.
+Use of vertical and oblique payoff-biased social learning evolved to serve as a scaffold for adaptive individual learning---they are not opposite strategies.
 Different types of uncertainty had varying effects.
@@
 interacted with other uncertainty parameters.
-\edit{This study begins to explain how social learning can predominate despite highly variable real-world environments when effective individual learning helps individuals recover from learning outdated social information.}
+This study begins to explain how social learning can predominate despite highly variable real-world environments when effective individual learning helps individuals recover from learning outdated social information.
 %, meaning social and individual learning complement one another
@@
 generation and asocial learners do not. All agents engage in individual learning
-within their lifespans. The model also assumes \edit{an adaptive},
-empirically-motivated learning mechanism, the softmax \edit{decision rule}, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
+within their lifespans. The model also assumes an adaptive,
+empirically-motivated learning mechanism, the softmax decision rule, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
 Our model design thereby affords us a richer and possibly more accurate assessment of trade-offs between social and asocial learning.
@@
 affects both uncertainty \emph{and} the strength of selection, with smaller payoff differences leading to greater uncertainty for a learner and weaker evolutionary selection favoring optimal strategies.
-\edit{It is an outstanding problem to understand how payoff variance and payoff
+It is an outstanding problem to understand how payoff variance and payoff
 distributions generally affect evolved behavioral strategies~\citep{Haaland2019}.
@@
 ambiguity as the difference between expected payoffs, even though empirical studies
-have sometimes included both forms of payoff uncertainty~\citep{McElreath2005,Toyokawa2019}, and a more complete model would include differences in mean and variance of payoffs.}
+have sometimes included both forms of payoff uncertainty~\citep{McElreath2005,Toyokawa2019}, and a more complete model would include differences in mean and variance of payoffs.
 
@@
 attention \citep{kline2013teaching}.
-While these phenomena map imperfectly onto effective lifespan in our model, given social learning is only allowed intergenerationally, \edit{the relative number of individual to social learning opportunities, i.e., this model's version of }effective lifespan, do vary across tasks, individuals, and species, yet most models assume only one learning opportunity per generation \citep{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
+While these phenomena map imperfectly onto effective lifespan in our model, given social learning is only allowed intergenerationally, the relative number of individual to social learning opportunities, i.e., this model's version of effective lifespan, do vary across tasks, individuals, and species, yet most models assume only one learning opportunity per generation \citep{BoydRicherson1985, Feldman1996,Henrich1998, perreault2012bayesian}.
 Some models do allow several cultural generations within one genetic generation \citep{Enquist2007,Rendell2010,lindstrom2016co}, but little formal theory explicitly examines the role of learning opportunities in the evolution of social learning.
@@
 social learning evolves as an adaptation to uncertainty, we endowed agents with an
-\edit{adaptive} cognition based on a softmax decision rule capable of integrating information from various sources to maximize payoffs~\citep{Gershman2019}, described in more detail below.
+adaptive cognition based on a softmax decision rule capable of integrating information from various sources to maximize payoffs~\citep{Gershman2019}, described in more detail below.
 
@@
 In other words, payoff ambiguity, and therefore uncertainty, increases with $\pilow$.
-Agents have $L$ time steps to \edit{act and learn asocially} per generation (i.e., the \emph{effective lifespan}).
+Agents have $L$ time steps to act and learn asocially per generation (i.e., the \emph{effective lifespan}).
 Uncertainty decreases with $L$.
@@
 Then the observed average payoffs known by agent $i$ for behavior $b$ are updated
-via \edit{moving arithmetic averaging},
+via moving arithmetic averaging,
 \begin{equation}
@@
 given %(implicit) 
-time step. \edit{This form allows the running mean payoffs to be calculated for each
+time step. This form allows the running mean payoffs to be calculated for each
 behavior, weighting each observation equally, without knowing in advance how many
@@
 provides a basic observational learning mechanism that may be further specified as
-appropriate for different cases.}
+appropriate for different cases.
 
@@
 By first subsetting $N_T$ prospective teachers we represent the fact that access to the entire population is not generally guaranteed, though this type of algorithm yields qualitatively similar results to ones that do not first produce subsamples \citep{smaldino2019open} and we show in the supplement that our results are robust to different $N_T$
-(Figure~\ref{fig:nteachersSensitivity}). Social learner $i$ adopts their chosen 
+(Figure~\ref{fig:nteachersSensitivity}).
+
+Social learner $i$ adopts their chosen 
 teacher $j$'s observed average payoffs for each behavior, $b$, i.e., 
@@
 one observation of behavior $b$, and $c_{ib}$ is set to 0 otherwise. This way, expected payoffs
-remain within $[0, 1]$, but social learners are flexible to adjust to environmental change. Setting
-$c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single
-observation with the associated uncertainty. \edit{If learners have more confidence
-in the teacher's information, or there are biological or cultural factors that more
-strongly weight teacher information, it may be more justifiable to set the learner's $c_{ib}$ to its teacher's $c_{jb}$}. Asocial learners ($s_i = 0$) are initialized with
+remain within $[0, 1]$, but social learners are flexible to adjust to environmental change.
+Setting $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single observation with the associated uncertainty, \edit{and serves as a useful baseline for understanding the interaction of different sources of uncertainty that we focus on here.
+In the real world this could represent the fact that some amount of information is always lost in social learning, through instruction or otherwise.
+If a learner's $c_{ib}$ is set instead to the teacher's $c_{jb}$, or some sizable fraction of it, learners will more slowly update their mean payoff values, making individual learning less adaptive, which could be desirable if there is good reason to have more confidence in a teacher's information, or there are other biological or cultural factors that make social learning more trustworthy.} Asocial learners ($s_i = 0$) are initialized with
 $c_{ib} = 0$ and $\ledger = 0$ for each behavior, $b$. % (Figure~\ref{fig:schematic}C). 
@@
 \begin{figure}
-  \caption{\edit{Model summary}. Agents are randomly initialized as social learners or not, with their
+  \caption{Model summary. Agents are randomly initialized as social learners or not, with their
   payoff observations all initialized to zero (A). Then agents begin selecting
@@
 %We varied $u \in \{0.0, 0.1, \ldots, 1.0\}$; $\pilow \in \{0.1, 0.45, 0.8\}$; $B \in \{2, 4, 10\}$; and $L \in \{1,2,4,8\}$ for $B=2$ and $L \in \{1,B/2,B,2B\}$ for $B=4,10$.
-\edit{We observed three outcome measures: first, the social learning (SL) fixation frequency, denoted $\meansl$, is how frequently social learning evolved to fixation across all trials for a given parameter setting.
-To support our analysis about why we observed the patterns in social learning fixation frequency that we did, we also measured the mean number of generations to fixation, which measures the strength of selection.} Finally we measured the average net payoffs at the end of the simulation across agents and trials, normalized by lifespan.
+We observed three outcome measures: first, the social learning (SL) fixation frequency, denoted $\meansl$, is how frequently social learning evolved to fixation across all trials for a given parameter setting.
+To support our analysis about why we observed the patterns in social learning fixation frequency that we did, we also measured the mean number of generations to fixation, which measures the strength of selection.
+Finally we measured the average net payoffs at the end of the simulation across agents and trials, normalized by lifespan.
 We analyze
@@
 learning monotonically decreases as temporal environmental variability, $u$,
-increases \edit{(Figure~\ref{fig:mainResults})}. 
+increases (Figure~\ref{fig:mainResults}). 
 When the environment is more likely to change between generations,
@@
 
-\edit{Across all parameter settings, we observed that there exists some threshold value of environmental
+Across all parameter settings, we observed that there exists some threshold value of environmental
 variability beyond which the evolution of social learning is exceedingly rare.  We call this the
@@
 the other uncertainty parameters and to highlight that social learning frequently 
-evolves despite high levels of environmental variability.}
+evolves despite high levels of environmental variability.
 
@@
 when the environment is more likely to change than not (i.e.,
-$u>0.5$\edit{---see Figure~\ref{fig:slCeiling}}).
+$u>0.5$---see Figure~\ref{fig:slCeiling}).
 
@@
 (left parts of plots on bottom row of Figure~\ref{fig:mainResults}). This reversal
-is partially explained by \edit{weaker selection} when there is little difference in the payoffs between
+is partially explained by weaker selection when there is little difference in the payoffs between
 behaviors, and by the fact that the quality of social information is poorer when payoffs are ambiguous and
 lifespans are short (more on these effects of payoff ambiguity below).  
-\edit{When $L$ becomes roughly equal to or greater than $B$ there is little marginal effect of increasing $L$, indicating that more individual learning experiences are unlikely to significantly affect an agent's ability to identify the optimal behavior in their lifetime.}
+When $L$ becomes roughly equal to or greater than $B$ there is little marginal effect of increasing $L$, indicating that more individual learning experiences are unlikely to significantly affect an agent's ability to identify the optimal behavior in their lifetime.
 % \cm{is this right? I thought we should say something about the exceptions in this paragraph though we describe in more detail below, but not sure I have the right explanation}
@@
 that \emph{do} reliably select the optimal behavior is relatively weak. This means
-\edit{selection} is weaker \emph{in favor} of social learning under low values of $u$ and
-\edit{weaker} \emph{against} social learning under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row). 
-This effect was especially \edit{pronounced} under other types of uncertainty, i.e., larger selection-set sizes and shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
-
-The effect of \edit{selection strength} when the benefit of social learning is ambiguous is powerful and complex.
+selection is weaker \emph{in favor} of social learning under low values of $u$ and
+weaker \emph{against} social learning under high values of $u$ (Figure~\ref{fig:mainResults}, bottom row). 
+This effect was especially pronounced under other types of uncertainty, i.e., larger selection-set sizes and shorter effective lifespans---particularly when $L=1$ where no individual learning occurred.
+
+The effect of selection strength when the benefit of social learning is ambiguous is powerful and complex.
 We explain how the frequency of social learning evolves in such circumstances in the following section.
@@
 \begin{figure}
-  \caption{\edit{Effect of four forms of uncertainty on evolution of social learning}. Social learning fixation frequency across trials (y-axes) monotonically decreases as 
+  \caption{Effect of four forms of uncertainty on evolution of social learning. Social learning fixation frequency across trials (y-axes) monotonically decreases as 
   environmental variability, $u$, increases (x-axes) in most uncertainty contexts. 
@@
 \begin{figure}
-  \caption{\edit{Effect of uncertainty on social learning ceiling.} As the selection-set size, $B$, and effective lifespan, $L$, increase (set equal along x-axis), 
+  \caption{Effect of uncertainty on social learning ceiling. As the selection-set size, $B$, and effective lifespan, $L$, increase (set equal along x-axis), 
   social learning frequently evolves across an increasingly large range of
@@
 
-\edit{To begin to confirm our interpretation of our analysis above, we measured
+To begin to confirm our interpretation of our analysis above, we measured
 strength of selection via the ensemble average of the number of
-time steps to fixation over all simulation trials for a given parameter setting. More steps to fixation here indicates weaker selection.} Strength of selection is the extent to which the
-social-learning trait provided agents with a consistent benefit. \edit{Selection
+time steps to fixation over all simulation trials for a given parameter setting. More steps to fixation here indicates weaker selection. Strength of selection is the extent to which the
+social-learning trait provided agents with a consistent benefit. Selection
 strength is minimal when social and asocial learning
-are equally beneficial.} 
+are equally beneficial. 
 % Even under consistent but weak selection pressure, drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}. 
@@
 
-When payoff ambiguity and selection-set size were small ($\pilow=0.1$ and $B=2$), and lifespan was long ($L \geq 4$), asocial learning fixated as a hedge against periods of protracted environmental instability, even though expected
+When payoff ambiguity and selection-set size were small ($\pilow=0.1$ and $B=2$), and lifespan
+was long ($L \geq 4$), asocial learning fixated \edit{because} periods of protracted
+environmental instability \edit{caused social learners to more severely underperform compared
+to asocial learners}, even though expected
 homogeneous social payoffs were greater than homogeneous asocial payoffs (Figure~\ref{fig:payoffTimeseries}A).
 Runs of environmental change strongly affected the geometric mean fitness of social learners who were weighing
-outdated information too heavily.
-\edit{In other words, environmental change lowers social learners' mean payoffs, but social-learner payoffs build back up as the information quality in the population improves (blue dots, Figure~\ref{fig:payoffTimeseries}A).
-Even though a homogenous population of social learners would outperform individual learners in this case, unpredictable environmental stochasticity undermines the reliability of social learning.
-When lifespan was minimal ($L=1$) and environmental variability was moderate ($u\approx0.5$), the opposite, unexpected outcome could occur where social learning fixates despite the fact that a homogenous population of asocial learners would outperform a homogenous population of social learners (Figure~\ref{fig:payoffTimeseries}B).
-In this case, it takes relatively few consecutive generations with environmental stability to attract the population to all become social learners.}
-
+outdated information too heavily. In other words, environmental change lowers social learners'
+mean payoffs, but social-learner payoffs build back up as the information quality in the
+population improves (blue dots, Figure~\ref{fig:payoffTimeseries}A). Even though a homogenous
+population of social learners would outperform individual learners in this case, unpredictable
+environmental stochasticity undermines the reliability of social learning. When lifespan was
+minimal ($L=1$) and environmental variability was moderate ($u\approx0.5$), the opposite,
+unexpected outcome could occur where social learning fixates despite the fact that a homogenous
+population of asocial learners would outperform a homogenous population of social learners
+(Figure~\ref{fig:payoffTimeseries}B).
+In this case, it takes relatively few consecutive generations with environmental stability to attract the population to all become social learners \edit{since social learners greatly outperform asocial learners during longer periods of environmental stability}.
 \begin{figure}
@@
 \begin{figure}
-  \addtocounter{figure}{-1}
+  % \addtocounter{figure}{-1}
     \caption{Example time series of geometric moving average (GMA) with window of 3
@@
 is fraught with uncertainty. Our model demonstrated that social learning can act
-as a scaffold for \edit{adaptive} individual learning. We endowed agents with a
-biologically-plausible individual learning mechanism \edit{based on a softmax decision rule}. This
+as a scaffold for adaptive individual learning. We endowed agents with a
+biologically-plausible individual learning mechanism based on a softmax decision rule. This
 enabled agents to recover from the potential cost of receiving outdated
@@
 between thirst and drinking water, or between friendship and warm laughter.
-\edit{If there were an exogenous cost of individual learning, this would likely
+If there were an exogenous cost of individual learning, this would likely
 increase the social learning ceiling across uncertainty parameter settings.
@@
 models that allowed for persistent frequency
-dependence of social learning benefit~\citep{BoydRicherson1985,Rogers1988,Feldman1996}.} Second, we only allow for
+dependence of social learning benefit~\citep{BoydRicherson1985,Rogers1988,Feldman1996}. Second, we only allow for
 intergenerational social learning and environmental change. Within generations,
 agents can only learn individually.
-This assumption \edit{is consistent with previous modeling work starting at least from \cite{Rogers1988}, and therefore} allows us to replicate the classic finding that if the environment changes too quickly, socially-learned information may become \edit{outdated.
+This assumption is consistent with previous modeling work starting at least from \cite{Rogers1988}, and therefore allows us to replicate the classic finding that if the environment changes too quickly, socially-learned information may become outdated.
 Adding horizontal social learning between vertical/oblique learning in this model would likely expand the range of environmental variability over which social learning would evolve~\citep{Turner2022}, i.e., horizontal learning would increase what we have called the social learning ceiling.
@@
 example if the generations are purely cultural ‘generations’ where parents, and
-others of the parent's generation, may also be peers.}
+others of the parent's generation, may also be peers.
 
@@
 choice maximizes the potential benefit to social learners, which suggests that
-other mechanisms, like conformity, may lead to \edit{weaker selection} overall. 
-\edit{Furthermore, our social learning procedure could be interpreted as direct copying of latent psychological variables (expected payoffs for each behavior).
-Such detailed information is most likely transmitted through teaching wherein the model explicitly informs the learner of their experiences.
-If children learned instead from observations of the parent's behaviors without knowing rewards, which in some cases would be a more realistic assumption~\citep{Wu2022b}, this may weaken the strength of selection for social learning.} We also assumed that the number of behaviors and their payoffs were constant within a
+other mechanisms, like conformity, may lead to weaker selection overall. 
+Furthermore, our social learning procedure could be interpreted as direct copying of latent psychological variables (expected payoffs for each
+behavior). Such detailed information is most likely transmitted through teaching wherein the model explicitly informs the learner of their
+experiences. If children learned instead from observations of the parent's behaviors without knowing rewards, which in some cases would be a more
+realistic assumption~\citep{Wu2022b}, this may weaken the strength of selection for social learning. 
+We also assumed that the number of behaviors and their payoffs were constant within a
 given simulation, but this fails to account for evolutionary feedback which creates
-new behavioral opportunities as time progresses\edit{~\citep{Chimento2022}}, e.g., via niche
+new behavioral opportunities as time progresses~\citep{Chimento2022}, e.g., via niche
 construction~\citep{Smaldino2012a,Heras-Escribano2020} or cumulative cultural
@@
 learners~\citep{Golub2012}.
-We assumed agents choose behaviors via a softmax \edit{decision rule, which is more cognitively sophisticated than most social-learning models and captures the adaptiveness of real human learning mechanisms.
-This modeling decision was essential for developing our understanding of how social and individual learning can combine to multiply the problem solving capacity of our agents, though it is still a pale shadow of the true sophistication of human learning capabilities~\citep{Schulz2020a,Wu2022}}.
+We assumed agents choose behaviors via a softmax decision rule, which is more cognitively sophisticated than most social-learning models and captures the adaptiveness of real human learning mechanisms.
+This modeling decision was essential for developing our understanding of how social and individual learning can combine to multiply the problem solving capacity of our agents, though it is still a pale shadow of the true sophistication of human learning capabilities~\citep{Schulz2020a,Wu2022}.
 More realistic and powerful individual learning could further support the evolution of
@@
 %We found that the 
-The evolution of social learning is a complex phenomenon, dependent on many interrelated factors, yet it is widespread across a
-range of taxa. Although social learning is broadly studied, few studies have taken a systematic approach to understanding the role
-of uncertainty in the evolution \edit{of} social learning. Understanding the role of uncertainty in social evolution is particularly important
-for understanding human evolution as evidence increasingly suggests that the genus \emph{Homo} emerged in the context of substantial
-(nonstationary) environmental variability \citep{anton_etal2014, levin2015}, and our global dispersal
-\edit{meant} that human groups regularly faced novel environments. \edit{These
-conditions and our longevity obviated the possibility of genetic
-adaptation to specific ecological circumstances, requiring instead the evolution of
-learning mechanisms for dealing with uncertainty. In our model, numerous behavioral
+% The evolution of social learning is a complex phenomenon, dependent on many interrelated factors, yet it is widespread across a
+% range of taxa. Although social learning is broadly studied, few studies have taken a systematic approach to understanding the role
+% of uncertainty in the evolution of social learning. 
+In our model, numerous behavioral
 options led agents to be more cognitively flexible via the softmax decision rule, and
 thus better able to adjust their behavior if social learning provided outdated
-information.
-While Rogers'-style models of social learning evolution may also predict greater social learning reliance in more challenging contexts (larger selection-set sizes), these models rely on limited individual learning mechanisms that are furthermore mutually exclusive with social learning.
-This may prevent social learning from evolving under such high values of environmental variability as we observed here, even if these models included more adaptive individual learning mechanisms.}
+information. This 
+explains why human social learning is widespread despite
+the fact that that the genus \emph{Homo} emerged in, and continues to face, substantial
+nonstationary environmental variability \citep{anton_etal2014, levin2015}:
+in our model social learning is supported by the ability to adaptively combine socially- and individually-acquired information.
+% and our global dispersal meant that human groups regularly faced novel environments. 
+Variable conditions and \emph{Homo} longevity have often obviated the possibility of genetic
+adaptation to most specific ecological circumstances, requiring instead the evolution of
+learning mechanisms for dealing with uncertainty. This has been demonstrated somewhat in previous Rogers'-style models of social
+learning evolution, but these models relied on limited individual learning mechanisms that are
+furthermore mutually exclusive with social learning. This may prevent social learning from
+evolving under such high values of environmental variability as we observed here.
+% , even if these models included more adaptive individual learning mechanisms.
+
 By carefully identifying and operationalizing different forms of uncertainty common in social-learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution.
@@
 The results deviate only in minor ways from the main results primarily because of
-\edit{weaker selection}
+weaker selection
 due to (1) finite population size effects (smaller $N$);
@@
 curve of $\meansl$ over $u$ becomes more linear with increasing $B$, 
-with $\meansl$ values pulled towards \edit{neutral selection}, $\meansl \to 0.5$ (Figure~\ref{fig:populationSensitivity}a,
+with $\meansl$ values pulled towards neutral selection, $\meansl \to 0.5$ (Figure~\ref{fig:populationSensitivity}a,
 purple curves). With
@@
 as $u$ increases, more social learning across $u$ for larger $B$, and the
-same complex \edit{selection-strength} effects for combinations of $\pilow$ and $L$ that interact
+same complex selection-strength effects for combinations of $\pilow$ and $L$ that interact
 with $u$ and $B$ settings.
@@
 We found that the number of prospective teachers had little effect on $\meansl$
-over $u$. There was slightly \edit{weaker selection} when $N_T = 2$ compared to our 
-main text analysis, slightly \edit{stronger selection} than our main analysis when $N_T = 20$; 
+over $u$. There was slightly weaker selection when $N_T = 2$ compared to our 
+main text analysis, slightly stronger selection than our main analysis when $N_T = 20$; 
 we also tested $N_T=10$, which showed no obvious difference from our main results
-with $N_T = 5$. When $N_T = 2$, \edit{weakened selection} is most pronounced in the
+with $N_T = 5$. When $N_T = 2$, weakened selection is most pronounced in the
 $\meansl$ curves when $\pilow=0.8$ (Figure~\ref{fig:nteachersSensitivity}a, 
@@
 First, when $\beta=1$, most general trends are preserved, but in many cases the evolution
-of social learning is suppressed, \edit{or selection strength weakens}, due to 
+of social learning is suppressed, or selection strength weakens, due to 
 the overall poor quality of information acquired through softmax search-based
-individual learning with this setting. \edit{Weakened selection} is especially pronounced 
+individual learning with this setting. Weakened selection is especially pronounced 
 when $\pilow=0.8$ since sub-optimal behaviors often pay off and $\beta=1$ is

### 2023-04-04 ms.tex
removed edit tags

@@
 remain within $[0, 1]$, but social learners are flexible to adjust to environmental change.
-Setting $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single observation with the associated uncertainty, \edit{and serves as a useful baseline for understanding the interaction of different sources of uncertainty that we focus on here.
+Setting $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single observation with the associated uncertainty, and serves as a useful baseline for understanding the interaction of different sources of uncertainty that we focus on here.
 In the real world this could represent the fact that some amount of information is always lost in social learning, through instruction or otherwise.
-If a learner's $c_{ib}$ is set instead to the teacher's $c_{jb}$, or some sizable fraction of it, learners will more slowly update their mean payoff values, making individual learning less adaptive, which could be desirable if there is good reason to have more confidence in a teacher's information, or there are other biological or cultural factors that make social learning more trustworthy.} Asocial learners ($s_i = 0$) are initialized with
+If a learner's $c_{ib}$ is set instead to the teacher's $c_{jb}$, or some sizable fraction of it, learners will more slowly update their mean payoff values, making individual learning less adaptive, which could be desirable if there is good reason to have more confidence in a teacher's information, or there are other biological or cultural factors that make social learning more trustworthy.
+Asocial learners ($s_i = 0$) are initialized with
 $c_{ib} = 0$ and $\ledger = 0$ for each behavior, $b$. % (Figure~\ref{fig:schematic}C). 
@@
 When payoff ambiguity and selection-set size were small ($\pilow=0.1$ and $B=2$), and lifespan
-was long ($L \geq 4$), asocial learning fixated \edit{because} periods of protracted
-environmental instability \edit{caused social learners to more severely underperform compared
-to asocial learners}, even though expected
+was long ($L \geq 4$), asocial learning fixated because periods of protracted
+environmental instability caused social learners to more severely underperform compared
+to asocial learners, even though expected
 homogeneous social payoffs were greater than homogeneous asocial payoffs (Figure~\ref{fig:payoffTimeseries}A).
@@
 (Figure~\ref{fig:payoffTimeseries}B).
-In this case, it takes relatively few consecutive generations with environmental stability to attract the population to all become social learners \edit{since social learners greatly outperform asocial learners during longer periods of environmental stability}.
+In this case, it takes relatively few consecutive generations with environmental stability to attract the population to all become social learners since social learners greatly outperform asocial learners during longer periods of environmental stability.
 \begin{figure}

### 2023-04-13 ms.tex
Updates from Overleaf

@@
 \emph{Risk} represents a decision with a variable payoff where the state space and probabilities associated with the different outcomes are both known.
-In contrast, \emph{uncertainty} implies that the outcome probabilities, and possibly the state space, are not known \citep{knight1921, keynes1921}.
+In contrast, \emph{uncertainty} implies that the outcome probabilities, and possibly the state space, are not known \citep{knight1921, keynes1921, johnson_etal2022}.
 Furthermore, usage of the term uncertainty often conflates several different interpretations of that word.
@@
 (the difference in the expected rewards for different behaviors); and (4) the effective lifespan of agents (the number of
-opportunities for individual learning), see next section for more details. In our model, social learners learn from the previous
+opportunities for individual learning). In our model, social learners learn from the previous
 generation and asocial learners do not. All agents engage in individual learning
-within their lifespans. The model also assumes an adaptive,
+within their lifespans. The model also assumes that agents use an adaptive,
 empirically-motivated learning mechanism, the softmax decision rule, which allows learners to make full use of the available data acquired by both individual and social learning \citep{SuttonBartoBook}.
@@
 \paragraph{Selection-set size.}
-When one does not know which option to take, uncertainty increases with the number of options, which we call the selection-set size.
+When one does not know which option to take, uncertainty increases with the number of options. We call this selection-set size.
 % This is a mathematical fact at the
@@
 perreault2012bayesian}.
-Larger, more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\citep{derex2013, wasielewski2014}, but these map imperfectly onto the theoretical literature that tends to use a limited set of behavioral options.
+Larger, more open sets of behavioral choices are not uncommon in experiments trying to capture more complex or naturalistic tasks~\citep{derex2013, wasielewski2014}, but these map imperfectly onto a theoretical literature that tends to use a limited set of behavioral options.
 Some models have studied systems with larger, but defined, selection sets~\citep{Rendell2010, lindstrom2016co}, while in others the number of options is subsumed under the probability that a learner gets the right  answer~\citep{Feldman1996,Enquist2007}.
@@
 perreault2012bayesian}, including those that integrate cognitively plausible
-mechanisms such as reinforcement learning \citep{lindstrom2016co}, though the latter
-approach remains the exception rather than the norm. In order to understand how
-social learning evolves as an adaptation to uncertainty, we endowed agents with an
-adaptive cognition based on a softmax decision rule capable of integrating information from various sources to maximize payoffs~\citep{Gershman2019}, described in more detail below.
+mechanisms such as reinforcement learning \citep{lindstrom2016co}.
+This approach, however, remains the exception rather than the norm.
+In order to understand how social learning evolves as an adaptation to uncertainty, we endowed agents with an adaptive cognition based on a softmax decision rule capable of integrating information from various sources to maximize payoffs~\citep{Gershman2019}, described in more detail below.
 
@@
 Setting $c_{ib}$ to 1 reflects the fact that the social learner treats the teacher's information as a single observation with the associated uncertainty, and serves as a useful baseline for understanding the interaction of different sources of uncertainty that we focus on here.
-In the real world this could represent the fact that some amount of information is always lost in social learning, through instruction or otherwise.
-If a learner's $c_{ib}$ is set instead to the teacher's $c_{jb}$, or some sizable fraction of it, learners will more slowly update their mean payoff values, making individual learning less adaptive, which could be desirable if there is good reason to have more confidence in a teacher's information, or there are other biological or cultural factors that make social learning more trustworthy.
+In the real world this could represent the fact that some amount of information is always lost in direct instruction or other forms of social learning.
+If a learner's $c_{ib}$ is set instead to the teacher's $c_{jb}$, or some sizable fraction of it, learners will update their mean payoff values more slowly, making individual learning less adaptive.
+This could be desirable if there is good reason to have more confidence in a teacher's information, or there are other biological or cultural factors that make social learning more trustworthy.
 Asocial learners ($s_i = 0$) are initialized with
@@
 When payoff ambiguity and selection-set size were small ($\pilow=0.1$ and $B=2$), and lifespan
-was long ($L \geq 4$), asocial learning fixated because periods of protracted
-environmental instability caused social learners to more severely underperform compared
+was long ($L \geq 4$), asocial learning fixated because periods of extended
+environmental instability (see environmental changes after generation 50 in  Figure~\ref{fig:payoffTimeseries}A) caused social learners to more severely underperform compared
 to asocial learners, even though expected
-homogeneous social payoffs were greater than homogeneous asocial payoffs (Figure~\ref{fig:payoffTimeseries}A).
-Runs of environmental change strongly affected the geometric mean fitness of social learners who were weighing
+homogeneous social payoffs were greater than homogeneous asocial payoffs. Runs of environmental change strongly affected the geometric mean fitness of social learners who were weighing
 outdated information too heavily. In other words, environmental change lowers social learners'
@@
 increase the social learning ceiling across uncertainty parameter settings.
-This means that our model does not capture the information-scrounging rewards to individual learning that produce mixed equilibria in precursor models \cite{Rogers1988}.
+This means that our model does not capture the information-scrounging rewards to individual learning that produce mixed equilibria in precursor models \citep{Rogers1988}.
 Furthermore, our model operationalizes environmental variability as fully stochastic in a finite population.
@@
 will be important to the development of more parsimonious theories of social learning.  
-For example, we only considered success-biased learning, although people may use conformity or other context biases to socially learn~\citep{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.
+For example, we only considered success-biased learning, while people may use conformity or other context biases to  learn socially~\citep{BoydRicherson1985,Muthukrishna2016a,Smaldino2018b}.
 This modeling
@@
 behavior). Such detailed information is most likely transmitted through teaching wherein the model explicitly informs the learner of their
-experiences. If children learned instead from observations of the parent's behaviors without knowing rewards, which in some cases would be a more
-realistic assumption~\citep{Wu2022b}, this may weaken the strength of selection for social learning. 
+experiences. If children learned instead from observations of the parent's behaviors without knowing rewards, which in some cases, would be a more
+realistic assumption~\citep{Wu2022b}, the strength of selection for social learning would likely be weakened. 
 We also assumed that the number of behaviors and their payoffs were constant within a
@@
 We assumed agents choose behaviors via a softmax decision rule, which is more cognitively sophisticated than most social-learning models and captures the adaptiveness of real human learning mechanisms.
-This modeling decision was essential for developing our understanding of how social and individual learning can combine to multiply the problem solving capacity of our agents, though it is still a pale shadow of the true sophistication of human learning capabilities~\citep{Schulz2020a,Wu2022}.
+This modeling decision was essential for developing our understanding of how social and individual learning can combine to multiply the problem-solving capacity of our agents, though it is still a pale shadow of the true sophistication of human learning capabilities~\citep{Schulz2020a,Wu2022}.
 More realistic and powerful individual learning could further support the evolution of
@@
 nonstationary environmental variability \citep{anton_etal2014, levin2015}:
-in our model social learning is supported by the ability to adaptively combine socially- and individually-acquired information.
+in our model, social learning is supported by the ability to adaptively combine socially- and individually-acquired information.
 % and our global dispersal meant that human groups regularly faced novel environments. 
-Variable conditions and \emph{Homo} longevity have often obviated the possibility of genetic
+Variable conditions and long lifespan have often obviated the possibility of genetic
 adaptation to most specific ecological circumstances, requiring instead the evolution of
-learning mechanisms for dealing with uncertainty. This has been demonstrated somewhat in previous Rogers'-style models of social
+learning mechanisms for dealing with uncertainty. This has been demonstrated somewhat in previous models of social
 learning evolution, but these models relied on limited individual learning mechanisms that are

### 2023-04-28 ms.tex
final version for publication

@@
 \maketitle
+\noindent
+\textbf{Social media summary:} You won’t believe this one weird adaptive trick social learners use{\ldots}asocial
+learners hate it! \\
+\textbf{Keywords:} Uncertainty, social learning, cultural evolution, agent-based modeling \\
 \clearpage
@@
 agent is unsure. To do softmax searching, agents track average payoffs acquired
-from each behavior they have performed, which requires knowing the number of times they have performed each behavior.
-The probability that the agent will perform a behavior is a function of the agent's beliefs about a behavior's average payoff in that time step and a fixed parameter that influences the amount of exploratory behavior (more details below).
-The softmax function used here is a biologically plausible generalization of behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative behavior they have observed, but also to sometimes explore alternatives~\citep{Schulz2019,Collins2013,Daw2006,Yechiam2005}.
+from each behavior they have performed, which requires knowing the number of times they have performed each
+behavior. The probability that an agent will perform a behavior is a function of the agent's beliefs about a
+behavior's average payoff in that time step and a fixed parameter that influences the amount of exploratory
+behavior (more details below). The softmax function used here is a biologically plausible generalization of
+behavior selection under uncertainty that enables agents to often greedily exploit the most lucrative
+behavior they have observed, but also to sometimes explore
+alternatives~\citep{Yechiam2005,Daw2006,Collins2013,Schulz2019}.
 
@@
 denoted $c_{ib}$. At model initialization, $\ledger = 0.0$ and $c_{ib} = 0$ for
-all $i$ and $b$.% (Figure~\ref{fig:schematic}A).
+all $i$ and $b$. % (Figure~\ref{fig:schematic}A).
 One of the behaviors is chosen at random to yield expected payoff $\pihigh$, with the other $B-1$ behaviors yielding
@@
 \begin{figure}
-  \caption{Model summary. Agents are randomly initialized as social learners or not, with their
-  payoff observations all initialized to zero (A). Then agents begin selecting
-and performing behaviors and accumulating payoffs, which goes on for $L$
-timesteps (B). After $L$ time steps, agents are selected to reproduce,
-social learner children learn from a member of their parent's generation, and
-the previous generation dies off (C). The simulation stops if children are all
-social or asocial learners (i.e.\ the system reaches fixation).
+  \caption{Model summary.
+Agents are randomly initialized as social learners or not, with their payoff observations all initialized to zero (A).
+Then agents begin selecting and performing behaviors and accumulating payoffs, which goes on for $L$ timesteps (B).
+After $L$ time steps, agents are selected to reproduce, social learner children learn from a member of their parent's generation, and the previous generation dies off (C).
+The simulation stops if children are all social or asocial learners (i.e.\ the system reaches fixation).
 Otherwise it repeats another generation and evolution continues.}
@@
 more likely to err by ascribing high value to non-optimal behaviors, since it is
-more difficult for them to discern the difference between optimal and sub optimal
+more difficult for them to discern the difference between optimal and suboptimal
 behaviors. Second, and perhaps more importantly, natural selection on strategies
@@
 % Even under consistent but weak selection pressure, drift can cause a population to take longer to reach fixation \citep{plutynski2007drift}. 
-We denote the ensemble average over simultaion trials of the number of generations to fixation, denoted $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
+We denote the ensemble average over simultaion trials of the number of generations to fixation as $\langle G \rangle$, where fixation means that the number of social learners, $\sum_i s_i$, is equal to either zero or $N$.
 %Indeed, social learning evolution and drift are reflected in the relative benefit of social learning to asocial learning.
 
-Figure~\ref{fig:steps} shows the average number of generations to fixation across all uncertainty parameters.
-Drift was greatest overall when payoff ambiguity was greatest, i.e., when $\pilow = 0.8$.
+Figure~\ref{fig:steps} shows the average number of generations to fixation across all uncertainty
+parameters.
+Strength of selection was weakest overall when payoff ambiguity was greatest, i.e., when $\pilow = 0.8$.
 When payoffs are highly ambiguous there is relatively little advantage to the optimal learning strategy, and therefore relatively weak selective pressure.
@@
 Figure~\ref{fig:payoffs} shows the average net payoffs normalized by lifespan
-for our main simulation compared with the two reference homogeneous populations
+from a selection of our main simulations compared with the two reference homogeneous populations
 initialized either as all-social or all-asocial learners.
@@
 population improves (blue dots, Figure~\ref{fig:payoffTimeseries}A). Even though a homogenous
-population of social learners would outperform individual learners in this case, unpredictable
+population of social learners would outperform asocial learners in this case, unpredictable
 environmental stochasticity undermines the reliability of social learning. When lifespan was
@@
   % \addtocounter{figure}{-1}
-    \caption{Example time series of geometric moving average (GMA) with window of 3
-      of payoffs from two select uncertainty settings (see main text), broken out by
-    social learners, asocial learners, and whole population, compared with the
-    expected homogeneous social and asocial population payoffs. Social-learner prevalence is also plotted. Vertical lines indicate environmental change.}
+    \caption{Example time series of geometric moving average (GMA) with window of 3 of payoffs from two select uncertainty settings (see main text), broken out by social learners, asocial learners, and whole population, compared with the expected homogeneous social and asocial population payoffs.
+Social-learner prevalence is also plotted.
+Vertical lines indicate environmental change.}
     \label{fig:payoffTimeseries}
@@
 
-By carefully identifying and operationalizing different forms of uncertainty common in social-learning models, we developed a more thorough understanding of how uncertainty can favor social learning and how different forms of uncertainty interact to favor its evolution.
-By explicitly modeling a key individual-level learning mechanism shared across taxa, namely the ability to adjust behavior to uncertainty and new information, we found that social learning could evolve even if it provides outdated information.
+By carefully identifying and operationalizing different forms of uncertainty common in social-learning
+models, we developed a more thorough understanding of how uncertainty can favor social learning and how
+different forms of uncertainty interact to favor its evolution. By explicitly modeling a key
+individual-level learning mechanism shared across taxa, namely the ability to adjust behavior to uncertainty
+and new information, we found that social learning could evolve even if it regularly provides outdated information.
 %Social learning is a critical component of problem solving among social creatures.
@@
 
-\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \url{https://osf.io/tpsy9}. Model and analysis code is
-publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}), and the data used to make the figures presented here is available via OSF
-(\url{https://osf.io/t8exa/}). A guide to running the analyses is available on the GitHub repository.
+\paragraph{Supplementary material.} Supplemental analyses confirming model robustness to free parameters is available at \url{https://osf.io/tpsy9}.
 
@@
 \paragraph{Author contributions.} JHJ, CM, PES, and MAT conceived of the project. MAT developed the model
-and analyses, with contributions from CM, PES, and JHJ.
-MAT implemented and analyzed the model.
-MAT wrote and edited the initial manuscript draft, which was extensively expanded and edited by CM, PES, and JHJ.
+and analyses, with contributions from CM, PES, and JHJ. MAT implemented and analyzed the model. MAT wrote and edited the initial manuscript draft, which was expanded and edited by CM, PES, and JHJ.
 
 \paragraph{Financial support.} This work was supported by NSF grants BCS-2028160 and BCS-2118926 (JHJ PI) and awards from the Center for Innovation in Global Health and the Center for Existential Risk, Stanford University to JHJ.
+
+\paragraph{Research transparency and reproducibility.}
+Model and analysis code is publicly available on GitHub (\url{https://github.com/mt-digital/UncMod}).  
+A guide to running the analyses is available on the GitHub repository.
+The code version used to generate the results presented here has been archived
+with a persistent identifier through Zenodo: \url{https://doi.org/10.5281/zenodo.7873161}.
+
+\paragraph{Data availability statement.} 
+The data used to make the figures presented here is available via OSF
+(\url{https://osf.io/t8exa/}).
 
@@
 % 	\caption{$N_T = 10$}
-% 	\includegraphics[width=\textwidth]{Figures/supplement/nteachers=10/mainResultsPlots.pdf}
+% 	\includegraphics[width=\textwidth]{Figures/nteachers=10/mainResultsPlots.pdf}
 %   \end{subfigure}
